### 2021-01-01 main.tex
Initial Overleaf Import

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[cancers,article,submit,moreauthors,pdftex]{Definitions/mdpi}

% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
%journal Cancers
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, appliedchem, applmech, applmicrobiol, applnano, applsci, arts, asi, atmosphere, atoms, audiolres, automation, axioms, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomechanics, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, brainsci, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coatings, colloids, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, crops, cryptography, crystals, curroncol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forensicsci, forests, fractalfract, fuels, futureinternet, futuretransp, futurepharmacol, futurephys, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, land, languages, laws, life, liquids, literature, livers, logistics, lubricants, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, metabolites, metals, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, minerals, mining, modelling, molbank, molecules, mps, mti, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photochem, photonics, physchem, physics, physiolsci, plants, plasma, pollutants, polymers, polysaccharides, proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, systems, taxonomy, technologies, telecom, textiles, thermo, tourismhosp, toxics, toxins, transplantology, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wevj, women, world

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2021}
\copyrightyear{2021}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
\dateaccepted{} 
\datepublished{}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% MDPI internal command: Title for citation in the left column
\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-4476-2600} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-6497-4232} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{
Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
Michael Hsiao $^{3}$*
and Yu-Chuan (Jack) Li $^{1,4}$*\orcidB{}}
%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Li-Hsing Chi, Alexander TH Wu, Michael Hsiao and Yu-Chuan (Jack) Li}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Chi, LH.; Wu, ATH.; Hsiao, M.; Li, YCJ.}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
$^{3}$ \quad Genomics Research Center\unskip, 
    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
}

% Contact information of the corresponding author
\corres{Correspondence: Hsiao: mhsiao@gate.sinica.edu.tw; Li: jaak88@gmail.com}
%(optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis. There is some optimization software for cutoff determination. However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses. There are few clinicopathological features available on their pre-processed data sets.
We developed a comprehensive workflow that includes data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes. After adjustment with confounders and Bonferroni adjusted P-value, ten candidate biomarkers, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival. At the same time, the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
We suggest this workflow could help for biomarker discovery.}

% Keywords
\keyword{Head and Neck Squamous Cell Carcinoma (HNSCC);
%Genome Database\sep
the Cancer Genome Atlas (TCGA);
RNA-sequencing;
Survival Analysis;
Optimal Cutoff;
%Biomarker\sep % Discovery\sep
%Tumor Type-agnostic Therapy\sep
%Immuno-Oncology\sep
%Targeted Therapy\sep
%Systemic Therapy\sep
Surgical Margin}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}

%The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}

% The MDPI table float is called specialtable
\begin{specialtable}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
%%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabular}
\end{specialtable}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:

\begin{equation}
a = 1,
\end{equation}

the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

\end{paracol}
\nointerlineskip
%\begin{equation}
%a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
%\end{equation}

% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
\begin{figure}[H]	
\widefigure
\includegraphics[width=15 cm]{Definitions/logo-mdpi}
\caption{This is a wide figure.\label{fig2}}
\end{figure}  
\begin{paracol}{2}
\linenumbers
\switchcolumn

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals.}

\informedconsent{Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.}

\dataavailability{Please refer to suggested Data Availability Statements in section “MDPI Research Data Policies” at \href{https://www.mdpi.com/ethics}{https://www.mdpi.com/ethics}.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}

%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendix
\section{}
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{paracol}
\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} stage of publication (under review; accepted; in~press).
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of Presentation. In Title of the Collected Work (if available), Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference; Editor 1, Editor 2, Eds. (if available); Publisher: City, Country, Year (if available); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2021-01-01 main.tex
Updates from Overleaf

@@
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.
+Head and neck squamous cell carcinoma (\acrshort{hnscc}), including oral, oropharyngeal, and hypopharyngeal origin, is the fourth leading cancer causes of death for males in Taiwan\cite{MOHW_death2017}.
+The age-standardized incidence rate of \acrshort{hnscc} in males is 42.43 per 100,000 persons\cite{MOHW_incidence2018}.
+% chemotherapy => systemic therapy
+The treatment strategies of \acrshort{hnscc} are surgery alone, systemic therapy with concurrent radiation therapy (systemic therapy/\acrshort{rt}), or surgery with adjuvant systemic therapy/\acrshort{rt} (according to \acrlong{nccn}, \acrshort{nccn} Clinical Practice Guidelines in \acrshort{hnscc}, Version 2.2020)\cite{Pfister2020a}.
+Despite the improvement in those interventions, the survival of \acrshort{hnscc} has improved only marginally over the past decade worldwide\cite{hpa2019}.
+The critical advancement of targeted therapy and immuno-oncology should benefit from emerging prognostic biomarkers, which guide the development of modern systemic therapy.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
+%% TP53 gene => p53 protein; mutation of TP53
+Accumulative knowledge showed that some biomarkers have prognostic significance in \acrshort{hnscc}.
+For example, node-negative \acrshort{hnscc} patients with p53 overexpression were found to have lower survival\cite{DeVicente2004}.
+Overexpression of \acrfull{hif}-1 alpha\cite{Aebersold2001} or Ki-67\cite{Couture2002} was found to be correlated with poor response to radiotherapy of \acrshort{hnscc}.
+The \acrfull{egfr}\cite{O-Charoenrat2000}\cite{Bentzen2005} and \acrfull{mmp}\cite{Harrington2017} were found to be over-expressed to promote invasion and metastasis of \acrshort{hnscc}.
+From 2000 to 2006, the anti-\acrshort{egfr} antibody-drug (cetuximab) has been developed and combined with radiotherapy, known as bio-\acrshort{rt}, to increase survival of unresectable locoregionally advanced disease\cite{Bonner2006a}.
+The systemic therapy of cetuximab plus platinum-fluorouracil chemotherapy (EXTREME regimen) improves overall survival when given as first-line treatment in patients with recurrent or metastatic \acrshort{hnscc}\cite{Vermorken2008}\cite{Rivera2009}.
+It was approved by the \acrshort{us} \acrfull{fda} in 2008.
+In advance, the bio-\acrshort{rt} could have proceeded with \acrfull{tpf} induction chemotherapy to overcome the radio-resistance of \acrshort{hnscc}\cite{Blanchard2013}.
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+However, Rampias and his colleagues suggested \acrfull{hras} mutations could mediate cetuximab resistance in systemic therapy of \acrshort{hnscc} via the \acrshort{egfr}/\acrfull{ras}/\acrfull{erk} signaling pathway\cite{Rampias2014}.
+After that, the \acrshort{egfr} \acrfull{tki} was introduced to help cetuximab in 2018.
+The anti-tumor activity was observed in a phase 1 trial for \acrshort{hnscc} patients using cetuximab and afatinib, a \acrshort{tki} of \acrshort{egfr}, \acrfull{her}2, and \acrshort{her}4\cite{Gazzah2018}.
+Other \acrshort{egfr} \acrshort{tki}, such as gefitinib, erlotinib, osimertinib, were also developed to treat advanced \acrshort{hnscc}.
+Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients.
+So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+Until the immuno-oncology era, \acrfull{ici} was introduced since 2014 for treating \acrshort{hnscc}\cite{Seiwert2014}\cite{Swanson2015}.
+The \acrshort{ici} works on immune checkpoint molecules, which including \acrfull{pd1}, \acrfull{ctla4}, \acrfull{tim3}, \acrfull{lag3}, \acrfull{tigit}, \acrfull{gitr} and \acrfull{vista}\cite{Mei2020}.
+The \acrshort{us} \acrshort{fda} has approved the anti-\acrshort{pd1} agents, pembrolizumab, and nivolumab, as a monotherapy for the platinum-treated patients of recurrent or metastatic \acrshort{hnscc}\cite{Cramer2019}.
+However, because of the complexity of immune-tumor interaction, \acrshort{ici} has not to guarantee the response to \acrfull{pdl1} expressed \acrshort{hnscc}\cite{Swanson2015}.
+According to the phase 3 KEYNOTE-048 study, \acrshort{pdl1} is a validated biomarker used in clinical guidance for candidate selection of pembrolizumab\cite{Burtness2019}\cite{Gavrielatou2020}.
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+In our previous proteomic study in 2017, \acrfull{tmsb4x} was reported to be related to tumor growth and metastasis of \acrshort{hnscc}\cite{Chi2017}.
+It was also found by the subsequent investigations that \acrshort{tmsb4x} engaged in tumor aggressiveness through \acrfull{emt} on pancreatic\cite{Zhang2008}, gastric\cite{Ryu2012}, colorectal\cite{Gemoll2015}, lung\cite{Huang2016}, ovarian\cite{Chu2019} and melanoma\cite{Makowiecka2019} cancers.
+Thus, it might be suggested that \acrshort{tmsb4x}  is possible for tumor type-agnostic therapy\cite{Yan2018} as a common biomarker crossing several types of cancer.
+%TMSB4X proteins regulate intracellular signal transduction and has been proved to overexpress in various cancers, including colorectal, lung, gastric, pancreatic, and squamous cell cancers.\cite{Chi2017}
+% https://doi.org/10.1038/s41598-017-09539-w
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
+However, there are three challenges of biomarker discovery from survival analysis, so far.
+Firstly, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, which over 50\% of the cohort, should be manually investigated and cleaned.
+Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type.
+They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
+SurvivaX.jsp, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort. After downloading the survival results, they could curate plots and tables carefully.
+It is not possible to scan the whole human protein-coding genome in this way.
+Third, we need to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage.
+The above mentioned online tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
+There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
+cutpointr), and cutoffR (available at https://cran.r-project.org/web/
+packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
+
+In our approach, this article described a comprehensive workflow implemented in the R script, which runs on the Rstudio server.
+Its functions include data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
+Using this workflow on the \acrshort{tcga} \acrshort{hnscc} cohort, the 20,500 human protein-coding genes were scanned. The analysis workflow is shown in Figure \ref{fig:figure1}.
+%We found that the surgical margin status and tobacco exposure are independent risk factors of patient survival. 
+%Our findings also suggested several candidate biomarkers are associated with the prognosis of overall survival (OS) under optimal cutoff point with significant P-value.
+Those genes may be potential therapeutic targets of HNSCC.
+
 \section{Results}
@@
 Future research directions may also be highlighted.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Materials and Methods}
+
+Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
+Please disclose at the submission stage any restrictions on the availability of materials or information.
+New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+
+Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
+If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
+They must be provided prior to publication.
+
+Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+\begin{quote}
+This is an example of a quote.
+\end{quote}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-01-01 highlights.tex
Updates from Overleaf

\documentclass[preprint,12pt]{elsarticle}

\begin{document}

Highlights
\begin{itemize}
    \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
    \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\end{itemize}

\end{document}

### 2021-01-01 main.tex
Updates from Overleaf

@@
 % The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
+%\usepackage[bf]{caption}
+%\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
+
+%\usepackage[upplemac]{inputenc} %applemac support if unicode package fails
+%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+%...
+%\usepackage{graphicx}
+%\DeclareGraphicsExtensions{.pdf,.png} % for high-resolution PDF image
+%\usepackage{hyperref}
+%\usepackage{url}
+
+\usepackage{array}
+\usepackage{ragged2e}
+\usepackage{rotating}
+% \usepackage{array}
+\usepackage{multirow}
+\usepackage{colortbl}
+\usepackage{hhline}
+\usepackage{siunitx} % for  1e-10 scientific notation
+%\usepackage{caption}
+%\usepackage{subcaption}
+\usepackage{booktabs, multirow} % for borders and merged ranges
+\usepackage{soul}% for underlines
+%\usepackage[table]{xcolor} % for cell colors
+\usepackage{changepage,threeparttable}
+
+%%% for abbreviations, or acronyms
+\usepackage[automake, acronym, nopostdot]{glossaries} 
+\usepackage{glossary-inline}
+%\setacronymstyle{long-short}
+%\renewcommand*{\glossarysection}[2][]{} 
+%\renewcommand*{\glossarysection}[2][]{\textbf{#1}: }
+% for abbreviations environment
+%\newcommand{\abbrlabel}[1]{\makebox[3cm][l]{\textbf{#1}\ \dotfill}}
+\newenvironment{abbreviation}%{\begin{list}{}{\renewcommand{\makelabel}{\abbrlabel}}}{\end{list}}
+% \newenvironment{<name>}[<number>][<default>]
+
+\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
+\newacronym{fdr}{FDR}{false discovery rate}
+
+\newacronym{hpa}{HPA}{the Human Protein Atlas}
+\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
+\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
+\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
+\newacronym{rna}{RNA}{ribonucleic acid}
+\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
+\newacronym{lncrna}{lncRNA}{long non-coding RNA}
+%\newacronym{km}{KM}{Kaplan-Meier}
+\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
+\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}
+
+\newacronym{mmp}{MMP}{matrix metalloproteinase}
+ %DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1
+ %ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683, and NPB
+
+\newacronym{DKK1}{DKK1}{dickkopf WNT signaling pathway inhibitor 1} 
+\newacronym{CAMK2N1}{CAMK2N1}{calcium/calmodulin dependent protein kinase II inhibitor 1} 
+\newacronym{STC2}{STC2}{stanniocalcin 2} 
+\newacronym{PGK1}{PGK1}{phosphoglycerate kinase 1} 
+\newacronym{SURF4}{SURF4}{surfeit 4} 
+\newacronym{USP10}{USP10}{ubiquitin specific peptidase 10} 
+\newacronym{NEDD4}{NEDD4}{neural precursor cell expressed, developmentally down-regulated 4}
+\newacronym{NDFIP1}{NDFIP1}{NEDD4 family interacting protein 1} 
+\newacronym{FOXA2}{FOXA2}{forkhead box A2} 
+\newacronym{STIP1}{STIP1}{stress-induced-phosphoprotein 1} 
+\newacronym{DKC1}{DKC1}{dyskeratosis congenita 1, dyskerin}
+
+\newacronym{ZNF557}{ZNF557}{zinc finger protein 557} 
+\newacronym{ZNF266}{ZNF266}{zinc finger protein 266} 
+\newacronym{IL19}{IL19}{interleukin 19} 
+\newacronym{MYO1H}{MYO1H}{myosin 1H} 
+\newacronym{FCGBP}{FCGBP}{Fc fragment of IgG binding protein} 
+\newacronym{LOC148709}{LOC148709}{LncRNA LOC148709} 
+\newacronym{EVPLL}{EVPLL}{envoplakin-like protein} 
+\newacronym{PNMA5}{PNMA5}{paraneoplastic antigen like 5} 
+%\newacronym{KIAA1683}{KIAA1683}{IQCN, IQ Motif Containing N} 
+\newacronym{IQCN}{IQCN}{IQ motif containing N} % previous name KIAA1683
+% "IQ" refers to the first two amino acids of the motif: isoleucine (commonly) and glutamine (invariably)
+\newacronym{NPB}{NPB}{neuropeptide B}
+
+ \newacronym{rt}{RT}{radiation therapy}
+ \newacronym{nccn}{NCCN}{National Comprehensive Cancer Network}
+ \newacronym{hif}{HIF}{hypoxia-inducible factor}
+ \newacronym{egfr}{EGFR}{epidermal growth factor receptor}
+ \newacronym{ras}{RAS}{rat sarcoma}
+ \newacronym{hras}{HRAS}{Harvey rat sarcoma viral oncoprotein}
+ \newacronym{erk}{ERK}{extracellular signal-regulated kinases}
+ \newacronym{us}{US}{United States}
+ \newacronym{fda}{FDA}{Food and Drug Administration}
+ \newacronym{tpf}{Tax-PF}{docetaxel, cisplatin, and 5-fluorouracil}
+ \newacronym{tki}{TKI}{tyrosine kinase inhibitor}
+ \newacronym{her}{HER}{human epidermal growth factor receptor}
+ \newacronym{ici}{ICI}{immune-checkpoint inhibitor}
+ \newacronym{ctla4}{CTLA-4}{cytotoxic T lymphocyte antigen 4}
+ \newacronym{pd1}{PD-1}{programmed death 1}
+ \newacronym{pdl1}{PD-L1}{programmed death ligand 1}
+ \newacronym{tim3}{TIM-3}{T-cell immunoglobulin mucin protein 3}
+ \newacronym{lag3}{LAG-3}{lymphocyte activation gene 3}
+ \newacronym{ifng}{IFN-$\gamma$}{interferon gamma}
+ \newacronym{tigit}{TIGIT}{T cell immunoglobin and immunoreceptor tyrosine-based inhibitory motif}
+ \newacronym{gitr}{GITR}{glucocorticoid-induced tumor necrosis factor receptor}
+ \newacronym{vista}{VISTA}{V-domain Ig suppressor of T-cell activation}
+ \newacronym{tmsb4x}{TMSB4X}{thymosin beta-4 X-linked}
+ \newacronym{emt}{EMT}{epithelial-mesenchymal-transition}
+ \newacronym{gdc}{GDC}{Genomic Data Commons}
+ \newacronym{nci}{NCI}{the National Cancer Institute}
+ \newacronym{gdac}{GDAC}{Genome Data Analysis Center}
+ \newacronym{rest}{REST}{Representational State Transfer} 
+ \newacronym{api}{API}{Application Programmable Interface}
+\newacronym{grch38}{GRCh38}{Genome Reference Consortium Homo sapiens genome assembly 38}
+\newacronym{fpkm}{FPKM}{Fragments per kilobase per million reads mapped}
+\newacronym{rsem}{RSEM}{RNA-Seq by Expectation-Maximization}
+\newacronym{slca}{SLC35E2A}{solute carrier family 35 member E2A}
+\newacronym{slcb}{SLC35E2B}{solute carrier family 35 member E2B}
+\newacronym{cde}{CDE}{Common Data Element}
+\newacronym{id}{ID}{identification}
+\newacronym{ajcc}{AJCC}{the American Joint Committee on Cancer}
+\newacronym{uicc}{UICC}{he Union for International Cancer Control}
+\newacronym{tnm}{TNM}{the tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M)}
+\newacronym{ci95}{95\% CI}{95\% confidence interval}
+\newacronym{os}{OS}{overall survival}
+\newacronym{hr}{HR}{hazard ratio}
+\newacronym{hpv}{HPV}{human papillomavirus}
+\newacronym{ene}{ENE}{extra-nodal extension}
+\newacronym{lvsi}{LVSI}{lymph-vascular space invasion}
+\newacronym{pni}{PNI}{perineural invasion}
+\newacronym{doi}{DOI}{depth of invasion}
+\newacronym{lnd}{LND}{lymph node density}
+\newacronym{wpoi5}{WPOI-5}{worst pattern of invasion score 5}
+\newacronym{glut4}{GLUT4}{glucose transporters 4}
+\newacronym{slc2a4}{SLC2A4}{solute carrier family 2 member A4}
+\newacronym{trim24}{TRIM24}{tripartite motif-containing 24}
+\newacronym{til}{TIL}{tumor-infiltrating lymphocytes}
+\newacronym{tmb}{TMB}{tumor mutational burden}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% for Cancers
+% *** All Figures, Schemes and Tables should be inserted into the main text close to their first citation
+% https://www.mdpi.com/journal/cancers/instructions#preparation
 
@@
 
+%\subsubsection{Figure 1:h}
+\begin{figure}[hp]
+\centering
+\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
+%, height=8cm
+%\caption
+\bcaption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).}
+%Step 3 (purple line: dealing with surgical margin).
+{The "main procedure" includes data retrieving from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses.
+The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier P-value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with low [green] or high [red] expression of a specific gene, to yield a collection of P-values; please see Materials and Methods section for details).
+The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted P-value as well as a hazard ratio of Cox model, which was based on the results from the step 1.
+(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
+\label{fig:figure1}
+\end{figure}
+
 \section{Results}
@@
 
-\subsection{Figures, Tables and Schemes}
+%\subsection{Figures, Tables and Schemes}
 
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
+%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
 
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-\caption{This is a figure.
+%\begin{figure}[H]
+%\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
+%\caption{This is a figure.
 Schemes follow the same formatting.
@@
 A caption on a single line should be centered.\label{fig1}}
-\end{figure}
+%\end{figure}
 
@@
 
-Text.
+%\subsection{Formatting of Mathematical Components}
 
-Text.
+%This is the example 1 of equation:
 
-\subsection{Formatting of Mathematical Components}
+%\begin{equation}
+%a = 1,
+%\end{equation}
 
-This is the example 1 of equation:
-
-\begin{equation}
-a = 1,
-\end{equation}
-
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
+%the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
 %% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
@@
 %% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
+%\begin{Theorem}
+%Example text of a theorem.
+%\end{Theorem}
 
 %% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+%\begin{proof}[Proof of Theorem 1]
+%Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
+%\end{proof}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
+%\section{Patents}
 
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+%This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
+\authorcontributions{
+%For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``
+Conceptualization, Michael Hsiao; Funding acquisition, Yu-Chuan (Jack) Li; Methodology, Li-Hsing Chi; Resources, Alexander TH Wu; Software, Li-Hsing Chi; Supervision, Yu-Chuan (Jack) Li; Validation, Michael Hsiao; Writing - original draft, Li-Hsing Chi; Writing - review and editing, Alexander TH Wu.
+All authors have read and agreed to the published version of the manuscript.}
+%'' please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
+Authorship must be limited to those who have contributed substantially to the work~reported.
 
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+\funding{The APC was funded by Taipei Medical University}
 
-\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
-You might choose to exclude this statement if the study did not require ethical approval.
-Please note that the Editorial Office might ask you for further information.
-Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals.}
+\institutionalreview{Not applicable}
 
-\informedconsent{Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.}
+\informedconsent{Not applicable}
 
-\dataavailability{Please refer to suggested Data Availability Statements in section “MDPI Research Data Policies” at \href{https://www.mdpi.com/ethics}{https://www.mdpi.com/ethics}.}
+\dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
+%All the supplementary figures, tables, and R script codes 
+The R script codes and datasets generated during the current study are available in the GitHub repository, https://github.com/texchi2/pvalueTex.}
 
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
+\acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
+The tables were generated by latex code with the help from https://github.com/JDMCreator/\newline
+LaTeXTableEditor.
+We like to thank Dr. Wen-Chang Wang,
+%https://orcid.org/0000-0003-3124-2136
+College of Medical Science and Technology, Taipei Medical University, for bioinformatics consultation and helps. 
+We like to thank Sylvain Hall\'e, Department of Computer Science and Mathematics, Univerit\'e du Qu\'ebec \`a Chicoutimi, Canada, for latex technique help with his TeXtidote.
+%We also thank the statistical consultation and helps by Dr. Hsin-Chou Yang of the Institute of Statistical Science, Academia Sinica, Taipei, Taiwan.
+We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
 
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}
+%\subsection*{Authors' information} % Author details (automatic placed here)
+
+% *** URL Accessed 20 May 2013.
+The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/\newline
+mtbwi/index.do. Accessed 20 May 2020.}
+
+\conflictsofinterest{The authors declare no conflict of interest.}
 
 %% Optional
-\sampleavailability{Samples of the compounds ... are available from the authors.}
+%\sampleavailability{Samples of the compounds ... are available from the authors.}
 
@@
 %% Optional
-\abbreviations{The following abbreviations are used in this manuscript:\\
+\abbreviations{The following abbreviations are used in this manuscript:
+\noindent 
+\renewcommand*{\glsinlinenameformat}[2]{\glstarget{#1} {\textsc{#2}},}
+\printglossary[type=\acronymtype, title= , nonumberlist, style=inline]
+% Abbreviations
 
-\noindent 
-\begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & Linear dichroism
-\end{tabular}}
+%\begin{tabular}{@{}ll}
+%MDPI & Multidisciplinary Digital Publishing Institute\\
+%DOAJ & Directory of open access journals\\
+%TLA & Three letter acronym\\
+%LD & Linear dichroism
+%\end{tabular}
+}
 
@@
 %% Optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendix
-\section{}
-\subsection{}
-The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
+%\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
+If the appendix sections contain a heading then change the argument to "yes".
+%\appendix
+%\section{}
+%\subsection{}
+%The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
 Mathematical proofs of results not central to the paper can be added as an appendix.
 
-\section{}
-All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
+%\section{}
+%All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
 
@@
 %=====================================
-%\externalbibliography{yes}
+\externalbibliography{yes}
 %\bibliography{your_external_BibTeX_file}
+%\bibliographystyle{model1-num-names}
+\bibliography{TCGA_margin_cutoff.bib}
 
@@
 %=====================================
-\begin{thebibliography}{999}
+%\begin{thebibliography}{999}
 % Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
+%\bibitem[Author1(year)]{ref-journal}
+%Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
 % Reference 2
-\bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 3
-\bibitem[Author3(year)]{ref-book2}
-Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-% Reference 4
-\bibitem[Author4(year)]{ref-unpublish}
-Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} stage of publication (under review; accepted; in~press).
-% Reference 5
-\bibitem[Author5(year)]{ref-communication}
-Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-% Reference 6
-\bibitem[Author6(year)]{ref-proceeding}
-Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of Presentation.
-In Title of the Collected Work (if available), Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference; Editor 1, Editor 2, Eds.
-(if available); Publisher: City, Country, Year (if available); Abstract Number (optional), Pagination (optional).
-% Reference 7
-\bibitem[Author7(year)]{ref-thesis}
-Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
+%\bibitem[Author2(year)]{ref-book1}
+%Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
 % Reference 8
-\bibitem[Author8(year)]{ref-url}
-Title of Site. Available online: URL (accessed on Day Month Year).
-\end{thebibliography}
+%\bibitem[Author8(year)]{ref-url}
+%Title of Site. Available online: URL (accessed on Day Month Year).
+%\end{thebibliography}
 

### 2021-01-02 main_backup.tex
debug

--- 2021-01-01 main.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
-%\usepackage[bf]{caption}
-%\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
+\usepackage[]{caption} % bf
+\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
 
@@
 \begin{document}
+%\begin{paracol}{2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\clearpage
+
 \section{Results}
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
+The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
+By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}A univariate, and Figure \ref{fig:figure2}B  multivariate plots).
+At the final step, a Bonferroni P-value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}C, D).
+The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
+%\subsubsection{Figure 3}
+while the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB (see Table \ref{table:table3}, with their full name of genes).
+We made a volcano plot for 9416 genes by Kaplan-Meier P-value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
+The plot revealed that the most significant (Bonferroni-adjusted P-value $< 0.05$) candidate genes are located above the dotted line.
+At the same time, Cox's HR separated them on the two-side with prognostic impact.
 
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
+%\subsubsection{Figure 2:h}
+\begin{figure}[hp]
+\centering
+\includegraphics[width=\textwidth]{Figure2.pdf}
+\bcaption{\acrshort{hnscc} Cox's hazard ratio and P-value plots.}
+{(a) Univariate HR versus uncorrected P-value; (b) Multivariate HR versus uncorrected P-value; (c) Univariate HR versus Bonferroni corrected P-value; and (d) Multivariate HR versus Bonferroni corrected P-value.}
+\label{fig:figure2}
+\end{figure}
 
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
+% tables 1  3
+%%% tables
+% Table1
+\begin{sidewaystable}[hp]
+\centering
+\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted P-value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
+\hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{P-value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\P-value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
+\hline
+DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                & **                                          \\
+\hline
+CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & **                                          \\
+\hline
+STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                & **                                          \\
+\hline
+PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & **                                          \\
+\hline
+SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & 3                                           \\
+\hline
+USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & **                                          \\
+\hline
+NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & 6                                           \\
+\hline
+FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & **                                          \\
+\hline
+STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                & **                                          \\
+\hline
+DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                & **                                          \\
+\hline
+\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
+\arrayrulecolor{black}\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted P-value $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
+\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: P-value $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
+\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: number of articles related with cancer research; ** as many~}                                                                                                                                                                                                                                                                                                                                                             \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table1}
+\end{sidewaystable}
+%\end{table}
 
-The text continues here.
+%\subsubsection{Table3/legend}
+%Table3. The 10 candidate genes over-expressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
+\begin{table}[hp]
+\centering
+\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected P-value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
+\hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~P-value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} & 0                                             \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           & 1                                             \\
+\hline
+IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & 14                                            \\
+\hline
+MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           & 0                                             \\
+\hline
+FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           & **                                            \\
+\hline
+LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           & 1                                             \\
+\hline
+EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           & 0                                             \\
+\hline
+PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           & 5                                             \\
+\hline
+KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           & 0                                             \\
+\hline
+NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           & 4                                             \\
+\hline
+                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\
+\hline
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted P-value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: P-value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table3}
+\end{table}
+
+%\subsubsection{Figure 3:h}
+\begin{figure}[hp]
+\centering
+\includegraphics[width=\textwidth]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
+\bcaption{Volcano plot of genes under survival analyses.}
+{X axis: unadjusted P-value of Kaplan-Meier survival (-log10 transformed).
+Y axis: multivariate hazard ratio from Cox proportional regression model.
+Dotted line: significant Bonferroni corrected P-value. 
+Red circles mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). Green circles mark 10 genes, which affect on better survival ($HR<=0.5$).}
+\label{fig:figure3}
+\end{figure}
+% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
+% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.
+
+\clearpage
+
+Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}A).
+The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
+In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted P-value as $0.001$).
+Figure \ref{fig:figure4}B's cumulative P-value plot showed that the uncorrected 116 P-values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
+The smallest P-value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal P-value.
+Conversely, the most associated gene with better survival is \acrfull{ZNF557}.
+In Figure \ref{fig:figure4}C, a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted P-value = $0.001$).
+The cutoff finding procedure (cutofFinder\_func.R) generated cumulative P-value plots in Figure \ref{fig:figure4}D.
+There were 166 uncorrected P-values estimated by a serial cut from 125 to 290 for grouping the cohort.
+All was less than 0.05, and the smallest P-value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal P-value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
+%The second candidate, which improving patient survival, is ZNF266.
+%\subsubsection{Tables} in main article
+
+%\subsubsection{Figure 4:h}
+\begin{figure}[hp]
+\centering
+\includegraphics[width=\textwidth]{Figure4.pdf}
+\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
+{(a) Kaplan-Meier plot of DKK1 under optimal P-value, and (b) the cutoff was derived from cumulative P-value plots of DKK1.
+(c) Kaplan-Meier plot of ZNF557 under optimal P-value, and (d) the cutoff was derived from cumulative P-value plots of ZNF557.}
+\label{fig:figure4}
+\end{figure}
+
+\clearpage
+
+Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier P-value.
+We found their Cox's univariate and multivariate HR are all greater than 1.837.
+There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
+In Table \ref{table:table2},
+after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, P-value $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, P-value = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, P-value = 0.004]).
+The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, P-value = 0.015]).
+The M stage could not be considered due to only 3 out of 414 patients which have distant metastasis.
+
+%\subsubsection{Table2/legend}
+%Table 2. Univariate/Multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in HNSCC.
+%(P-value Significant codes is denoted as  0.01 mark as *; 0.001 mark as **; if $<$0.001  mark as ***)
+\begin{table}[hp]
+\centering
+\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in \acrshort{hnscc}}
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|} 
+\arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
+\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\
+\arrayrulecolor{black}\hline
+\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}}  \\
+\cline{2-8}
+                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.178                                                                          & 0.841-1.650                                                                   & 0.342                                                                          \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.462                                                                          & 1.078-1.983                                                                   & \textcolor{red}{0.015}                                                         \\
+\hline
+\multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 1.978                                                                          & 1.046-3.737                                                                   & \textcolor{red}{0.036}                                                         \\
+\hline
+\multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.149                                                                          & 0.805-1.640                                                                   & 0.445                                                                          \\
+\hline
+\multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor{red}{0.049}                                                        & 6.513                                                                          & 1.415-29.96                                                                   & \textcolor{red}{0.016}                                                         \\
+\hline
+\multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.597                                                                          & 0.277-1.287                                                                   & 0.188                                                                          \\
+\hline
+\multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.601                                                                          & 1.159-2.211                                                                   & \textcolor{red}{0.004}                                                         \\
+\hline
+\multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.302                                                                          & 0.943-1.797                                                                   & 0.109                                                                          \\
+\hline
+\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 2.266                                                                          & 1.666-3.082                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & 2.135                                                                          & 1.559-2.924                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                      \\
+\hline
+\multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table2}
+\end{table}
+
+There were also ten candidate genes over-expressed with a better prognosis of \acrshort{hnscc}, listed in Table \ref{table:table3}. Cox's univariate and multivariate HR is just under 0.5.
+In Table \ref{table:table4},
+after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, P-value = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, P-value = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, P-value = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, P-value $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.
+
+In overall results, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+
+%\subsubsection{Table4/legend}
+\begin{table}[!hp]
+\centering
+\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of ZNF557 gene expression in \acrshort{hnscc}}
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|} 
+\arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
+\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\
+\arrayrulecolor{black}\hline
+\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}}  \\
+\cline{2-8}
+                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.163                                                                          & 0.833-1.625                                                                   & 0.375                                                                          \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.328                                                                          & 0.976-1.808                                                                   & 0.071                                                                          \\
+\hline
+\multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor[rgb]{1,0.149,0}{0.033}                                             & 1.961                                                                          & 1.035-3.714                                                                   & \textcolor[rgb]{1,0.149,0}{0.039}                                              \\
+\hline
+\multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.179                                                                          & 0.824-1.686                                                                   & 0.367                                                                          \\
+\hline
+\multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor[rgb]{1,0.149,0}{0.049}                                             & 8.478                                                                          & 1.847-38.92                                                                   & \textcolor[rgb]{1,0.149,0}{0.006}                                              \\
+\hline
+\multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.512                                                                          & 0.239-1.096                                                                   & 0.085                                                                          \\
+\hline
+\multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor[rgb]{1,0.149,0}{0.004}                                             & 1.631                                                                          & 1.180-2.254                                                                   & \textcolor[rgb]{1,0.149,0}{0.003}                                              \\
+\hline
+\multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor[rgb]{1,0.149,0}{0.044}                                             & 1.453                                                                          & 1.055-2.000                                                                   & \textcolor[rgb]{1,0.149,0}{0.022}                                              \\
+\hline
+\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 0.465                                                                          & 0.348-0.619                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                          & 0.499                                                                          & 0.372-0.669                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                           \\
+\hline
+\multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table4}
+\end{table}
+
+% end of result
+
+%Bulleted lists look like this:
+%\begin{itemize}
+%\item	First bullet;
+%\item	Second bullet;
+%\item	Third bullet.
+%\end{itemize}
+
+%Numbered lists can be added as follows:
+%\begin{enumerate}
+%\item	First item; 
+%\item	Second item;
+%\item	Third item.
+%\end{enumerate}
 
@@
 % The MDPI table float is called specialtable
-\begin{specialtable}[H] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
+%\begin{specialtable}[H] 
+%\caption{This is a table caption. Tables %should be placed in the main text near to %the first time they are~cited.\label{tab1}}
 %%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabular}
-\end{specialtable}
+%\begin{tabular}{ccc}
+%\toprule
+%\textbf{Title 1}	& \textbf{Title 2}	& %\textbf{Title 3}\\
+%\midrule
+%Entry 1		& Data			& Data\\
+%Entry 2		& Data			& Data\\
+%\bottomrule
+%\end{tabular}
+%\end{specialtable}
 
@@
 \nointerlineskip
+
 %\begin{equation}
@@
 % Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
-\begin{figure}[H]	
-\widefigure
-\includegraphics[width=15 cm]{Definitions/logo-mdpi}
-\caption{This is a wide figure.\label{fig2}}
-\end{figure}  
+
 \begin{paracol}{2}
@@
 
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
 %% Example of a theorem:
@@
 
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
+% TCGAbiolinks
+%alcohol consumption
+Besides ethnicity, age, gender, the \acrshort{tnm} stage, radiation therapy, chemotherapy, and targeted therapy, the comprehensive adverse features of prognosis in \acrshort{hnscc} should include tobacco exposure, \acrshort{egfr} amplification, \acrfull{hpv} status, positive/close surgical margin ($<5 mm$), \acrfull{ene}, \acrfull{lvsi}, \acrfull{pni}, \acrfull{doi} ($>5 mm$), as well as metastatic \acrfull{lnd}\cite{Cheraghlou2018}, and \acrfull{wpoi5}, which was defined as tumor dispersion $>= 1 mm$ between tumor satellites or positive \acrshort{pni}/\acrshort{lvsi}\cite{Amin2017}.
+The features of \acrshort{doi}, \acrshort{lnd}, and tumor dispersion were not available on the \acrshort{tcga} dataset.
+The Brandwein-Gensler's risk model (lymphocytic host response, \acrshort{wpoi5}, and \acrshort{pni})\cite{Brandwein-Gensler2010}\cite{Sinha2018} was suggested to be routinely performed on pathological examination.
+In previous reports of \acrshort{hnscc}, the loco-regional failure will be high when the initial frozen section has a positive/close surgical margin, and even the final margin revision revealed negative\cite{Bulbul2019b}.
+According to Table \ref{table:table2} and Table \ref{table:table4} in our study, the positive surgical margin yielded a hazard ratio greater than 1.6 to influence on patient's \acrshort{os}.
+It was suggested by authors \cite{Scholl1986}\cite{Sutton2003}\cite{Shaw2004}\cite{Guillemaud2010a}\cite{Patel2010}\cite{Kuriakose2017}\cite{Shapiro2017}\cite{Saidak2018}\cite{Miguelanez-Medran2019}\cite{Saidak2019} that the reason of positive/close surgical margin is possibly due to tumor aggressiveness or dispersion (WPOI-5) instead of iatrogenic reason of surgery.
+The surgical margin status is suggested as an independent surrogate for tumor dispersion, and important in the \acrshort{hnscc} study.
+Thus, in the current study, we selected the common clinicopathological features, including gender, age, clinical T, clinical N, clinical M, surgical margin status, and tobacco exposure in the biomarker discovery for adjustment of confounders (details description at Materials and Methods section).
+
+In our previous work, altered glucose metabolism (e.k.a.
+the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrfull{slc2a4} (or \acrfull{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}.
+In this study, LOC148709 (a \acrfull{lncrna}) was suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3}).
+%on page \pageref{table:table3}). I
+It was also found to has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
+
+There is a trend toward cancer type-agnostic study. The success of pembrolizumab and nivolumab was based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
+It showed a precedent of tumor type-agnostic therapy\cite{Yan2018}.
+%*** PD-L1/PD-L2 is a biomarker; Keynote-012
+Currently, there are several common biomarkers of \acrshort{ici} under evaluation, which include \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
+The other  \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019}(ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (ClinicalTrials.gov Identifier: NCT04080804) studies.
+
+Although we combined the power of genome-wide scanning and an optimal cutoff finder for Kaplan-Meier survival analysis, the study has some limitations.
+We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
+The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excited the cancer research community\cite{Li2013c}\cite{Li2017b}.
+By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses.
+However, there are only 237 antibodies available so far. We found our 20 candidates are not included in the \acrshort{tcpa} database (v3.0\cite{Chen2019}).
+%> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))
+%validation at protein level:
+At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa}
+(available at https://www.proteinatlas.org/humanproteome/\newline
+pathology/head+and+neck+cancer, accessed 28 September 2020). The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+% > semi_join(pvalueTex_good, HPA_good, by=c("V1"="Gene"))
+%There are 628 genes that consensus of pvalue005KM (6429 genes) and HPA (bad+good in HNSCC)
+Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+% second limitation:
+In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers.
+However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
+Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
+It should be carefully curated to confirm the data integrity with the correct definition.
+We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R.
+The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}.
+Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
 
@@
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+\subsection*{Patient Cohort}
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available on a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
+%\cite{SeanDavis;MartinMorgan2020}
+GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
+\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
+Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
+The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
+We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, step 1) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+\subsubsection*{RNA Sequencing Data}
+
+The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}.
+The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
+The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
+It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
+We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].\newline
+Fire.Rda".
+%\cite{Guo2013} RSEM is better than %FPKM (one-end read) %***RSEM at TCGA: 長度不同的 gene transcript 相比依然公平
+%The RNA-Seq normalization methods RPKM and RSEM produce similar results on the gene level and reasonably concordant results on the exon level.
+%RNA-Seq by Expectation-Maximization (RSEM)
+After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
+We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
+We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
+
+\subsubsection*{Clinical Data}
+
+We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
+Fire.Rda" (accessed November 2019).
+
+One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
+[GeneName].Fire.Rda" tables were transposed and merged by their \newline
+\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
+The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
+The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
+% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
+We made data clean by removing duplicated rows and columns.
+
+\subsection*{Cutoff Finder Core Engine}
+
+%\label{key:cutoff}
+To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
+Our cutofFinder\_func subroutine employs the minimum P-value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
+First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
+Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort").
+The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier P-values for each gene.
+Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum P-value, was selected by the cutofFinder\_func subroutine.
+This iteration method could calculate all possible cutoff of each gene expression in this cohort.
+At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x.
+0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}).
+The optimal cutoff value and its correlated patient grouping size (e.x.
+low-expression in 262 persons vs.
+high-expression in 152 persons with gene \acrshort{CAMK2N1}) would be returned to the main program to allow downstream Cox survival analysis.
+The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
+In case there was no significant P-value, a median expression of this gene was set as its cutpoint as usual.
+
+\subsection*{Statistical Consideration}
+
+Our workflow has loops to call function survival\_marginSFP(GeneName) with given GeneName to process the survival analysis gene by gene.
+We dichotomized the clinicopathological features, which includes gender (male/ female), age at diagnosed (below/beyond 65 year-old), clinical tumor size (T1-2/T3-4), clinical nodal status (negative/positive), clinical distant metastasis (negative/positive), TNM staging (early/late), surgical margin status (negative/positive) and tobacco exposure (low/high).
+The patients were grouped by an \acrshort{rnaseq} value of each gene, cut at low- or high-expression on an optimal P-value obtained from the cutofFinder\_func subroutine (see the section of "Cutoff Finder Core Engine").
+Pearson's chi-square test was used for these binary variables.
+Kaplan-Meier survival was analyzed using the log-rank test for two groups OS comparison.
+The Cox proportional hazards regression is the widely accepted approach for modeling survival while accounting for confounding factors\cite{Magen2019}.
+Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the OS.
+Results were considered statistically significant when a two-sided P-value $<$ 0.05, or a lower threshold if indicated.
+The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal P-value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
+%statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
+There were also multiple correlated tests of null hypotheses in the Kaplan-Meier family during our global scanning of protein-coding genes.
+The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
+%There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes.
+The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
+
+The resulting data, including Kaplan-Meier curves, cumulative P-value plots, and Cox regression tables, were exported to ".xlsx" and ".Rda" files (by R package "r2excel") for subsequent biomarker selection.
+
+\subsection*{Biomarker Selection}
+
+Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
+Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
+%\begin{quote}
+%This is an example of a quote.
+%\end{quote}
 
@@
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+Our findings suggested 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni P-values and proper confounders control.
+They also might be potential common biomarkers for subsequent study.
+We wish this bioinformatics tool will be available for the broad usage of tumor-agnostic research\cite{Looney2020} to cross several \acrshort{tcga} diseases to make translational impacts.
+%Tex: PvalueTex
 

### 2021-01-02 main.tex
debug only on materials and methods

@@
 %----------
-%journal Cancers
+% journal
 %----------
@@
 
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Diversity
-%\LSID{\url{http://}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Applied Sciences:
-%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Toxins
-%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Encyclopedia
-%\encyclopediadef{Instead of the abstract}
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% for Cancers
-% *** All Figures, Schemes and Tables should be inserted into the main text close to their first citation
-% https://www.mdpi.com/journal/cancers/instructions#preparation
-
 \begin{document}
+%\begin{paracol}{2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Results}
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
+The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
+By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}A univariate, and Figure \ref{fig:figure2}B  multivariate plots).
+At the final step, a Bonferroni P-value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}C, D).
+The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
+%\subsubsection{Figure 3}
+while the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB (see Table \ref{table:table3}, with their full name of genes).
+We made a volcano plot for 9416 genes by Kaplan-Meier P-value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
+The plot revealed that the most significant (Bonferroni-adjusted P-value $< 0.05$) candidate genes are located above the dotted line.
+At the same time, Cox's HR separated them on the two-side with prognostic impact.
 
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
+%\subsubsection{Figure 2:h}
+\begin{figure}[hp]
+\centering
+\includegraphics[width=\textwidth]{Figure2.pdf}
+\bcaption{\acrshort{hnscc} Cox's hazard ratio and P-value plots.}
+{(a) Univariate HR versus uncorrected P-value; (b) Multivariate HR versus uncorrected P-value; (c) Univariate HR versus Bonferroni corrected P-value; and (d) Multivariate HR versus Bonferroni corrected P-value.}
+\label{fig:figure2}
+\end{figure}
 
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
+% tables 1  3
+%%% tables
+% Table1
+\begin{sidewaystable}[hp]
+\centering
+\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted P-value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
+\hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{P-value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\P-value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
+\hline
+DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                & **                                          \\
+\hline
+CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & **                                          \\
+\hline
+STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                & **                                          \\
+\hline
+PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & **                                          \\
+\hline
+SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & 3                                           \\
+\hline
+USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & **                                          \\
+\hline
+NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & 6                                           \\
+\hline
+FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & **                                          \\
+\hline
+STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                & **                                          \\
+\hline
+DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                & **                                          \\
+\hline
+\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
+\arrayrulecolor{black}\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted P-value $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
+\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: P-value $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
+\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: number of articles related with cancer research; ** as many~}                                                                                                                                                                                                                                                                                                                                                             \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table1}
+\end{sidewaystable}
+%\end{table}
 
-The text continues here.
+%\subsubsection{Table3/legend}
+%Table3. The 10 candidate genes over-expressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
+\begin{table}[hp]
+\centering
+\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected P-value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
+\hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~P-value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} & 0                                             \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           & 1                                             \\
+\hline
+IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & 14                                            \\
+\hline
+MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           & 0                                             \\
+\hline
+FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           & **                                            \\
+\hline
+LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           & 1                                             \\
+\hline
+EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           & 0                                             \\
+\hline
+PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           & 5                                             \\
+\hline
+KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           & 0                                             \\
+\hline
+NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           & 4                                             \\
+\hline
+                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\
+\hline
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted P-value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: P-value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table3}
+\end{table}
+
+%\subsubsection{Figure 3:h}
+\begin{figure}[hp]
+\centering
+\includegraphics[width=\textwidth]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
+\bcaption{Volcano plot of genes under survival analyses.}
+{X axis: unadjusted P-value of Kaplan-Meier survival (-log10 transformed).
+Y axis: multivariate hazard ratio from Cox proportional regression model.
+Dotted line: significant Bonferroni corrected P-value. 
+Red circles mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). Green circles mark 10 genes, which affect on better survival ($HR<=0.5$).}
+\label{fig:figure3}
+\end{figure}
+% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
+% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.
+
+\clearpage
+
+Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}A).
+The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
+In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted P-value as $0.001$).
+Figure \ref{fig:figure4}B's cumulative P-value plot showed that the uncorrected 116 P-values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
+The smallest P-value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal P-value.
+Conversely, the most associated gene with better survival is \acrfull{ZNF557}.
+In Figure \ref{fig:figure4}C, a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted P-value = $0.001$).
+The cutoff finding procedure (cutofFinder\_func.R) generated cumulative P-value plots in Figure \ref{fig:figure4}D.
+There were 166 uncorrected P-values estimated by a serial cut from 125 to 290 for grouping the cohort.
+All was less than 0.05, and the smallest P-value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal P-value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
+%The second candidate, which improving patient survival, is ZNF266.
+%\subsubsection{Tables} in main article
+
+%\subsubsection{Figure 4:h}
+\begin{figure}[hp]
+\centering
+\includegraphics[width=\textwidth]{Figure4.pdf}
+\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
+{(a) Kaplan-Meier plot of DKK1 under optimal P-value, and (b) the cutoff was derived from cumulative P-value plots of DKK1.
+(c) Kaplan-Meier plot of ZNF557 under optimal P-value, and (d) the cutoff was derived from cumulative P-value plots of ZNF557.}
+\label{fig:figure4}
+\end{figure}
+
+\clearpage
+
+Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier P-value.
+We found their Cox's univariate and multivariate HR are all greater than 1.837.
+There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
+In Table \ref{table:table2},
+after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, P-value $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, P-value = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, P-value = 0.004]).
+The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, P-value = 0.015]).
+The M stage could not be considered due to only 3 out of 414 patients which have distant metastasis.
+
+%\subsubsection{Table2/legend}
+%Table 2. Univariate/Multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in HNSCC.
+%(P-value Significant codes is denoted as  0.01 mark as *; 0.001 mark as **; if $<$0.001  mark as ***)
+\begin{table}[hp]
+\centering
+\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in \acrshort{hnscc}}
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|} 
+\arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
+\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\
+\arrayrulecolor{black}\hline
+\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}}  \\
+\cline{2-8}
+                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.178                                                                          & 0.841-1.650                                                                   & 0.342                                                                          \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.462                                                                          & 1.078-1.983                                                                   & \textcolor{red}{0.015}                                                         \\
+\hline
+\multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 1.978                                                                          & 1.046-3.737                                                                   & \textcolor{red}{0.036}                                                         \\
+\hline
+\multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.149                                                                          & 0.805-1.640                                                                   & 0.445                                                                          \\
+\hline
+\multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor{red}{0.049}                                                        & 6.513                                                                          & 1.415-29.96                                                                   & \textcolor{red}{0.016}                                                         \\
+\hline
+\multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.597                                                                          & 0.277-1.287                                                                   & 0.188                                                                          \\
+\hline
+\multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.601                                                                          & 1.159-2.211                                                                   & \textcolor{red}{0.004}                                                         \\
+\hline
+\multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.302                                                                          & 0.943-1.797                                                                   & 0.109                                                                          \\
+\hline
+\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 2.266                                                                          & 1.666-3.082                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & 2.135                                                                          & 1.559-2.924                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                      \\
+\hline
+\multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table2}
+\end{table}
+
+There were also ten candidate genes over-expressed with a better prognosis of \acrshort{hnscc}, listed in Table \ref{table:table3}. Cox's univariate and multivariate HR is just under 0.5.
+In Table \ref{table:table4},
+after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, P-value = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, P-value = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, P-value = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, P-value $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.
+
+In overall results, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+
+%\subsubsection{Table4/legend}
+\begin{table}[!hp]
+\centering
+\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of ZNF557 gene expression in \acrshort{hnscc}}
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|} 
+\arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
+\cline{3-8}
+\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\
+\arrayrulecolor{black}\hline
+\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}}  \\
+\cline{2-8}
+                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.163                                                                          & 0.833-1.625                                                                   & 0.375                                                                          \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.328                                                                          & 0.976-1.808                                                                   & 0.071                                                                          \\
+\hline
+\multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor[rgb]{1,0.149,0}{0.033}                                             & 1.961                                                                          & 1.035-3.714                                                                   & \textcolor[rgb]{1,0.149,0}{0.039}                                              \\
+\hline
+\multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.179                                                                          & 0.824-1.686                                                                   & 0.367                                                                          \\
+\hline
+\multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor[rgb]{1,0.149,0}{0.049}                                             & 8.478                                                                          & 1.847-38.92                                                                   & \textcolor[rgb]{1,0.149,0}{0.006}                                              \\
+\hline
+\multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.512                                                                          & 0.239-1.096                                                                   & 0.085                                                                          \\
+\hline
+\multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor[rgb]{1,0.149,0}{0.004}                                             & 1.631                                                                          & 1.180-2.254                                                                   & \textcolor[rgb]{1,0.149,0}{0.003}                                              \\
+\hline
+\multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor[rgb]{1,0.149,0}{0.044}                                             & 1.453                                                                          & 1.055-2.000                                                                   & \textcolor[rgb]{1,0.149,0}{0.022}                                              \\
+\hline
+\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\cline{2-8}
+                                        & High                                                                                & 0.465                                                                          & 0.348-0.619                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                          & 0.499                                                                          & 0.372-0.669                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                           \\
+\hline
+\multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table4}
+\end{table}
+
+% end of result
+
+%Bulleted lists look like this:
+%\begin{itemize}
+%\item	First bullet;
+%\item	Second bullet;
+%\item	Third bullet.
+%\end{itemize}
+
+%Numbered lists can be added as follows:
+%\begin{enumerate}
+%\item	First item; 
+%\item	Second item;
+%\item	Third item.
+%\end{enumerate}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
 
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
+% TCGAbiolinks
+%alcohol consumption
+Besides ethnicity, age, gender, the \acrshort{tnm} stage, radiation therapy, chemotherapy, and targeted therapy, the comprehensive adverse features of prognosis in \acrshort{hnscc} should include tobacco exposure, \acrshort{egfr} amplification, \acrfull{hpv} status, positive/close surgical margin ($<5 mm$), \acrfull{ene}, \acrfull{lvsi}, \acrfull{pni}, \acrfull{doi} ($>5 mm$), as well as metastatic \acrfull{lnd}\cite{Cheraghlou2018}, and \acrfull{wpoi5}, which was defined as tumor dispersion $>= 1 mm$ between tumor satellites or positive \acrshort{pni}/\acrshort{lvsi}\cite{Amin2017}.
+The features of \acrshort{doi}, \acrshort{lnd}, and tumor dispersion were not available on the \acrshort{tcga} dataset.
+The Brandwein-Gensler's risk model (lymphocytic host response, \acrshort{wpoi5}, and \acrshort{pni})\cite{Brandwein-Gensler2010}\cite{Sinha2018} was suggested to be routinely performed on pathological examination.
+In previous reports of \acrshort{hnscc}, the loco-regional failure will be high when the initial frozen section has a positive/close surgical margin, and even the final margin revision revealed negative\cite{Bulbul2019b}.
+According to Table \ref{table:table2} and Table \ref{table:table4} in our study, the positive surgical margin yielded a hazard ratio greater than 1.6 to influence on patient's \acrshort{os}.
+It was suggested by authors \cite{Scholl1986}\cite{Sutton2003}\cite{Shaw2004}\cite{Guillemaud2010a}\cite{Patel2010}\cite{Kuriakose2017}\cite{Shapiro2017}\cite{Saidak2018}\cite{Miguelanez-Medran2019}\cite{Saidak2019} that the reason of positive/close surgical margin is possibly due to tumor aggressiveness or dispersion (WPOI-5) instead of iatrogenic reason of surgery.
+The surgical margin status is suggested as an independent surrogate for tumor dispersion, and important in the \acrshort{hnscc} study.
+Thus, in the current study, we selected the common clinicopathological features, including gender, age, clinical T, clinical N, clinical M, surgical margin status, and tobacco exposure in the biomarker discovery for adjustment of confounders (details description at Materials and Methods section).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
+In our previous work, altered glucose metabolism (e.k.a.
+the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrfull{slc2a4} (or \acrfull{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}.
+In this study, LOC148709 (a \acrfull{lncrna}) was suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3}).
+%on page \pageref{table:table3}). I
+It was also found to has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+There is a trend toward cancer type-agnostic study. The success of pembrolizumab and nivolumab was based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
+It showed a precedent of tumor type-agnostic therapy\cite{Yan2018}.
+%*** PD-L1/PD-L2 is a biomarker; Keynote-012
+Currently, there are several common biomarkers of \acrshort{ici} under evaluation, which include \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
+The other  \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019}\linebreak
+(ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (ClinicalTrials.gov Identifier: NCT04080804) studies.
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+Although we combined the power of genome-wide scanning and an optimal cutoff finder for Kaplan-Meier survival analysis, the study has some limitations.
+We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
+The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excited the cancer research community\cite{Li2013c}\cite{Li2017b}.
+By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses.
+However, there are only 237 antibodies available so far. We found our 20 candidates are not included in the \acrshort{tcpa} database (v3.0\cite{Chen2019}).
+%> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))
+%validation at protein level:
+At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa}
+(available at https://www.proteinatlas.org/humanproteome/\newline
+pathology/head+and+neck+cancer, accessed 28 September 2020). The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+% > semi_join(pvalueTex_good, HPA_good, by=c("V1"="Gene"))
+%There are 628 genes that consensus of pvalue005KM (6429 genes) and HPA (bad+good in HNSCC)
+Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+% second limitation:
+In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers.
+However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
+Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
+It should be carefully curated to confirm the data integrity with the correct definition.
+We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R.
+The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}.
+Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Materials and Methods} % 4
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%
 \section{Conclusions}
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+Our findings suggested 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni P-values and proper confounders control.
+They also might be potential common biomarkers for subsequent study.
+We wish this bioinformatics tool will be available for the broad usage of tumor-agnostic research\cite{Looney2020} to cross several \acrshort{tcga} diseases to make translational impacts.
+%Tex: PvalueTex
 

### 2021-01-02 main.tex
last 3 has error-prone

@@
 
+\subsection*{Patient Cohort}
+
+The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available on a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
+%\cite{SeanDavis;MartinMorgan2020}
+GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
+\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
+Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
+The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
+FirebrowseR)\cite{Deng2017}. 
+We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, step 1) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
+
+\subsubsection*{RNA Sequencing Data}
+
+The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}.
+The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
+The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
+It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
+We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].\newline
+Fire.Rda".
+After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
+We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
+We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
+
+\subsubsection*{Clinical Data}
+
+We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
+Fire.Rda" (accessed November 2019).
+
+One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
+[GeneName].Fire.Rda" tables were transposed and merged by their \newline
+\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
+The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
+The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
+% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
+We made data clean by removing duplicated rows and columns.
+
 %%%%%
-\section{Conclusions}
+\section{Conclusions} % 5
 

### 2021-01-02 main.tex
error from \subsection*{Cutoff Finder Core Engine}
\subsection*{Statistical Consideration}

@@
 
+\subsection*{Cutoff Finder Core Engine}
+
+\subsection*{Statistical Consideration}
+
+\subsection*{Biomarker Selection}
+
+Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
+Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
+
 %%%%%

### 2021-01-02 main.tex
\maxdeadcycles = 300

@@
 \documentclass[cancers,article,submit,moreauthors,pdftex]{Definitions/mdpi}
+\maxdeadcycles=300 % Output loop---200 consecutive dead cycles.
 
@@
 
-\subsection*{Patient Cohort}
+\subsection{Patient Cohort}
 
@@
 
-\subsubsection*{RNA Sequencing Data}
+\subsubsection{RNA Sequencing Data}
 
@@
 
-\subsubsection*{Clinical Data}
+\subsubsection{Clinical Data}
 
@@
 
-\subsection*{Cutoff Finder Core Engine}
-
-\subsection*{Statistical Consideration}
-
-\subsection*{Biomarker Selection}
+\subsection{Cutoff Finder Core Engine}
+
+%\label{key:cutoff}
+To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
+Our cutofFinder\_func subroutine employs the minimum P-value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
+First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
+Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort").
+The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier P-values for each gene.
+Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum P-value, was selected by the cutofFinder\_func subroutine.
+This iteration method could calculate all possible cutoff of each gene expression in this cohort.
+At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x.
+0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}).
+The optimal cutoff value and its correlated patient grouping size (e.x.
+low-expression in 262 persons vs.
+high-expression in 152 persons with gene \acrshort{CAMK2N1}) would be returned to the main program to allow downstream Cox survival analysis.
+The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
+In case there was no significant P-value, a median expression of this gene was set as its cutpoint as usual.
+
+\subsection{Statistical Consideration}
+
+Our workflow has loops to call function survival\_marginSFP(GeneName) with given GeneName to process the survival analysis gene by gene.
+We dichotomized the clinicopathological features, which includes gender (male/ female), age at diagnosed (below/beyond 65 year-old), clinical tumor size (T1-2/T3-4), clinical nodal status (negative/positive), clinical distant metastasis (negative/positive), TNM staging (early/late), surgical margin status (negative/positive) and tobacco exposure (low/high).
+The patients were grouped by an \acrshort{rnaseq} value of each gene, cut at low- or high-expression on an optimal P-value obtained from the cutofFinder\_func subroutine (see the section of "Cutoff Finder Core Engine").
+Pearson's chi-square test was used for these binary variables.
+Kaplan-Meier survival was analyzed using the log-rank test for two groups OS comparison.
+The Cox proportional hazards regression is the widely accepted approach for modeling survival while accounting for confounding factors\cite{Magen2019}.
+Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the OS.
+Results were considered statistically significant when a two-sided P-value $<$ 0.05, or a lower threshold if indicated.
+The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal P-value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
+%statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
+There were also multiple correlated tests of null hypotheses in the Kaplan-Meier family during our global scanning of protein-coding genes.
+The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
+%There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes.
+The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
+
+The resulting data, including Kaplan-Meier curves, cumulative P-value plots, and Cox regression tables, were exported to ".xlsx" and ".Rda" files (by R package "r2excel") for subsequent biomarker selection.
+
+\subsection{Biomarker Selection}
 

### 2021-01-02 main.tex
done for submitting
Updates from Overleaf

@@
 The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
-By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}A univariate, and Figure \ref{fig:figure2}B  multivariate plots).
-At the final step, a Bonferroni P-value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}C, D).
+By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
+At the final step, a Bonferroni P-value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
 The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
@@
 \centering
-\includegraphics[width=\textwidth]{Figure2.pdf}
+\includegraphics[width=14cm]{Figure2.pdf}
 \bcaption{\acrshort{hnscc} Cox's hazard ratio and P-value plots.}
@@
 \centering
-\includegraphics[width=\textwidth]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
+\includegraphics[width=14cm]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
 \bcaption{Volcano plot of genes under survival analyses.}
@@
 
-Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}A).
+Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}(a)).
 The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
 In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted P-value as $0.001$).
-Figure \ref{fig:figure4}B's cumulative P-value plot showed that the uncorrected 116 P-values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
+Figure \ref{fig:figure4}(b)'s cumulative P-value plot showed that the uncorrected 116 P-values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
 The smallest P-value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal P-value.
 Conversely, the most associated gene with better survival is \acrfull{ZNF557}.
-In Figure \ref{fig:figure4}C, a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted P-value = $0.001$).
-The cutoff finding procedure (cutofFinder\_func.R) generated cumulative P-value plots in Figure \ref{fig:figure4}D.
+In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted P-value = $0.001$).
+The cutoff finding procedure (cutofFinder\_func.R) generated cumulative P-value plots in Figure \ref{fig:figure4}(d).
 There were 166 uncorrected P-values estimated by a serial cut from 125 to 290 for grouping the cohort.
@@
 \centering
-\includegraphics[width=\textwidth]{Figure4.pdf}
+\includegraphics[width=15cm]{Figure4.pdf}
 \bcaption{Kaplan-Meier survival analyses, by cutoff finding.}

### 2021-01-24 highlights.tex
start the major revision

@@
 \documentclass[preprint,12pt]{elsarticle}
+% major revision and answer question (3 reviewers)
+%Sunday, January 24⋅22:30 – 22:55
+%Daily, until Jan 29, 2021
+\begin{document}
+\section{Responses to Reviewers' comments}
+%***Response to reviewer's comments: [藍色字]
+\subsection{1-1}
+Comments from the reviewer #1:
 
-\begin{document}
+Comments and Suggestions for Authors
+The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method.
+I have a few minor questions.
+This is an attractive analysis method and I would like to know more details.
 
+1-1) it is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
+[我的 candidate 中為什麼沒有 EGFR]
+
+[Answer]
+[我的 candidate 中為什麼沒有 EGFR]
+removed by literature review
+
+\subsection{1-2}
+1-2)
+ DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
+[如果加入 DNA alteration 又會如何? 選擇 mRNA 的原因是?]
+
+Answer
+a). mRNA study: in drug discovery, the gene expression (overexpression) is much easier to find a candidate for an inhibitory lead (pro-drug?) 比較容易研發
+
+b). => it needs deep learning (DNA+RNA omics study)
+\cite{Lawrence2015a} TCGA 的第一篇文章
+[see 01/24 google calendar: DNA mutation
+
+%======
+\subsection{2-1}
+reviewer #2
+
+Can be improved
+Does the introduction provide sufficient background and include all relevant references? [Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.] 1) 4)
+
+[找出其他 database cohort 的比較]
+2-1) How representative is the TCGA database for HNSCC?
+Answer
+有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).
+\cite{Lawrence2015a}
+until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).
+\cite{Tang2019}\cite{Wei2020a}
+(ok)
+
+\subsection{2-2}
+2-2) Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?
+Answer
+GSE2837 (GEO) from PrognoScan: http://dna00.bio.kyutech.ac.jp/PrognoScan-cgi/PrognoScan.cgi \cite{Mizuno2009a}
+https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
+Relapse Free Survival (RFS) in GSE2837 (not available in the TCGA dataset)
+microarray gene expression experiments (Affymetrix X3P chips U133_X3P)
+cohort: VUMC, VAMC, UTMDACC (1992-2005), published on 2006
+40 HNSCC samples
+cohort n=28 in the following probes of genes with survival significance:
+17 out of 20 candidates => 10 genes achieve similar positive and negative prognostic effect comparable with our candidate genes, however, its group separation was be cut by 偏激 a skewed manner
+FCGBP (P-value 0.005658 of KM plot)
+FOXA2 (0.001587)
+
+A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
+GSE52793: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE52793
+GSE75537: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE75537
+...
+
+\subsection{2-3}
+2-3) Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?
+Answer
+Currently, less HNSCC dataset is available worldwide (Indian?) => GEO
+generalized use is fine for this workflow, it needs to modify the R code to adapt 
+能否套用在別的 database，可以，但需要 d/l raw microarray or RNA-seq 而且需要標準化(fpkm or  It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
+Moreover, we are planning to expand this workflow for pan-cancer studies (other cancer types in the TCGA database).
+the elements of the workflow: ...
+
+\subsection{2-4}
+2-4) Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.
+Answer
+We modified the introduction ...
+https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
+
+=========
+\subsection{3-1}
+reviewer #3
+
+Must be improved:
+Is the research design appropriate?
+Are the results clearly presented?
+Are the conclusions supported by the results?
+
+3-1) Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.
+  There is little information provided. The authors should provide more evidence to support this article.
+
+[Answer]
+a) Embase searching; https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+\cite{Wei2019}
+through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+
+% bad guy
+http://gepia2.cancer-pku.cn/detail.php?gene=DKK1
+DKK1: 13 results of HNSCC \cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}
+CAMK2N1: 26 results of cancer: ; 1 HNSCC cell line (CAL-27)\cite{Li2018b}
+STC2: \cite{Ma2020}
+PGK1: glycolysis enzyme is responsive in cisplatin-resistant oral squamous cell carcinoma cell line\cite{Nakamura2005}
+SURF4: patients with tumors (not HNSCC) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.\cite{Kim2018a}
+USP10: one of autophagy related genes for HNSCC prognosis prediction.\cite{Ren2020}
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+NDFIP1, was reported as candidate biomarker for hepatocellular carcinoma\cite{Zhang2019a} and breast cancer\cite{Tian2020}.
+%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
+It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
+FOXA2: hihger expression is significantly associated with the poor prognosis of HNSCC\cite{Shen2017a}.
+%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
+STIP1, increased expression of STIP1, detectable auto-antibody in serum sample, may indicate poor survival outcome in ovarian cancer patients\cite{Chao2013}\cite{Cho2014}.
+The auto-antibody against STIP1 could be a useful biomarker for esophageal squamous cell carcinoma\cite{Xu2017}.
+DKC1, DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+%is the tumor suppressor gene in HNSCC
+
+% good guy
+ZNF557, oncogenic human herpesviruses, EBV and KSHV are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}.
+ZNF266, % or ZNF16, HZF1?
+those genes were reported at following, 
+IL19 in esophageal squamous cell carcinoma\cite{Hsing2013},
+MYO1H associated mandibular prognathism\cite{Sun2018}, 
+FCGBP in thyroid cancer\cite{Griffith2006}, 
+?LOC148709?, 
+EVPLL in cDNA project,
+PNMA5 promotes apoptosis signaling in HeLa and MCF-7 cells\cite{Lee2016}, 
+IQCN (previous name as KIAA1683), and 
+NPB (Neuropeptide B) is endogenous ligand of the G protein-coupled receptors, named GPR7\cite{Andreis2005}, which is associated with prostate cancer prognosis\cite{Cottrell2007}.
+
+b) (ok) SurvExpress
+試試利用手動找到類似的結果 Web resource for Biomarker comparison and validation of Survival gene expression data. 
+Dataset: HNSC - TCGA Head and Neck squamous cell carcinoma June 2016 (dup=all, data=raw)，(only TCGA June 2016, n=502) \cite{Aguirre-Gamboa2013}
+有  DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1,ZNF557, ZNF266, FCGBP,  類似的結果;
+沒有，FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
+因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
+ (TCGA)(***please see Figure \label{fig_SurvExpress})
+
+x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+We could provide more evidence to support the prognostic impact of these candidate genes.
+
+% the end of response letter
+
+\section{Highlights}
 Highlights
@@
 
+%\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
+\bibliographystyle{unsrt} %model1-num-names}
+\bibliography{TCGA_margin_cutoff.bib}
+
 \end{document}

### 2021-01-25 rebuttal_responses_revision1.tex
\textcolor{red}{...} (ok)

\documentclass[preprint,12pt]{elsarticle}
% major revision and answer question (3 reviewers)
%Sunday, January 24⋅22:30 – 22:55
%Daily, until Jan 29, 2021

% mark in blue or red
\usepackage{xcolor}

\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

\begin{document}

\section{Revision cover letter (cancers-1082127)} % 2021/01/25
%其實直接 online 填寫即可
%Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript

%Assistant Editor
%E-Mail: aubree.zhu@mdpi.com
%MDPI Branch Office, Tianjin
Assistant Editor of Cancers%\newline

Jan 29, 2021

Dear Dr. Aubree Zhu:

Enclosed, please find our revised manuscript (cancers-1082127) entitled "A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Cancers. We greatly appreciate your time in serving as the editor handling this manuscript and also thank the reviewers for their critical comments and suggestions on our manuscript.

We have since performed additional analysis, experiment and revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner, 
%{%
1) the description of the rationale that how to pick up the Thymosin Beta-4 X-Linked (TMSB4X) in details, 2) the statistical analysis of MALDI imaging mass spectrometry and 3) the IHC staining with positive and negative control images and further analysis of nuclear TMSB4X staining. 
We re-wrote the introduction in detail and re-examined the tissue microarray slides according to the suggestion by reviewer \#1.
%}

According to the editor's comments, we have the manuscript checked for English grammar and reformat Table 1 by rotating 90 degrees to portrait mode. %（Table 1 轉正)

%{%
According to the reviewers' comments, we added new Figure 1C, 2, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 to enhance the rationale and removed the old supplementary Table S1.
%}

We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.

Kind regards,

Yu-Chuan (Jack) Li, M.D., Ph.D.

Graduate Institute of Biomedical Informatics,

College of Medical Science and Technology,

Taipei Medical University,

Taipei, Taiwan

%2) [cancers-1082127_main_redMarked] 自動化 by latex:
%"Track Changes" function in latex => by latexdiff
%Some options, taken from the documentation, include:
%UNDERLINE—added text is wavy-underlined and blue, discarded text is struck out and red;
%CTRADITIONAL—added text is blue and set in sans-serif, and a red footnote is created for each discarded piece of text;
%TRADITIONAL—like CTRADITIONAL but without the use of colour;
%CFONT—added text is blue and set in sans-serif, and discarded text is red and very small size;
%FONTSTRIKE—added text is set in sans-serif, discarded text small and struck out;
%CHANGEBAR—added text is blue, and discarded text is red. Additionally, the changed text is marked with a bar in the margin.
%https://www.overleaf.com/learn/latex/Articles/Using_Latexdiff_For_Marking_Changes_To_Tex_Documents

\section{rebuttal} % Response2Referees
We greatly appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer’s comments are as follows (marked as \textcolor{blue}{blue}). 
And the revised portions in the manuscript are indicated in \textcolor{red}{red}.

Reviewer comments:
%Reviewer #1(Technical Comments to the Author):
%   The ms investigates an interesting and timely topic. However, the discovery cohort involves a small sample size and throughout the analysis, the issue of correcting the obtained p-values for multiple comparisons is not addressed. Hence, the evidence for zooming into TMSB4X is not convincing.

%\section{Responses to Reviewers' comments}
% our responses to the reviewers' comments.
%***Response to reviewer's comments: [藍色字]
\subsection*{1-1}
Comments from the reviewer \#1:

Comments and Suggestions for Authors
The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.
This is an attractive analysis method and I would like to know more details.

1-1) it is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
%[我的 candidate 中為什麼沒有 EGFR]

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
%[我的 candidate 中為什麼沒有 EGFR]
removed by literature review
citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
\end{MyColorPar}

\subsection*{1-2}
 DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 選擇 mRNA 的原因是?]

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
a). mRNA study: in drug discovery, the gene expression (overexpression) is much easier to find a candidate for an inhibitory lead (pro-drug?) %比較容易研發

b). => it needs deep learning (DNA+RNA omics study)
\cite{Lawrence2015a} TCGA %的第一篇文章
[see 01/24 google calendar: DNA mutation
Epigenetics in cancer: CpG islands
Lawrence, M. S., Sougnez, C., Lichtenstein, L., Cibulskis, K., Lander, E., Gabriel, S. B., … Pham, M. (2015). Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature, 517(7536), 576–582. https://doi.org/10.1038/nature14129

The presence of widespread genomic instability in HNSCC, such as cytogenetic aberrations, allelic imbalance/loss of heterozygosity, and microsatellite instability, suggests that there is an imperfection in the host DNA repair machinery. Genomic instability with progressive accumulation of detrimental genetic alterations appears to be dependent upon a circuitous interaction between the environmental genotoxic insults and the host DNA repair machinery, the functional integrity of which is governed by the proper cell cycle control and host DNA repair capacity.
https://www.nature.com/articles/nature14129 Comprehensive genomic characterization of head and neck squamous cell carcinomas
Genomics allows the identification of possibly relevant variants, such as single nucleotide polymorphisms (SNPs), copy number variation (CNV), mutations and translocations => %https://cancersheadneck.biomedcentral.com/articles/10.1186/s41199-020-0047-y

%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7080958/#SM8 The Landscape of Somatic Copy Number Alterations in Head and Neck Squamous Cell Carcinoma, 2020.
18 GSE dataset + TCGA: chromothripsis 6\%

TMB: To calculate TMB, you need to know the total size of the region sequenced. If data is from exome sequencing, you would find the size of the exome capture, and divide total mutations (or non-synonymous only depending on strategy), by that size (e.g. ~45MB) to get SNV/MB ratio.

ICIs <- TMB <- DDR DNA repair gene
Identification of Genomic Predictors for Treatment Response to Cancer Immunotherapy Using Omics Data Analysis
Yu-Chao Wang

tumor mutational burden-high (TMB-H) [≥10 mutations/megabase (mut/Mb)] solid tumors (for pembrolizumab)

%===================
epigenetic trinity:
%http://www.biomedicine.org.tw/Upload/07_DNA甲基化程度在大腸直腸癌扮演的角色.pdf
%脊椎動物之基因體中約20\%之序列為5'-GC-3' (簡稱CpG)之雙核苷酸(dinucleotide)。然而有 些長約1至2kb之序列段，其CpG含量高達60% (CpG islands)

60\% protein-coding genes with CpG islands on their promoter region

(
McGough JM, Yang D, Huang S, et al. DNA methylation represses IFN-gamma-induced and signal transducer and activator of transcription 1-mediated IFN regulatory factor 8 activation in colon carcinoma cells. Mol Cancer Res 2008;6:1841-1851.
)

methyl CpG-binding domain protein; MBD prevents TF binding on the promoter of gene
=> causing impairment of mismatch repair; MMR => microsatellite instable; MSI

%環境因子的致癌機轉
=>CpG hypermethylation
turn off tumor suppressor genes
and
Hypomethylation turn on oncogene
DKK1
...
hypomethylation ->
loss of gene imprinting
alleles 
..
histone methylation
%http://webcache.googleusercontent.com/search?q=cache:z8zvnjS-C3AJ:sites.mc.ntu.edu.tw/board.php?courseID%3D83%26f%3Ddoc%26folderID%3D581%26cid%3D3060&client=safari&hl=en&gl=tw&strip=1&vwsrc=0
%雖然以上我們討論的是癌症的基因體，但癌症的厲害就是它本來就利用人體原有的生物機制來生存（co-opting），因此，以上在癌症觀察到的基因體複雜性，其實也存在於正常人體.

%從最早，很單純的基因之exon序列，轉錄成mRNA，再轉譯成polypeptide，形成protein，到現在還要考慮epigenetics、mi RNA、TUF (ENCODE將之名為transcripts of unknown function (TUF)=> non-coding RNA 後來很紅)、chromosome environment，基因體的複雜性真是增加了不知多少倍，這也提醒我們在了解基因功能方面，必需更有全面性的關照。這也是「基因體醫學」必需以「基因體科學」為基礎的道理。

%...

%DNA mutation, copy number 增加造成 overexpression of gene

???Answer:
%所以 DNA vs mRNA
high dimensional multi-omics analysis by CNN 
%分析不是獨立變數，彼此有 confounding 放入分析需要使用不同的方法

It may be beneficial to include these different data types in models predicting outcomes, such as the survival time of patients. Until recently, only data from a single omics type were used to build such prediction models, with or without the inclusion of standard clinical data [2]. In recent years, however, the increasing availability of different types of omics data measured for the same patients (called multi-omics data from now on) has led to their combined use for building outcome prediction models. An important characteristic of multi-omics data is the high-dimensionality of the datasets, which frequently have more than 10 000 or even 100 000 variables. This places particular demands on the methods used to build prediction models: they must be able to handle data where the number of variables by far exceeds the number of observations. Moreover, practitioners often prefer sparse and interpretable models containing only a few variables [3]. Last but not the least, multi-omics data are structured: the variables are partitioned into (nonoverlapping) groups. This structure may be taken into account when building prediction models.
%Citation: https://academic.oup.com/bib/advance-article/doi/10.1093/bib/bbaa167/5895463
%特別的 algorithm 
..
Or

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6419526/

Deep learning

SALMON (Survival Analysis Learning with Multi-Omics Neural Networks)

DNA mutation:
copy number burden (CNB) and tumor mutation burden (TMB) are important for predicting tumor progression (Marshall et al., 2017; Thomas et al., 2018)
\end{MyColorPar}

%======
\subsection*{2-1}
reviewer \#2

Can be improved
Does the introduction provide sufficient background and include all relevant references? [Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.] 1) 4)

%[找出其他 database cohort 的比較]
2-1) How representative is the TCGA database for HNSCC?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).
\cite{Lawrence2015a}
until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).
\cite{Tang2019}\cite{Wei2020a}
(ok)
\end{MyColorPar}

\subsection*{2-2}
Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
GSE2837 (GEO) from PrognoScan: http://dna00.bio.kyutech.ac.jp/PrognoScan-cgi/PrognoScan.cgi \cite{Mizuno2009a}
https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
Relapse Free Survival (RFS) in GSE2837 (not available in the TCGA dataset)
microarray gene expression experiments (Affymetrix X3P chips U133\_X3P)
cohort: VUMC, VAMC, UTMDACC (1992-2005), published on 2006
40 HNSCC samples
cohort n=28 in the following probes of genes with survival significance:
17 out of 20 candidates => 10 genes achieve similar positive and negative prognostic effect comparable with our candidate genes, however, its group separation was be cut by a skewed manner
FCGBP (P-value 0.005658 of KM plot)
FOXA2 (0.001587)

there is survival feature:
A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
GSE52793: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE52793
GSE75537: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE75537
\end{MyColorPar}

\subsection*{2-3}
Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
Currently, less HNSCC dataset is available worldwide (Indian?) => GEO
generalized use is fine for this workflow, it needs to modify the R code to adapt 
%能否套用在別的 database，可以，但需要 d/l raw microarray or RNA-seq 而且需要標準化(fpkm or RSEM)
It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
Moreover, we are planning to expand this workflow for pan-cancer studies (other cancer types in the TCGA database).
the elements of the workflow: ...
\end{MyColorPar}

\subsection*{2-4}
Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
*** We modified the introduction according to reviewer's comment...
https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
\end{MyColorPar}

\subsection*{3-1}
reviewer \#3

Must be improved:
Is the research design appropriate?
Are the results clearly presented?
Are the conclusions supported by the results?

3-1) Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.

There is little information provided. The authors should provide more evidence to support this article.
%  Once the authors identify TMSB4X as a target, the rest of the analysis seems fine, but their rationale for looking into TMSB4X is not strongly supported by the available data.

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
a) Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
\cite{Wei2019}
through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.

% bad guy
http://gepia2.cancer-pku.cn/detail.php?gene=DKK1
DKK1: 13 results of HNSCC \cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}
CAMK2N1: 26 results of cancer: ; 1 HNSCC cell line (CAL-27)\cite{Li2018b}
STC2: \cite{Ma2020}
PGK1: glycolysis enzyme is responsive in cisplatin-resistant oral squamous cell carcinoma cell line\cite{Nakamura2005}
SURF4: patients with tumors (not HNSCC) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.\cite{Kim2018a}
USP10: one of autophagy related genes for HNSCC prognosis prediction.\cite{Ren2020}
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
NDFIP1, was reported as candidate biomarker for hepatocellular carcinoma\cite{Zhang2019a} and breast cancer\cite{Tian2020}.
%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN. It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
FOXA2: hihger expression is significantly associated with the poor prognosis of HNSCC\cite{Shen2017a}.
%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
STIP1, increased expression of STIP1, detectable auto-antibody in serum sample, may indicate poor survival outcome in ovarian cancer patients\cite{Chao2013}\cite{Cho2014}. The auto-antibody against STIP1 could be a useful biomarker for esophageal squamous cell carcinoma\cite{Xu2017}.
DKC1, DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
%is the tumor suppressor gene in HNSCC

% good guy
ZNF557, oncogenic human herpesviruses, EBV and KSHV are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}.
ZNF266, % or ZNF16, HZF1?
those genes were reported at following, 
IL19 in esophageal squamous cell carcinoma\cite{Hsing2013},
MYO1H associated mandibular prognathism\cite{Sun2018}, 
FCGBP in thyroid cancer\cite{Griffith2006}, 
?LOC148709?, 
EVPLL in cDNA project,
PNMA5 promotes apoptosis signaling in HeLa and MCF-7 cells\cite{Lee2016}, 
IQCN (previous name as KIAA1683), and 
NPB (Neuropeptide B) is endogenous ligand of the G protein-coupled receptors, named GPR7\cite{Andreis2005}, which is associated with prostate cancer prognosis\cite{Cottrell2007}.

b) (ok) SurvExpress
%試試利用手動找到類似的結果 
Web resource for Biomarker comparison and validation of Survival gene expression data. 
Dataset: HNSC - TCGA Head and Neck squamous cell carcinoma June 2016 (dup=all, data=raw)，(only TCGA June 2016, n=502) \cite{Aguirre-Gamboa2013}
%有類似的結果:
DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1,ZNF557, ZNF266, FCGBP;
%沒有
FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
it supposed that ...
%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
 (TCGA)(***please see Figure \label{fig_SurvExpress})

%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
We provide more evidences mentioned above to support the prognostic impact of these candidate genes. It needs to be further validated.
\end{MyColorPar}

% the end of response letter

\section{Highlights}
Highlights
\begin{itemize}
    \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
    \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\end{itemize}

%\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
\bibliographystyle{unsrt} %model1-num-names}
\bibliography{TCGA_margin_cutoff.bib}

\end{document}

### 2021-01-25 rebuttal_responses_revision1.tex
Updates from Overleaf

@@
 
+%%% for abbreviations, or acronyms
+\usepackage[automake, acronym, nopostdot]{glossaries} 
+%\usepackage{glossary-inline}
+%\newenvironment{abbreviation}
+%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
+\newacronym{fdr}{FDR}{false discovery rate}
+\newacronym{hpa}{HPA}{the Human Protein Atlas}
+\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
+\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
+\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
+\newacronym{rna}{RNA}{ribonucleic acid}
+\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
+\newacronym{lncrna}{lncRNA}{long non-coding RNA}
+%\newacronym{km}{KM}{Kaplan-Meier}
+\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
+\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}
+
+\newacronym{mmp}{MMP}{matrix metalloproteinase}
+ %DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1
+ %ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683, and NPB
+
+\newacronym{DKK1}{DKK1}{dickkopf WNT signaling pathway inhibitor 1} 
+\newacronym{CAMK2N1}{CAMK2N1}{calcium/calmodulin dependent protein kinase II inhibitor 1} 
+\newacronym{STC2}{STC2}{stanniocalcin 2} 
+\newacronym{PGK1}{PGK1}{phosphoglycerate kinase 1} 
+\newacronym{SURF4}{SURF4}{surfeit 4} 
+\newacronym{USP10}{USP10}{ubiquitin specific peptidase 10} 
+\newacronym{NEDD4}{NEDD4}{neural precursor cell expressed, developmentally down-regulated 4}
+\newacronym{NDFIP1}{NDFIP1}{NEDD4 family interacting protein 1} 
+\newacronym{FOXA2}{FOXA2}{forkhead box A2} 
+\newacronym{STIP1}{STIP1}{stress-induced-phosphoprotein 1} 
+\newacronym{DKC1}{DKC1}{dyskeratosis congenita 1, dyskerin}
+
+\newacronym{ZNF557}{ZNF557}{zinc finger protein 557} 
+\newacronym{ZNF266}{ZNF266}{zinc finger protein 266} 
+\newacronym{IL19}{IL19}{interleukin 19} 
+\newacronym{MYO1H}{MYO1H}{myosin 1H} 
+\newacronym{FCGBP}{FCGBP}{Fc fragment of IgG binding protein} 
+\newacronym{LOC148709}{LOC148709}{LncRNA LOC148709} 
+\newacronym{EVPLL}{EVPLL}{envoplakin-like protein} 
+\newacronym{PNMA5}{PNMA5}{paraneoplastic antigen like 5} 
+%\newacronym{KIAA1683}{KIAA1683}{IQCN, IQ Motif Containing N} 
+\newacronym{IQCN}{IQCN}{IQ motif containing N} % previous name KIAA1683
+% "IQ" refers to the first two amino acids of the motif: isoleucine (commonly) and glutamine (invariably)
+\newacronym{NPB}{NPB}{neuropeptide B}
+
+ \newacronym{rt}{RT}{radiation therapy}
+ \newacronym{nccn}{NCCN}{National Comprehensive Cancer Network}
+ \newacronym{hif}{HIF}{hypoxia-inducible factor}
+ \newacronym{egfr}{EGFR}{epidermal growth factor receptor}
+ \newacronym{ras}{RAS}{rat sarcoma}
+ \newacronym{hras}{HRAS}{Harvey rat sarcoma viral oncoprotein}
+ \newacronym{erk}{ERK}{extracellular signal-regulated kinases}
+ \newacronym{us}{US}{United States}
+ \newacronym{fda}{FDA}{Food and Drug Administration}
+ \newacronym{tpf}{Tax-PF}{docetaxel, cisplatin, and 5-fluorouracil}
+ \newacronym{tki}{TKI}{tyrosine kinase inhibitor}
+ \newacronym{her}{HER}{human epidermal growth factor receptor}
+ \newacronym{ici}{ICI}{immune-checkpoint inhibitor}
+ \newacronym{ctla4}{CTLA-4}{cytotoxic T lymphocyte antigen 4}
+ \newacronym{pd1}{PD-1}{programmed death 1}
+ \newacronym{pdl1}{PD-L1}{programmed death ligand 1}
+ \newacronym{tim3}{TIM-3}{T-cell immunoglobulin mucin protein 3}
+ \newacronym{lag3}{LAG-3}{lymphocyte activation gene 3}
+ \newacronym{ifng}{IFN-$\gamma$}{interferon gamma}
+ \newacronym{tigit}{TIGIT}{T cell immunoglobin and immunoreceptor tyrosine-based inhibitory motif}
+ \newacronym{gitr}{GITR}{glucocorticoid-induced tumor necrosis factor receptor}
+ \newacronym{vista}{VISTA}{V-domain Ig suppressor of T-cell activation}
+ \newacronym{tmsb4x}{TMSB4X}{thymosin beta-4 X-linked}
+ \newacronym{emt}{EMT}{epithelial-mesenchymal-transition}
+ \newacronym{gdc}{GDC}{Genomic Data Commons}
+ \newacronym{nci}{NCI}{the National Cancer Institute}
+ \newacronym{gdac}{GDAC}{Genome Data Analysis Center}
+ \newacronym{rest}{REST}{Representational State Transfer} 
+ \newacronym{api}{API}{Application Programmable Interface}
+\newacronym{grch38}{GRCh38}{Genome Reference Consortium Homo sapiens genome assembly 38}
+\newacronym{fpkm}{FPKM}{Fragments per kilobase per million reads mapped}
+\newacronym{rsem}{RSEM}{RNA-Seq by Expectation-Maximization}
+\newacronym{slca}{SLC35E2A}{solute carrier family 35 member E2A}
+\newacronym{slcb}{SLC35E2B}{solute carrier family 35 member E2B}
+\newacronym{cde}{CDE}{Common Data Element}
+\newacronym{id}{ID}{identification}
+\newacronym{ajcc}{AJCC}{the American Joint Committee on Cancer}
+\newacronym{uicc}{UICC}{he Union for International Cancer Control}
+\newacronym{tnm}{TNM}{the tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M)}
+\newacronym{ci95}{95\% CI}{95\% confidence interval}
+\newacronym{os}{OS}{overall survival}
+\newacronym{hr}{HR}{hazard ratio}
+\newacronym{hpv}{HPV}{human papillomavirus}
+\newacronym{ene}{ENE}{extra-nodal extension}
+\newacronym{lvsi}{LVSI}{lymph-vascular space invasion}
+\newacronym{pni}{PNI}{perineural invasion}
+\newacronym{doi}{DOI}{depth of invasion}
+\newacronym{lnd}{LND}{lymph node density}
+\newacronym{wpoi5}{WPOI-5}{worst pattern of invasion score 5}
+\newacronym{glut4}{GLUT4}{glucose transporters 4}
+\newacronym{slc2a4}{SLC2A4}{solute carrier family 2 member A4}
+\newacronym{trim24}{TRIM24}{tripartite motif-containing 24}
+\newacronym{til}{TIL}{tumor-infiltrating lymphocytes}
+\newacronym{tmb}{TMB}{tumor mutational burden}
+
+%==================
 \begin{document}
@@
 
+\pagebreak
+
 \section{rebuttal} % Response2Referees
@@
 
-Reviewer comments:
 %Reviewer #1(Technical Comments to the Author):
@@
 I have a few minor questions.
+
 This is an attractive analysis method and I would like to know more details.
@@
 1-1) it is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
-%[我的 candidate 中為什麼沒有 EGFR]
 
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
-%[我的 candidate 中為什麼沒有 EGFR]
-removed by literature review
-citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
+We appreciate the reviewer for the critical comments and thank for his/her agreement of our analysis using the TCGA cohort.
+%[我的 candidate 中為什麼沒有 EGFR];  
+In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
+by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
+(please see https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv for reference, the table was ranked by FDR P-value)
+
+% transforming growth factor- (TGF-α) 
+% epidermal growth factor receptor (EGFR)
+As in our manuscript mentioned, 
+In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
+Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab) and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}.
+Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}.
+So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
+%citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
+Thus, we wish the further validations of our candidate genes to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
+% a list from literature review, 留 下少於  50 articles mentioned candidates
+%HNSCC_survivalAnalysis_marginS_EGFR.Rda
+%HNSCC_survivalAnalysis_marginS_EGFR.xlsx
+%https://github.com/texchi2/pvalueTex/blob/master/file20500_list.txt
+%analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
 \end{MyColorPar}
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
+We appreciate the reviewer for the question.
 a). mRNA study: in drug discovery, the gene expression (overexpression) is much easier to find a candidate for an inhibitory lead (pro-drug?) %比較容易研發
@@
 
+\acrshort{egfr} amplification, mutation
 %===================

### 2021-01-27 rebuttal_responses_revision1.tex
Answer 2-1 done

@@
 %***Response to reviewer's comments: [藍色字]
-\subsection*{1-1}
+
 Comments from the reviewer \#1:
@@
 
-1-1) it is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
+\subsection*{1-1}
+It is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
 
@@
 by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
-(please see https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv for reference, the table was ranked by FDR P-value)
+(please see https://github.com/texchi2/\linebreak
+pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)
 
@@
 In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
-Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab) and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}.
+Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}.
 Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}.
@@
 %citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
-Thus, we wish the further validations of our candidate genes to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
+Thus, we wish the further validations of our meaningful hypotheses of candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
 % a list from literature review, 留 下少於  50 articles mentioned candidates
@@
  DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
-%[如果加入 DNA alteration 又會如何? 選擇 mRNA 的原因是?]
+%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]
 
@@
 
-We appreciate the reviewer for the question.
-a). mRNA study: in drug discovery, the gene expression (overexpression) is much easier to find a candidate for an inhibitory lead (pro-drug?) %比較容易研發
+We appreciate the reviewer for reminding the importance of DNA alteration in survival analysis.
+Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e.
+DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation),
+epigenomics, transcriptomics (i.e. RNA expression), proteomics, metabolomics and microbiomics.
+The usefulness of multi-omics data for the prediction of HNSCC outcome is expected.
+%such as the (censored) survival time.
+Moritz Herrmann et al.(2020) observed that using multi-omics and survival data can slightly improve the performance of prediction methods for particular datasets, such as TCGA HNSCC\cite{Herrmann2020}.
+%It is limited that the utility of multi-omics data for prediction purposes in the considered TCGA studies\cite{Herrmann2020}.
+%18 cancer datasets from The Cancer Genome Atlas (TCGA) 
+According to their study, %the multi-omics structure have a slightly better prediction performance than naive (0.562 vs.	0.557 ) with favoring clinical variables leads to better prediction results for HNSCC.
+%likelihood-based boosting (CoxBoost and CoxBoost favoring)
+% Exemplary t-tests comparing blockForest with CoxBoost favoring and the Clinical only model showed no significant differences in performance. 
+% blockForest also offers the possibility of favoring clinical covariates using the argument always.select.block of the blockfor function
+%Last but not the least, multi-omics data are structured: the variables are partitioned into (non overlapping) groups. 
+% ***
+the survival analysis of TCGA HNSCC dataset by blockForest method (with multi-omics and clinical variables) has a similar prediction performance than that by Cox's model (with clinical variables alone).
+%from The Cancer Genome Atlas (TCGA)
+They also reported the performance C-index as 0.582 [CI: 0.554, 0.610] in blockForest method and 0.554 [CI: 0.519, 0.588] in Cox's model\cite{Herrmann2020}.
 
-b). => it needs deep learning (DNA+RNA omics study)
-\cite{Lawrence2015a} TCGA %的第一篇文章
-[see 01/24 google calendar: DNA mutation
-Epigenetics in cancer: CpG islands
-Lawrence, M.
-S., Sougnez, C., Lichtenstein, L., Cibulskis, K., Lander, E., Gabriel, S.
-B., … Pham, M.
-(2015).
-Comprehensive genomic characterization of head and neck squamous cell carcinomas.
-Nature, 517(7536), 576–582.
-https://doi.org/10.1038/nature14129
+% 小心光茫太甚  Well-established prognostic clinical variables: prioritize
+% the number of variables in the group of variables of TCGA HNSCC dataset:
+% 11 clinical variables, 57964 CNV variables, 17248 mutation variables and 21520 RNA expression variables.
+%*** Taking this structure into account can protect the predictive information that transcriptomics (e.x.
+RNA-Seq) or low-dimensional clinical variables might get lost within the huge amount of genomics (e.x.
+DNA mutation/amplification, copy number variation) data\cite{Boulesteix2011}\cite{Herrmann2020}.
+DNA amplification will usually be one of the causes to overexpress the gene.
+Moreover, transcriptomics study is helpful in drug discovery.
+For example, the overexpressed gene is possible to be a drug-targetable candidate\cite{Park2015}.
+After thoughtful validation in vitro/in vivo then pathway study, the EGFR inhibitory leads were constructed by antibody design or chemical compound screening\cite{Mahajan2016}.
+%比較容易研發 clinical and transcriptomics by ssurvival::survfit and urvival::coxph
+% the selection of clinicalfeatures by domain knowledge and studies where HNSCC was under investigation.
+The discovery of EGFR inhibitors\cite{Bonner2006a} for HNSCC therapy will encourage research community to conduct the survival analysis under abnormality in gene expression.
 
-The presence of widespread genomic instability in HNSCC, such as cytogenetic aberrations, allelic imbalance/loss of heterozygosity, and microsatellite instability, suggests that there is an imperfection in the host DNA repair machinery.
-Genomic instability with progressive accumulation of detrimental genetic alterations appears to be dependent upon a circuitous interaction between the environmental genotoxic insults and the host DNA repair machinery, the functional integrity of which is governed by the proper cell cycle control and host DNA repair capacity.
-https://www.nature.com/articles/nature14129 Comprehensive genomic characterization of head and neck squamous cell carcinomas
-Genomics allows the identification of possibly relevant variants, such as single nucleotide polymorphisms (SNPs), copy number variation (CNV), mutations and translocations => %https://cancersheadneck.biomedcentral.com/articles/10.1186/s41199-020-0047-y
-
-%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7080958/#SM8 The Landscape of Somatic Copy Number Alterations in Head and Neck Squamous Cell Carcinoma, 2020.
-18 GSE dataset + TCGA: chromothripsis 6\%
-
-TMB: To calculate TMB, you need to know the total size of the region sequenced.
-If data is from exome sequencing, you would find the size of the exome capture, and divide total mutations (or non-synonymous only depending on strategy), by that size (e.g.
-~45MB) to get SNV/MB ratio.
-
-ICIs <- TMB <- DDR DNA repair gene
-Identification of Genomic Predictors for Treatment Response to Cancer Immunotherapy Using Omics Data Analysis
-Yu-Chao Wang
-
-tumor mutational burden-high (TMB-H) [≥10 mutations/megabase (mut/Mb)] solid tumors (for pembrolizumab)
-
-\acrshort{egfr} amplification, mutation
-%===================
-epigenetic trinity:
-%http://www.biomedicine.org.tw/Upload/07_DNA甲基化程度在大腸直腸癌扮演的角色.pdf
-%脊椎動物之基因體中約20\%之序列為5'-GC-3' (簡稱CpG)之雙核苷酸(dinucleotide)。然而有 些長約1至2kb之序列段，其CpG含量高達60% (CpG islands)
-
-60\% protein-coding genes with CpG islands on their promoter region
-
-(
-McGough JM, Yang D, Huang S, et al.
-DNA methylation represses IFN-gamma-induced and signal transducer and activator of transcription 1-mediated IFN regulatory factor 8 activation in colon carcinoma cells.
-Mol Cancer Res 2008;6:1841-1851.
-)
-
-methyl CpG-binding domain protein; MBD prevents TF binding on the promoter of gene
-=> causing impairment of mismatch repair; MMR => microsatellite instable; MSI
-
-%環境因子的致癌機轉
-=>CpG hypermethylation
-turn off tumor suppressor genes
-and
-Hypomethylation turn on oncogene
-DKK1
-...
-hypomethylation ->
-loss of gene imprinting
-alleles 
-..
-histone methylation
-%http://webcache.googleusercontent.com/search?q=cache:z8zvnjS-C3AJ:sites.mc.ntu.edu.tw/board.php?courseID%3D83%26f%3Ddoc%26folderID%3D581%26cid%3D3060&client=safari&hl=en&gl=tw&strip=1&vwsrc=0
-%雖然以上我們討論的是癌症的基因體，但癌症的厲害就是它本來就利用人體原有的生物機制來生存（co-opting），因此，以上在癌症觀察到的基因體複雜性，其實也存在於正常人體.
-
-%從最早，很單純的基因之exon序列，轉錄成mRNA，再轉譯成polypeptide，形成protein，到現在還要考慮epigenetics、mi RNA、TUF (ENCODE將之名為transcripts of unknown function (TUF)=> non-coding RNA 後來很紅)、chromosome environment，基因體的複雜性真是增加了不知多少倍，這也提醒我們在了解基因功能方面，必需更有全面性的關照。這也是「基因體醫學」必需以「基因體科學」為基礎的道理。
-
-%...
-
-%DNA mutation, copy number 增加造成 overexpression of gene
-
-???Answer:
-%所以 DNA vs mRNA
-high dimensional multi-omics analysis by CNN 
-%分析不是獨立變數，彼此有 confounding 放入分析需要使用不同的方法
-
-It may be beneficial to include these different data types in models predicting outcomes, such as the survival time of patients.
+% *** it needs deep learning, but less interpretability (yet under development\cite{Chaudhary2018}) (DNA+RNA and clinical dataset => multi-omics cancer study)
+%high dimensional multi-omics analysis by deep learning 
+%It may be beneficial to include these different data types in models predicting outcomes, such as the survival time of patients.
 Until recently, only data from a single omics type were used to build such prediction models, with or without the inclusion of standard clinical data [2].
@@
 %特別的 algorithm 
-..
-Or
+%however, interpretation and practical application of the model to the prediction of independent data are easier with regression-based methods yielding coefficients that reflect the effects of variables on the outcome than with machine learning algorithms [8].
+%Multi-omics data, that is, datasets containing different types of high-dimensional molecular variables; they must be able to handle data where the number of variables by far exceeds the number of observations.
+%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6419526/
+%Deep learning
+%SALMON (Survival Analysis Learning with Multi-Omics Neural Networks)
 
-https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6419526/
+%\cite{Lawrence2015a} TCGA %的第一篇文章已經分析過 DNA mutation of HNSCC
+%Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature, 517(7536), 576–582.
 
-Deep learning
+%The presence of widespread genomic instability in HNSCC, such as cytogenetic aberrations, allelic imbalance/loss of heterozygosity, and microsatellite instability (MSI), suggests that there is an imperfection in the host DNA repair machinery.
+Genomic instability with progressive accumulation of detrimental genetic alterations appears to be dependent upon a circuitous interaction between the environmental genotoxic insults and the host DNA repair machinery, the functional integrity of which is governed by the proper cell cycle control and host DNA repair capacity.
+Genomics allows the identification of possibly relevant variants, such as single nucleotide polymorphisms (SNPs), copy number variation (CNV), mutations and translocations => %https://cancersheadneck.biomedcentral.com/articles/10.1186/s41199-020-0047-y
+%DNA mutation: copy number burden (CNB) and tumor mutation burden (TMB) are important for predicting tumor progression (Marshall et al., 2017; Thomas et al., 2018)
+% *** The Landscape of Somatic Copy Number Alterations in Head and Neck Squamous Cell Carcinoma, 2020. => 18 GEO dataset (873 patients from GEO) + TCGA: chromothripsis 6\%\cite{Yang2020}
+%metaanalysis of NCBI GEO database (https://www.ncbi.nlm.nih.gov/geo/).
+We integrated the following datasets: TCGA-HNSCC, GSE11938, GSE20306, GSE20939, GSE23831, GSE25103, GSE31984, GSE33229, GSE33983, GSE34507, GSE36790, GSE39367, GSE40777,GSE47443, GSE51265, GSE57201, GSE66136, GSE68717, and GSE85514.
 
-SALMON (Survival Analysis Learning with Multi-Omics Neural Networks)
+%TMB: To calculate TMB, you need to know the total size of the region sequenced.
+If data is from exome sequencing, you would find the size of the exome capture, and divide total mutations (or non-synonymous only depending on strategy), by that size (e.g.
+~45MB) to get SNV/MB ratio.
+%tumor mutational burden-high (TMB-H) [≥10 mutations/megabase (mut/Mb)] in solid tumors (criteria for pembrolizumab)
+%Identification of Genomic Predictors for Treatment Response to Cancer Immunotherapy Using Omics Data Analysis (Yu-Chao Wang)
+%=> ICIs criteria <- TMB <- DDR DNA repair gene
+\end{MyColorPar}
+\pagebreak
+%======
 
-DNA mutation:
-copy number burden (CNB) and tumor mutation burden (TMB) are important for predicting tumor progression (Marshall et al., 2017; Thomas et al., 2018)
-\end{MyColorPar}
+Comments from the reviewer \#2
 
-%======
-\subsection*{2-1}
-reviewer \#2
+How representative is the TCGA database for HNSCC?
 
-Can be improved
-Does the introduction provide sufficient background and include all relevant references? [Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.] 1) 4)
+Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?
+
+Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?
+
+Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.
 
 %[找出其他 database cohort 的比較]
-2-1) How representative is the TCGA database for HNSCC?
+\subsection*{2-1}
+How representative is the TCGA database for HNSCC?
 
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
-%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).
-\cite{Lawrence2015a}
-until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).
-\cite{Tang2019}\cite{Wei2020a}
-(ok)
+We appreciate the reviewer for the question giving an opportunity to discuss TCGA in detail.
+To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
+When we queried from the Embase database using the MESH words "HNSCC AND TCGA", a simple statistics shows total 12,636 research articles/conference abstracts for HNSCC from 2008 to 2021, since the first TCGA article was published on 2008\cite{McLendon2008} by TCGA research network.
+Thereafter, there are 18,082 cross-cancer type articles which were produced using TCGA database.
+The 778 publications among them were focused on HNSCC research.
+Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time period.
+Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008.
+(see Figure below) %\ref{figure:fig_embase}
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_2-1.pdf}
+%\label{figure:fig_embase}
+\end{figure}
+\clearpage
+%778/4350 = 17.9\% using TCGA data
+%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
+%http://www.actrec.gov.in/OCDB/index.htm
+
+Despite of other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI GEO datasets (e.x.
+GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.
+However,  MSKCC, Broad and Johns Hopkins databases were processed the whole-exome sequencing instead of whole-genome sequencing in TCGA database.
+
+There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010}, and SurvExpress\cite{Aguirre-Gamboa2013}.
+According to the citing articles\cite{Wu2020} and their online documents, the back-end database was collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO (available at https://www.ncbi.nlm.nih.gov/gds) datasets.
+Furthermore, almost all of their survival data came from TCGA database.
+%GEO (few survival features, less than 100 participate in each GSE dataset)
+%GSE31056, GSE2837 (Prognoscan)
+%there is survival feature: A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
+%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).\cite{Lawrence2015a}
+%datasets for each cancer type that include exactly the same prediction and outcome variables and consider comparable target populations. Currently, such data is simply not available.
+
+Conclusion: TCGA database is representative for HNSCC.
+
 \end{MyColorPar}
@@
 ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
-Relapse Free Survival (RFS) in GSE2837 (not available in the TCGA dataset)
+Relapse Free Survival (RFS) in GSE2837 (not available on the TCGA dataset)
 microarray gene expression experiments (Affymetrix X3P chips U133\_X3P)
@@
 
-there is survival feature:
-A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
-GSE52793: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE52793
-GSE75537: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE75537
 \end{MyColorPar}
@@
 https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
+The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 30 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
+Sample types available at TCGA are: primary solid tumors, recurrent solid tumors, blood derived normal and tumor, metastatic, and solid tissue normal.
+
 \end{MyColorPar}
@@
 \subsection*{3-1}
-reviewer \#3
+Comments from the reviewer \#3
 
@@
 We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
+
+DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet_HNSCC_result.tsv)\cite{Li2012a}.
+%gene regulatory or protein interaction network
+% cited by 10 articles
+% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
+% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
+The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
+
 a) Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
@@
 % bad guy
+until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).
+\cite{Tang2019}\cite{Wei2020a}
+https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
 http://gepia2.cancer-pku.cn/detail.php?gene=DKK1

### 2021-01-27 main.tex
Answer 2-1 done

@@
 They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
-SurvivaX.jsp, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort. After downloading the survival results, they could curate plots and tables carefully.
+SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort.
+After downloading the survival results, they could curate plots and tables carefully.
 It is not possible to scan the whole human protein-coding genome in this way.
@@
 
-The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available on a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
+The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
 %\cite{SeanDavis;MartinMorgan2020}
@@
 %All the supplementary figures, tables, and R script codes 
-The R script codes and datasets generated during the current study are available in the GitHub repository, https://github.com/texchi2/pvalueTex.}
+The R script codes and datasets generated during the current study are available at the GitHub repository, https://github.com/texchi2/pvalueTex.}
 

### 2021-01-27 rebuttal_responses_revision1.tex
2-2 figure

@@
 Thereafter, there are 18,082 cross-cancer type articles which were produced using TCGA database.
-The 778 publications among them were focused on HNSCC research.
+The 778 publications (Figure \ref{figure:fig_embase}, b.
+778) among them were focused on HNSCC research.
 Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time period.
 Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008.
-(see Figure below) %\ref{figure:fig_embase}
+%\ref{figure:fig_embase}
 \begin{figure}
@@
 \includegraphics[width=14cm]{Answer_2-1.pdf}
-%\label{figure:fig_embase}
+\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
+\label{figure:fig_embase}
 \end{figure}
@@
 There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010}, and SurvExpress\cite{Aguirre-Gamboa2013}.
-According to the citing articles\cite{Wu2020} and their online documents, the back-end database was collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO (available at https://www.ncbi.nlm.nih.gov/gds) datasets.
+According to the citing articles\cite{Wu2020} and their online documents, the back-end database was collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
 Furthermore, almost all of their survival data came from TCGA database.
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
-GSE2837 (GEO) from PrognoScan: http://dna00.bio.kyutech.ac.jp/PrognoScan-cgi/PrognoScan.cgi \cite{Mizuno2009a}
-https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
-ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
-Relapse Free Survival (RFS) in GSE2837 (not available on the TCGA dataset)
-microarray gene expression experiments (Affymetrix X3P chips U133\_X3P)
-cohort: VUMC, VAMC, UTMDACC (1992-2005), published on 2006
-40 HNSCC samples
-cohort n=28 in the following probes of genes with survival significance:
-17 out of 20 candidates => 10 genes achieve similar positive and negative prognostic effect comparable with our candidate genes, however, its group separation was be cut by a skewed manner
+We appreciate the reviewer for the critical comment.
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort 40 cases) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan-cgi/PrognoScan.cgi)\cite{Mizuno2009a}.
+MD Anderson (40 cases)
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+The GSE2837 has data from HNSCC cohort,
+% VUMC, VAMC, UTMDACC (1992-2005)
+which recruited 28 participants with 
+relapse free survival (RFS) data, 
+%(TCGA dataset: overall survival)
+and microarray gene expression (Affymetrix X3P chips U133\_X3P).
+The result shows the survival significance is in the following probes of genes:
+%17 out of 20 candidates
+11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes, however, PrognoScan has group separation cut by a skewed manner.
+poor prognosis: DKK1, CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2
+better prognosis: IL19, FCGBP, KIAA1683 (IQCN), NPB
+
+%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
+
 FCGBP (P-value 0.005658 of KM plot)
 FOXA2 (0.001587)
+(please see Figure \ref{figure:fig_GSE2837}
 
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_2-2.pdf}
+\caption{GSE2837 query results from PrognoScan}
+\label{figure:fig_GSE2837}
+\end{figure}
+\clearpage
 \end{MyColorPar}

### 2021-01-28 rebuttal_responses_revision1.tex
Updates from Overleaf

@@
 We appreciate the reviewer for the critical comment.
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort 40 cases) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan-cgi/PrognoScan.cgi)\cite{Mizuno2009a}.
-MD Anderson (40 cases)
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
 %https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 has data from HNSCC cohort,
+The GSE2837 carries
 % VUMC, VAMC, UTMDACC (1992-2005)
-which recruited 28 participants with 
-relapse free survival (RFS) data, 
-%(TCGA dataset: overall survival)
-and microarray gene expression (Affymetrix X3P chips U133\_X3P).
-The result shows the survival significance is in the following probes of genes:
+relapse free survival (RFS) data, instead of overall survival in TCGA dataset,
+and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
+The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
+1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
 %17 out of 20 candidates
-11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes, however, PrognoScan has group separation cut by a skewed manner.
-poor prognosis: DKK1, CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2
-better prognosis: IL19, FCGBP, KIAA1683 (IQCN), NPB
-
+%?DKK1 (0.253635), 
+Please see Figure \ref{figure:fig_GSE2837}.
+Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far less participants than TCGA cohort.
 %DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
 %ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
-
-FCGBP (P-value 0.005658 of KM plot)
-FOXA2 (0.001587)
-(please see Figure \ref{figure:fig_GSE2837}
+%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
+The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using GSE2837 dataset other than TCGA cohort.
 
@@
 \includegraphics[width=14cm]{Answer_2-2.pdf}
-\caption{GSE2837 query results from PrognoScan}
+\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
 \label{figure:fig_GSE2837}
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
-Currently, less HNSCC dataset is available worldwide (Indian?) => GEO
-generalized use is fine for this workflow, it needs to modify the R code to adapt 
+We appreciate the reviewer for the critical comments and thank for your agreement of our workflow in cancer research.
+
+the elements of the workflow:
+\begin{itemize} %summarize the elements of the workflow
+    \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
+    \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
+    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
+\end{itemize}
+Currently, less HNSCC dataset is available worldwide (Indian?) => 
+GEO database could be generalized applied by this workflow, since modification of the R script is necessary.
 %能否套用在別的 database，可以，但需要 d/l raw microarray or RNA-seq 而且需要標準化(fpkm or RSEM)
@@
 Moreover, we are planning to expand this workflow for pan-cancer studies (other cancer types in the TCGA database).
-the elements of the workflow: ...
+
+% workflow
+The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}.
+The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
+The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
+It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
+We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].\newline
+Fire.Rda".
+After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
+We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
+We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
+
+We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
+Fire.Rda" (accessed November 2019).
+
+One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
+[GeneName].Fire.Rda" tables were transposed and merged by their \newline
+\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
+The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
+The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
+% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
+We made data clean by removing duplicated rows and columns.
+
+%\subsection{Cutoff Finder Core Engine}
+To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
+Our cutofFinder\_func subroutine employs the minimum P-value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
+First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
+Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort").
+The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier P-values for each gene.
+Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum P-value, was selected by the cutofFinder\_func subroutine.
+This iteration method could calculate all possible cutoff of each gene expression in this cohort.
+At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x.
+0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}).
+The optimal cutoff value and its correlated patient grouping size (e.x.
+low-expression in 262 persons vs.
+high-expression in 152 persons with gene \acrshort{CAMK2N1}) would be returned to the main program to allow downstream Cox survival analysis.
+The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
+In case there was no significant P-value, a median expression of this gene was set as its cutpoint as usual.
+
+%\subsection{Biomarker Selection}
+
+Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
+Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
+
+% we plan to extend this workflow on other TCGA cancer types
+Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+% second limitation:
+In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers.
+However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
+Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
+It should be carefully curated to confirm the data integrity with the correct definition.
+We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R.
+The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}.
+Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
 \end{MyColorPar}
@@
 Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.
+
+% from materials and methods
+The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
+%\cite{SeanDavis;MartinMorgan2020}
+GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
+\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
+Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
+The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
+FirebrowseR)\cite{Deng2017}. 
+We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, step 1) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
 
@@
 Are the results clearly presented?
-Are the conclusions supported by the results?
+*** Are the conclusions supported by the results?
 
@@
 
-DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet_HNSCC_result.tsv)\cite{Li2012a}.
+by GEO 2387? (PrognoScan)
+by Embase/Pubmed articles
+by HPA
+
+DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
 %gene regulatory or protein interaction network
@@
 
-b) (ok) SurvExpress
+b) (ok) SurvExpress (TCGA)
 %試試利用手動找到類似的結果 
@@
 %x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+c) At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa}
+(available at https://www.proteinatlas.org/humanproteome/\newline
+pathology/head+and+neck+cancer, accessed 28 September 2020). The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+
 We provide more evidences mentioned above to support the prognostic impact of these candidate genes. It needs to be further validated.
@@
 
-\section{Highlights}
-Highlights
-\begin{itemize}
-    \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
-    \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
-    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
-\end{itemize}
+%\section{Highlights}
+%Highlights
 

### 2021-01-28 rebuttal_responses_revision1.tex
Answer 2-2 complete

@@
 
+to generalize the purpose of our workflow:
+TCGA HNSCC -> TCGA CRC -> TCGA LUAD -> TCGA BRCA -> GEO or other uploaded cancer cohort
+how to apply or modify the R scripts to use other datasets
 the elements of the workflow:
+raw data cleaning
+Description:table transformation and merge
+data structure (dataset schema): GDAC format
+clinical features: dichotomization
+R scripts could not be applied to start the analysis of any dataset without re-coding.
+%R 的特色 邊分析解讀，一邊 coding
 \begin{itemize} %summarize the elements of the workflow

### 2021-01-31 rebuttal_responses_revision1.tex
Answer2-4 done

--- 2021-01-27 rebuttal_responses_revision1.tex
@@
 }%
+
+\usepackage{outlines}
 
@@
 
-Despite of other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI GEO datasets (e.x.
+Despite of other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
 GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.
@@
 
-There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010}, and SurvExpress\cite{Aguirre-Gamboa2013}.
+There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, and UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a}.
 According to the citing articles\cite{Wu2020} and their online documents, the back-end database was collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
-Currently, less HNSCC dataset is available worldwide (Indian?) => GEO
-generalized use is fine for this workflow, it needs to modify the R code to adapt 
-%能否套用在別的 database，可以，但需要 d/l raw microarray or RNA-seq 而且需要標準化(fpkm or RSEM)
-It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
-Moreover, we are planning to expand this workflow for pan-cancer studies (other cancer types in the TCGA database).
-the elements of the workflow: ...
+We appreciate the reviewer for the critical comments and thank for your agreement of our workflow in the field of cancer research.
+
+%how to apply or modify the R scripts to use on other datasets
+%\begin{itemize} %summarize the elements of the workflow
+\begin{outline}
+The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x.
+data schema, table size, definition of features, number of features and their location on the table column).\\
+In short, the elements of the workflow with the \{codes\} shows:\\
+(please also see Figure \ref{fig:workflow})
+\1 $[\# step 1 (main)]$
+\{main\_marginSFP\_HNSCC.R\}
+        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
+%\1 $[\# step 1]$
+    \2 \{TCGA\_HNSCC\_marginSFP.R\}
+        \3 \underline{raw data cleaning}
+        \3 \underline{data transformation and merge}
+        \3 \underline{dichotomization of clinical features}
+%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
+        \3 survival analysis
+            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
+%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
+            \4 Cox modelling
+\1 $[\# step 2]$
+\{analysis\_export.R\}
+    \2 analysis of the tables generated from \# step 1
+    \2 candidate selection
+%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
+\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
+\end{outline}
+
+%\begin{outline}
+%\linebreak
+
+%\1 $[\# step 1]$
+%\{TCGA\_HNSCC\_marginSFP.R\}
+%    \2 raw data cleaning
+%    \2 data transformation and merge
+%    \2 clinical features
+%\end{itemize}
+%\end{outline}
+
+%to generalize the utility of our workflow:
+%R scripts could be re-coded and applied to start a new analysis of dataset.
+% *** R 的特色 邊分析解讀，一邊 coding
+%Currently, less HNSCC dataset is available worldwide (Indian?) => 
+%能否套用在別的 database，可以，需要標準化(fpkm or RSEM)
+%It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
+Moreover, we are planning to extend this workflow applied on other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
+Then it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=14cm]{Figure_1_manuscript_workflow_modify.pdf}
+    \caption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).
+The portion of "data process/cleaning"(red rectangled) should be modified aggressively according to different databases.}
+    \label{fig:workflow}
+\end{figure}
+%(other cancer types in the TCGA database). 
+%TCGA HNSCC -> TCGA CRC, TCGA LUAD, TCGA BRCA cohorts -> GEO or other uploaded cancer cohort
+
+% workflow from the manuscript ##########
+%The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}.
+The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
+%The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
+It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
+%We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].\newline
+%Fire.Rda".
+%After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
+We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
+We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
+
+%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
+%Fire.Rda" (accessed November 2019).
+
+%One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
+%[GeneName].Fire.Rda" tables were transposed and merged by their \newline
+%\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
+%The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
+%The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
+% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
+%%We made data clean by removing duplicated rows and columns.
+
+%\subsection{Cutoff Finder Core Engine}
+%To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
+%Our cutofFinder\_func subroutine employs the minimum P-value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
+%First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
+Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort").
+The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier P-values for each gene.
+%Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum P-value, was selected by the cutofFinder\_func subroutine.
+%This iteration method could calculate all possible cutoff of each gene expression in this cohort.
+At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x.
+0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}).
+The optimal cutoff value and its correlated patient grouping size (e.x.
+low-expression in 262 persons vs.
+high-expression in 152 persons with gene \acrshort{CAMK2N1}) would be returned to the main program to allow downstream Cox survival analysis.
+The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
+%In case there was no significant P-value, a median expression of this gene was set as its cutpoint as usual.
+
+%\subsection{Biomarker Selection}
+
+%Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
+%Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
+
+% we plan to extend this workflow on other TCGA cancer types
+%Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+% second limitation:
+%In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers.
+However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
+Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
+It should be carefully curated to confirm the data integrity with the correct definition.
+We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R.
+The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}.
+Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
 \end{MyColorPar}
 
+% #####################
 \subsection*{2-4}
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
-*** We modified the introduction according to reviewer's comment...
-https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
-The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 30 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
+We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
+
+%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga
+% adopted from materials and methods
+
+%The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
+%\cite{SeanDavis;MartinMorgan2020}
+\textcolor{red}{
+The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI) funded by the US government since 2005.
+TCGA represents a comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - October 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
+%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
+
+TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA) and protein (reverse protein phase array) of the biospecimen.
 Sample types available at TCGA are: primary solid tumors, recurrent solid tumors, blood derived normal and tumor, metastatic, and solid tissue normal.
+\acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+
+The NCI's Genomic Data Commons (GDC, available at https://portal.gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
+%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
+\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research.
+Thus, TCGA has remarkable advantage for computational and life scientists who study cancer, and many achievements of diagnoses, treatments and prevention with these data have already been published.\cite{Tomczak2015}
+There is three categories of routes to approach the TCGA data from GDC.
+
+First, GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools, and other available web-based tools so far has been reviewed by Zhang et al.\cite{Zhang2019b} and
+Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
+One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC Firehose), provides TCGA public-accessible Level 3 data and Level 4 analyses packaged in a form amenable to immediate algorithmic analysis.
+This is an analytical infrastructure to access analyses algorithms not performed by the GDC (e.g.
+GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering etc.).
+A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40 , 2019\-10\-13).
+%Python and UNIX bindings
+%R bindings
+Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a comprehensive mutation analysis of each TCGA disease.
+
+Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
+% RESTful API
+
+Third, the GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
+This includes searching, viewing, submitting and downloading subsets of data files, metadata, and annotations based on specific parameters.
+Moreover, if restricted data is requested, a token must be provided by the user along with the API call.
+This token can be downloaded directly from the GDC Portals.
+(this paragraph was originally published and courtesy of the National Cancer Institute)
+
+Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
+FirebrowseR)\cite{Deng2017}.
+In our workflow, we utilized FirebrowseR in the step 1 to receive standardized data frames while avoiding data re-formatting, often causing some errors. (please also see Figure \ref{fig:workflow})
+% clinical
+We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
+}   % marked in red
+
+%The other GDAC, the MD Anderson GDAC's MBatch (http://bioinformatics.mdanderson.org/tcgabatcheffects) is a website that enables scientists to identify and quantify the batch effects accompanying TCGA data set, currently according to hierarchical clustering and enhanced PCA plots.
+
+% RNA-Seq
+%The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
+%The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
+It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
 
 \end{MyColorPar}
+\pagebreak
 
@@
 
-\section{Highlights}
-Highlights
-\begin{itemize}
-    \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
-    \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
-    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
-\end{itemize}
+%\section{Highlights}
+%Highlights
+% https://quicklatex.com
+\begin{flushleft}
+% equation
+%\begin{math}
+Linear regression equation (without error term)\par
+\linebreak\\[1cm]
+ground truth Y:\\[0.5cm]
+predicted $\hat Y$:\\[0.3cm]
+$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
+\linebreak
+\linebreak
+input $X_1...n$
+\\[0.5cm]
+(predicted Y, output)
+intercept
+slope
+independent (input) \Times
+%\end{math}
+\end{flushleft}
 

### 2021-01-31 rebuttal_responses_revision1.tex
Answer 2-4 done

@@
 
-We appreciate the reviewer for the question giving an opportunity to discuss TCGA in detail.
+We appreciate the reviewer for the question giving an opportunity to discuss TCGA in detail.\\
 To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
@@
 There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, and UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a}.
-According to the citing articles\cite{Wu2020} and their online documents, the back-end database was collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
+According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
 Furthermore, almost all of their survival data came from TCGA database.
@@
     \caption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).
-The portion of "data process/cleaning"(red rectangled) should be modified aggressively according to different databases.}
+The portion of "data process/cleaning"(red rectangled) should be modified aggressively according to different sources of databases, e.x.
+The NCI's TCGA Genomic Data Commons (GDC) porting to Broad Firehose, or other databases.}
     \label{fig:workflow}
@@
 %\cite{SeanDavis;MartinMorgan2020}
-\textcolor{red}{
+
+\begin{MyColorPar}{red}
+
 The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI) funded by the US government since 2005.
@@
 
-TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA) and protein (reverse protein phase array) of the biospecimen.
+TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA) and protein (reverse protein phase array) data derived from biospecimen.
 Sample types available at TCGA are: primary solid tumors, recurrent solid tumors, blood derived normal and tumor, metastatic, and solid tissue normal.
-\acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
 
-The NCI's Genomic Data Commons (GDC, available at https://portal.gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
+The NCI's Genomic Data Commons (GDC, available at https://portal.\\gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
+The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
+The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
 %The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
-\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research.
-Thus, TCGA has remarkable advantage for computational and life scientists who study cancer, and many achievements of diagnoses, treatments and prevention with these data have already been published.\cite{Tomczak2015}
-There is three categories of routes to approach the TCGA data from GDC.
+\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research. %There is three categories of tools to approach the TCGA data from GDC.
 
-First, GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools, and other available web-based tools so far has been reviewed by Zhang et al.\cite{Zhang2019b} and
-Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
-One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC Firehose), provides TCGA public-accessible Level 3 data and Level 4 analyses packaged in a form amenable to immediate algorithmic analysis.
-This is an analytical infrastructure to access analyses algorithms not performed by the GDC (e.g.
+GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools. Other available web-based tools has been reviewed by Zhang et al.\cite{Zhang2019b} and 
+Matthieu Foll (availalbe at https://\\github.com/IARCbioinfo/awesome-TCGA).
+One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose which is a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
+Broad GDAC Firehose is an analytical infrastructure to provide analyses algorithms not performed by the GDC (e.x.
 GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering etc.).
@@
 %R bindings
-Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a comprehensive mutation analysis of each TCGA disease.
+Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.
 
-Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
+%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
 % RESTful API
 
-Third, the GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
+GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
 This includes searching, viewing, submitting and downloading subsets of data files, metadata, and annotations based on specific parameters.
@@
 (this paragraph was originally published and courtesy of the National Cancer Institute)
+Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
 
-Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
-FirebrowseR)\cite{Deng2017}.
-In our workflow, we utilized FirebrowseR in the step 1 to receive standardized data frames while avoiding data re-formatting, often causing some errors. (please also see Figure \ref{fig:workflow})
 % clinical
-We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
-}   % marked in red
+%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
 
+%In summarize the advantages of its use.
+In summary, the advantages of applying the TCGA data for cancer research includes:
+\begin{outline}
+\1  To the best of our knowledge, TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
+The whole-genome sequencing data has been harmonized cross all GDACs.
+The basic demographic data is usually available on many database.
+However, TCGA data has more comprehensive features, such as exposure of alcohol, asbestos, radioactive radon, tobacco smoking or cigarette, than others.
+\1  TCGA has remarkable advantage for computational and life scientists who study cancer, since useful web-tools and API are ready for analysis and visualization of TCGA data.
+It might be getting help easily from research community for trouble-shooting.
+\1  Many achievements of diagnoses, treatments and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
+\end{outline}
+
+\end{MyColorPar}   % marked in red above
+In our workflow, we utilize FirebrowseR in the step 1 to receive standardized genomic and clinical data frames while avoiding data re-formatting, often causing some errors.
+(please also see Figure \ref{fig:workflow}, different sources of databases)
 %The other GDAC, the MD Anderson GDAC's MBatch (http://bioinformatics.mdanderson.org/tcgabatcheffects) is a website that enables scientists to identify and quantify the batch effects accompanying TCGA data set, currently according to hierarchical clustering and enhanced PCA plots.
@@
 
-Must be improved:
-Is the research design appropriate?
-Are the results clearly presented?
+%Must be improved:
+%Is the research design appropriate?
+%Are the results clearly presented?
 *** Are the conclusions supported by the results?
 
-3-1) Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.
+Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.
 
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
+We appreciate the reviewer for the critical comment. We provide more evidences mentioned below, to support the prognostic impact of these candidate genes. It needs to be further validated.
+According to the reviewer's comment, the Discussion was modified accordingly (marked as red).
+
+\begin{MyColorPar}{red}
 
@@
 
-We provide more evidences mentioned above to support the prognostic impact of these candidate genes. It needs to be further validated.
+\end{MyColorPar} % marked as red
+
 \end{MyColorPar}
@@
 
-%\section{Highlights}
+\section{linear regression}
 %Highlights

### 2021-01-31 rebuttal_responses_revision1.tex
Answer3-1: PrognoScan done

@@
 
-by GEO 2387? (PrognoScan)
-by Embase/Pubmed articles
-by HPA
+\subsubsection*{SurvExpress} % TCGA
+SurvExpress\cite{Aguirre-Gamboa2013} is
+%試試利用手動找到類似的結果 2021/01/23 pdf from SurvExpress
+web-based tools for Biomarker comparison and validation of survival gene expression data.
+Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
+1) poor prognosis: DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1;
+%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: ZNF557, ZNF266, FCGBP.
+%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635),
+The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort. Please see Figure \label{fig_SurvExpress}
 
-DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
+% red or green is NOT by expression level
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_3-1.pdf}
+\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization.
+%cumulative P-value plots).
+The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{yellow}{yellow}.}
+\label{figure:fig_SurvExpress}
+\end{figure}
+\clearpage
+
+% % SurvExpress 沒有類似的結果是因為:
+Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
+Our workflow has advantage to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage.
+%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
+
+%\subsubsection{HPA} still TCGA's RNA-Seq
+%The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
+The HPA's Pathology Atlas makes analysis of each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
+Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
+ %All transcriptomics data has been retrieved from the Cancer Genome Atlas and all proteomics data has been generated in-house using the same antibodies
+%Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020\-11\-19).
+The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+
+% Version: 3.0.2 Date: 2015/06/11 SurvNet
+%Preloaded TCGA  data is also available for analysis.
+%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
 %gene regulatory or protein interaction network
@@
 % SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
-The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
+%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
 
-a) Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+\subsubsection*{GSE2837} % non-TCGA
+% from Anwser2-2
+%by GEO GSE2837 HNSCC dataset (PrognoScan)
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+The GSE2837 carries
+% VUMC, VAMC, UTMDACC (1992-2005)
+relapse free survival (RFS) data, instead of overall survival in TCGA dataset,
+and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
+The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
+1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635), 
+Please see Figure \ref{figure:fig_GSE2837}.
+Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far less participants than TCGA cohort.
+%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
+%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
+The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using GSE2837 dataset other than TCGA cohort.
+
+\subsubsection*{Review articles}
+by Embase/Pubmed articles
+Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
 \cite{Wei2019}
@@
 
-b) (ok) SurvExpress (TCGA)
-%試試利用手動找到類似的結果 
-Web resource for Biomarker comparison and validation of Survival gene expression data. 
-Dataset: HNSC - TCGA Head and Neck squamous cell carcinoma June 2016 (dup=all, data=raw)，(only TCGA June 2016, n=502) \cite{Aguirre-Gamboa2013}
-%有類似的結果:
-DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1,ZNF557, ZNF266, FCGBP;
-%沒有
-FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
-it supposed that ...
-%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
- (TCGA)(***please see Figure \label{fig_SurvExpress})
-
 %x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
-c) At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa}
-(available at https://www.proteinatlas.org/humanproteome/\newline
-pathology/head+and+neck+cancer, accessed 28 September 2020). The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
 

### 2021-01-31 rebuttal_responses_revision1.tex
Updates from Overleaf

@@
 
-%\cite{Lawrence2015a} TCGA %的第一篇文章已經分析過 DNA mutation of HNSCC
+%\cite{Lawrence2015a} TCGA HNSCC %的第一篇文章已經分析過 DNA mutation of HNSCC
 %Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature, 517(7536), 576–582. 
+%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
+%=> HNSCC marker paper\cite{Lawrence2015a}
 
@@
 SurvExpress\cite{Aguirre-Gamboa2013} is
-%試試利用手動找到類似的結果 2021/01/23 pdf from SurvExpress
+% 2021/01/23 pdf x 12 from SurvExpress
 web-based tools for Biomarker comparison and validation of survival gene expression data.
 Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
-1) poor prognosis: DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1;
+1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);
 %CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-2) better prognosis: ZNF557, ZNF266, FCGBP.
+2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).
 %IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
@@
 %?DKK1 (0.253635),
-The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort. Please see Figure \label{fig_SurvExpress}
+The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort. Please see Figure \ref{fig:fig_SurvExpress}.
 
@@
 %cumulative P-value plots).
-The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{yellow}{yellow}.}
-\label{figure:fig_SurvExpress}
+Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
+Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
+\label{fig:fig_SurvExpress}
 \end{figure}
@@
 \subsubsection*{Review articles}
-by Embase/Pubmed articles
-Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
-\cite{Wei2019}
-through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+After discovery by our workflow, we performed the literature review by Embase/Pubmed  to find the evidence of suggested biomarker in cancer research.
+%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
 
-% bad guy
-until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).
-\cite{Tang2019}\cite{Wei2020a}
-https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
-http://gepia2.cancer-pku.cn/detail.php?gene=DKK1
-DKK1: 13 results of HNSCC \cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}
+%%%%%% bad guy
+DKK1: 13 results of HNSCC
+The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
+Overexpression of DKK1 indicated adverse OS in bladder urothelial carcinoma (BLCA), HNSCC, and PADD.\cite{Wei2020}
+\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}
+%until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).\cite{Wei2020}
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
+%The analysis of prognosis was conducted by using the UALCAN, Gene Expression Profiling Interactive Analysis (GEPIA2)\cite{Tang2019}, and DriverDBv3 databases.
+
 CAMK2N1: 26 results of cancer: ; 1 HNSCC cell line (CAL-27)\cite{Li2018b}
+
 STC2: \cite{Ma2020}
+
 PGK1: glycolysis enzyme is responsive in cisplatin-resistant oral squamous cell carcinoma cell line\cite{Nakamura2005}
+
 SURF4: patients with tumors (not HNSCC) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.\cite{Kim2018a}
+
 USP10: one of autophagy related genes for HNSCC prognosis prediction.\cite{Ren2020}
@@
 The auto-antibody against STIP1 could be a useful biomarker for esophageal squamous cell carcinoma\cite{Xu2017}.
-DKC1, DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+
+DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
 %is the tumor suppressor gene in HNSCC
 
-% good guy
+%%%%%% good guy
 ZNF557, oncogenic human herpesviruses, EBV and KSHV are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}.
+
 ZNF266, % or ZNF16, HZF1?
+
 those genes were reported at following, 
@@
 FCGBP in thyroid cancer\cite{Griffith2006}, 
-?LOC148709?, 
+%?LOC148709?, 
 EVPLL in cDNA project,

### 2021-02-01 rebuttal_responses_revision1.tex
Answer3-1 done

@@
 
-%\subsubsection{HPA} still TCGA's RNA-Seq
-%The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
+\subsubsection{HPA} still TCGA's RNA-Seq
+The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
 The HPA's Pathology Atlas makes analysis of each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
 Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
- %All transcriptomics data has been retrieved from the Cancer Genome Atlas and all proteomics data has been generated in-house using the same antibodies
-%Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020\-11\-19).
+All transcriptomics data has been retrieved from the Cancer Genome Atlas and all proteomics data has been generated in-house using the same antibodies.
+Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020\-11\-19).
 The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+Moreover, overexpression of ubiquitin specific peptidase 10 (USP10), one of autophagy related genes, has poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+found at Human Protein Atlas dataset (HPA) https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
 
@@
 \subsubsection*{Review articles}
-After discovery by our workflow, we performed the literature review by Embase/Pubmed  to find the evidence of suggested biomarker in cancer research.
+After discovery by our workflow, we performed the literature review by Embase/Pubmed  to find the evidence of suggested 7 biomarkers in cancer research.
 %Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
@@
 %%%%%% bad guy
-DKK1: 13 results of HNSCC
 The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
-Overexpression of DKK1 indicated adverse OS in bladder urothelial carcinoma (BLCA), HNSCC, and PADD.\cite{Wei2020}
-\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+Overexpression of DKK1 indicated adverse OS in bladder urothelial carcinoma (BLCA), HNSCC\cite{Chakraborty2020}\cite{Hu2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
 %until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).\cite{Wei2020}
@@
 
-CAMK2N1: 26 results of cancer: ; 1 HNSCC cell line (CAL-27)\cite{Li2018b}
+%STC2:
+The miR-381 suppresses cell proliferation, migration and invasion in HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2), and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
 
-STC2: \cite{Ma2020}
+Phosphoglycerate kinase 1 (PGK1 or PGK-1), one of an glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
+The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression of Caveolin 1\cite{Nakamura2005}.
 
-PGK1: glycolysis enzyme is responsive in cisplatin-resistant oral squamous cell carcinoma cell line\cite{Nakamura2005}
+Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
+) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.
+SURF4 has the potential for inducing cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
+%NIH/3T3 cells (Mus musculus, mouse), 293T cell
+%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
+%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
+%web-based tools survival (not TCGA?)
 
-SURF4: patients with tumors (not HNSCC) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.\cite{Kim2018a}
+Ubiquitin specific peptidase 10 (USP10), one of autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
+Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
+https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
 
-USP10: one of autophagy related genes for HNSCC prognosis prediction.\cite{Ren2020}
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-NDFIP1, was reported as candidate biomarker for hepatocellular carcinoma\cite{Zhang2019a} and breast cancer\cite{Tian2020}.
+FOXA2:
+Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients 
+FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
+%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
+%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
+% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
+%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
+Further, SIS analysis was performed to further screen out a stable probe combination.
+Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
+2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
+Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
+2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
+%Association between gene expression and methylation.
+Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
+Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
+
+% non-TCGA
+Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
+in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. T
+The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-staged esophageal squamous cell carcinoma\cite{Xu2017}.
+%STIP1 could bind to bind Hsp70 and Hsp90.
+
+%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
+%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
+%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
+% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
+
+%%%%%% good guy
+%ZNF557 is a tumor supressor in HPV-positive HNSCC???
+%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
+%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
+%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
+
+%ZNF266, % or ZNF16, HZF1?
+%MYO1H associated mandibular prognathism\cite{Sun2018}
+
+% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
+Fc fragment of IgG binding protein (($Fc\gamma BP$, FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas.\cite{ODonovan2002}\cite{Griffith2006}
+%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
+%gene ID @gene@8857
+
+%?LOC148709?, 
+%EVPLL in cDNA project,
+Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
+
+%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
+GPR7 is associated with poor prognosis of prostate cancer\cite{Cottrell2007}.
+
+%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
+(PMID31598163)
+%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
+The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
+Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
+%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
+%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
+%\cite{Li2018b}
+%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
+%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+
+%NDFIP1:
+%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
+was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
+%MCF7 cells 
+%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
+%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
+%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
+Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
+We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
+hepatocellular carcinoma\cite{Zhang2019a}
+% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
 %  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
 It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
-FOXA2: hihger expression is significantly associated with the poor prognosis of HNSCC\cite{Shen2017a}.
-%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
-STIP1, increased expression of STIP1, detectable auto-antibody in serum sample, may indicate poor survival outcome in ovarian cancer patients\cite{Chao2013}\cite{Cho2014}.
-The auto-antibody against STIP1 could be a useful biomarker for esophageal squamous cell carcinoma\cite{Xu2017}.
 
-DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
-%is the tumor suppressor gene in HNSCC
+%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+%DKC1 is the tumor suppressor gene in HNSCC
+% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
 
-%%%%%% good guy
-ZNF557, oncogenic human herpesviruses, EBV and KSHV are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}.
-
-ZNF266, % or ZNF16, HZF1?
-
-those genes were reported at following, 
-IL19 in esophageal squamous cell carcinoma\cite{Hsing2013},
-MYO1H associated mandibular prognathism\cite{Sun2018}, 
-FCGBP in thyroid cancer\cite{Griffith2006}, 
-%?LOC148709?, 
-EVPLL in cDNA project,
-PNMA5 promotes apoptosis signaling in HeLa and MCF-7 cells\cite{Lee2016}, 
-IQCN (previous name as KIAA1683), and 
-NPB (Neuropeptide B) is endogenous ligand of the G protein-coupled receptors, named GPR7\cite{Andreis2005}, which is associated with prostate cancer prognosis\cite{Cottrell2007}.
-
-%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+The 9 out of 20 positive and negative prognostic genes underlined has been also suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
 
 \end{MyColorPar} % marked as red
+
+\begin{outline} % still blue
+In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
+Comparison with previous publications or database analyses,
+
+\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort
+
+\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using TCGA HNSCC cohort from \acrfull{hpa}.
+Moreover, overexpression of ubiquitin specific peptidase 10 (USP10), one of autophagy related genes, has poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
+
+\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using GSE2837 dataset other than TCGA cohort.
+
+\1 The 9 out of 20 positive and negative prognostic genes underlined has been also suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+
+\end{outline}
 

### 2021-02-01 rebuttal_responses_revision1.tex
Updates from Overleaf

@@
 %Are the results clearly presented?
-*** Are the conclusions supported by the results?
+Are the conclusions supported by the results?
 
@@
 
+\pagebreak
+
 \begin{outline} % still blue
@@
 Linear regression equation (without error term)\par
-\linebreak\\[1cm]
+\\[1cm]
 ground truth Y:\\[0.5cm]

### 2021-02-01 rebuttal_responses_revision1.tex
figure 4 and figure 5: done

@@
 
+The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+Overexpression of DKK1 indicated adverse OS in bladder urothelial carcinoma (BLCA), HNSCC\cite{Chakraborty2020}\cite{Hu2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+%until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).\cite{Wei2020}
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
+%The analysis of prognosis was conducted by using the UALCAN, Gene Expression Profiling Interactive Analysis (GEPIA2)\cite{Tang2019}, and DriverDBv3 databases.
+
 Conclusion: TCGA database is representative for HNSCC.
@@
 
-\subsubsection{HPA} still TCGA's RNA-Seq
+\subsubsection{HPA} %still TCGA's RNA-Seq
 The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
@@
 % 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-found at Human Protein Atlas dataset (HPA) https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
+found at Human Protein Atlas dataset (HPA, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/\\head+and+neck+cancer).
+(Please see Figure \ref{fig:fig_HPA_USP10})
+
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_3-1_USP10.pdf}
+\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
+Overexpression of USP10 has poor prognosis on HNSCC.}
+\label{fig:fig_HPA_USP10}
+\end{figure}
+\clearpage
 
@@
 
-\section{linear regression}
-%Highlights
-% https://quicklatex.com
-\begin{flushleft}
-% equation
-%\begin{math}
-Linear regression equation (without error term)\par
-\\[1cm]
-ground truth Y:\\[0.5cm]
-predicted $\hat Y$:\\[0.3cm]
-$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
-\linebreak
-\linebreak
-input $X_1...n$
-\\[0.5cm]
-(predicted Y, output)
-intercept
-slope
-independent (input) \Times
-%\end{math}
-\end{flushleft}
-
 %\reftitle{References}

### 2021-02-02 rebuttal_responses_revision1.tex
Updates from Overleaf

@@
 
-There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, and UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a}.
+There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a} and Gene Expression Profiling Interactive Analysis (GEPIA, GEPIA2)\cite{Tang2019}.
 According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
@@
 
-The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
-Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
-Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
-Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
-DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
-The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Overexpression of DKK1 indicated adverse OS in bladder urothelial carcinoma (BLCA), HNSCC\cite{Chakraborty2020}\cite{Hu2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
+%Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+%Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+%Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+%DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+%The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+
+For example, Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a web-based tools that plots expression profiles of given genes (dataset from TCGA database)
+They has suggested that overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
 %Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
 %\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-%until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).\cite{Wei2020}
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
-%The analysis of prognosis was conducted by using the UALCAN, Gene Expression Profiling Interactive Analysis (GEPIA2)\cite{Tang2019}, and DriverDBv3 databases.
 
@@
 \subsubsection*{SurvExpress} % TCGA
-SurvExpress\cite{Aguirre-Gamboa2013} is
+SurvExpress\cite{Aguirre-Gamboa2013} is one of the
 % 2021/01/23 pdf x 12 from SurvExpress
@@
 The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Overexpression of DKK1 indicated adverse OS in bladder urothelial carcinoma (BLCA), HNSCC\cite{Chakraborty2020}\cite{Hu2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+Ovverexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
 %Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
 %\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-%until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).\cite{Wei2020}
+%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
 %using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
 %GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
-%The analysis of prognosis was conducted by using the UALCAN, Gene Expression Profiling Interactive Analysis (GEPIA2)\cite{Tang2019}, and DriverDBv3 databases.
 

### 2021-02-02 rebuttal_responses_revision1.tex
rebuttal done (red marked on page xx line xx NOT YET)

@@
 
-Jan 29, 2021
+Feb 2, 2021
 
@@
 Enclosed, please find our revised manuscript (cancers-1082127) entitled "A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Cancers.
-We greatly appreciate your time in serving as the editor handling this manuscript and also thank the reviewers for their critical comments and suggestions on our manuscript.
+We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.
 
-We have since performed additional analysis, experiment and revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner, 
+We have since performed the additional literature review and revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,
+
 %{%
-1) the description of the rationale that how to pick up the Thymosin Beta-4 X-Linked (TMSB4X) in details, 2) the statistical analysis of MALDI imaging mass spectrometry and 3) the IHC staining with positive and negative control images and further analysis of nuclear TMSB4X staining.
-We re-wrote the introduction in detail and re-examined the tissue microarray slides according to the suggestion by reviewer \#1.
+% {2-4}
+"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
+We re-wrote the Introduction in detail according to the suggestion by reviewer \#2 (comment No 4).
 %}
 
-According to the editor's comments, we have the manuscript checked for English grammar and reformat Table 1 by rotating 90 degrees to portrait mode. %（Table 1 轉正)
-
-%{%
-According to the reviewers' comments, we added new Figure 1C, 2, S2, S3, and Table S2.
+% {3-1}
+"Are the conclusions supported by the results?
+Only computer computing in this research to support 20 candidate biomarkers, ... are all heavily associated with the prognosis of OS.
+There is little information provided. The authors should provide more evidence to support this article."\\
+We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
+We re-wrote the Discussion with additional information according to the suggestion by reviewer \#3.
+%}
+%{% Answer_3-1_USP10.pdf, Answer_2-1.pdf
+According to the reviewers' comments, we added new supplementary Figure S1, S2 %, S2, S3, and Table S2.
 We also replaced Figure 3D and 4A with high magnitude images from the same slides.
-We transferred the original Figure 2 into supplementary Figure S1 to enhance the rationale and removed the old supplementary Table S1.
+We transferred the original Figure 2 into supplementary Figure S1
+to provide more evidence from the significant literature review.
 %}
 
+According to the editor's comments, we have the manuscript checked for English grammar and reformatted Table 1 by rotating 90 degrees to portrait mode. %
 We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.
@@
 Taipei Medical University,
-
 Taipei, Taiwan
 
-%2) [cancers-1082127_main_redMarked] 自動化 by latex:
+%2) [cancers-1082127_main_redMarked] 自動化 by latex: red marked on page xx line xx
 %"Track Changes" function in latex => by latexdiff
@@
 \section{rebuttal} % Response2Referees
-We greatly appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
-The detailed point-by-point reply to the reviewer’s comments are as follows (marked as \textcolor{blue}{blue}).
-And the revised portions in the manuscript are indicated in \textcolor{red}{red}.
-
+We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
+The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
+Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
 %Reviewer #1(Technical Comments to the Author):
@@
 
-Comments and Suggestions for Authors
 The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method.
@@
 
-We appreciate the reviewer for the critical comments and thank for his/her agreement of our analysis using the TCGA cohort.
+We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.
 %[我的 candidate 中為什麼沒有 EGFR];  
@@
 %citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
-Thus, we wish the further validations of our meaningful hypotheses of candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
+Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
 % a list from literature review, 留 下少於  50 articles mentioned candidates
@@
 We appreciate the reviewer for reminding the importance of DNA alteration in survival analysis.
-Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e.
-DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation),
-epigenomics, transcriptomics (i.e. RNA expression), proteomics, metabolomics and microbiomics.
+Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation),
+epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
 The usefulness of multi-omics data for the prediction of HNSCC outcome is expected.
 %such as the (censored) survival time.
-Moritz Herrmann et al.(2020) observed that using multi-omics and survival data can slightly improve the performance of prediction methods for particular datasets, such as TCGA HNSCC\cite{Herrmann2020}.
+Moritz Herrmann et al.(2020) observed that using multi-omics and survival data can slightly improve prediction methods for particular datasets, such as TCGA HNSCC\cite{Herrmann2020}.
 %It is limited that the utility of multi-omics data for prediction purposes in the considered TCGA studies\cite{Herrmann2020}.
 %18 cancer datasets from The Cancer Genome Atlas (TCGA) 
-According to their study, %the multi-omics structure have a slightly better prediction performance than naive (0.562 vs.	0.557 ) with favoring clinical variables leads to better prediction results for HNSCC.
+According to their study, %the multi-omics structure have a slightly better prediction performance than naive (0.562 vs.
+0.557 ) with favoring clinical variables leads to better prediction results for HNSCC.
 %likelihood-based boosting (CoxBoost and CoxBoost favoring)
@@
 % ***
-the survival analysis of TCGA HNSCC dataset by blockForest method (with multi-omics and clinical variables) has a similar prediction performance than that by Cox's model (with clinical variables alone).
+the survival analysis of the TCGA HNSCC dataset by blockForest method (with multi-omics and clinical variables) has a similar prediction performance than Cox's model (with clinical variables alone).
 %from The Cancer Genome Atlas (TCGA)
@@
 %比較容易研發 clinical and transcriptomics by ssurvival::survfit and urvival::coxph
-% the selection of clinicalfeatures by domain knowledge and studies where HNSCC was under investigation.
-The discovery of EGFR inhibitors\cite{Bonner2006a} for HNSCC therapy will encourage research community to conduct the survival analysis under abnormality in gene expression.
+% the selection of clinical features by domain knowledge and studies where HNSCC was under investigation.
+The discovery of EGFR inhibitors\cite{Bonner2006a} for HNSCC therapy will encourage the research community to conduct the survival analysis under abnormality in gene expression.
 
@@
 
-We appreciate the reviewer for the question giving an opportunity to discuss TCGA in detail.\\
+We appreciate the reviewer for the question allowing discussing TCGA in detail.\\
 To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
-When we queried from the Embase database using the MESH words "HNSCC AND TCGA", a simple statistics shows total 12,636 research articles/conference abstracts for HNSCC from 2008 to 2021, since the first TCGA article was published on 2008\cite{McLendon2008} by TCGA research network.
-Thereafter, there are 18,082 cross-cancer type articles which were produced using TCGA database.
+When we queried from the Embase database using the MESH words "HNSCC AND TCGA," simple statistics show a total of 12,636 research articles/conference abstracts for HNSCC from 2008 to 2021, since the first TCGA article was published on 2008\cite{McLendon2008} by TCGA research network.
+After that, there are 18,082 cross-cancer type articles produced using the TCGA database.
 The 778 publications (Figure \ref{figure:fig_embase}, b.
 778) among them were focused on HNSCC research.
-Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time period.
+Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time.
 Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008.
@@
 
-Despite of other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
+Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
 GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.
-However,  MSKCC, Broad and Johns Hopkins databases were processed the whole-exome sequencing instead of whole-genome sequencing in TCGA database.
+However, the MSKCC, Broad, and Johns Hopkins databases were processed through whole-exome sequencing instead of whole-genome sequencing in the TCGA database.
 
@@
 According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
-Furthermore, almost all of their survival data came from TCGA database.
+Furthermore, almost all of their survival data came from the TCGA database.
 %GEO (few survival features, less than 100 participate in each GSE dataset)
@@
 
-For example, Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+For example, Wei et al.\cite{Wei2020} conducted the analysis of the prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
 %using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a web-based tools that plots expression profiles of given genes (dataset from TCGA database)
+%GEPIA is a web-based tool that plots expression profiles of given genes (dataset from TCGA database)
 They has suggested that overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
@@
 
-Conclusion: TCGA database is representative for HNSCC.
+Conclusion: TCGA database is representative of HNSCC.
 
@@
 % VUMC, VAMC, UTMDACC (1992-2005)
-relapse free survival (RFS) data, instead of overall survival in TCGA dataset,
+relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
 and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
@@
 Please see Figure \ref{figure:fig_GSE2837}.
-Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far less participants than TCGA cohort.
+Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
 %DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
@@
 %Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using GSE2837 dataset other than TCGA cohort.
+The 10 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using GSE2837 dataset other than the TCGA cohort.
 
@@
 
-We appreciate the reviewer for the critical comments and thank for your agreement of our workflow in the field of cancer research.
+We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
 
@@
 %It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
-Moreover, we are planning to extend this workflow applied on other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
+Moreover, we are planning to extend this workflow applied to other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
 Then it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
@@
 
-The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI) funded by the US government since 2005.
-TCGA represents a comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - October 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
+The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
+TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/\\organization/ccg/research/structural-genomics/tcga/studied-cancers).
 %The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
 
-TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA) and protein (reverse protein phase array) data derived from biospecimen.
-Sample types available at TCGA are: primary solid tumors, recurrent solid tumors, blood derived normal and tumor, metastatic, and solid tissue normal.
+TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen.
+Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.
 
@@
 
-GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools. Other available web-based tools has been reviewed by Zhang et al.\cite{Zhang2019b} and 
+GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools.
+Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and
 Matthieu Foll (availalbe at https://\\github.com/IARCbioinfo/awesome-TCGA).
-One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose which is a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
-Broad GDAC Firehose is an analytical infrastructure to provide analyses algorithms not performed by the GDC (e.x.
-GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering etc.).
-A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40 , 2019\-10\-13).
+One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
+Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x.
+GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering).
+A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).
+
 %Python and UNIX bindings
@@
 GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
-This includes searching, viewing, submitting and downloading subsets of data files, metadata, and annotations based on specific parameters.
-Moreover, if restricted data is requested, a token must be provided by the user along with the API call.
+Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
+Moreover, if restricted data is requested, the user must provide a token along with the API call.
 This token can be downloaded directly from the GDC Portals.
-(this paragraph was originally published and courtesy of the National Cancer Institute)
+(courtesy of the National Cancer Institute)
 Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
@@
 %In summarize the advantages of its use.
-In summary, the advantages of applying the TCGA data for cancer research includes:
+In summary, the advantages of applying the TCGA data for cancer research include:
 \begin{outline}
-\1  To the best of our knowledge, TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
-The whole-genome sequencing data has been harmonized cross all GDACs.
-The basic demographic data is usually available on many database.
-However, TCGA data has more comprehensive features, such as exposure of alcohol, asbestos, radioactive radon, tobacco smoking or cigarette, than others.
-\1  TCGA has remarkable advantage for computational and life scientists who study cancer, since useful web-tools and API are ready for analysis and visualization of TCGA data.
-It might be getting help easily from research community for trouble-shooting.
-\1  Many achievements of diagnoses, treatments and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
+\1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
+The whole-genome sequencing data has been harmonized across all GDACs.
+The basic demographic data is usually available on many databases.
+However, TCGA data has more comprehensive features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
+\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data.
+It might be getting help quickly from the research community for trouble-shooting.
+\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
 \end{outline}
@@
 \end{MyColorPar}   % marked in red above
-In our workflow, we utilize FirebrowseR in the step 1 to receive standardized genomic and clinical data frames while avoiding data re-formatting, often causing some errors.
+In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
 (please also see Figure \ref{fig:workflow}, different sources of databases)
@@
 
-We appreciate the reviewer for the critical comment. We provide more evidences mentioned below, to support the prognostic impact of these candidate genes. It needs to be further validated.
+We appreciate the reviewer for the critical comment. We provide more evidence mentioned below to support the prognostic impact of these candidate genes. It needs to be further validated.
 According to the reviewer's comment, the Discussion was modified accordingly (marked as red).
@@
 \subsubsection*{SurvExpress} % TCGA
-SurvExpress\cite{Aguirre-Gamboa2013} is one of the
 % 2021/01/23 pdf x 12 from SurvExpress
-web-based tools for Biomarker comparison and validation of survival gene expression data.
+SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
 Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
@@
 %?DKK1 (0.253635),
-The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort. Please see Figure \ref{fig:fig_SurvExpress}.
+The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort. Please see Figure \ref{fig:fig_SurvExpress}.
 
@@
 Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
-Our workflow has advantage to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage.
+Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
 %因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
@@
 The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
-The HPA's Pathology Atlas makes analysis of each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
+The HPA's Pathology Atlas analyzes each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
 Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
-All transcriptomics data has been retrieved from the Cancer Genome Atlas and all proteomics data has been generated in-house using the same antibodies.
-Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020\-11\-19).
+All transcriptomics data has been retrieved from the Cancer Genome Atlas, and all proteomics data has been generated in-house using the same antibodies.
+Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
 The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
-Moreover, overexpression of ubiquitin specific peptidase 10 (USP10), one of autophagy related genes, has poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/\\head+and+neck+cancer)\cite{Ren2020}.
 % 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-found at Human Protein Atlas dataset (HPA, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/\\head+and+neck+cancer).
+%found at Human Protein Atlas dataset 
 (Please see Figure \ref{fig:fig_HPA_USP10})
@@
 %https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 carries
-% VUMC, VAMC, UTMDACC (1992-2005)
-relapse free survival (RFS) data, instead of overall survival in TCGA dataset,
+The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
+relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
 and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
@@
 %Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using GSE2837 dataset other than TCGA cohort.
+The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
 
 \subsubsection*{Review articles}
-After discovery by our workflow, we performed the literature review by Embase/Pubmed  to find the evidence of suggested 7 biomarkers in cancer research.
+After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
 %Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
@@
 %%%%%% bad guy
-The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
+The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
 Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
-Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
 Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
@@
 The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Ovverexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
+Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
 %\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
@@
 %STC2:
-The miR-381 suppresses cell proliferation, migration and invasion in HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2), and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
+The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
 
-Phosphoglycerate kinase 1 (PGK1 or PGK-1), one of an glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
-The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression of Caveolin 1\cite{Nakamura2005}.
+% PGK1
+Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
+The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.
 
-Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
+%SURF4
+Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
 ) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.
-SURF4 has the potential for inducing cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
+SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
 %NIH/3T3 cells (Mus musculus, mouse), 293T cell
@@
 
-Ubiquitin specific peptidase 10 (USP10), one of autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
+% USP10
+Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
 Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
@@
 
-FOXA2:
-Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients 
+%FOXA2
+Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
 FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
@@
 
-% non-TCGA
+% STIP1; non-TCGA
 Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
 in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. T
-The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-staged esophageal squamous cell carcinoma\cite{Xu2017}.
+The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
 %STIP1 could bind to bind Hsp70 and Hsp90.
@@
 %%%%%% good guy
-%ZNF557 is a tumor supressor in HPV-positive HNSCC???
+%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
 %Oncogenic human herpesviruses (e.x. EBV and KSHV) 
@@
 
+% FCGBP
 % IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
@@
 %?LOC148709?, 
-%EVPLL in cDNA project,
+%EVPLL in cDNA project
+
+% PNMA5
 Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
 
-%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
-GPR7 is associated with poor prognosis of prostate cancer\cite{Cottrell2007}.
+%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
+GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
 
@@
 
-The 9 out of 20 positive and negative prognostic genes underlined has been also suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
 
@@
 \begin{outline} % still blue
-In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
+n conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
 Comparison with previous publications or database analyses,
@@
 \1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using TCGA HNSCC cohort from \acrfull{hpa}.
-Moreover, overexpression of ubiquitin specific peptidase 10 (USP10), one of autophagy related genes, has poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
 
-\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using GSE2837 dataset other than TCGA cohort.
+\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
 
-\1 The 9 out of 20 positive and negative prognostic genes underlined has been also suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+\1 The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
 

### 2021-02-02 rebuttal_responses_revision1.tex
Updates from Overleaf

@@
 %{%
-% {2-4}
+1) % {2-4}
 "Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
-We re-wrote the Introduction in detail according to the suggestion by reviewer \#2 (comment No 4).
+We re-wrote the Introduction in detail according to the suggestion by reviewer \#2. %(comment No 2-4).
 %}
 
-% {3-1}
+2) % {3-1}
 "Are the conclusions supported by the results?
@@
 We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
-We re-wrote the Discussion with additional information according to the suggestion by reviewer \#3.
+According to the suggestion by reviewer \#3,
+we re-wrote the Discussion with additional information, and
 %}
 %{% Answer_3-1_USP10.pdf, Answer_2-1.pdf
-According to the reviewers' comments, we added new supplementary Figure S1, S2 %, S2, S3, and Table S2.
+%According to the reviewers' comments, we 
+added new supplementary Figure S1, S2, and S3 %, S2, S3, and Table S2.
 We also replaced Figure 3D and 4A with high magnitude images from the same slides.
@@
 We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.
-
+\\[0.7cm]
 Kind regards,
@@
 We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
+In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
+(please also see Figure \ref{fig:workflow}, different sources of databases)
+
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+\\[0.3cm]
+%(the revised portions in the manuscript are indicated in \textcolor{red}{red} since page 2 at line 77-129)
 
@@
 
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 
-The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
+"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
 TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/\\organization/ccg/research/structural-genomics/tcga/studied-cancers).
@@
 Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and
-Matthieu Foll (availalbe at https://\\github.com/IARCbioinfo/awesome-TCGA).
+Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
 One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
@@
 
-%In summarize the advantages of its use.
-In summary, the advantages of applying the TCGA data for cancer research include:
+% to summarize the advantages of its use.
+The highlights of the advantages of applying the TCGA data for cancer research include:
 \begin{outline}
@@
 \1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
-\end{outline}
+\end{outline}"
 
-\end{MyColorPar}   % marked in red above
-In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
-(please also see Figure \ref{fig:workflow}, different sources of databases)
+%\end{MyColorPar}   % marked in red above
+
 %The other GDAC, the MD Anderson GDAC's MBatch (http://bioinformatics.mdanderson.org/tcgabatcheffects) is a website that enables scientists to identify and quantify the batch effects accompanying TCGA data set, currently according to hierarchical clustering and enhanced PCA plots.
@@
 
-We appreciate the reviewer for the critical comment. We provide more evidence mentioned below to support the prognostic impact of these candidate genes. It needs to be further validated.
-According to the reviewer's comment, the Discussion was modified accordingly (marked as red).
+We appreciate the reviewer for the critical comment. We provide more evidence mentioned below to support the prognostic impact of these candidate genes. We summarized the conclusion below.
 
-\begin{MyColorPar}{red}
+\begin{outline} % still blue
+In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
+Comparison with previous publications or database analyses,
 
-\subsubsection*{SurvExpress} % TCGA
+\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort
+
+\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using TCGA HNSCC cohort from \acrfull{hpa}.
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
+
+\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
+
+\1 The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+
+\end{outline}
+
+According to the reviewer's comment, the Discussion was modified accordingly.
+The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised.
+Also, it was shown here in the following paragraph.
+\\[0.3cm]
+%(the revised portions in the manuscript are indicated in \textcolor{red}{red})
+
+%\begin{MyColorPar}{red}
+
+"We utilized other approaches to validate our candidates.
+
+\subsubsection*{Analysis by web-tools}
+
+%\subsubsection*{SurvExpress} % TCGA
 % 2021/01/23 pdf x 12 from SurvExpress
@@
 %?DKK1 (0.253635),
-The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort. Please see Figure \ref{fig:fig_SurvExpress}.
-
-% red or green is NOT by expression level
-\begin{figure}
-\raggedleft
-\includegraphics[width=14cm]{Answer_3-1.pdf}
-\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization.
-%cumulative P-value plots).
-Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
-Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
-\label{fig:fig_SurvExpress}
-\end{figure}
-\clearpage
+The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort.
+Please see Supplementary Figure 1.
+%\ref{fig:fig_SurvExpress}.
+% moved to supplementary file
 
@@
 
-\subsubsection{HPA} %still TCGA's RNA-Seq
+%\subsubsection{HPA} %still TCGA's RNA-Seq
 The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
@@
 All transcriptomics data has been retrieved from the Cancer Genome Atlas, and all proteomics data has been generated in-house using the same antibodies.
-Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/\\pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
 The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/\\head+and+neck+cancer)\cite{Ren2020}.
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/\\ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
 % 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
 %found at Human Protein Atlas dataset 
-(Please see Figure \ref{fig:fig_HPA_USP10})
-
-\begin{figure}
-\raggedleft
-\includegraphics[width=14cm]{Answer_3-1_USP10.pdf}
-\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
-Overexpression of USP10 has poor prognosis on HNSCC.}
-\label{fig:fig_HPA_USP10}
-\end{figure}
-\clearpage
+(Please see Supplementary Figure 2.) %\ref{fig:fig_HPA_USP10})
+% moved to Supplementary
 
@@
 
-\subsubsection*{GSE2837} % non-TCGA
+%\subsubsection*{GSE2837} % non-TCGA
 % from Anwser2-2
 %by GEO GSE2837 HNSCC dataset (PrognoScan)
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
 %??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
@@
 %?DKK1 (0.253635), 
-Please see Figure \ref{figure:fig_GSE2837}.
+Please see Supplementary figure 3. %\ref{figure:fig_GSE2837}.
 Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
@@
 
-The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo."
 
-\end{MyColorPar} % marked as red
+%\end{MyColorPar} % marked as red
 
@@
 
-\begin{outline} % still blue
-n conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
-Comparison with previous publications or database analyses,
-
-\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort
-
-\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using TCGA HNSCC cohort from \acrfull{hpa}.
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
-
-\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
-
-\1 The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
-
-\end{outline}
-
 \end{MyColorPar}
 
-% the end of response letter
+% the end of response rebuttal
 

### 2021-02-02 main.tex
Updates from Overleaf
table 1 uprighted (by tabularx)

@@
 \newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
-
+\usepackage{outlines}
+% mark in blue or red
+\usepackage{xcolor}
+
+\newenvironment{MyColorPar}[1]{%
+    \leavevmode\color{#1}\ignorespaces%
+}{%
+}%
 %\usepackage[upplemac]{inputenc} %applemac support if unicode package fails
@@
 \usepackage{rotating}
+\usepackage{tabularx}
+\usepackage{makecell}
 % \usepackage{array}
@@
 
+\begin{MyColorPar}{red}
+%%%%%% revision1 added [TCGA] [2021/02/02]
+The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
+TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
+%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
+TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen.
+Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.
+
+The NCI's Genomic Data Commons (GDC, available at https://portal.\\gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
+The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
+The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
+\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research. %There is three categories of tools to approach the TCGA data from GDC.
+GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools.
+Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and
+Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
+One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
+Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x.
+GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering).
+A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).
+%Python and UNIX bindings
+%R bindings
+Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.
+
+%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
+% RESTful API
+
+GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
+Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
+Moreover, if restricted data is requested, the user must provide a token along with the API call.
+This token can be downloaded directly from the GDC Portals.
+(courtesy of the National Cancer Institute)
+Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
+
+% clinical
+%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
+
+% to summarize the advantages of its use.
+The highlights of the advantages of applying the TCGA data for cancer research include:
+\begin{outline}
+\1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
+The whole-genome sequencing data has been harmonized across all GDACs.
+The basic demographic data is usually available on many databases.
+However, TCGA data has more comprehensive features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
+\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data.
+It might be getting help quickly from the research community for trouble-shooting.
+\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
+\end{outline}
+
+\end{MyColorPar}
+%%%%%% end of additional revision1
+
 In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
@@
 % Table1
-\begin{sidewaystable}[hp]
+% wide table \usepackage{tabularx}
+% makecell{}
+
+\begin{table}
+%\begin{sidewaystable}[hp]
 \centering
@@
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
+\resizebox{\linewidth}{!}{
+%\begin{tabular}{|l|l|l|l|l|l|l|l|c|}
+\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|c|} % *** capital X or p{2cm}
+% p{2cm}
 \hline
@@
 \hline
-\end{tabular}
+\end{tabularx}
 }
@@
 \label{table:table1}
-\end{sidewaystable}
-%\end{table}
+
+%\end{sidewaystable}
+\end{table}
 
@@
 By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses.
-However, there are only 237 antibodies available so far. We found our 20 candidates are not included in the \acrshort{tcpa} database (v3.0\cite{Chen2019}).
+However, there are only 237 antibodies available so far. We found that our candidates are not included in the \acrshort{tcpa} database (v3.0\cite{Chen2019}) yet. %  USP-10 in HPA
 %> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))
 %validation at protein level:
-At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa}
-(available at https://www.proteinatlas.org/humanproteome/\newline
-pathology/head+and+neck+cancer, accessed 28 September 2020). The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+%At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteomepathology/head+and+neck+cancer, accessed 28 September 2020).
+The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
 % > semi_join(pvalueTex_good, HPA_good, by=c("V1"="Gene"))
 %There are 628 genes that consensus of pvalue005KM (6429 genes) and HPA (bad+good in HNSCC)
+%%%%%%%%%% modified discussion
+\begin{MyColorPar}{red}
+We utilized other approaches to validate our candidates.
+
+\subsubsection*{Analysis by web-tools}
+After discovering using our workflow, we also used the web-tools to find the evidence convincing up to 12 of our suggested 20 biomarkers in TCGA and GSE2837 cohort.
+%\subsubsection*{SurvExpress} % TCGA
+% 2021/01/23 pdf x 12 from SurvExpress
+SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
+Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
+1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);
+%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).
+%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635),
+The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort.
+Please see Supplementary Figure 1.
+%\ref{fig:fig_SurvExpress}.
+% moved to supplementary file
+
+% % SurvExpress 沒有類似的結果是因為:
+Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
+Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
+
+%\subsubsection{HPA} %still TCGA's RNA-Seq
+The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
+The HPA's Pathology Atlas analyzes each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
+Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
+All transcriptomics data has been retrieved from the Cancer Genome Atlas, and all proteomics data has been generated in-house using the same antibodies.
+Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+\\cancer)\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset 
+(Please see Supplementary Figure 2.) %\ref{fig:fig_HPA_USP10})
+% moved to Supplementary
+
+% Version: 3.0.2 Date: 2015/06/11 SurvNet
+%Preloaded TCGA  data is also available for analysis.
+%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
+%gene regulatory or protein interaction network
+% cited by 10 articles
+% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
+% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
+%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
+
+%\subsubsection*{GSE2837} % non-TCGA
+% from Anwser2-2
+%by GEO GSE2837 HNSCC dataset (PrognoScan)
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
+relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
+and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
+The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
+1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
+2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635), 
+Please see Supplementary figure 3.\\ %\ref{figure:fig_GSE2837}.
+Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
+%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
+%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
+The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
+
+\subsubsection*{Review articles}
+After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
+%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
+
+%%%%%% bad guy
+The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
+
+%STC2:
+The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
+
+% PGK1
+Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
+The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.
+
+%SURF4
+Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
+) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.
+SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
+%NIH/3T3 cells (Mus musculus, mouse), 293T cell
+%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
+%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
+%web-based tools survival (not TCGA?)
+
+% USP10
+Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
+Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
+https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
+
+%FOXA2
+Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
+FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
+%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
+%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
+% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
+%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
+Further, SIS analysis was performed to further screen out a stable probe combination.
+Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
+2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
+Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
+2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
+%Association between gene expression and methylation.
+Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
+Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
+
+% STIP1; non-TCGA
+Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
+in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. T
+The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
+%STIP1 could bind to bind Hsp70 and Hsp90.
+
+%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
+%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
+%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
+% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
+
+%%%%%% good guy
+%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
+%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
+%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
+%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
+
+%ZNF266, % or ZNF16, HZF1?
+%MYO1H associated mandibular prognathism\cite{Sun2018}
+
+% FCGBP
+% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
+Fc fragment of IgG binding protein (($Fc\gamma BP$, FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas.\cite{ODonovan2002}\cite{Griffith2006}
+%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
+%gene ID @gene@8857
+
+%?LOC148709?, 
+%EVPLL in cDNA project
+
+% PNMA5
+Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
+
+%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
+GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
+
+%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
+(PMID31598163)
+%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
+The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
+Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
+%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
+%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
+%\cite{Li2018b}
+%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
+%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+
+%NDFIP1:
+%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
+was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
+%MCF7 cells 
+%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
+%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
+%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
+Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
+We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
+hepatocellular carcinoma\cite{Zhang2019a}
+% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
+%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
+It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
+
+%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+%DKC1 is the tumor suppressor gene in HNSCC
+% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
+
+The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo."
+
+\end{MyColorPar} % marked as red
+
+%%%%%%%5%%%%% modified end
+
 Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.

### 2021-02-02 supplementary_figures.tex
Updates from Overleaf

--- 2021-01-02 main.tex
@@
-%  LaTeX support: latex@mdpi.com 
-%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
+\documentclass[preprint,12pt]{elsarticle}
 
-%=================================================================
-\documentclass[cancers,article,submit,moreauthors,pdftex]{Definitions/mdpi}
-\maxdeadcycles=300 % Output loop---200 consecutive dead cycles.
+% major revision and answer question (3 reviewers)
+%Sunday, January 24⋅22:30 – 22:55
+%Daily, until Jan 29, 2021
 
-% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
-The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
-This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
-For preprints.org, the editorial staff will make this change immediately prior to posting.
+\renewcommand{\figurename}{Supplementary Figure}
 
-%--------------------
-% Class Options:
-%--------------------
-%----------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, appliedchem, applmech, applmicrobiol, applnano, applsci, arts, asi, atmosphere, atoms, audiolres, automation, axioms, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomechanics, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, brainsci, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coatings, colloids, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, crops, cryptography, crystals, curroncol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forensicsci, forests, fractalfract, fuels, futureinternet, futuretransp, futurepharmacol, futurephys, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, land, languages, laws, life, liquids, literature, livers, logistics, lubricants, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, metabolites, metals, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, minerals, mining, modelling, molbank, molecules, mps, mti, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photochem, photonics, physchem, physics, physiolsci, plants, plasma, pollutants, polymers, polysaccharides, proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, systems, taxonomy, technologies, telecom, textiles, thermo, tourismhosp, toxics, toxins, transplantology, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wevj, women, world
+% mark in blue or red
+\usepackage{xcolor}
 
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
-% supfile = supplementary materials
+\newenvironment{MyColorPar}[1]{%
+    \leavevmode\color{#1}\ignorespaces%
+}{%
+}%
 
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
-\usepackage[]{caption} % bf
-\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
-
-%\usepackage[upplemac]{inputenc} %applemac support if unicode package fails
-%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
-%...
-%\usepackage{graphicx}
-%\DeclareGraphicsExtensions{.pdf,.png} % for high-resolution PDF image
-%\usepackage{hyperref}
-%\usepackage{url}
-
-\usepackage{array}
-\usepackage{ragged2e}
-\usepackage{rotating}
-% \usepackage{array}
-\usepackage{multirow}
-\usepackage{colortbl}
-\usepackage{hhline}
-\usepackage{siunitx} % for  1e-10 scientific notation
-%\usepackage{caption}
-%\usepackage{subcaption}
-\usepackage{booktabs, multirow} % for borders and merged ranges
-\usepackage{soul}% for underlines
-%\usepackage[table]{xcolor} % for cell colors
-\usepackage{changepage,threeparttable}
+\usepackage{outlines}
 
@@
 \usepackage[automake, acronym, nopostdot]{glossaries} 
-\usepackage{glossary-inline}
-%\setacronymstyle{long-short}
-%\renewcommand*{\glossarysection}[2][]{} 
-%\renewcommand*{\glossarysection}[2][]{\textbf{#1}: }
-% for abbreviations environment
-%\newcommand{\abbrlabel}[1]{\makebox[3cm][l]{\textbf{#1}\ \dotfill}}
-\newenvironment{abbreviation}%{\begin{list}{}{\renewcommand{\makelabel}{\abbrlabel}}}{\end{list}}
-% \newenvironment{<name>}[<number>][<default>]
-
+%\usepackage{glossary-inline}
+%\newenvironment{abbreviation}
 \makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
 \newacronym{fdr}{FDR}{false discovery rate}
-
 \newacronym{hpa}{HPA}{the Human Protein Atlas}
@@
 
-%=================================================================
-\firstpage{1} 
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother
-\pubvolume{1}
-\issuenum{1}
-\articlenumber{0}
-\pubyear{2021}
-\copyrightyear{2021}
-%\externaleditor{Academic Editor: Firstname Lastname}
-\datereceived{} 
-\dateaccepted{} 
-\datepublished{}
+%==================
+\begin{document}
+\underline{Supplementary information}
+% title and author
 
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
+Supplementary figure legends:
 
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+Supplementary figure 1\\
+The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
+Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
+Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.
 
-%=================================================================
-%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+Supplementary figure 2\\
+The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
+Over-expression of USP10 has poor prognosis on HNSCC.
 
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
+Supplementary figure 3\\
+GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as red; the better prognostic genes are marked as green.
 
-% MDPI internal command: Title for citation in the left column
-\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
+% SFigure 1, SurvExpress
 
-% Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-4476-2600} % Add \orcidA{} behind the author's name
-\newcommand{\orcidauthorB}{0000-0001-6497-4232} % Add \orcidB{} behind the author's name
-
-% Authors, for the paper (add full first names)
-\Author{
-Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
-Michael Hsiao $^{3}$*
-and Yu-Chuan (Jack) Li $^{1,4}$*\orcidB{}}
-%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
-
-% MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Li-Hsing Chi, Alexander TH Wu, Michael Hsiao and Yu-Chuan (Jack) Li}
-
-% MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Chi, LH.; Wu, ATH.; Hsiao, M.; Li, YCJ.}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
-    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
-$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
-    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
-$^{3}$ \quad Genomics Research Center\unskip, 
-    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
-$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
-}
-
-% Contact information of the corresponding author
-\corres{Correspondence: Hsiao: mhsiao@gate.sinica.edu.tw; Li: jaak88@gmail.com}
-%(optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
-
-% Current address and/or shared authorship
-%\firstnote{Current address: Affiliation 3} 
-%\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-% Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
-It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis.
-There is some optimization software for cutoff determination.
-However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses.
-There are few clinicopathological features available on their pre-processed data sets.
-We developed a comprehensive workflow that includes data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
-Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes.
-After adjustment with confounders and Bonferroni adjusted P-value, ten candidate biomarkers, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival.
-At the same time, the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
-We suggest this workflow could help for biomarker discovery.}
-
-% Keywords
-\keyword{Head and Neck Squamous Cell Carcinoma (HNSCC);
-%Genome Database\sep
-the Cancer Genome Atlas (TCGA);
-RNA-sequencing;
-Survival Analysis;
-Optimal Cutoff;
-%Biomarker\sep % Discovery\sep
-%Tumor Type-agnostic Therapy\sep
-%Immuno-Oncology\sep
-%Targeted Therapy\sep
-%Systemic Therapy\sep
-Surgical Margin}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-%\begin{paracol}{2}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\setcounter{section}{-1} %% Remove this when starting to work on the template.
-%\section{How to Use this Template}
-
-%The template details the sections that can be used in a manuscript.
-Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
-Please check the instructions on the authors' page of the journal to verify the correct order and names.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX-related questions please contact latex@mdpi.com.
-%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
-
-\section{Introduction}
-
-Head and neck squamous cell carcinoma (\acrshort{hnscc}), including oral, oropharyngeal, and hypopharyngeal origin, is the fourth leading cancer causes of death for males in Taiwan\cite{MOHW_death2017}.
-The age-standardized incidence rate of \acrshort{hnscc} in males is 42.43 per 100,000 persons\cite{MOHW_incidence2018}.
-% chemotherapy => systemic therapy
-The treatment strategies of \acrshort{hnscc} are surgery alone, systemic therapy with concurrent radiation therapy (systemic therapy/\acrshort{rt}), or surgery with adjuvant systemic therapy/\acrshort{rt} (according to \acrlong{nccn}, \acrshort{nccn} Clinical Practice Guidelines in \acrshort{hnscc}, Version 2.2020)\cite{Pfister2020a}.
-Despite the improvement in those interventions, the survival of \acrshort{hnscc} has improved only marginally over the past decade worldwide\cite{hpa2019}.
-The critical advancement of targeted therapy and immuno-oncology should benefit from emerging prognostic biomarkers, which guide the development of modern systemic therapy.
-
-%% TP53 gene => p53 protein; mutation of TP53
-Accumulative knowledge showed that some biomarkers have prognostic significance in \acrshort{hnscc}.
-For example, node-negative \acrshort{hnscc} patients with p53 overexpression were found to have lower survival\cite{DeVicente2004}.
-Overexpression of \acrfull{hif}-1 alpha\cite{Aebersold2001} or Ki-67\cite{Couture2002} was found to be correlated with poor response to radiotherapy of \acrshort{hnscc}.
-The \acrfull{egfr}\cite{O-Charoenrat2000}\cite{Bentzen2005} and \acrfull{mmp}\cite{Harrington2017} were found to be over-expressed to promote invasion and metastasis of \acrshort{hnscc}.
-From 2000 to 2006, the anti-\acrshort{egfr} antibody-drug (cetuximab) has been developed and combined with radiotherapy, known as bio-\acrshort{rt}, to increase survival of unresectable locoregionally advanced disease\cite{Bonner2006a}.
-The systemic therapy of cetuximab plus platinum-fluorouracil chemotherapy (EXTREME regimen) improves overall survival when given as first-line treatment in patients with recurrent or metastatic \acrshort{hnscc}\cite{Vermorken2008}\cite{Rivera2009}.
-It was approved by the \acrshort{us} \acrfull{fda} in 2008.
-In advance, the bio-\acrshort{rt} could have proceeded with \acrfull{tpf} induction chemotherapy to overcome the radio-resistance of \acrshort{hnscc}\cite{Blanchard2013}.
-
-However, Rampias and his colleagues suggested \acrfull{hras} mutations could mediate cetuximab resistance in systemic therapy of \acrshort{hnscc} via the \acrshort{egfr}/\acrfull{ras}/\acrfull{erk} signaling pathway\cite{Rampias2014}.
-After that, the \acrshort{egfr} \acrfull{tki} was introduced to help cetuximab in 2018.
-The anti-tumor activity was observed in a phase 1 trial for \acrshort{hnscc} patients using cetuximab and afatinib, a \acrshort{tki} of \acrshort{egfr}, \acrfull{her}2, and \acrshort{her}4\cite{Gazzah2018}.
-Other \acrshort{egfr} \acrshort{tki}, such as gefitinib, erlotinib, osimertinib, were also developed to treat advanced \acrshort{hnscc}.
-Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients.
-So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
-
-Until the immuno-oncology era, \acrfull{ici} was introduced since 2014 for treating \acrshort{hnscc}\cite{Seiwert2014}\cite{Swanson2015}.
-The \acrshort{ici} works on immune checkpoint molecules, which including \acrfull{pd1}, \acrfull{ctla4}, \acrfull{tim3}, \acrfull{lag3}, \acrfull{tigit}, \acrfull{gitr} and \acrfull{vista}\cite{Mei2020}.
-The \acrshort{us} \acrshort{fda} has approved the anti-\acrshort{pd1} agents, pembrolizumab, and nivolumab, as a monotherapy for the platinum-treated patients of recurrent or metastatic \acrshort{hnscc}\cite{Cramer2019}.
-However, because of the complexity of immune-tumor interaction, \acrshort{ici} has not to guarantee the response to \acrfull{pdl1} expressed \acrshort{hnscc}\cite{Swanson2015}.
-According to the phase 3 KEYNOTE-048 study, \acrshort{pdl1} is a validated biomarker used in clinical guidance for candidate selection of pembrolizumab\cite{Burtness2019}\cite{Gavrielatou2020}.
-
-In our previous proteomic study in 2017, \acrfull{tmsb4x} was reported to be related to tumor growth and metastasis of \acrshort{hnscc}\cite{Chi2017}.
-It was also found by the subsequent investigations that \acrshort{tmsb4x} engaged in tumor aggressiveness through \acrfull{emt} on pancreatic\cite{Zhang2008}, gastric\cite{Ryu2012}, colorectal\cite{Gemoll2015}, lung\cite{Huang2016}, ovarian\cite{Chu2019} and melanoma\cite{Makowiecka2019} cancers.
-Thus, it might be suggested that \acrshort{tmsb4x}  is possible for tumor type-agnostic therapy\cite{Yan2018} as a common biomarker crossing several types of cancer.
-%TMSB4X proteins regulate intracellular signal transduction and has been proved to overexpress in various cancers, including colorectal, lung, gastric, pancreatic, and squamous cell cancers.\cite{Chi2017}
-% https://doi.org/10.1038/s41598-017-09539-w
-
-In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
-However, there are three challenges of biomarker discovery from survival analysis, so far.
-Firstly, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, which over 50\% of the cohort, should be manually investigated and cleaned.
-Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
-Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type.
-They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
-SurvivaX.jsp, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort. After downloading the survival results, they could curate plots and tables carefully.
-It is not possible to scan the whole human protein-coding genome in this way.
-Third, we need to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage.
-The above mentioned online tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
-There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
-cutpointr), and cutoffR (available at https://cran.r-project.org/web/
-packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
-
-In our approach, this article described a comprehensive workflow implemented in the R script, which runs on the Rstudio server.
-Its functions include data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
-Using this workflow on the \acrshort{tcga} \acrshort{hnscc} cohort, the 20,500 human protein-coding genes were scanned. The analysis workflow is shown in Figure \ref{fig:figure1}.
-%We found that the surgical margin status and tobacco exposure are independent risk factors of patient survival. 
-%Our findings also suggested several candidate biomarkers are associated with the prognosis of overall survival (OS) under optimal cutoff point with significant P-value.
-Those genes may be potential therapeutic targets of HNSCC.
-
-%\subsubsection{Figure 1:h}
-\begin{figure}[hp]
-\centering
-\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
-%, height=8cm
-%\caption
-\bcaption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).}
-%Step 3 (purple line: dealing with surgical margin).
-{The "main procedure" includes data retrieving from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses.
-The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier P-value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with low [green] or high [red] expression of a specific gene, to yield a collection of P-values; please see Materials and Methods section for details).
-The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted P-value as well as a hazard ratio of Cox model, which was based on the results from the step 1.
-(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
-\label{fig:figure1}
+% red or green is NOT by expression level
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_3-1.pdf}
+\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization.
+%cumulative P-value plots).
+Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
+Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
+\label{fig:fig_SurvExpress}
 \end{figure}
-
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-
-The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
-By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
-At the final step, a Bonferroni P-value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
-The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
-%\subsubsection{Figure 3}
-while the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB (see Table \ref{table:table3}, with their full name of genes).
-We made a volcano plot for 9416 genes by Kaplan-Meier P-value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
-The plot revealed that the most significant (Bonferroni-adjusted P-value $< 0.05$) candidate genes are located above the dotted line.
-At the same time, Cox's HR separated them on the two-side with prognostic impact.
-
-%\subsubsection{Figure 2:h}
-\begin{figure}[hp]
-\centering
-\includegraphics[width=14cm]{Figure2.pdf}
-\bcaption{\acrshort{hnscc} Cox's hazard ratio and P-value plots.}
-{(a) Univariate HR versus uncorrected P-value; (b) Multivariate HR versus uncorrected P-value; (c) Univariate HR versus Bonferroni corrected P-value; and (d) Multivariate HR versus Bonferroni corrected P-value.}
-\label{fig:figure2}
-\end{figure}
-
-% tables 1  3
-%%% tables
-% Table1
-\begin{sidewaystable}[hp]
-\centering
-\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted P-value) }
-\arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
-\hline
-\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\
-\cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{P-value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\P-value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
-\hline
-DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                & **                                          \\
-\hline
-CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & **                                          \\
-\hline
-STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                & **                                          \\
-\hline
-PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & **                                          \\
-\hline
-SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & 3                                           \\
-\hline
-USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & **                                          \\
-\hline
-NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & 6                                           \\
-\hline
-FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & **                                          \\
-\hline
-STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                & **                                          \\
-\hline
-DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                & **                                          \\
-\hline
-\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
-\arrayrulecolor{black}\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted P-value $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
-\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: P-value $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
-\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: number of articles related with cancer research; ** as many~}                                                                                                                                                                                                                                                                                                                                                             \\
-\hline
-\end{tabular}
-}
-\arrayrulecolor{black}
-\label{table:table1}
-\end{sidewaystable}
-%\end{table}
-
-%\subsubsection{Table3/legend}
-%Table3. The 10 candidate genes over-expressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
-\begin{table}[hp]
-\centering
-\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected P-value) }
-\arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
-\hline
-\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
-\cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~P-value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
-\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} & 0                                             \\
-\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           & 1                                             \\
-\hline
-IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & 14                                            \\
-\hline
-MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           & 0                                             \\
-\hline
-FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           & **                                            \\
-\hline
-LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           & 1                                             \\
-\hline
-EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           & 0                                             \\
-\hline
-PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           & 5                                             \\
-\hline
-KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           & 0                                             \\
-\hline
-NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           & 4                                             \\
-\hline
-                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\
-\hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted P-value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: P-value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\
-\hline
-\end{tabular}
-}
-\arrayrulecolor{black}
-\label{table:table3}
-\end{table}
-
-%\subsubsection{Figure 3:h}
-\begin{figure}[hp]
-\centering
-\includegraphics[width=14cm]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
-\bcaption{Volcano plot of genes under survival analyses.}
-{X axis: unadjusted P-value of Kaplan-Meier survival (-log10 transformed).
-Y axis: multivariate hazard ratio from Cox proportional regression model.
-Dotted line: significant Bonferroni corrected P-value. 
-Red circles mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). Green circles mark 10 genes, which affect on better survival ($HR<=0.5$).}
-\label{fig:figure3}
-\end{figure}
-% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
-% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.
-
 \clearpage
 
-Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}(a)).
-The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
-In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted P-value as $0.001$).
-Figure \ref{fig:figure4}(b)'s cumulative P-value plot showed that the uncorrected 116 P-values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
-The smallest P-value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal P-value.
-Conversely, the most associated gene with better survival is \acrfull{ZNF557}.
-In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted P-value = $0.001$).
-The cutoff finding procedure (cutofFinder\_func.R) generated cumulative P-value plots in Figure \ref{fig:figure4}(d).
-There were 166 uncorrected P-values estimated by a serial cut from 125 to 290 for grouping the cohort.
-All was less than 0.05, and the smallest P-value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal P-value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
-%The second candidate, which improving patient survival, is ZNF266.
-%\subsubsection{Tables} in main article
+%%
 
-%\subsubsection{Figure 4:h}
-\begin{figure}[hp]
-\centering
-\includegraphics[width=15cm]{Figure4.pdf}
-\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
-{(a) Kaplan-Meier plot of DKK1 under optimal P-value, and (b) the cutoff was derived from cumulative P-value plots of DKK1.
-(c) Kaplan-Meier plot of ZNF557 under optimal P-value, and (d) the cutoff was derived from cumulative P-value plots of ZNF557.}
-\label{fig:figure4}
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_3-1_USP10.pdf}
+\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
+Overexpression of USP10 has poor prognosis on HNSCC.}
+\label{fig:fig_HPA_USP10}
 \end{figure}
-
 \clearpage
 
-Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier P-value.
-We found their Cox's univariate and multivariate HR are all greater than 1.837.
-There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
-In Table \ref{table:table2},
-after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, P-value $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, P-value = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, P-value = 0.004]).
-The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, P-value = 0.015]).
-The M stage could not be considered due to only 3 out of 414 patients which have distant metastasis.
+% from Answer2-2 GSE2837
 
-%\subsubsection{Table2/legend}
-%Table 2. Univariate/Multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in HNSCC.
-%(P-value Significant codes is denoted as  0.01 mark as *; 0.001 mark as **; if $<$0.001  mark as ***)
-\begin{table}[hp]
-\centering
-\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in \acrshort{hnscc}}
-\arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|} 
-\arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
-\cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\
-\arrayrulecolor{black}\hline
-\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}}  \\
-\cline{2-8}
-                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.178                                                                          & 0.841-1.650                                                                   & 0.342                                                                          \\
-\arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
-\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.462                                                                          & 1.078-1.983                                                                   & \textcolor{red}{0.015}                                                         \\
-\hline
-\multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 1.978                                                                          & 1.046-3.737                                                                   & \textcolor{red}{0.036}                                                         \\
-\hline
-\multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.149                                                                          & 0.805-1.640                                                                   & 0.445                                                                          \\
-\hline
-\multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor{red}{0.049}                                                        & 6.513                                                                          & 1.415-29.96                                                                   & \textcolor{red}{0.016}                                                         \\
-\hline
-\multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.597                                                                          & 0.277-1.287                                                                   & 0.188                                                                          \\
-\hline
-\multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.601                                                                          & 1.159-2.211                                                                   & \textcolor{red}{0.004}                                                         \\
-\hline
-\multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.302                                                                          & 0.943-1.797                                                                   & 0.109                                                                          \\
-\hline
-\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & High                                                                                & 2.266                                                                          & 1.666-3.082                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & 2.135                                                                          & 1.559-2.924                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                      \\
-\hline
-\multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
-\hline
-\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
-\hline
-\end{tabular}
-}
-\arrayrulecolor{black}
-\label{table:table2}
-\end{table}
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_2-2.pdf}
+\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
+\label{figure:fig_GSE2837}
+\end{figure}
+\clearpage
 
-There were also ten candidate genes over-expressed with a better prognosis of \acrshort{hnscc}, listed in Table \ref{table:table3}. Cox's univariate and multivariate HR is just under 0.5.
-In Table \ref{table:table4},
-after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, P-value = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, P-value = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, P-value = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, P-value $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.
-
-In overall results, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
-
-%\subsubsection{Table4/legend}
-\begin{table}[!hp]
-\centering
-\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of ZNF557 gene expression in \acrshort{hnscc}}
-\arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|} 
-\arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
-\cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\
-\arrayrulecolor{black}\hline
-\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}}  \\
-\cline{2-8}
-                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.163                                                                          & 0.833-1.625                                                                   & 0.375                                                                          \\
-\arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
-\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.328                                                                          & 0.976-1.808                                                                   & 0.071                                                                          \\
-\hline
-\multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor[rgb]{1,0.149,0}{0.033}                                             & 1.961                                                                          & 1.035-3.714                                                                   & \textcolor[rgb]{1,0.149,0}{0.039}                                              \\
-\hline
-\multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.179                                                                          & 0.824-1.686                                                                   & 0.367                                                                          \\
-\hline
-\multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor[rgb]{1,0.149,0}{0.049}                                             & 8.478                                                                          & 1.847-38.92                                                                   & \textcolor[rgb]{1,0.149,0}{0.006}                                              \\
-\hline
-\multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.512                                                                          & 0.239-1.096                                                                   & 0.085                                                                          \\
-\hline
-\multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor[rgb]{1,0.149,0}{0.004}                                             & 1.631                                                                          & 1.180-2.254                                                                   & \textcolor[rgb]{1,0.149,0}{0.003}                                              \\
-\hline
-\multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor[rgb]{1,0.149,0}{0.044}                                             & 1.453                                                                          & 1.055-2.000                                                                   & \textcolor[rgb]{1,0.149,0}{0.022}                                              \\
-\hline
-\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & High                                                                                & 0.465                                                                          & 0.348-0.619                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                          & 0.499                                                                          & 0.372-0.669                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                           \\
-\hline
-\multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
-\hline
-\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
-\hline
-\end{tabular}
-}
-\arrayrulecolor{black}
-\label{table:table4}
-\end{table}
-
-% end of result
-
-%Bulleted lists look like this:
-%\begin{itemize}
-%\item	First bullet;
-%\item	Second bullet;
-%\item	Third bullet.
-%\end{itemize}
-
-%Numbered lists can be added as follows:
-%\begin{enumerate}
-%\item	First item; 
-%\item	Second item;
-%\item	Third item.
-%\end{enumerate}
-
-%\subsection{Figures, Tables and Schemes}
-
-%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
-
-%\begin{figure}[H]
-%\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-%\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
-%\end{figure}
-
-% The MDPI table float is called specialtable
-%\begin{specialtable}[H] 
-%\caption{This is a table caption. Tables %should be placed in the main text near to %the first time they are~cited.\label{tab1}}
-%%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-%\begin{tabular}{ccc}
-%\toprule
-%\textbf{Title 1}	& \textbf{Title 2}	& %\textbf{Title 3}\\
-%\midrule
-%Entry 1		& Data			& Data\\
-%Entry 2		& Data			& Data\\
-%\bottomrule
-%\end{tabular}
-%\end{specialtable}
-
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
-
-%\subsection{Formatting of Mathematical Components}
-
-%This is the example 1 of equation:
-
-%\begin{equation}
-%a = 1,
-%\end{equation}
-
-%the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-\end{paracol}
-\nointerlineskip
-
-%\begin{equation}
-%a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-%\end{equation}
-
-% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
-
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-%Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-%\begin{Theorem}
-%Example text of a theorem.
-%\end{Theorem}
-
-%% Example of a proof:
-%\begin{proof}[Proof of Theorem 1]
-%Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-%\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-% TCGAbiolinks
-%alcohol consumption
-Besides ethnicity, age, gender, the \acrshort{tnm} stage, radiation therapy, chemotherapy, and targeted therapy, the comprehensive adverse features of prognosis in \acrshort{hnscc} should include tobacco exposure, \acrshort{egfr} amplification, \acrfull{hpv} status, positive/close surgical margin ($<5 mm$), \acrfull{ene}, \acrfull{lvsi}, \acrfull{pni}, \acrfull{doi} ($>5 mm$), as well as metastatic \acrfull{lnd}\cite{Cheraghlou2018}, and \acrfull{wpoi5}, which was defined as tumor dispersion $>= 1 mm$ between tumor satellites or positive \acrshort{pni}/\acrshort{lvsi}\cite{Amin2017}.
-The features of \acrshort{doi}, \acrshort{lnd}, and tumor dispersion were not available on the \acrshort{tcga} dataset.
-The Brandwein-Gensler's risk model (lymphocytic host response, \acrshort{wpoi5}, and \acrshort{pni})\cite{Brandwein-Gensler2010}\cite{Sinha2018} was suggested to be routinely performed on pathological examination.
-In previous reports of \acrshort{hnscc}, the loco-regional failure will be high when the initial frozen section has a positive/close surgical margin, and even the final margin revision revealed negative\cite{Bulbul2019b}.
-According to Table \ref{table:table2} and Table \ref{table:table4} in our study, the positive surgical margin yielded a hazard ratio greater than 1.6 to influence on patient's \acrshort{os}.
-It was suggested by authors \cite{Scholl1986}\cite{Sutton2003}\cite{Shaw2004}\cite{Guillemaud2010a}\cite{Patel2010}\cite{Kuriakose2017}\cite{Shapiro2017}\cite{Saidak2018}\cite{Miguelanez-Medran2019}\cite{Saidak2019} that the reason of positive/close surgical margin is possibly due to tumor aggressiveness or dispersion (WPOI-5) instead of iatrogenic reason of surgery.
-The surgical margin status is suggested as an independent surrogate for tumor dispersion, and important in the \acrshort{hnscc} study.
-Thus, in the current study, we selected the common clinicopathological features, including gender, age, clinical T, clinical N, clinical M, surgical margin status, and tobacco exposure in the biomarker discovery for adjustment of confounders (details description at Materials and Methods section).
-
-In our previous work, altered glucose metabolism (e.k.a.
-the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrfull{slc2a4} (or \acrfull{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}.
-In this study, LOC148709 (a \acrfull{lncrna}) was suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3}).
-%on page \pageref{table:table3}). I
-It was also found to has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
-
-There is a trend toward cancer type-agnostic study. The success of pembrolizumab and nivolumab was based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
-It showed a precedent of tumor type-agnostic therapy\cite{Yan2018}.
-%*** PD-L1/PD-L2 is a biomarker; Keynote-012
-Currently, there are several common biomarkers of \acrshort{ici} under evaluation, which include \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
-The other  \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019}\linebreak
-(ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (ClinicalTrials.gov Identifier: NCT04080804) studies.
-
-Although we combined the power of genome-wide scanning and an optimal cutoff finder for Kaplan-Meier survival analysis, the study has some limitations.
-We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
-The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excited the cancer research community\cite{Li2013c}\cite{Li2017b}.
-By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses.
-However, there are only 237 antibodies available so far. We found our 20 candidates are not included in the \acrshort{tcpa} database (v3.0\cite{Chen2019}).
-%> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))
-%validation at protein level:
-At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa}
-(available at https://www.proteinatlas.org/humanproteome/\newline
-pathology/head+and+neck+cancer, accessed 28 September 2020). The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
-% > semi_join(pvalueTex_good, HPA_good, by=c("V1"="Gene"))
-%There are 628 genes that consensus of pvalue005KM (6429 genes) and HPA (bad+good in HNSCC)
-Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
-% second limitation:
-In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers.
-However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
-Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
-It should be carefully curated to confirm the data integrity with the correct definition.
-We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R.
-The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}.
-Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods} % 4
-
-\subsection{Patient Cohort}
-
-The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available on a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
-%\cite{SeanDavis;MartinMorgan2020}
-GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
-\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
-Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
-The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
-FirebrowseR)\cite{Deng2017}. 
-We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, step 1) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
-
-\subsubsection{RNA Sequencing Data}
-
-The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}.
-The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
-\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
-The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
-It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
-We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].\newline
-Fire.Rda".
-After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
-We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
-We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
-
-\subsubsection{Clinical Data}
-
-We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
-Fire.Rda" (accessed November 2019).
-
-One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
-[GeneName].Fire.Rda" tables were transposed and merged by their \newline
-\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
-The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
-The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
-% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
-We made data clean by removing duplicated rows and columns.
-
-\subsection{Cutoff Finder Core Engine}
-
-%\label{key:cutoff}
-To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
-Our cutofFinder\_func subroutine employs the minimum P-value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
-First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
-Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort").
-The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier P-values for each gene.
-Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum P-value, was selected by the cutofFinder\_func subroutine.
-This iteration method could calculate all possible cutoff of each gene expression in this cohort.
-At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x.
-0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}).
-The optimal cutoff value and its correlated patient grouping size (e.x.
-low-expression in 262 persons vs.
-high-expression in 152 persons with gene \acrshort{CAMK2N1}) would be returned to the main program to allow downstream Cox survival analysis.
-The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
-In case there was no significant P-value, a median expression of this gene was set as its cutpoint as usual.
-
-\subsection{Statistical Consideration}
-
-Our workflow has loops to call function survival\_marginSFP(GeneName) with given GeneName to process the survival analysis gene by gene.
-We dichotomized the clinicopathological features, which includes gender (male/ female), age at diagnosed (below/beyond 65 year-old), clinical tumor size (T1-2/T3-4), clinical nodal status (negative/positive), clinical distant metastasis (negative/positive), TNM staging (early/late), surgical margin status (negative/positive) and tobacco exposure (low/high).
-The patients were grouped by an \acrshort{rnaseq} value of each gene, cut at low- or high-expression on an optimal P-value obtained from the cutofFinder\_func subroutine (see the section of "Cutoff Finder Core Engine").
-Pearson's chi-square test was used for these binary variables.
-Kaplan-Meier survival was analyzed using the log-rank test for two groups OS comparison.
-The Cox proportional hazards regression is the widely accepted approach for modeling survival while accounting for confounding factors\cite{Magen2019}.
-Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the OS.
-Results were considered statistically significant when a two-sided P-value $<$ 0.05, or a lower threshold if indicated.
-The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal P-value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
-%statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
-There were also multiple correlated tests of null hypotheses in the Kaplan-Meier family during our global scanning of protein-coding genes.
-The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
-%There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes.
-The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
-
-The resulting data, including Kaplan-Meier curves, cumulative P-value plots, and Cox regression tables, were exported to ".xlsx" and ".Rda" files (by R package "r2excel") for subsequent biomarker selection.
-
-\subsection{Biomarker Selection}
-
-Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
-Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
-
-%%%%%
-\section{Conclusions} % 5
-
-Our findings suggested 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni P-values and proper confounders control.
-They also might be potential common biomarkers for subsequent study.
-We wish this bioinformatics tool will be available for the broad usage of tumor-agnostic research\cite{Looney2020} to cross several \acrshort{tcga} diseases to make translational impacts.
-%Tex: PvalueTex
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Patents}
-
-%This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
-
-% Only for the journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{
-%For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``
-Conceptualization, Michael Hsiao; Funding acquisition, Yu-Chuan (Jack) Li; Methodology, Li-Hsing Chi; Resources, Alexander TH Wu; Software, Li-Hsing Chi; Supervision, Yu-Chuan (Jack) Li; Validation, Michael Hsiao; Writing - original draft, Li-Hsing Chi; Writing - review and editing, Alexander TH Wu.
-All authors have read and agreed to the published version of the manuscript.}
-%'' please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.
-
-\funding{The APC was funded by Taipei Medical University}
-
-\institutionalreview{Not applicable}
-
-\informedconsent{Not applicable}
-
-\dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
-%All the supplementary figures, tables, and R script codes 
-The R script codes and datasets generated during the current study are available in the GitHub repository, https://github.com/texchi2/pvalueTex.}
-
-\acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
-The tables were generated by latex code with the help from https://github.com/JDMCreator/\newline
-LaTeXTableEditor.
-We like to thank Dr. Wen-Chang Wang,
-%https://orcid.org/0000-0003-3124-2136
-College of Medical Science and Technology, Taipei Medical University, for bioinformatics consultation and helps. 
-We like to thank Sylvain Hall\'e, Department of Computer Science and Mathematics, Univerit\'e du Qu\'ebec \`a Chicoutimi, Canada, for latex technique help with his TeXtidote.
-%We also thank the statistical consultation and helps by Dr. Hsin-Chou Yang of the Institute of Statistical Science, Academia Sinica, Taipei, Taiwan.
-We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
-
-%\subsection*{Authors' information} % Author details (automatic placed here)
-
-% *** URL Accessed 20 May 2013.
-The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/\newline
-mtbwi/index.do. Accessed 20 May 2020.}
-
-\conflictsofinterest{The authors declare no conflict of interest.}
-
-%% Optional
-%\sampleavailability{Samples of the compounds ... are available from the authors.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\abbreviations{The following abbreviations are used in this manuscript:
-\noindent 
-\renewcommand*{\glsinlinenameformat}[2]{\glstarget{#1} {\textsc{#2}},}
-\printglossary[type=\acronymtype, title= , nonumberlist, style=inline]
-% Abbreviations
-
-%\begin{tabular}{@{}ll}
-%MDPI & Multidisciplinary Digital Publishing Institute\\
-%DOAJ & Directory of open access journals\\
-%TLA & Three letter acronym\\
-%LD & Linear dichroism
-%\end{tabular}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-%\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
-If the appendix sections contain a heading then change the argument to "yes".
-%\appendix
-%\section{}
-%\subsection{}
-%The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-%\section{}
-%All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{paracol}
-\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-\externalbibliography{yes}
-%\bibliography{your_external_BibTeX_file}
-%\bibliographystyle{model1-num-names}
+\bibliographystyle{unsrt} %model1-num-names}
 \bibliography{TCGA_margin_cutoff.bib}
 
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-%\begin{thebibliography}{999}
-% Reference 1
-%\bibitem[Author1(year)]{ref-journal}
-%Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-%\bibitem[Author2(year)]{ref-book1}
-%Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 8
-%\bibitem[Author8(year)]{ref-url}
-%Title of Site. Available online: URL (accessed on Day Month Year).
-%\end{thebibliography}
-
-% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
-For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}

### 2021-02-02 supplementary_figures.tex
revision1 done

@@
 
-\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\figurename}{Supplementary Figure S}
 
@@
 
+\begin{document}
+%%%%%%%%% title
+% Full title of the paper (Capitalized)
+%\Title{
+A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma
+
+% MDPI internal command: Title for citation in the left column
+%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
+
+% Author Orchid ID: enter ID or remove command
+%\newcommand{\orcidauthorA}{0000-0002-4476-2600} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0001-6497-4232} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+%\Author{
+Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
+Michael Hsiao $^{3}$*
+and Yu-Chuan (Jack) Li $^{1,4}$*%\orcidB{}
+%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
+
+% MDPI internal command: Authors, for metadata in PDF
+%\AuthorNames{Li-Hsing Chi, Alexander TH Wu, Michael Hsiao and Yu-Chuan (Jack) Li}
+
+% MDPI internal command: Authors, for citation in the left column
+%\AuthorCitation{Chi, LH.; Wu, ATH.; Hsiao, M.; Li, YCJ.}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+%\address{%
+
+$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
+    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
+$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
+    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
+$^{3}$ \quad Genomics Research Center\unskip, 
+    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
+$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
+
+% Contact information of the corresponding author
+%\corres{
+Correspondence: Hsiao: mhsiao@gate.sinica.edu.tw; Li: jaak88@gmail.com\\[1cm]
+%(optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
+
 %==================
-\begin{document}
-\underline{Supplementary information}
+
+%\underline{Supplementary information}
 % title and author
 
-Supplementary figure legends:
+\underline{Supplementary figure legends}\\[1cm]
 
-Supplementary figure 1\\
+Supplementary Figure S1\\
 The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
@@
 
-Supplementary figure 2\\
+Supplementary Figure S2\\
 The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
@@
 
-Supplementary figure 3\\
+Supplementary Figure S3\\
 GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
@@
 
-\bibliographystyle{unsrt} %model1-num-names}
-\bibliography{TCGA_margin_cutoff.bib}
+%\bibliographystyle{unsrt} %model1-num-names}
+%\bibliography{TCGA_margin_cutoff.bib}
 

### 2021-02-02 rebuttal_responses_revision1.tex
revision1 done
revision1 submitted (2021/02/02)

@@
 
-\section{Revision cover letter (cancers-1082127)} % 2021/01/25
+\section*{Cover letter for the revision (cancers-1082127)} % 2021/01/25
 %其實直接 online 填寫即可
@@
 We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.
-\\[0.7cm]
+%\\[0.4cm]
 Kind regards,
@@
 Graduate Institute of Biomedical Informatics, 
-
-College of Medical Science and Technology,
-
+College of Medical Science and Technology,\\
 Taipei Medical University,
@@
 
-\section{rebuttal} % Response2Referees
+\section*{Response to Reviewer 1 Comments}
+%Response to Referees} % rebuttal
 We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
@@
 %======
+\section*{Response to Reviewer 2 Comments}
+%Response to Referees} % rebuttal
+We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
+The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
+Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
 
@@
 
+\section*{Response to Reviewer 3 Comments}
+%Response to Referees} % rebuttal
+We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
+The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
+Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
+
 \subsection*{3-1}
@@
 The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort.
-Please see Supplementary Figure 1.
+Please see Supplementary Figure S1.
 %\ref{fig:fig_SurvExpress}.
@@
 %found at Human Protein Atlas dataset 
-(Please see Supplementary Figure 2.) %\ref{fig:fig_HPA_USP10})
+(Please see Supplementary Figure S2.) %\ref{fig:fig_HPA_USP10})
 % moved to Supplementary
@@
 %?DKK1 (0.253635), 
-Please see Supplementary figure 3. %\ref{figure:fig_GSE2837}.
+Please see Supplementary Figure S3. %\ref{figure:fig_GSE2837}.
 Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.

### 2021-02-02 main.tex
revision1 submitted (2021/02/02)

@@
 
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 %%%%%% revision1 added [TCGA] [2021/02/02]
@@
 
-\end{MyColorPar}
+%\end{MyColorPar}
 %%%%%% end of additional revision1
@@
 %%%%%%%%%% modified discussion
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 We utilized other approaches to validate our candidates.
@@
 %?DKK1 (0.253635), 
-Please see Supplementary figure 3.\\ %\ref{figure:fig_GSE2837}.
+Please see Supplementary Figure S3.\\ %\ref{figure:fig_GSE2837}.
 Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
@@
 
-\end{MyColorPar} % marked as red
+%\end{MyColorPar} % marked as red
 

### 2021-02-02 main_p10ectopic.tex
Updates from Overleaf

--- 2021-02-02 main.tex
@@
 
-\subsubsection*{Analysis by web-tools}
+\subsection*{Analysis by web-tools}
 After discovering using our workflow, we also used the web-tools to find the evidence convincing up to 12 of our suggested 20 biomarkers in TCGA and GSE2837 cohort.
@@
 %by GEO GSE2837 HNSCC dataset (PrognoScan)
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
 %??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
@@
 
-\subsubsection*{Review articles}
+%%%%%%%5%%%%% no ectopic error above %%%%%%%
+
+\subsection*{Review articles}
 After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
@@
 
+%%%
 %%%%%% bad guy
@@
 The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
-%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
-
-%STC2:
-The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
-
-% PGK1
-Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
-The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.
-
-%SURF4
-Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
-) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.
-SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
-%NIH/3T3 cells (Mus musculus, mouse), 293T cell
-%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
-%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
-%web-based tools survival (not TCGA?)
-
-% USP10
-Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
-Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
-https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
-
-%FOXA2
-Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
-FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
-%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
-%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
-% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
-%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
-Further, SIS analysis was performed to further screen out a stable probe combination.
-Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
-2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
-Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
-2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
-%Association between gene expression and methylation.
-Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
-Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
-
-% STIP1; non-TCGA
-Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
-in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. T
-The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
-%STIP1 could bind to bind Hsp70 and Hsp90.
-
-%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
-%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
-%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
-% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
-
-%%%%%% good guy
-%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
-%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
-%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
-%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
-
-%ZNF266, % or ZNF16, HZF1?
-%MYO1H associated mandibular prognathism\cite{Sun2018}
-
-% FCGBP
-% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
-Fc fragment of IgG binding protein (($Fc\gamma BP$, FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas.\cite{ODonovan2002}\cite{Griffith2006}
-%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
-%gene ID @gene@8857
-
-%?LOC148709?, 
-%EVPLL in cDNA project
-
+% try omit last sentence
+%Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+
+%==
+%..
+%==
 % PNMA5
-Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
-
-%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
-GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
-
-%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
-(PMID31598163)
-%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
-The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
-Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
-%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
-%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
-%\cite{Li2018b}
-%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
-%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
-
-%NDFIP1:
-%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
-was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
-%MCF7 cells 
-%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
-%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
-%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
-Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
-We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
-hepatocellular carcinoma\cite{Zhang2019a}
-% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
-%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
-It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
-
-%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
-%DKC1 is the tumor suppressor gene in HNSCC
-% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
-
-The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo."
+%Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
+
+%==
+The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
 
 %\end{MyColorPar} % marked as red
-
 %%%%%%%5%%%%% modified end
-
 Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\pagebreak
+
 \section{Materials and Methods} % 4
@@
 
-We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
-Fire.Rda" (accessed November 2019).
-
-One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
-[GeneName].Fire.Rda" tables were transposed and merged by their \newline
-\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
+We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.Fire.Rda" (accessed November 2019).
+
+One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.[GeneName].\\Fire.Rda" tables were transposed and merged by their \_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
 The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
@@
 \acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
-The tables were generated by latex code with the help from https://github.com/JDMCreator/\newline
-LaTeXTableEditor.
+The tables were generated by latex code with the help from https://github.com/JDMCreator/LaTeXTableEditor.
 We like to thank Dr. Wen-Chang Wang,
@@
 We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
+We also give our mercy to mice belonging to the Mouse Tumor Biology Database (http://tumor.informatics.jax.org/mtbwi/index.do. Accessed 20 May 2020)
+}
 
 %\subsection*{Authors' information} % Author details (automatic placed here)
-
-% *** URL Accessed 20 May 2013.
-The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/\newline
-mtbwi/index.do. Accessed 20 May 2020.}
 

### 2021-02-04 rebuttal2_responses_revision2.tex
2021-02-04 reviewer #3 comments

--- 2021-02-02 rebuttal_responses_revision1.tex
@@
 
+Round 1:
 %Must be improved:
@@
 There is little information provided. The authors should provide more evidence to support this article.
+
+Round 2:
+The authors still did not provide any experiment results that support the finding of the manuscript.
 %  Once the authors identify TMSB4X as a target, the rest of the analysis seems fine, but their rationale for looking into TMSB4X is not strongly supported by the available data.
@@
 
-We appreciate the reviewer for the critical comment. We provide more evidence mentioned below to support the prognostic impact of these candidate genes. We summarized the conclusion below.
+We appreciate the reviewer for the critical comment and apology for inadequate evidence provided. 
+We then did experiment for mRNA expression among HNSCC cell lysates to provide more evidence below to support our discovery of those candidate genes.
+We modified "Material and Methods" , Results and Discussion of manuscript according the new evidence.
+
+\subsubsection*{Material and Methods}
+Quantitative real-time PCR (qRT-PCR) analysis
+\subsectionmark*{qRT-PCR analysis}
+
+DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3].
+The primer sequences were as follows: DKK1 forward primer: 5'-TAGAGTCTAGAACGCAAGGATCT-3' and DKK1 reverse primer: 5'-CAAAAACTATCACAGCCTAAAGGG--3'; $\beta$-actin forward primer: 5'-TTGTTACAG GAAG TCCCTTGC C-3' and $\beta$-actin reverse primer: 5'-ATGCTATCACCTCCCC TGTGTG-3'.
+Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)].
+All experiments were performed in triplicate.\cite{Shi2014}
+
+\subsubsection*{Results}
+
+\subsubsection*{Discussion}
+
+\subsectionmark*{qPCR}
 
@@
 
-\subsubsection*{Analysis by web-tools}
+\subsubsubsection*{Analysis by web-tools}
 
@@
 
-\subsubsection*{Review articles}
+\subsubsubsection*{Review articles}
 After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
@@
 The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
-Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}. %quantitative real-time PCR and western blot analyses
 Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
@@
 
-% USP10
+% USP10 qPCR primer https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153
 Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
@@
 Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
-in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. T
+in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. 
 The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.

### 2021-02-07 revisionNotel2_responses.tex
revision note 2: rebuttal for reviewer #3

\documentclass[preprint,12pt]{elsarticle}
% major revision and answer question (3 reviewers)
%Sunday, January 24⋅22:30 – 22:55
%Daily, until Jan 29, 2021

% mark in blue or red
\usepackage{xcolor}

\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

\usepackage{outlines}

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{fdr}{FDR}{false discovery rate}
\newacronym{hpa}{HPA}{the Human Protein Atlas}
\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
\newacronym{rna}{RNA}{ribonucleic acid}
\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
\newacronym{lncrna}{lncRNA}{long non-coding RNA}
%\newacronym{km}{KM}{Kaplan-Meier}
\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}

\newacronym{mmp}{MMP}{matrix metalloproteinase}
 %DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1
 %ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683, and NPB

\newacronym{DKK1}{DKK1}{dickkopf WNT signaling pathway inhibitor 1} 
\newacronym{CAMK2N1}{CAMK2N1}{calcium/calmodulin dependent protein kinase II inhibitor 1} 
\newacronym{STC2}{STC2}{stanniocalcin 2} 
\newacronym{PGK1}{PGK1}{phosphoglycerate kinase 1} 
\newacronym{SURF4}{SURF4}{surfeit 4} 
\newacronym{USP10}{USP10}{ubiquitin specific peptidase 10} 
\newacronym{NEDD4}{NEDD4}{neural precursor cell expressed, developmentally down-regulated 4}
\newacronym{NDFIP1}{NDFIP1}{NEDD4 family interacting protein 1} 
\newacronym{FOXA2}{FOXA2}{forkhead box A2} 
\newacronym{STIP1}{STIP1}{stress-induced-phosphoprotein 1} 
\newacronym{DKC1}{DKC1}{dyskeratosis congenita 1, dyskerin}

\newacronym{ZNF557}{ZNF557}{zinc finger protein 557} 
\newacronym{ZNF266}{ZNF266}{zinc finger protein 266} 
\newacronym{IL19}{IL19}{interleukin 19} 
\newacronym{MYO1H}{MYO1H}{myosin 1H} 
\newacronym{FCGBP}{FCGBP}{Fc fragment of IgG binding protein} 
\newacronym{LOC148709}{LOC148709}{LncRNA LOC148709} 
\newacronym{EVPLL}{EVPLL}{envoplakin-like protein} 
\newacronym{PNMA5}{PNMA5}{paraneoplastic antigen like 5} 
%\newacronym{KIAA1683}{KIAA1683}{IQCN, IQ Motif Containing N} 
\newacronym{IQCN}{IQCN}{IQ motif containing N} % previous name KIAA1683
% "IQ" refers to the first two amino acids of the motif: isoleucine (commonly) and glutamine (invariably)
\newacronym{NPB}{NPB}{neuropeptide B}

 \newacronym{rt}{RT}{radiation therapy}
 \newacronym{nccn}{NCCN}{National Comprehensive Cancer Network}
 \newacronym{hif}{HIF}{hypoxia-inducible factor}
 \newacronym{egfr}{EGFR}{epidermal growth factor receptor}
 \newacronym{ras}{RAS}{rat sarcoma}
 \newacronym{hras}{HRAS}{Harvey rat sarcoma viral oncoprotein}
 \newacronym{erk}{ERK}{extracellular signal-regulated kinases}
 \newacronym{us}{US}{United States}
 \newacronym{fda}{FDA}{Food and Drug Administration}
 \newacronym{tpf}{Tax-PF}{docetaxel, cisplatin, and 5-fluorouracil}
 \newacronym{tki}{TKI}{tyrosine kinase inhibitor}
 \newacronym{her}{HER}{human epidermal growth factor receptor}
 \newacronym{ici}{ICI}{immune-checkpoint inhibitor}
 \newacronym{ctla4}{CTLA-4}{cytotoxic T lymphocyte antigen 4}
 \newacronym{pd1}{PD-1}{programmed death 1}
 \newacronym{pdl1}{PD-L1}{programmed death ligand 1}
 \newacronym{tim3}{TIM-3}{T-cell immunoglobulin mucin protein 3}
 \newacronym{lag3}{LAG-3}{lymphocyte activation gene 3}
 \newacronym{ifng}{IFN-$\gamma$}{interferon gamma}
 \newacronym{tigit}{TIGIT}{T cell immunoglobin and immunoreceptor tyrosine-based inhibitory motif}
 \newacronym{gitr}{GITR}{glucocorticoid-induced tumor necrosis factor receptor}
 \newacronym{vista}{VISTA}{V-domain Ig suppressor of T-cell activation}
 \newacronym{tmsb4x}{TMSB4X}{thymosin beta-4 X-linked}
 \newacronym{emt}{EMT}{epithelial-mesenchymal-transition}
 \newacronym{gdc}{GDC}{Genomic Data Commons}
 \newacronym{nci}{NCI}{the National Cancer Institute}
 \newacronym{gdac}{GDAC}{Genome Data Analysis Center}
 \newacronym{rest}{REST}{Representational State Transfer} 
 \newacronym{api}{API}{Application Programmable Interface}
\newacronym{grch38}{GRCh38}{Genome Reference Consortium Homo sapiens genome assembly 38}
\newacronym{fpkm}{FPKM}{Fragments per kilobase per million reads mapped}
\newacronym{rsem}{RSEM}{RNA-Seq by Expectation-Maximization}
\newacronym{slca}{SLC35E2A}{solute carrier family 35 member E2A}
\newacronym{slcb}{SLC35E2B}{solute carrier family 35 member E2B}
\newacronym{cde}{CDE}{Common Data Element}
\newacronym{id}{ID}{identification}
\newacronym{ajcc}{AJCC}{the American Joint Committee on Cancer}
\newacronym{uicc}{UICC}{he Union for International Cancer Control}
\newacronym{tnm}{TNM}{the tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M)}
\newacronym{ci95}{95\% CI}{95\% confidence interval}
\newacronym{os}{OS}{overall survival}
\newacronym{hr}{HR}{hazard ratio}
\newacronym{hpv}{HPV}{human papillomavirus}
\newacronym{ene}{ENE}{extra-nodal extension}
\newacronym{lvsi}{LVSI}{lymph-vascular space invasion}
\newacronym{pni}{PNI}{perineural invasion}
\newacronym{doi}{DOI}{depth of invasion}
\newacronym{lnd}{LND}{lymph node density}
\newacronym{wpoi5}{WPOI-5}{worst pattern of invasion score 5}
\newacronym{glut4}{GLUT4}{glucose transporters 4}
\newacronym{slc2a4}{SLC2A4}{solute carrier family 2 member A4}
\newacronym{trim24}{TRIM24}{tripartite motif-containing 24}
\newacronym{til}{TIL}{tumor-infiltrating lymphocytes}
\newacronym{tmb}{TMB}{tumor mutational burden}

%==================
\begin{document}

\section*{Cover letter for the revision (cancers-1082127)} % 2021/01/25
%其實直接 online 填寫即可
%Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript

%Assistant Editor
%E-Mail: aubree.zhu@mdpi.com
%MDPI Branch Office, Tianjin
Assistant Editor of Cancers%\newline

Feb 2, 2021

Dear Dr. Aubree Zhu:

Enclosed, please find our revised manuscript (cancers-1082127) entitled "A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Cancers. We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.

We have since performed the additional literature review and revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,

%{%
1) % {2-4}
"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
We re-wrote the Introduction in detail according to the suggestion by reviewer \#2. %(comment No 2-4).
%}

2) % {3-1}
"Are the conclusions supported by the results?
Only computer computing in this research to support 20 candidate biomarkers, ... are all heavily associated with the prognosis of OS.
There is little information provided. The authors should provide more evidence to support this article."\\
We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
According to the suggestion by reviewer \#3,
we re-wrote the Discussion with additional information, and
%}
%{% Answer_3-1_USP10.pdf, Answer_2-1.pdf
%According to the reviewers' comments, we 
added new supplementary Figure S1, S2, and S3 %, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
to provide more evidence from the significant literature review.
%}

According to the editor's comments, we have the manuscript checked for English grammar and reformatted Table 1 by rotating 90 degrees to portrait mode. %
We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.
%\\[0.4cm]
Kind regards,

Yu-Chuan (Jack) Li, M.D., Ph.D.

Graduate Institute of Biomedical Informatics, 
College of Medical Science and Technology,\\
Taipei Medical University,
Taipei, Taiwan

%2) [cancers-1082127_main_redMarked] 自動化 by latex: red marked on page xx line xx
%"Track Changes" function in latex => by latexdiff
%Some options, taken from the documentation, include:
%UNDERLINE—added text is wavy-underlined and blue, discarded text is struck out and red;
%CTRADITIONAL—added text is blue and set in sans-serif, and a red footnote is created for each discarded piece of text;
%TRADITIONAL—like CTRADITIONAL but without the use of colour;
%CFONT—added text is blue and set in sans-serif, and discarded text is red and very small size;
%FONTSTRIKE—added text is set in sans-serif, discarded text small and struck out;
%CHANGEBAR—added text is blue, and discarded text is red. Additionally, the changed text is marked with a bar in the margin.
%https://www.overleaf.com/learn/latex/Articles/Using_Latexdiff_For_Marking_Changes_To_Tex_Documents

\pagebreak

\section*{Response to Reviewer 1 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
%Reviewer #1(Technical Comments to the Author):
%   The ms investigates an interesting and timely topic. However, the discovery cohort involves a small sample size and throughout the analysis, the issue of correcting the obtained p-values for multiple comparisons is not addressed. Hence, the evidence for zooming into TMSB4X is not convincing.

%\section{Responses to Reviewers' comments}
% our responses to the reviewers' comments.
%***Response to reviewer's comments: [藍色字]

Comments from the reviewer \#1:

The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.

This is an attractive analysis method and I would like to know more details.

\subsection*{1-1}
It is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.
%[我的 candidate 中為什麼沒有 EGFR];  
In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
(please see https://github.com/texchi2/\linebreak
pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)

% transforming growth factor- (TGF-α) 
% epidermal growth factor receptor (EGFR)
As in our manuscript mentioned, 
In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}. Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}. So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
%citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
% a list from literature review, 留 下少於  50 articles mentioned candidates
%HNSCC_survivalAnalysis_marginS_EGFR.Rda
%HNSCC_survivalAnalysis_marginS_EGFR.xlsx
%https://github.com/texchi2/pvalueTex/blob/master/file20500_list.txt
%analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
\end{MyColorPar}

\subsection*{1-2}
DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for reminding the importance of DNA alteration in survival analysis.
Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation), 
epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
The usefulness of multi-omics data for the prediction of HNSCC outcome is expected.
%such as the (censored) survival time.
Moritz Herrmann et al.(2020) observed that using multi-omics and survival data can slightly improve prediction methods for particular datasets, such as TCGA HNSCC\cite{Herrmann2020}.
%It is limited that the utility of multi-omics data for prediction purposes in the considered TCGA studies\cite{Herrmann2020}.
%18 cancer datasets from The Cancer Genome Atlas (TCGA) 
According to their study, %the multi-omics structure have a slightly better prediction performance than naive (0.562 vs. 0.557 ) with favoring clinical variables leads to better prediction results for HNSCC. %likelihood-based boosting (CoxBoost and CoxBoost favoring)
% Exemplary t-tests comparing blockForest with CoxBoost favoring and the Clinical only model showed no significant differences in performance. 
% blockForest also offers the possibility of favoring clinical covariates using the argument always.select.block of the blockfor function
%Last but not the least, multi-omics data are structured: the variables are partitioned into (non overlapping) groups. 
% ***
the survival analysis of the TCGA HNSCC dataset by blockForest method (with multi-omics and clinical variables) has a similar prediction performance than Cox's model (with clinical variables alone). %from The Cancer Genome Atlas (TCGA) 
They also reported the performance C-index as 0.582 [CI: 0.554, 0.610] in blockForest method and 0.554 [CI: 0.519, 0.588] in Cox's model\cite{Herrmann2020}.

% 小心光茫太甚  Well-established prognostic clinical variables: prioritize
% the number of variables in the group of variables of TCGA HNSCC dataset:
% 11 clinical variables, 57964 CNV variables, 17248 mutation variables and 21520 RNA expression variables.
%*** Taking this structure into account can protect the predictive information that transcriptomics (e.x. RNA-Seq) or low-dimensional clinical variables might get lost within the huge amount of genomics (e.x. DNA mutation/amplification, copy number variation) data\cite{Boulesteix2011}\cite{Herrmann2020}.
DNA amplification will usually be one of the causes to overexpress the gene.
Moreover, transcriptomics study is helpful in drug discovery. For example, the overexpressed gene is possible to be a drug-targetable candidate\cite{Park2015}. After thoughtful validation in vitro/in vivo then pathway study, the EGFR inhibitory leads were constructed by antibody design or chemical compound screening\cite{Mahajan2016}. %比較容易研發 clinical and transcriptomics by ssurvival::survfit and urvival::coxph
% the selection of clinical features by domain knowledge and studies where HNSCC was under investigation.
The discovery of EGFR inhibitors\cite{Bonner2006a} for HNSCC therapy will encourage the research community to conduct the survival analysis under abnormality in gene expression.

% *** it needs deep learning, but less interpretability (yet under development\cite{Chaudhary2018}) (DNA+RNA and clinical dataset => multi-omics cancer study)
%high dimensional multi-omics analysis by deep learning 
%It may be beneficial to include these different data types in models predicting outcomes, such as the survival time of patients. Until recently, only data from a single omics type were used to build such prediction models, with or without the inclusion of standard clinical data [2]. In recent years, however, the increasing availability of different types of omics data measured for the same patients (called multi-omics data from now on) has led to their combined use for building outcome prediction models. An important characteristic of multi-omics data is the high-dimensionality of the datasets, which frequently have more than 10 000 or even 100 000 variables. This places particular demands on the methods used to build prediction models: they must be able to handle data where the number of variables by far exceeds the number of observations. Moreover, practitioners often prefer sparse and interpretable models containing only a few variables [3]. Last but not the least, multi-omics data are structured: the variables are partitioned into (nonoverlapping) groups. This structure may be taken into account when building prediction models.
%Citation: https://academic.oup.com/bib/advance-article/doi/10.1093/bib/bbaa167/5895463
%特別的 algorithm 
%however, interpretation and practical application of the model to the prediction of independent data are easier with regression-based methods yielding coefficients that reflect the effects of variables on the outcome than with machine learning algorithms [8].
%Multi-omics data, that is, datasets containing different types of high-dimensional molecular variables; they must be able to handle data where the number of variables by far exceeds the number of observations.
%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6419526/
%Deep learning
%SALMON (Survival Analysis Learning with Multi-Omics Neural Networks)

%\cite{Lawrence2015a} TCGA HNSCC %的第一篇文章已經分析過 DNA mutation of HNSCC
%Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature, 517(7536), 576–582. 
%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
%=> HNSCC marker paper\cite{Lawrence2015a}

%The presence of widespread genomic instability in HNSCC, such as cytogenetic aberrations, allelic imbalance/loss of heterozygosity, and microsatellite instability (MSI), suggests that there is an imperfection in the host DNA repair machinery. Genomic instability with progressive accumulation of detrimental genetic alterations appears to be dependent upon a circuitous interaction between the environmental genotoxic insults and the host DNA repair machinery, the functional integrity of which is governed by the proper cell cycle control and host DNA repair capacity. Genomics allows the identification of possibly relevant variants, such as single nucleotide polymorphisms (SNPs), copy number variation (CNV), mutations and translocations => %https://cancersheadneck.biomedcentral.com/articles/10.1186/s41199-020-0047-y
%DNA mutation: copy number burden (CNB) and tumor mutation burden (TMB) are important for predicting tumor progression (Marshall et al., 2017; Thomas et al., 2018)
% *** The Landscape of Somatic Copy Number Alterations in Head and Neck Squamous Cell Carcinoma, 2020. => 18 GEO dataset (873 patients from GEO) + TCGA: chromothripsis 6\%\cite{Yang2020}
%metaanalysis of NCBI GEO database (https://www.ncbi.nlm.nih.gov/geo/). We integrated the following datasets: TCGA-HNSCC, GSE11938, GSE20306, GSE20939, GSE23831, GSE25103, GSE31984, GSE33229, GSE33983, GSE34507, GSE36790, GSE39367, GSE40777,GSE47443, GSE51265, GSE57201, GSE66136, GSE68717, and GSE85514.

%TMB: To calculate TMB, you need to know the total size of the region sequenced. If data is from exome sequencing, you would find the size of the exome capture, and divide total mutations (or non-synonymous only depending on strategy), by that size (e.g. ~45MB) to get SNV/MB ratio.
%tumor mutational burden-high (TMB-H) [≥10 mutations/megabase (mut/Mb)] in solid tumors (criteria for pembrolizumab)
%Identification of Genomic Predictors for Treatment Response to Cancer Immunotherapy Using Omics Data Analysis (Yu-Chao Wang)
%=> ICIs criteria <- TMB <- DDR DNA repair gene
\end{MyColorPar}
\pagebreak
%======
\section*{Response to Reviewer 2 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

Comments from the reviewer \#2

How representative is the TCGA database for HNSCC?

Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?

Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?

Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.

%[找出其他 database cohort 的比較]
\subsection*{2-1}
How representative is the TCGA database for HNSCC?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the question allowing discussing TCGA in detail.\\
To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
When we queried from the Embase database using the MESH words "HNSCC AND TCGA," simple statistics show a total of 12,636 research articles/conference abstracts for HNSCC from 2008 to 2021, since the first TCGA article was published on 2008\cite{McLendon2008} by TCGA research network.
After that, there are 18,082 cross-cancer type articles produced using the TCGA database. The 778 publications (Figure \ref{figure:fig_embase}, b. 778) among them were focused on HNSCC research. Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time. Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008. %\ref{figure:fig_embase}
\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_2-1.pdf}
\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
\label{figure:fig_embase}
\end{figure}
\clearpage
%778/4350 = 17.9\% using TCGA data
%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
%http://www.actrec.gov.in/OCDB/index.htm

Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x. GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}. However, the MSKCC, Broad, and Johns Hopkins databases were processed through whole-exome sequencing instead of whole-genome sequencing in the TCGA database.

There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a} and Gene Expression Profiling Interactive Analysis (GEPIA, GEPIA2)\cite{Tang2019}. According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds). Furthermore, almost all of their survival data came from the TCGA database.
%GEO (few survival features, less than 100 participate in each GSE dataset)
%GSE31056, GSE2837 (Prognoscan)
%there is survival feature: A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).\cite{Lawrence2015a}
%datasets for each cancer type that include exactly the same prediction and outcome variables and consider comparable target populations. Currently, such data is simply not available.

%The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
%Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
%Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo. 
%Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
%DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
%The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.

For example, Wei et al.\cite{Wei2020} conducted the analysis of the prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
%GEPIA is a web-based tool that plots expression profiles of given genes (dataset from TCGA database)
They has suggested that overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}. %Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients. 
%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}

Conclusion: TCGA database is representative of HNSCC.

\end{MyColorPar}

\subsection*{2-2}
Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comment.
We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries
% VUMC, VAMC, UTMDACC (1992-2005)
relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635), 
Please see Figure \ref{figure:fig_GSE2837}.
Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using GSE2837 dataset other than the TCGA cohort.

\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{figure:fig_GSE2837}
\end{figure}
\clearpage
\end{MyColorPar}

\subsection*{2-3}
Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.

%how to apply or modify the R scripts to use on other datasets
%\begin{itemize} %summarize the elements of the workflow
\begin{outline}
The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x. data schema, table size, definition of features, number of features and their location on the table column).\\
In short, the elements of the workflow with the \{codes\} shows:\\
(please also see Figure \ref{fig:workflow})
\1 $[\# step 1 (main)]$
\{main\_marginSFP\_HNSCC.R\}
        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
%\1 $[\# step 1]$
    \2 \{TCGA\_HNSCC\_marginSFP.R\}
        \3 \underline{raw data cleaning}
        \3 \underline{data transformation and merge}
        \3 \underline{dichotomization of clinical features}
%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
        \3 survival analysis
            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
            \4 Cox modelling
\1 $[\# step 2]$
\{analysis\_export.R\}
    \2 analysis of the tables generated from \# step 1
    \2 candidate selection
%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
\end{outline}

%\begin{outline}
%\linebreak

%\1 $[\# step 1]$
%\{TCGA\_HNSCC\_marginSFP.R\}
%    \2 raw data cleaning
%    \2 data transformation and merge
%    \2 clinical features
%\end{itemize}
%\end{outline}

%to generalize the utility of our workflow:
%R scripts could be re-coded and applied to start a new analysis of dataset.
% *** R 的特色 邊分析解讀，一邊 coding
%Currently, less HNSCC dataset is available worldwide (Indian?) => 
%能否套用在別的 database，可以，需要標準化(fpkm or RSEM)
%It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
Moreover, we are planning to extend this workflow applied to other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
Then it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.

\begin{figure}
    \centering
    \includegraphics[width=14cm]{Figure_1_manuscript_workflow_modify.pdf}
    \caption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export). The portion of "data process/cleaning"(red rectangled) should be modified aggressively according to different sources of databases, e.x. The NCI's TCGA Genomic Data Commons (GDC) porting to Broad Firehose, or other databases.}
    \label{fig:workflow}
\end{figure}
%(other cancer types in the TCGA database). 
%TCGA HNSCC -> TCGA CRC, TCGA LUAD, TCGA BRCA cohorts -> GEO or other uploaded cancer cohort

% workflow from the manuscript ##########
%The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}. The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}). \acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
%The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}. It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
%We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].\newline
%Fire.Rda".
%After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities. We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500. We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.

%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
%Fire.Rda" (accessed November 2019).

%One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
%[GeneName].Fire.Rda" tables were transposed and merged by their \newline
%\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
%The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
%The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
%%We made data clean by removing duplicated rows and columns.

%\subsection{Cutoff Finder Core Engine}
%To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
%Our cutofFinder\_func subroutine employs the minimum P-value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
%First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene. Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort"). The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier P-values for each gene.
%Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum P-value, was selected by the cutofFinder\_func subroutine.
%This iteration method could calculate all possible cutoff of each gene expression in this cohort. At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x. 0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}). The optimal cutoff value and its correlated patient grouping size (e.x. low-expression in 262 persons vs. high-expression in 152 persons with gene \acrshort{CAMK2N1}) would be returned to the main program to allow downstream Cox survival analysis. The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
%In case there was no significant P-value, a median expression of this gene was set as its cutpoint as usual.

%\subsection{Biomarker Selection}

%Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
%Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).

% we plan to extend this workflow on other TCGA cancer types
%Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
% second limitation:
%In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers. However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope. Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen. It should be carefully curated to confirm the data integrity with the correct definition. We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R. The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}. Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
\end{MyColorPar}

% #####################
\subsection*{2-4}
Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors. (please also see Figure \ref{fig:workflow}, different sources of databases)

The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]
%(the revised portions in the manuscript are indicated in \textcolor{red}{red} since page 2 at line 77-129)

%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga
% adopted from materials and methods

%The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
%\cite{SeanDavis;MartinMorgan2020}

%\begin{MyColorPar}{red}

"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/\\organization/ccg/research/structural-genomics/tcga/studied-cancers).
%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.

TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen. Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.

The NCI's Genomic Data Commons (GDC, available at https://portal.\\gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs. The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}. The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research. %There is three categories of tools to approach the TCGA data from GDC.

GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools. Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and 
Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses. Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x. GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering). 
A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).

%Python and UNIX bindings
%R bindings
Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.

%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
% RESTful API

GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals. Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters. Moreover, if restricted data is requested, the user must provide a token along with the API call. This token can be downloaded directly from the GDC Portals. (courtesy of the National Cancer Institute)
Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.

% clinical
%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.

% to summarize the advantages of its use.
The highlights of the advantages of applying the TCGA data for cancer research include:
\begin{outline}
\1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far. The whole-genome sequencing data has been harmonized across all GDACs. The basic demographic data is usually available on many databases. However, TCGA data has more comprehensive features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data. It might be getting help quickly from the research community for trouble-shooting.
\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
\end{outline}"

%\end{MyColorPar}   % marked in red above

%The other GDAC, the MD Anderson GDAC's MBatch (http://bioinformatics.mdanderson.org/tcgabatcheffects) is a website that enables scientists to identify and quantify the batch effects accompanying TCGA data set, currently according to hierarchical clustering and enhanced PCA plots.

% RNA-Seq
%The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}). \acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
%The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}. It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.

\end{MyColorPar}
\pagebreak

\section*{Response to Reviewer 3 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
%Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

\subsection*{Comments from the reviewer \#3}

Round 1:
%Must be improved:
%Is the research design appropriate?
%Are the results clearly presented?
Are the conclusions supported by the results?

Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.

There is little information provided. The authors should provide more evidence to support this article.

Round 2:
The authors still did not provide any experiment results that support the finding of the manuscript.

\begin{MyColorPar}{blue}
Answer

\subsection*{Revision notes: rebuttal}  
%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
%in a respectful and considerate manner.
We appreciate the reviewer for the critical comment and apology for short of experiment results. 
%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
It is encouraged for multidisciplinary studies that use complementary computational and  experimental approaches to address challenging cancer research.
%下一篇文章的內容。目前在計畫中，但還沒有開始進行
These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
We plan to analysis on mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm expression of those candidate genes.
%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
The effect of over-expression and knockdown of gene by lenti-viral clones should be observed on cell function assay (e.x. proliferation, migration, and invasion) and mouse xenograft model (e.x. tumor growth). %這些都需要一年以上的時間
%their rationale for looking into TMSB4X is not strongly supported by the available data.

This bioinformatics paper is providing targets and hints for the in vitro and in vivo validation.
We open invitation of research community by strongly support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
We also aim to promote a reproducible research\cite{Preeyanon2014} with this workflow which will apply on their in-house HNSCC database to find more useful biomarkers. % or even other cancer types
why reproducibility?

Once those candidates are identified as the target, the compound screening could help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions

%The authors should provide a separate Revision Notes file for revisions. The file should include a point-by-point response to each reviewer's comments, which the authors have received alongside the initial decision letter from the handling editor. Revision notes should clearly state the revisions the authors made to the manuscript, preferably including the subdivision title and page/line numbers to indicate where the manuscript has been edited.

% rebuttal
%Reconsider after Major Revisions: 
%The acceptance of the manuscript would depend on the revisions. The author needs to provide a point by point response or provide a rebuttal if some of the reviewer’s comments cannot be revised.

%All reviewer comments should be responded to in a point-by-point fashion.

%usually, only one round of major revisions is allowed. Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.

\subsubsection*{Author Appeals for a rejection, in case}
%Authors may appeal a rejection by sending an e-mail to the Editorial Office of the journal. The appeal must provide a detailed justification, including point-by-point responses to the reviewers' and/or Editor's comments. The Managing Editor of the journal will forward the manuscript and related information (including the identities of the referees) to the Editor-in-Chief, Associate Editor, or Editorial Board member. The academic Editor being consulted will be asked to give an advisory recommendation on the manuscript and may recommend acceptance, further peer-review, or uphold the original rejection decision. A reject decision at this stage is final and cannot be reversed.

...

\subsection*{Material and Methods}

\subsubsection{Quantitative real-time PCR (qRT-PCR) analysis}
%\subsectionmark*{qRT-PCR analysis}

DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3]. The primer sequences were as follows: DKK1 forward primer: 5'-TAGAGTCTAGAACGCAAGGATCT-3' and DKK1 reverse primer: 5'-CAAAAACTATCACAGCCTAAAGGG--3'; $\beta$-actin forward primer: 5'-TTGTTACAG GAAG TCCCTTGC C-3' and $\beta$-actin reverse primer: 5'-ATGCTATCACCTCCCC TGTGTG-3'. Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)]. 
All experiments were performed in triplicate.\cite{Shi2014}

由 HNSCC cell lysate 測出 qRT-PCR，DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1 表現高；ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN and NPB 表現低？

然後我收集 7 genes 的 primer sequence pairs
做 qPCR 證明在 HNSCC 口腔癌 cell lysate 中是多的。當成回答問題：experiment prove our discovered 7 (out of 20 )genes 是值得繼續探索下去。

qRT-PCR and western blot analyses

DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3]. The primer sequences were as follows: DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCT C-3′ and DKK1 reverse primer: 5′-CAAAAAC TATCACAGCCTAAAGGG-3′; β-actin forward primer: 5′-TTGTTACAG GAAG TCCCTTGC C-3′and β-actin reverse primer: 5′-ATGCTATCACCTCCCC TGTGTG-3′. Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)]. All experiments were performed in triplicate.

qRT-PCR primer design: primer sequence of
DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCTC-3′
DKK1 reverse primer: 5′-CAAAAACTATCACAGCCTAAAGGG-3′

FaDu cells
STC2 forward primer: 5'-TGAAATGTAAGGCCCACGCT-3'
STC2 reverse primer: 5'-CGAGGTGCAGAAGCTCAAGA-3'

PGK1 (condition: 62dC, Ct 25)
PGK1 forward primer: 5'-CAAGAAGTGTGCTGAGGCTGTCAC-3'
PGK1 reverse primer: 5'-GCAGTGTCTCCACCACCTATGAT-3'

SURF4 forward primer: 5'-GAT CCC CTC AGC ACC TTC CTG GAG GAT TCA AGA GAT CCT CCA GGA AGG TGC-3'
SURF4  reverse primer: 5'-AGC TTT TCC AAA AAT CAG CAC CTT CCT GGA GGA TCT CTT GAA TTC TCC AGG AAG-3'

USP10
USP10  forward primer: 5'-AAATGCCACCGAACCTATCGGC-3'
USP10 reverse primer: 5'-CAGCCATTCAGACCGATCTGGA-3'
(https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153)

FOXA2
FOXA2 forward primer: 5'-GGAACACCACTACGCCTTCAAC-3'
FOXA2 reverse primer: 5'-AGTGCATCACCTGTTCGTAGGC-3'

STIP1
STIP1 forward primer: 5'-ATCCTCAGCGTCCTCTTGG‐3′
STIP1 reverse primer: 5'-GGTGGAGGTGTTGCAATCTCTT‐3′
(https://onlinelibrary.wiley.com/doi/full/10.1002/gcc.22136)\cite{Cho2014}

\subsection*{Results}

\subsection*{Discussion}

\begin{outline} % still blue
In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
Comparison with previous publications or database analyses,

\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort

\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using TCGA HNSCC cohort from \acrfull{hpa}. Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}

\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.

\1 The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.

\end{outline}

According to the reviewer's comment, the Discussion was modified accordingly. The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]
%(the revised portions in the manuscript are indicated in \textcolor{red}{red})

%\begin{MyColorPar}{red}

"We utilized other approaches to validate our candidates.

\subsubsubsection*{Analysis by web-tools}

%\subsubsection*{SurvExpress} % TCGA
% 2021/01/23 pdf x 12 from SurvExpress
SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data. Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);
%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).
%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635),
The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort. Please see Supplementary Figure S1. %\ref{fig:fig_SurvExpress}.
% moved to supplementary file

% % SurvExpress 沒有類似的結果是因為:
Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項

%\subsubsection{HPA} %still TCGA's RNA-Seq
The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins. The HPA's Pathology Atlas analyzes each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA. Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
All transcriptomics data has been retrieved from the Cancer Genome Atlas, and all proteomics data has been generated in-house using the same antibodies.
Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/\\pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19). The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/\\ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
%found at Human Protein Atlas dataset 
(Please see Supplementary Figure S2.) %\ref{fig:fig_HPA_USP10})
% moved to Supplementary

% Version: 3.0.2 Date: 2015/06/11 SurvNet
%Preloaded TCGA  data is also available for analysis.
%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}. %gene regulatory or protein interaction network
% cited by 10 articles
% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)

%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635), 
Please see Supplementary Figure S3. %\ref{figure:fig_GSE2837}.
Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.

\subsubsubsection*{Review articles}
After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
%PubTator Central\cite{Wei2019} is a useful Pubmed text miner

%%%%%% bad guy
The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}. %quantitative real-time PCR and western blot analyses
Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo. 
Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}. Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}. %Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients. 
%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)

%STC2:
The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}

% PGK1
Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.

%SURF4
Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression. SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
%NIH/3T3 cells (Mus musculus, mouse), 293T cell
%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
%web-based tools survival (not TCGA?)

% USP10 qPCR primer https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153
Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631. https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer

%FOXA2
Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05. Further, SIS analysis was performed to further screen out a stable probe combination. Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig. 2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively. Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig. 2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
%Association between gene expression and methylation. Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis). Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.

% STIP1; non-TCGA
Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. 
The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
%STIP1 could bind to bind Hsp70 and Hsp90.

%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60

%%%%%% good guy
%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}

%ZNF266, % or ZNF16, HZF1?
%MYO1H associated mandibular prognathism\cite{Sun2018}

% FCGBP
% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
Fc fragment of IgG binding protein (($Fc\gamma BP$, FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas.\cite{ODonovan2002}\cite{Griffith2006}
%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
%gene ID @gene@8857

%?LOC148709?, 
%EVPLL in cDNA project

% PNMA5
Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}

%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}. GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.

%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target. (PMID31598163)
%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression. The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC. Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
%\cite{Li2018b}
%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz

%NDFIP1:
%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}. was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
%MCF7 cells 
%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells. Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift. We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression. hepatocellular carcinoma\cite{Zhang2019a}
% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN. It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)

%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
%DKC1 is the tumor suppressor gene in HNSCC
% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).

The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo."

%\end{MyColorPar} % marked as red

\pagebreak

\end{MyColorPar}

% the end of response rebuttal

%\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
\bibliographystyle{unsrt} %model1-num-names}
\bibliography{TCGA_margin_cutoff.bib}

\end{document}

### 2021-02-07 revisonNote1_responses.tex
revision note 2: rebuttal for reviewer #3

--- 2021-02-07 revisionNotel2_responses.tex
@@
 The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
-%Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
+Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
 
-\subsection*{Comments from the reviewer \#3}
+\subsection*{3-1}
+Comments from the reviewer \#3
 
-Round 1:
 %Must be improved:
@@
 There is little information provided. The authors should provide more evidence to support this article.
-
-Round 2:
-The authors still did not provide any experiment results that support the finding of the manuscript.
+%  Once the authors identify TMSB4X as a target, the rest of the analysis seems fine, but their rationale for looking into TMSB4X is not strongly supported by the available data.
 
@@
 
-\subsection*{Revision notes: rebuttal}  
-%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
-%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
-% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
-%in a respectful and considerate manner.
-We appreciate the reviewer for the critical comment and apology for short of experiment results. 
-%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
-It is encouraged for multidisciplinary studies that use complementary computational and  experimental approaches to address challenging cancer research.
-%下一篇文章的內容。目前在計畫中，但還沒有開始進行
-These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
-We plan to analysis on mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm expression of those candidate genes.
-%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
-The effect of over-expression and knockdown of gene by lenti-viral clones should be observed on cell function assay (e.x.
-proliferation, migration, and invasion) and mouse xenograft model (e.x.
-tumor growth).
-%這些都需要一年以上的時間
-%their rationale for looking into TMSB4X is not strongly supported by the available data.
-
-This bioinformatics paper is providing targets and hints for the in vitro and in vivo validation.
-We open invitation of research community by strongly support their rationale for looking into these HNSCC candidates.
-%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
-%the rest of the analysis seems fine, but 
-%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
-We also aim to promote a reproducible research\cite{Preeyanon2014} with this workflow which will apply on their in-house HNSCC database to find more useful biomarkers. % or even other cancer types
-why reproducibility?
-
-Once those candidates are identified as the target, the compound screening could help to discover a potential drug for HNSCC therapy.
-%https://www.mdpi.com/journal/cancers/instructions
-
-%The authors should provide a separate Revision Notes file for revisions.
-The file should include a point-by-point response to each reviewer's comments, which the authors have received alongside the initial decision letter from the handling editor.
-Revision notes should clearly state the revisions the authors made to the manuscript, preferably including the subdivision title and page/line numbers to indicate where the manuscript has been edited.
-
-% rebuttal
-%Reconsider after Major Revisions: 
-%The acceptance of the manuscript would depend on the revisions. The author needs to provide a point by point response or provide a rebuttal if some of the reviewer’s comments cannot be revised.
-
-%All reviewer comments should be responded to in a point-by-point fashion.
-
-%usually, only one round of major revisions is allowed.
-Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.
-
-\subsubsection*{Author Appeals for a rejection, in case}
-%Authors may appeal a rejection by sending an e-mail to the Editorial Office of the journal.
-The appeal must provide a detailed justification, including point-by-point responses to the reviewers' and/or Editor's comments.
-The Managing Editor of the journal will forward the manuscript and related information (including the identities of the referees) to the Editor-in-Chief, Associate Editor, or Editorial Board member.
-The academic Editor being consulted will be asked to give an advisory recommendation on the manuscript and may recommend acceptance, further peer-review, or uphold the original rejection decision.
-A reject decision at this stage is final and cannot be reversed.
-
-...
-
-\subsection*{Material and Methods}
-
-\subsubsection{Quantitative real-time PCR (qRT-PCR) analysis}
-%\subsectionmark*{qRT-PCR analysis}
-
-DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3].
-The primer sequences were as follows: DKK1 forward primer: 5'-TAGAGTCTAGAACGCAAGGATCT-3' and DKK1 reverse primer: 5'-CAAAAACTATCACAGCCTAAAGGG--3'; $\beta$-actin forward primer: 5'-TTGTTACAG GAAG TCCCTTGC C-3' and $\beta$-actin reverse primer: 5'-ATGCTATCACCTCCCC TGTGTG-3'.
-Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)].
-All experiments were performed in triplicate.\cite{Shi2014}
-
-由 HNSCC cell lysate 測出 qRT-PCR，DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1 表現高；ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN and NPB 表現低？
-
-然後我收集 7 genes 的 primer sequence pairs
-做 qPCR 證明在 HNSCC 口腔癌 cell lysate 中是多的。當成回答問題：experiment prove our discovered 7 (out of 20 )genes 是值得繼續探索下去。
-
-qRT-PCR and western blot analyses
-
-DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3].
-The primer sequences were as follows: DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCT C-3′ and DKK1 reverse primer: 5′-CAAAAAC TATCACAGCCTAAAGGG-3′; β-actin forward primer: 5′-TTGTTACAG GAAG TCCCTTGC C-3′and β-actin reverse primer: 5′-ATGCTATCACCTCCCC TGTGTG-3′.
-Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)].
-All experiments were performed in triplicate.
-
-qRT-PCR primer design: primer sequence of
-DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCTC-3′
-DKK1 reverse primer: 5′-CAAAAACTATCACAGCCTAAAGGG-3′
-
-FaDu cells
-STC2 forward primer: 5'-TGAAATGTAAGGCCCACGCT-3'
-STC2 reverse primer: 5'-CGAGGTGCAGAAGCTCAAGA-3'
-
-PGK1 (condition: 62dC, Ct 25)
-PGK1 forward primer: 5'-CAAGAAGTGTGCTGAGGCTGTCAC-3'
-PGK1 reverse primer: 5'-GCAGTGTCTCCACCACCTATGAT-3'
-
-SURF4 forward primer: 5'-GAT CCC CTC AGC ACC TTC CTG GAG GAT TCA AGA GAT CCT CCA GGA AGG TGC-3'
-SURF4  reverse primer: 5'-AGC TTT TCC AAA AAT CAG CAC CTT CCT GGA GGA TCT CTT GAA TTC TCC AGG AAG-3'
-
-USP10
-USP10  forward primer: 5'-AAATGCCACCGAACCTATCGGC-3'
-USP10 reverse primer: 5'-CAGCCATTCAGACCGATCTGGA-3'
-(https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153)
-
-FOXA2
-FOXA2 forward primer: 5'-GGAACACCACTACGCCTTCAAC-3'
-FOXA2 reverse primer: 5'-AGTGCATCACCTGTTCGTAGGC-3'
-
-STIP1
-STIP1 forward primer: 5'-ATCCTCAGCGTCCTCTTGG‐3′
-STIP1 reverse primer: 5'-GGTGGAGGTGTTGCAATCTCTT‐3′
-(https://onlinelibrary.wiley.com/doi/full/10.1002/gcc.22136)\cite{Cho2014}
-
-\subsection*{Results}
-
-\subsection*{Discussion}
+We appreciate the reviewer for the critical comment. We provide more evidence mentioned below to support the prognostic impact of these candidate genes. We summarized the conclusion below.
 
@@
 
-\subsubsubsection*{Analysis by web-tools}
+\subsubsection*{Analysis by web-tools}
 
@@
 
-\subsubsubsection*{Review articles}
+\subsubsection*{Review articles}
 After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.

### 2021-02-08 revisionNotel2_responses.tex
rebuttal for reviewer #3 (round 1 2)

@@
 
-This bioinformatics paper is providing targets and hints for the in vitro and in vivo validation.
-We open invitation of research community by strongly support their rationale for looking into these HNSCC candidates.
+% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
+Moreover, this bioinformatics paper is providing targets and supporting community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
+%Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
+%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
 %邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
@@
 %文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
-We also aim to promote a reproducible research\cite{Preeyanon2014} with this workflow which will apply on their in-house HNSCC database to find more useful biomarkers. % or even other cancer types
-why reproducibility?
-
-Once those candidates are identified as the target, the compound screening could help to discover a potential drug for HNSCC therapy.
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset.
+% to find more useful biomarkers.
+% or even other cancer types
+% to allow successful repetition and extension of analyses based on original data
+A good practice of research reproducibility is necessary in order to allow %previously developed methodology to be effectively applied on new data, or to allow 
+reuse of code and results for new projects. %In other words, good habits of reproducibility
+It may actually turn out to be a time-saver in the longer run.
+When a result can be reproduced by multiple scientists, it will also validate our original results and readiness to progress to the next phase of research. 
+%why reproducibility?
+%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows.
+Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
+%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
+
+Once those candidates are identified by Alex's laboratory (or community) as the targets, the compound screening could facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
+%help to discover a potential drug for HNSCC therapy.
 %https://www.mdpi.com/journal/cancers/instructions
@@
 Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.
+\pagebreak
 

### 2021-02-08 revisionNotel2_responses.tex
grammerly checked

@@
 These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
-We plan to analysis on mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm expression of those candidate genes.
+We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
 %mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
-The effect of over-expression and knockdown of gene by lenti-viral clones should be observed on cell function assay (e.x.
+The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x.
 proliferation, migration, and invasion) and mouse xenograft model (e.x.
@@
 % 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
-Moreover, this bioinformatics paper is providing targets and supporting community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
+Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
 %Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
@@
 % to allow successful repetition and extension of analyses based on original data
-A good practice of research reproducibility is necessary in order to allow %previously developed methodology to be effectively applied on new data, or to allow 
-reuse of code and results for new projects. %In other words, good habits of reproducibility
-It may actually turn out to be a time-saver in the longer run.
-When a result can be reproduced by multiple scientists, it will also validate our original results and readiness to progress to the next phase of research. 
+A good practice of research reproducibility is necessary to allow the reuse of code and results for new projects.
+%previously developed methodology to be effectively applied on new data, or to allow 
+%reuse of code and results for new projects. %In other words, good habits of reproducibility
+It may turn out to be a time-saver in the longer run.
+When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
 %why reproducibility?
@@
 
-Once those candidates are identified by Alex's laboratory (or community) as the targets, the compound screening could facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
+Once Alex's laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis.
 %help to discover a potential drug for HNSCC therapy.

### 2021-02-09 revisionNotel2_responses.tex
Alex’s approval: done (our laboratory)

@@
 %下一篇文章的內容。目前在計畫中，但還沒有開始進行
-These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
+These in vitro and in vivo validation experiments will be undertaken in our laboratory.
 We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
@@
 
-Once Alex's laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis.
+Once our laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis.
 %help to discover a potential drug for HNSCC therapy.

### 2021-02-11 main_Cancers.tex
rename as JPM

--- 2021-02-02 main.tex
@@
 
-\subsubsection*{Review articles}
+\subsection*{Review articles}
 After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.

### 2021-02-14 main.tex
graphic abstract loaded

@@
 %=================================================================
-\documentclass[cancers,article,submit,moreauthors,pdftex]{Definitions/mdpi}
-\maxdeadcycles=300 % Output loop---200 consecutive dead cycles.
+% Journal of Personalized Medicine, JPM
+\documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi}
+\maxdeadcycles=500 % Output loop---200 consecutive dead cycles.
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
+\abstract{
+The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
 It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis.
@@
 At the same time, the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
-We suggest this workflow could help for biomarker discovery.}
+We suggest this workflow could help for biomarker discovery.
+}
 
 % Keywords
-\keyword{Head and Neck Squamous Cell Carcinoma (HNSCC);
+\keyword{
+Head and Neck Squamous Cell Carcinoma (HNSCC);
 %Genome Database\sep
@@
 %Systemic Therapy\sep
-Surgical Margin}
-
+%Surgical Margin
+}
+
+% I have a graphic abstract: graphic_abstract_pvalueTex.pdf
+% National Cancer Institute.
+Changing the dressing on a patient’s neck.
+https://unsplash.com/photos/IrqLPsxemQ4?utm_source=unsplash&utm_medium=referral&utm_content=creditShareLink (1950).\cite{nci1950}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
+%%
+
+\begin{figure}
+    \centering
+    \includegraphics[width=14cm]{graphic_abstract_pvalueTex.pdf}
+    \caption{(inset image courtesy of National Cancer Institute\cite{nci1950})}
+    \label{fig:my_label}
+\end{figure}
 
@@
 This token can be downloaded directly from the GDC Portals.
-(courtesy of the National Cancer Institute)
+(paragraph is provided here courtesy of the National Cancer Institute)
+% Articles from Cureus are provided here courtesy of Cureus Inc.
 Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
@@
 %For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``
-Conceptualization, Michael Hsiao; Funding acquisition, Yu-Chuan (Jack) Li; Methodology, Li-Hsing Chi; Resources, Alexander TH Wu; Software, Li-Hsing Chi; Supervision, Yu-Chuan (Jack) Li; Validation, Michael Hsiao; Writing - original draft, Li-Hsing Chi; Writing - review and editing, Alexander TH Wu.
+%Conceptualization, Michael Hsiao; Funding acquisition, Yu-Chuan (Jack) Li; Methodology, Li-Hsing Chi; Resources, Alexander TH Wu; Software, Li-Hsing Chi; Supervision, Yu-Chuan (Jack) Li; Validation, Michael Hsiao; Writing - original draft, Li-Hsing Chi; Writing - review and editing, Alexander TH Wu.
+Conceptualization, Yu-Chuan (Jack) Li; Data curation, Alexander TH Wu; Formal analysis, Li-Hsing Chi; Investigation, Michael Hsiao; Methodology, Michael Hsiao; Resources, Alexander TH Wu; Software, Li-Hsing Chi and Yu-Chuan (Jack) Li; Supervision, Michael Hsiao and Yu-Chuan (Jack) Li; Writing – original draft, Li-Hsing Chi; Writing – review and editing, Alexander TH Wu.
 All authors have read and agreed to the published version of the manuscript.}
@@
 %\bibliographystyle{model1-num-names}
-\bibliography{TCGA_margin_cutoff.bib}
+\bibliography{TCGA_margin_cutoff.bib, Holistic.bib}
 

### 2021-02-14 main.tex
before \textit{P} value

@@
 \abstract{
-The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
-It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis.
+The survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
+It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression.
 There is some optimization software for cutoff determination.
-However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses.
-There are few clinicopathological features available on their pre-processed data sets.
-We developed a comprehensive workflow that includes data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
-Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes.
-After adjustment with confounders and Bonferroni adjusted P-value, ten candidate biomarkers, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival.
-At the same time, the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
+However, that software's predetermined cutoffs have been set at the median or quantiles of RNA sequencing value to perform the survival analysis.
+%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
+We developed a comprehensive workflow to perform biomarker discovery.
+It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
+Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected P-value.
+The result showed that ten over-expressed genes (named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) 
+are significantly associated with a poor prognosis of overall survival. 
+Furthermore, the other ten over-expressed genes (named ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former name as KIAA1683, and NPB) are correlated with better survival.
 We suggest this workflow could help for biomarker discovery.
@@
 
+\subsection{holistic}
+TCGA 都是手術後？TNM available yes
+discussion: limitation
+the TCGA has not collected holistic features
+癌症與身心靈的重要關係：中醫、citation?
+repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
+自他不二
+心存正念
+1.衷心懺悔
+2.真心感謝
+3.誠意祝福
+4.永存善念
+5.心無恐懼: 情志養生
+
+祝福全世界
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-02-14 main.tex
Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.

@@
 \abstract{
-The survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
+Survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
 It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression.
-There is some optimization software for cutoff determination.
-However, that software's predetermined cutoffs have been set at the median or quantiles of RNA sequencing value to perform the survival analysis.
+Usually, an optimization algorithm for cutoff determination has been set at the median or quantiles of RNA sequencing value.
 %There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
@@
 It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
-Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected P-value.
+Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected \textit{P} value.
 The result showed that ten over-expressed genes (named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) 
@@
 Furthermore, the other ten over-expressed genes (named ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former name as KIAA1683, and NPB) are correlated with better survival.
-We suggest this workflow could help for biomarker discovery.
+We suggest this workflow equipped with a cutoff-mining engine could help for biomarker discovery.
 }
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=14cm]{graphic_abstract_pvalueTex.pdf}
-    \caption{(inset image courtesy of National Cancer Institute\cite{nci1950})}
-    \label{fig:my_label}
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=14cm]{graphic_abstract_pvalueTex.pdf}
+%    \caption{(inset image courtesy of National Cancer Institute\cite{nci1950})}
+%    \label{fig:my_label}
+%\end{figure}
 
@@
 Despite the improvement in those interventions, the survival of \acrshort{hnscc} has improved only marginally over the past decade worldwide\cite{hpa2019}.
-The critical advancement of targeted therapy and immuno-oncology should benefit from emerging prognostic biomarkers, which guide the development of modern systemic therapy.
+The critical advancement of targeted therapy and immuno-oncology should benefit from emerging prognostic  biomarkers guiding modern systemic therapy.
+
+%latex https://www.latex-tutorial.com/symbols/greek-alphabet/
+\subsection*{Linear regression in biomarker discovery}
+Linear regression is useful as a concept in biomarker discovery.
+A linear regression equation that relates a Y-variable to n X-variables is written as%\\[1cm]
+\par
+%Highlights
+% https://quicklatex.com
+\begin{flushleft}
+% equation
+%\begin{math}
+
+ground truth Y (e.x. patient's survival):\\[0.5cm]
+%Y$:\\[0.3cm]
+$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
+\linebreak
+\linebreak
+Input $X_1...n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
+\\[0.5cm]
+Coefficients $\beta_0...n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)\\[0.5cm]
+A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
+Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
+$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
+\linebreak
+%(predicted Y, output) intercept, slope, independent (input) \Times
+%\end{math}
+\end{flushleft}
+Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.
 
@@
 
+\subsection{A introduction of TCGA}
 %\begin{MyColorPar}{red}
@@
 \1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
+There are many $X_1 ... X_n$ physical and social features of patients available for survival modelling.
 The whole-genome sequencing data has been harmonized across all GDACs.
@@
 {The "main procedure" includes data retrieving from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses.
-The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier P-value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with low [green] or high [red] expression of a specific gene, to yield a collection of P-values; please see Materials and Methods section for details).
-The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted P-value as well as a hazard ratio of Cox model, which was based on the results from the step 1.
+The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with low [green] or high [red] expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details).
+The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, which was based on the results from the step 1.
 (HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
@@
 The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
-By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
-At the final step, a Bonferroni P-value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
+By uncorrected \textit{P} value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
+At the final step, a Bonferroni \textit{P} value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
 The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
@@
 while the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB (see Table \ref{table:table3}, with their full name of genes).
-We made a volcano plot for 9416 genes by Kaplan-Meier P-value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
-The plot revealed that the most significant (Bonferroni-adjusted P-value $< 0.05$) candidate genes are located above the dotted line.
+We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
+The plot revealed that the most significant (Bonferroni-adjusted \textit{P} $< 0.05$) candidate genes are located above the dotted line.
 At the same time, Cox's HR separated them on the two-side with prognostic impact.
@@
 \includegraphics[width=14cm]{Figure2.pdf}
-\bcaption{\acrshort{hnscc} Cox's hazard ratio and P-value plots.}
-{(a) Univariate HR versus uncorrected P-value; (b) Multivariate HR versus uncorrected P-value; (c) Univariate HR versus Bonferroni corrected P-value; and (d) Multivariate HR versus Bonferroni corrected P-value.}
+\bcaption{\acrshort{hnscc} Cox's hazard ratio and \textit{P} value plot.}
+{(a) Univariate HR versus uncorrected \textit{P} value; (b) Multivariate HR versus uncorrected \textit{P} value; (c) Univariate HR versus Bonferroni corrected \textit{P} value; and (d) Multivariate HR versus Bonferroni corrected \textit{P} value.}
 \label{fig:figure2}
@@
 \centering
-\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted P-value) }
+\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 \cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{P-value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\P-value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\textit{P} value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
 \hline
@@
 \arrayrulecolor{black}\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted P-value $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
-\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: P-value $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
+\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
+\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: \textit{P} $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
 \hline
@@
 \centering
-\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected P-value) }
+\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 \cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~P-value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
 \cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
@@
 \hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted P-value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: P-value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: \textit{P} value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\
 \hline
@@
 \bcaption{Volcano plot of genes under survival analyses.}
-{X axis: unadjusted P-value of Kaplan-Meier survival (-log10 transformed).
+{X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
 Y axis: multivariate hazard ratio from Cox proportional regression model.
-Dotted line: significant Bonferroni corrected P-value. 
+Dotted line: significant Bonferroni corrected \textit{P} value. 
 Red circles mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). Green circles mark 10 genes, which affect on better survival ($HR<=0.5$).}
@@
 The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
-In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted P-value as $0.001$).
-Figure \ref{fig:figure4}(b)'s cumulative P-value plot showed that the uncorrected 116 P-values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
-The smallest P-value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal P-value.
+In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted \textit{P} = $0.001$).
+Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot showed that the uncorrected 116 \textit{P} values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
+The smallest \textit{P} value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal \textit{P} value.
 Conversely, the most associated gene with better survival is \acrfull{ZNF557}.
-In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted P-value = $0.001$).
-The cutoff finding procedure (cutofFinder\_func.R) generated cumulative P-value plots in Figure \ref{fig:figure4}(d).
-There were 166 uncorrected P-values estimated by a serial cut from 125 to 290 for grouping the cohort.
-All was less than 0.05, and the smallest P-value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal P-value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
+In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted \textit{P} = $0.001$).
+The cutoff finding procedure (cutofFinder\_func.R) generated cumulative \textit{P} value plots in Figure \ref{fig:figure4}(d).
+There were 166 uncorrected \textit{P} values estimated by a serial cut from 125 to 290 for grouping the cohort.
+All was less than 0.05, and the smallest \textit{P} value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal \textit{P} value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
 %The second candidate, which improving patient survival, is ZNF266.
@@
 \bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
-{(a) Kaplan-Meier plot of DKK1 under optimal P-value, and (b) the cutoff was derived from cumulative P-value plots of DKK1.
-(c) Kaplan-Meier plot of ZNF557 under optimal P-value, and (d) the cutoff was derived from cumulative P-value plots of ZNF557.}
+{(a) Kaplan-Meier plot of DKK1 under optimal \textit{P} value, and (b) the cutoff was derived from cumulative \textit{P} value plot of DKK1.
+(c) Kaplan-Meier plot of ZNF557 under optimal \textit{P} value, and (d) the cutoff was derived from cumulative \textit{P} value plot of ZNF557.}
 \label{fig:figure4}
@@
 
-Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier P-value.
+Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value.
 We found their Cox's univariate and multivariate HR are all greater than 1.837.
@@
 In Table \ref{table:table2},
-after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, P-value $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, P-value = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, P-value = 0.004]).
-The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, P-value = 0.015]).
+after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
+The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, \textit{P} = 0.015]).
 The M stage could not be considered due to only 3 out of 414 patients which have distant metastasis.
@@
 \cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\
+\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                              \\
 \arrayrulecolor{black}\hline
@@
 \hline
-\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\multicolumn{8}{|l|}{(\textit{P} value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
 \hline
@@
 In Table \ref{table:table4},
-after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, P-value = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, P-value = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, P-value = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, P-value $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.
+after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.
 
@@
 %\begin{MyColorPar}{red}
+
+\subsection{our lab}
+It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
+%下一篇文章的內容。目前在計畫中，但還沒有開始進行
+These in vitro and in vivo validation experiments will be undertaken in our laboratory.
+We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
+%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
+The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x.
+proliferation, migration, and invasion) and mouse xenograft model (e.x.
+tumor growth).
+%這些都需要一年以上的時間
+%their rationale for looking into TMSB4X is not strongly supported by the available data.
+
+% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
+Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
+%Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
+%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
+%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
+%the rest of the analysis seems fine, but 
+%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset.
+% to find more useful biomarkers.
+% or even other cancer types
+% to allow successful repetition and extension of analyses based on original data
+A good practice of research reproducibility is necessary to allow the reuse of code and results for new projects.
+%previously developed methodology to be effectively applied on new data, or to allow 
+%reuse of code and results for new projects. %In other words, good habits of reproducibility
+It may turn out to be a time-saver in the longer run.
+When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
+%why reproducibility?
+%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows.
+Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
+%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
+
+Once our laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis.
+
 We utilized other approaches to validate our candidates.
@@
 SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
-Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
+Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
 1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);
@@
 Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
-%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
+%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
 
@@
 and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
-The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
+The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
 1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
@@
 
-\subsection{holistic}
-TCGA 都是手術後？TNM available yes
+\subsection{Holistic health care}
+TCGA treated by surgery and more; TNM available yes
 discussion: limitation
+Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
 the TCGA has not collected holistic features
-癌症與身心靈的重要關係：中醫、citation?
+%癌症與身心靈的重要關係：中醫、citation?
+中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
 repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
-自他不二
-心存正念
-1.衷心懺悔
-2.真心感謝
-3.誠意祝福
-4.永存善念
-5.心無恐懼: 情志養生
-
-祝福全世界
+%自他不二 心存正念
+%1.衷心懺悔
+%2.真心感謝
+%3.誠意祝福
+%4.永存善念
+%5.心無恐懼: 情志養生
+
+Wish and bless the whole world
 
@@
 To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
-Our cutofFinder\_func subroutine employs the minimum P-value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
+Our cutofFinder\_func subroutine employs the minimum \textit{P} value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
 First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
 Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort").
-The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier P-values for each gene.
-Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum P-value, was selected by the cutofFinder\_func subroutine.
+The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier \textit{P} values for each gene.
+Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum \textit{P} value, was selected by the cutofFinder\_func subroutine.
 This iteration method could calculate all possible cutoff of each gene expression in this cohort.
@@
 The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
-In case there was no significant P-value, a median expression of this gene was set as its cutpoint as usual.
+In case there was no significant \textit{P} value, a median expression of this gene was set as its cutpoint as usual.
 
@@
 We dichotomized the clinicopathological features, which includes gender (male/ female), age at diagnosed (below/beyond 65 year-old), clinical tumor size (T1-2/T3-4), clinical nodal status (negative/positive), clinical distant metastasis (negative/positive), TNM staging (early/late), surgical margin status (negative/positive) and tobacco exposure (low/high).
-The patients were grouped by an \acrshort{rnaseq} value of each gene, cut at low- or high-expression on an optimal P-value obtained from the cutofFinder\_func subroutine (see the section of "Cutoff Finder Core Engine").
+The patients were grouped by an \acrshort{rnaseq} value of each gene, cut at low- or high-expression on an optimal \textit{P} value obtained from the cutofFinder\_func subroutine (see the section of "Cutoff Finder Core Engine").
 Pearson's chi-square test was used for these binary variables.
@@
 Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the OS.
-Results were considered statistically significant when a two-sided P-value $<$ 0.05, or a lower threshold if indicated.
-The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal P-value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
+Results were considered statistically significant when a two-sided \textit{P} $<$ 0.05, or a lower threshold if indicated.
+The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal \textit{P} value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
 %statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
 There were also multiple correlated tests of null hypotheses in the Kaplan-Meier family during our global scanning of protein-coding genes.
-The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
+The stringent Bonferroni correction could result in an adjusted \textit{P} value to ensure the control for type I error.
 %There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes.
@@
 
-The resulting data, including Kaplan-Meier curves, cumulative P-value plots, and Cox regression tables, were exported to ".xlsx" and ".Rda" files (by R package "r2excel") for subsequent biomarker selection.
+The resulting data, including Kaplan-Meier curves, cumulative \textit{P} value plots, and Cox regression tables, were exported to ".xlsx" and ".Rda" files (by R package "r2excel") for subsequent biomarker selection.
 
@@
 Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
-Bonferroni adjusted (Kaplan-Meier) P-value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
+Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
 
@@
 
-Our findings suggested 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni P-values and proper confounders control.
+Our findings suggested 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni \textit{P} values and proper confounders control.
 They also might be potential common biomarkers for subsequent study.

### 2021-02-14 main.tex
introduction is done

@@
 \makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
+
+\newacronym{ihc}{IHC}{immunohistochemistry}
 \newacronym{fdr}{FDR}{false discovery rate}
@@
 Accumulative knowledge showed that some biomarkers have prognostic significance in \acrshort{hnscc}.
-For example, node-negative \acrshort{hnscc} patients with p53 overexpression were found to have lower survival\cite{DeVicente2004}.
+For example, node-negative \acrshort{hnscc} patients with p53 overexpression were found to hold lower survival\cite{DeVicente2004}.
 Overexpression of \acrfull{hif}-1 alpha\cite{Aebersold2001} or Ki-67\cite{Couture2002} was found to be correlated with poor response to radiotherapy of \acrshort{hnscc}.
 The \acrfull{egfr}\cite{O-Charoenrat2000}\cite{Bentzen2005} and \acrfull{mmp}\cite{Harrington2017} were found to be over-expressed to promote invasion and metastasis of \acrshort{hnscc}.
-From 2000 to 2006, the anti-\acrshort{egfr} antibody-drug (cetuximab) has been developed and combined with radiotherapy, known as bio-\acrshort{rt}, to increase survival of unresectable locoregionally advanced disease\cite{Bonner2006a}.
-The systemic therapy of cetuximab plus platinum-fluorouracil chemotherapy (EXTREME regimen) improves overall survival when given as first-line treatment in patients with recurrent or metastatic \acrshort{hnscc}\cite{Vermorken2008}\cite{Rivera2009}.
-It was approved by the \acrshort{us} \acrfull{fda} in 2008.
-In advance, the bio-\acrshort{rt} could have proceeded with \acrfull{tpf} induction chemotherapy to overcome the radio-resistance of \acrshort{hnscc}\cite{Blanchard2013}.
-
-However, Rampias and his colleagues suggested \acrfull{hras} mutations could mediate cetuximab resistance in systemic therapy of \acrshort{hnscc} via the \acrshort{egfr}/\acrfull{ras}/\acrfull{erk} signaling pathway\cite{Rampias2014}.
+From 2000 to 2006, the first anti-\acrshort{egfr} antibody-drug (cetuximab) has been developed and combined with radiotherapy, known as bio-\acrshort{rt}, to increase survival of unresectable locoregionally advanced disease\cite{Bonner2006a}.
+The systemic therapy of cetuximab plus platinum-fluorouracil chemotherapy (EXTREME regimen) has improved overall survival when given as first-line treatment in patients with recurrent or metastatic \acrshort{hnscc}\cite{Vermorken2008}\cite{Rivera2009}.
+It has been approved by the \acrshort{us} \acrfull{fda} since 2008.
+In advance, the bio-\acrshort{rt} could be proceeded with \acrfull{tpf} induction chemotherapy to overcome  radio-resistance of \acrshort{hnscc}\cite{Blanchard2013}.
+
+However, Rampias and his colleagues\cite{Rampias2014} suggested that \acrfull{hras} mutations could mediate cetuximab resistance in systemic therapy of \acrshort{hnscc} via the \acrshort{egfr}/\acrfull{ras}/\acrfull{erk} signaling pathway.
 After that, the \acrshort{egfr} \acrfull{tki} was introduced to help cetuximab in 2018.
 The anti-tumor activity was observed in a phase 1 trial for \acrshort{hnscc} patients using cetuximab and afatinib, a \acrshort{tki} of \acrshort{egfr}, \acrfull{her}2, and \acrshort{her}4\cite{Gazzah2018}.
-Other \acrshort{egfr} \acrshort{tki}, such as gefitinib, erlotinib, osimertinib, were also developed to treat advanced \acrshort{hnscc}.
+Other \acrshort{egfr} \acrshort{tki}s, such as gefitinib, erlotinib, osimertinib, were also developed to treat advanced \acrshort{hnscc}.
 Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients.
-So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
+So far, cetuximab is still the only drug of choice with proven efficacy, which has targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
 
 Until the immuno-oncology era, \acrfull{ici} was introduced since 2014 for treating \acrshort{hnscc}\cite{Seiwert2014}\cite{Swanson2015}.
-The \acrshort{ici} works on immune checkpoint molecules, which including \acrfull{pd1}, \acrfull{ctla4}, \acrfull{tim3}, \acrfull{lag3}, \acrfull{tigit}, \acrfull{gitr} and \acrfull{vista}\cite{Mei2020}.
-The \acrshort{us} \acrshort{fda} has approved the anti-\acrshort{pd1} agents, pembrolizumab, and nivolumab, as a monotherapy for the platinum-treated patients of recurrent or metastatic \acrshort{hnscc}\cite{Cramer2019}.
-However, because of the complexity of immune-tumor interaction, \acrshort{ici} has not to guarantee the response to \acrfull{pdl1} expressed \acrshort{hnscc}\cite{Swanson2015}.
+The \acrshort{ici} works on immune checkpoint molecules, including \acrfull{pd1}, \acrfull{ctla4}, \acrfull{tim3}, \acrfull{lag3}, \acrfull{tigit}, \acrfull{gitr}, and \acrfull{vista}\cite{Mei2020}.
+The \acrshort{us} \acrshort{fda} has approved the anti-\acrshort{pd1} agents (e.g.
+pembrolizumab and nivolumab) as a monotherapy for the platinum-treated patients with recurrent or metastatic \acrshort{hnscc}\cite{Cramer2019}.
 According to the phase 3 KEYNOTE-048 study, \acrshort{pdl1} is a validated biomarker used in clinical guidance for candidate selection of pembrolizumab\cite{Burtness2019}\cite{Gavrielatou2020}.
-
-In our previous proteomic study in 2017, \acrfull{tmsb4x} was reported to be related to tumor growth and metastasis of \acrshort{hnscc}\cite{Chi2017}.
-It was also found by the subsequent investigations that \acrshort{tmsb4x} engaged in tumor aggressiveness through \acrfull{emt} on pancreatic\cite{Zhang2008}, gastric\cite{Ryu2012}, colorectal\cite{Gemoll2015}, lung\cite{Huang2016}, ovarian\cite{Chu2019} and melanoma\cite{Makowiecka2019} cancers.
-Thus, it might be suggested that \acrshort{tmsb4x}  is possible for tumor type-agnostic therapy\cite{Yan2018} as a common biomarker crossing several types of cancer.
+However, because of the complexity of immune-tumor interaction, \acrshort{ici} has 20\% response rate to \acrfull{pdl1} expressed patients (over 50\% in \acrlong{ihc}, \acrshort{ihc} staining of \acrshort{hnscc})\cite{Swanson2015}\cite{Gavrielatou2020}.
+
+According to our proteomic study between 2010 to 2017, \acrfull{tmsb4x} was reported to be related to tumor growth and metastasis of \acrshort{hnscc}\cite{Chi2017}.
+It was also reported by the subsequent investigations that \acrshort{tmsb4x} has engaged in tumor aggressiveness through \acrfull{emt} on pancreatic\cite{Zhang2008}, gastric\cite{Ryu2012}, colorectal\cite{Gemoll2015}, lung\cite{Huang2016}, ovarian\cite{Chu2019}, and melanoma\cite{Makowiecka2019} cancers.
+Thus, it might be suggested that \acrshort{tmsb4x}  is a candidate for tumor type-agnostic therapy\cite{Yan2018} as a common biomarker crossing several types of cancer.
 %TMSB4X proteins regulate intracellular signal transduction and has been proved to overexpress in various cancers, including colorectal, lung, gastric, pancreatic, and squamous cell cancers.\cite{Chi2017}
@@
 %%%%%% revision1 added [TCGA] [2021/02/02]
-The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
+A large-scale cancer database, aggregating many $X_1 ... X_n$ features, is necessary to facilitate the biomarker discovery.
+The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} has been developed since 2005 and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government.
 TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
@@
 
-The NCI's Genomic Data Commons (GDC, available at https://portal.\\gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
+The NCI's Genomic Data Commons (GDC, available at https://portal.gdc.cancer.gov) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
 The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
@@
 %The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
-\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research. %There is three categories of tools to approach the TCGA data from GDC.
-GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools.
-Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and
+\acrshort{tcga}, GDC and some research communities offer several computational tools to the public for facilitating cancer research.
+%There is three categories of tools to approach the TCGA data from GDC.
+GDC Data Portal is the official web-based TCGA data analysis tools. Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and 
 Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
@@
 % to summarize the advantages of its use.
-The highlights of the advantages of applying the TCGA data for cancer research include:
+The highlights of the advantages of applying the TCGA data for cancer biomarker identification include:
 \begin{outline}
-\1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
-There are many $X_1 ... X_n$ physical and social features of patients available for survival modelling.
+\1  To the best of our knowledge, the TCGA database is the largest collection (in both cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
+There are many physical and social features ($X_1 ... X_n$) of patients available for survival modeling.
 The whole-genome sequencing data has been harmonized across all GDACs.
-The basic demographic data is usually available on many databases.
-However, TCGA data has more comprehensive features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
+Many databases adopt the essential demographic data from TCGA since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
 \1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data.
@@
 %%%%%% end of additional revision1
-
+\par
 In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
-However, there are three challenges of biomarker discovery from survival analysis, so far.
-Firstly, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, which over 50\% of the cohort, should be manually investigated and cleaned.
+However, there are three challenges of biomarker discovery from survival analysis.
+First, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
 Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
@@
 They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
-SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort.
+SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.x.
+\acrshort{tcga}).
 After downloading the survival results, they could curate plots and tables carefully.
 It is not possible to scan the whole human protein-coding genome in this way.
-Third, we need to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage.
-The above mentioned online tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
+Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+The above mentioned web-tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
 There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
@@
 
-In our approach, this article described a comprehensive workflow implemented in the R script, which runs on the Rstudio server.
-Its functions include data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
-Using this workflow on the \acrshort{tcga} \acrshort{hnscc} cohort, the 20,500 human protein-coding genes were scanned. The analysis workflow is shown in Figure \ref{fig:figure1}.
+Our approach describes a comprehensive workflow implemented in the R script, which runs on the Rstudio server.
+Its function includes data retrieval, data pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
+The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.
+
 %We found that the surgical margin status and tobacco exposure are independent risk factors of patient survival. 
@@
 The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
-The HPA's Pathology Atlas analyzes each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
+The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA.
 Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
@@
 Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
+ since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
 the TCGA has not collected holistic features

### 2021-02-14 main.tex
updated Figure 1

@@
 %\caption
-\bcaption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).}
+\bcaption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (\textcolor{blue}{blue line}: main procedure) and step 2 (\textcolor{orange}{orange line}: analysis export).}
 %Step 3 (purple line: dealing with surgical margin).
-{The "main procedure" includes data retrieving from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses.
-The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with low [green] or high [red] expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details).
-The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, which was based on the results from the step 1.
+{The "main procedure" includes data retrieval from TCGA GDC data portal, data process with merging and cleaning (red rectangled),% should be modified aggressively according to different sources of database)
+then performing the survival analyses.
+The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with \textcolor{green}{low [green]} or \textcolor{red}{high [red]} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details).
+The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, based on the results from the step 1.
 (HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}

### 2021-02-14 main.tex
Updates from Overleaf

@@
 However, there are three challenges of biomarker discovery from survival analysis.
-First, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
+First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
 Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.

### 2021-02-15 main.tex
Results is done

@@
 Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected \textit{P} value.
-The result showed that ten over-expressed genes (named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) 
-are significantly associated with a poor prognosis of overall survival. 
-Furthermore, the other ten over-expressed genes (named ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former name as KIAA1683, and NPB) are correlated with better survival.
+The result showed ten over-expressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of overall survival. 
+Furthermore, the other ten over-expressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
 We suggest this workflow equipped with a cutoff-mining engine could help for biomarker discovery.
@@
 The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
-By uncorrected \textit{P} value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
-At the final step, a Bonferroni \textit{P} value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
-The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
-%\subsubsection{Figure 3}
-while the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB (see Table \ref{table:table3}, with their full name of genes).
+The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.5 or less than 0.5) (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b) multivariate plots).
+At the final step, a stringent criteria (Bonferroni \textit{P} value correction) was used to yield twenty candidates (see Figure \ref{fig:figure2}(c), (d)). 
+Among these candidates, ten over-expressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{table:table1}).
+The other ten over-expressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{table:table3}, with their gene name).
 We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
-The plot revealed that the most significant (Bonferroni-adjusted \textit{P} $< 0.05$) candidate genes are located above the dotted line.
+The plot reveals that the most significant (Bonferroni-adjusted \textit{P} $< 0.05$) candidate genes are located above the dotted line.
 At the same time, Cox's HR separated them on the two-side with prognostic impact.
@@
 Dotted line: significant Bonferroni corrected \textit{P} value. 
-Red circles mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). Green circles mark 10 genes, which affect on better survival ($HR<=0.5$).}
+\textcolor{red}{Red circles} mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green circles} mark 10 genes, which affect on better survival ($HR<=0.5$).}
 \label{fig:figure3}
@@
 
-Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}(a)).
-The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
-In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted \textit{P} = $0.001$).
-Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot showed that the uncorrected 116 \textit{P} values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
-The smallest \textit{P} value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal \textit{P} value.
+Our top 1 candidate is \acrfull{DKK1}.
+The Kaplan-Meier curve reveals 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
+In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) had a better prognosis (adjusted \textit{P} = $0.001$) (see Figure \ref{fig:figure4}(a)).
+Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot shows that the uncorrected 116 \textit{P} values ($< 0.05$) have been estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
+The smallest \textit{P} value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), has been defined as an optimal \textit{P} value.
 Conversely, the most associated gene with better survival is \acrfull{ZNF557}.
-In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted \textit{P} = $0.001$).
-The cutoff finding procedure (cutofFinder\_func.R) generated cumulative \textit{P} value plots in Figure \ref{fig:figure4}(d).
-There were 166 uncorrected \textit{P} values estimated by a serial cut from 125 to 290 for grouping the cohort.
-All was less than 0.05, and the smallest \textit{P} value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal \textit{P} value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
+In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 264 patients bearing the higher expression of \acrshort{ZNF557} had 55\% of 5-year OS survival rate (adjusted \textit{P} = $0.001$).
+The cutoff finding procedure (cutofFinder\_func.R) generated cumulative \textit{P} value plot in Figure \ref{fig:figure4}(d).
+The 166 uncorrected \textit{P} values were estimated by a serial cut from 125 to 290 for grouping the cohort.
+The smallest \textit{P} value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
 %The second candidate, which improving patient survival, is ZNF266.
@@
 \bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
-{(a) Kaplan-Meier plot of DKK1 under optimal \textit{P} value, and (b) the cutoff was derived from cumulative \textit{P} value plot of DKK1.
-(c) Kaplan-Meier plot of ZNF557 under optimal \textit{P} value, and (d) the cutoff was derived from cumulative \textit{P} value plot of ZNF557.}
+{(a) Kaplan-Meier plot of DKK1 under optimal \textit{P} value, and (b) the cutoff is derived from cumulative \textit{P} value plot of DKK1.
+(c) Kaplan-Meier plot of ZNF557 under optimal \textit{P} value, and (d) the cutoff is derived from cumulative \textit{P} value plot of ZNF557.}
 \label{fig:figure4}
@@
 
-Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value.
+Table \ref{table:table1} shows ten over-expressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value. 
 We found their Cox's univariate and multivariate HR are all greater than 1.837. 
-There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
+%There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
 In Table \ref{table:table2},
-after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
-The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, \textit{P} = 0.015]).
-The M stage could not be considered due to only 3 out of 414 patients which have distant metastasis.
+after adjustment of confounders, \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
+Older age (more than 65) also worse the survival (HR 1.462 [95\% CI: 1.078-1.983, \textit{P} = 0.015]). 
+The M stage could be ignored in this cohort due to only 3 out of 414 patients with distant metastasis.
 
@@
 
-There were also ten candidate genes over-expressed with a better prognosis of \acrshort{hnscc}, listed in Table \ref{table:table3}. Cox's univariate and multivariate HR is just under 0.5.
+In Table \ref{table:table3}, the other ten over-expressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
 In Table \ref{table:table4},
-after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.
-
-In overall results, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+after adjustment of confounders, prognosis is influenced by advance clinical T Status (HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] ), positive surgical margin involvement (HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003]) , and higher tobacco exposure (HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022]).
+Over-expressed \acrshort{ZNF557} gene could has a protective influencce on prognosis (HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001]).
+
+In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
 

### 2021-02-15 main.tex
Updates from Overleaf

@@
 \linebreak
-Input $X_1...n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
+Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
 \\[0.5cm]
-Coefficients $\beta_0...n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)\\[0.5cm]
+Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
 A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
@@
 \end{flushleft}
-Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.
+Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.\\[1cm]
 
@@
 In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
+The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
+%\\[0.5cm]
 
@@
 the TCGA has not collected holistic features
+Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
+[Results] In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
+The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
 %癌症與身心靈的重要關係：中醫、citation?

### 2021-02-15 Supplementary_figures.tex
next on \subsection{Research limitation}

--- 2021-02-02 supplementary_figures.tex
@@
+% Supplementary_figures.tex
 \documentclass[preprint,12pt]{elsarticle}
@@
 %%% for abbreviations, or acronyms
-\usepackage[automake, acronym, nopostdot]{glossaries} 
+\usepackage[acronym, nopostdot]{glossaries} 
 %\usepackage{glossary-inline}
 %\newenvironment{abbreviation}
-\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
+%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
 \newacronym{fdr}{FDR}{false discovery rate}
@@
 %\Author{
-Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
+Li-Hsing Chi $^{1,2}$%\orcidA{}
+, Alexander TH Wu $^{1}$,
 Michael Hsiao $^{3}$*
@@
 
-Supplementary Figure S1\\
+Supplementary Figure S\ref{fig:fig_SurvExpress}\\
 The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
@@
 
-Supplementary Figure S2\\
+Supplementary Figure S\ref{fig:fig_HPA_USP10}\\
 The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
@@
 
-Supplementary Figure S3\\
+Supplementary Figure S\ref{fig:fig_GSE2837}\\
 GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
@@
 \raggedleft
-\includegraphics[width=14cm]{Answer_3-1.pdf}
+\includegraphics[width=10cm]{Answer_3-1.pdf}
 \caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization.
@@
 \raggedleft
-\includegraphics[width=14cm]{Answer_3-1_USP10.pdf}
+\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
 \caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
@@
 \raggedleft
-\includegraphics[width=14cm]{Answer_2-2.pdf}
+\includegraphics[width=12cm]{Answer_2-2.pdf}
 \caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
 The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
-\label{figure:fig_GSE2837}
+\label{fig:fig_GSE2837}
 \end{figure}

### 2021-02-15 main.tex
Updates from Overleaf
next on \subsection{Research limitation}

@@
 %\usepackage{hyperref}
+\usepackage{xr}
+% for xr in your preamble
+% https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf
+\makeatletter
+\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{%
+    \externaldocument{#1}%
+    \addFileDependency{#1.tex}%
+    \addFileDependency{#1.aux}%
+}
+% my external document I would like to reference the labels of. 
+\myexternaldocument{Supplementary_figures} %.tex .aux
+
 %\usepackage{url}
@@
 %latex https://www.latex-tutorial.com/symbols/greek-alphabet/
-\subsection*{Linear regression in biomarker discovery}
+%\subsection*{Linear regression in biomarker discovery}
 Linear regression is useful as a concept in biomarker discovery.
-A linear regression equation that relates a Y-variable to n X-variables is written as%\\[1cm]
-\par
+A linear regression equation that relates a Y-variable to n X-variables is written as\\[1cm]
+%\par
 %Highlights
@@
 
-\subsection{A introduction of TCGA}
+%\subsection{A introduction of TCGA}
 %\begin{MyColorPar}{red}
@@
 Many databases adopt the essential demographic data from TCGA since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
-\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data.
+\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-based tools and API are ready to analyze and visualize TCGA data.
 It might be getting help quickly from the research community for trouble-shooting.
-\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
+\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing\cite{Tomczak2015}.\\[0.5cm]
 \end{outline}
 
-%\end{MyColorPar}
-%%%%%% end of additional revision1
-\par
 In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
@@
 Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
-The above mentioned web-tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
+The above mentioned web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
 There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
@@
 
+%%%%
+\subsection{Feature selection for survival modeling} % Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
 % TCGAbiolinks
 %alcohol consumption
-Besides ethnicity, age, gender, the \acrshort{tnm} stage, radiation therapy, chemotherapy, and targeted therapy, the comprehensive adverse features of prognosis in \acrshort{hnscc} should include tobacco exposure, \acrshort{egfr} amplification, \acrfull{hpv} status, positive/close surgical margin ($<5 mm$), \acrfull{ene}, \acrfull{lvsi}, \acrfull{pni}, \acrfull{doi} ($>5 mm$), as well as metastatic \acrfull{lnd}\cite{Cheraghlou2018}, and \acrfull{wpoi5}, which was defined as tumor dispersion $>= 1 mm$ between tumor satellites or positive \acrshort{pni}/\acrshort{lvsi}\cite{Amin2017}.
-The features of \acrshort{doi}, \acrshort{lnd}, and tumor dispersion were not available on the \acrshort{tcga} dataset.
-The Brandwein-Gensler's risk model (lymphocytic host response, \acrshort{wpoi5}, and \acrshort{pni})\cite{Brandwein-Gensler2010}\cite{Sinha2018} was suggested to be routinely performed on pathological examination.
+Besides ethnicity, age, gender, \acrshort{tnm} stage, radiation therapy, chemotherapy, and targeted therapy, the comprehensive adversely prognostic features in \acrshort{hnscc} should also include tobacco exposure, \acrshort{egfr} amplification, \acrfull{hpv} status, positive/close surgical margin ($<5 mm$), \acrfull{ene}, \acrfull{lvsi}, \acrfull{pni}, \acrfull{doi} ($>5 mm$), as well as metastatic \acrfull{lnd}\cite{Cheraghlou2018}, and \acrfull{wpoi5}, which is defined as tumor dispersion (1 mm apart between tumor satellites) or positive \acrshort{pni}/\acrshort{lvsi}\cite{Amin2017}.
+The features of \acrshort{doi}, \acrshort{lnd}, and tumor dispersion are not available on the \acrshort{tcga} dataset.
+The Brandwein-Gensler's risk model (lymphocytic host response, \acrshort{wpoi5}, and \acrshort{pni})\cite{Brandwein-Gensler2010}\cite{Sinha2018} has been suggested to be routinely performed on pathological examination.
 In previous reports of \acrshort{hnscc}, the loco-regional failure will be high when the initial frozen section has a positive/close surgical margin, and even the final margin revision revealed negative\cite{Bulbul2019b}.
-According to Table \ref{table:table2} and Table \ref{table:table4} in our study, the positive surgical margin yielded a hazard ratio greater than 1.6 to influence on patient's \acrshort{os}.
-It was suggested by authors \cite{Scholl1986}\cite{Sutton2003}\cite{Shaw2004}\cite{Guillemaud2010a}\cite{Patel2010}\cite{Kuriakose2017}\cite{Shapiro2017}\cite{Saidak2018}\cite{Miguelanez-Medran2019}\cite{Saidak2019} that the reason of positive/close surgical margin is possibly due to tumor aggressiveness or dispersion (WPOI-5) instead of iatrogenic reason of surgery.
-The surgical margin status is suggested as an independent surrogate for tumor dispersion, and important in the \acrshort{hnscc} study.
-Thus, in the current study, we selected the common clinicopathological features, including gender, age, clinical T, clinical N, clinical M, surgical margin status, and tobacco exposure in the biomarker discovery for adjustment of confounders (details description at Materials and Methods section).
-
+According to Table \ref{table:table2} and Table \ref{table:table4} in our study, the positive surgical margin yields a hazard ratio greater than 1.6 to influence on patient's \acrshort{os}.
+It is suggested by authors \cite{Scholl1986}\cite{Sutton2003}\cite{Shaw2004}\cite{Guillemaud2010a}\cite{Patel2010}\cite{Kuriakose2017}\cite{Shapiro2017}\cite{Saidak2018}\cite{Miguelanez-Medran2019}\cite{Saidak2019} that the reason of positive/close surgical margin is possibly due to tumor aggressiveness or dispersion (WPOI-5) instead of iatrogenic reason of surgery.
+The surgical margin status has also been suggested as an independent surrogate for tumor dispersion in the \acrshort{hnscc} study.
+Thus, we selected common clinicopathological features in the current biomarker discovery, including gender, age, clinical T, clinical N, clinical M, surgical margin status, and tobacco exposure, to adjust confounders (details description at Materials and Methods section).
+
+%%%
+
+\subsection{Validation by web-based tools}
+We utilized another approach of web-based tools (TCGA and GSE2837 cohort) to validate our candidates.
+%Since the discovery of workflow, we also used the web-based tools to find the evidence convincing up to 12 of our suggested 20 biomarkers in TCGA and GSE2837 cohort.
+
+%\subsubsection*{SurvExpress} % TCGA
+% 2021/01/23 pdf x 12 from SurvExpress
+SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
+Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
+1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);\\
+%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).\\
+%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635),
+The 12 out of 20 candidate genes are confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S1.%\ref{fig:fig_SurvExpress}.
+% moved to supplementary file: Supplementary_figures.tex
+
+% % SurvExpress 沒有類似的結果是因為:
+Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
+Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
+
+%\subsubsection{HPA} %still TCGA's RNA-Seq
+The Human Protein Atlas project (HPA) has proteomics analysis based on 26,941 antibodies targeting 17,165 unique proteins.
+The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA.
+Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
+All transcriptomics data has been retrieved from the TCGA, and all proteomics data has been generated in-house using the same antibodies.
+Our 9 candidates (e.g., DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+\\cancer)\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset 
+(Please see Supplementary Figure S2)%\ref{fig:fig_HPA_USP10})
+% moved to Supplementary
+
+% Version: 3.0.2 Date: 2015/06/11 SurvNet
+%Preloaded TCGA  data is also available for analysis.
+%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
+%gene regulatory or protein interaction network
+% cited by 10 articles
+% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
+% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
+%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
+
+%\subsubsection*{GSE2837} % non-TCGA
+% from Anwser2-2
+%by GEO GSE2837 HNSCC dataset (PrognoScan)
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
+relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
+and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
+The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
+1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
+2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
+%17 out of 20 candidates
+%?DKK1 (0.253635), 
+Please see Supplementary Figure S3.%\ref{fig:fig_GSE2837}.
+
+Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
+%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
+%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
+The 10 out of 20 candidates are confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
+
+%%%
+\subsection{The candidates shown in literature review}
+% *** why here?
 In our previous work, altered glucose metabolism (e.k.a.
-the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrfull{slc2a4} (or \acrfull{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}.
-In this study, LOC148709 (a \acrfull{lncrna}) was suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3}).
-%on page \pageref{table:table3}). I
-It was also found to has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
-
-There is a trend toward cancer type-agnostic study. The success of pembrolizumab and nivolumab was based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
-It showed a precedent of tumor type-agnostic therapy\cite{Yan2018}.
-%*** PD-L1/PD-L2 is a biomarker; Keynote-012
-Currently, there are several common biomarkers of \acrshort{ici} under evaluation, which include \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
-The other  \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019}\linebreak
-(ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (ClinicalTrials.gov Identifier: NCT04080804) studies.
-
+the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrfull{slc2a4} (or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}.
+
+%%
+%\subsection*{Review articles}
+Since the discovery of workflow, we performed the literature review by Embase/Pubmed.% to find the evidence convincing the suggested biomarkers in cancer research. 
+The 10 out of 20 candidates has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+
+%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
+
+%%%%%% bad guy
+The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+Pang et al.\cite{Pang2018} has proved that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhances their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Increased DKK1 levels in HNSCC tissues is correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+DKK1 expression is significantly associated with smoking, alcohol abuse, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+The mRNA expression of DKK1 and DKK3 is elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
+
+%STC2:
+The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway\cite{Ma2020}.
+
+% PGK1
+Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). 
+The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
+
+%SURF4
+The patients with tumors (such as glioma, breast cancer, lymphoma, pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
+) exhibiting high Surfeit gene 4 (SURF4) expression have significantly shorter overall survival than low SURF4 expression.
+SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
+%NIH/3T3 cells (Mus musculus, mouse), 293T cell
+%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
+%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
+%web-based tools survival (not TCGA?)
+
+% USP10
+Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs), may serve as a prognostic biomarker and target for various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
+Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - reveals that USP10 is significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL-2–STAT5 signaling, transforming growth factor beta (TGFB or $TGF\beta$) signaling, and PI3K/Akt/mTOR signaling\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
+https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
+
+%FOXA2
+Prognostic signature integrated of DNA methylation, gene expression, and clinical information could provide a prognostic prediction value for HNSCC patients.
+Forkhead Box A2 (FOXA2) is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
+%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
+%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
+% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
+%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
+Further, SIS analysis was performed to further screen out a stable probe combination.
+Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
+2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
+Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
+2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
+%Association between gene expression and methylation.
+Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
+Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
+
+% STIP1; non-TCGA
+Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. 
+The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
+%STIP1 could bind to bind Hsp70 and Hsp90.
+
+%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
+%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
+%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
+% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
+
+%%%%%% good guy
+%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
+%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
+%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
+%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
+
+%ZNF266, % or ZNF16, HZF1?
+%MYO1H associated mandibular prognathism\cite{Sun2018}
+
+% FCGBP
+% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
+Fc fragment of IgG binding protein ($Fc\gamma BP$ or FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas\cite{ODonovan2002}\cite{Griffith2006}.
+%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
+%gene ID @gene@8857
+
+\acrfull{LOC148709} has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
+In our current study, LOC148709 is also suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3} on page \pageref{table:table3}).
+
+%EVPLL in cDNA project
+
+% PNMA5
+Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}.
+
+%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
+GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
+
+%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
+(PMID31598163)
+%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
+The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
+Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
+%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
+%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
+%\cite{Li2018b}
+%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
+%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+
+%NDFIP1:
+%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
+was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
+%MCF7 cells 
+%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
+%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
+%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
+Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
+We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
+hepatocellular carcinoma\cite{Zhang2019a}
+% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
+%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
+It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
+
+%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+%DKC1 is the tumor suppressor gene in HNSCC
+% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
+
+\subsection{Research limitation}
 Although we combined the power of genome-wide scanning and an optimal cutoff finder for Kaplan-Meier survival analysis, the study has some limitations.
@@
 
-\subsection{our lab}
+\subsection{Future work}
+\subsubsection{Laboratory validation}
 It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
@@
 
-We utilized other approaches to validate our candidates.
-
-\subsection*{Analysis by web-tools}
-After discovering using our workflow, we also used the web-tools to find the evidence convincing up to 12 of our suggested 20 biomarkers in TCGA and GSE2837 cohort.
-%\subsubsection*{SurvExpress} % TCGA
-% 2021/01/23 pdf x 12 from SurvExpress
-SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
-Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
-1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);
-%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).
-%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
-%17 out of 20 candidates
-%?DKK1 (0.253635),
-The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort.
-Please see Supplementary Figure S1.
-%\ref{fig:fig_SurvExpress}.
-% moved to supplementary file
-
-% % SurvExpress 沒有類似的結果是因為:
-Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
-Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
-%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
-
-%\subsubsection{HPA} %still TCGA's RNA-Seq
-The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
-The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA.
-Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
-All transcriptomics data has been retrieved from the Cancer Genome Atlas, and all proteomics data has been generated in-house using the same antibodies.
-Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
-The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+\\cancer)\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset 
-(Please see Supplementary Figure S2.) %\ref{fig:fig_HPA_USP10})
-% moved to Supplementary
-
-% Version: 3.0.2 Date: 2015/06/11 SurvNet
-%Preloaded TCGA  data is also available for analysis.
-%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
-%gene regulatory or protein interaction network
-% cited by 10 articles
-% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
-% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
-%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
-
-%\subsubsection*{GSE2837} % non-TCGA
-% from Anwser2-2
-%by GEO GSE2837 HNSCC dataset (PrognoScan)
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
-%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
-%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
-relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
-and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
-The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
-1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
-2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
-%17 out of 20 candidates
-%?DKK1 (0.253635), 
-Please see Supplementary Figure S3.\\ %\ref{figure:fig_GSE2837}.
-Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
-%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
-%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
-%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
-
-\subsection*{Review articles}
-After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
-%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
-%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
-%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
-
-%%%%%% bad guy
-The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
-Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
-Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
-Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
-DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
-The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
-%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
-
-%STC2:
-The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
-
-% PGK1
-Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
-The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.
-
-%SURF4
-Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
-) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.
-SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
-%NIH/3T3 cells (Mus musculus, mouse), 293T cell
-%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
-%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
-%web-based tools survival (not TCGA?)
-
-% USP10
-Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
-Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
-https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
-
-%FOXA2
-Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
-FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
-%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
-%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
-% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
-%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
-Further, SIS analysis was performed to further screen out a stable probe combination.
-Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
-2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
-Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
-2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
-%Association between gene expression and methylation.
-Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
-Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
-
-% STIP1; non-TCGA
-Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
-in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. T
-The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
-%STIP1 could bind to bind Hsp70 and Hsp90.
-
-%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
-%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
-%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
-% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
-
-%%%%%% good guy
-%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
-%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
-%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
-%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
-
-%ZNF266, % or ZNF16, HZF1?
-%MYO1H associated mandibular prognathism\cite{Sun2018}
-
-% FCGBP
-% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
-Fc fragment of IgG binding protein (($Fc\gamma BP$, FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas.\cite{ODonovan2002}\cite{Griffith2006}
-%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
-%gene ID @gene@8857
-
-%?LOC148709?, 
-%EVPLL in cDNA project
-
-% PNMA5
-Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
-
-%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
-GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
-
-%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
-(PMID31598163)
-%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
-The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
-Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
-%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
-%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
-%\cite{Li2018b}
-%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
-%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
-
-%NDFIP1:
-%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
-was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
-%MCF7 cells 
-%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
-%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
-%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
-Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
-We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
-hepatocellular carcinoma\cite{Zhang2019a}
-% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
-%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
-It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
-
-%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
-%DKC1 is the tumor suppressor gene in HNSCC
-% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
-
-The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo."
-
-%\end{MyColorPar} % marked as red
-
-%%%%%%%5%%%%% modified end
-
+\subsubsection{Cancer type-agnostic study}
 Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+
 % second limitation:
+
+There is a trend toward cancer type-agnostic study. The success of pembrolizumab and nivolumab was based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
+It showed a precedent of tumor type-agnostic therapy\cite{Yan2018}.
+%*** PD-L1/PD-L2 is a biomarker; Keynote-012
+Currently, there are several common biomarkers of \acrshort{ici} under evaluation, which include \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
+The other  \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019}\linebreak
+(ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (ClinicalTrials.gov Identifier: NCT04080804) studies.
+
 In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers.
@@
 
-\subsection{Holistic health care}
+\subsubsection{Holistic health care}
 TCGA treated by surgery and more; TNM available yes
@@
 \dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
-%All the supplementary figures, tables, and R script codes 
+The supplementary figures are available online.%, tables, and R script codes 
 The R script codes and datasets generated during the current study are available at the GitHub repository, https://github.com/texchi2/pvalueTex.}

### 2021-02-15 main.tex
next on \subsection{Future work} \subsubsection{Laboratory validation}

@@
 \subsection{Research limitation}
-Although we combined the power of genome-wide scanning and an optimal cutoff finder for Kaplan-Meier survival analysis, the study has some limitations.
+Although we combined the power of genome-wide scanning and an optimal cutoff finder for survival analysis, the study has some limitations.
 We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
@@
 By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses.
-However, there are only 237 antibodies available so far. We found that our candidates are not included in the \acrshort{tcpa} database (v3.0\cite{Chen2019}) yet. %  USP-10 in HPA
+However, in the \acrshort{tcpa} database (v3.0\cite{Chen2019}), there are only 237 antibodies available, not including our candidates so far. %  USP-10 in HPA
 %> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))

### 2021-02-16 Supplementary_figures.tex
ready to going Holistic

@@
 % Supplementary_figures.tex
-\documentclass[preprint,12pt]{elsarticle}
+%\documentclass[preprint,12pt]{elsarticle}
+\documentclass[jpm,supfile,submit,moreauthors,pdftex]{Definitions/mdpi}
 
@@
 
-\renewcommand{\figurename}{Supplementary Figure S}
+\renewcommand{\figurename}{Supplementary Figure } %S
 
@@
 %\Title{
-A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma
-
-% MDPI internal command: Title for citation in the left column
-%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
-
-% Author Orchid ID: enter ID or remove command
-%\newcommand{\orcidauthorA}{0000-0002-4476-2600} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0001-6497-4232} % Add \orcidB{} behind the author's name
-
-% Authors, for the paper (add full first names)
-%\Author{
-Li-Hsing Chi $^{1,2}$%\orcidA{}
-, Alexander TH Wu $^{1}$,
-Michael Hsiao $^{3}$*
-and Yu-Chuan (Jack) Li $^{1,4}$*%\orcidB{}
-%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
-
-% MDPI internal command: Authors, for metadata in PDF
-%\AuthorNames{Li-Hsing Chi, Alexander TH Wu, Michael Hsiao and Yu-Chuan (Jack) Li}
-
-% MDPI internal command: Authors, for citation in the left column
-%\AuthorCitation{Chi, LH.; Wu, ATH.; Hsiao, M.; Li, YCJ.}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-%\address{%
-
-$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
-    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
-$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
-    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
-$^{3}$ \quad Genomics Research Center\unskip, 
-    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
-$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
-
-% Contact information of the corresponding author
-%\corres{
-Correspondence: Hsiao: mhsiao@gate.sinica.edu.tw; Li: jaak88@gmail.com\\[1cm]
-%(optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
+Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
+%}
 
@@
 \underline{Supplementary figure legends}\\[1cm]
-
-Supplementary Figure S\ref{fig:fig_SurvExpress}\\
+% S1
+Supplementary Figure \ref{fig:fig_SurvExpress}\\
 The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
@@
 
-Supplementary Figure S\ref{fig:fig_HPA_USP10}\\
+%S2
+Supplementary Figure \ref{fig:fig_HPA_USP10}\\
 The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
@@
 
-Supplementary Figure S\ref{fig:fig_GSE2837}\\
+%S3
+Supplementary Figure \ref{fig:fig_GSE2837}\\
 GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
@@
 \end{figure}
-\clearpage
+%\clearpage
 
@@
 \end{document}
+
+%%%
+% MDPI internal command: Title for citation in the left column
+\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
+
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0002-4476-2600} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0001-6497-4232} % Add \orcidB{} behind the author's name
+
+% Authors, for the paper (add full first names)
+\Author{
+Li-Hsing Chi $^{1,2}$\orcidA{}
+, Alexander TH Wu $^{1}$,
+Michael Hsiao $^{3}$*
+and Yu-Chuan (Jack) Li $^{1,4}$*\orcidB{}
+}
+%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
+
+% MDPI internal command: Authors, for metadata in PDF
+\AuthorNames{Li-Hsing Chi, Alexander TH Wu, Michael Hsiao and Yu-Chuan (Jack) Li}
+
+% MDPI internal command: Authors, for citation in the left column
+\AuthorCitation{Chi, LH.; Wu, ATH.; Hsiao, M.; Li, YCJ.}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+
+$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
+    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
+$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
+    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
+$^{3}$ \quad Genomics Research Center\unskip, 
+    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
+$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
+}
+
+% Contact information of the corresponding author
+\corres{
+Correspondence: Hsiao: mhsiao@gate.sinica.edu.tw; Li: jaak88@gmail.com\\[1cm]
+}
+%(optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

### 2021-02-16 main.tex
Updates from Overleaf
ready to going Holistic

@@
 Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected \textit{P} value.
-The result showed ten over-expressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of overall survival. 
-Furthermore, the other ten over-expressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
+The result showed ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of overall survival. 
+Furthermore, the other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
 We suggest this workflow equipped with a cutoff-mining engine could help for biomarker discovery.
@@
 Overexpression of \acrfull{hif}-1 alpha\cite{Aebersold2001} or Ki-67\cite{Couture2002} was found to be correlated with poor response to radiotherapy of \acrshort{hnscc}.
-The \acrfull{egfr}\cite{O-Charoenrat2000}\cite{Bentzen2005} and \acrfull{mmp}\cite{Harrington2017} were found to be over-expressed to promote invasion and metastasis of \acrshort{hnscc}.
+The \acrfull{egfr}\cite{O-Charoenrat2000}\cite{Bentzen2005} and \acrfull{mmp}\cite{Harrington2017} were found to be overexpressed to promote invasion and metastasis of \acrshort{hnscc}.
 From 2000 to 2006, the first anti-\acrshort{egfr} antibody-drug (cetuximab) has been developed and combined with radiotherapy, known as bio-\acrshort{rt}, to increase survival of unresectable locoregionally advanced disease\cite{Bonner2006a}.
@@
 At the final step, a stringent criteria (Bonferroni \textit{P} value correction) was used to yield twenty candidates (see Figure \ref{fig:figure2}(c), (d)). 
-Among these candidates, ten over-expressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{table:table1}).
-The other ten over-expressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{table:table3}, with their gene name).
+Among these candidates, ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{table:table1}).
+The other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{table:table3}, with their gene name).
 We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
@@
 \centering
-\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }
+\caption{ The 10 candidate genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 %\subsubsection{Table3/legend}
-%Table3. The 10 candidate genes over-expressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
+%Table3. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
 \begin{table}[hp]
 \centering
-\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }
+\caption{The 10 candidate genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 
-Table \ref{table:table1} shows ten over-expressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value. 
+Table \ref{table:table1} shows ten overexpressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value. 
 We found their Cox's univariate and multivariate HR are all greater than 1.837. 
@@
 In Table \ref{table:table2},
-after adjustment of confounders, \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
+after adjustment of confounders, \acrshort{DKK1} overexpression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
 Older age (more than 65) also worse the survival (HR 1.462 [95\% CI: 1.078-1.983, \textit{P} = 0.015]). 
@@
 
-In Table \ref{table:table3}, the other ten over-expressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
+In Table \ref{table:table3}, the other ten overexpressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
 In Table \ref{table:table4},
 after adjustment of confounders, prognosis is influenced by advance clinical T Status (HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] ), positive surgical margin involvement (HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003]) , and higher tobacco exposure (HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022]).
-Over-expressed \acrshort{ZNF557} gene could has a protective influencce on prognosis (HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001]).
+Overexpressed \acrshort{ZNF557} gene could has a protective influencce on prognosis (HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001]).
 
@@
 \subsection{The candidates shown in literature review}
-% *** why here?
-In our previous work, altered glucose metabolism (e.k.a.
-the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrfull{slc2a4} (or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}.
 
@@
 
-\subsection{Research limitation}
-Although we combined the power of genome-wide scanning and an optimal cutoff finder for survival analysis, the study has some limitations.
+\subsection{Limitations of the work}
+
+Although we combine the power of genome-wide scanning and an optimal cutoff finder for survival analysis, the study has some limitations.
+% first limitation:
 We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
-The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excited the cancer research community\cite{Li2013c}\cite{Li2017b}.
-By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses.
-However, in the \acrshort{tcpa} database (v3.0\cite{Chen2019}), there are only 237 antibodies available, not including our candidates so far. %  USP-10 in HPA
+The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excites the cancer research community\cite{Li2013c}\cite{Li2017b}.
+By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray kind of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses from \acrshort{rnaseq} study.
+However, in the \acrshort{tcpa} database (v3.0\cite{Chen2019}), there are only 237 antibodies available, not covering our candidates so far. %  USP-10 in HPA
 %> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))
@@
 
-\subsection{Future work}
+% second limitation:
+%\subsubsection{Cancer type-agnostic study}
+Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+% *** why here?
+In our previous work, altered glucose metabolism (e.k.a.
+the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
+% Cited In for PMID: 28061796
+Lactic acidosis induced \acrshort{glut4} overexpression was also found in lung cancer cells\cite{Prado-Garcia2020}. 
+%The overexpression of \acrshort{glut4} will lead to higher glucose uptake in proliferating cancer cells\cite{Mani2020}.
+%There is a trend toward cancer type-agnostic study. 
+Currently, Pembrolizumab and nivolumab's success has been based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
+It shows a model of tumor type-agnostic therapy\cite{Yan2018}.
+%*** PD-L1/PD-L2 is a biomarker; Keynote-012
+There are several common biomarkers of \acrfull{ici} under evaluation, including \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
+The other \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019} (ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (NCT04080804) studies.
+
+In line with tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases.
+However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
+Before the global genes scanning process, it is necessary to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
+This process should be carefully curated to confirm the data integrity within the correct definition.
+We also plan to upgrade our R script of the cutoff engine to the C++ language and source it in the Rstudio server.
+The high performance of C++ could speed up the critical steps in this workflow involving heavy computation of matrix data\cite{Woodward2020}.
+Moreover, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+
+\subsection{Future research directions}
 \subsubsection{Laboratory validation}
@@
 These in vitro and in vivo validation experiments will be undertaken in our laboratory.
-We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
+We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. Western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
 %mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
-The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x.
+The effect of overexpression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x.
 proliferation, migration, and invasion) and mouse xenograft model (e.x.
@@
 %the rest of the analysis seems fine, but 
-%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
-We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset.
+%文章的初衷、跨領域：如同deep leaning Keras API，推廣給研究者一個有效的方法 
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
 % to find more useful biomarkers.
@@
 % to allow successful repetition and extension of analyses based on original data
-A good practice of research reproducibility is necessary to allow the reuse of code and results for new projects.
+A good research reproducibility practice is necessary to allow the reuse of code and results for new projects.
 %previously developed methodology to be effectively applied on new data, or to allow 
@@
 %Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows.
-Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
+Thus, it guarantees to final users the ability to repeat any analysis independently using UNIX-like architecture.
 %Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
-
-Once our laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis.
-
-\subsubsection{Cancer type-agnostic study}
-Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
-
-% second limitation:
-
-There is a trend toward cancer type-agnostic study. The success of pembrolizumab and nivolumab was based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
-It showed a precedent of tumor type-agnostic therapy\cite{Yan2018}.
-%*** PD-L1/PD-L2 is a biomarker; Keynote-012
-Currently, there are several common biomarkers of \acrshort{ici} under evaluation, which include \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
-The other  \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019}\linebreak
-(ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (ClinicalTrials.gov Identifier: NCT04080804) studies.
-
-In line with tumor-agnostic research, we plan to explore more TCGA diseases to find common biomarkers.
-However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
-Before the global genes scanning process, we needed to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
-It should be carefully curated to confirm the data integrity with the correct definition.
-We also plan to upgrade our plain R script at the Rstudio platform to program in the C++ language and source it in R.
-The high performance of C++ could speed up the cutoff finding engine in this workflow involving heavy computations\cite{Woodward2020}.
-Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
+Once our laboratory or the community confirms those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients.
+%and improve prognosis.
 
@@
 %5.心無恐懼: 情志養生
-
+the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+with more TCGA features
+graph convolutional neural network (GCNN)
 Wish and bless the whole world
@@
 \section{Conclusions} % 5
+% Conclusions: This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
 
@@
 They also might be potential common biomarkers for subsequent study.
-We wish this bioinformatics tool will be available for the broad usage of tumor-agnostic research\cite{Looney2020} to cross several \acrshort{tcga} diseases to make translational impacts.
+% welcome for study
+
+%tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases
+We wish this bioinformatics tool will be available for the broad usage of tumor-agnostic research\cite{Looney2020} to crossing several \acrshort{tcga} diseases to make translational impacts.
 %Tex: PvalueTex
 
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
+TCGA has not collected holistic features.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
+%% optional: The data presented in this study are available in supplementary material.
+\supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, Figure S1: The query results from SurvExpress, Figure S2: The query results from HPA, Figure S3: GSE2837 query results from PrognoScan.}
+%Table S1: title, Video S1: title.}
+%S1
+%S2
+%S3
 
@@
 \dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
-The supplementary figures are available online.%, tables, and R script codes 
+%The supplementary figures are available online.%, tables, and R script codes 
 The R script codes and datasets generated during the current study are available at the GitHub repository, https://github.com/texchi2/pvalueTex.}

### 2021-02-16 main.tex
Cullen and WHO done

@@
 
-\subsubsection{Holistic health care}
+\subsubsection{Holistic cancer care}
+Bruce Lipton: the biology of belief 信念的力量
+biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
+那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。
+也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。所以我們的科學家依舊在研究，基因對癌症的影響（單向）。
+冤親債主的意念
 TCGA treated by surgery and more; TNM available yes
@@
  since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
-the TCGA has not collected holistic features
-Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
+the TCGA does not collect holistic features
+Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
+or even spiritual, emotional, and social status) go holistic
+
+World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}.
+Core principles can be taken to achieve people-centred and integrated health service delivery.
+First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being.
+(Holistic care: care to the “whole person” that considers psychological, social and environmental factors rather than just the symptoms of disease or ill-health)
+Second principle is Empowering – supporting people to manage and take responsibility for their own health.
+(Empowerment: the process of supporting people and communities to take control of their own health needs resulting, for example, in the uptake of healthier behaviours or the ability to self- manage illnesses)
+People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
+Glossary:
+%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways.
+People-centred care also requires that people have the education and support they need to make decisions and participate in their own care.
+It is organized around the health needs and expectations of people rather than diseases (7,8)
+%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
+(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)
+
+The spiritual care is he key of holistic healthcare in dental practice or for cancer patient.
+Being mindful to patient’s mental health and emotional changes during the dental care.
+Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration.
+Learning to listen proactively
+9) Therapeutic relationship is an essential key towards spiritual care.
+Being aware of patient’s spiritual needs during/after treatment.
+12) Applying the holistic healthcare strategies, such as the Shared Decision Marking, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}
+
+Lipton 1992, epinephrine and histamine signals in endothelium, 心智作用
+The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
+
 [Results] In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
@@
 The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
-%癌症與身心靈的重要關係：中醫、citation?
+依舊是以管窺天
+% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
+%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
+PCA and ECA
+Carl Rogers: Carl Rogers' person-centered theory
+the therapist is providing the appropriate social-environmental conditions \cite{Rogers1957}.\cite{Joseph2004}\cite{Griffiths2013}
+Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers\cite{Rogers1957}.
+The research implication is to investigate the relationship between the client’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
+Dealing with negative emotions.
+As the client feels intense negative emotions of fear, despair, sadness and so on, it is not the client-centred therapist’s task to try and remove these feelings: The task is simply to stay with the client’s experiences.
+T he research implication is to investigate the necessity and sufficiency of the six conditions.
+
+Rogers, C.
+R.
+A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework.
+in Psychology: A Study of a Science.
+Study 1, Volume 3: Formulations of the Person and the Social Context (ed.
+Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
+% http://bibliotecaparalapersona-epimeleia.com/greenstone/collect/ecritos2/index/assoc/HASH01a5/4583605e.dir/doc.pdf
+
+% so do the cancer
+Individual treatment and avoiding assumptions.
+Although it is useful for therapists to have a knowledge of the trauma literature on the general reactions of people who experience trauma, the therapist should not assume that this knowledge necessarily applies to each and every client\cite{Joseph2004}.
+
+Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction,13,16 centred on a physician's therapeutic intentions and his attunement to patient sympathy.
+we educate them
+1.
+Mong, L.-C., Liao, F., Chiou, J.
+& Chiang, P.
+Tips for Integrating Spiritual Care Delivery in Dental Education.
+in Asia Pacific Medical Education Conference.
+Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}
+
+*** make Figure 5 holistic:
+meridian and emotion has mutual reaction
+meridian effect tissue and organ
+(autonomic nerve system, myofascial network, prefrontal cortex)
+placebo-effect influence on drug discovery
+博士班學生，越研究越發現，科學的不足
+，心理與靈性的力量，更是背後推動的冥冥力量
+身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
+
+騙過你的病-安慰劑效應 The Placebo Effect
+(Emmanuelle Sapin, Pascal Goblot)
+%1. Sapin, E. & Goblot, P. L’effet placebo (English: The Placebo Effect) [enregistrement vidéo] : le formidable pouvoir de l’auto-guérison. 53 PP-Quebec (Cinéfête, 2014).\cite{Sapin2014}
+% https://biblio.bdeb.qc.ca/in/sim/faces/details.xhtml;jsessionid=E3DD39109012D0BEA598E6E5B66A4FD2?id=p::usmarcdef_0000058243&posInPage=8
+1. Finniss, D. G. Placebo Effects: Historical and Modern Evaluation. in International review of neurobiology vol. 139 1–27 (2018).\cite{Finniss2018}
+%蓋倫劑量 placebo effect 身心靈醫學的核心
+In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo.
+If I had thought of any internal medicine it would have been a dose of the Dover's powders."\cite{Kerr2008}\cite{Finniss2018}.
+ (made up of Ipecac and opium) 
+ Cullen studied the objective science of analytical chemistry.
+He also sense that the patient's subjective, psychosomatic or ‘sympathetic constitution’ determined his reaction to a prescribed therapeutic substance.
+***Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
+Cullen's theory of sympathy is a mind-body function, a kind of ‘vital force’ that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
+This finely calibrated, rational use of active placebo treatment, in which the physician dispensed a weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
+%啟蒙運動
+
+%sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
+The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, whether by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
+placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
+醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
+安慰劑效應的研究，最後導向了良好醫病關係的思考，並成為醫生臨床醫術的元素之一：
+「醫師開藥時，其實是把自己當藥方開出去」。
+安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
+The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}
+
+prefrontal lobe 理智腦 意識 正念 杏仁核
+「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
+物理作用、信號，雷射針灸
+
+Warburg effect and carcinogenesis
+cancer therapy by 患者自癒
+Self-Compassion  慈悲
+Self-compassion 
+除我執
+ global self-esteem:
+自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
+
 中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
+養生和治療的原則:
+一、某些病症可以透過食療而改善的會建議自行調養
+二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
+三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
+四、沒有一勞永逸的食療，不宜執著特定的食療神話
+五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
+六、認識自己身體的狀態比吸收營養資訊更重要
+七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
+
 repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
-%自他不二 心存正念
+
+mindfulness and meditation for cancer
+情志養生 悲喜憂思苦 七情
+%自他不二 心存正念 向內看，解決苦之源
 %1.衷心懺悔
@@
 %3.誠意祝福
-%4.永存善念
+%4.永存善念 慈悲
 %5.心無恐懼: 情志養生
+
+ground truth Y (e.x. patient's survival):\\[0.5cm]
+%Y$:\\[0.3cm]
+$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
+
+There is much work to be done in investigating the functional relationships more fully.\cite{Rogers1959}
+
+how to do: once holistic feature available, graph convolutional neural network (GCNN) is mandatory: 以免 genomics 光芒萬丈
+
 the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
 with more TCGA features
-graph convolutional neural network (GCNN)
+
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on all the TCGA or other in-house cancer datasets.
+
 Wish and bless the whole world
+Dali Lama
 

### 2021-02-17 main.tex
Updates from Overleaf

@@
 安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
+前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
+PCA理論
+以心印心 engaging
+身心相連 body-mind connection
+捨末求本
+the anterior cingulate cortex and the dorsolateral prefrontal cortex have been found to be activated by placebo administration.
+\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}
+But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}.
+Today, pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced\cite{Bennett2018}.
+身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，
+「他自己本身」就具有療癒效果
+「把自己當藥方開出去」
+#正念 減壓，療癒疼痛\cite{Krummenacher2010}\cite{Bennett2018}、免疫系統、內分泌系統或自律神經系統相關的疾病，以及憂鬱症、焦慮症 
 The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}
@@
 物理作用、信號，雷射針灸
+Therapeutic Relationship
+Spirituality
+慈悲心 compassion 
+同情心 sympathy
+同理心 empathy
+non-verbal contact
+前額葉內側 (medial prefrontal cortex)
+額葉底部(orbitofrontal cortex)
+治療關係的核心條件: 說好話 眼對眼 engaging 用真心
+empowering
+(一)雙方有心理的接觸。
+(二)當事人正感到焦慮或不一致(incongruence)。 
+(三)治療者在治療關係中是一致的、真實的或真誠的。
+(四)治療者能夠對當事人表現出無條件的正向關懷。
+(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
+Personhood: Carl Rogers
+尋找生命的意義
+真誠、能深刻地善解人意
+非認知性核心能力
+正念止觀(在當下)
+人人有自癒能力
+真誠 (Genuineness/Validity/Bona Fides)
+內在聲音與外在態度一致/明心見性/超越的意識狀態
+(Congruence/Consistency)
+共情理解(設身處地/同理心/除我執)
+(Empathic Understanding of Reference/Track)
+無條件關懷(不批判/頓悟)
+(unconditional positive regard)
+***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
+諮商員的
+靈性功力
+治療關係
+I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
+Then simply my presence is releasing and helpful\cite{Rogers1979}.
+%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
+%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
+「診後說三句，更勝良帖十方」
 
@@
 cancer therapy by 患者自癒
+Mindfullness Meditation help 復原力（resilience）
 Self-Compassion  慈悲
@@
 情志養生 悲喜憂思苦 七情
+人俯仰於天地之間
+順從四季氣候變化
+保養正氣陶冶性情
+自我療癒身心靈疾病
 %自他不二 心存正念 向內看，解決苦之源
@@
 %5.心無恐懼: 情志養生
+每位醫師都可以成為「創傷知情者」
+幫助我們身邊的病患， 懂他的心靈創傷
+讓他有安全感， 才有機會改變疾病的走向
+
+“每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）”
+解說：
+患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。
 
@@
 the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
-with more TCGA features
+with more TCGA features (holistic)
+Impact of stress on cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}
+cancer initiation under stress\cite{Lutgendorf2010}\cite{Powell2013}
+HNSCC\cite{Iftikhar2021}
+Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress or depression, and domestic or community violence, have been associated in epidemiological studies with increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses.
+Additional work has shed light on the potential molecular mechanisms by which early adversity becomes “biologically embedded” in altered physiology across body systems.\cite{Berens2017}
 

### 2021-02-18 main.tex
abstract and result is updated (after validation with GSE2837, 10 candidates remained)

@@
 It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
-Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected \textit{P} value.
-The result showed ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of overall survival. 
-Furthermore, the other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
+Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders, and Bonferroni corrected \textit{P} value.
+After validation with an independent \acrshort{hnscc} cohort (GSE2837), the result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
+Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
 We suggest this workflow equipped with a cutoff-mining engine could help for biomarker discovery.
 }
+% validated by the other HNSCC cohort:
+%1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
+%2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
+
+% row 20: The result showed ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of overall survival.
+Furthermore, the other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
 
@@
 At the final step, a stringent criteria (Bonferroni \textit{P} value correction) was used to yield twenty candidates (see Figure \ref{fig:figure2}(c), (d)). 
+% before validation
 Among these candidates, ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{table:table1}).
@@
 At the same time, Cox's HR separated them on the two-side with prognostic impact.
+% => after validation: The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
+Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
 
@@
 \subsection{Validation by web-based tools}
-We utilized another approach of web-based tools (TCGA and GSE2837 cohort) to validate our candidates.
-%Since the discovery of workflow, we also used the web-based tools to find the evidence convincing up to 12 of our suggested 20 biomarkers in TCGA and GSE2837 cohort.
-
+%注意 強調GSE2837: 
+The prognostic
+significance of the candidate genes has been validated by an independent patient cohort.
+
+%\subsubsection*{GSE2837} % non-TCGA
+% from Anwser2-2
+%by GEO GSE2837 HNSCC dataset (PrognoScan)
+After the discovery with our workflow, we validated the suggested 20 biomarkers in the other \acrshort{hnscc} cohort.
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005)
+microarray gene expression (by Affymetrix X3P chips U133\_X3P) and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
+The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
+1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
+2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
+%17 out of 20 candidates
+%?DKK1 (0.253635), 
+%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
+%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
+%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
+The 10 out of 20 candidates are confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
+
+%
+We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
 %\subsubsection*{SurvExpress} % TCGA
@@
 %?DKK1 (0.253635),
-The 12 out of 20 candidate genes are confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S1.%\ref{fig:fig_SurvExpress}.
+The 12 out of 20 candidate genes are confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
 % moved to supplementary file: Supplementary_figures.tex
@@
 %found at Human Protein Atlas dataset 
-(Please see Supplementary Figure S2)%\ref{fig:fig_HPA_USP10})
+(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
 % moved to Supplementary
@@
 %The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
-
-%\subsubsection*{GSE2837} % non-TCGA
-% from Anwser2-2
-%by GEO GSE2837 HNSCC dataset (PrognoScan)
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
-%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
-%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
-relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
-and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
-The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
-1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
-2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
-%17 out of 20 candidates
-%?DKK1 (0.253635), 
-Please see Supplementary Figure S3.%\ref{fig:fig_GSE2837}.
-
-Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
-%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
-%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
-%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 candidates are confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
 
@@
 % Conclusions: This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-Our findings suggested 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni \textit{P} values and proper confounders control.
+%The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
+Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
+Our findings suggested 10 candidate biomarkers,CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2, as well as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni \textit{P} values and proper confounders control.
 They also might be potential common biomarkers for subsequent study.

### 2021-02-25 main.tex
Lipton: mind-brain-body system

@@
 %Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
-Once our laboratory or the community confirms those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients.
+Once our laboratory or the community confirms those candidates as the targets, the compound screening\cite{Yang2004}\cite{Hsu2011}\cite{Pathak2021} could facilitate more individualized therapy for HNSCC patients.
 %and improve prognosis.
-
-\subsubsection{Holistic cancer care}
-Bruce Lipton: the biology of belief 信念的力量
-biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
-那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。
-也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。所以我們的科學家依舊在研究，基因對癌症的影響（單向）。
-冤親債主的意念
+% 1.
+Pathak, N.
+et al.
+Uncovering flexible active site conformations of SARS-COV-2 3Cl proteases through protease pharmacophore clusters and covid-19 drug repurposing.
+ACS Nano 15, 857–872 (2021).
+陽明交大
+
+\subsubsection{Holistic cancer care} % by epigenetic control (placebo), person-central approach, PCA
+
 TCGA treated by surgery and more; TNM available yes
@@
 
-Lipton 1992, epinephrine and histamine signals in endothelium, 心智作用
+Lipton introduced mind-brain-body system.
+Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
+ In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
+dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.
+
+Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
 The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
-
-[Results] In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+Bruce Lipton: the biology of belief %信念的力量
+placebo effect and the old belief of genetic determinism\cite{Gustafson2017}
+%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
+%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
+genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
+The genetics of the cell give us all kinds of potentials. % 自性空
+
+%冤親債主的意念 unknown X factors
+[Results] In summary, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
 Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
@@
 %癌症與身心靈的重要關係：中醫、citation? emotional centered approach
+
 PCA and ECA
@@
 placebo-effect influence on drug discovery
-博士班學生，越研究越發現，科學的不足
-，心理與靈性的力量，更是背後推動的冥冥力量
-身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
+博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
 
@@
 
-prefrontal lobe 理智腦 意識 正念 杏仁核
+prefrontal lobe 理智腦 意識 正念 杏仁核 prefrontal cortex runs conscious mind
 「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
@@
 
-Warburg effect and carcinogenesis
-cancer therapy by 患者自癒
-Mindfullness Meditation help 復原力（resilience）
-Self-Compassion  慈悲
-Self-compassion 
-除我執
- global self-esteem:
-自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
-
 中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
@@
 mindfulness and meditation for cancer
+% 人的腦波一般分為β（12-30Hz）、α(8-12Hz）、θ(4-8Hz)、δ（1-4Hz)，四種波。當我們處於清醒、警覺狀態時，腦波是處於高頻率的β波。隨著身心狀態逐漸放鬆，卸下防衛時，腦波頻率也會逐漸下降至α、θ波，此時身心狀態是處於最寧靜、創造能力最好、對事情洞察能力最佳的狀態。如果能夠安祥進入睡眠階段，則腦波會降至δ波。靜坐時不僅可以使腦波由快速的β波降至α、θ波
+In human EEG studies, cortical theta wave (4–7 Hz) tends to appear during meditative, drowsy, hypnotic or sleeping states in older children and adults.
+Theta is a frequency lower than consciousness.
+Theta is actually a brain function associated with imagination.
+
+Warburg effect and carcinogenesis
+cancer therapy by 患者自癒
+Mindfullness Meditation help 復原力（resilience）
+Self-Compassion  慈悲
+Self-compassion 
+除我執
+ global self-esteem:
+自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
+%%%% healing and cure
+Reprogramming cells:
+Environmental signals controlling cell behavior and cell behavior include genetics.
+The environmental signal via signal transduction can go into the nucleus and selectively change the reading of our gene, epigenetics regulation.
+
+the membrane proteins and the chromosomal proteins that control the DNA, called regulatory proteins. But even those proteins are controlled by environmental signals. It is not DNA to RNA to protein.
+
+The new understanding is: environmental signals to regulatory protein to DNA to RNA and then to protein.
+
+療癒 There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process.
+After 8 hours of meditation, the activity of the genes changed.
+You can change your genetic activity by how you change your response to the environment.
+
+to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.
+
+Becoming aware of the subconscious source of our behavior gives us an opportunity to change our lives by rewriting the programs (in subconscious mind) of limitation or the things that interfere with us.
+
+愛自己、蜜月；其實是 正念 mindfulness (因為自他不二）
+You are creating a world of joy and love, and that’s called the honeymoon. When we fall in love, we stop focusing our conscious mind in thought and start keeping it present. 
+It is called being mindful. 
+You’ve been looking for yourself your whole life.
+愛、性、正念止觀
+Science has recognized that immediately after falling in love, we enter a period of mindfulness where we keep our conscious mind present.
+
+You start running programs that are based on your conscious wishes and desires. All of a sudden, without the programs—without the subconscious programs—we begin to experience a heavenly life.
+%%%%
+
 情志養生 悲喜憂思苦 七情
@@
 
+%%%%%% carcinomgenesis
+95\% of cognitive behavior runs on subconscious program:
+
+7\% 對於健康有不良影響 => 但是惡劣競爭下的生存技能
+Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage.
+These programs were acquired from other people, not from ourselves.
+Again, being subconscious, these programs are occurring without conscious recognition and awareness.
+It effects on epigenetic regulation.
+
+Less than 1\% of disease is associated with genetics.
+Over 90\% of disease is a total reflection of environment and especially our programming: the disempowering, self-sabotaging behaviors that we acquired in the first 7 years.
+
+Genes are not self-actualizing.
+The control of genes is not due to any inherent activity in the DNA itself.
+The change of genetic activity is due to the interaction of the cell with environmental signals.
+
+the cell membrane through receptors picking up the signals and translating them into biology, which then sends signals into the nucleus, which then controls the genetic activity.
+
+%%%%%
+
 ground truth Y (e.x. patient's survival):\\[0.5cm]
@@
 Dali Lama
+
+*** TCPA with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
+佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。
+
+在生物醫學領域，氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。
 

### 2021-02-25 main.tex
Updates from Overleaf

@@
 
+\subsubsection{TCPA validation}
+TCGA pathology Deep learning TCPA
+數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
+
+https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
+% NCI
+NCI:
+
+Aiding the Genomic Characterization of Tumors
+
+AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
+For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas.
+Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.
+
+Understanding the Method Behind the Machine
+
+One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process.
+For example, a DL algorithm that predicts the optimal treatment for a patient does not provide the reasoning it used to make that prediction.
+Additional efforts are needed to reveal how algorithms arrive at a decision or prediction so that the process becomes transparent to scientists and clinicians.
+Making these algorithms transparent could help researchers identify new biological features relevant to disease diagnosis or treatment.
+
+Incorporating information about biological processes into the algorithm is likely to improve its accuracy and decrease dependence on large amounts of annotated data, which may not be available.
+One danger of the “black box” problem is that DL may inadvertently perpetuate existing unconscious biases.
+Researchers need to carefully consider how potential biases affect the data being used to develop a model, adopt practices to address and monitor those biases, and monitor performance and applicability of AI models.
+
+With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk.
+
+Updated: August 31, 2020
+%
+TMA by deep learning (CNN) mRNA expression associated with pathological images
+
+recurrent neural network for NLP
+%氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。
+
 \subsubsection{Holistic cancer care} % by epigenetic control (placebo), person-central approach, PCA
@@
 Bruce Lipton: the biology of belief %信念的力量
-placebo effect and the old belief of genetic determinism\cite{Gustafson2017}
+placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
 %biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
 %那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
+
+%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
+As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life.
+I have experienced unjustified conflicts in my social relations, feeling stale in mind and body, indefinite self-image, emotional instability, and successive spontaneous bleeds despite the continuous factor replacement.
+My research is based on my experience of living with hemophilia for 37 years, reading countless books on personal development and the mind-body relationship, and having profound discussions about these experiences with my wife.
+Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds.
+These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment.
+Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings.
+Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors.
+As Dr.
+Bruce Lipton explains in his book, 'The Biology of Belief': DNA does not control our biology; instead DNA is controlled by signals from outside the cell.
+Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows.
+New holistic approaches should be considered for treating PWH as a complete synchronized system of Soul, Mind, and Body; treatment should include more than just factor adjustment.
+Factor adjustment only treats symptoms, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}
+
+%%
+
 genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）

### 2021-02-25 main.tex
TCIA

@@
 
-\subsubsection{TCPA validation}
-TCGA pathology Deep learning TCPA
+\subsubsection{TCIA validation}
+https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
+https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
+TCGA Pathology Images (TCIA) Deep learning
 數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
+image-based phenotypes and their underlying genomic data 
+https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
+https://github.com/Serian1992/ImgBio.
+
+The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
+https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447
 
@@
 TMA by deep learning (CNN) mRNA expression associated with pathological images
-
+*** TCGA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
 recurrent neural network for NLP
-%氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。
-
-\subsubsection{Holistic cancer care} % by epigenetic control (placebo), person-central approach, PCA
+
+佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。
+
+%在生物醫學領域，氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。
+
+\subsubsection{Holistic cancer care} 
+% by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system.
+% person-central approach, PCA; Cullen, Carl Rogers
 
@@
 
-Lipton introduced mind-brain-body system.
+%%
+Bruce Lipton introduced mind-brain-body system.
 Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
@@
 
+%%%
 PCA and ECA
@@
 
-%%%%%% carcinomgenesis
+%%%%%% carcinogenesis
+mind-brain-body axis: subconscious fear -> inflammatory and stress hormones -> DNA/methylation mutation/mRNA expression alteration -> carcinogenesis of cancer.
 95\% of cognitive behavior runs on subconscious program:
 
-7\% 對於健康有不良影響 => 但是惡劣競爭下的生存技能
+7\% 對於健康有不良影響 => 卻是惡劣競爭下的生存技能
 Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage.
@@
 Dali Lama
-
-*** TCPA with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
-佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。
-
-在生物醫學領域，氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。
 

### 2021-02-26 main.tex
TCIA Schmauch, B., Romagnoni, A., Pronier, E., Saillard, C., Maillé, P., Calderaro, J., … Wainrib, G. (2020). A deep learning model to predict RNA-Seq expression of tumours from whole slide images. Nature Communications, 11(1), 3877. https://doi.org/10.1038/s41467-020-17678-4

@@
 https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
-TCGA Pathology Images (TCIA) Deep learning
-數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
+TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Keras framework)
+%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
 image-based phenotypes and their underlying genomic data 
@@
 
-The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
-https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447
+%The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
+%https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447; there is few HNSCC slides
 
@@
 % NCI
-NCI:
-
-Aiding the Genomic Characterization of Tumors
-
-AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
+Aiding the Genomic Characterization of Tumors: 
+deep learning could predict commonly mutated genes and mRNA expression from the images
+*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
+Preprocessing of whole-slide images.
+The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets.
+We divided the whole-slide images into squares of 112 × 112 μm (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
+We sampled a maximum of 8000 such tiles from each slide.
+We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
+For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster.
+The use of these supertiles reduces the dimensions of a slide to 100 × 2048.
+The model was first trained on this reduced dataset, with all the TCGA data.
+Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.
+
+%AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
 For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas.
@@
 Understanding the Method Behind the Machine
-
-One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process.
+interpredability
+
+%One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process.
 For example, a DL algorithm that predicts the optimal treatment for a patient does not provide the reasoning it used to make that prediction.
@@
 Making these algorithms transparent could help researchers identify new biological features relevant to disease diagnosis or treatment.
-
+***  unconscious biases:
 Incorporating information about biological processes into the algorithm is likely to improve its accuracy and decrease dependence on large amounts of annotated data, which may not be available.
@@
 
-With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk.
-
+%With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk.
 Updated: August 31, 2020
@@
 TMA by deep learning (CNN) mRNA expression associated with pathological images
-*** TCGA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
+*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
 recurrent neural network for NLP
 
-佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。
+%佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。
 

### 2021-02-27 main.tex
holistic to PCA

@@
 Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
-% *** why here?
+% *** yes here
 In our previous work, altered glucose metabolism (e.k.a.
@@
 Before the global genes scanning process, it is necessary to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
-This process should be carefully curated to confirm the data integrity within the correct definition.
+This process should be carefully curated to confirm the data integrity within the correct definition\cite{Rendleman2019}.
 We also plan to upgrade our R script of the cutoff engine to the C++ language and source it in the Rstudio server.
@@
 
+*** interpretable or explainable CNN
+
 https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
@@
 
+%the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+%with more TCGA features (holistic)
+
 \subsubsection{Holistic cancer care} 
-% by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system.
-% person-central approach, PCA; Cullen, Carl Rogers
-
-TCGA treated by surgery and more; TNM available yes
-discussion: limitation
-Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
- since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
-the TCGA does not collect holistic features
-Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
-or even spiritual, emotional, and social status) go holistic
-
-World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}.
+% carcinogenesis by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system.
+(gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$)
+% cancer care with person-central approach, PCA; Cullen, Carl Rogers
+
+%TCGA treated by surgery and more; TNM available yes
+
+%discussion: the third limitation
+Even there are eighty one ($X_1 ... X_81$) physical, pathological and social features of patients available for survival modelling in the TCGA, 
+% since it has comprehensive clinical features, 
+such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon, the TCGA did not collect other holistic features from their participants.
+% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equal important comparing with physical and social status.
+%
+World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
 Core principles can be taken to achieve people-centred and integrated health service delivery. 
 First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being. 
-(Holistic care: care to the “whole person” that considers psychological, social and environmental factors rather than just the symptoms of disease or ill-health)
+Holistic care: care and see the person as a whole with psychological, social and environmental levels of needs and goals.
+%that considers  factors rather than just the symptoms of disease or ill-health.
 Second principle is Empowering – supporting people to manage and take responsibility for their own health. 
-(Empowerment: the process of supporting people and communities to take control of their own health needs resulting, for example, in the uptake of healthier behaviours or the ability to self- manage illnesses)
+Empowerment: the process of supporting people and communities to take control of their own health needs resulting, for example, in the uptake of healthier behaviours or the ability to self-manage illnesses.
 People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
-Glossary:
+%Glossary:
 %People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways.
@@
 %Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
-(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)
-
-The spiritual care is he key of holistic healthcare in dental practice or for cancer patient.
+%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)
+
+The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} or even for cancer patient.
 Being mindful to patient’s mental health and emotional changes during the dental care.
 Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration.
-Learning to listen proactively
-9) Therapeutic relationship is an essential key towards spiritual care.
+Learning to listen proactively.
 Being aware of patient’s spiritual needs during/after treatment.
-12) Applying the holistic healthcare strategies, such as the Shared Decision Marking, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}
-
-%%
-Bruce Lipton introduced mind-brain-body system.
-Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
- In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
-dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.
-
-Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
-The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
-Bruce Lipton: the biology of belief %信念的力量
-placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
-%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
-%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
-
-%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
-As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life.
-I have experienced unjustified conflicts in my social relations, feeling stale in mind and body, indefinite self-image, emotional instability, and successive spontaneous bleeds despite the continuous factor replacement.
-My research is based on my experience of living with hemophilia for 37 years, reading countless books on personal development and the mind-body relationship, and having profound discussions about these experiences with my wife.
-Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds.
-These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment.
-Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings.
-Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors.
-As Dr.
-Bruce Lipton explains in his book, 'The Biology of Belief': DNA does not control our biology; instead DNA is controlled by signals from outside the cell.
-Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows.
-New holistic approaches should be considered for treating PWH as a complete synchronized system of Soul, Mind, and Body; treatment should include more than just factor adjustment.
-Factor adjustment only treats symptoms, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}
-
-%%
-
-genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
-The genetics of the cell give us all kinds of potentials. % 自性空
-
-%冤親債主的意念 unknown X factors
-[Results] In summary, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
-Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
-The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
-依舊是以管窺天
-% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
-%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
-
-%%%
-PCA and ECA
-Carl Rogers: Carl Rogers' person-centered theory
-the therapist is providing the appropriate social-environmental conditions \cite{Rogers1957}.\cite{Joseph2004}\cite{Griffiths2013}
-Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers\cite{Rogers1957}.
-The research implication is to investigate the relationship between the client’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
+%Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}
+
+%% PCA and ECA
+Therapeutic relationship is an essence towards spiritual care.
+Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
+Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}.
+The research implication is to investigate the relationship between the patient’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
 Dealing with negative emotions.
-As the client feels intense negative emotions of fear, despair, sadness and so on, it is not the client-centred therapist’s task to try and remove these feelings: The task is simply to stay with the client’s experiences.
-T he research implication is to investigate the necessity and sufficiency of the six conditions.
-
-Rogers, C.
+As the patient feels intense negative emotions of fear, despair, sadness and so on, it is not the patient-centred therapist’s task to try and remove these feelings: The task is simply to stay with the patient’s experiences.
+%The research implication is to investigate the necessity and sufficiency of the six conditions.
+%Rogers, C.
 R.
@@
 Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
-% http://bibliotecaparalapersona-epimeleia.com/greenstone/collect/ecritos2/index/assoc/HASH01a5/4583605e.dir/doc.pdf
-
-% so do the cancer
-Individual treatment and avoiding assumptions.
-Although it is useful for therapists to have a knowledge of the trauma literature on the general reactions of people who experience trauma, the therapist should not assume that this knowledge necessarily applies to each and every client\cite{Joseph2004}.
-
-Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction,13,16 centred on a physician's therapeutic intentions and his attunement to patient sympathy.
-we educate them
-1.
-Mong, L.-C., Liao, F., Chiou, J.
-& Chiang, P.
-Tips for Integrating Spiritual Care Delivery in Dental Education.
-in Asia Pacific Medical Education Conference.
-Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}
-
-*** make Figure 5 holistic:
-meridian and emotion has mutual reaction
-meridian effect tissue and organ
-(autonomic nerve system, myofascial network, prefrontal cortex)
-placebo-effect influence on drug discovery
-博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
-
-騙過你的病-安慰劑效應 The Placebo Effect
-(Emmanuelle Sapin, Pascal Goblot)
-%1. Sapin, E. & Goblot, P. L’effet placebo (English: The Placebo Effect) [enregistrement vidéo] : le formidable pouvoir de l’auto-guérison. 53 PP-Quebec (Cinéfête, 2014).\cite{Sapin2014}
-% https://biblio.bdeb.qc.ca/in/sim/faces/details.xhtml;jsessionid=E3DD39109012D0BEA598E6E5B66A4FD2?id=p::usmarcdef_0000058243&posInPage=8
-1. Finniss, D. G. Placebo Effects: Historical and Modern Evaluation. in International review of neurobiology vol. 139 1–27 (2018).\cite{Finniss2018}
-%蓋倫劑量 placebo effect 身心靈醫學的核心
-In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo.
-If I had thought of any internal medicine it would have been a dose of the Dover's powders."\cite{Kerr2008}\cite{Finniss2018}.
- (made up of Ipecac and opium) 
- Cullen studied the objective science of analytical chemistry.
-He also sense that the patient's subjective, psychosomatic or ‘sympathetic constitution’ determined his reaction to a prescribed therapeutic substance.
-***Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
-Cullen's theory of sympathy is a mind-body function, a kind of ‘vital force’ that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
-This finely calibrated, rational use of active placebo treatment, in which the physician dispensed a weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
-%啟蒙運動
-
-%sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
-The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, whether by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
-placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
-醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
-安慰劑效應的研究，最後導向了良好醫病關係的思考，並成為醫生臨床醫術的元素之一：
-「醫師開藥時，其實是把自己當藥方開出去」。
-安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
-前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
-PCA理論
+
+%PCA理論
+治療關係的核心條件: 說好話 眼對眼 engaging 用真心
 以心印心 engaging
@@
 捨末求本
-the anterior cingulate cortex and the dorsolateral prefrontal cortex have been found to be activated by placebo administration.
-\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}
-But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}.
-Today, pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced\cite{Bennett2018}.
 身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，
@@
 「把自己當藥方開出去」
-#正念 減壓，療癒疼痛\cite{Krummenacher2010}\cite{Bennett2018}、免疫系統、內分泌系統或自律神經系統相關的疾病，以及憂鬱症、焦慮症 
-The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}
-
-prefrontal lobe 理智腦 意識 正念 杏仁核 prefrontal cortex runs conscious mind
-「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
-物理作用、信號，雷射針灸
-Therapeutic Relationship
-Spirituality
-慈悲心 compassion 
-同情心 sympathy
-同理心 empathy
-non-verbal contact
-前額葉內側 (medial prefrontal cortex)
-額葉底部(orbitofrontal cortex)
-治療關係的核心條件: 說好話 眼對眼 engaging 用真心
+
 empowering
@@
 
+%% why holistic?
 中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
@@
 七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
-
-repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
-
-mindfulness and meditation for cancer
-% 人的腦波一般分為β（12-30Hz）、α(8-12Hz）、θ(4-8Hz)、δ（1-4Hz)，四種波。當我們處於清醒、警覺狀態時，腦波是處於高頻率的β波。隨著身心狀態逐漸放鬆，卸下防衛時，腦波頻率也會逐漸下降至α、θ波，此時身心狀態是處於最寧靜、創造能力最好、對事情洞察能力最佳的狀態。如果能夠安祥進入睡眠階段，則腦波會降至δ波。靜坐時不僅可以使腦波由快速的β波降至α、θ波
-In human EEG studies, cortical theta wave (4–7 Hz) tends to appear during meditative, drowsy, hypnotic or sleeping states in older children and adults.
-Theta is a frequency lower than consciousness.
-Theta is actually a brain function associated with imagination.
-
-Warburg effect and carcinogenesis
-cancer therapy by 患者自癒
-Mindfullness Meditation help 復原力（resilience）
-Self-Compassion  慈悲
-Self-compassion 
-除我執
- global self-esteem:
-自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
-%%%% healing and cure
-Reprogramming cells:
-Environmental signals controlling cell behavior and cell behavior include genetics.
-The environmental signal via signal transduction can go into the nucleus and selectively change the reading of our gene, epigenetics regulation.
-
-the membrane proteins and the chromosomal proteins that control the DNA, called regulatory proteins. But even those proteins are controlled by environmental signals. It is not DNA to RNA to protein.
-
-The new understanding is: environmental signals to regulatory protein to DNA to RNA and then to protein.
-
-療癒 There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process.
-After 8 hours of meditation, the activity of the genes changed.
-You can change your genetic activity by how you change your response to the environment.
-
-to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.
-
-Becoming aware of the subconscious source of our behavior gives us an opportunity to change our lives by rewriting the programs (in subconscious mind) of limitation or the things that interfere with us.
-
-愛自己、蜜月；其實是 正念 mindfulness (因為自他不二）
-You are creating a world of joy and love, and that’s called the honeymoon. When we fall in love, we stop focusing our conscious mind in thought and start keeping it present. 
-It is called being mindful. 
-You’ve been looking for yourself your whole life.
-愛、性、正念止觀
-Science has recognized that immediately after falling in love, we enter a period of mindfulness where we keep our conscious mind present.
-
-You start running programs that are based on your conscious wishes and desires. All of a sudden, without the programs—without the subconscious programs—we begin to experience a heavenly life.
-%%%%
-
 情志養生 悲喜憂思苦 七情
@@
 
+%% why holistic?
+Bruce Lipton introduced mind-brain-body system.
+Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
+ In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
+dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.
+
+Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
+The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
+Bruce Lipton: the biology of belief %信念的力量
+placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
+%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
+%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
+
+%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
+As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life.
+I have experienced unjustified conflicts in my social relations, feeling stale in mind and body, indefinite self-image, emotional instability, and successive spontaneous bleeds despite the continuous factor replacement.
+My research is based on my experience of living with hemophilia for 37 years, reading countless books on personal development and the mind-body relationship, and having profound discussions about these experiences with my wife.
+Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds.
+These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment.
+Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings.
+Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors.
+As Dr.
+Bruce Lipton explains in his book, 'The Biology of Belief': DNA does not control our biology; instead DNA is controlled by signals from outside the cell.
+Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows.
+New holistic approaches should be considered for treating PWH as a complete synchronized system of Soul, Mind, and Body; treatment should include more than just factor adjustment.
+Factor adjustment only treats symptoms, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}
+
+%%
+
+genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
+The genetics of the cell give us all kinds of potentials. % 自性空
+
+%冤親債主的意念 unknown X factors
+[Results] In summary, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
+The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
+依舊是以管窺天
+% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
+%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
+
+% so do the cancer
+Individual treatment and avoiding assumptions.
+Although it is useful for therapists to have a knowledge of the trauma literature on the general reactions of people who experience trauma, the therapist should not assume that this knowledge necessarily applies to each and every client\cite{Joseph2004}.
+
+Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction,13,16 centred on a physician's therapeutic intentions and his attunement to patient sympathy.
+we educate them
+%1.
+Mong, L.-C., Liao, F., Chiou, J.
+& Chiang, P.
+Tips for Integrating Spiritual Care Delivery in Dental Education.
+in Asia Pacific Medical Education Conference.
+Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}
+
+%騙過你的病-安慰劑效應 
+The Placebo Effect (Emmanuelle Sapin, Pascal Goblot)
+%1. Sapin, E. & Goblot, P. L’effet placebo (English: The Placebo Effect) [enregistrement vidéo] : le formidable pouvoir de l’auto-guérison. 53 PP-Quebec (Cinéfête, 2014).\cite{Sapin2014}
+% https://biblio.bdeb.qc.ca/in/sim/faces/details.xhtml;jsessionid=E3DD39109012D0BEA598E6E5B66A4FD2?id=p::usmarcdef_0000058243&posInPage=8
+1. Finniss, D. G. Placebo Effects: Historical and Modern Evaluation. in International review of neurobiology vol. 139 1–27 (2018).\cite{Finniss2018}
+%蓋倫劑量 placebo effect 身心靈醫學的核心
+In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo.
+If I had thought of any internal medicine it would have been a dose of the Dover's powders."\cite{Kerr2008}\cite{Finniss2018}.
+ (made up of Ipecac and opium) 
+ Cullen studied the objective science of analytical chemistry.
+He also sense that the patient's subjective, psychosomatic or ‘sympathetic constitution’ determined his reaction to a prescribed therapeutic substance.
+***Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
+Cullen's theory of sympathy is a mind-body function, a kind of ‘vital force’ that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
+This finely calibrated, rational use of active placebo treatment, in which the physician dispensed a weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
+%啟蒙運動
+
+% how placebo effect works?
+安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
+前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
+the anterior cingulate cortex and the dorsolateral prefrontal cortex have been found to be activated by placebo administration.
+\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}
+But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}.
+Today, pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced\cite{Bennett2018}.
+
+%sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
+The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, whether by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
+placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
+醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
+安慰劑效應的研究，最後導向了良好醫病關係的思考，並成為醫生臨床醫術的元素之一：
+「醫師開藥時，其實是把自己當藥方開出去」。
+
+#正念 減壓，療癒疼痛\cite{Krummenacher2010}\cite{Bennett2018}、免疫系統、內分泌系統或自律神經系統相關的疾病，以及憂鬱症、焦慮症 
+The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}
+
+prefrontal lobe 理智腦 意識 正念 杏仁核 prefrontal cortex runs conscious mind
+「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
+物理作用、信號，雷射針灸
+Therapeutic Relationship
+Spirituality
+慈悲心 compassion 
+同情心 sympathy
+同理心 empathy
+non-verbal contact
+前額葉內側 (medial prefrontal cortex)
+額葉底部(orbitofrontal cortex)
+
+*** make Figure 5 holistic:
+meridian and emotion has mutual reaction
+meridian effect tissue and organ
+(autonomic nerve system, myofascial network, prefrontal cortex)
+placebo-effect influence on drug discovery
+博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
+
+repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
+
+mindfulness and meditation for cancer
+% 人的腦波一般分為β（12-30Hz）、α(8-12Hz）、θ(4-8Hz)、δ（1-4Hz)，四種波。當我們處於清醒、警覺狀態時，腦波是處於高頻率的β波。隨著身心狀態逐漸放鬆，卸下防衛時，腦波頻率也會逐漸下降至α、θ波，此時身心狀態是處於最寧靜、創造能力最好、對事情洞察能力最佳的狀態。如果能夠安祥進入睡眠階段，則腦波會降至δ波。靜坐時不僅可以使腦波由快速的β波降至α、θ波
+In human EEG studies, cortical theta wave (4–7 Hz) tends to appear during meditative, drowsy, hypnotic or sleeping states in older children and adults.
+Theta is a frequency lower than consciousness.
+Theta is actually a brain function associated with imagination.
+
+Warburg effect and carcinogenesis
+cancer therapy by 患者自癒
+Mindfullness Meditation help 復原力（resilience）
+Self-Compassion  慈悲
+Self-compassion 
+除我執
+ global self-esteem:
+自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
+%%%% healing and cure
+Reprogramming cells:
+Environmental signals controlling cell behavior and cell behavior include genetics.
+The environmental signal via signal transduction can go into the nucleus and selectively change the reading of our gene, epigenetics regulation.
+
+the membrane proteins and the chromosomal proteins that control the DNA, called regulatory proteins. But even those proteins are controlled by environmental signals. It is not DNA to RNA to protein.
+
+The new understanding is: environmental signals to regulatory protein to DNA to RNA and then to protein.
+
+療癒 There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process.
+After 8 hours of meditation, the activity of the genes changed.
+You can change your genetic activity by how you change your response to the environment.
+
+to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.
+
+Becoming aware of the subconscious source of our behavior gives us an opportunity to change our lives by rewriting the programs (in subconscious mind) of limitation or the things that interfere with us.
+
+愛自己、蜜月；其實是 正念 mindfulness (因為自他不二）
+You are creating a world of joy and love, and that’s called the honeymoon. When we fall in love, we stop focusing our conscious mind in thought and start keeping it present. 
+It is called being mindful. 
+You’ve been looking for yourself your whole life.
+愛、性、正念止觀
+Science has recognized that immediately after falling in love, we enter a period of mindfulness where we keep our conscious mind present.
+
+You start running programs that are based on your conscious wishes and desires. All of a sudden, without the programs—without the subconscious programs—we begin to experience a heavenly life.
+%%%%
+
 %%%%%% carcinogenesis
@@
 $Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
-
+gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$
 There is much work to be done in investigating the functional relationships more fully.\cite{Rogers1959}
+We wish the TCGA does collect holistic features from their participants in the future. % electric healthcare record, EHR, enabled in holistic way
 
@@
 
-the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
-with more TCGA features (holistic)
 Impact of stress on cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}

### 2021-02-27 main.tex
holistic chart

@@
 靈性功力
-治療關係
+治療關係: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
 I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
@@
 We wish the TCGA does collect holistic features from their participants in the future. % electric healthcare record, EHR, enabled in holistic way
+Deep Patient
+
+We design a #holisticDental chart in our outpaitent department for Psycho-Social-Spiritual Evaluation\cite{Ling-ChengMong2021}.:
+1. Emotional: stable/depression/ anxiety/ agitated/ perplexed
+2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment
+3. Social: (disturbing living/ disturbing working/ disturbing other life aspect) by present illness
+4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind
+5. Self-expectation: lack of confidence/ low self-esteem/ social-withdrawal
+6. Impact to life: financial problem/ family problem
+7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment 
+side-effects/ litigation experience
+8. Other aspects
+/no other specific issues
 

### 2021-03-05 main.tex
add items from 2021/03/01

@@
 *** interpretable or explainable CNN
-
+Manning meap book: 不再是黑盒子
+https://www.manning.com/books/trust-in-machine-learning
+Trust in Machine Learning
+
+*** 必備 explainable interpretable 
+By saliency mapping: e.x. diabetes retinopathy, model focused on retinal aterry
+
+https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
+#XAI
+Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data
+
+Jie Hao, 2019
+By PyTorch
+
+https://www.deeplearningbook.org/
 https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
@@
 %discussion: the third limitation
-Even there are eighty one ($X_1 ... X_81$) physical, pathological and social features of patients available for survival modelling in the TCGA, 
+There are eighty one ($X_1 ... X_81$) physical, pathological and social features of patients available for survival modelling in the TCGA, 
 % since it has comprehensive clinical features, 
-such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon, the TCGA did not collect other holistic features from their participants.
+such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon.
+However, the TCGA did not collect other holistic features from their participants.
 % Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
@@
 
+% ***七星山的 idea [2021/03/01]
+Generative adversarial networks simulate gene expression and predict perturbations in single cells
+3.1. Gene expression in \cite{Ching2018} % deep review
+% 環境 -> chromosome accessibility
+%  unsupervised deep learning algorithm
+generative adversarial networks (GAN) with VAE (variational autoencoder) could simulate environment causing carcinogenesis
+%graph convolutional network (from deepchem import GraphConvModel)
+deep or graph convolutional network in gene regulation, which includes chromosome accessibility, transcription factor binding site, DNA methylation, and RNA inhibitions (RNAi, microRNA, LncRNA).
+
+%GAN overview
+In this paper compares GAN with VAE (variational autoencoder) and RBM (restricted Boltzmann machine) models.
+As a new unsupervised learning algorithm framework, generative adversarial networks (GAN) has been favored by more and more researchers, and it has become a research hotspot.
+GAN is inspired by the two-person zero-sum game theory in game theory.
+Its unique confrontation training idea can generate high-quality samples and has more powerful feature learning and feature expression ability than traditional machine learning algorithms.
+At present, GAN has achieved remarkable success in the field of computer vision, especially in the field of sample generation.
+%Learning Generative Models of Tissue Organization with Supervised GANs
+\cite{Han2018}
+
+%https://www.amazon.com/Deep-Learning-Life-Sciences-Microscopy-ebook/dp/B07QM3G5JM
+
+%book: https://github.com/deepchem/DeepLearningLifeSciences
+%https://github.com/deepchem/torchchem
+
+%https://github.com/hindupuravinash/the-gan-zoo
+
 %%%%%
@@
 There is much work to be done in investigating the functional relationships more fully.\cite{Rogers1959}
-We wish the TCGA does collect holistic features from their participants in the future. % electric healthcare record, EHR, enabled in holistic way
+We wish the TCGA does collect holistic features from their participants in the future.
+
+holistic-enabled Electric healthcare record, EHR
 Deep Patient
+Under HL7, RESTful
+deep learning by EHR-converted FHIR: with holistic observations
+=> Level 4 Record-keeping and Data Exchange for the healthcare process
+(clinical data)
+Allergy, Problem,
+Procedure,
+CarePlan/Goal,
+ServiceRequest,
+Family History,
+Risk Assessment (APGAR, Glasgow coma scale)
+condition: physical, mental
+{observations: 
+vital signs, 
+body temperature, body weight and body height, 
+x-ray, 
+laboratory data, 
+pulse oximetry, 
+ECG, EEG, EMG, 
+clinical findings (symptom and sign), 
+tobacco exposure, family support, cognitive status
+pregnancy status
+death assertion
+HIV, HBV, HCV status
+}
+
+%https://mos2718.github.io/FHIRspec/Index.html
+%https://www.hl7.org/fhir/patient.html
+%https://mos2718.github.io/FHIRspec/Spec/Patient/EHR_Patient.docx
 
@@
 /no other specific issues
+
+In personal history section of admission note (EHR for inpatient): 
+< Habits >
+　　　　-Tobacco:
+　、　1.5　pack/day for　30　years
+　　　　-Alcohol drinking:　Occasionally
+　　　　-Betel nuts:　、　nuts/day for　30　years　
+　　< Social/Economic Evaluation >
+　　　　-Living condition:　Living with family
+　　　　-Family support:　Well
+　　　　-Main caregiver:　Spouse
+　　　　-Financial support:　Sufficient
+　　< Psychological Evaluation >
+　　　　Stable
+　　　　Suspected to be ” abuse ” or ”neglected victim” (if the answer is “Yes“ should be assisted by social workers)　No
+　　< Spiritual Assessment >
+　　　　Religion:　Nil
+　　　　Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers?　No
 

### 2021-03-05 main.tex
%慈悲心 利他心

@@
 
-The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} or even for cancer patient.
+The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} or even more for cancer patient.
 Being mindful to patient’s mental health and emotional changes during the dental care.
@@
 ***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
-諮商員的
-靈性功力
-治療關係: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
+諮商員的靈性功力
+%治療關係: 
+Therapeutic relationship: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
 I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
@@
 
-%% why holistic?
+%% why holistic? % Environment 環境
 Bruce Lipton introduced mind-brain-body system.
@@
 
-%%
-
+%% Environment 環境
 genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
@@
 
-% how placebo effect works?
+% how placebo effect works? % Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
 安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
@@
 博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
-
+Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
+
+% cancer cure (care) 的證明
 repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
@@
 
-Wish and bless the whole world
-Dali Lama
+Dali Lama: Wish and bless the whole world %慈悲心 利他心
+% 多了解身心靈的關係，減少癌症對健康的損害
 

### 2021-03-08 main.tex
PCA

@@
 %discussion: the third limitation
-There are eighty one ($X_1 ... X_81$) physical, pathological and social features of patients available for survival modelling in the TCGA, 
+There are eighty one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modelling in the TCGA, 
 % since it has comprehensive clinical features, 
 such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
-However, the TCGA did not collect other holistic features from their participants.
-% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
+However, the TCGA did not collect other features in holistic cancer care.
+% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
 Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equal important comparing with physical and social status.
@@
 First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being. 
-Holistic care: care and see the person as a whole with psychological, social and environmental levels of needs and goals.
+Holistic care is defined that care and see the person as a whole with psychological, social and environmental levels of needs and goals.
 %that considers  factors rather than just the symptoms of disease or ill-health.
-Second principle is Empowering – supporting people to manage and take responsibility for their own health. 
-Empowerment: the process of supporting people and communities to take control of their own health needs resulting, for example, in the uptake of healthier behaviours or the ability to self-manage illnesses.
+Second principle is empowering – supporting people to manage and take responsibility for their own health,
+%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
+for example, in the uptake of healthier behaviours or the ability to self-manage illnesses.
 People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
@@
 
-The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} or even more for cancer patient.
-Being mindful to patient’s mental health and emotional changes during the dental care.
-Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration.
+The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
+Being mindful to patient’s mental health, emotional changes, socioeconomic during healthcare.
+%Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration.
 Learning to listen proactively.
-Being aware of patient’s spiritual needs during/after treatment.
+Being aware of patient’s spiritual needs.
 %Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}
-
-%% PCA and ECA
+% mindfulness-based cognitive therapies [MBCT]
+%%%% MBSR "念" 今天的心 專心才有幸福感(味覺嗅覺靈敏專心吃
+Mindfulness-Based Stress Reduction (MBSR) program has been introduced by Jon Kabat-Zinn in 1979\cite{Niazi2011}.
+MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes the development of a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation.
+It employs (static) mindfulness meditation to alleviate suffering associated with physical, psychosomatic and psychiatric disorders.
+%是1979年麻薩諸塞大學的榮譽教授Jon Kabat-Zinn => 佛教禪修的mindfulness 正念止觀（中譯建譯：自我覺察）帶入西方身心醫學及心理學領域。
+The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage mindfulness and self-awareness.
+
+%Search Inside Yourself was born at Google in 2007 when one of Google’s earliest engineers, Chade-Meng Tan, gathered a team of leading experts in mindfulness, neuroscience, leadership and emotional intelligence to develop an internal course for fellow Google employees lovingly called Search Inside Yourself (SIY).
+
+% 目的與功效
+%  出入息 呼吸念頭 回到覺知，不再被潛意識自動導航干擾情緒
+%正念，放下二元評價 正念覺知 XAI saliency mapping and trustworthiness in deep learning
+%覺知 漸入空性 Y=wX + bias
+%解決情緒苦(七情) 四聖諦
+%慈悲心 安心（情緒穩定）
+%了卻見人苦的「慈悲心」易感者同理心 empathy
+%道歉不是一段文字，不是一個儀式（療癒冤親債主來自慈悲心）
+%冤親債主 決定不再影響環境 基因 expression，減少意外與疾病、癌症
+A systematic review of spiritually based interventions and psychoneuroimmunological outcomes in breast cancer survivorship was reported by Hulett et al.\cite{Hulett2016}. 
+%Objective This is a review of spiritually based interventions (eg, mindfulness-based stress reduction, MBSR) that utilized psychoneuroimmunological (PNI) outcome measures in breast cancer survivors.
+Specifically, this review sought to examine the evidence regarding relationships between spiritually based interventions, psychosocial-spiritual outcomes, and biomarker outcomes in breast cancer survivors.
+%Methods A systematic search of 9 online databases was conducted for articles of original research, peer-reviewed, randomized and nonrandomized control trials from 2005-2015.
+Data were extracted in order to answer selected questions regarding relationships between psychosocial-spiritual and physiological measures utilized in spiritually based interventions.
+Implications for future spiritually based interventions in breast cancer survivorship are discussed.
+Results Twenty-two articles were reviewed.
+%mindfulness-based cancer recovery (MBCR) 
+Psychosocial stress is associated with cancer incidence and poor survival\cite{Chida2008}.
+This impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
+Thus, cortisol is one of the most common (objective) outcome studied in psychoneuroimmunological (PNI) factors.
+% others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV
+The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
+%  body-mind-spirit (BMS) group therapy in the Meaning in Life questionnaire (MLQ) including two sub-scales: MLQ-Presence and MLQ-Search.
+% The MLQ [15] for measuring psychological well-being consists of two subscales: the 5-item MLQ-Presence subscale, measuring the subjective sense that one’s life is meaningful, and the 5-item MLQ-Search subscale, measuring the drive and orientation toward finding meaning in one’s life.
+%Compared with control groups, intervention groups demonstrated positive mental health outcomes and improved or stable neuroendocrine-immune profiles, although limitations exist.
+%Design methods have improved with regard to increased use of comparison groups compared with previous reviews.
+There are few spiritually based interventions that specifically measure religious or spiritual constructs.
+Similarly, there are few existing studies that utilize standardized religious or spiritual measures with PNI outcome measures.
+Findings suggest that mindfulness-breathing-stretching interventions appear to offer potential improvement or stabilization of neuroendocrine-immune activity in breast cancer survivors compared to control groups.
+This review revealed a positive pattern between spiritually based interventions and a number of PNI biomarker outcomes, suggesting that spiritually based interventions offer positive mental and physiological health benefits.
+For breast cancer survivors, these studies suggested that engaging in spiritually based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.
+%From a PNI perspective, future spiritually based interventions should include standardized measures of religiousness and spirituality in order to understand relationships between and among religiousness, spirituality, and neuroendocrine-immune outcomes.
+Future research should now focus on determining the minimum dose and duration needed to improve or stabilize neuroendocrine-immune function, as well as
+%diverse setting needs, including tele-medicine practice for survivors who are too ill to travel to group sessions or lack economic resources.
+
+% 自動導航（潛意識）易受情緒影響，造成焦慮、發炎、免疫 Cancer
+%Mindfulness based stress reduction provides psychological benefit and restores immune function of women newly diagnosed with breast cancer: A randomized trial with active control.
+%BACKGROUND: Women newly diagnosed with breast cancer experience psychological distress, accompanied by reduced Natural Killer Cell Activity (NKCA) and altered levels of cytokines, which may compromise cancer control.
+Few studies have evaluated psycho-immune outcomes of mindfulness-based stress reduction (MBSR) for women newly diagnosed with breast cancer in comparison to an active control condition.
+OBJECTIVE: The purpose of this study was to determine whether MBSR benefits psychological, behavioral, and immunological function in women recently diagnosed with breast cancer.
+DESIGN: After confirmation of breast cancer staging, women diagnosed with early-stage breast cancer (n = 192) were randomized to an 8-week MBSR program or an 8-week active control condition (ACC).
+The ACC consisted of a series of cancer recovery and health education classes.
+Both MBSR and the ACC were administered in group format.
+METHODS: Women completed psychometric instruments and provided blood for NKCA and cytokine levels at pre-, mid-, and completion of program, as well as at 1- and 6-months post-program.
+One hundred and twenty four women completed all five-assessments (MBSR, n = 63; ACC, n = 61).
+Hierarchical linear modeling was used to analyze trajectories of outcomes over time and between groups.
+%RESULTS: Compared to the ACC group, women randomized to MBSR exhibited decreasing trajectories of perceived stress, fatigue, sleep disturbance, and depressive symptoms. 
+%Further, compared to women randomized to ACC, MBSR women exhibited trajectories demonstrating significantly more rapid restoration of NKCA, accompanied by 
+%lower circulating TNF-alpha levels, lower IL-6 production =>  pro-inflammatory cytokines
+%and greater IFN-gamma production => IFN gamma supports an immune-mediated response against cancer and this may be important during the transition following cancer treatment
+A randomized clinical trial with active control proved that early provision of MBSR for women newly diagnosed with breast cancer provides psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) supportive of cancer survival.\cite{WitekJanusek2019}
+
+%%%% PCA and ECA: the delivery of MBSR
 Therapeutic relationship is an essence towards spiritual care.
@@
 Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}.
-The research implication is to investigate the relationship between the patient’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
-Dealing with negative emotions.
-As the patient feels intense negative emotions of fear, despair, sadness and so on, it is not the patient-centred therapist’s task to try and remove these feelings: The task is simply to stay with the patient’s experiences.
+For constructive personality change to occur, it is necessary that these
+conditions exist and continue over a period of time: 
+1. Two persons are in psychological contact. 
+2. The first, whom we shall term the client, is in a state of incongruence, being vulnerable or anxious. 
+3. The second person, whom we shall term the therapist, is congruent
+or integrated in the relationship. 
+4. The therapist experiences unconditional positive regard for the client. 
+5. The therapist experiences an empathic understanding of the client's
+internal frame of reference and endeavors to communicate this experience to the client. 
+6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.
+
+%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
+As the cancer patient feels intense negative emotions of fear, depression, stress, anxiety, fatigue, sadness, it is not the patient-centred therapist’s task to remove these feelings: The task is simply to stay with the patient’s experiences.
 %The research implication is to investigate the necessity and sufficiency of the six conditions.
@@
 
-%% why holistic?
+%% why holistic? 太極 氣功 情緒 myofascia and sympathetic system
 中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
@@
 The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
+
+gene expression in deep learning
+Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).\cite{Ching2018}
+%慈悲心 利他心
+*** make Figure 5 holistic:
+meridian and emotion has mutual reaction
+meridian effect tissue and organ
+(autonomic nerve system, myofascial network, prefrontal cortex)
+placebo-effect influence on drug discovery
+博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
+#正念 除了可以減壓，還可以治癒疼痛
+Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
+
 Bruce Lipton: the biology of belief %信念的力量
@@
 　　　　
+　　　　suggested TCGA features:
+cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors.
+Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
+The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
+ psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6)
 how to do: once holistic feature available, graph convolutional neural network (GCNN) is mandatory: 以免 genomics 光芒萬丈

### 2021-03-08 main.tex
Updates from Overleaf

@@
 6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.
+%empowering
+%(一)雙方有心理的接觸。
+%(二)當事人正感到焦慮或不一致(incongruence)。 
+%(三)治療者在治療關係中是一致的、真實的或真誠的。
+%(四)治療者能夠對當事人表現出無條件的正向關懷。
+%(五)治療者能夠同理的瞭解當事人的內在，
+%(六)並努力傳達「我懂你的」。
 
@@
 As the cancer patient feels intense negative emotions of fear, depression, stress, anxiety, fatigue, sadness, it is not the patient-centred therapist’s task to remove these feelings: The task is simply to stay with the patient’s experiences.
+The resilience of patients is the key of healing.
 %The research implication is to investigate the necessity and sufficiency of the six conditions.
@@
 
-empowering
-(一)雙方有心理的接觸。
-(二)當事人正感到焦慮或不一致(incongruence)。 
-(三)治療者在治療關係中是一致的、真實的或真誠的。
-(四)治療者能夠對當事人表現出無條件的正向關懷。
-(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
 Personhood: Carl Rogers
-尋找生命的意義
+尋找生命的意義 meaning of life
 真誠、能深刻地善解人意
 非認知性核心能力
-正念止觀(在當下)
+正念止觀(在當下) mindfulness meditation
 人人有自癒能力

### 2021-03-08 main.tex
Updates from Overleaf

@@
 As the cancer patient feels intense negative emotions of fear, depression, stress, anxiety, fatigue, sadness, it is not the patient-centred therapist’s task to remove these feelings: The task is simply to stay with the patient’s experiences.
-The resilience of patients is the key of healing.
 %The research implication is to investigate the necessity and sufficiency of the six conditions.
@@
 Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
-
-%PCA理論
-治療關係的核心條件: 說好話 眼對眼 engaging 用真心
-以心印心 engaging
+%PCA理論 by *** Tex Chi
+%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
+%以心印心 engaging
 身心相連 body-mind connection
-捨末求本
-身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，
-「他自己本身」就具有療癒效果
-「把自己當藥方開出去」
+捨末求本 find the source
+A holistic healthcare providers will engage his/her patients with eye-to-eye contact and mind-to-mind connection.
+Their compassion, empathy and sympathy is induced by suffering of their patients from those diseases.
+They treat patients by using medication, surgery, and "themselves"
+The resilience of patients will be also induced by the holistic healthcare. % of healing.
+%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
+%「把自己當藥方開出去」
+%Spirituality
+%慈悲心 compassion 
+%同情心 sympathy
+%同理心 empathy
+%non-verbal contact
 
@@
 每位醫師都可以成為「創傷知情者」
-幫助我們身邊的病患， 懂他的心靈創傷
-讓他有安全感， 才有機會改變疾病的走向
-
-“每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）”
+幫助我們身邊的病患，懂他的心靈創傷，讓他有安全感， 才有機會改變疾病的走向
+
+"每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）"
 解說：

### 2021-03-09 main.tex
Updates from Overleaf

@@
 such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
-However, the TCGA did not collect other features in holistic cancer care.
+However, the TCGA did not collect other features from holistic cancer care.
 % Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
@@
 
+%we educate them
+%1.
+Mong, L.-C., Liao, F., Chiou, J.
+& Chiang, P.
+Tips for Integrating Spiritual Care Delivery in Dental Education.
+in Asia Pacific Medical Education Conference.
+Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}
 The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
@@
 MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes the development of a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation.
-It employs (static) mindfulness meditation to alleviate suffering associated with physical, psychosomatic and psychiatric disorders.
+It employs (static) mindfulness meditation to alleviate suffering associated with physical (pain), psychosomatic and psychiatric disorders.
 %是1979年麻薩諸塞大學的榮譽教授Jon Kabat-Zinn => 佛教禪修的mindfulness 正念止觀（中譯建譯：自我覺察）帶入西方身心醫學及心理學領域。
 The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage mindfulness and self-awareness. 
-
 %Search Inside Yourself was born at Google in 2007 when one of Google’s earliest engineers, Chade-Meng Tan, gathered a team of leading experts in mindfulness, neuroscience, leadership and emotional intelligence to develop an internal course for fellow Google employees lovingly called Search Inside Yourself (SIY).
-
-% 目的與功效
-%  出入息 呼吸念頭 回到覺知，不再被潛意識自動導航干擾情緒
+% 目的與功效  出入息 呼吸念頭 回到覺知，不再被潛意識自動導航干擾情緒
 %正念，放下二元評價 正念覺知 XAI saliency mapping and trustworthiness in deep learning
@@
 %diverse setting needs, including tele-medicine practice for survivors who are too ill to travel to group sessions or lack economic resources.
-
 % 自動導航（潛意識）易受情緒影響，造成焦慮、發炎、免疫 Cancer
@@
 
-%%%% PCA and ECA: the delivery of MBSR
+%%%% PCA and ECA: the way to delivery of MBSR
 Therapeutic relationship is an essence towards spiritual care.
+According to my 17-year clinical experience of healthcare, sometimes patient could tell me: "how amazing it is, I would like to talk about myself more when I visit this doctor who I trust".
+In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
+Then simply my presence is releasing and helpful."\cite{Rogers1979}
 Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
-Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}.
-For constructive personality change to occur, it is necessary that these
-conditions exist and continue over a period of time: 
-1. Two persons are in psychological contact. 
-2. The first, whom we shall term the client, is in a state of incongruence, being vulnerable or anxious. 
+Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
+%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
+1. Two persons are in psychological contact. \\
+2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
 3. The second person, whom we shall term the therapist, is congruent
-or integrated in the relationship. 
-4. The therapist experiences unconditional positive regard for the client. 
+or integrated in the relationship. \\
+4. The therapist experiences "unconditional positive regard" for the client. \\
 5. The therapist experiences an empathic understanding of the client's
-internal frame of reference and endeavors to communicate this experience to the client. 
-6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.
+internal frame of reference and endeavors to communicate this experience to the client. \\
+6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
 %empowering
@@
 %(二)當事人正感到焦慮或不一致(incongruence)。 
-%(三)治療者在治療關係中是一致的、真實的或真誠的。
-%(四)治療者能夠對當事人表現出無條件的正向關懷。
-%(五)治療者能夠同理的瞭解當事人的內在，
-%(六)並努力傳達「我懂你的」。
-
+%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
+%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
+%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
+%(六) 第五點只要有個適當的開始，療癒就會開始
 %Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
-As the cancer patient feels intense negative emotions of fear, depression, stress, anxiety, fatigue, sadness, it is not the patient-centred therapist’s task to remove these feelings: The task is simply to stay with the patient’s experiences.
+As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
+%七情: 喜、怒、思、悲、恐、驚、憂
+depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is simply to stay with the patient’s experiences. 
+% 只是陪伴
 %The research implication is to investigate the necessity and sufficiency of the six conditions.
@@
 %以心印心 engaging
-身心相連 body-mind connection
-捨末求本 find the source
-A holistic healthcare providers will engage his/her patients with eye-to-eye contact and mind-to-mind connection.
-Their compassion, empathy and sympathy is induced by suffering of their patients from those diseases.
-They treat patients by using medication, surgery, and "themselves"
-The resilience of patients will be also induced by the holistic healthcare. % of healing.
+%身心相連 body-mind connection
+%捨末求本 find the source: emotion
+A holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
+Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases.
+They will try to treat patients by medication therapy, surgery, and "themselves".
+The resilience of patients will be induced by unconditional positive regard. % of healing.
+Thus, patients will trust them who take care of and have confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
 %身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
@@
 
-Personhood: Carl Rogers
-尋找生命的意義 meaning of life
-真誠、能深刻地善解人意
-非認知性核心能力
-正念止觀(在當下) mindfulness meditation
-人人有自癒能力
-真誠 (Genuineness/Validity/Bona Fides)
-內在聲音與外在態度一致/明心見性/超越的意識狀態
-(Congruence/Consistency)
-共情理解(設身處地/同理心/除我執)
-(Empathic Understanding of Reference/Track)
-無條件關懷(不批判/頓悟)
-(unconditional positive regard)
-***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
-諮商員的靈性功力
+%Personhood: Carl Rogers
+% ***尋找生命的意義 meaning of life
+%真誠、能深刻地善解人意
+%非認知性核心能力
+%正念止觀(在當下) mindfulness meditation
+%人人有自癒能力 resilience
+%真誠 (Genuineness/Validity/Bona Fides) 善意?
+%內在聲音與外在態度一致/明心見性/超越的意識狀態 (Congruence/Consistency)
+%共情理解(設身處地/同理心/除我執 自他不二) (Empathic Understanding of Reference/Track)
+%無條件關懷(不批判/頓悟) (unconditional positive regard) 只是陪伴
+%***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）by 諮商員的靈性功力
 %治療關係: 
-Therapeutic relationship: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
-I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
+%Tex Chi's Therapeutic relationship: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
+%I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
 Then simply my presence is releasing and helpful\cite{Rogers1979}.
@@
 %Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
-「診後說三句，更勝良帖十方」
+%***「診後說三句，更勝良帖十方」
 
 %% why holistic? 太極 氣功 情緒 myofascia and sympathetic system
-中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
-養生和治療的原則:
-一、某些病症可以透過食療而改善的會建議自行調養
-二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
-三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
-四、沒有一勞永逸的食療，不宜執著特定的食療神話
-五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
-六、認識自己身體的狀態比吸收營養資訊更重要
-七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
-情志養生 悲喜憂思苦 七情
-人俯仰於天地之間
-順從四季氣候變化
-保養正氣陶冶性情
-自我療癒身心靈疾病
+%中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
+%養生和治療的原則:
+%一、某些病症可以透過食療而改善的會建議自行調養
+%二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
+%三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
+%四、沒有一勞永逸的食療，不宜執著特定的食療神話
+%五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
+%六、認識自己身體的狀態比吸收營養資訊更重要
+%七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
+%情志養生 喜、怒、思、悲、恐 or 七情
+%喜、怒、思、悲、恐為代表，就稱為五志 Joy, anger, thought, sadness, fear
+%喜、怒、思、悲、恐、"驚憂"，稱為七氣，即七情。加之以寒熱，稱為九氣
+%人俯仰於天地之間
+%順從四季氣候變化
+%保養正氣陶冶性情
+%自我療癒身心靈疾病
 %自他不二 心存正念 向內看，解決苦之源
@@
 %5.心無恐懼: 情志養生
-每位醫師都可以成為「創傷知情者」
-幫助我們身邊的病患，懂他的心靈創傷，讓他有安全感， 才有機會改變疾病的走向
-
-"每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）"
-解說：
-患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。
-
-%% why holistic? % Environment 環境
-Bruce Lipton introduced mind-brain-body system.
-Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
- In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
-dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.
-
-Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
-The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
-
-gene expression in deep learning
-Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).\cite{Ching2018}
-%慈悲心 利他心
-*** make Figure 5 holistic:
-meridian and emotion has mutual reaction
-meridian effect tissue and organ
-(autonomic nerve system, myofascial network, prefrontal cortex)
-placebo-effect influence on drug discovery
-博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
-#正念 除了可以減壓，還可以治癒疼痛
-Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
-
-Bruce Lipton: the biology of belief %信念的力量
-placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
+%每位醫師都可以成為「創傷知情者」幫助我們身邊的病患，懂他的心靈創傷，讓他有安全感， 才有機會改變疾病的走向
+%"每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）"
+%解說：患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。
+
+%% why holistic? % Environment 環境 => 分享權力、 自決 empowering
+The WHO's second principle is empowering – supporting people to manage and take responsibility for their own health.
+Bruce Lipton introduced mind-brain-body system in 1992\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}.
+%Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
+In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory cytokines.
+In the other state of love, dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.
+%Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
+%placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
 %biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
 %那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
-
 %% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
-As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life.
-I have experienced unjustified conflicts in my social relations, feeling stale in mind and body, indefinite self-image, emotional instability, and successive spontaneous bleeds despite the continuous factor replacement.
-My research is based on my experience of living with hemophilia for 37 years, reading countless books on personal development and the mind-body relationship, and having profound discussions about these experiences with my wife.
-Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds.
+%As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life.
+I have experienced unjustified conflicts in my social relations, feeling stale in mind and body
+%Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds.
 These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment.
-Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings.
-Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors.
+%Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings.
+%Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors.
 As Dr.
-Bruce Lipton explains in his book, 'The Biology of Belief': DNA does not control our biology; instead DNA is controlled by signals from outside the cell.
+Bruce Lipton explains in his book, 'The Biology of Belief'\cite{Lipton2015}: DNA does not control our biology; instead DNA is controlled by signals from outside the cell.
 Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows.
-New holistic approaches should be considered for treating PWH as a complete synchronized system of Soul, Mind, and Body; treatment should include more than just factor adjustment.
-Factor adjustment only treats symptoms, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}
-
-%% Environment 環境
-genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
-The genetics of the cell give us all kinds of potentials. % 自性空
-
-%冤親債主的意念 unknown X factors
-[Results] In summary, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
-Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
-The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
-依舊是以管窺天
-% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
-%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
-
-% so do the cancer
-Individual treatment and avoiding assumptions.
-Although it is useful for therapists to have a knowledge of the trauma literature on the general reactions of people who experience trauma, the therapist should not assume that this knowledge necessarily applies to each and every client\cite{Joseph2004}.
-
-Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction,13,16 centred on a physician's therapeutic intentions and his attunement to patient sympathy.
-we educate them
-%1.
-Mong, L.-C., Liao, F., Chiou, J.
-& Chiang, P.
-Tips for Integrating Spiritual Care Delivery in Dental Education.
-in Asia Pacific Medical Education Conference.
-Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}
+% 萬法唯心造
+Holistic healthcare should be considered for treating patients as a complete synchronized system of soul, mind, and body; treatment should include more than medication or surgery, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}\cite{Lipton2015}
 
 %騙過你的病-安慰劑效應 
-The Placebo Effect (Emmanuelle Sapin, Pascal Goblot)
+%The Placebo Effect (film by Emmanuelle Sapin, Pascal Goblot)\cite{Sapin2014}
 %1. Sapin, E. & Goblot, P. L’effet placebo (English: The Placebo Effect) [enregistrement vidéo] : le formidable pouvoir de l’auto-guérison. 53 PP-Quebec (Cinéfête, 2014).\cite{Sapin2014}
 % https://biblio.bdeb.qc.ca/in/sim/faces/details.xhtml;jsessionid=E3DD39109012D0BEA598E6E5B66A4FD2?id=p::usmarcdef_0000058243&posInPage=8
-1. Finniss, D. G. Placebo Effects: Historical and Modern Evaluation. in International review of neurobiology vol. 139 1–27 (2018).\cite{Finniss2018}
+%1. Finniss, D. G. Placebo Effects: Historical and Modern Evaluation. in International review of neurobiology vol. 139 1–27 (2018).\cite{Finniss2018}
 %蓋倫劑量 placebo effect 身心靈醫學的核心
 In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo.
-If I had thought of any internal medicine it would have been a dose of the Dover's powders."\cite{Kerr2008}\cite{Finniss2018}.
- (made up of Ipecac and opium) 
+If I had thought of any internal medicine it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}.
 Cullen studied the objective science of analytical chemistry.
-He also sense that the patient's subjective, psychosomatic or ‘sympathetic constitution’ determined his reaction to a prescribed therapeutic substance.
+He also sense that the patient's subjective, psychosomatic or "sympathetic constitution" determined his reaction to a prescribed therapeutic substance.
 ***Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
-Cullen's theory of sympathy is a mind-body function, a kind of ‘vital force’ that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
+Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
 This finely calibrated, rational use of active placebo treatment, in which the physician dispensed a weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
 %啟蒙運動
-
-% how placebo effect works? % Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
-安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
-前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
-the anterior cingulate cortex and the dorsolateral prefrontal cortex have been found to be activated by placebo administration.
-\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}
-But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}.
-Today, pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced\cite{Bennett2018}.
-
+Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction centred on a physician's therapeutic intentions to patient sympathy\cite{Sapin2014}.
+How does placebo effect work in patient's internal environment?  %改造患者的心，就能改造他的身體環境，有利消除癌症
+%安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
+%前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
+%But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}.
+Pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced in neuroimaging studies\cite{Bennett2018}. 
+The anterior cingulate cortex and the dorsolateral prefrontal cortex of brain have been found to be activated by placebo administration\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}.
+The prefrontal cortex runs conscious mind generating empathy and love, and will be influenced during mindfulness meditation\cite{Krummenacher2010}\cite{Bennett2018}.
+%prefrontal lobe 理智腦 意識 正念 杏仁核 prefrontal cortex runs conscious mind「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
 %sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
-The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, whether by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
-placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
-醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
-安慰劑效應的研究，最後導向了良好醫病關係的思考，並成為醫生臨床醫術的元素之一：
-「醫師開藥時，其實是把自己當藥方開出去」。
-
-#正念 減壓，療癒疼痛\cite{Krummenacher2010}\cite{Bennett2018}、免疫系統、內分泌系統或自律神經系統相關的疾病，以及憂鬱症、焦慮症 
-The idea of placebo as a diluted but active substance persisted into the 19th century17 but the term also came to mean a physiologically inert substance - bread or lactose, for example.18,19 Inert substances began to be used in comparative clinical trials during the first half of the 19th century,20 but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.21 This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008}
-
-prefrontal lobe 理智腦 意識 正念 杏仁核 prefrontal cortex runs conscious mind
-「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
-物理作用、信號，雷射針灸
-Therapeutic Relationship
-Spirituality
-慈悲心 compassion 
-同情心 sympathy
-同理心 empathy
-non-verbal contact
-前額葉內側 (medial prefrontal cortex)
-額葉底部(orbitofrontal cortex)
-
-*** make Figure 5 holistic:
-meridian and emotion has mutual reaction
-meridian effect tissue and organ
-(autonomic nerve system, myofascial network, prefrontal cortex)
-placebo-effect influence on drug discovery
-博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
-Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
-
-% cancer cure (care) 的證明
-repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
-
-mindfulness and meditation for cancer
+The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, either by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
+%placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
+%醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
+%#正念 減壓，療癒疼痛\cite{Krummenacher2010}\cite{Bennett2018}、免疫系統、內分泌系統或自律神經系統相關的疾病，以及憂鬱症、焦慮症 
+%The idea of placebo as a diluted but active substance persisted into the 19th century but the term also came to mean a physiologically inert substance - bread or lactose, for example.
+Inert substances began to be used in comparative clinical trials during the first half of the 19th century but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.
+This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008} % 漸漸被特意忽略
+%物理作用、信號，雷射針灸
+%non-verbal contact
+%前額葉內側 (medial prefrontal cortex)
+%額葉底部(orbitofrontal cortex)
+%%%%%%%%
+% mindfulness meditation
 % 人的腦波一般分為β（12-30Hz）、α(8-12Hz）、θ(4-8Hz)、δ（1-4Hz)，四種波。當我們處於清醒、警覺狀態時，腦波是處於高頻率的β波。隨著身心狀態逐漸放鬆，卸下防衛時，腦波頻率也會逐漸下降至α、θ波，此時身心狀態是處於最寧靜、創造能力最好、對事情洞察能力最佳的狀態。如果能夠安祥進入睡眠階段，則腦波會降至δ波。靜坐時不僅可以使腦波由快速的β波降至α、θ波
-In human EEG studies, cortical theta wave (4–7 Hz) tends to appear during meditative, drowsy, hypnotic or sleeping states in older children and adults.
+%In human EEG studies, cortical theta wave (4–7 Hz) tends to appear during meditative, drowsy, hypnotic or sleeping states in older children and adults.
 Theta is a frequency lower than consciousness.
-Theta is actually a brain function associated with imagination.
-
-Warburg effect and carcinogenesis
-cancer therapy by 患者自癒
-Mindfullness Meditation help 復原力（resilience）
-Self-Compassion  慈悲
-Self-compassion 
-除我執
- global self-esteem:
-自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
-%%%% healing and cure
-Reprogramming cells:
-Environmental signals controlling cell behavior and cell behavior include genetics.
-The environmental signal via signal transduction can go into the nucleus and selectively change the reading of our gene, epigenetics regulation.
-
-the membrane proteins and the chromosomal proteins that control the DNA, called regulatory proteins. But even those proteins are controlled by environmental signals. It is not DNA to RNA to protein.
-
+Theta is actually a brain function also associated with imagination.
+
+%cancer therapy by 患者自癒 Mindfulness Meditation help 復原力（resilience）
+%Self-Compassion  慈悲
+% 除我執 global self-esteem:
+%自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
+
+%%%% healing and cure by Changing the Environment 環境
+%genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
+The genetics of the cell give all kinds of potentials. % 自性空
+Environmental signals from the cell membrane can go into the nucleus via signal transduction.
+The signal selectively change the reading of our gene, e.g.
+epigenetics regulation, controlling cell behaviors.% including genetics.
 The new understanding is: environmental signals to regulatory protein to DNA to RNA and then to protein.
-
-療癒 There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process.
+Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}.
+% so do the cancer
+%Individual treatment and avoiding assumptions.
+Although it is useful for therapists to have a knowledge of the trauma literature on the general reactions of people who experience trauma, the therapist should not assume that this knowledge necessarily applies to each and every client\cite{Joseph2004}.
+%The membrane proteins and the chromosomal proteins that control the DNA, called regulatory proteins. But even those proteins are controlled by environmental signals. %It is not DNA to RNA to protein.
+%療癒 
+There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process.
 After 8 hours of meditation, the activity of the genes changed.
-You can change your genetic activity by how you change your response to the environment.
-
-to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.
-
+%You can change your genetic activity by how you change your response to the environment. 
+%to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.
 Becoming aware of the subconscious source of our behavior gives us an opportunity to change our lives by rewriting the programs (in subconscious mind) of limitation or the things that interfere with us.
-
-愛自己、蜜月；其實是 正念 mindfulness (因為自他不二）
-You are creating a world of joy and love, and that’s called the honeymoon. When we fall in love, we stop focusing our conscious mind in thought and start keeping it present. 
-It is called being mindful. 
-You’ve been looking for yourself your whole life.
-愛、性、正念止觀
-Science has recognized that immediately after falling in love, we enter a period of mindfulness where we keep our conscious mind present.
-
-You start running programs that are based on your conscious wishes and desires. All of a sudden, without the programs—without the subconscious programs—we begin to experience a heavenly life.
-%%%%
-
+Warburg effect\cite{Warburg1956}\cite{Chang2017b} is an example of carcinogenesis, metabolic reprogramming cells by some environmental factors.
+%honeymoon by Lipton 愛自己就是渡蜜月；其實是 正念 mindfulness (因為自他不二）
+%You are creating a world of joy and love, and that’s called the honeymoon. When we fall in love, we stop focusing our conscious mind in thought and start keeping it present. 
+%It is called being mindful. 
+%You’ve been looking for yourself your whole life.
+%愛、性、正念止觀
+%Science has recognized that immediately after falling in love, we enter a period of mindfulness where we keep our conscious mind present.
+%You start running programs that are based on your conscious wishes and desires. All of a sudden, without the programs—without the subconscious programs—we begin to experience a heavenly life.
 %%%%%% carcinogenesis
-mind-brain-body axis: subconscious fear -> inflammatory and stress hormones -> DNA/methylation mutation/mRNA expression alteration -> carcinogenesis of cancer.
-95\% of cognitive behavior runs on subconscious program:
-
-7\% 對於健康有不良影響 => 卻是惡劣競爭下的生存技能
+%95\% of cognitive behavior runs on subconscious program:
+%70\% %對於健康有不良影響 => 卻是惡劣競爭下的生存技能
 Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage.
-These programs were acquired from other people, not from ourselves.
-Again, being subconscious, these programs are occurring without conscious recognition and awareness.
+These programs were acquired from other people, not from ourselves, with survival advantage.
+Being subconscious, these programs are occurring without conscious recognition and awareness. 
 It effects on epigenetic regulation.
-
-Less than 1\% of disease is associated with genetics.
-Over 90\% of disease is a total reflection of environment and especially our programming: the disempowering, self-sabotaging behaviors that we acquired in the first 7 years.
-
 Genes are not self-actualizing.
@@
 The change of genetic activity is due to the interaction of the cell with environmental signals.
-
-the cell membrane through receptors picking up the signals and translating them into biology, which then sends signals into the nucleus, which then controls the genetic activity.
-
-% ***七星山的 idea [2021/03/01]
-Generative adversarial networks simulate gene expression and predict perturbations in single cells
-3.1. Gene expression in \cite{Ching2018} % deep review
-% 環境 -> chromosome accessibility
-%  unsupervised deep learning algorithm
-generative adversarial networks (GAN) with VAE (variational autoencoder) could simulate environment causing carcinogenesis
-%graph convolutional network (from deepchem import GraphConvModel)
-deep or graph convolutional network in gene regulation, which includes chromosome accessibility, transcription factor binding site, DNA methylation, and RNA inhibitions (RNAi, microRNA, LncRNA).
-
-%GAN overview
-In this paper compares GAN with VAE (variational autoencoder) and RBM (restricted Boltzmann machine) models.
-As a new unsupervised learning algorithm framework, generative adversarial networks (GAN) has been favored by more and more researchers, and it has become a research hotspot.
-GAN is inspired by the two-person zero-sum game theory in game theory.
-Its unique confrontation training idea can generate high-quality samples and has more powerful feature learning and feature expression ability than traditional machine learning algorithms.
-At present, GAN has achieved remarkable success in the field of computer vision, especially in the field of sample generation.
-%Learning Generative Models of Tissue Organization with Supervised GANs
-\cite{Han2018}
-
-%https://www.amazon.com/Deep-Learning-Life-Sciences-Microscopy-ebook/dp/B07QM3G5JM
-
-%book: https://github.com/deepchem/DeepLearningLifeSciences
-%https://github.com/deepchem/torchchem
-
-%https://github.com/hindupuravinash/the-gan-zoo
-
+%Less than 1\% of disease is associated with genetics. 
+Over 90\% of disease is a total reflection of environment and especially our programming.
+%the disempowering, self-sabotaging behaviors that we acquired in the first 7 years.
+%the cell membrane through receptors picking up the signals and translating them into biology, which then sends signals into the nucleus, which then controls the genetic activity.
+The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from brain, in terms of cell alteration in DNA methylation, mutation, mRNA expression.
+Carcinogenesis will occurs if the reprogramming is persistent in a longer period of time.
 %%%%%
@@
 　　　　
-　　　　suggested TCGA features:
+　　　　
+　　　　
+　　　　%冤親債主的意念 unknown X factors 回到我們的文章
+　　　　% cancer cure (care) 的證明
+%# 懺悔
+repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
+mindfulness and meditation for cancer
+
+In summary, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
+Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
+The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin.
+%依舊是以管窺天
+% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
+%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
+Moreover, we suggest TCGA should cover more holistic features:
 cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors.
@@
 how to do: once holistic feature available, graph convolutional neural network (GCNN) is mandatory: 以免 genomics 光芒萬丈
+%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
+%七情: 喜、怒、思、悲、恐、驚、憂
+*** make Figure 5 holistic:
+meridian and emotion has mutual reaction
+meridian effect tissue and organ
+(autonomic nerve system, myofascial network, prefrontal cortex)
+placebo-effect influence on drug discovery
+gene expression in deep learning
+Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).\cite{Ching2018}
+%慈悲心 利他心
+博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
+#正念 除了可以減壓，還可以治癒疼痛
+Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
+The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
 

### 2021-03-09 main.tex
holistic draft

@@
 Carcinogenesis will occurs if the reprogramming is persistent in a longer period of time.
+Moreover, long-term stress could be correlated with cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021},
+and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}. %HNSCC
+Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses.
+Additional work has shed light on the potential molecular mechanisms by which early adversity becomes “biologically embedded” in altered physiology across body systems.\cite{Berens2017}
 %%%%%
 
+%% TCGA new holistic features %%%%%
+In summary of our current study, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
+Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
+The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin so far.
+When we consider the survival prediction model again,
 ground truth Y (e.x. patient's survival):\\[0.5cm]
 %Y$:\\[0.3cm]
-$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
-gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$
-There is much work to be done in investigating the functional relationships more fully.\cite{Rogers1959}
-We wish the TCGA does collect holistic features from their participants in the future.
-
-holistic-enabled Electric healthcare record, EHR
-Deep Patient
-Under HL7, RESTful
-deep learning by EHR-converted FHIR: with holistic observations
-=> Level 4 Record-keeping and Data Exchange for the healthcare process
-(clinical data)
-Allergy, Problem,
-Procedure,
-CarePlan/Goal,
-ServiceRequest,
-Family History,
-Risk Assessment (APGAR, Glasgow coma scale)
-condition: physical, mental
-{observations: 
-vital signs, 
-body temperature, body weight and body height, 
-x-ray, 
-laboratory data, 
-pulse oximetry, 
-ECG, EEG, EMG, 
-clinical findings (symptom and sign), 
-tobacco exposure, family support, cognitive status
-pregnancy status
-death assertion
-HIV, HBV, HCV status
-}
+$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
+gene expression is not an independent $X_mrna$, which could be correlated with other $X_body, X_stress, X_fear, X_meaningOfLife, X_inflammation, X_ros$ factors.
+There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
+%We wish the TCGA does collect more holistic features from their participants in the future.
+%依舊是以管窺天
+% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
+%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
+We suggest TCGA should cover more holistic features:
+cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors.
+Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
+The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
+%冤親債主的意念 unknown X factors 回到我們的文章
+Since sychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.
+
+% holistic EHR
+Moreover, we encourage that physician might write their electric healthcare record (EHR) in a "holistic way".
+% Deep Patient:  
+Deep learning applied to EHR can derive patient representations that offer improved clinical predictions\cite{Miotto2016}
+Deep learning also might convert EHR to the Fast Healthcare Interoperability Resources (FHIR) format\cite{Rajkomar2018}\cite{HealthLevelSeven2019} for handling free-text notes.
+%=> Level 4 Record-keeping and Data Exchange for the healthcare process (clinical data) %Under HL7, RESTful
+%Allergy, Problem,
+%Procedure,
+%CarePlan/Goal,
+%ServiceRequest,
+%Family History,
+%Risk Assessment (APGAR, Glasgow coma scale)
+%condition: physical, mental
+%{observations: 
+%vital signs, 
+%body temperature, body weight and body height, 
+%x-ray, 
+%laboratory data, 
+%pulse oximetry, 
+%ECG, EEG, EMG, 
+%clinical findings (symptom and sign), 
+%tobacco exposure, family support, cognitive status and pregnancy status.
+%death assertion
+%HIV, HBV, HCV status
+%}
 
@@
 %https://mos2718.github.io/FHIRspec/Spec/Patient/EHR_Patient.docx
-
-We design a #holisticDental chart in our outpaitent department for Psycho-Social-Spiritual Evaluation\cite{Ling-ChengMong2021}.:
-1. Emotional: stable/depression/ anxiety/ agitated/ perplexed
-2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment
-3. Social: (disturbing living/ disturbing working/ disturbing other life aspect) by present illness
-4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind
-5. Self-expectation: lack of confidence/ low self-esteem/ social-withdrawal
-6. Impact to life: financial problem/ family problem
-7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment 
-side-effects/ litigation experience
-8. Other aspects
-/no other specific issues
-
-In personal history section of admission note (EHR for inpatient): 
-< Habits >
-　　　　-Tobacco:
-　、　1.5　pack/day for　30　years
-　　　　-Alcohol drinking:　Occasionally
-　　　　-Betel nuts:　、　nuts/day for　30　years　
-　　< Social/Economic Evaluation >
-　　　　-Living condition:　Living with family
-　　　　-Family support:　Well
-　　　　-Main caregiver:　Spouse
-　　　　-Financial support:　Sufficient
-　　< Psychological Evaluation >
-　　　　Stable
-　　　　Suspected to be ” abuse ” or ”neglected victim” (if the answer is “Yes“ should be assisted by social workers)　No
-　　< Spiritual Assessment >
-　　　　Religion:　Nil
-　　　　Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers?　No
-　　　　
-　　　　
-　　　　
-　　　　%冤親債主的意念 unknown X factors 回到我們的文章
+In Taipei Medical University Hospital, holistic-enabled EHR has been designed as holistic dental chart for our outpaitent with psycho-social-spiritual evaluation\cite{Ling-ChengMong2021}:\\
+1. Emotional: stable/depression/ anxiety/ agitated/ perplexed\\
+2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment\\
+3. Social: (disturbing living/ disturbing working/ disturbing other life aspect) by present illness\\
+4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind\\
+5. Self-expectation: lack of confidence/ low self-esteem/ social-withdrawal\\
+6. Impact to life: financial problem/ family problem\\
+7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[2cm]
+
+In personal history section of admission note for inpatient:\\
+<Habits>\\
+　　　　-Tobacco: 1.5 pack/day for 30 years\\
+　　　　-Alcohol drinking: Occasionally\\
+　　　　-Betel nuts: 30 nuts/day for 30 years\\
+<Social/Economic Evaluation>\\
+　　　　-Living condition: Living with family\\
+　　　　-Family support: Well\\
+　　　　-Main caregiver: Spouse\\
+　　　　-Financial support: Sufficient\\
+<Psychological Evaluation>\\
+　　　　Stable but worry about this oral lesion\\
+　　　　Suspected to be abuse or neglected victim: negative\\
+<Spiritual Assessment>\\
+　　　　Religion: Nil\\
+　　　　Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers?　No\\
 % cancer cure (care) 的證明
 %# 懺悔
-repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
-mindfulness and meditation for cancer
-
-In summary, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
-Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
-The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin.
-%依舊是以管窺天
-% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
-%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
-Moreover, we suggest TCGA should cover more holistic features:
-cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors.
-Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
-The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
- psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6)
-how to do: once holistic feature available, graph convolutional neural network (GCNN) is mandatory: 以免 genomics 光芒萬丈
+We always educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the pass, and sincere thanks for the hard work of our physical body.
+Mindfulness and meditation will be helpful in cancer healthcare.
+Once holistic feature is available, graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018}.
+The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
 %  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
 %七情: 喜、怒、思、悲、恐、驚、憂
+
 *** make Figure 5 holistic:
-meridian and emotion has mutual reaction
-meridian effect tissue and organ
-(autonomic nerve system, myofascial network, prefrontal cortex)
-placebo-effect influence on drug discovery
-gene expression in deep learning
-Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).\cite{Ching2018}
+%meridian and emotion has mutual reaction
+%meridian effect tissue and organ
+%(autonomic nerve system, myofascial network, prefrontal cortex)
+%placebo-effect influence on drug discovery
+%gene expression in deep learning
+%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
 %慈悲心 利他心
-博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
-#正念 除了可以減壓，還可以治癒疼痛
-Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
-The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
-
-Impact of stress on cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}
-cancer initiation under stress\cite{Lutgendorf2010}\cite{Powell2013}
-HNSCC\cite{Iftikhar2021}
-Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress or depression, and domestic or community violence, have been associated in epidemiological studies with increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses.
-Additional work has shed light on the potential molecular mechanisms by which early adversity becomes “biologically embedded” in altered physiology across body systems.\cite{Berens2017}
-
-We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on all the TCGA or other in-house cancer datasets.
-
-Dali Lama: Wish and bless the whole world %慈悲心 利他心
+%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
+%#正念 除了可以減壓，還可以治癒疼痛
+%Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
+
+We also aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on all the TCGA or other in-house cancer datasets.
+
+%Dali Lama: Wish and bless the whole world %慈悲心 利他心
 % 多了解身心靈的關係，減少癌症對健康的損害

### 2021-03-09 main.tex
Updates from Overleaf

@@
 \subsubsection{TCIA validation}
-https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
-https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
+%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
+%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
 TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Keras framework)
@@
 image-based phenotypes and their underlying genomic data 
-https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
-https://github.com/Serian1992/ImgBio.
+%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
+%https://github.com/Serian1992/ImgBio.
 
@@
 *** interpretable or explainable CNN
-Manning meap book: 不再是黑盒子
-https://www.manning.com/books/trust-in-machine-learning
+%Manning meap book: 不再是黑盒子
+%https://www.manning.com/books/trust-in-machine-learning
 Trust in Machine Learning
 
-*** 必備 explainable interpretable 
+%*** 必備 explainable interpretable 
 By saliency mapping: e.x. diabetes retinopathy, model focused on retinal aterry
@@
 
-Understanding the Method Behind the Machine
-interpredability
+Understanding the Method Behind the Machine: interpredability
 
@@
 $Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
-gene expression is not an independent $X_mrna$, which could be correlated with other $X_body, X_stress, X_fear, X_meaningOfLife, X_inflammation, X_ros$ factors.
+gene expression is not an independent $X_mrna$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
 There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
@@
 %冤親債主的意念 unknown X factors 回到我們的文章
-Since sychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.
+Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.
 

### 2021-03-09 main.tex
Updates from Overleaf

@@
 
-\subsubsection{TCIA validation}
+\subsubsection{TCIA validation by deep learning}
 %https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
@@
 
-https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
+%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
 #XAI
@@
 
-https://www.deeplearningbook.org/
-https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
+%https://www.deeplearningbook.org/
+%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
 % NCI
@@
 *** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
-recurrent neural network for NLP
+%recurrent neural network for NLP
 
@@
 $Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
-gene expression is not an independent $X_mrna$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
+gene expression is not an independent $X_{mrna}$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
 There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.

### 2021-03-10 main.tex
Updates from Overleaf

@@
 \begin{document}
-%\begin{paracol}{2}
+\begin{paracol}{2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
-#XAI
+%#XAI
 Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data
@@
 Mindfulness and meditation will be helpful in cancer healthcare.
-Once holistic feature is available, graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018}.
+Once holistic feature is available, graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
 The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
@@
 %\bibliographystyle{model1-num-names}
-\bibliography{TCGA_margin_cutoff.bib, Holistic.bib}
+\bibliography{TCGA_margin_cutoff.bib, Holistic.bib, Deep_Learning.bib}
 

### 2021-03-10 main.tex
\begin{document} \begin{paracol}{2}

@@
 The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets.
-We divided the whole-slide images into squares of 112 × 112 μm (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
+We divided the whole-slide images into squares of 112 × 112 $\mu$m (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
 We sampled a maximum of 8000 such tiles from each slide.

### 2021-03-10 main.tex
ERROR free
Updates from Overleaf
truncated TCIA subsection

--- 2021-03-10 main.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\globalcounter* % for paracol
 
 \begin{document}
-\begin{paracol}{2}
+%\linenumbers
+%\begin{paracol}{2}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
+%\widefigure
 \includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
@@
 \linenumbers
-\switchcolumn
+\switchcolumn[1]
 
@@
 陽明交大
-
-\subsubsection{TCIA validation by deep learning}
-%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
-%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
-TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Keras framework)
-%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
-image-based phenotypes and their underlying genomic data 
-%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
-%https://github.com/Serian1992/ImgBio.
-
-%The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
-%https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447; there is few HNSCC slides
-
-*** interpretable or explainable CNN
-%Manning meap book: 不再是黑盒子
-%https://www.manning.com/books/trust-in-machine-learning
-Trust in Machine Learning
-
-%*** 必備 explainable interpretable 
-By saliency mapping: e.x. diabetes retinopathy, model focused on retinal aterry
-
-%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
-%#XAI
-Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data
-
-Jie Hao, 2019
-By PyTorch
-
-%https://www.deeplearningbook.org/
-%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
-% NCI
-Aiding the Genomic Characterization of Tumors: 
-deep learning could predict commonly mutated genes and mRNA expression from the images
-*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
-Preprocessing of whole-slide images.
-The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets.
-We divided the whole-slide images into squares of 112 × 112 μm (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
-We sampled a maximum of 8000 such tiles from each slide.
-We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
-For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster.
-The use of these supertiles reduces the dimensions of a slide to 100 × 2048.
-The model was first trained on this reduced dataset, with all the TCGA data.
-Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.
-
-%AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
-For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas.
-Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.
-
-Understanding the Method Behind the Machine: interpredability
-
-%One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process.
-For example, a DL algorithm that predicts the optimal treatment for a patient does not provide the reasoning it used to make that prediction.
-Additional efforts are needed to reveal how algorithms arrive at a decision or prediction so that the process becomes transparent to scientists and clinicians.
-Making these algorithms transparent could help researchers identify new biological features relevant to disease diagnosis or treatment.
-***  unconscious biases:
-Incorporating information about biological processes into the algorithm is likely to improve its accuracy and decrease dependence on large amounts of annotated data, which may not be available.
-One danger of the “black box” problem is that DL may inadvertently perpetuate existing unconscious biases.
-Researchers need to carefully consider how potential biases affect the data being used to develop a model, adopt practices to address and monitor those biases, and monitor performance and applicability of AI models.
-
-%With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk.
-Updated: August 31, 2020
-%
-TMA by deep learning (CNN) mRNA expression associated with pathological images
-*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
-%recurrent neural network for NLP
-
-%佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。
-
-%在生物醫學領域，氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。
-
-%the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
-%with more TCGA features (holistic)
 
@@
 We also aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on all the TCGA or other in-house cancer datasets.
-
+%the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+%with more TCGA features (holistic)
 %Dali Lama: Wish and bless the whole world %慈悲心 利他心

### 2021-03-15 main.tex
Updates from Overleaf
grammarly checked

@@
 \documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi}
-\maxdeadcycles=500 % Output loop---200 consecutive dead cycles.
+\maxdeadcycles=1000 % Output loop---200 consecutive dead cycles.
 
@@
 
+%****************%
 \subsubsection{Holistic cancer care} 
@@
 %discussion: the third limitation
-There are eighty one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modelling in the TCGA, 
+There are eighty-one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
 % since it has comprehensive clinical features, 
@@
 % Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
-Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equal important comparing with physical and social status.
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status.
 %
-World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
+World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
 Core principles can be taken to achieve people-centred and integrated health service delivery. 
-First principle is holistic – focusing on physical, socioeconomic, mental and emotional well-being. 
-Holistic care is defined that care and see the person as a whole with psychological, social and environmental levels of needs and goals.
+The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
+Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
 %that considers  factors rather than just the symptoms of disease or ill-health.
-Second principle is empowering – supporting people to manage and take responsibility for their own health,
+The second principle is empowering – supporting people to manage and take responsibility for their health,
 %Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
-for example, in the uptake of healthier behaviours or the ability to self-manage illnesses.
-People-centred care requires that people have the education and support they need to make decisions and participate in their own care.
+for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
+People-centred care requires that people have the education and support they need to make decisions and participate in their care.
 %Glossary:
@@
 Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}
-The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
-Being mindful to patient’s mental health, emotional changes, socioeconomic during healthcare.
+Spiritual care is the key to holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
+It is mindful of patient's mental health, emotional changes, socioeconomic during healthcare.
 %Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration.
-Learning to listen proactively.
-Being aware of patient’s spiritual needs.
+We are learning to listen proactively.
+It is aware of the patient's spiritual needs.
 %Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}
@@
 %%%% MBSR "念" 今天的心 專心才有幸福感(味覺嗅覺靈敏專心吃
-Mindfulness-Based Stress Reduction (MBSR) program has been introduced by Jon Kabat-Zinn in 1979\cite{Niazi2011}.
-MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes the development of a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation.
+Jon Kabat-Zinn has introduced the mindfulness-Based Stress Reduction (MBSR) program in 1979\cite{Niazi2011}.
+MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation.
 It employs (static) mindfulness meditation to alleviate suffering associated with physical (pain), psychosomatic and psychiatric disorders.
@@
 Psychosocial stress is associated with cancer incidence and poor survival\cite{Chida2008}.
-This impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
-Thus, cortisol is one of the most common (objective) outcome studied in psychoneuroimmunological (PNI) factors.
+These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
+Thus, cortisol is one of the most common (objective) outcomes studied in psychoneuroimmunological (PNI) factors.
 % others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV
-The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
+The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
 %  body-mind-spirit (BMS) group therapy in the Meaning in Life questionnaire (MLQ) including two sub-scales: MLQ-Presence and MLQ-Search.
@@
 Findings suggest that mindfulness-breathing-stretching interventions appear to offer potential improvement or stabilization of neuroendocrine-immune activity in breast cancer survivors compared to control groups.
-This review revealed a positive pattern between spiritually based interventions and a number of PNI biomarker outcomes, suggesting that spiritually based interventions offer positive mental and physiological health benefits.
-For breast cancer survivors, these studies suggested that engaging in spiritually based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.
+This review revealed a positive pattern between spiritually-based interventions and several PNI biomarker outcomes, suggesting that spiritually-based interventions offer positive mental and physiological health benefits.
+For breast cancer survivors, these studies suggested that engaging in spiritually-based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.
 %From a PNI perspective, future spiritually based interventions should include standardized measures of religiousness and spirituality in order to understand relationships between and among religiousness, spirituality, and neuroendocrine-immune outcomes.
@@
 %and greater IFN-gamma production => IFN gamma supports an immune-mediated response against cancer and this may be important during the transition following cancer treatment
-A randomized clinical trial with active control proved that early provision of MBSR for women newly diagnosed with breast cancer provides psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) supportive of cancer survival.\cite{WitekJanusek2019}
+A randomized clinical trial with active control proved that early provision of MBSR for women newly diagnosed with breast cancer provides psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) supportive of cancer survival\cite{WitekJanusek2019}.
 
 %%%% PCA and ECA: the way to delivery of MBSR
-Therapeutic relationship is an essence towards spiritual care.
-According to my 17-year clinical experience of healthcare, sometimes patient could tell me: "how amazing it is, I would like to talk about myself more when I visit this doctor who I trust".
+The therapeutic relationship is essential towards spiritual care.
+According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
 In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
@@
 3. The second person, whom we shall term the therapist, is congruent
-or integrated in the relationship. \\
+or integrated with the relationship. \\
 4. The therapist experiences "unconditional positive regard" for the client. \\
@@
 %七情: 喜、怒、思、悲、恐、驚、憂
-depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is simply to stay with the patient’s experiences. 
+depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
 % 只是陪伴
@@
 %捨末求本 find the source: emotion
-A holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
-Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases.
-They will try to treat patients by medication therapy, surgery, and "themselves".
-The resilience of patients will be induced by unconditional positive regard. % of healing.
-Thus, patients will trust them who take care of and have confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
+Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
+Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases.
+They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
+Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
+The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
 %身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
@@
 %% why holistic? % Environment 環境 => 分享權力、 自決 empowering
-The WHO's second principle is empowering – supporting people to manage and take responsibility for their own health.
+The WHO's second principle is empowering – supporting people to manage and take responsibility for their health.
 Bruce Lipton introduced mind-brain-body system in 1992\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}.
 %Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
-In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory cytokines.
-In the other state of love, dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.
+In a state of fear, the brain releases chemicals of stress hormones and inflammatory cytokines.
+Conversely, dopamine, oxytocin, vasopressin, and growth hormone will be released by the central nervous system in response to the perception of love.
 %Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
@@
 In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo.
-If I had thought of any internal medicine it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}.
+If I had thought of any internal medicine, it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}.
 Cullen studied the objective science of analytical chemistry.
-He also sense that the patient's subjective, psychosomatic or "sympathetic constitution" determined his reaction to a prescribed therapeutic substance.
-***Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
-Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, coordinated function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
-This finely calibrated, rational use of active placebo treatment, in which the physician dispensed a weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
+He also sensed that the patient's subjective, psychosomatic, or "sympathetic constitution" determined his reaction to a prescribed therapeutic substance.
+Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with the psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
+Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
+This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
 %啟蒙運動
 Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction centred on a physician's therapeutic intentions to patient sympathy\cite{Sapin2014}.
-How does placebo effect work in patient's internal environment?  %改造患者的心，就能改造他的身體環境，有利消除癌症
+%How does placebo effect work in patient's internal environment?  %改造患者的心，就能改造他的身體環境，有利消除癌症
 %安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
@@
 Pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced in neuroimaging studies\cite{Bennett2018}. 
-The anterior cingulate cortex and the dorsolateral prefrontal cortex of brain have been found to be activated by placebo administration\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}.
+The anterior cingulate cortex and the dorsolateral prefrontal cortex of the brain have been found to be activated by placebo administration\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}.
 The prefrontal cortex runs conscious mind generating empathy and love, and will be influenced during mindfulness meditation\cite{Krummenacher2010}\cite{Bennett2018}.
@@
 %sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
-The role of the physician was to be a gentle, sympathetic listener, who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, either by prescribing placebos to please (influence the emotional states of patients), or medicine to cure the patient's disorder.
+The physician's role was to be a gentle, sympathetic listener who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, either by prescribing placebos to please (influence the patients' emotional states) medicine to cure the patient's disorder.
 %placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
@@
 %genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
-The genetics of the cell give all kinds of potentials. % 自性空
+The genetics of the cell gives all kinds of potentials. % 自性空
 Environmental signals from the cell membrane can go into the nucleus via signal transduction.
-The signal selectively change the reading of our gene, e.g.
-epigenetics regulation, controlling cell behaviors.% including genetics.
-The new understanding is: environmental signals to regulatory protein to DNA to RNA and then to protein.
+The signal selectively changes the reading of our gene, e.g., epigenetics regulation, controlling cell behaviors.% including genetics.
+The new understanding is environmental signals to regulatory protein to DNA to RNA and then to protein.
 Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}.
@@
 %療癒 
-There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process.
-After 8 hours of meditation, the activity of the genes changed.
+Some studies showed the genetic readout of some inflammatory genes in a group of people who went through a meditation process. After 8 hours of meditation, the activity of the genes changed. 
 %You can change your genetic activity by how you change your response to the environment. 
 %to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.
-Becoming aware of the subconscious source of our behavior gives us an opportunity to change our lives by rewriting the programs (in subconscious mind) of limitation or the things that interfere with us.
+Becoming aware of our behavior's subconscious source allows us to change our lives by rewriting the programs (in the subconscious mind) of limitation or the things that interfere with us.
 Warburg effect\cite{Warburg1956}\cite{Chang2017b} is an example of carcinogenesis, metabolic reprogramming cells by some environmental factors.
@@
 Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage.
-These programs were acquired from other people, not from ourselves, with survival advantage.
+These programs were acquired from other people, not from ourselves, with a survival advantage.
 Being subconscious, these programs are occurring without conscious recognition and awareness. 
-It effects on epigenetic regulation.
+It affects epigenetic regulation.
 Genes are not self-actualizing.
@@
 %Less than 1\% of disease is associated with genetics. 
-Over 90\% of disease is a total reflection of environment and especially our programming.
+Over 90\% of disease is a total reflection of the environment and especially our programming.
 %the disempowering, self-sabotaging behaviors that we acquired in the first 7 years.
 %the cell membrane through receptors picking up the signals and translating them into biology, which then sends signals into the nucleus, which then controls the genetic activity.
-The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from brain, in terms of cell alteration in DNA methylation, mutation, mRNA expression.
-Carcinogenesis will occurs if the reprogramming is persistent in a longer period of time.
+The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression.
+Carcinogenesis will occur if the reprogramming is persistent for a longer time.
 Moreover, long-term stress could be correlated with cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021},
 and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}. %HNSCC
-Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses.
-Additional work has shed light on the potential molecular mechanisms by which early adversity becomes “biologically embedded” in altered physiology across body systems.\cite{Berens2017}
+Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses.
+Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}
 %%%%%
@@
 %% TCGA new holistic features %%%%%
-In summary of our current study, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
+Our current study summarizes those six candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
 Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
-The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin so far.
+The important input $X_1...X_n$ should be patients' features: age, specific six gene expressions, clinical T stage, and surgical margin so far.
 When we consider the survival prediction model again,
@@
 We suggest TCGA should cover more holistic features:
-cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors.
-Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
-The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
+cortisol is one of the most common objective outcomes studied in psychoneuroimmunological (PNI) factors.
+Other factors are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
+The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
 %冤親債主的意念 unknown X factors 回到我們的文章
@@
 % holistic EHR
-Moreover, we encourage that physician might write their electric healthcare record (EHR) in a "holistic way".
+Moreover, we encourage physicians to write their electric healthcare record (EHR) in a "holistic way".
 % Deep Patient:  
@@
 %https://mos2718.github.io/FHIRspec/Spec/Patient/EHR_Patient.docx
-In Taipei Medical University Hospital, holistic-enabled EHR has been designed as holistic dental chart for our outpaitent with psycho-social-spiritual evaluation\cite{Ling-ChengMong2021}:\\
+In Taipei Medical University Hospital, holistic-enabled EHR has been designed as the holistic dental chart for our outpatient with psycho-social-spiritual evaluation\cite{Ling-ChengMong2021}:\\
 1. Emotional: stable/depression/ anxiety/ agitated/ perplexed\\
@@
 <Habits>\\
--Tobacco: 1.5 pack/day for 30 years\\
+-Tobacco: __ pack/day for __ years\\
 -Alcohol drinking: Occasionally\\
--Betel nuts: 30 nuts/day for 30 years\\
+-Betel nuts: __ nuts/day for __ years\\
 <Social/Economic Evaluation>\\
@@
 %# 懺悔
-We always educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the pass, and sincere thanks for the hard work of our physical body.
+We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body does hard work.
 Mindfulness and meditation will be helpful in cancer healthcare.
-Once holistic feature is available, graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
+Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
 The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.

### 2021-03-15 main.tex
Updates from Overleaf

@@
 <Habits>\\
--Tobacco: __ pack/day for __ years\\
+-Tobacco: \underline{ }\underline{ } pack/day for \underline{ }\underline{ } years\\
 -Alcohol drinking: Occasionally\\
--Betel nuts: __ nuts/day for __ years\\
+-Betel nuts: \underline{ }\underline{ } nuts/day for \underline{ }\underline{ } years\\
 <Social/Economic Evaluation>\\

### 2021-03-16 main.tex
{fig:figure5}

@@
 
-*** make Figure 5 holistic:
+%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
+\begin{figure}[hp]
+\centering
+\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
+\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
+{
+[Carcinogenesis] Under the mind-brain-body axis, a stressful environment will trigger the emotional reception.
+The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.
+The inner environment of physical body (cells) alter epigenetic control in terms of gene regulation and mRNA expression.
+In a long time of incubation, the tissue/cells will be transformed into dysplasia then malignancy.\\
+[Cancer care] Holistic care should take care of spiritual, emotional, physical and socioeconomic needs of cancer patients.
+Physical care will be carried out by medication therapy or surgery.
+After establishment of therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recovery their self-compassion to gain the resilience against the disease.
+[Suggested health care record] Beside physical, pathological, or psychological data, electric healthcare record (EHR) and \acrshort{tcga} should collect "holistic features".
+}
+\label{fig:figure5}
+\end{figure}
 %meridian and emotion has mutual reaction
@@
 %#正念 除了可以減壓，還可以治癒疼痛
-%Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
+% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
 

### 2021-03-16 main.tex
Updates from Overleaf

--- 2021-03-15 main.tex
@@
 
-*** make Figure 5 holistic:
+%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
+\begin{figure}[hp]
+\centering
+\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
+\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
+{Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception.
+The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.
+The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression.
+In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
+Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs.
+Physical care will be carried out by medication therapy or surgery.
+After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
+Suggested health care record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
+\label{fig:figure5}
+\end{figure}
 %meridian and emotion has mutual reaction

### 2021-03-16 main.tex
Updates from Overleaf

@@
 % Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
-Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status.
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status. (see Figure \ref{fig:figure5})
 %
@@
 The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
+(see Figure \ref{fig:figure5})
 %身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
@@
 Conversely, dopamine, oxytocin, vasopressin, and growth hormone will be released by the central nervous system in response to the perception of love.
+% Arginine vasopressin (AVP) and oxytocin (OXT) are two centrally released neuropeptides that are involved in shaping essential social behaviors, like aggression, social recognition, and social motivation.
 %Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
@@
 The new understanding is environmental signals to regulatory protein to DNA to RNA and then to protein.
-Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}.
+Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}. (see Figure \ref{fig:figure5})
 % so do the cancer
@@
 Carcinogenesis will occur if the reprogramming is persistent for a longer time.
+(see Figure \ref{fig:figure5})
 Moreover, long-term stress could be correlated with cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021},
@@
 %# 懺悔
-We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body does hard work.
+We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body's hard working.
 Mindfulness and meditation will be helpful in cancer healthcare.
@@
 \bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
-{Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception.
+{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception.
 The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.

### 2021-03-16 main.tex
Updates from Overleaf

@@
 %(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)
+
+%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
+\begin{figure}[hp]
+\centering
+\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
+\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
+{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception.
+The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.
+The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression.
+In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
+Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs.
+Physical care will be carried out by medication therapy or surgery.
+After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
+Suggested healthcare record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
+\label{fig:figure5}
+\end{figure}
+%meridian and emotion has mutual reaction
+%meridian effect tissue and organ
+%(autonomic nerve system, myofascial network, prefrontal cortex)
+%placebo-effect influence on drug discovery
+%gene expression in deep learning
+%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
+%慈悲心 利他心
+%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
+%#正念 除了可以減壓，還可以治癒疼痛
+% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
 
@@
 
-%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
-\begin{figure}[hp]
-\centering
-\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
-\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
-{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception.
-The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.
-The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression.
-In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
-Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs.
-Physical care will be carried out by medication therapy or surgery.
-After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
-Suggested health care record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
-\label{fig:figure5}
-\end{figure}
-%meridian and emotion has mutual reaction
-%meridian effect tissue and organ
-%(autonomic nerve system, myofascial network, prefrontal cortex)
-%placebo-effect influence on drug discovery
-%gene expression in deep learning
-%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
-%慈悲心 利他心
-%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
-%#正念 除了可以減壓，還可以治癒疼痛
-% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
-
 We also aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on all the TCGA or other in-house cancer datasets.

### 2021-03-16 main.tex
TMWH

@@
 \Author{
-Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
-Michael Hsiao $^{3}$*
-and Yu-Chuan (Jack) Li $^{1,4}$*\orcidB{}}
+Li-Hsing Chi $^{1,2,3}$\orcidA{}, Alexander TH Wu $^{1}$,
+Michael Hsiao $^{4}$*
+and Yu-Chuan (Jack) Li $^{1,5}$*\orcidB{}}
 %\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
@@
     Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
+
+%Director,
 $^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip, 
+    Taipei Municipal Wanfang Hospital\unskip, Taipei\unskip, Taiwan\\
+
+$^{3}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
     Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
-$^{3}$ \quad Genomics Research Center\unskip, 
+
+$^{4}$ \quad Genomics Research Center\unskip, 
     Academia Sinica\unskip, Taipei\unskip, Taiwan\\
-$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
+$^{5}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
 }
@@
 %discussion: the third limitation
-There are eighty-one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
+There are eighty-one ($X_1 ... X_{81}$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
 % since it has comprehensive clinical features, 
@@
 %Y$:\\[0.3cm]
-$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
-gene expression is not an independent $X_{mrna}$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
+$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\[0.5cm]
+Gene expression is not an independent $X_{mrna}$. It could be correlated with other\\ $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
 There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
@@
 6. Impact to life: financial problem/ family problem\\
-7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[2cm]
+7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[0.5cm]
 
@@
 Religion: Nil\\
-Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No\\
+Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No
 % cancer cure (care) 的證明
 %# 懺悔
+
 We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body's hard working.

### 2021-03-16 main.tex
Updates from Overleaf

@@
 Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
-This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
+%This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
 %啟蒙運動
@@
 The signal selectively changes the reading of our gene, e.g., epigenetics regulation, controlling cell behaviors.% including genetics.
-The new understanding is environmental signals to regulatory protein to DNA to RNA and then to protein.
+The central dogma of molecular biology should be modified as environmental signals to regulatory protein to DNA to RNA and then to protein.
 Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}. (see Figure \ref{fig:figure5})
@@
 %療癒 
-Some studies showed the genetic readout of some inflammatory genes in a group of people who went through a meditation process. After 8 hours of meditation, the activity of the genes changed. 
+Some studies showed that after 8 hours of meditation, the expression of some inflammatory genes changed\cite{Gustafson2017}.
 %You can change your genetic activity by how you change your response to the environment. 
@@
 %70\% %對於健康有不良影響 => 卻是惡劣競爭下的生存技能
-Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage.
+%Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage.
 These programs were acquired from other people, not from ourselves, with a survival advantage.
-Being subconscious, these programs are occurring without conscious recognition and awareness. 
-It affects epigenetic regulation.
+Being subconscious, those programs acquired from other people before age 7, are occurring without conscious recognition and awareness. 
+The survival advantage programs, such as limitation, disempowerment, and self-sabotage, will affect epigenetic regulation.
 Genes are not self-actualizing. 
-The control of genes is not due to any inherent activity in the DNA itself.
-The change of genetic activity is due to the interaction of the cell with environmental signals.
+The regulation of genetic activity is due to the interaction of the cell with environmental signals.
+Genes are not self-actualizing. %The control of genes is not due to any inherent activity in the DNA itself. 
+The regulation of genetic activity is due to the interaction of the cell with environmental signals.
 %Less than 1\% of disease is associated with genetics. 
@@
 and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}. %HNSCC
-Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses.
-Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}
+Adverse psychosocial experiences in early life, such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased risk of diabetes, heart disease, cancers, and psychiatric illnesses.
+The possible molecular mechanisms could be related with the mind-brain-body axis\cite{Berens2017}.
+%Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}
 %%%%%

### 2021-03-16 main.tex
Turnitin done

@@
 Similarly, there are few existing studies that utilize standardized religious or spiritual measures with PNI outcome measures.
-Findings suggest that mindfulness-breathing-stretching interventions appear to offer potential improvement or stabilization of neuroendocrine-immune activity in breast cancer survivors compared to control groups.
-This review revealed a positive pattern between spiritually-based interventions and several PNI biomarker outcomes, suggesting that spiritually-based interventions offer positive mental and physiological health benefits.
-For breast cancer survivors, these studies suggested that engaging in spiritually-based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.
+Findings suggest that mindfulness meditation could stabilize neuroendocrine-immune activity (measured by PNI biomarkers) in breast cancer patients comparing to control groups\cite{Hulett2016}.
+%This review revealed a positive pattern between spiritually-based interventions and several PNI biomarker outcomes, suggesting that spiritually-based interventions offer positive mental and physiological health benefits.
+%For breast cancer survivors, these studies suggested that engaging in spiritually-based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.
 %From a PNI perspective, future spiritually based interventions should include standardized measures of religiousness and spirituality in order to understand relationships between and among religiousness, spirituality, and neuroendocrine-immune outcomes.
@@
 In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo.
-If I had thought of any internal medicine, it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}.
-Cullen studied the objective science of analytical chemistry.
-He also sensed that the patient's subjective, psychosomatic, or "sympathetic constitution" determined his reaction to a prescribed therapeutic substance.
-Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with the psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
-Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
+If I had thought of any internal medicine, it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}
+Cullen studied the objective science of analytical chemistry. He also studied that the patient's therapeutic response could be influenced by his
+subjective, psychosomatic, or "sympathetic constitution"\cite{Kerr2008}.
+%Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with the psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
+Cullen's theory of sympathy (or empathy) is a mind-body therapeutics, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
 %This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
 %啟蒙運動
-Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction centred on a physician's therapeutic intentions to patient sympathy\cite{Sapin2014}.
+%Cullen found the power of mind-body interaction that a physician's therapeutic intentions could be triggered by sympathy\cite{Sapin2014}.
 %How does placebo effect work in patient's internal environment?  %改造患者的心，就能改造他的身體環境，有利消除癌症
@@
 %sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
-The physician's role was to be a gentle, sympathetic listener who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, either by prescribing placebos to please (influence the patients' emotional states) medicine to cure the patient's disorder.
+The physician could listen and interpret the patient's sympathetic disorder and select either placebos to please (influence the patients' emotional states) or medicine to cure the patient's disorder.
 %placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。

### 2021-03-17 main.tex
Updates from Overleaf

@@
 The above mentioned web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
-There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
-cutpointr), and cutoffR (available at https://cran.r-project.org/web/
+There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
 packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
@@
 Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
+
+%注意 強調GSE2837: 
+The prognostic significance of the candidate genes has been validated by an independent patient cohort.
+
+% validation by GSE2837 cohort (with web-tools)
+%\subsubsection*{GSE2837} % non-TCGA
+% from Anwser2-2
+%by GEO GSE2837 HNSCC dataset (PrognoScan)
+After the discovery with our workflow, we validated the suggested 20 biomarkers in the other \acrshort{hnscc} cohort.
+The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
+1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
+2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
+%17 out of 20 candidates
+%?DKK1 (0.253635), 
+%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
+%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
+%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
+The 10 out of 20 candidates are confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
 
@@
 
-In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+In summary, those ten candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
 Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
-The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
+The important input $X_1...X_n$ should be patients' features: age, specific ten gene expressions, clinical T stage, and surgical margin.
 %\\[0.5cm]
+% total 6+4 =10
+% After validation with an independent \acrshort{hnscc} cohort (GSE2837), the result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
+%Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
 
@@
 %%%%
-\subsection{Feature selection for survival modeling} % Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
+\subsection{Feature Selection for Survival Modeling} % Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
 % TCGAbiolinks
@@
 
-\subsection{Validation by web-based tools}
-%注意 強調GSE2837: 
-The prognostic
-significance of the candidate genes has been validated by an independent patient cohort.
-
-%\subsubsection*{GSE2837} % non-TCGA
-% from Anwser2-2
-%by GEO GSE2837 HNSCC dataset (PrognoScan)
-After the discovery with our workflow, we validated the suggested 20 biomarkers in the other \acrshort{hnscc} cohort.
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
-%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
-%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005)
-microarray gene expression (by Affymetrix X3P chips U133\_X3P) and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
-The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
-1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
-2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
-%17 out of 20 candidates
-%?DKK1 (0.253635), 
-%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
-%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
-%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
-%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 candidates are confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
+\subsection{Validation by Web-based Tools}
 
@@
 %%%
-\subsection{The candidates shown in literature review}
+\subsection{The Candidates Shown in Literature Review}
 
@@
 
-\subsection{Limitations of the work}
+\subsection{Limitations of the Work}
 
@@
 
-\subsection{Future research directions}
-\subsubsection{Laboratory validation}
+\subsection{Future Direction in Translational Medicine}
+
+\subsubsection{Laboratory Validation}
 It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
@@
 %****************%
-\subsubsection{Holistic cancer care} 
+\subsubsection{Holistic Cancer Care} 
 % carcinogenesis by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system.
@@
 We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body's hard working.
-Mindfulness and meditation will be helpful in cancer healthcare.
+Since mindfulness meditation will be helpful in cancer healthcare.
 Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
-The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
 %  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
 %七情: 喜、怒、思、悲、恐、驚、憂
-
-We also aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on all the TCGA or other in-house cancer datasets.
-%the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
 %with more TCGA features (holistic)
@@
 It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
-We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].\newline
-Fire.Rda".
+We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].Fire.Rda".
 After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
@@
 
-We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.\linebreak
-Fire.Rda" (accessed November 2019).
-
-One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.\newline
-[GeneName].Fire.Rda" tables were transposed and merged by their \newline
-\_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
+We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.Fire.Rda" (accessed November 2019).
+%\linebreak or \newline
+
+One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.[GeneName].\\
+Fire.Rda" tables were transposed and merged by their \_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
 The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
@@
 
-\subsection{Biomarker Selection}
+\subsection{Biomarker Selection and Validation}
 
@@
 Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
+
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005)
+microarray gene expression (by Affymetrix X3P chips U133\_X3P) and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
 
@@
 %tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases
-We wish this bioinformatics tool will be available for the broad usage of tumor-agnostic research\cite{Looney2020} to crossing several \acrshort{tcga} diseases to make translational impacts.
+We wish this workflow will be available for the reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} and tumor-agnostic research\cite{Looney2020} to crossing several \acrshort{tcga} diseases to make translational impacts.
 %Tex: PvalueTex
-
-We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
-TCGA has not collected holistic features.
+% the broad usage
+%We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
+%TCGA has not collected holistic features so far.
+The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using holistic multi-parametric approaches.
+
+%the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-03-17 main.tex
Updates from Overleaf

@@
 %注意 強調GSE2837: 
-The prognostic significance of the candidate genes has been validated by an independent patient cohort.
-
+%The prognostic significance of the candidate genes has been validated by an independent patient cohort.
 % validation by GSE2837 cohort (with web-tools)
@@
 %by GEO GSE2837 HNSCC dataset (PrognoScan)
-After the discovery with our workflow, we validated the suggested 20 biomarkers in the other \acrshort{hnscc} cohort.
+After the discovery with our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
 The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
@@
 \hline
-DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                & **                                          \\
-\hline
-CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & **                                          \\
-\hline
-STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                & **                                          \\
-\hline
-PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & **                                          \\
-\hline
-SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & 3                                           \\
-\hline
-USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & **                                          \\
-\hline
-NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & 6                                           \\
-\hline
-FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & **                                          \\
-\hline
-STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                & **                                          \\
-\hline
-DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                & **                                          \\
+DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                &                                           \\
+\hline
+CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & \checkmark                                          \\
+\hline
+STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                &                                           \\
+\hline
+PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & \checkmark                                          \\
+\hline
+SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & \checkmark                                           \\
+\hline
+USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & \checkmark                                         \\
+\hline
+NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & \checkmark                                           \\
+\hline
+FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & \checkmark                                          \\
+\hline
+STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                &                                           \\
+\hline
+DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                &                                           \\
 \hline
@@
 \hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: number of articles related with cancer research; ** as many~}                                                                                                                                                                                                                                                                                                                                                             \\
+\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\
 \hline
@@
 
-%\subsubsection{Table3/legend}
+%\subsubsection{Table3/legend} or Table 2?
 %Table3. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
@@
 \cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} & 0                                             \\
+ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\
 \cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           & 1                                             \\
-\hline
-IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & 14                                            \\
-\hline
-MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           & 0                                             \\
-\hline
-FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           & **                                            \\
-\hline
-LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           & 1                                             \\
-\hline
-EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           & 0                                             \\
-\hline
-PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           & 5                                             \\
-\hline
-KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           & 0                                             \\
-\hline
-NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           & 4                                             \\
+ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\
+\hline
+IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & \checkmark                                            \\
+\hline
+MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\
+\hline
+FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &  \checkmark                                           \\
+\hline
+LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\
+\hline
+EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\
+\hline
+PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\
+\hline
+KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &   \checkmark                                           \\
+\hline
+NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &      \checkmark                                        \\
 \hline
@@
 \hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: \textit{P} value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\ * Cox's model: \textit{P} value \textless{} 0.001\\lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
 \hline
@@
 \acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
-The tables were generated by latex code with the help from https://github.com/JDMCreator/\newline
-LaTeXTableEditor.
+The tables were generated by latex code with the help from https://github.com/JDMCreator/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
 We like to thank Dr. Wen-Chang Wang,

### 2021-03-17 main.tex
new Table 3 and Table 4

@@
 
-%\subsubsection{Table2/legend}
+\subsubsection{Table3/legend} Table 3
 %Table 2. Univariate/Multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in HNSCC.
@@
 \centering
-\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in \acrshort{hnscc}}
+\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of CAMK2N1 gene expression in HNSCC}
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 \begin{tabular}{|l|l|l|l|l|l|l|l|} 
+%\begin{tabularx}{\textwidth}{|p{2.5cm}|l|l|l|l|l|l|l|} 
 \arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
+\multicolumn{2}{|l!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
 \cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                              \\
+\multicolumn{2}{|l!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{l!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{l!{\color{black}\vrule}}{\textit{P}~value}                    & \multicolumn{1}{l!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{l!{\color{black}\vrule}}{\textit{P}~value}                     \\
 \arrayrulecolor{black}\hline
@@
 \cline{2-8}
-                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.178                                                                          & 0.841-1.650                                                                   & 0.342                                                                          \\
+                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.076                                                                          & 0.767-1.510                                                                   & 0.671                                                                          \\
 \arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
-\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}=65y                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
 \cline{2-8}
-                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.462                                                                          & 1.078-1.983                                                                   & \textcolor{red}{0.015}                                                         \\
+                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.391                                                                          & 1.025-1.888                                                                   & \textcolor{red}{0.034}                                                         \\
 \hline
@@
 \cline{2-8}
-                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 1.978                                                                          & 1.046-3.737                                                                   & \textcolor{red}{0.036}                                                         \\
+                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 1.982                                                                          & 1.048-3.745                                                                   & \textcolor{red}{0.035}                                                         \\
 \hline
@@
 \cline{2-8}
-                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.149                                                                          & 0.805-1.640                                                                   & 0.445                                                                          \\
+                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.145                                                                          & 0.801-1.636                                                                   & 0.457                                                                          \\
 \hline
@@
 \cline{2-8}
-                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor{red}{0.049}                                                        & 6.513                                                                          & 1.415-29.96                                                                   & \textcolor{red}{0.016}                                                         \\
+                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.644                                                                  & \textcolor{red}{0.049}                                                        & 7.314                                                                          & 1.590-33.631                                                                  & \textcolor{red}{0.011}                                                         \\
 \hline
@@
 \cline{2-8}
-                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.597                                                                          & 0.277-1.287                                                                   & 0.188                                                                          \\
+                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.621                                                                          & 0.287-1.343                                                                   & 0.226                                                                          \\
 \hline
@@
 \cline{2-8}
-                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.601                                                                          & 1.159-2.211                                                                   & \textcolor{red}{0.004}                                                         \\
+                                        & Positive                                                                            & 1.591                                                                          & 1.155–2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.631                                                                          & 1.182-2.250                                                                   & \textcolor{red}{0.003}                                                         \\
 \hline
@@
 \cline{2-8}
-                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.302                                                                          & 0.943-1.797                                                                   & 0.109                                                                          \\
+                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.363                                                                          & 0.990-1.875                                                                   & 0.058                                                                          \\
 \hline
@@
 \cline{2-8}
-                                        & High                                                                                & 2.266                                                                          & 1.666-3.082                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & 2.135                                                                          & 1.559-2.924                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                      \\
+                                        & High                                                                                & 2.101                                                                          & 1.572-2.809                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & 2.007                                                                          & 1.490-2.704                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                      \\
 \hline
@@
 \hline
-\multicolumn{8}{|l|}{(\textit{P} value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\multicolumn{8}{|l|}{(\textit{P}~value significant codes is denoted: red \textless{} 0.05; *** \textless{} 0.001)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               \\
 \hline
 \end{tabular}
-}
+} % end of \resizebox
 \arrayrulecolor{black}
@@
 
-%\subsubsection{Table4/legend}
+\subsubsection{Table4/legend} Table 4
 \begin{table}[!hp]
 \centering
-\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of ZNF557 gene expression in \acrshort{hnscc}}
+\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of IL19 gene expression in HNSCC}
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
 \resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|} 
+\begin{tabular}{|l|l|l|l|l|l!{\color{black}\vrule}l!{\color{black}\vrule}l!{\color{black}\vrule}} 
 \arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\
+\multicolumn{2}{|l!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                    \\
 \cline{3-8}
-\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                              \\
+\multicolumn{2}{|l!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{l!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{l!{\color{black}\vrule}}{\textit{P}~value}                    & HR                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%} & \textit{P}~value                           \\
 \arrayrulecolor{black}\hline
-\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}}  \\
+\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
 \cline{2-8}
-                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.163                                                                          & 0.833-1.625                                                                   & 0.375                                                                          \\
-\arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
-\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
-\cline{2-8}
-                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.328                                                                          & 0.976-1.808                                                                   & 0.071                                                                          \\
-\hline
+                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.183                                & 0.847-1.652                                      & 0.325                                      \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}=65y                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.481                                & 1.087-2.018                                      & \textcolor{red}{0.013}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
 \multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
-\cline{2-8}
-                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor[rgb]{1,0.149,0}{0.033}                                             & 1.961                                                                          & 1.035-3.714                                                                   & \textcolor[rgb]{1,0.149,0}{0.039}                                              \\
-\hline
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 2.175                                & 1.152-4.106                                      & \textcolor{red}{0.017}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
 \multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
-\cline{2-8}
-                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.179                                                                          & 0.824-1.686                                                                   & 0.367                                                                          \\
-\hline
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.237                                & 0.864-1.770                                      & 0.245                                      \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
 \multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
-\cline{2-8}
-                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor[rgb]{1,0.149,0}{0.049}                                             & 8.478                                                                          & 1.847-38.92                                                                   & \textcolor[rgb]{1,0.149,0}{0.006}                                              \\
-\hline
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.644                                                                  & \textcolor{red}{0.049}                                                        & 8.629                                & 1.879-39.63                                      & \textcolor{red}{0.006}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
 \multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
-\cline{2-8}
-                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.512                                                                          & 0.239-1.096                                                                   & 0.085                                                                          \\
-\hline
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.476                                & 0.222-1.024                                      & 0.057                                      \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
 \multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
-\cline{2-8}
-                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor[rgb]{1,0.149,0}{0.004}                                             & 1.631                                                                          & 1.180-2.254                                                                   & \textcolor[rgb]{1,0.149,0}{0.003}                                              \\
-\hline
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & Positive                                                                            & 1.591                                                                          & 1.155–2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.63                                 & 1.180-2.252                                      & \textcolor{red}{0.003}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
 \multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
-\cline{2-8}
-                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor[rgb]{1,0.149,0}{0.044}                                             & 1.453                                                                          & 1.055-2.000                                                                   & \textcolor[rgb]{1,0.149,0}{0.022}                                              \\
-\hline
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.62                                 & 1.173-2.238                                      & \textcolor{red}{0.003}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
 \multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
-\cline{2-8}
-                                        & High                                                                                & 0.465                                                                          & 0.348-0.619                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                          & 0.499                                                                          & 0.372-0.669                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                           \\
-\hline
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & High                                                                                & 0.472                                                                          & 0.351-0.635                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & \multicolumn{1}{l|}{0.459}           & 0.340-0.619                                      & \multicolumn{1}{c|}{\textcolor{red}{***}}  \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{1-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{8-8}
 \multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \\
 \hline
-\multicolumn{8}{|l|}{(\textit{P} value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\
+\multicolumn{8}{|l|}{(\textit{P}~value significant codes is denoted: red \textless{} 0.05; *** \textless{} 0.001)}                                                                                                                                                                                                                                                                                                                                                                                                    \\
 \hline
 \end{tabular}
-}
+}% end of \resizebox
 \arrayrulecolor{black}

### 2021-03-18 main.tex
new Figure_4_CAMK2N1_IL19.pdf
Updates from Overleaf

@@
 Dotted line: significant Bonferroni corrected \textit{P} value. 
-\textcolor{red}{Red circles} mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green circles} mark 10 genes, which affect on better survival ($HR<=0.5$).}
+\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$).
+\textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).}
 \label{fig:figure3}
@@
 
-Our top 1 candidate is \acrfull{DKK1}.
-The Kaplan-Meier curve reveals 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate.
+After validated by GSE2837, our top 1 candidate is \acrfull{CAMK2N1}.
+The Kaplan-Meier curve reveals 227 patients bearing the higher expression of \acrshort{CAMK2N1} were suffered from only 40\% of 5-year \acrshort{os} rate.
 In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) had a better prognosis (adjusted \textit{P} = $0.001$) (see Figure \ref{fig:figure4}(a)).
@@
 The smallest \textit{P} value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), has been defined as an optimal \textit{P} value.
-Conversely, the most associated gene with better survival is \acrfull{ZNF557}.
-In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 264 patients bearing the higher expression of \acrshort{ZNF557} had 55\% of 5-year OS survival rate (adjusted \textit{P} = $0.001$).
+Conversely, the most associated gene with better survival is \acrfull{IL19}.
+In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 264 patients bearing the higher expression of \acrshort{IL19} had 55\% of 5-year OS survival rate (adjusted \textit{P} = $0.001$).
 The cutoff finding procedure (cutofFinder\_func.R) generated cumulative \textit{P} value plot in Figure \ref{fig:figure4}(d).
@@
 \centering
-\includegraphics[width=15cm]{Figure4.pdf}
+\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
 \bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
-{(a) Kaplan-Meier plot of DKK1 under optimal \textit{P} value, and (b) the cutoff is derived from cumulative \textit{P} value plot of DKK1.
-(c) Kaplan-Meier plot of ZNF557 under optimal \textit{P} value, and (d) the cutoff is derived from cumulative \textit{P} value plot of ZNF557.}
+{(a) Kaplan-Meier plot of CAMK2N1 under optimal \textit{P} value, and (b) the cutoff is derived from cumulative \textit{P} value plot of CAMK2N1.
+(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value, and (d) the cutoff is derived from cumulative \textit{P} value plot of IL19.}
 \label{fig:figure4}
@@
 Table \ref{table:table1} shows ten overexpressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value.
-We found their Cox's univariate and multivariate HR are all greater than 1.837. 
+Six out of ten genes has been validated by using GSE2837.
+We found those six candidates have the Cox's univariate and multivariate HR above 1.914.
 %There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
-In Table \ref{table:table2},
-after adjustment of confounders, \acrshort{DKK1} overexpression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
+In Table \ref{table:table2}, % table 3
+after adjustment of confounders, \acrshort{CAMK2N1} overexpression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
 Older age (more than 65) also worse the survival (HR 1.462 [95\% CI: 1.078-1.983, \textit{P} = 0.015]). 
@@
 In Table \ref{table:table3}, the other ten overexpressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
+Four out of ten has been validated by using GSE2837.
 In Table \ref{table:table4},
 after adjustment of confounders, prognosis is influenced by advance clinical T Status (HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] ), positive surgical margin involvement (HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003]) , and higher tobacco exposure (HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022]).
-Overexpressed \acrshort{ZNF557} gene could has a protective influencce on prognosis (HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001]).
+Overexpressed \acrshort{IL19} gene could has a protective influencce on prognosis (HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001]).
 
@@
 \subsection{Validation by Web-based Tools}
-
-%
+% GSE2837 validated candidates: 10
 We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
@@
 SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
-Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
-1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);\\
-%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).\\
-%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 6 genes:\\ % SurvExpress 有類似的結果:
+1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
+%, STIP1 (0.001), DKC1 (0.01);\\
+%DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: FCGBP (0.001).\\
+%ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
 %17 out of 20 candidates
 %?DKK1 (0.253635),
-The 12 out of 20 candidate genes are confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
+The 6 out of 10 candidate genes are also confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
 % moved to supplementary file: Supplementary_figures.tex
+% \linksupplementary{Supplementary_figures.pdf},
 
 % % SurvExpress 沒有類似的結果是因為:
-Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
-Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+%Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
+Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
+Our workflow has the advantage to find ai optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
 %因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
@@
 All transcriptomics data has been retrieved from the TCGA, and all proteomics data has been generated in-house using the same antibodies.
-Our 9 candidates (e.g., DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
-The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+Our 5 candidates (e.g.
+CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+FCGBP is on the list of favorable prognostic genes as well.
+% DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
+% ZNF557, ZNF266, and FCGBP
 Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+\\cancer)\cite{Ren2020}.
@@
 Since the discovery of workflow, we performed the literature review by Embase/Pubmed.% to find the evidence convincing the suggested biomarkers in cancer research. 
-The 10 out of 20 candidates has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+The 5 out of 10 candidates has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
 
@@
 %%%%%% bad guy
-The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
+%The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
 Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
@@
 %STC2:
-The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway\cite{Ma2020}.
+%The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway\cite{Ma2020}.
 
@@
 % STIP1; non-TCGA
-Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. 
+%Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}.
 The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
@@
 
-\acrfull{LOC148709} has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
+%\acrfull{LOC148709} has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
 In our current study, LOC148709 is also suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3} on page \pageref{table:table3}).
@@
 % PNMA5
-Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}.
+%Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}.
 

### 2021-03-19 main.tex
TCIA return

@@
 %by GEO GSE2837 HNSCC dataset (PrognoScan)
-After the discovery with our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
+After the discovery by our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
 The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
@@
 %Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 candidates are confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
+The 10 out of 20 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
+Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
 
@@
 
-\subsubsection{Table3/legend} Table 3
+%\subsubsection{Table3/legend} Table 3
 %Table 2. Univariate/Multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in HNSCC.
@@
 
-\subsubsection{Table4/legend} Table 4
+%\subsubsection{Table4/legend} Table 4
 \begin{table}[!hp]
@@
 陽明交大
+
+%***
+
+\subsubsection{TCIA validation by deep learning}
+%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
+%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
+TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
+%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
+
+OFA:  TCIA for whole slide deep learning
+IL19 is a candidate marker
+TCPA modeling: Y (RNA-seq) ← X (slide represents gene expression)
+Apply model on TMUH HNSCC test cohort (with survival outcome):
+Y (survival) ← X (slide represents gene expression)
+(as IL19 validation, to see is it still a biomarker)
+%x The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
+%https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447; there is few HNSCC slides
+
+%Manning meap book: 不再是黑盒子
+%https://www.manning.com/books/trust-in-machine-learning
+Trust in Machine Learning *** interpretable or explainable CNN
+By saliency mapping: e.x. diabetes retinopathy, model focused on retinal artery
+%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
+%#XAI
+Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data\cite{Hao2019a}
+By PyTorch
+
+%https://www.deeplearningbook.org/
+image-based phenotypes could be correlated with their underlying genomics data 
+TMA by deep learning (CNN) mRNA expression associated with pathological images
+*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, digital TMA
+%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
+%https://github.com/Serian1992/ImgBio.
+%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
+% NCI
+Aiding the Genomics Characterization of Tumors: 
+deep learning could predict commonly mutated genes and mRNA expression from the images
+*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
+Preprocessing of whole-slide images.
+The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets.
+We divided the whole-slide images into squares of 112 × 112 $\mu$m (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
+We sampled a maximum of 8000 such tiles from each slide.
+We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
+For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster.
+The use of these supertiles reduces the dimensions of a slide to 100 × 2048.
+The model was first trained on this reduced dataset, with all the TCGA data.
+Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.
+
+%AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
+For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas.
+Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.
+
+Understanding the Method Behind the Machine: interpredability
+
+%One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process.
+For example, a DL algorithm that predicts the optimal treatment for a patient does not provide the reasoning it used to make that prediction.
+Additional efforts are needed to reveal how algorithms arrive at a decision or prediction so that the process becomes transparent to scientists and clinicians.
+Making these algorithms transparent could help researchers identify new biological features relevant to disease diagnosis or treatment.
+***  unconscious biases:
+Incorporating information about biological processes into the algorithm is likely to improve its accuracy and decrease dependence on large amounts of annotated data, which may not be available.
+One danger of the “black box” problem is that DL may inadvertently perpetuate existing unconscious biases.
+Researchers need to carefully consider how potential biases affect the data being used to develop a model, adopt practices to address and monitor those biases, and monitor performance and applicability of AI models.
+
+%With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk.
+Updated: August 31, 2020
+%
 

### 2021-03-19 main.tex
Updates from Overleaf

@@
 After validated by GSE2837, our top 1 candidate is \acrfull{CAMK2N1}.
-The Kaplan-Meier curve reveals 227 patients bearing the higher expression of \acrshort{CAMK2N1} were suffered from only 40\% of 5-year \acrshort{os} rate.
-In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) had a better prognosis (adjusted \textit{P} = $0.001$) (see Figure \ref{fig:figure4}(a)).
-Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot shows that the uncorrected 116 \textit{P} values ($< 0.05$) have been estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
-The smallest \textit{P} value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), has been defined as an optimal \textit{P} value.
+The Kaplan-Meier curve reveals 152 patients bearing the higher expression of \acrshort{CAMK2N1} were suffered from only 35\% of 5-year \acrshort{os} rate.
+In comparison, the other 262 patients with lower expression (the cutoff at 0.027(RSEM)) had a better prognosis (adjusted \textit{P} = $0.002$) (see Figure \ref{fig:figure4}(a)).
+Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot shows that the uncorrected 147 \textit{P} values ($< 0.05$) have been estimated by a serial cut from 144 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
+The smallest \textit{P} value (\num{2.97e-7}), when cut on n=262 (63.3\% of 414), has been defined as an optimal \textit{P} value.
 Conversely, the most associated gene with better survival is \acrfull{IL19}.
-In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 264 patients bearing the higher expression of \acrshort{IL19} had 55\% of 5-year OS survival rate (adjusted \textit{P} = $0.001$).
+In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 215 patients bearing the higher expression of \acrshort{IL19} had 60\% of 5-year OS survival rate (adjusted \textit{P} = $0.002$).
 The cutoff finding procedure (cutofFinder\_func.R) generated cumulative \textit{P} value plot in Figure \ref{fig:figure4}(d).
-The 166 uncorrected \textit{P} values were estimated by a serial cut from 125 to 290 for grouping the cohort.
-The smallest \textit{P} value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
+The 161 uncorrected \textit{P} values were estimated by a serial cut from 125 to 286 for grouping the cohort.
+The smallest \textit{P} value (\num{3.73e-7}), when cut on n=199 (48.1\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.147(RSEM) of \acrshort{rnaseq}.
 %The second candidate, which improving patient survival, is ZNF266.
@@
 In Table \ref{table:table2}, % table 3
-after adjustment of confounders, \acrshort{CAMK2N1} overexpression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]).
-Older age (more than 65) also worse the survival (HR 1.462 [95\% CI: 1.078-1.983, \textit{P} = 0.015]). 
+after adjustment of confounders, \acrshort{CAMK2N1} overexpression is the independent prognostic factor (multivariate HR 2.007 [95\% CI: 1.490-2.704, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.982 [95\% CI: 1.048-3.745, \textit{P} = 0.035]) and surgical margins status (HR 1.631 [95\% CI: 1.182-2.250, \textit{P} = 0.003]).
+Older age (more than 65) also worse the survival (HR 1.391 [95\% CI: 1.025-1.888, \textit{P} = 0.034]). 
 The M stage could be ignored in this cohort due to only 3 out of 414 patients with distant metastasis.

### 2021-03-19 main.tex
Updates from Overleaf

@@
 After the discovery by our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
-The survival significance (Kaplan Meier \textit{P} value) is in the following probes of 10 genes:\\
+The survival significance (Kaplan-Meier \textit{P} value) is in the following probes of 10 genes:\\
 1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
@@
 %Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
+Thus, these 10 out of 20 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
 Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
@@
 %% optional: The data presented in this study are available in supplementary material.
-\supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, Figure S1: The query results from SurvExpress, Figure S2: The query results from HPA, Figure S3: GSE2837 query results from PrognoScan.}
+\supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, 
+Figure S1: GSE2837 analysis by PrognoScan, 
+Figure S2: The query results from SurvExpress, 
+Figure S3: The query results from HPA.}
 %Table S1: title, Video S1: title.}

### 2021-03-19 main.tex
TCIA

@@
 TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
+
 %數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
-
-OFA:  TCIA for whole slide deep learning
+The transcriptomic representation of TCGA learned by HE2RNA.
+TCIA for whole slide deep learning
 IL19 is a candidate marker
@@
 
-%Manning meap book: 不再是黑盒子
-%https://www.manning.com/books/trust-in-machine-learning
-Trust in Machine Learning *** interpretable or explainable CNN
-By saliency mapping: e.x. diabetes retinopathy, model focused on retinal artery
-%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
-%#XAI
-Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data\cite{Hao2019a}
-By PyTorch
-
 %https://www.deeplearningbook.org/
@@
 *** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, digital TMA
+The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
 %https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
@@
 deep learning could predict commonly mutated genes and mRNA expression from the images
-*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
+*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}.
+A HE2RNA model should be trained to systematically predict RNA-Seq profiles from whole-slide images\cite{Schmauch2020}.
 Preprocessing of whole-slide images.
@@
 Understanding the Method Behind the Machine: interpredability
+%Manning meap book: 不再是黑盒子
+%https://www.manning.com/books/trust-in-machine-learning
+Trust in Machine Learning *** interpretable or explainable CNN
+By saliency mapping: e.x. diabetes retinopathy, model focused on retinal artery
+%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
+%#XAI
+Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data\cite{Hao2019a}
+By PyTorch
 

### 2021-03-22 main.tex
Updates from Overleaf

--- 2021-03-19 main.tex
@@
 The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
+PGK1 is responsive in hypoxia status, since it is one of HIF-1\alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.
 
@@
 
-\subsubsection{TCIA validation by deep learning}
+\subsubsection{Transcriptomic Representation by Deep Learning}
 %https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
 %https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
-TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
+%TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
+
 %數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
-
-OFA:  TCIA for whole slide deep learning
-IL19 is a candidate marker
-TCPA modeling: Y (RNA-seq) ← X (slide represents gene expression)
+A deep-learning model, named HE2RNA\cite{Schmauch2020}, could use to encode transcriptomic representation from histological whole slide images of TCGA. 
+%The transcriptomic representation of TCGA learned by HE2RNA.
+%TCIA is for radiomics deep learning
+Even with RNA-Seq data obtained from bulk cells isolated from whole slide images, HE2RNA model has also been able to predict the spatial expression of more than 8,000 genes from the H\&E slide of HNSCC alone.
+GDC store pathology Aperio SVS image. An SVS file is a digital slide image file created by an Aperio ScanScope slide scanner or others.
+CAMK2N1 and IL19 are candidate markers suggested in our current study.
+
+HE2RNA modeling: Y (RNA-seq) ← X (slide represents gene expression)
 Apply model on TMUH HNSCC test cohort (with survival outcome):
@@
 
+% TMU joiny IRB
+We will introduce TMU HNSCC cohort from our joint biobank.
+
+%https://www.deeplearningbook.org/
+image-based phenotypes could be correlated with their underlying genomics data 
+TMA by deep learning (CNN) mRNA expression associated with pathological images
+*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, digital TMA
+
+%The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
+%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
+%https://github.com/Serian1992/ImgBio.
+%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
+% NCI
+Aiding the Genomics Characterization of Tumors: 
+deep learning could predict commonly mutated genes and mRNA expression from the images
+*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}.
+A HE2RNA model should be trained to systematically predict RNA-Seq profiles from whole-slide images\cite{Schmauch2020}.
+%Preprocessing of whole-slide images.
+The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets.
+We divided the whole-slide images into squares of 112 × 112 $\mu$m (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
+We sampled a maximum of 8000 such tiles from each slide.
+We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
+%For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster.
+The use of these supertiles reduces the dimensions of a slide to 100 × 2048.
+The model was first trained on this reduced dataset, with all the TCGA data.
+Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.
+
+%AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
+For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas.
+Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.
+
+Understanding the Method Behind the Machine: interpredability
 %Manning meap book: 不再是黑盒子
@@
 
-%https://www.deeplearningbook.org/
-image-based phenotypes could be correlated with their underlying genomics data 
-TMA by deep learning (CNN) mRNA expression associated with pathological images
-*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, digital TMA
-%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
-%https://github.com/Serian1992/ImgBio.
-%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
-% NCI
-Aiding the Genomics Characterization of Tumors: 
-deep learning could predict commonly mutated genes and mRNA expression from the images
-*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
-Preprocessing of whole-slide images.
-The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets.
-We divided the whole-slide images into squares of 112 × 112 $\mu$m (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
-We sampled a maximum of 8000 such tiles from each slide.
-We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
-For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster.
-The use of these supertiles reduces the dimensions of a slide to 100 × 2048.
-The model was first trained on this reduced dataset, with all the TCGA data.
-Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.
-
-%AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
-For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas.
-Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.
-
-Understanding the Method Behind the Machine: interpredability
-
 %One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process.
@@
 %
+HE2RNA was able to spatialize differentially genes specifically expressed by T cells or B cells, even though discriminating between those two types from their morphology alone is notoriously difficult.
+HE2RNA could be a useful tool for pathologists and oncologists to consistently quantify immune infiltration or guide treatment decision in the context of immunotherapy\cite{Schmauch2020}.
+The practical implications of predicting gene expression level from H\&E slides should be emphasized.
+For example, it could predict molecular profiling from pathology slides, such as the hormonal status of breast cancer cases.
+Recent studies have shown that mRNA and protein expressions may be poorly correlated due to various factors, such as different half-lives and post-transcription machinery.
 

### 2021-03-22 main.tex
HE2RNA moved to Ph.D. dissertation

--- 2021-03-19 main.tex
@@
 %***
-
-\subsubsection{TCIA validation by deep learning}
-%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
-%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
-TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Pytorch/Keras framework)
-%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
-
-OFA:  TCIA for whole slide deep learning
-IL19 is a candidate marker
-TCPA modeling: Y (RNA-seq) ← X (slide represents gene expression)
-Apply model on TMUH HNSCC test cohort (with survival outcome):
-Y (survival) ← X (slide represents gene expression)
-(as IL19 validation, to see is it still a biomarker)
-%x The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
-%https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447; there is few HNSCC slides
-
-%Manning meap book: 不再是黑盒子
-%https://www.manning.com/books/trust-in-machine-learning
-Trust in Machine Learning *** interpretable or explainable CNN
-By saliency mapping: e.x. diabetes retinopathy, model focused on retinal artery
-%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
-%#XAI
-Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data\cite{Hao2019a}
-By PyTorch
-
-%https://www.deeplearningbook.org/
-image-based phenotypes could be correlated with their underlying genomics data 
-TMA by deep learning (CNN) mRNA expression associated with pathological images
-*** TCGA TCIA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, digital TMA
-%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
-%https://github.com/Serian1992/ImgBio.
-%https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
-% NCI
-Aiding the Genomics Characterization of Tumors: 
-deep learning could predict commonly mutated genes and mRNA expression from the images
-*** A deep learning model to predict RNA-Seq expression of tumours from whole slide images\cite{Schmauch2020}
-Preprocessing of whole-slide images.
-The application of deep-learning algo- rithms to histological data is a challenging problem, particularly due to the high dimensionality of the data (up to 100,000 × 100,000 pixels for a single whole-slide image) and the small size of available datasets.
-We divided the whole-slide images into squares of 112 × 112 $\mu$m (224 × 224 pixels) called “tiles”, and used the Otsu algorithm62 (as implemented in python package skimage) to select only those containing tissue, excluding the white background.
-We sampled a maximum of 8000 such tiles from each slide.
-We then extracted 2048 features from those tiles with a 50-layer ResNet63 pretrained on the ImageNet dataset64 (using the Keras implementation), such that a slide could be represented as a 8000 × 2048 matrix.
-For the first phase of this work (transcriptome prediction), we accelerated the training of our models through a simple preprocessing step inspired by simple linear iterative clustering (SLIC)65: we used the k-means algorithm (as implemented in python package libkmcuda) to create 100 clusters (supertiles) of tiles on the basis of tile location on the slide, and we averaged the features of the tiles within each cluster.
-The use of these supertiles reduces the dimensions of a slide to 100 × 2048.
-The model was first trained on this reduced dataset, with all the TCGA data.
-Then, for specific organs, fine-tuning was achieved with full-scale data from the organs concerned only.
-
-%AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing.
-For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas.
-Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.
-
-Understanding the Method Behind the Machine: interpredability
-
-%One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process.
-For example, a DL algorithm that predicts the optimal treatment for a patient does not provide the reasoning it used to make that prediction.
-Additional efforts are needed to reveal how algorithms arrive at a decision or prediction so that the process becomes transparent to scientists and clinicians.
-Making these algorithms transparent could help researchers identify new biological features relevant to disease diagnosis or treatment.
-***  unconscious biases:
-Incorporating information about biological processes into the algorithm is likely to improve its accuracy and decrease dependence on large amounts of annotated data, which may not be available.
-One danger of the “black box” problem is that DL may inadvertently perpetuate existing unconscious biases.
-Researchers need to carefully consider how potential biases affect the data being used to develop a model, adopt practices to address and monitor those biases, and monitor performance and applicability of AI models.
-
-%With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk.
-Updated: August 31, 2020
-%
 

### 2021-03-23 main.tex
Updates from Overleaf
proof reading

@@
 %Surgical Margin
+Holistic Cancer Care;
+Therapeutic Relationship
 }
@@
 %by GEO GSE2837 HNSCC dataset (PrognoScan)
-After the discovery by our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
-The survival significance (Kaplan-Meier \textit{P} value) is in the following probes of 10 genes:\\
+After the discovery by our workflow, we validated the those 20 genes in the other independent \acrshort{hnscc} cohort (GSE2837).
+The survival significance (Kaplan-Meier \textit{P} value) is in the following probes among 10 genes:\\
 1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
@@
 %Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-Thus, these 10 out of 20 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
+Thus, these 10 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
 Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
@@
 \centering
-\caption{ The 10 candidate genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }
+\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 \centering
-\caption{The 10 candidate genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }
+\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 % \linksupplementary{Supplementary_figures.pdf},
-
 % % SurvExpress 沒有類似的結果是因為:
@@
 Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
-Our workflow has the advantage to find ai optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
+Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
 %因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
@@
 Our 5 candidates (e.g.
-CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
 FCGBP is on the list of favorable prognostic genes as well.
@@
 % ZNF557, ZNF266, and FCGBP
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+\\cancer)\cite{Ren2020}.
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.\\
+org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
 % 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
@@
 The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
-PGK1 is responsive in hypoxia status, since it is one of HIF-1\alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.
+PGK1 is responsive in hypoxia status, since it is one of \acrshort{hif}-1 alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.
 
@@
 %\begin{MyColorPar}{red}
-
-% second limitation:
-%\subsubsection{Cancer type-agnostic study}
-Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
-% *** yes here
-In our previous work, altered glucose metabolism (e.k.a.
-the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
-% Cited In for PMID: 28061796
-Lactic acidosis induced \acrshort{glut4} overexpression was also found in lung cancer cells\cite{Prado-Garcia2020}. 
-%The overexpression of \acrshort{glut4} will lead to higher glucose uptake in proliferating cancer cells\cite{Mani2020}.
-%There is a trend toward cancer type-agnostic study. 
-Currently, Pembrolizumab and nivolumab's success has been based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
-It shows a model of tumor type-agnostic therapy\cite{Yan2018}.
-%*** PD-L1/PD-L2 is a biomarker; Keynote-012
-There are several common biomarkers of \acrfull{ici} under evaluation, including \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
-The other \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019} (ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (NCT04080804) studies.
-
-In line with tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases.
-However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
-Before the global genes scanning process, it is necessary to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
-This process should be carefully curated to confirm the data integrity within the correct definition\cite{Rendleman2019}.
-We also plan to upgrade our R script of the cutoff engine to the C++ language and source it in the Rstudio server.
-The high performance of C++ could speed up the critical steps in this workflow involving heavy computation of matrix data\cite{Woodward2020}.
-Moreover, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
-
-\subsection{Future Direction in Translational Medicine}
 
@@
 
+\subsection{Future Direction in Translational Medicine}
+
+%\subsubsection{Tumor-agnostic Research}
+% second limitation:
+\subsubsection{Cancer Type-agnostic Study}
+Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+% *** yes here
+In our previous work, altered glucose metabolism (e.k.a.
+the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
+% Cited In for PMID: 28061796
+Lactic acidosis induced \acrshort{glut4} overexpression was also found in lung cancer cells\cite{Prado-Garcia2020}. 
+%The overexpression of \acrshort{glut4} will lead to higher glucose uptake in proliferating cancer cells\cite{Mani2020}.
+%There is a trend toward cancer type-agnostic study. 
+Currently, Pembrolizumab and nivolumab's success has been based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
+It shows a model of tumor type-agnostic therapy\cite{Yan2018}.
+%*** PD-L1/PD-L2 is a biomarker; Keynote-012
+There are several common biomarkers of \acrfull{ici} under evaluation, including \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
+The other \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019} (ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (NCT04080804) studies.
+
+In line with tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases.
+However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
+Before the global genes scanning process, it is necessary to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
+This process should be carefully curated to confirm the data integrity within the correct definition\cite{Rendleman2019}.
+We also plan to upgrade our R script of the cutoff engine to the C++ language and source it in the Rstudio server.
+The high performance of C++ could speed up the critical steps in this workflow involving heavy computation of matrix data\cite{Woodward2020}.
+Moreover, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+
 %****************%
@@
 % Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
-Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status. (see Figure \ref{fig:figure5})
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status (see Figure \ref{fig:figure5}).
+
 %
@@
 \bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
-{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception.
+{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment (giant \textcolor{black}{black} arrow) will trigger emotional reception.
 The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.
 The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression.
-In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
+In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy (e.x.
+HNSCC) with helping from known carcinogens.\\
 Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs.
 Physical care will be carried out by medication therapy or surgery.
-After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
-Suggested healthcare record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
+After establishing a therapeutic relationship (TR), the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease through their mind-brain-body axis.
+Thus, we suggest electric healthcare records (EHR) include physical, pathological, psychological data, and even more spiritual information.
+The \acrshort{tcga} should collect "holistic features" as well (\textcolor{green}{green} dashed line).}
 \label{fig:figure5}
@@
 %是1979年麻薩諸塞大學的榮譽教授Jon Kabat-Zinn => 佛教禪修的mindfulness 正念止觀（中譯建譯：自我覺察）帶入西方身心醫學及心理學領域。
-The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage mindfulness and self-awareness. 
+The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage (dynamic) mindfulness and self-awareness. 
 %Search Inside Yourself was born at Google in 2007 when one of Google’s earliest engineers, Chade-Meng Tan, gathered a team of leading experts in mindfulness, neuroscience, leadership and emotional intelligence to develop an internal course for fellow Google employees lovingly called Search Inside Yourself (SIY).
@@
 %冤親債主 決定不再影響環境 基因 expression，減少意外與疾病、癌症
-A systematic review of spiritually based interventions and psychoneuroimmunological outcomes in breast cancer survivorship was reported by Hulett et al.\cite{Hulett2016}. 
+A systematic review of spiritually based interventions and psychoneuroimmunological (PNI) outcomes in breast cancer survivorship was reported by Hulett et al.\cite{Hulett2016}. 
 %Objective This is a review of spiritually based interventions (eg, mindfulness-based stress reduction, MBSR) that utilized psychoneuroimmunological (PNI) outcome measures in breast cancer survivors.
@@
 These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
-Thus, cortisol is one of the most common (objective) outcomes studied in psychoneuroimmunological (PNI) factors.
+Thus, cortisol is one of the most common (objective) outcomes studied in PNI factors.
 % others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV
@@
 %%%% PCA and ECA: the way to delivery of MBSR
-The therapeutic relationship is essential towards spiritual care.
+The therapeutic relationship (TR) is essential towards spiritual care.
 According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
-In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
-Then simply my presence is releasing and helpful."\cite{Rogers1979}
+In 1979, Carl Rogers wrote\cite{Rogers1979}: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
+Then simply my presence is releasing and helpful."
 Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
@@
 Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
-Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases.
+Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases.
 They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
 Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
-The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner.
-(see Figure \ref{fig:figure5})
+The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure \ref{fig:figure5}).
 %身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
@@
 The central dogma of molecular biology should be modified as environmental signals to regulatory protein to DNA to RNA and then to protein.
-Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}. (see Figure \ref{fig:figure5})
+Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017} (e.x.
+stressful environment, see Figure \ref{fig:figure5}).
 % so do the cancer
@@
 %療癒 
-Some studies showed that after 8 hours of meditation, the expression of some inflammatory genes changed\cite{Gustafson2017}.
+Study showed that after several hours of meditation, the expression of some inflammatory genes changed\cite{Gustafson2017}.
 %You can change your genetic activity by how you change your response to the environment. 
@@
 Becoming aware of our behavior's subconscious source allows us to change our lives by rewriting the programs (in the subconscious mind) of limitation or the things that interfere with us.
-Warburg effect\cite{Warburg1956}\cite{Chang2017b} is an example of carcinogenesis, metabolic reprogramming cells by some environmental factors.
+Warburg effect\cite{Warburg1956}\cite{Chang2017b} is an example of carcinogenesis and metabolic reprogramming of cells by some environmental factors.
 %honeymoon by Lipton 愛自己就是渡蜜月；其實是 正念 mindfulness (因為自他不二）
@@
 These programs were acquired from other people, not from ourselves, with a survival advantage.
-Being subconscious, those programs acquired from other people before age 7, are occurring without conscious recognition and awareness. 
+%Being subconscious, those programs acquired from other people before age 7, are occurring without conscious recognition and awareness. 
 The survival advantage programs, such as limitation, disempowerment, and self-sabotage, will affect epigenetic regulation.
-Genes are not self-actualizing. 
-The regulation of genetic activity is due to the interaction of the cell with environmental signals.
 Genes are not self-actualizing. %The control of genes is not due to any inherent activity in the DNA itself. 
@@
 %Less than 1\% of disease is associated with genetics. 
-Over 90\% of disease is a total reflection of the environment and especially our programming.
+Over 90\% of disease is a total reflection of the environment.% and especially our programming.
 %the disempowering, self-sabotaging behaviors that we acquired in the first 7 years.
@@
 The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression. 
-Carcinogenesis will occur if the reprogramming is persistent for a longer time.
-(see Figure \ref{fig:figure5})
+%Carcinogenesis will occur if the reprogramming is persistent for a longer time.
 Moreover, long-term stress could be correlated with cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021},
-and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}. %HNSCC
+and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}.(see Figure \ref{fig:figure5}) %HNSCC
 Adverse psychosocial experiences in early life, such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased risk of diabetes, heart disease, cancers, and psychiatric illnesses.
-The possible molecular mechanisms could be related with the mind-brain-body axis\cite{Berens2017}.
+The possible molecular mechanisms could be also related with the mind-brain-body axis\cite{Berens2017}.
 %Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}
@@
 %% TCGA new holistic features %%%%%
-Our current study summarizes those six candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
-Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
+Our current \acrshort{hnscc} study summarizes that six candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors.
+The prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
 The important input $X_1...X_n$ should be patients' features: age, specific six gene expressions, clinical T stage, and surgical margin so far.
-When we consider the survival prediction model again,
+When we consider the survival prediction model in holistic manner,
 ground truth Y (e.x. patient's survival):\\[0.5cm]
@@
 $Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\[0.5cm]
-Gene expression is not an independent $X_{mrna}$. It could be correlated with other\\ $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
+Gene expression is not an independent $X_{mrna}$. It could be correlated with other (for example)\\ $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{empathy}$ factors.\\
 There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
@@
 We suggest TCGA should cover more holistic features:
-cortisol is one of the most common objective outcomes studied in psychoneuroimmunological (PNI) factors.
-Other factors are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
+cortisol is one of the most common objective outcomes studied in psychoneuroimmunological (PNI) factor, interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, and heart rate variability (HRV).
 The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
@@
 % Deep Patient:  
-Deep learning applied to EHR can derive patient representations that offer improved clinical predictions\cite{Miotto2016}
-Deep learning also might convert EHR to the Fast Healthcare Interoperability Resources (FHIR) format\cite{Rajkomar2018}\cite{HealthLevelSeven2019} for handling free-text notes.
+Deep learning can convert EHR to the Fast Healthcare Interoperability Resources (FHIR) format\cite{Rajkomar2018}\cite{HealthLevelSeven2019} for handling free-text notes by physicians.
+Deep learning can also derive patient representations that offer improved clinical predictions\cite{Miotto2016}.
 %=> Level 4 Record-keeping and Data Exchange for the healthcare process (clinical data) %Under HL7, RESTful
@@
 %}
-
 %https://mos2718.github.io/FHIRspec/Index.html
@@
 %https://mos2718.github.io/FHIRspec/Spec/Patient/EHR_Patient.docx
+Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
+
 In Taipei Medical University Hospital, holistic-enabled EHR has been designed as the holistic dental chart for our outpatient with psycho-social-spiritual evaluation\cite{Ling-ChengMong2021}:\\
@@
 2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment\\
-3. Social: (disturbing living/ disturbing working/ disturbing other life aspect) by present illness\\
+3. Social: (disturbing living/ disturbing working/ disturbing other life aspect)\\
 4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind\\
@@
 6. Impact to life: financial problem/ family problem\\
-7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[0.5cm]
+7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[0.1cm]
 
@@
 Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No
-% cancer cure (care) 的證明
-%# 懺悔
-
-We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body's hard working.
-Since mindfulness meditation will be helpful in cancer healthcare.
-Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
-%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
-%七情: 喜、怒、思、悲、恐、驚、憂
-%with more TCGA features (holistic)
-%Dali Lama: Wish and bless the whole world %慈悲心 利他心
-% 多了解身心靈的關係，減少癌症對健康的損害
 
@@
 At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x.
-0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}).
+0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}, Figure \ref{fig:figure4}).
 The optimal cutoff value and its correlated patient grouping size (e.x.
@@
 
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
+Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
+we analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
 %??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
@@
 The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005)
-microarray gene expression (by Affymetrix X3P chips U133\_X3P) and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
+microarray gene expression (by Affymetrix X3P chips U133\_X3P).
+%and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
 
@@
 % welcome for study
-
 %tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases
@@
 %TCGA has not collected holistic features so far.
+
 The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using holistic multi-parametric approaches.
+% cancer cure (care) 的證明
+%# 懺悔
+Since mindfulness meditation will be helpful in cancer healthcare, we continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for their physical body's hard working.
+
+%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
+%七情: 喜、怒、思、悲、恐、驚、憂
+%with more TCGA features (holistic)
+%Dali Lama: Wish and bless the whole world %慈悲心 利他心
+% 多了解身心靈的關係，減少癌症對健康的損害
 

### 2021-04-25 Cover_letter_JPM.tex
start extended revision

--- 2021-02-09 revisionNotel2_responses.tex
@@
 \documentclass[preprint,12pt]{elsarticle}
-% major revision and answer question (3 reviewers)
-%Sunday, January 24⋅22:30 – 22:55
-%Daily, until Jan 29, 2021
+% Extended revision and answer question (2 reviewers)
+% for JPM-1174473
+%Since April 19, 2021
+%Please resubmit your revised manuscript through the following link:
+% https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f
 
@@
 
-\section*{Cover letter for the revision (cancers-1082127)} % 2021/01/25
-%其實直接 online 填寫即可
+\section*{Cover letter for the re-submission (jpm-1174473)} 
+% 2021/04/25
+% 直接 online 填寫即可
 %Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript
@@
 %Assistant Editor
-%E-Mail: aubree.zhu@mdpi.com
-%MDPI Branch Office, Tianjin
-Assistant Editor of Cancers%\newline
+%Suite 305, Zhongjia Mansion, Building No.13, Taiyangyuan Community, Dazhongsi 
+%East Road,
+%Haidian District, Beijing 100190, China
+%Email: sonia.sun@mdpi.com
+Assistant Editor of JPM%\newline
 
-Feb 2, 2021
+April 30, 2021
 
-Dear Dr. Aubree Zhu:
+Dear Ms. Sonia Sun:
 
-Enclosed, please find our revised manuscript (cancers-1082127) entitled "A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Cancers.
+Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine.
 We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.
 
-We have since performed the additional literature review and revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,
+We have since revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,
 
@@
 
-According to the editor's comments, we have the manuscript checked for English grammar and reformatted Table 1 by rotating 90 degrees to portrait mode. %
-We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.
+According to the editor's comments, we have the manuscript checked for English grammar. %
+We wish our revised manuscript could be satisfied and accepted for publication in JPM. Thanks very much for the kind helps and the reviewers' critical comments.
 %\\[0.4cm]
@@
 Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
-%Reviewer #1(Technical Comments to the Author):
-%   The ms investigates an interesting and timely topic.
-However, the discovery cohort involves a small sample size and throughout the analysis, the issue of correcting the obtained p-values for multiple comparisons is not addressed.
-Hence, the evidence for zooming into TMSB4X is not convincing.
 
-%\section{Responses to Reviewers' comments}
-% our responses to the reviewers' comments.
-%***Response to reviewer's comments: [藍色字]
+Comments and Suggestions for Authors from the reviewer \#1:
 
-Comments from the reviewer \#1:
+This manuscript perhaps describes the biomarkers of head and neck SCC using several data-bases.
+They also describe the relationship between the expression level of each candidate biomarkers in their patients and other factors such as gender, age, margin, lymph-node metastasis and so on.
+%=> RNA expression and other contributing factors in the survival of HNSCC patients
 
-The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method.
+I myself think this manuscript is very interesting, however, I do not find the difference between the previously published manuscript from your institute.
+https://www.researchsquare.com/article/rs-80673/v1
+
+\subsection*{1-1}
+First of all, please describe the difference between the two manuscripts.
+
+%The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method.
 I have a few minor questions.
 
-This is an attractive analysis method and I would like to know more details.
+%This is an attractive analysis method and I would like to know more details.
 
-\subsection*{1-1}
-It is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
+%It is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
 
@@
 We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.
+
+The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
+Since previous reviewer's suggestion, we made a major revision on the followings:
+1) suggested  candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
+We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
+2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).
+
 %[我的 candidate 中為什麼沒有 EGFR];  
-In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
-by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
-(please see https://github.com/texchi2/\linebreak
-pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)
+%In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
+%by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
+%(please see https://github.com/texchi2/\linebreak
+%pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)
 
@@
 % epidermal growth factor receptor (EGFR)
-As in our manuscript mentioned, 
-In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
-Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}.
+%As in our manuscript mentioned, In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
+%Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}.
 Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}.
@@
 %citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
-Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
+%Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
 % a list from literature review, 留 下少於  50 articles mentioned candidates
@@
 \subsection*{1-2}
-DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
+Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
+The latter half of the discussion may not be appropriate for this manuscript.
+Many people aware of the relationship between prognosis and mental/financial/familial situations.
+Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something.
+Isn’t it a totally different theme from biomarkers of HNSCC?
+Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different.
+If you want to describe spiritual something, please submit it as a brand new manuscript.
+Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.
+
+%DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
 %[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]
@@
 
-We appreciate the reviewer for reminding the importance of DNA alteration in survival analysis.
-Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation),
-epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
-The usefulness of multi-omics data for the prediction of HNSCC outcome is expected.
+One day in February 2021, after meditation in the morning, the first author (Dr.
+Chi) has raised this idea then wrote it in discussion section with comprehensive references.
+Dr.
+Chi want to say "Stress is also be a kind of biomarker of HNSCC in the future study".
+We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.
+
+The summary of holistic cancer care in this revised manuscript could be:
+"
+".
+
+%Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation),
+%epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
+%The usefulness of multi-omics data for the prediction of HNSCC outcome %is expected.
 %such as the (censored) survival time.
-Moritz Herrmann et al.(2020) observed that using multi-omics and survival data can slightly improve prediction methods for particular datasets, such as TCGA HNSCC\cite{Herrmann2020}.
-%It is limited that the utility of multi-omics data for prediction purposes in the considered TCGA studies\cite{Herrmann2020}.
-%18 cancer datasets from The Cancer Genome Atlas (TCGA) 
-According to their study, %the multi-omics structure have a slightly better prediction performance than naive (0.562 vs.
-0.557 ) with favoring clinical variables leads to better prediction results for HNSCC.
-%likelihood-based boosting (CoxBoost and CoxBoost favoring)
-% Exemplary t-tests comparing blockForest with CoxBoost favoring and the Clinical only model showed no significant differences in performance. 
-% blockForest also offers the possibility of favoring clinical covariates using the argument always.select.block of the blockfor function
-%Last but not the least, multi-omics data are structured: the variables are partitioned into (non overlapping) groups. 
-% ***
-the survival analysis of the TCGA HNSCC dataset by blockForest method (with multi-omics and clinical variables) has a similar prediction performance than Cox's model (with clinical variables alone).
-%from The Cancer Genome Atlas (TCGA)
-They also reported the performance C-index as 0.582 [CI: 0.554, 0.610] in blockForest method and 0.554 [CI: 0.519, 0.588] in Cox's model\cite{Herrmann2020}.
 
-% 小心光茫太甚  Well-established prognostic clinical variables: prioritize
-% the number of variables in the group of variables of TCGA HNSCC dataset:
-% 11 clinical variables, 57964 CNV variables, 17248 mutation variables and 21520 RNA expression variables.
-%*** Taking this structure into account can protect the predictive information that transcriptomics (e.x.
-RNA-Seq) or low-dimensional clinical variables might get lost within the huge amount of genomics (e.x.
-DNA mutation/amplification, copy number variation) data\cite{Boulesteix2011}\cite{Herrmann2020}.
-DNA amplification will usually be one of the causes to overexpress the gene.
-Moreover, transcriptomics study is helpful in drug discovery.
-For example, the overexpressed gene is possible to be a drug-targetable candidate\cite{Park2015}.
-After thoughtful validation in vitro/in vivo then pathway study, the EGFR inhibitory leads were constructed by antibody design or chemical compound screening\cite{Mahajan2016}.
-%比較容易研發 clinical and transcriptomics by ssurvival::survfit and urvival::coxph
-% the selection of clinical features by domain knowledge and studies where HNSCC was under investigation.
-The discovery of EGFR inhibitors\cite{Bonner2006a} for HNSCC therapy will encourage the research community to conduct the survival analysis under abnormality in gene expression.
-
-% *** it needs deep learning, but less interpretability (yet under development\cite{Chaudhary2018}) (DNA+RNA and clinical dataset => multi-omics cancer study)
-%high dimensional multi-omics analysis by deep learning 
-%It may be beneficial to include these different data types in models predicting outcomes, such as the survival time of patients.
-Until recently, only data from a single omics type were used to build such prediction models, with or without the inclusion of standard clinical data [2].
-In recent years, however, the increasing availability of different types of omics data measured for the same patients (called multi-omics data from now on) has led to their combined use for building outcome prediction models.
-An important characteristic of multi-omics data is the high-dimensionality of the datasets, which frequently have more than 10 000 or even 100 000 variables.
-This places particular demands on the methods used to build prediction models: they must be able to handle data where the number of variables by far exceeds the number of observations.
-Moreover, practitioners often prefer sparse and interpretable models containing only a few variables [3].
-Last but not the least, multi-omics data are structured: the variables are partitioned into (nonoverlapping) groups.
-This structure may be taken into account when building prediction models.
-%Citation: https://academic.oup.com/bib/advance-article/doi/10.1093/bib/bbaa167/5895463
-%特別的 algorithm 
-%however, interpretation and practical application of the model to the prediction of independent data are easier with regression-based methods yielding coefficients that reflect the effects of variables on the outcome than with machine learning algorithms [8].
-%Multi-omics data, that is, datasets containing different types of high-dimensional molecular variables; they must be able to handle data where the number of variables by far exceeds the number of observations.
-%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6419526/
-%Deep learning
-%SALMON (Survival Analysis Learning with Multi-Omics Neural Networks)
-
-%\cite{Lawrence2015a} TCGA HNSCC %的第一篇文章已經分析過 DNA mutation of HNSCC
-%Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature, 517(7536), 576–582. 
-%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
-%=> HNSCC marker paper\cite{Lawrence2015a}
-
-%The presence of widespread genomic instability in HNSCC, such as cytogenetic aberrations, allelic imbalance/loss of heterozygosity, and microsatellite instability (MSI), suggests that there is an imperfection in the host DNA repair machinery.
-Genomic instability with progressive accumulation of detrimental genetic alterations appears to be dependent upon a circuitous interaction between the environmental genotoxic insults and the host DNA repair machinery, the functional integrity of which is governed by the proper cell cycle control and host DNA repair capacity.
-Genomics allows the identification of possibly relevant variants, such as single nucleotide polymorphisms (SNPs), copy number variation (CNV), mutations and translocations => %https://cancersheadneck.biomedcentral.com/articles/10.1186/s41199-020-0047-y
-%DNA mutation: copy number burden (CNB) and tumor mutation burden (TMB) are important for predicting tumor progression (Marshall et al., 2017; Thomas et al., 2018)
-% *** The Landscape of Somatic Copy Number Alterations in Head and Neck Squamous Cell Carcinoma, 2020. => 18 GEO dataset (873 patients from GEO) + TCGA: chromothripsis 6\%\cite{Yang2020}
-%metaanalysis of NCBI GEO database (https://www.ncbi.nlm.nih.gov/geo/).
-We integrated the following datasets: TCGA-HNSCC, GSE11938, GSE20306, GSE20939, GSE23831, GSE25103, GSE31984, GSE33229, GSE33983, GSE34507, GSE36790, GSE39367, GSE40777,GSE47443, GSE51265, GSE57201, GSE66136, GSE68717, and GSE85514.
-
-%TMB: To calculate TMB, you need to know the total size of the region sequenced.
-If data is from exome sequencing, you would find the size of the exome capture, and divide total mutations (or non-synonymous only depending on strategy), by that size (e.g.
-~45MB) to get SNV/MB ratio.
-%tumor mutational burden-high (TMB-H) [≥10 mutations/megabase (mut/Mb)] in solid tumors (criteria for pembrolizumab)
-%Identification of Genomic Predictors for Treatment Response to Cancer Immunotherapy Using Omics Data Analysis (Yu-Chao Wang)
-%=> ICIs criteria <- TMB <- DDR DNA repair gene
 \end{MyColorPar}
@@
 
-Comments from the reviewer \#2
+Comments and Suggestions for Authors from the reviewer \#2 % 善意提醒、指導
 
-How representative is the TCGA database for HNSCC?
+The authors introduced a workflow to identify gene-expression biomarkers based on TCGA data and applied it to head and neck squamous cell carcinoma.
+The authors tried to highlight their workflow and present it as a new tool, however, their workflow is very common, and I cannot see its novelty.
+The selection of gene expression cutoff is not well handled statistically (see below my first comment). 
+Therefore, I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them.
+% new Title, abstract, change tone
+Exploring all possible expression cutoffs is also usable but should only be used for established biomarkers.
+Once it is known that a gene is a strong biomarker (e.g., from a genome-wide test using fixed cutoffs), one can fine-tune the cutoffs utilizing this strategy.
 
-Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?
-
-Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?
-
-Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.
-
-%[找出其他 database cohort 的比較]
 \subsection*{2-1}
-How representative is the TCGA database for HNSCC?
+Exploring all possible expression cutoffs is controversial.
+A robust expression biomarker should be effective and detectable at most major cutoffs.
+Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05).
+For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff.
+But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff.
+This strategy only identifies more weak “biomarkers,” and it also captures more false positives.
+Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
 
@@
 We appreciate the reviewer for the question allowing discussing TCGA in detail.\\
-To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
-When we queried from the Embase database using the MESH words "HNSCC AND TCGA," simple statistics show a total of 12,636 research articles/conference abstracts for HNSCC from 2008 to 2021, since the first TCGA article was published on 2008\cite{McLendon2008} by TCGA research network.
-After that, there are 18,082 cross-cancer type articles produced using the TCGA database.
+
+[after cut-off finding]
+Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
+
+***=> Bonferroni correction should be used in final decision.
+%位置要換一下：
+The false discovery rate
+645 (FDR) (< 0.05) could be used to pick up the optimal P value to ensure the control for
+646 type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
+4.2. Cutoff Finder Core Engine.
+
+..
+%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
+
+%After that, there are 18,082 cross-cancer type articles produced using the TCGA database.
 The 778 publications (Figure \ref{figure:fig_embase}, b.
@@
 \subsection*{2-2}
-Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?
+I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them.
+% new Title, abstract, change tone
 
@@
 We appreciate the reviewer for the critical comment.
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
-%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
-%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 carries
-% VUMC, VAMC, UTMDACC (1992-2005)
-relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
-and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
-The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
-1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
-%17 out of 20 candidates
-%?DKK1 (0.253635), 
-Please see Figure \ref{figure:fig_GSE2837}.
-Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
-%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
-%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
-%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using GSE2837 dataset other than the TCGA cohort.
+We change new Title, abstract, change tone
 
@@
 \subsection*{2-3}
-Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?
+% strategy should changing
+In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01.
+Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable.
+The p-values are affected by the sample size, which should be described in the main text.
+As I mentioned above, the authors should look for more data to verify these biomarkers.
 
@@
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
-
+% ???
+% x
 %how to apply or modify the R scripts to use on other datasets
@@
 \subsection*{2-4}
-Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.
+How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
+Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
 
@@
 
-%\begin{MyColorPar}{red}
+\end{MyColorPar}
 
-"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
-TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/\\organization/ccg/research/structural-genomics/tcga/studied-cancers).
-%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
+\begin{MyColorPar}{red}
 
-TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen.
-Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.
+"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."
 
-The NCI's Genomic Data Commons (GDC, available at https://portal.\\gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
-The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
-The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
-%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
-\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research. %There is three categories of tools to approach the TCGA data from GDC.
-
-GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools.
-Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and
-Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
-One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
-Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x.
-GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering).
-A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).
-
-%Python and UNIX bindings
-%R bindings
-Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.
-
-%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
-% RESTful API
-
-GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
-Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
-Moreover, if restricted data is requested, the user must provide a token along with the API call.
-This token can be downloaded directly from the GDC Portals.
-(courtesy of the National Cancer Institute)
-Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
-
-% clinical
-%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
-
-% to summarize the advantages of its use.
-The highlights of the advantages of applying the TCGA data for cancer research include:
-\begin{outline}
-\1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
-The whole-genome sequencing data has been harmonized across all GDACs.
-The basic demographic data is usually available on many databases.
-However, TCGA data has more comprehensive features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
-\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data.
-It might be getting help quickly from the research community for trouble-shooting.
-\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
-\end{outline}"
-
-%\end{MyColorPar}   % marked in red above
+\end{MyColorPar}   % marked in red above
 
@@
 
+\subsection*{2-5}
+[Minor comments]
+The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
+More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
+Detailed introduction of TCGA-related tools should be removed or moved to Methods.
+In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
+In Figure 1, the diagram should have direction. 
+The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
+In Figure 2, unlabeled scales on the x-axis.
+
+\begin{MyColorPar}{blue}
+Answer
+
+We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
+
+\begin{MyColorPar}{red}
+
 \end{MyColorPar}
+
+\end{MyColorPar}
+
+% the end of response rebuttal
+
+%\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
+\bibliographystyle{unsrt} %model1-num-names}
+\bibliography{TCGA_margin_cutoff.bib}
+
+\section{end_document}
+\end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \pagebreak
 
-\section*{Response to Reviewer 3 Comments}
+%\section*{Response to Reviewer 3 Comments}
 %Response to Referees} % rebuttal
@@
 
-\subsection*{Comments from the reviewer \#3}
+%\subsection*{Comments from the reviewer \#3}
 
@@
 
-\subsection*{Revision notes: rebuttal}  
+%\subsection*{Revision notes: rebuttal}  
 %Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
@@
 
-\subsubsection*{Author Appeals for a rejection, in case}
+%\subsubsection*{Author Appeals for a rejection, in case}
 %Authors may appeal a rejection by sending an e-mail to the Editorial Office of the journal.
@@
 
-\subsection*{Material and Methods}
+%\subsection*{Material and Methods}
 
-\subsubsection{Quantitative real-time PCR (qRT-PCR) analysis}
+%\subsubsection{Quantitative real-time PCR (qRT-PCR) analysis}
 %\subsectionmark*{qRT-PCR analysis}
@@
 
-\subsection*{Results}
+%\subsection*{Results}
 
-\subsection*{Discussion}
+%\subsection*{Discussion}
 
@@
 \end{MyColorPar}
-
-% the end of response rebuttal
-
-%\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%\externalbibliography{yes}
-%\bibliography{your_external_BibTeX_file}
-\bibliographystyle{unsrt} %model1-num-names}
-\bibliography{TCGA_margin_cutoff.bib}
-
-\end{document}

### 2021-04-26 main.tex
Updates from Overleaf

@@
 %=================================================================
+% pm-1174473
 % Journal of Personalized Medicine, JPM
@@
 
-\newenvironment{MyColorPar}[1]{%
+\newenvironment{MyColorPar}[1]{% for RED marked of revision
     \leavevmode\color{#1}\ignorespaces%
@@
 }%
+
+%\begin{MyColorPar}{red}
+%\end{MyColorPar}
+
 %\usepackage[upplemac]{inputenc} %applemac support if unicode package fails
@@
 % Full title of the paper (Capitalized)
-\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
+\Title{Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+%\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
+\TitleCitation{Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
 
@@
 It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression.
-Usually, an optimization algorithm for cutoff determination has been set at the median or quantiles of RNA sequencing value.
-%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
-We developed a comprehensive workflow to perform biomarker discovery.
+We have used a workflow to perform biomarker discovery.
 It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
@@
 Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
-We suggest this workflow equipped with a cutoff-mining engine could help for biomarker discovery.
+We suggest these ten genes could be the candidates in biomarker discovery of HNSCC.
 }
+
+%Survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
+It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression.
+Usually, an optimization algorithm for cutoff determination has been set at the median or quantiles of RNA sequencing value.
+%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
 % validated by the other HNSCC cohort:
@@
 %Surgical Margin
-Holistic Cancer Care;
-Therapeutic Relationship
+%Holistic Cancer Care;
+%Therapeutic Relationship;
+Mindfulness Meditation
 }
@@
 We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
-
-%\subsection*{Authors' information} % Author details (automatic placed here)
-
 % *** URL Accessed 20 May 2013.
@@
 mtbwi/index.do. Accessed 20 May 2020.}
+
+%\subsection*{Authors' information} % Author details (automatic placed here)
 

### 2021-04-26 Cover_letter_JPM.tex
Updates from Overleaf

@@
 We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
+
+{ 
+(ok)Result 改寫 CAMK2N1, IL19; 
+Supplementary;
+Discussion:
+([ok] 3.2, 3.3 只留下 validated by GSE2837)
+(ok)Figure_4_CAMK2N1_IL19.pdf  KM plots
+(ok)table 1 (6 genes), (ok) table 2 (4 genes)
+
+\resizebox{\linewidth}{!}{ % adjust table size to fit the page width
+Table 3: CAMK2N1 (ok)
+Table 4: IL19  (ok)
+\label
+}
+six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
+four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
+}
 2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).
@@
 
+% modify on main.tex, marked with
+%\begin{MyColorPar}{red}
+%\end{MyColorPar}
 The summary of holistic cancer care in this revised manuscript could be:
@@
 
-We appreciate the reviewer for the question allowing discussing TCGA in detail.\\
+We appreciate the reviewer for kind instruction of expression cutoff in detail.\\
+We modified the workflow as ...
 
@@
 4.2. Cutoff Finder Core Engine.
-
-..
-%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
-
-%After that, there are 18,082 cross-cancer type articles produced using the TCGA database.
-The 778 publications (Figure \ref{figure:fig_embase}, b.
-778) among them were focused on HNSCC research.
-Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time.
-Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008.
-%\ref{figure:fig_embase}
-\begin{figure}
-\raggedleft
-\includegraphics[width=14cm]{Answer_2-1.pdf}
-\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
-\label{figure:fig_embase}
-\end{figure}
-\clearpage
-%778/4350 = 17.9\% using TCGA data
-%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
-%http://www.actrec.gov.in/OCDB/index.htm
-
-Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
-GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.
-However, the MSKCC, Broad, and Johns Hopkins databases were processed through whole-exome sequencing instead of whole-genome sequencing in the TCGA database.
-
-There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a} and Gene Expression Profiling Interactive Analysis (GEPIA, GEPIA2)\cite{Tang2019}.
-According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
-Furthermore, almost all of their survival data came from the TCGA database.
-%GEO (few survival features, less than 100 participate in each GSE dataset)
-%GSE31056, GSE2837 (Prognoscan)
-%there is survival feature: A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
-%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).\cite{Lawrence2015a}
-%datasets for each cancer type that include exactly the same prediction and outcome variables and consider comparable target populations. Currently, such data is simply not available.
-
-%The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
-%Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
-%Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
-%Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
-%DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
-%The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-
-For example, Wei et al.\cite{Wei2020} conducted the analysis of the prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a web-based tool that plots expression profiles of given genes (dataset from TCGA database)
-They has suggested that overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
-%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-
-Conclusion: TCGA database is representative of HNSCC.
 
@@
 
-\begin{figure}
-\raggedleft
-\includegraphics[width=14cm]{Answer_2-2.pdf}
-\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
-The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
-\label{figure:fig_GSE2837}
-\end{figure}
-\clearpage
 \end{MyColorPar}
@@
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
+調整 workfow 更加嚴格
+以增加 validation rate
+The p-values are affected by the sample size, which has be described in the main text.
+as following:
 % ???
@@
 How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
-Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
 
@@
 We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
+= 詳細描述 univariable and multivariable tests work
+In a multivariable test, which variables were used? 
+= 列出來，並且強調 surgical margin
+
+% x
 In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
@@
 \subsection*{2-5}
+Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
+=> = a gene signature with deep learning CNN
+https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
+
+https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
+
+\begin{MyColorPar}{blue}
+Answer
+
+We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
+
+\end{MyColorPar}
+
+\subsection*{2-6}
 [Minor comments]
@@
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
+[Minor comments]
+The background should be revised extensively. 
+x For example, the description of the linear model should be removed. X1...Xn should be removed. 
+***More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
+Detailed introduction of TCGA-related tools should be moved to Methods.
 
+In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 
+In Figure 1, the diagram should have direction. 
+加上 direction of view
+
+The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)???
+
+In Figure 2, unlabeled scales on the x-axis???
+除去 unlabeled stick 即可立刻改進
 \begin{MyColorPar}{red}
@@
 \end{MyColorPar}
+
+%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
+
+%After that, there are 18,082 cross-cancer type articles produced using the TCGA database.
+The 778 publications (Figure \ref{figure:fig_embase}, b.
+778) among them were focused on HNSCC research.
+Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time.
+Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008.
+%\ref{figure:fig_embase}
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_2-1.pdf}
+\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
+\label{figure:fig_embase}
+\end{figure}
+\clearpage
+%778/4350 = 17.9\% using TCGA data
+%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
+%http://www.actrec.gov.in/OCDB/index.htm
+
+Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
+GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.
+However, the MSKCC, Broad, and Johns Hopkins databases were processed through whole-exome sequencing instead of whole-genome sequencing in the TCGA database.
+
+There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a} and Gene Expression Profiling Interactive Analysis (GEPIA, GEPIA2)\cite{Tang2019}.
+According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
+Furthermore, almost all of their survival data came from the TCGA database.
+%GEO (few survival features, less than 100 participate in each GSE dataset)
+%GSE31056, GSE2837 (Prognoscan)
+%there is survival feature: A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
+%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).\cite{Lawrence2015a}
+%datasets for each cancer type that include exactly the same prediction and outcome variables and consider comparable target populations. Currently, such data is simply not available.
+
+%The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
+%Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+%Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+%Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+%DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+%The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+
+For example, Wei et al.\cite{Wei2020} conducted the analysis of the prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a web-based tool that plots expression profiles of given genes (dataset from TCGA database)
+They has suggested that overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+
+Conclusion: TCGA database is representative of HNSCC.
+
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_2-2.pdf}
+\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
+\label{figure:fig_GSE2837}
+\end{figure}
+\clearpage

### 2021-05-04 main.tex
modified Figure 1

@@
 \usepackage{xcolor}
+\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
 
@@
 
-%latex https://www.latex-tutorial.com/symbols/greek-alphabet/
-%\subsection*{Linear regression in biomarker discovery}
-Linear regression is useful as a concept in biomarker discovery.
-A linear regression equation that relates a Y-variable to n X-variables is written as\\[1cm]
-%\par
-%Highlights
-% https://quicklatex.com
-\begin{flushleft}
-% equation
-%\begin{math}
-
-ground truth Y (e.x. patient's survival):\\[0.5cm]
-%Y$:\\[0.3cm]
-$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
-\linebreak
-\linebreak
-Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
-\\[0.5cm]
-Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
-A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
-Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
-$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
-\linebreak
-%(predicted Y, output) intercept, slope, independent (input) \Times
-%\end{math}
-\end{flushleft}
-Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.\\[1cm]
-
 %% TP53 gene => p53 protein; mutation of TP53
@@
 
-%\subsection{A introduction of TCGA}
-%\begin{MyColorPar}{red}
-%%%%%% revision1 added [TCGA] [2021/02/02]
-A large-scale cancer database, aggregating many $X_1 ... X_n$ features, is necessary to facilitate the biomarker discovery.
-The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} has been developed since 2005 and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government.
-TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
-%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
-TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen.
-Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.
-
-The NCI's Genomic Data Commons (GDC, available at https://portal.gdc.cancer.gov) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
-The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
-The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
-%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
-\acrshort{tcga}, GDC and some research communities offer several computational tools to the public for facilitating cancer research.
-%There is three categories of tools to approach the TCGA data from GDC.
-GDC Data Portal is the official web-based TCGA data analysis tools. Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and 
-Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
-One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
-Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x.
-GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering).
-A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).
-%Python and UNIX bindings
-%R bindings
-Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.
-
-%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
-% RESTful API
-
-GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
-Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
-Moreover, if restricted data is requested, the user must provide a token along with the API call.
-This token can be downloaded directly from the GDC Portals.
-(paragraph is provided here courtesy of the National Cancer Institute)
-% Articles from Cureus are provided here courtesy of Cureus Inc.
-Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
-
-% clinical
-%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
+\begin{MyColorPar}{red}
+The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
+%\cite{SeanDavis;MartinMorgan2020}
+\end{MyColorPar}
 
@@
 \1  To the best of our knowledge, the TCGA database is the largest collection (in both cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
-There are many physical and social features ($X_1 ... X_n$) of patients available for survival modeling.
+There are many physical and social features of patients available for survival modeling. % ($X_1 ... X_n$)
 The whole-genome sequencing data has been harmonized across all GDACs.
@@
 \end{outline}
+
+\begin{MyColorPar}{red}
+\subsubsection{utility of TCGA}
+%%%
+Usually, how researchers used TCGA to find expression biomarkers
+%%%%%%
+\end{MyColorPar}
 
@@
 %, height=8cm
-%\caption
-\bcaption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (\textcolor{blue}{blue line}: main procedure) and step 2 (\textcolor{orange}{orange line}: analysis export).}
+%\caption % , step 1 (\textcolor{blue}{blue line}: main procedure) and step 2 (\textcolor{orange}{orange line}: analysis export).
 %Step 3 (purple line: dealing with surgical margin).
-{The "main procedure" includes data retrieval from TCGA GDC data portal, data process with merging and cleaning (red rectangled),% should be modified aggressively according to different sources of database)
-then performing the survival analyses.
-The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with \textcolor{green}{low [green]} or \textcolor{red}{high [red]} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details).
-The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, based on the results from the step 1.
+\bcaption{A workflow of \acrshort{hnscc} biomarker discovery}
+{The workflow includes data retrieval from TCGA GDC data portal, data process with merging and cleaning,% should be modified aggressively according to different sources of database)
+then performing the survival analyses (within \textcolor{yellow}{yellow} square).
+The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of gene expression for subsequent Cox modeling.
+The candidate selection performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, based on the results from the survival analyses.
+The selected genes will be validated by a independent HNSCC cohort (GSE2837).
 (HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
@@
 \end{figure}
+
+% \definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
 
@@
 Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. 
-The important input $X_1...X_n$ should be patients' features: age, specific ten gene expressions, clinical T stage, and surgical margin.
+%The important input $X_1...X_n$ should be patients' features: age, specific ten gene expressions, clinical T stage, and surgical margin.
 %\\[0.5cm]
@@
 
-The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
-%\cite{SeanDavis;MartinMorgan2020}
+\begin{MyColorPar}{red}
+%\subsection{A introduction of TCGA}
+%\begin{MyColorPar}{red}
+%%%%%% revision1 added [TCGA] [2021/02/02] %$X_1 ... X_n$ of independent features
+A large-scale cancer database, aggregating many independent features, is necessary to facilitate the biomarker discovery.
+The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} has been developed since 2005 and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government.
+TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
+%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
+TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen.
+Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.
+
+The NCI's Genomic Data Commons (GDC, available at https://portal.gdc.cancer.gov) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
+The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
+The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
+\acrshort{tcga}, GDC and some research communities offer several computational tools to the public for facilitating cancer research.
+%There is three categories of tools to approach the TCGA data from GDC.
+GDC Data Portal is the official web-based TCGA data analysis tools. Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and 
+Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
+One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
+Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x.
+GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering).
+A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).
+%Python and UNIX bindings
+%R bindings
+Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.
+
+%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
+% RESTful API
+\end{MyColorPar}
+
+GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
+Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
+Moreover, if restricted data is requested, the user must provide a token along with the API call.
+This token can be downloaded directly from the GDC Portals.
+(paragraph is provided here courtesy of the National Cancer Institute)
+% Articles from Cureus are provided here courtesy of Cureus Inc.
+Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
+
+% clinical
+%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
+
 GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
@@
 \end{document}
+
+% moved from line 363
+
+%latex https://www.latex-tutorial.com/symbols/greek-alphabet/
+%\subsection*{Linear regression in biomarker discovery}
+Linear regression is useful as a concept in biomarker discovery.
+A linear regression equation that relates a Y-variable to n X-variables is written as\\[1cm]
+%\par
+%Highlights
+% https://quicklatex.com
+\begin{flushleft}
+% equation
+%\begin{math}
+
+ground truth Y (e.x. patient's survival):\\[0.5cm]
+%Y$:\\[0.3cm]
+$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
+\linebreak
+\linebreak
+Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
+\\[0.5cm]
+Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
+A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
+Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
+$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
+\linebreak
+%(predicted Y, output) intercept, slope, independent (input) \Times
+%\end{math}
+\end{flushleft}
+Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.\\[1cm]

### 2021-05-04 main.tex
Updates from Overleaf

@@
 Our approach describes a comprehensive workflow implemented in the R script, which runs on the Rstudio server.
-Its function includes data retrieval, data pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
+Its function includes data retrieval, data preprocessing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
 The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.
@@
 
-The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
+The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
 The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.5 or less than 0.5) (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b) multivariate plots).
@@
 In comparison, the other 262 patients with lower expression (the cutoff at 0.027(RSEM)) had a better prognosis (adjusted \textit{P} = $0.002$) (see Figure \ref{fig:figure4}(a)).
-Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot shows that the uncorrected 147 \textit{P} values ($< 0.05$) have been estimated by a serial cut from 144 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort").
+Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot shows that the uncorrected 147 \textit{P} values ($< 0.05$) have been estimated by a serial cut from 144 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, cutoff engine).
 The smallest \textit{P} value (\num{2.97e-7}), when cut on n=262 (63.3\% of 414), has been defined as an optimal \textit{P} value.
@@
 FirebrowseR)\cite{Deng2017}. 
-We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, step 1) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
+We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, \textcolor{green}{green} square) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
 
@@
 First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
-Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} "HNSCC cohort").
+Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} cutoff engine).
 The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier \textit{P} values for each gene.
@@
 Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
-Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, step 2).
+Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, candidate selection).
 

### 2021-05-09 Cover_letter_JPM.tex
modified Figure 1
Updates from Overleaf

@@
 
-April 30, 2021
+May 16, 2021
 
@@
 %{%
-1) % {2-4}
+Reviewer 1: % {2-4}
 "Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
@@
 
-2) % {3-1}
+Reviewer 2: % {3-1}
 "Are the conclusions supported by the results?
@@
 We appreciate the reviewer for kind instruction of expression cutoff in detail.\\
-We modified the workflow as ...
-
-[after cut-off finding]
-Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
-
-***=> Bonferroni correction should be used in final decision.
-%位置要換一下：
-The false discovery rate
-645 (FDR) (< 0.05) could be used to pick up the optimal P value to ensure the control for
-646 type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
-4.2. Cutoff Finder Core Engine.
+*We modified the workflow as ...
+
+We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+\\[0.3cm]
+%as follows:
+%\begin{MyColorPar}
+The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
+%\end{MyColorPar}
+
+%***=> Bonferroni correction should be used in final decision.
 
@@
 We appreciate the reviewer for the critical comment.
-We change new Title, abstract, change tone
+We changed title as "Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
+
+* more evidence to support or validate them
 
@@
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
-調整 workfow 更加嚴格
-以增加 validation rate
-The p-values are affected by the sample size, which has be described in the main text.
+***調整 workfow 更加嚴格以增加 validation rate
+*The p-values are affected by the sample size, which has be described in the main text.
 as following:
+
+*the authors should look for more data to verify these biomarkers.
 % ???
+
 % x
-%how to apply or modify the R scripts to use on other datasets
-%\begin{itemize} %summarize the elements of the workflow
 \begin{outline}
@@
 We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
-= 詳細描述 univariable and multivariable tests work
+= 詳細描述 univariable and multivariable tests work in the Cox proportional hazard regression model.
 In a multivariable test, which variables were used? 
@@
 
-In Figure 2, unlabeled scales on the x-axis???
-除去 unlabeled stick 即可立刻改進
+In Figure 2, the ticks and labels on the x-axis were corrected.
+
 \begin{MyColorPar}{red}
@@
 
-\begin{outline} % still blue
+\begin{outline} % highlight still blue
 In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.

### 2021-05-09 main.tex
Updates from Overleaf

@@
 %\label{key:cutoff}
-To evaluate the effect of gene expression on the patient's survival, we introduced the stratifying of patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
+To evaluate the effect of gene expression on the patient's survival, we introduce a sliding window cutoff selection by stratifying patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
 Our cutofFinder\_func subroutine employs the minimum \textit{P} value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
@@
 This iteration method could calculate all possible cutoff of each gene expression in this cohort.
-At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff value (e.x.
-0.027 for gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}, Figure \ref{fig:figure4}).
-The optimal cutoff value and its correlated patient grouping size (e.x.
+At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff at specific patient grouping  (e.x.
 low-expression in 262 persons vs.
-high-expression in 152 persons with gene \acrshort{CAMK2N1}) would be returned to the main program to allow downstream Cox survival analysis.
+high-expression in 152 persons with gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}, please see Figure \ref{fig:figure4}).
+The cutoff would be returned to the main program to allow downstream Cox survival analysis.
 The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
 In case there was no significant \textit{P} value, a median expression of this gene was set as its cutpoint as usual.
-
-\subsection{Statistical Consideration}
+\begin{MyColorPar}{red}
+The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
+\end{MyColorPar}
+
+\subsection{Statistical Consideration for Survival Analysis}
 
@@
 Kaplan-Meier survival was analyzed using the log-rank test for two groups OS comparison.
-The Cox proportional hazards regression is the widely accepted approach for modeling survival while accounting for confounding factors\cite{Magen2019}.
+
+% reviewer comment 
+\begin{MyColorPar}{red}
+%The Cox proportional hazards regression is the widely accepted approach for modeling survival while
+
+The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data.
+It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}.
+% Classification trees and artificial neural networks in survival analysis
+The Cox model is also accounting for confounding factors\cite{Magen2019}.
+It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:
+
+%Linear regression is useful as a concept in biomarker discovery.
+%A linear regression equation that relates a Y-variable to n X-variables is written as\\[1cm]
+%\par
+%Highlights
+% https://quicklatex.com
+\begin{flushleft}
+% equation
+%\begin{math}
+
+%ground truth Y (e.x. patient's survival):\\[0.5cm]
+$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
+% natural exponential function => y=e^x
+\end{flushleft}
+%Y$:
+%$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
+%\linebreak
+%\linebreak
+where,\\
+\begin{outline} % for highlight
+\1 t represents the survival time
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$)
+\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
+\1 the term $h_0$ is called the baseline hazard.
+It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
+The ‘t’ in $h(t)$ indicates us that the hazard may vary over time
+
+\end{outline}
+
+Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
+\\[0.5cm]
+Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
+%A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
+%Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
+%$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
+%\linebreak
+%(predicted Y, output) intercept, slope, independent (input) \Times
+%\end{math}
+
+Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.\\[1cm]
+
 Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the OS.
+
+In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+\end{MyColorPar}
+%%
+
 Results were considered statistically significant when a two-sided \textit{P} $<$ 0.05, or a lower threshold if indicated.

### 2021-05-09 main.tex
Updates from Overleaf

@@
 \1 t represents the survival time
-\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$)
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g.
+clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
 \1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
@@
 It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
-The ‘t’ in $h(t)$ indicates us that the hazard may vary over time
-
+The ‘t’ in $h(t)$ indicates the hazard may vary over time
 \end{outline}
 
-Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
-\\[0.5cm]
-Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
+%Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
+%\\[0.5cm]
+%Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
 %A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
@@
 %\end{math}
-
-Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.\\[1cm]
-
-Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the OS.
+Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
+
+Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).
 

### 2021-05-09 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
-We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
-= 詳細描述 univariable and multivariable tests work in the Cox proportional hazard regression model.
-In a multivariable test, which variables were used? 
-= 列出來，並且強調 surgical margin
-
-% x
-In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
-(please also see Figure \ref{fig:workflow}, different sources of databases)
-
+We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
 \\[0.3cm]
+%\begin{MyColorPar}{red}
+%The Cox proportional hazards regression is the widely accepted approach for modeling survival while
+
+The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data.
+It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}.
+% Classification trees and artificial neural networks in survival analysis
+The Cox model is also accounting for confounding factors\cite{Magen2019}.
+It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:
+
+%Highlights
+% https://quicklatex.com
+\begin{flushleft}
+% equation
+%\begin{math}
+
+$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
+% natural exponential function => y=e^x
+\end{flushleft}
+where,\\
+\begin{outline} % for highlight
+\1 t represents the survival time
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g.
+clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
+\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
+\1 the term $h_0$ is called the baseline hazard.
+It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
+The ‘t’ in $h(t)$ indicates the hazard may vary over time
+\end{outline}
+
+Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
+
+Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).
+
+In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+%\end{MyColorPar}
+
+% x
+%In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
+(please also see Figure \ref{fig:workflow}, different sources of databases)
+
 %(the revised portions in the manuscript are indicated in \textcolor{red}{red} since page 2 at line 77-129)
 
-%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga
-% adopted from materials and methods
-
-%The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
-%\cite{SeanDavis;MartinMorgan2020}
-
 \end{MyColorPar}
 
-\begin{MyColorPar}{red}
-
-"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."
-
-\end{MyColorPar}   % marked in red above
+%\begin{MyColorPar}{red}
+
+%"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."
+
+%\end{MyColorPar}   % marked in red above
 
@@
 Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
-=> = a gene signature with deep learning CNN
-https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
-
-https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
 
@@
 
-We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
+We appreciate the reviewer for the critical comments.
+*** => a gene signature with deep learning CNN
+https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
+
+https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
 
@@
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
-[Minor comments]
-The background should be revised extensively. 
-x For example, the description of the linear model should be removed. X1...Xn should be removed. 
-***More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
-Detailed introduction of TCGA-related tools should be moved to Methods.
-
-In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 
-In Figure 1, the diagram should have direction. 
-加上 direction of view
-
-The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)???
-
+The description of the linear model has been removed. 
+Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
+We made a new Figure 1 with clear direction of the workflow.
+A "gene expression values (20500 genes)", instead of "RNAseq", indicates the expression data obtained from the TCGA.
 In Figure 2, the ticks and labels on the x-axis were corrected.
 
-\begin{MyColorPar}{red}
-
-\end{MyColorPar}
+***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section. 
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+%\subsubsection{utility of TCGA}
+%%%
+Usually, researchers used TCGA to find expression biomarkers...
+%%%%%%%%%
+
+***[latex line 410]
+In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
+=> First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned. 
+After detailed 梳理, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500)
+The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 謙虛道歉，修改說法
+
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+%%%
+=>  However, there are three steps of biomarker discovery from survival analysis.
+***=> Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage. 這個 要改為 reviewer's comment (risk of maximizing P-value with cutoff scan)
+...
 

### 2021-05-09 Cover_letter_JPM.tex
Updates from Overleaf

@@
 => First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned. 
-After detailed 梳理, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500)
-The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 謙虛道歉，修改說法
-
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
+%% The three challenges are not "challenges" at all. The authors exaggerated the difficulties here. 
+%不要誇大說明 謙虛道歉，修改說法
+=> We are apology for exaggerating the difficulties of our workflow.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.
+
 %%%
-=>  However, there are three steps of biomarker discovery from survival analysis.
-***=> Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage. 這個 要改為 reviewer's comment (risk of maximizing P-value with cutoff scan)
-...
+There are three steps of biomarker discovery from survival analysis.
+First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
+%%% *** with more
+Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+
+% risk of 
+Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.
 

### 2021-05-09 main.tex
Updates from Overleaf

@@
 
+%%% ***
 In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
-However, there are three challenges of biomarker discovery from survival analysis.
+\begin{MyColorPar}{red} %%%
+There are three steps of biomarker discovery from survival analysis.
 First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
-Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+%%% *** with more
+Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+\end{MyColorPar} %%%
 Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type.
@@
 It is not possible to scan the whole human protein-coding genome in this way.
-Third, we need to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+\begin{MyColorPar}{red} %%% %%%
+% risk of 
+Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.
+%Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. 
+%Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05).
+For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff.
+But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff.
+\end{MyColorPar} %%%
 The above mentioned web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.

### 2021-05-09 Cover_letter_JPM.tex
Updates from Overleaf

@@
 Usually, researchers used TCGA to find expression biomarkers...
+see https://www.biostars.org/p/153013/
+Tutorial: Survival analysis of TCGA patients
+#integrating gene expression (RNASeq) data Why would you want to do survival
+#analysis based on gene expression data? Well, let's say you have a number of
+#genes that you are interested in and they are differentially expressed between
+#tumor and normal samples, it would be very powerful to show that alteration in
+#gene expression correlates with worse survival or earlier tumor recurrence.
+#https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
+#from Mary Goldman and Jing Zhu, UCSC Cancer Browser
+#https://genome-cancer.ucsc.edu/
 %%%%%%%%%
@@
 First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
-%%% *** with more
+%%% 
+{
+[main_marginSFP_HNSCC.R] line 1361
+=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
+OS_live_days /30 # derived from last followup [30]/ last known alive [31])
+event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
+R help from Jorge I Velez
+[line 1654]
+=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
+# SLC35E2A: 9906
+# SLC35E2B: 728661
+}
+
+%%%
 Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.

### 2021-05-10 Cover_letter_JPM.tex
Updates from Overleaf

@@
 \subsection*{1-1}
+\begin{MyColorPar}{blue}
 First of all, please describe the difference between the two manuscripts.
-
+\end{MyColorPar}
 %The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method.
@@
 
-\begin{MyColorPar}{blue}
 Answer
@@
 ([ok] 3.2, 3.3 只留下 validated by GSE2837)
-(ok)Figure_4_CAMK2N1_IL19.pdf  KM plots
+(ok) Figure_4_CAMK2N1_IL19.pdf  KM plots
 (ok)table 1 (6 genes), (ok) table 2 (4 genes)
@@
 }
+
 six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
@@
 }
+
 2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).
@@
 %analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
-\end{MyColorPar}
+%\end{MyColorPar}
 
 \subsection*{1-2}
+\begin{MyColorPar}{blue}
 Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
@@
 Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.
-
+\end{MyColorPar}
 %DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
@@
 
-\begin{MyColorPar}{blue}
+%\begin{MyColorPar}{blue}
 Answer
@@
 %\end{MyColorPar}
-The summary of holistic cancer care in this revised manuscript could be:
+The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129).
+Also, it was shown here in the following paragraph.
+\begin{MyColorPar}{red}
 "
-".
+"
+\end{MyColorPar}
 
@@
 \subsection*{2-1}
+\begin{MyColorPar}{blue}
 Exploring all possible expression cutoffs is controversial.
@@
 Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
-
-\begin{MyColorPar}{blue}
+\end{MyColorPar}
+
+%
 Answer
@@
 \\[0.3cm]
-%as follows:
-%\begin{MyColorPar}
+
+\begin{MyColorPar}{red}
 The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
-%\end{MyColorPar}
+\end{MyColorPar}
 
@@
 
-\end{MyColorPar}
+%
 
 \subsection*{2-2}
+\begin{MyColorPar}{blue}
 I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them.
 % new Title, abstract, change tone
-
-\begin{MyColorPar}{blue}
+\end{MyColorPar}
+
+%
 Answer
@@
 
-\end{MyColorPar}
+%
 
 \subsection*{2-3}
+\begin{MyColorPar}{blue}
 % strategy should changing
@@
 As I mentioned above, the authors should look for more data to verify these biomarkers.
-
-\begin{MyColorPar}{blue}
+\end{MyColorPar}
+
+%
 Answer
@@
 *the authors should look for more data to verify these biomarkers.
-% ???
-
-% x
+???
+
+% xxxxx
 \begin{outline}
@@
 %It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
-Moreover, we are planning to extend this workflow applied to other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
-Then it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=14cm]{Figure_1_manuscript_workflow_modify.pdf}
-    \caption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).
-The portion of "data process/cleaning"(red rectangled) should be modified aggressively according to different sources of databases, e.x.
-The NCI's TCGA Genomic Data Commons (GDC) porting to Broad Firehose, or other databases.}
-    \label{fig:workflow}
-\end{figure}
+
+%Moreover, we are planning to extend this workflow applied to other studies, such as TCGA CRC (colorectal cancer), TCGA LUAD (lung adenocarcinoma), or TCGA BRCA (breast cancer).
+%Then it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
+
 %(other cancer types in the TCGA database). 
@@
 Thus, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web application of the "pvalueTex" packaged with our workflow in the future.
-\end{MyColorPar}
+%\end{MyColorPar}
 
@@
 \subsection*{2-4}
+\begin{MyColorPar}{blue}
 How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
-
-\begin{MyColorPar}{blue}
+\end{MyColorPar}
+
+%
 Answer
@@
 \\[0.3cm]
-%\begin{MyColorPar}{red}
+
+\begin{MyColorPar}{red}
 %The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
-
 The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data.
@@
 In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
-%\end{MyColorPar}
+\end{MyColorPar}
 
@@
 
-\end{MyColorPar}
-
-%\begin{MyColorPar}{red}
-
 %"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."
-
-%\end{MyColorPar}   % marked in red above
 
@@
 \subsection*{2-5}
+\begin{MyColorPar}{blue}
 Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
-
-\begin{MyColorPar}{blue}
+\end{MyColorPar}
+%
 Answer
@@
 
-\end{MyColorPar}
+%
 
 \subsection*{2-6}
+\begin{MyColorPar}{blue}
 [Minor comments]
@@
 In Figure 2, unlabeled scales on the x-axis.
-
-\begin{MyColorPar}{blue}
+\end{MyColorPar}
+
+%
 Answer
@@
 
+%%
+\begin{MyColorPar}{blue} % minor comment
 ***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
+\end{MyColorPar}
+
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+
+\begin{MyColorPar}{red}
 %\subsubsection{utility of TCGA}
@@
 %%%%%%%%%
-
-***[latex line 410]
+\end{MyColorPar}
+
+%%%***[latex line 410]
+\begin{MyColorPar}{blue} % minor comment
 In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
-=> First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned. 
-After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
-%% The three challenges are not "challenges" at all. The authors exaggerated the difficulties here. 
-%不要誇大說明 謙虛道歉，修改說法
+The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
+\end{MyColorPar}
+
+% 不要誇大說明 謙虛道歉
 => We are apology for exaggerating the difficulties of our workflow.
@@
 
+\begin{MyColorPar}{red}
 %%%
 There are three steps of biomarker discovery from survival analysis.
-First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
-%%% 
+First, although \acrshort{tcga} genomics data was harmonized, there are 
+several points should be manually investigated and cleaned.
+
+\begin{outline}
+\1 including null expressed genes, over 50\% of the cohort, 
+\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
 {
@@
 }
-
-%%%
+\end{outline}
+
 Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
@@
 
-% the end of response rebuttal
+% the end of response rebuttal %%%%%%%%%%%%
 

### 2021-05-10 Cover_letter_JPM.tex
Updates from Overleaf

@@
 \subsection*{1-1}
-\begin{MyColorPar}{blue}
+%\begin{MyColorPar}{blue}
 First of all, please describe the difference between the two manuscripts.
-\end{MyColorPar}
+
 %The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method.
@@
 
+\begin{MyColorPar}{blue}
 Answer
@@
 2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).
-
+\end{MyColorPar}
+
+%% x
 %[我的 candidate 中為什麼沒有 EGFR];  
@@
 \subsection*{1-2}
-\begin{MyColorPar}{blue}
+%
 Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
@@
 Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.
-\end{MyColorPar}
+
 %DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
@@
 
-%\begin{MyColorPar}{blue}
+\begin{MyColorPar}{blue}
 Answer
@@
 "
-\end{MyColorPar}
-
+\end{MyColorPar} %red
+\end{MyColorPar} % blue
 %Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation),
@@
 
-\end{MyColorPar}
 \pagebreak
+
 %======
@@
 \subsection*{2-1}
-\begin{MyColorPar}{blue}
+
 Exploring all possible expression cutoffs is controversial.
@@
 Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
-\end{MyColorPar}
 
 %
+\begin{MyColorPar}{blue}
 Answer
@@
 
+\end{MyColorPar}
 %***=> Bonferroni correction should be used in final decision.
@@
 \subsection*{2-2}
-\begin{MyColorPar}{blue}
+
 I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them.
 % new Title, abstract, change tone
-\end{MyColorPar}
 
 %
+\begin{MyColorPar}{blue}
 Answer
@@
 %
+\end{MyColorPar}
 
 \subsection*{2-3}
-\begin{MyColorPar}{blue}
+
 % strategy should changing
@@
 As I mentioned above, the authors should look for more data to verify these biomarkers.
-\end{MyColorPar}
 
 %
+\begin{MyColorPar}{blue}
 Answer
@@
 ???
+
+\end{MyColorPar}
+
+% #####################
+\subsection*{2-4}
+
+How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
+
+%
+\begin{MyColorPar}{blue}
+Answer
+
+We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+\\[0.3cm]
+
+\begin{MyColorPar}{red}
+%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
+The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data.
+It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}.
+% Classification trees and artificial neural networks in survival analysis
+The Cox model is also accounting for confounding factors\cite{Magen2019}.
+It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:
+
+%Highlights
+% https://quicklatex.com
+\begin{flushleft}
+% equation
+%\begin{math}
+
+$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
+% natural exponential function => y=e^x
+\end{flushleft}
+where,\\
+\begin{outline} % for highlight
+\1 t represents the survival time
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g.
+clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
+\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
+\1 the term $h_0$ is called the baseline hazard.
+It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
+The ‘t’ in $h(t)$ indicates the hazard may vary over time
+\end{outline}
+
+Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
+
+Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).
+
+In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+\end{MyColorPar}
+
+\end{MyColorPar}% end of answer 2.4
+
+% x
+%In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
+(please also see Figure \ref{fig:workflow}, different sources of databases)
+
+%(the revised portions in the manuscript are indicated in \textcolor{red}{red} since page 2 at line 77-129)
+
+%"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."
+
+%The other GDAC, the MD Anderson GDAC's MBatch (http://bioinformatics.mdanderson.org/tcgabatcheffects) is a website that enables scientists to identify and quantify the batch effects accompanying TCGA data set, currently according to hierarchical clustering and enhanced PCA plots.
+
+% RNA-Seq
+%The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
+%The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
+It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
+
+\subsection*{2-5}
+
+Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
+
+%
+\begin{MyColorPar}{blue}
+Answer
+
+We appreciate the reviewer for the critical comments.
+*** => a gene signature with deep learning CNN
+https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
+
+https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
+
+\end{MyColorPar}
+%
+
+\subsection*{2-6}
+[Minor comments]
+The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
+More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
+Detailed introduction of TCGA-related tools should be removed or moved to Methods.
+In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
+In Figure 1, the diagram should have direction. 
+The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
+In Figure 2, unlabeled scales on the x-axis.
+
+%
+\begin{MyColorPar}{blue}
+Answer
+
+We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
+The description of the linear model has been removed. 
+Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
+We made a new Figure 1 with clear direction of the workflow.
+A "gene expression values (20500 genes)", instead of "RNAseq", indicates the expression data obtained from the TCGA.
+In Figure 2, the ticks and labels on the x-axis were corrected.
+
+%%
+\begin{MyColorPar}{black} % minor comment
+***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
+\end{MyColorPar}
+
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+
+\begin{MyColorPar}{red}
+%\subsubsection{utility of TCGA}
+%%%
+Usually, researchers used TCGA to find expression biomarkers...
+see https://www.biostars.org/p/153013/
+Tutorial: Survival analysis of TCGA patients
+#integrating gene expression (RNASeq) data Why would you want to do survival
+#analysis based on gene expression data? Well, let's say you have a number of
+#genes that you are interested in and they are differentially expressed between
+#tumor and normal samples, it would be very powerful to show that alteration in
+#gene expression correlates with worse survival or earlier tumor recurrence.
+#https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
+#from Mary Goldman and Jing Zhu, UCSC Cancer Browser
+#https://genome-cancer.ucsc.edu/
+%%%%%%%%%
+\end{MyColorPar}
+
+%%%***[latex line 410]
+\begin{MyColorPar}{black} % minor comment
+In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
+The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
+\end{MyColorPar}
+
+% 不要誇大說明 謙虛道歉
+=> We are apology for exaggerating the difficulties of our workflow.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.
+
+\begin{MyColorPar}{red}
+%%%
+There are three steps of biomarker discovery from survival analysis.
+First, although \acrshort{tcga} genomics data was harmonized, there are 
+several points should be manually investigated and cleaned.
+
+\begin{outline}
+\1 including null expressed genes, over 50\% of the cohort, 
+\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
+{
+[main_marginSFP_HNSCC.R] line 1361
+=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
+OS_live_days /30 # derived from last followup [30]/ last known alive [31])
+event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
+R help from Jorge I Velez
+[line 1654]
+=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
+# SLC35E2A: 9906
+# SLC35E2B: 728661
+}
+\end{outline}
+
+Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+
+% risk of 
+Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.
+
+\end{MyColorPar} % end of red
+
+\end{MyColorPar} % end of blue answer 2-6
+% the end of response rebuttal %%%%%%%%%%%%
+
+%\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
+\bibliographystyle{unsrt} %model1-num-names}
+\bibliography{TCGA_margin_cutoff.bib}
+
+\section{end_document}
+\end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagebreak
+
+%\section*{Response to Reviewer 3 Comments}
+%Response to Referees} % rebuttal
+We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
+The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
+%Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
+
+%\subsection*{Comments from the reviewer \#3}
+
+Round 1:
+%Must be improved:
+%Is the research design appropriate?
+%Are the results clearly presented?
+Are the conclusions supported by the results?
+
+Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.
+
+There is little information provided. The authors should provide more evidence to support this article.
+
+Round 2:
+The authors still did not provide any experiment results that support the finding of the manuscript.
+
+\begin{MyColorPar}{blue}
+Answer
+
+%\subsection*{Revision notes: rebuttal}  
+%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
+%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
+% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
+%in a respectful and considerate manner.
+We appreciate the reviewer for the critical comment and apology for short of experiment results. 
+%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
+It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
+%下一篇文章的內容。目前在計畫中，但還沒有開始進行
+These in vitro and in vivo validation experiments will be undertaken in our laboratory.
+We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
+%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
+The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x.
+proliferation, migration, and invasion) and mouse xenograft model (e.x.
+tumor growth).
+%這些都需要一年以上的時間
+%their rationale for looking into TMSB4X is not strongly supported by the available data.
+
+% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
+Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
+%Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
+%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
+%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
+%the rest of the analysis seems fine, but 
+%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset.
+% to find more useful biomarkers.
+% or even other cancer types
+% to allow successful repetition and extension of analyses based on original data
+A good practice of research reproducibility is necessary to allow the reuse of code and results for new projects.
+%previously developed methodology to be effectively applied on new data, or to allow 
+%reuse of code and results for new projects. %In other words, good habits of reproducibility
+It may turn out to be a time-saver in the longer run.
+When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
+%why reproducibility?
+%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows.
+Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
+%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
+
+Once our laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis.
+%help to discover a potential drug for HNSCC therapy.
+%https://www.mdpi.com/journal/cancers/instructions
+
+%The authors should provide a separate Revision Notes file for revisions.
+The file should include a point-by-point response to each reviewer's comments, which the authors have received alongside the initial decision letter from the handling editor.
+Revision notes should clearly state the revisions the authors made to the manuscript, preferably including the subdivision title and page/line numbers to indicate where the manuscript has been edited.
+
+% rebuttal
+%Reconsider after Major Revisions: 
+%The acceptance of the manuscript would depend on the revisions. The author needs to provide a point by point response or provide a rebuttal if some of the reviewer’s comments cannot be revised.
+
+%All reviewer comments should be responded to in a point-by-point fashion.
+
+%usually, only one round of major revisions is allowed.
+Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.
+\pagebreak
+
+%\subsubsection*{Author Appeals for a rejection, in case}
+%Authors may appeal a rejection by sending an e-mail to the Editorial Office of the journal.
+The appeal must provide a detailed justification, including point-by-point responses to the reviewers' and/or Editor's comments.
+The Managing Editor of the journal will forward the manuscript and related information (including the identities of the referees) to the Editor-in-Chief, Associate Editor, or Editorial Board member.
+The academic Editor being consulted will be asked to give an advisory recommendation on the manuscript and may recommend acceptance, further peer-review, or uphold the original rejection decision.
+A reject decision at this stage is final and cannot be reversed.
+
+...
+
+%\subsection*{Material and Methods}
+
+%\subsubsection{Quantitative real-time PCR (qRT-PCR) analysis}
+%\subsectionmark*{qRT-PCR analysis}
+
+DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3].
+The primer sequences were as follows: DKK1 forward primer: 5'-TAGAGTCTAGAACGCAAGGATCT-3' and DKK1 reverse primer: 5'-CAAAAACTATCACAGCCTAAAGGG--3'; $\beta$-actin forward primer: 5'-TTGTTACAG GAAG TCCCTTGC C-3' and $\beta$-actin reverse primer: 5'-ATGCTATCACCTCCCC TGTGTG-3'.
+Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)].
+All experiments were performed in triplicate.\cite{Shi2014}
+
+由 HNSCC cell lysate 測出 qRT-PCR，DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1 表現高；ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN and NPB 表現低？
+
+然後我收集 7 genes 的 primer sequence pairs
+做 qPCR 證明在 HNSCC 口腔癌 cell lysate 中是多的。當成回答問題：experiment prove our discovered 7 (out of 20 )genes 是值得繼續探索下去。
+
+qRT-PCR and western blot analyses
+
+DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3].
+The primer sequences were as follows: DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCT C-3′ and DKK1 reverse primer: 5′-CAAAAAC TATCACAGCCTAAAGGG-3′; β-actin forward primer: 5′-TTGTTACAG GAAG TCCCTTGC C-3′and β-actin reverse primer: 5′-ATGCTATCACCTCCCC TGTGTG-3′.
+Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)].
+All experiments were performed in triplicate.
+
+qRT-PCR primer design: primer sequence of
+DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCTC-3′
+DKK1 reverse primer: 5′-CAAAAACTATCACAGCCTAAAGGG-3′
+
+FaDu cells
+STC2 forward primer: 5'-TGAAATGTAAGGCCCACGCT-3'
+STC2 reverse primer: 5'-CGAGGTGCAGAAGCTCAAGA-3'
+
+PGK1 (condition: 62dC, Ct 25)
+PGK1 forward primer: 5'-CAAGAAGTGTGCTGAGGCTGTCAC-3'
+PGK1 reverse primer: 5'-GCAGTGTCTCCACCACCTATGAT-3'
+
+SURF4 forward primer: 5'-GAT CCC CTC AGC ACC TTC CTG GAG GAT TCA AGA GAT CCT CCA GGA AGG TGC-3'
+SURF4  reverse primer: 5'-AGC TTT TCC AAA AAT CAG CAC CTT CCT GGA GGA TCT CTT GAA TTC TCC AGG AAG-3'
+
+USP10
+USP10  forward primer: 5'-AAATGCCACCGAACCTATCGGC-3'
+USP10 reverse primer: 5'-CAGCCATTCAGACCGATCTGGA-3'
+(https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153)
+
+FOXA2
+FOXA2 forward primer: 5'-GGAACACCACTACGCCTTCAAC-3'
+FOXA2 reverse primer: 5'-AGTGCATCACCTGTTCGTAGGC-3'
+
+STIP1
+STIP1 forward primer: 5'-ATCCTCAGCGTCCTCTTGG‐3′
+STIP1 reverse primer: 5'-GGTGGAGGTGTTGCAATCTCTT‐3′
+(https://onlinelibrary.wiley.com/doi/full/10.1002/gcc.22136)\cite{Cho2014}
+
+%\subsection*{Results}
+
+%\subsection*{Discussion}
+
+\begin{outline} % highlight still blue
+In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
+Comparison with previous publications or database analyses,
+
+\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort
+
+\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using TCGA HNSCC cohort from \acrfull{hpa}.
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
+
+\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
+
+\1 The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+
+\end{outline}
+
+According to the reviewer's comment, the Discussion was modified accordingly.
+The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised.
+Also, it was shown here in the following paragraph.
+\\[0.3cm]
+%(the revised portions in the manuscript are indicated in \textcolor{red}{red})
+
+%\begin{MyColorPar}{red}
+
+"We utilized other approaches to validate our candidates.
+
+\subsubsubsection*{Analysis by web-tools}
+
+%\subsubsection*{SurvExpress} % TCGA
+% 2021/01/23 pdf x 12 from SurvExpress
+SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
+Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
+1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);
+%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).
+%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635),
+The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort.
+Please see Supplementary Figure S1.
+%\ref{fig:fig_SurvExpress}.
+% moved to supplementary file
+
+% % SurvExpress 沒有類似的結果是因為:
+Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
+Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
+%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
+
+%\subsubsection{HPA} %still TCGA's RNA-Seq
+The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
+The HPA's Pathology Atlas analyzes each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
+Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
+All transcriptomics data has been retrieved from the Cancer Genome Atlas, and all proteomics data has been generated in-house using the same antibodies.
+Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/\\pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/\\ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset 
+(Please see Supplementary Figure S2.) %\ref{fig:fig_HPA_USP10})
+% moved to Supplementary
+
+% Version: 3.0.2 Date: 2015/06/11 SurvNet
+%Preloaded TCGA  data is also available for analysis.
+%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
+%gene regulatory or protein interaction network
+% cited by 10 articles
+% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
+% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
+%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
+
+%\subsubsection*{GSE2837} % non-TCGA
+% from Anwser2-2
+%by GEO GSE2837 HNSCC dataset (PrognoScan)
+We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
+relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
+and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
+The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
+1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635), 
+Please see Supplementary Figure S3. %\ref{figure:fig_GSE2837}.
+Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
+%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
+%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
+%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
+The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
+
+\subsubsubsection*{Review articles}
+After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
+%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
+
+%%%%%% bad guy
+The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}. %quantitative real-time PCR and western blot analyses
+Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
+
+%STC2:
+The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
+
+% PGK1
+Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
+The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.
+
+%SURF4
+Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
+) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.
+SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
+%NIH/3T3 cells (Mus musculus, mouse), 293T cell
+%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
+%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
+%web-based tools survival (not TCGA?)
+
+% USP10 qPCR primer https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153
+Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
+Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
+https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
+
+%FOXA2
+Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
+FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
+%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
+%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
+% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
+%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
+Further, SIS analysis was performed to further screen out a stable probe combination.
+Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
+2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
+Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
+2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
+%Association between gene expression and methylation.
+Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
+Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
+
+% STIP1; non-TCGA
+Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
+in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. 
+The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
+%STIP1 could bind to bind Hsp70 and Hsp90.
+
+%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
+%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
+%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
+% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
+
+%%%%%% good guy
+%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
+%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
+%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
+%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
+
+%ZNF266, % or ZNF16, HZF1?
+%MYO1H associated mandibular prognathism\cite{Sun2018}
+
+% FCGBP
+% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
+Fc fragment of IgG binding protein (($Fc\gamma BP$, FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas.\cite{ODonovan2002}\cite{Griffith2006}
+%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
+%gene ID @gene@8857
+
+%?LOC148709?, 
+%EVPLL in cDNA project
+
+% PNMA5
+Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
+
+%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
+GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
+
+%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
+(PMID31598163)
+%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
+The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
+Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
+%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
+%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
+%\cite{Li2018b}
+%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
+%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+
+%NDFIP1:
+%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
+was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
+%MCF7 cells 
+%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
+%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
+%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
+Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
+We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
+hepatocellular carcinoma\cite{Zhang2019a}
+% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
+%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
+It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
+
+%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+%DKC1 is the tumor suppressor gene in HNSCC
+% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
+
+The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo."
+
+%\end{MyColorPar} % marked as red
+
+\pagebreak
+
+\end{MyColorPar}
+
+%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
+
+%After that, there are 18,082 cross-cancer type articles produced using the TCGA database.
+The 778 publications (Figure \ref{figure:fig_embase}, b.
+778) among them were focused on HNSCC research.
+Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time.
+Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008.
+%\ref{figure:fig_embase}
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_2-1.pdf}
+\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
+\label{figure:fig_embase}
+\end{figure}
+\clearpage
+%778/4350 = 17.9\% using TCGA data
+%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
+%http://www.actrec.gov.in/OCDB/index.htm
+
+Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
+GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.
+However, the MSKCC, Broad, and Johns Hopkins databases were processed through whole-exome sequencing instead of whole-genome sequencing in the TCGA database.
+
+There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a} and Gene Expression Profiling Interactive Analysis (GEPIA, GEPIA2)\cite{Tang2019}.
+According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
+Furthermore, almost all of their survival data came from the TCGA database.
+%GEO (few survival features, less than 100 participate in each GSE dataset)
+%GSE31056, GSE2837 (Prognoscan)
+%there is survival feature: A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
+%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).\cite{Lawrence2015a}
+%datasets for each cancer type that include exactly the same prediction and outcome variables and consider comparable target populations. Currently, such data is simply not available.
+
+%The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
+%Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+%Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+%Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+%DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+%The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+
+For example, Wei et al.\cite{Wei2020} conducted the analysis of the prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a web-based tool that plots expression profiles of given genes (dataset from TCGA database)
+They has suggested that overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+
+Conclusion: TCGA database is representative of HNSCC.
+
+\begin{figure}
+\raggedleft
+\includegraphics[width=14cm]{Answer_2-2.pdf}
+\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
+\label{figure:fig_GSE2837}
+\end{figure}
+\clearpage
+
+%%%
 
@@
 %\end{MyColorPar}
-
-% #####################
-\subsection*{2-4}
-\begin{MyColorPar}{blue}
-How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
-\end{MyColorPar}
-
-%
-Answer
-
-We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
-\\[0.3cm]
-
-\begin{MyColorPar}{red}
-%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
-The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data.
-It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}.
-% Classification trees and artificial neural networks in survival analysis
-The Cox model is also accounting for confounding factors\cite{Magen2019}.
-It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:
-
-%Highlights
-% https://quicklatex.com
-\begin{flushleft}
-% equation
-%\begin{math}
-
-$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
-% natural exponential function => y=e^x
-\end{flushleft}
-where,\\
-\begin{outline} % for highlight
-\1 t represents the survival time
-\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g.
-clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
-\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
-\1 the term $h_0$ is called the baseline hazard.
-It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
-The ‘t’ in $h(t)$ indicates the hazard may vary over time
-\end{outline}
-
-Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
-
-Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).
-
-In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
-\end{MyColorPar}
-
-% x
-%In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors.
-(please also see Figure \ref{fig:workflow}, different sources of databases)
-
-%(the revised portions in the manuscript are indicated in \textcolor{red}{red} since page 2 at line 77-129)
-
-%"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."
-
-%The other GDAC, the MD Anderson GDAC's MBatch (http://bioinformatics.mdanderson.org/tcgabatcheffects) is a website that enables scientists to identify and quantify the batch effects accompanying TCGA data set, currently according to hierarchical clustering and enhanced PCA plots.
-
-% RNA-Seq
-%The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
-\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
-%The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
-It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
-
-\subsection*{2-5}
-\begin{MyColorPar}{blue}
-Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
-\end{MyColorPar}
-%
-Answer
-
-We appreciate the reviewer for the critical comments.
-*** => a gene signature with deep learning CNN
-https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
-
-https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
-
-%
-
-\subsection*{2-6}
-\begin{MyColorPar}{blue}
-[Minor comments]
-The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
-More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
-Detailed introduction of TCGA-related tools should be removed or moved to Methods.
-In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
-In Figure 1, the diagram should have direction. 
-The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
-In Figure 2, unlabeled scales on the x-axis.
-\end{MyColorPar}
-
-%
-Answer
-
-We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
-The description of the linear model has been removed. 
-Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
-We made a new Figure 1 with clear direction of the workflow.
-A "gene expression values (20500 genes)", instead of "RNAseq", indicates the expression data obtained from the TCGA.
-In Figure 2, the ticks and labels on the x-axis were corrected.
-
-%%
-\begin{MyColorPar}{blue} % minor comment
-***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
-\end{MyColorPar}
-
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
-
-\begin{MyColorPar}{red}
-%\subsubsection{utility of TCGA}
-%%%
-Usually, researchers used TCGA to find expression biomarkers...
-see https://www.biostars.org/p/153013/
-Tutorial: Survival analysis of TCGA patients
-#integrating gene expression (RNASeq) data Why would you want to do survival
-#analysis based on gene expression data? Well, let's say you have a number of
-#genes that you are interested in and they are differentially expressed between
-#tumor and normal samples, it would be very powerful to show that alteration in
-#gene expression correlates with worse survival or earlier tumor recurrence.
-#https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
-#from Mary Goldman and Jing Zhu, UCSC Cancer Browser
-#https://genome-cancer.ucsc.edu/
-%%%%%%%%%
-\end{MyColorPar}
-
-%%%***[latex line 410]
-\begin{MyColorPar}{blue} % minor comment
-In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
-The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
-\end{MyColorPar}
-
-% 不要誇大說明 謙虛道歉
-=> We are apology for exaggerating the difficulties of our workflow.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.
-
-\begin{MyColorPar}{red}
-%%%
-There are three steps of biomarker discovery from survival analysis.
-First, although \acrshort{tcga} genomics data was harmonized, there are 
-several points should be manually investigated and cleaned.
-
-\begin{outline}
-\1 including null expressed genes, over 50\% of the cohort, 
-\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
-{
-[main_marginSFP_HNSCC.R] line 1361
-=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
-OS_live_days /30 # derived from last followup [30]/ last known alive [31])
-event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
-R help from Jorge I Velez
-[line 1654]
-=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
-# SLC35E2A: 9906
-# SLC35E2B: 728661
-}
-\end{outline}
-
-Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
-
-% risk of 
-Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
-However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.
-
-\end{MyColorPar}
-
-% the end of response rebuttal %%%%%%%%%%%%
-
-%\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%\externalbibliography{yes}
-%\bibliography{your_external_BibTeX_file}
-\bibliographystyle{unsrt} %model1-num-names}
-\bibliography{TCGA_margin_cutoff.bib}
-
-\section{end_document}
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\pagebreak
-
-%\section*{Response to Reviewer 3 Comments}
-%Response to Referees} % rebuttal
-We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
-The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
-%Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
-
-%\subsection*{Comments from the reviewer \#3}
-
-Round 1:
-%Must be improved:
-%Is the research design appropriate?
-%Are the results clearly presented?
-Are the conclusions supported by the results?
-
-Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.
-
-There is little information provided. The authors should provide more evidence to support this article.
-
-Round 2:
-The authors still did not provide any experiment results that support the finding of the manuscript.
-
-\begin{MyColorPar}{blue}
-Answer
-
-%\subsection*{Revision notes: rebuttal}  
-%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
-%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
-% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
-%in a respectful and considerate manner.
-We appreciate the reviewer for the critical comment and apology for short of experiment results. 
-%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
-It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
-%下一篇文章的內容。目前在計畫中，但還沒有開始進行
-These in vitro and in vivo validation experiments will be undertaken in our laboratory.
-We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
-%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
-The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x.
-proliferation, migration, and invasion) and mouse xenograft model (e.x.
-tumor growth).
-%這些都需要一年以上的時間
-%their rationale for looking into TMSB4X is not strongly supported by the available data.
-
-% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
-Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
-%Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
-%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
-%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
-%the rest of the analysis seems fine, but 
-%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
-We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset.
-% to find more useful biomarkers.
-% or even other cancer types
-% to allow successful repetition and extension of analyses based on original data
-A good practice of research reproducibility is necessary to allow the reuse of code and results for new projects.
-%previously developed methodology to be effectively applied on new data, or to allow 
-%reuse of code and results for new projects. %In other words, good habits of reproducibility
-It may turn out to be a time-saver in the longer run.
-When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
-%why reproducibility?
-%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows.
-Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
-%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
-
-Once our laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis.
-%help to discover a potential drug for HNSCC therapy.
-%https://www.mdpi.com/journal/cancers/instructions
-
-%The authors should provide a separate Revision Notes file for revisions.
-The file should include a point-by-point response to each reviewer's comments, which the authors have received alongside the initial decision letter from the handling editor.
-Revision notes should clearly state the revisions the authors made to the manuscript, preferably including the subdivision title and page/line numbers to indicate where the manuscript has been edited.
-
-% rebuttal
-%Reconsider after Major Revisions: 
-%The acceptance of the manuscript would depend on the revisions. The author needs to provide a point by point response or provide a rebuttal if some of the reviewer’s comments cannot be revised.
-
-%All reviewer comments should be responded to in a point-by-point fashion.
-
-%usually, only one round of major revisions is allowed.
-Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.
-\pagebreak
-
-%\subsubsection*{Author Appeals for a rejection, in case}
-%Authors may appeal a rejection by sending an e-mail to the Editorial Office of the journal.
-The appeal must provide a detailed justification, including point-by-point responses to the reviewers' and/or Editor's comments.
-The Managing Editor of the journal will forward the manuscript and related information (including the identities of the referees) to the Editor-in-Chief, Associate Editor, or Editorial Board member.
-The academic Editor being consulted will be asked to give an advisory recommendation on the manuscript and may recommend acceptance, further peer-review, or uphold the original rejection decision.
-A reject decision at this stage is final and cannot be reversed.
-
-...
-
-%\subsection*{Material and Methods}
-
-%\subsubsection{Quantitative real-time PCR (qRT-PCR) analysis}
-%\subsectionmark*{qRT-PCR analysis}
-
-DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3].
-The primer sequences were as follows: DKK1 forward primer: 5'-TAGAGTCTAGAACGCAAGGATCT-3' and DKK1 reverse primer: 5'-CAAAAACTATCACAGCCTAAAGGG--3'; $\beta$-actin forward primer: 5'-TTGTTACAG GAAG TCCCTTGC C-3' and $\beta$-actin reverse primer: 5'-ATGCTATCACCTCCCC TGTGTG-3'.
-Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)].
-All experiments were performed in triplicate.\cite{Shi2014}
-
-由 HNSCC cell lysate 測出 qRT-PCR，DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1 表現高；ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN and NPB 表現低？
-
-然後我收集 7 genes 的 primer sequence pairs
-做 qPCR 證明在 HNSCC 口腔癌 cell lysate 中是多的。當成回答問題：experiment prove our discovered 7 (out of 20 )genes 是值得繼續探索下去。
-
-qRT-PCR and western blot analyses
-
-DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3].
-The primer sequences were as follows: DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCT C-3′ and DKK1 reverse primer: 5′-CAAAAAC TATCACAGCCTAAAGGG-3′; β-actin forward primer: 5′-TTGTTACAG GAAG TCCCTTGC C-3′and β-actin reverse primer: 5′-ATGCTATCACCTCCCC TGTGTG-3′.
-Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)].
-All experiments were performed in triplicate.
-
-qRT-PCR primer design: primer sequence of
-DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCTC-3′
-DKK1 reverse primer: 5′-CAAAAACTATCACAGCCTAAAGGG-3′
-
-FaDu cells
-STC2 forward primer: 5'-TGAAATGTAAGGCCCACGCT-3'
-STC2 reverse primer: 5'-CGAGGTGCAGAAGCTCAAGA-3'
-
-PGK1 (condition: 62dC, Ct 25)
-PGK1 forward primer: 5'-CAAGAAGTGTGCTGAGGCTGTCAC-3'
-PGK1 reverse primer: 5'-GCAGTGTCTCCACCACCTATGAT-3'
-
-SURF4 forward primer: 5'-GAT CCC CTC AGC ACC TTC CTG GAG GAT TCA AGA GAT CCT CCA GGA AGG TGC-3'
-SURF4  reverse primer: 5'-AGC TTT TCC AAA AAT CAG CAC CTT CCT GGA GGA TCT CTT GAA TTC TCC AGG AAG-3'
-
-USP10
-USP10  forward primer: 5'-AAATGCCACCGAACCTATCGGC-3'
-USP10 reverse primer: 5'-CAGCCATTCAGACCGATCTGGA-3'
-(https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153)
-
-FOXA2
-FOXA2 forward primer: 5'-GGAACACCACTACGCCTTCAAC-3'
-FOXA2 reverse primer: 5'-AGTGCATCACCTGTTCGTAGGC-3'
-
-STIP1
-STIP1 forward primer: 5'-ATCCTCAGCGTCCTCTTGG‐3′
-STIP1 reverse primer: 5'-GGTGGAGGTGTTGCAATCTCTT‐3′
-(https://onlinelibrary.wiley.com/doi/full/10.1002/gcc.22136)\cite{Cho2014}
-
-%\subsection*{Results}
-
-%\subsection*{Discussion}
-
-\begin{outline} % highlight still blue
-In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
-Comparison with previous publications or database analyses,
-
-\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using SurvExpress with TCGA cohort
-
-\1 The 12 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using TCGA HNSCC cohort from \acrfull{hpa}.
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level.\cite{Ren2020}
-
-\1 The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
-
-\1 The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
-
-\end{outline}
-
-According to the reviewer's comment, the Discussion was modified accordingly.
-The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised.
-Also, it was shown here in the following paragraph.
-\\[0.3cm]
-%(the revised portions in the manuscript are indicated in \textcolor{red}{red})
-
-%\begin{MyColorPar}{red}
-
-"We utilized other approaches to validate our candidates.
-
-\subsubsubsection*{Analysis by web-tools}
-
-%\subsubsection*{SurvExpress} % TCGA
-% 2021/01/23 pdf x 12 from SurvExpress
-SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
-Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier P-value) shows in 12 genes:\\ % SurvExpress 有類似的結果:
-1) poor prognosis: DKK1 (0.00005), CAMK2N1 (0.000006), STC2 (0.001), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008), STIP1 (0.001), DKC1 (0.01);
-%CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-2) better prognosis: ZNF557 (0.0007), ZNF266 (0.00008), FCGBP (0.001).
-%IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
-%17 out of 20 candidates
-%?DKK1 (0.253635),
-The 12 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using SurvExpress with the TCGA cohort.
-Please see Supplementary Figure S1.
-%\ref{fig:fig_SurvExpress}.
-% moved to supplementary file
-
-% % SurvExpress 沒有類似的結果是因為:
-Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
-Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
-%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
-
-%\subsubsection{HPA} %still TCGA's RNA-Seq
-The Human Protein Atlas project (HPA) Proteome analysis is based on26941 antibodies targeting 17165 unique proteins.
-The HPA's Pathology Atlas analyzes each protein in patients, using immunohistochemistry (IHC) analysis based on tissue microarrays (TMAs) adopted from TCGA.
-Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
-All transcriptomics data has been retrieved from the Cancer Genome Atlas, and all proteomics data has been generated in-house using the same antibodies.
-Our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/\\pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
-The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level((HPA database, available at https://www.proteinatlas.org/\\ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset 
-(Please see Supplementary Figure S2.) %\ref{fig:fig_HPA_USP10})
-% moved to Supplementary
-
-% Version: 3.0.2 Date: 2015/06/11 SurvNet
-%Preloaded TCGA  data is also available for analysis.
-%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
-%gene regulatory or protein interaction network
-% cited by 10 articles
-% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
-% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
-%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
-
-%\subsubsection*{GSE2837} % non-TCGA
-% from Anwser2-2
-%by GEO GSE2837 HNSCC dataset (PrognoScan)
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
-%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
-%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
-relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
-and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
-The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
-1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
-%17 out of 20 candidates
-%?DKK1 (0.253635), 
-Please see Supplementary Figure S3. %\ref{figure:fig_GSE2837}.
-Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
-%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
-%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
-%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
-
-\subsubsubsection*{Review articles}
-After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
-%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
-%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
-%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
-
-%%%%%% bad guy
-The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
-Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}. %quantitative real-time PCR and western blot analyses
-Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
-Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
-DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
-The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
-%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
-
-%STC2:
-The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}
-
-% PGK1
-Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R).
-The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.
-
-%SURF4
-Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
-) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression.
-SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
-%NIH/3T3 cells (Mus musculus, mouse), 293T cell
-%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
-%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
-%web-based tools survival (not TCGA?)
-
-% USP10 qPCR primer https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153
-Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
-Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
-https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
-
-%FOXA2
-Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
-FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
-%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
-%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
-% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
-%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
-Further, SIS analysis was performed to further screen out a stable probe combination.
-Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
-2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
-Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
-2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
-%Association between gene expression and methylation.
-Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
-Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
-
-% STIP1; non-TCGA
-Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
-in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. 
-The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
-%STIP1 could bind to bind Hsp70 and Hsp90.
-
-%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
-%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
-%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
-% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
-
-%%%%%% good guy
-%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
-%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
-%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
-%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
-
-%ZNF266, % or ZNF16, HZF1?
-%MYO1H associated mandibular prognathism\cite{Sun2018}
-
-% FCGBP
-% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
-Fc fragment of IgG binding protein (($Fc\gamma BP$, FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas.\cite{ODonovan2002}\cite{Griffith2006}
-%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
-%gene ID @gene@8857
-
-%?LOC148709?, 
-%EVPLL in cDNA project
-
-% PNMA5
-Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}
-
-%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
-GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
-
-%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
-(PMID31598163)
-%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
-The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
-Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
-%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
-%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
-%\cite{Li2018b}
-%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
-%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
-
-%NDFIP1:
-%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
-was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
-%MCF7 cells 
-%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
-%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
-%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
-Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
-We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
-hepatocellular carcinoma\cite{Zhang2019a}
-% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
-%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
-It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
-
-%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
-%DKC1 is the tumor suppressor gene in HNSCC
-% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
-
-The 9 out of 20 positive and negative prognostic genes underlined has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo."
-
-%\end{MyColorPar} % marked as red
-
-\pagebreak
-
-\end{MyColorPar}
-
-%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
-
-%After that, there are 18,082 cross-cancer type articles produced using the TCGA database.
-The 778 publications (Figure \ref{figure:fig_embase}, b.
-778) among them were focused on HNSCC research.
-Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time.
-Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008.
-%\ref{figure:fig_embase}
-\begin{figure}
-\raggedleft
-\includegraphics[width=14cm]{Answer_2-1.pdf}
-\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
-\label{figure:fig_embase}
-\end{figure}
-\clearpage
-%778/4350 = 17.9\% using TCGA data
-%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
-%http://www.actrec.gov.in/OCDB/index.htm
-
-Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
-GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.
-However, the MSKCC, Broad, and Johns Hopkins databases were processed through whole-exome sequencing instead of whole-genome sequencing in the TCGA database.
-
-There is several useful web-tools for survival analysis, such as cBioportal\cite{Cerami2012b}\cite{Gao2013a}, KM-Plotter\cite{Gyorffy2010},  SurvExpress\cite{Aguirre-Gamboa2013}, UALCAN (available at http://ualcan\\.path.uab.edu/)\cite{Chandrashekar2017a} and Gene Expression Profiling Interactive Analysis (GEPIA, GEPIA2)\cite{Tang2019}.
-According to the citing articles\cite{Wu2020} and their online documents, the back-end databases of those web-tools were collected from TCGA, the European Genome-phenome Archive (EGA)\cite{Lappalainen2015} and NCBI GEO datasets (available at https://www.ncbi.nlm.nih.gov/gds).
-Furthermore, almost all of their survival data came from the TCGA database.
-%GEO (few survival features, less than 100 participate in each GSE dataset)
-%GSE31056, GSE2837 (Prognoscan)
-%there is survival feature: A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
-%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).\cite{Lawrence2015a}
-%datasets for each cancer type that include exactly the same prediction and outcome variables and consider comparable target populations. Currently, such data is simply not available.
-
-%The Dickkopf1 (DKK1) gene encodes a protein that was mainly involved in Wnt and other signaling pathways.
-%Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
-%Pang et al\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
-%Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
-%DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
-%The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-
-For example, Wei et al.\cite{Wei2020} conducted the analysis of the prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a web-based tool that plots expression profiles of given genes (dataset from TCGA database)
-They has suggested that overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC leading to the worst prognosis of the patients.
-%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-
-Conclusion: TCGA database is representative of HNSCC.
-
-\begin{figure}
-\raggedleft
-\includegraphics[width=14cm]{Answer_2-2.pdf}
-\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
-The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
-\label{figure:fig_GSE2837}
-\end{figure}
-\clearpage

### 2021-05-10 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
-{ 
-(ok)Result 改寫 CAMK2N1, IL19; 
+%%{
+(ok)Result altered to CAMK2N1, IL19; 
 Supplementary;
 Discussion:
-([ok] 3.2, 3.3 只留下 validated by GSE2837)
-(ok) Figure_4_CAMK2N1_IL19.pdf  KM plots
+([ok] 3.2, 3.3 remained validated by GSE2837)
+(ok) new Figure4.pdf  KM plots
 (ok)table 1 (6 genes), (ok) table 2 (4 genes)
 
-\resizebox{\linewidth}{!}{ % adjust table size to fit the page width
 Table 3: CAMK2N1 (ok)
 Table 4: IL19  (ok)
-\label
-}
 
@@
 four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
-}
+%%}
 
@@
 *** => a gene signature with deep learning CNN
-https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
-
-https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
+%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
+
+%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
 
@@
 \end{MyColorPar}
+
+Answer
 
@@
 
+Answer
+
 % 不要誇大說明 謙虛道歉
-=> We are apology for exaggerating the difficulties of our workflow.
+We are apology for exaggerating the difficulties of our workflow.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.
@@
 \1 including null expressed genes, over 50\% of the cohort, 
-\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 -> 20500).
-{
-[main_marginSFP_HNSCC.R] line 1361
-=> osccT_2021 <- osccT[c(30,31)] # [30] "days_to_last_followup", [31] "days_to_last_known_alive" 
-OS_live_days /30 # derived from last followup [30]/ last known alive [31])
-event (alive) => censored (status 0) # to handle missing data of censored by OS_months imputation
+\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 to 20500).
+%
+
+%[main\_marginSFP\_HNSCC.R] line 1361
+osccT_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
+OS\_live_days /30 % derived from last followup [30]/ last known alive [31])
+event (alive) to censored (status 0) % to handle missing data of censored by OS_months imputation
 R help from Jorge I Velez
 [line 1654]
-=> gene correction (20499 -> 20500) from SLC35E2A to 2 genes:
-# SLC35E2A: 9906
-# SLC35E2B: 728661
-}
+for gene correction (20499 to 20500) from SLC35E2A to 2 genes:
+% SLC35E2A: 9906
+% SLC35E2B: 728661
 \end{outline}

### 2021-05-10 main.tex
Updates from Overleaf

@@
 $^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip, 
-    Taipei Municipal Wanfang Hospital\unskip, Taipei\unskip, Taiwan\\
+%    Taipei Municipal Wanfang Hospital\unskip, Taipei\unskip, Taiwan\\
+Wan Fang Hospital\unskip, Taipei Medical University\\
 
 $^{3}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
-    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
+    Taipei Medical University Hospital\unskip, Taipei Medical University\\
 
@@
     Academia Sinica\unskip, Taipei\unskip, Taiwan\\
-$^{5}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
+
+$^{5}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip,
+No.172-1, Sec. 2, Keelung Rd.\unskip, Taipei 106\unskip, Taiwan\\
+%Taipei\unskip, Taiwan\\
 }

### 2021-05-10 Cover_letter_JPM.tex
Updates from Overleaf

@@
 We appreciate the reviewer for kind instruction of expression cutoff in detail.\\
-*We modified the workflow as ...
-
-We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
+***We modified the workflow as ...
+
+We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
@@
 % #####################
-\subsection*{2-4}
+\subsection*{2-4} % (ok)
 
@@
 %The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
-The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data.
-It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}.
+The Cox proportional-hazards model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
+It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
 % Classification trees and artificial neural networks in survival analysis
@@
 It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
-The ‘t’ in $h(t)$ indicates the hazard may vary over time
+The "t" in $h(t)$ indicates the hazard may vary over time
 \end{outline}
@@
 
-Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).
-
-In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+Univariate Cox proportional regression model, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival (OS) individually.
+
+In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+All covariates has been pool in the hazard function h(t) to estimate their impact on the overall survival.
 \end{MyColorPar}
@@
 
+% (ok)
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
@@
 We made a new Figure 1 with clear direction of the workflow.
-A "gene expression values (20500 genes)", instead of "RNAseq", indicates the expression data obtained from the TCGA.
+A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
 In Figure 2, the ticks and labels on the x-axis were corrected.
@@
 %\subsubsection{utility of TCGA} 
-%%%
+%%% how other researchers used TCGA to find expression biomarkers
 Usually, researchers used TCGA to find expression biomarkers...
-see https://www.biostars.org/p/153013/
+% reference https://www.biostars.org/p/153013/
 Tutorial: Survival analysis of TCGA patients
@@
 #gene expression correlates with worse survival or earlier tumor recurrence.
-#https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
-#from Mary Goldman and Jing Zhu, UCSC Cancer Browser
-#https://genome-cancer.ucsc.edu/
+% https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
+% from Mary Goldman and Jing Zhu, UCSC Cancer Browser
+% https://genome-cancer.ucsc.edu/
 %%%%%%%%%
@@
 % 不要誇大說明 謙虛道歉
-We are apology for exaggerating the difficulties of our workflow.
+We apologize for exaggerating the difficulties of our workflow.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.
@@
 %%%
-There are three steps of biomarker discovery from survival analysis.
-First, although \acrshort{tcga} genomics data was harmonized, there are 
-several points should be manually investigated and cleaned.
+There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.
+First, although \acrshort{tcga} genomics data has been harmonized, two things were found during our investigating and data cleaning:
 
 \begin{outline}
-\1 including null expressed genes, over 50\% of the cohort, 
-\1 After extended organizing, we found that the number of protein-coding genes in the TCGA RNA-Seq dataset should be corrected  (20499 to 20500).
+\1 null expressed genes over 50\% of the cohort have been excluded in the workflow
+\1 after extended organizing, the number of protein-coding genes in the  RNA-Seq dataset should be corrected  (from 20499 to 20500);
 %
-
+that is because of ...
 %[main\_marginSFP\_HNSCC.R] line 1361
@@
 
-Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+%Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
 
 % risk of 
-Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
-However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.
+Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy might identify more but weak "biomarkers". 
+Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
 

### 2021-05-10 main.tex
Updates from Overleaf

@@
 %The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
-
-The Cox proportional-hazards model\cite{Cox1972} is commonly used for modeling survival analysis data.
-It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (hazard) for them\cite{Bradburn2003b}.
+The Cox proportional-hazards model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
+It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
 % Classification trees and artificial neural networks in survival analysis
@@
 
-%Linear regression is useful as a concept in biomarker discovery.
-%A linear regression equation that relates a Y-variable to n X-variables is written as\\[1cm]
-%\par
 %Highlights
@@
 
-%ground truth Y (e.x. patient's survival):\\[0.5cm]
 $h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
@@
 \end{flushleft}
-%Y$:
-%$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
-%\linebreak
-%\linebreak
 where,\\
@@
 It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
-The ‘t’ in $h(t)$ indicates the hazard may vary over time
+The "t" in $h(t)$ indicates the hazard may vary over time
 \end{outline}
 
-%Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
-%\\[0.5cm]
-%Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
-%A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
-%Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
-%$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
-%\linebreak
-%(predicted Y, output) intercept, slope, independent (input) \Times
-%\end{math}
 Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
 
-Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).
-
-In a multivariate test, those variables used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+Univariate Cox proportional regression model, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival (OS) individually.
+
+In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+All covariates has been pool in the hazard function h(t) to estimate their impact on the overall survival.
 \end{MyColorPar}

### 2021-05-14 Cover_letter_JPM.tex
lasso

@@
 
-% strategy should changing
+% strategy should changing; run GCP Rstudio? hard work to do
 In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01.
@@
 
+% dimension reduction? feature selection for further multivariate Cox modeling =>
+%Least absolute shrinkage and selection operator (LASSO) is a biased estimation tool for data with complex collinearity.
+It can select variables and estimate parameter simultaneously and better solve the multicollinearity problem in regression analysis [19].
+Thus, we used the LASSO Cox regression analysis to decrease the number of IRGPs by R package glmnet.
+
 In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
@@
 We appreciate the reviewer for the critical comments.
-*** => a gene signature with deep learning CNN
+***  a gene signature with deep learning CNN,
 %https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
@@
 %https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
+
+or
+Prognostic gene signature:\\ % https://www.hindawi.com/journals/jir/2020/5494858/
+
+The risk score for each HNSCC sample was calculated based on the IRGP prognostic signature using the following formula:\\[0.5cm]
+risk score = $expression_{gene1} \times \beta_{gene1} + expression_{gene2} \times \beta_{gene2} + ... + expression_{geneX} \times \beta_{geneX}$\\
+
+, in which $X$ was the number of IRGPs and $\beta$ was coefficient value for each IRGPs.
+Taking the median value of risk score as the threshold, we divided all the HCC samples into high-risk or low-risk groups.
+The accuracy and sensitivity of survival prediction based on the risk score were verified by receiver operating characteristic (ROC) curve analysis and determined by the value of area under the curve (AUC) in 1, 3, and 5 years.
+Kaplan–Meier (KM) survival curves analysis () was used to analyze the over survival (OS) of the high-risk and low-risk groups.
+We then integrated IRGPs with existing clinical and pathologic features for multivariate Cox regression analysis.
+Tumor TNM, stage, grade, age, and body mass index (BMI) were regarded as continuous variables.
+The association between IRGPs risk score, clinical, and pathologic features was determined by KM analysis.
+Prognostic risk models of tumor TNM, grade, age, and stage were constructed.
+Subsequently, a Cox proportional hazards regression model was constructed by combined the Tumor TNM, grade, age, stage, and risk scored.
+The R package rms was used to compare these models with the IRGP prognostic signature.
+Concordance index (C-index) was used to assess the accuracy of the prognostic biomarkers.
+Also, the comparison between IRGPs and clinical/pathologic features was performed by forest and nomogram plots to determine the effectiveness of the prognostic value.
+The statistical difference of IRGPs in the clinical/pathologic features was compared using the Kruskal–Wallis test.
+
+***Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these primitive biomarkers.
+In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.
 
@@
 Answer
-
+We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
@@
 \begin{MyColorPar}{red}
-%\subsubsection{utility of TCGA} 
+% EdgeR
+Some researchers\cite{Xu2021a} tried to find DEGs of gene expression data (without survival information) for HNSCC biomarker discovery.
+RNA-Seq data were downloaded from The Cancer Genome Atlas (TCGA) database or other GSE datasets (e.x. GSE30784: 167 OSCC samples and 45 normal controls) from the Gene Expression Omnibus. 
+We employed DAVID (https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function.
+The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was used to annotate the potential functions.
+%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
+and the protein-protein interaction (PPI) network was conducted to identify differentially expressed genes (DEGs) closely associated with HNSCC.
+the pathway enrichment analysis of DEGs was performed by DAVID, String, and Sytoscape software programs\cite{Huang2019}\cite{Shen2019}.
+The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score >0.9, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
+Moreover, genes with degree> = 25 were selected as hub genes.
+Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.
+
+..
+by integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
+The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
+GOfunctional annotation and KEGG pathway analyses were performed using the Database for Annotation, Visualization, and Integrated Discovery.
+Hub genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA) and the Human Protein Atlas (HPA) website.
+
+DEGs to hub: The 230 differentially expressed genes and 12 hub genes were subjected to functional and pathway enrichment analyses.
+Then hub genes for survival analyses.
+
+% Cox Risk Regression Establishment and Validation with lncRNA data
+OSCC samples were randomly divided into a training set and a validation set.
+Univariate Cox regression was used to select prognosis-associated genes (p < 0.05).
+Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
+establish a prognostic risk score model, and the penalty regularization parameter lambda (λ) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
+%https://glmnet.stanford.edu/articles/glmnet.html
+Lambda.min was identified to pick out the variables. According to these variables, a stepwise regression was performed to establish the Cox model. 
+%Least Absolute Shrinkage and Selection Operator (LASSO) cox regression model along with 10-fold cross-validation
+Finally, a validation set and Kaplan–Meier survival curves along with a logrank p test were applied to validate its accuracy.
+In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
+Biomarkers Screening and Validation
+The status and survival time of OSCC patients were extracted.
+Subsequently, the mRNA was enrolled in the PPI and ceRNA networks, and lncRNA and miRNA identified in ceRNA were selected for screening biomarkers.
+We used univariate Cox regression to screen prognostic factors (p < 0.05), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (p < 0.01) were selected as primitive biomarkers.
+Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these biomarkers.
+In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.
+
+%\subsubsection{from TCGA to expression biomarkers} 
 %%% how other researchers used TCGA to find expression biomarkers
@@
 % https://genome-cancer.ucsc.edu/
+
 %%%%%%%%%
@@
 There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.
-First, although \acrshort{tcga} genomics data has been harmonized, two things were found during our investigating and data cleaning:
+First, although \acrshort{tcga} genomics data has been harmonized, 
+%two things were found during our investigating and data cleaning:
+the preprocessing of TCGA RNA-Seq is as follows:
 
 \begin{outline}
-\1 null expressed genes over 50\% of the cohort have been excluded in the workflow
-\1 after extended organizing, the number of protein-coding genes in the  RNA-Seq dataset should be corrected  (from 20499 to 20500);
+\1 HNSCC samples without complete clinical information have been removed;
+\1 null expressed genes in more than half of the HNSCC samples have been excluded;
+\1 after extended organizing, the number of protein-coding genes in the  RNA-Seq dataset should be updated from 20499 to 20500;
 %

### 2021-05-14 main.tex
lasso

@@
 \begin{MyColorPar}{red}
-\subsubsection{utility of TCGA}
-%%%
-Usually, how researchers used TCGA to find expression biomarkers
-%%%%%%
-\end{MyColorPar}
-
-%%% ***
-In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
-\begin{MyColorPar}{red} %%%
-There are three steps of biomarker discovery from survival analysis.
-First, although \acrshort{tcga} genomics data was harmonized, there is unclean data, including null expressed genes, over 50\% of the cohort, should be manually investigated and cleaned.
-%%% *** with more
-Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
-\end{MyColorPar} %%%
-Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type.
+\subsubsection{From TCGA to expression biomarkers}
+%%% https://www.biostars.org/p/153013/
+%% download data with offline analysis
+Usually, investigators could download the TCGA data in order to analyze and find expression biomarkers.
+A number of genes of interested could be differentially expressed between tumor samples obtained from those patients with better/worse survival of HNSCC.
+A brief overview of steps:
+\begin{outlin}
+\1 obtain the data (RNA-Seq and clinicopathological data): go to FireBrowse (firebrowse.org) or FireHose (http://gdac.broadinstitute.org/), select "Clinical" and "mRNASeq" data of \acrfull{hnscc}
+\1 prepare the data for the analysis
+\1 run the analysis under the R package "survival", and interpret the results
+\end{outlin}
+
+%%%%%% web-based tools
+%Usually, 
+The other investigators should get the rationale or revelation of the genes of interest on a specific cancer type.
 They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
@@
 It is not possible to scan the whole human protein-coding genome in this way.
+The web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
+There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
+packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
+
+\end{MyColorPar}
+
+%%% ***
+In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
+\begin{MyColorPar}{red} %%%
+There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.
+First, although \acrshort{tcga} genomics data has been harmonized, two things were found during our investigating and data cleaning:
+
+\begin{outline}
+\1 null expressed genes over 50\% of the cohort have been excluded in the workflow
+\1 after extended organizing, the number of protein-coding genes in the  RNA-Seq dataset should be corrected  (from 20499 to 20500);
+%
+that is because of ...
+%[main\_marginSFP\_HNSCC.R] line 1361
+osccT_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
+OS\_live_days /30 % derived from last followup [30]/ last known alive [31])
+event (alive) to censored (status 0) % to handle missing data of censored by OS_months imputation
+R help from Jorge I Velez
+[line 1654]
+for gene correction (20499 to 20500) from SLC35E2A to 2 genes:
+% SLC35E2A: 9906
+% SLC35E2B: 728661
+\end{outline}
+%Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+
+%Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+\end{MyColorPar} %%%
+
 \begin{MyColorPar}{red} %%% %%%
 % risk of 
-Third, we try to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage.
-However, this strategy might identify more weak "biomarkers". Thus, the false positives and adjustment of multiple comparison should be corrected by \acrfull{fdr}.
+Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy might identify more but weak "biomarkers". 
+Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
 %Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. 
@@
 \end{MyColorPar} %%%
-The above mentioned web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
-There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
-packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
 

### 2021-06-03 Cover_letter_JPM.tex
Updates from Overleaf

@@
 % https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f
+
+\usepackage[bf]{caption}
+\newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
 
@@
 We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript.
-The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
+The detailed point-by-point answer to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}).
 Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
@@
 We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
+2) Since that revision, we added holistic cancer care in the discussion section (please see Answer 1-2).% \ref{page:1-2}).
 
 %%{
-(ok)Result altered to CAMK2N1, IL19; 
-Supplementary;
-Discussion:
-([ok] 3.2, 3.3 remained validated by GSE2837)
-(ok) new Figure4.pdf  KM plots
-(ok)table 1 (6 genes), (ok) table 2 (4 genes)
-
-Table 3: CAMK2N1 (ok)
-Table 4: IL19  (ok)
-
-six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
-four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
+%(ok)Result altered to CAMK2N1, IL19; 
+%Supplementary;
+%Discussion:
+%([ok] 3.2, 3.3 remained validated by GSE2837)
+%(ok) new Figure4.pdf  KM plots
+%(ok)table 1 (6 genes), (ok) table 2 (4 genes)
+
+%Table 3: CAMK2N1 (ok)
+%Table 4: IL19  (ok)
+
+%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
+%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
 %%}
 
-2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).
 \end{MyColorPar}
@@
 \subsection*{1-2}
+\label{page:1-2}
 %
@@
 
-One day in February 2021, after meditation in the morning, the first author (Dr.
+After morning meditation in a wonderful day of February 2021,, the first author (Dr.
 Chi) has raised this idea then wrote it in discussion section with comprehensive references.
 Dr.
-Chi want to say "Stress is also be a kind of biomarker of HNSCC in the future study".
+Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
 We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.
@@
 Also, it was shown here in the following paragraph.
+
 \begin{MyColorPar}{red}
+"%discussion: the third limitation
+There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
+such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
+However, the TCGA did not collect other features related to holistic care.
+% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
+Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
+These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
+Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
+Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases.
+They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
+Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
+The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
 "
-"
+
+%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
+%「把自己當藥方開出去」
+
+%Moreover, long-term stress could be correlated with cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021},
+%and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}.(see Figure \ref{fig:figure5}) %HNSCC
+%dverse psychosocial experiences in early life, such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased risk of diabetes, heart disease, cancers, and psychiatric illnesses.
+%The possible molecular mechanisms could be also related with the mind-brain-body axis\cite{Berens2017}.
+%Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}
+
+% make Figure 5 holistic: Figure_5_holisticCare.pdf
+%\begin{figure}[hp]
+%...
+%\end{figure}
+%meridian and emotion has mutual reaction
+%meridian effect tissue and organ
+%(autonomic nerve system, myofascial network, prefrontal cortex)
+%placebo-effect influence on drug discovery
+%gene expression in deep learning
+%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
+%慈悲心 利他心
+%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
+%#正念 除了可以減壓，還可以治癒疼痛
+% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
+
 \end{MyColorPar} %red
 \end{MyColorPar} % blue
+
 %Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation),
@@
 % strategy should changing; run GCP Rstudio? hard work to do
-In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01.
+In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$.
 Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable.
@@
 %The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
+"
 The Cox proportional-hazards model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
@@
 All covariates has been pool in the hazard function h(t) to estimate their impact on the overall survival.
+"
 \end{MyColorPar}
@@
 \subsection*{2-6}
-[Minor comments]
+\subsubsection*{[Minor comments]}
 The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
@@
 A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
-In Figure 2, the ticks and labels on the x-axis were corrected.
+In Figure 2, the ticks and labels on the x-axis were corrected.\\[0.5cm]
 
@@
 \begin{MyColorPar}{black} % minor comment
-***More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
+\subsubsection*{[Minor comments]}
+
+More introduction to how other researchers used TCGA to find expression biomarkers should be presented in the Introduction section.
 \end{MyColorPar}
@@
 We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised.
+Also, it was shown here in the following paragraph.\\[0.3cm]
 
@@
 % EdgeR
+"
 Some researchers\cite{Xu2021a} tried to find DEGs of gene expression data (without survival information) for HNSCC biomarker discovery.
 RNA-Seq data were downloaded from The Cancer Genome Atlas (TCGA) database or other GSE datasets (e.x. GSE30784: 167 OSCC samples and 45 normal controls) from the Gene Expression Omnibus. 
-We employed DAVID (https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function.
+They employed DAVID (https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function. 
 The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was used to annotate the potential functions.
 %Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
-and the protein-protein interaction (PPI) network was conducted to identify differentially expressed genes (DEGs) closely associated with HNSCC.
-the pathway enrichment analysis of DEGs was performed by DAVID, String, and Sytoscape software programs\cite{Huang2019}\cite{Shen2019}.
-The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score >0.9, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
-Moreover, genes with degree> = 25 were selected as hub genes.
+The protein-protein interaction (PPI) network was conducted to identify differentially expressed genes (DEGs) closely associated with HNSCC.
+The pathway enrichment analysis of DEGs was performed by DAVID, String, and Sytoscape software programs\cite{Huang2019}\cite{Shen2019}.
+The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
+Moreover, genes with degree $>= 25$ were selected as hub genes.
 Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.
 
-..
-by integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
+By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
 The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
@@
 % Cox Risk Regression Establishment and Validation with lncRNA data
-OSCC samples were randomly divided into a training set and a validation set.
-Univariate Cox regression was used to select prognosis-associated genes (p < 0.05).
+HNSCC samples were randomly divided into a training set and a validation set.
+Univariate Cox regression was used to select prognosis-associated genes (\textit{p} value $< 0.05$).
 Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
-establish a prognostic risk score model, and the penalty regularization parameter lambda (λ) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
+establish a prognostic risk score model, and the penalty regularization parameter lambda ($\lambda$) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
 %https://glmnet.stanford.edu/articles/glmnet.html
@@
 Biomarkers Screening and Validation
-The status and survival time of OSCC patients were extracted.
+The status and survival time of HNSCC patients were extracted.
 Subsequently, the mRNA was enrolled in the PPI and ceRNA networks, and lncRNA and miRNA identified in ceRNA were selected for screening biomarkers.
-We used univariate Cox regression to screen prognostic factors (p < 0.05), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (p < 0.01) were selected as primitive biomarkers.
-Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these biomarkers.
-In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.
+We used univariate Cox regression to screen prognostic factors (p $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{p} value < 0.01) were selected as primitive biomarkers.
+Ultimately, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.
+In addition, a combination of two or more biomarkers was performed to predict HNSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.
 
@@
 %%% how other researchers used TCGA to find expression biomarkers
-Usually, researchers used TCGA to find expression biomarkers...
+Usually, researchers used TCGA to find expression biomarkers:\\
 % reference https://www.biostars.org/p/153013/
@@
 % https://genome-cancer.ucsc.edu/
+"
 
@@
 
+\begin{MyColorPar}{black} % minor comment
+\subsubsection*{[Minor comments]}
 %%%***[latex line 410]
-\begin{MyColorPar}{black} % minor comment
+
 In line 154 paragraph, what does "unclean data" mean, missing values or zero expression? 
-The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.
+The three challenges are not "challenges" at all. The authors exaggerated the difficulties here.\\[0.3cm]
 \end{MyColorPar}
@@
 There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.
+
 First, although \acrshort{tcga} genomics data has been harmonized, 
@@
 \1 HNSCC samples without complete clinical information have been removed;
-\1 null expressed genes in more than half of the HNSCC samples have been excluded;
-\1 after extended organizing, the number of protein-coding genes in the  RNA-Seq dataset should be updated from 20499 to 20500;
+
+\1 Null expressed genes in more than 30\% or 50\% of the HNSCC samples have been excluded;
+
+\1 After investigation of mRNA expression dataset, the number of protein-coding genes in the TCGA HNSCC should be updated as 20500 (instead of 20499);
 %
-that is because of ...
-%[main\_marginSFP\_HNSCC.R] line 1361
-osccT_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
-OS\_live_days /30 % derived from last followup [30]/ last known alive [31])
-event (alive) to censored (status 0) % to handle missing data of censored by OS_months imputation
-R help from Jorge I Velez
-[line 1654]
-for gene correction (20499 to 20500) from SLC35E2A to 2 genes:
-% SLC35E2A: 9906
-% SLC35E2B: 728661
+we found that different expression value of gene SLC35E2.
+% [line 1549]
+%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
+%[line 1654]
+%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
+According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities in TCGA HNSCC dataset.
+% updated on 18-May-2021
 \end{outline}

### 2021-06-03 main.tex
Updates from Overleaf

@@
 \acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
-The tables were generated by latex code with the help from https://github.com/JDMCreator/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
+The tables were generated by latex code with the help from https://www.tablesgenerator.com/latex_tables# and https://github.com/JDMCreator/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
 We like to thank Dr. Wen-Chang Wang,

### 2021-06-04 Cover_letter_JPM.tex
Updates from Overleaf

@@
 *the authors should look for more data to verify these biomarkers.
-???
+by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
+or CPTAC (digital TMA, not HPA)
+or more GEO datasets (GEO2837, GSE40774, GSE65858, GSE148944)
 
@@
 %for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
+NCBI Reference Sequences (RefSeq)
 According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities in TCGA HNSCC dataset.
+% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
+% keyword: (SLC35E2) AND "Homo sapiens" 
+SLC35E2 is the previous symbols of SLC35E2A (Ref: https://www.genenames.org/data/gene-symbol-report/#!/hgnc_id/HGNC:20863).
+We made reassignment of the expression value as SLC35E2A and SLC35E2B. % according to what?
 % updated on 18-May-2021
@@
 Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
+And further validation of those candidate is required in the other independent dataset.% in larger patient populations.
+%warrant.
 

### 2021-06-05 Cover_letter_JPM.tex
minor3 done

@@
 
-\1 After investigation of mRNA expression dataset, the number of protein-coding genes in the TCGA HNSCC should be updated as 20500 (instead of 20499);
-%
-we found that different expression value of gene SLC35E2.
+\1 After investigation of mRNA expression dataset obtained through Firehose API, we found that gene ID (9906), gene ID (728661), and their expression values were saved together under the entity of gene symbol "SLC35E2".
+The expression file of SLC35E2 has almost double size than those of SLC35E1 or SLC35E3.
 % [line 1549]
@@
 %for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
-NCBI Reference Sequences (RefSeq)
-According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities in TCGA HNSCC dataset.
+%NCBI Reference Sequences (RefSeq)
+According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
 % https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
 % keyword: (SLC35E2) AND "Homo sapiens" 
-SLC35E2 is the previous symbols of SLC35E2A (Ref: https://www.genenames.org/data/gene-symbol-report/#!/hgnc_id/HGNC:20863).
-We made reassignment of the expression value as SLC35E2A and SLC35E2B. % according to what?
+SLC35E2 is the previous symbol of SLC35E2A (Ref: https://www.genenames.org/data/gene-symbol-report/#!/hgnc_id/HGNC:20863).
+Thus, we made reassignment of the expression value as SLC35E2A and SLC35E2B, and updated the number of protein-coding genes in the TCGA HNSCC as 20500.
 % updated on 18-May-2021

### 2021-06-06 Cover_letter_JPM.tex
2-6 minor2 done

--- 2021-06-03 Cover_letter_JPM.tex
@@
 %\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
+\newacronym{degs}{DEGs}{differentially expressed genes}
+
 \newacronym{fdr}{FDR}{false discovery rate}
@@
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
-***調整 workfow 更加嚴格以增加 validation rate
+***調整 workflow 更加嚴格以增加 validation rate
+Validation rate: 
+FDR for Cutoff mining: 先偷看答案 2837
+重新挑選 candidate (from Cox) 多選一些、偷偷看答案(GSE2837)
+
+%{
+six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
+four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
+%}
+
+Validation by:
+TCIA CPTAC (not HPA 抗體很少）
+
+This collection contains subjects from the National Cancer Institute’s Clinical Proteomic Tumor Analysis Consortium Head-and-Neck cancer (CPTAC-HNSCC) cohort.
+
+https://wiki.cancerimagingarchive.net/display/Public/CPTAC-HNSCC
+As digital tissue microarray?
+
+===
+For validation by GEO datasets:
 *The p-values are affected by the sample size, which has be described in the main text.
-as following:
-
+
+GEOquery: SOFT file (or MINiML) %https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
 *the authors should look for more data to verify these biomarkers.
-???
+by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
+or CPTAC (digital TMA, not HPA)i
+
+or more GEO datasets (GEO2837, GSE40774, GSE65858, GSE148944, and GSE41613/xGSE42743)i
+**  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
+*** \cite{Zhao2018} used GSE41613 (with survival data of 97 HNSCC cohort) for DEGs.
+GEO2R: GSE41613 and GSE42743 has only 131 genes of the Affymetrix array data % https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE41613
+from 97 HPV-negative OSCC patients %on the 131 gene 
+to identify a model for prediction of OSCC-specific survival\cite{Lohavanichbutr2013}.
+
+as following: % search by StarGEO
+StarGEO http://stargeo.org/ searching: HNSCC + survival (n>100]
+GSE 2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837
+
+and more
+https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE40774
+n=134; Agilent-026652 Whole Human Genome Microarray 4x44K v2 (Probe Name version)
+supplementary data:
+https://clincancerres.aacrjournals.org/content/21/4/870.figures-only#fig-data-additional-files
+# Version info: R 3.2.3, Biobase 2.30.0, GEOquery 2.40.0, limma getGEO("GSE40774", GSEMatrix =TRUE, cex=1.5)library("maptools")
+
+https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858GSE65858
+https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
+
+https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE148944
+   784 probes (gene）
+n=40; 110 FFPE samples were collected from a retrospective cohort of 67 OTSCC patients and 10 non-cancerous tongue samples.
+Targets including CD4, CD8, FOXP3, PD-L1 and PD-1 were analyzed by immunohistochemistry.
+The Nanostring PanCancer Immune Profiling Panel was used for gene expression profiling.
+Data were externally validated in the TCGA head and neck (HNSCC), melanoma and lung squamous cell carcinoma (LSCC) cohorts.
+GPL28285
+NanoString nCounter PanCancer Immune Profiling Panel
+
+https://onlinelibrary.wiley.com/doi/full/10.1002/cam4.3106
+.................
+
+% *** how to do? ROC
+% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
+In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
 
@@
 \subsection*{2-5}
-
+% gene signature
 Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
@@
 ***  a gene signature with deep learning CNN,
+or http://gepia2.cancer-pku.cn/#index
 %https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
-
 %https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
-
 or 
+Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
+To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.
+
+or \cite{Zhao2018}
 Prognostic gene signature:\\ % https://www.hindawi.com/journals/jir/2020/5494858/
@@
 
-% (ok)
+% (ok) minor comments1
 We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
@@
 %%
-\begin{MyColorPar}{black} % minor comment
+\begin{MyColorPar}{black} % minor comment2
 \subsubsection*{[Minor comments]}
@@
 Answer
-We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction.
+
+We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction section.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised.
@@
 \begin{MyColorPar}{red}
+
 % EdgeR
+% GEPIA2: most differential survival gene = pvalueTex
 "
-Some researchers\cite{Xu2021a} tried to find DEGs of gene expression data (without survival information) for HNSCC biomarker discovery.
-RNA-Seq data were downloaded from The Cancer Genome Atlas (TCGA) database or other GSE datasets (e.x. GSE30784: 167 OSCC samples and 45 normal controls) from the Gene Expression Omnibus. 
-They employed DAVID (https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function. 
-The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was used to annotate the potential functions.
-%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
-The protein-protein interaction (PPI) network was conducted to identify differentially expressed genes (DEGs) closely associated with HNSCC.
-The pathway enrichment analysis of DEGs was performed by DAVID, String, and Sytoscape software programs\cite{Huang2019}\cite{Shen2019}.
-The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
-Moreover, genes with degree $>= 25$ were selected as hub genes.
-Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.
-
-By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
-The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
-GOfunctional annotation and KEGG pathway analyses were performed using the Database for Annotation, Visualization, and Integrated Discovery.
-Hub genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA) and the Human Protein Atlas (HPA) website.
-
-DEGs to hub: The 230 differentially expressed genes and 12 hub genes were subjected to functional and pathway enrichment analyses.
-Then hub genes for survival analyses.
-
-% Cox Risk Regression Establishment and Validation with lncRNA data
-HNSCC samples were randomly divided into a training set and a validation set.
-Univariate Cox regression was used to select prognosis-associated genes (\textit{p} value $< 0.05$).
-Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
-establish a prognostic risk score model, and the penalty regularization parameter lambda ($\lambda$) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
-%https://glmnet.stanford.edu/articles/glmnet.html
-Lambda.min was identified to pick out the variables. According to these variables, a stepwise regression was performed to establish the Cox model. 
-%Least Absolute Shrinkage and Selection Operator (LASSO) cox regression model along with 10-fold cross-validation
-Finally, a validation set and Kaplan–Meier survival curves along with a logrank p test were applied to validate its accuracy.
-In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
-Biomarkers Screening and Validation
-The status and survival time of HNSCC patients were extracted.
-Subsequently, the mRNA was enrolled in the PPI and ceRNA networks, and lncRNA and miRNA identified in ceRNA were selected for screening biomarkers.
-We used univariate Cox regression to screen prognostic factors (p $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{p} value < 0.01) were selected as primitive biomarkers.
-Ultimately, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.
-In addition, a combination of two or more biomarkers was performed to predict HNSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.
-
 %\subsubsection{from TCGA to expression biomarkers} 
 %%% how other researchers used TCGA to find expression biomarkers
-Usually, researchers used TCGA to find expression biomarkers:\\
+Usually, researchers developed in-house workflow of gene expression analysis to find HNSCC biomarkers.
+%Workflow of GDCRNATool
 % reference https://www.biostars.org/p/153013/
-Tutorial: Survival analysis of TCGA patients
-#integrating gene expression (RNASeq) data Why would you want to do survival
-#analysis based on gene expression data? Well, let's say you have a number of
-#genes that you are interested in and they are differentially expressed between
-#tumor and normal samples, it would be very powerful to show that alteration in
-#gene expression correlates with worse survival or earlier tumor recurrence.
+%Tutorial: Survival analysis of TCGA patients
+%integrating gene expression (RNASeq) data.
+%Why would you want to do survival analysis based on gene expression data? Well, let's say you
+% **** DEGs is a different concept with cutoff finding survival analysis of individual gene expression
+They have a number of genes that are differentially expressed between tumor and normal samples.
+It would be useful to show that alteration in gene expression correlates with phenotypes of HNSCC.
 % https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
@@
 % https://genome-cancer.ucsc.edu/
+%Here are the summarized techniques currently used: from 2000 to 2017\cite{Tonella2017a}
+%Gene expression profiling is applied for HNSCC to help in early diagnosis, prediction of recurrence or metastasis, prediction of prognosis or response to some therapies.
+% Rstudio\cite{Loraine2015a}
+Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
+Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.x. GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
+% IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
+%e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
+They employed the Database for Annotation, Visualization and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function.
+The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.
+%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
+The protein-protein interaction (PPI) network was conducted by STRING (availalbe at https://string-db.org).
+The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
+Li\cite{Li2018a} and his colleagues made a R package (GDCRNATool) for the implementation of those workflow on gene expression analyses of the TCGA.
+%The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
+Moreover, genes with degree $>= 25$ were selected as hub genes.
+Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.
+%a validation set and
+%Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
+Xu and his collegues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{p} value $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{p} value $< 0.01$) were selected as primitive biomarkers.
+%By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
+The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
+The candidate genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
+%, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
+), GEPIA2021\cite{Li2021} (available at http://\\gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
+% GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
+% GEPIA1/2 contact us: tangzefang@pku.edu.cn
+Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\
+
+%DEGs to hub: The 230 differentially expressed genes and 12 hub genes were subjected to functional and pathway enrichment analyses. Then hub genes for survival analyses.
+
+% Cox Risk Regression Establishment and Validation with lncRNA data
+%HNSCC samples were randomly divided into a training set and a validation set.
+Univariate Cox regression was used to select prognosis-associated genes (\textit{p} value $< 0.05$).
+Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
+%establish a prognostic risk score model, and the penalty regularization parameter lambda ($\lambda$) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21).
+%https://glmnet.stanford.edu/articles/glmnet.html
+%Lambda.min was identified to pick out the variables. According to these variables, a stepwise regression was performed to establish the Cox model. 
+%Least Absolute Shrinkage and Selection Operator (LASSO) cox regression model along with 10-fold cross-validation
+
+%Biomarkers Screening and Validation
+%The status and survival time of HNSCC patients were extracted.
+Subsequently, the mRNA was enrolled in the PPI and ceRNA networks, and lncRNA and miRNA identified in ceRNA were selected for screening biomarkers.
+
+%
 "
@@
 
-\begin{MyColorPar}{black} % minor comment
+% ok
+\begin{MyColorPar}{black} % minor comment3
 \subsubsection*{[Minor comments]}
@@
 \begin{outline}
-\1 HNSCC samples without complete clinical information have been removed;
-
-\1 Null expressed genes in more than 30\% or 50\% of the HNSCC samples have been excluded;
-
-\1 After investigation of mRNA expression dataset, the number of protein-coding genes in the TCGA HNSCC should be updated as 20500 (instead of 20499);
-%
-we found that different expression value of gene SLC35E2.
+\1 HNSCC samples without complete clinical information have been removed;\\
+% or 50\%
+\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded;\\
+
+\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.\\
+After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that gene ID (9906), gene ID (728661), and their expression values were saved together under the entity of gene symbol "SLC35E2".
+The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
+% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
 % [line 1549]
@@
 %for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
-According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities in TCGA HNSCC dataset.
+%NCBI Reference Sequences (RefSeq)
+According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
+% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
+% keyword: (SLC35E2) AND "Homo sapiens" 
+SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!\\/hgnc\_id/HGNC:20863).
+Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B, and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
 % updated on 18-May-2021

### 2021-06-06 main.tex
2-6 minor2 done

@@
 \makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
+
+\newacronym{degs}{DEGs}{differentially expressed genes}
 
@@
 A brief overview of steps:
-\begin{outlin}
+\begin{outline}
 \1 obtain the data (RNA-Seq and clinicopathological data): go to FireBrowse (firebrowse.org) or FireHose (http://gdac.broadinstitute.org/), select "Clinical" and "mRNASeq" data of \acrfull{hnscc}
@@
 \1 run the analysis under the R package "survival", and interpret the results
-\end{outlin}
+\end{outline}
 
@@
 The web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
-There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
+There are several visualization software or R packages which deal with cutoff determination\cite{Abel1984}, %CRITLEVEL
+such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
 packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.

### 2021-06-07 Cover_letter_JPM.tex
Updates from Overleaf
Answer 2-1 done (FDR)

@@
 %\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
+\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
 \newacronym{degs}{DEGs}{differentially expressed genes}
@@
 %\begin{MyColorPar}{blue}
+%(OK)
 First of all, please describe the difference between the two manuscripts.
@@
 Answer
-
+%(OK)
 We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.
@@
 \label{page:1-2}
-%
+% (OK)
 Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
@@
 Answer
-
+%(OK)
 After morning meditation in a wonderful day of February 2021,, the first author (Dr.
@@
 The authors tried to highlight their workflow and present it as a new tool, however, their workflow is very common, and I cannot see its novelty.
-The selection of gene expression cutoff is not well handled statistically (see below my first comment). 
+The selection of gene expression cutoff is not well handled statistically (see below my first comment). % FDR
 Therefore, I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them.
@@
 
-\subsection*{2-1}
-
+\subsection*{2-1}%(ok)
+% sliding window cutoff selection with FDR corrected
 Exploring all possible expression cutoffs is controversial. 
@@
 Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05).
-For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff.
-But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff.
+For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
+But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
 This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
 Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
+% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity
 
@@
 Answer
-
-We appreciate the reviewer for kind instruction of expression cutoff in detail.\\
-***We modified the workflow as ...
-
+%(ok)
+
+% 1) ***We modified the workflow as ...(本來就有計算 FDR and excluding >= 0.05)
+% 2) and FDR (done)
+We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
+% and give us this nomenclature as "sliding window"
+We correct our statement of this workflow (please see Answer 2-2).
+There is more evidence to validate them (please see Answer 2-3).
+
+%\begin{MyColorPar}{red}
+%\end{MyColorPar}
+
+% and FDR (done; ok)
 We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
+%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
+The caption of Figure 1, Table 1, and Table 2 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
@@
 \begin{MyColorPar}{red}
-The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
+% TCGA_HNSCC_marginSFP.R [line 111] cutoffReturn <- cutofFinder_func_HNSCC.R
+% retrieving optimized (minimal) p value of each Kaplan-Meier plot 
+% **A summary table of P-value, Z-score standardization from all HNSCC_survival*.Rda 
+% 不必每次重 run (saved at HNSCC_OS_marginS_pvalueKM_candidate_cox.Rda)
+% variable name: candidate_sample (with gene symbol and KM p value), candidate_cox, n_percent_Bonferroni
+%=> FDR() or p.adjust() The FDR function uses the Benjamini & Hochberg (\cite{Benjamini1995a}) ("BH", alias "fdr") correction by default.
+% analysis_export.R [line 197] has FDR < 0.05 for filtering (done)
+% [line 196] OS_pvalueS$p_value_adj_FDR <- p.adjust(OS_pvalue$p_OS, method='fdr')
+
+% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
+The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} has been be applied and shows which genes should be retained for further univariate and multivariate analysis.
+% of Cox modeling
+It is ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
 \end{MyColorPar}
@@
 \subsection*{2-2}
-
+%(OK)
 I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them.
@@
 Answer
-
+%(OK)
 We appreciate the reviewer for the critical comment.
-We changed title as "Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
-
-* more evidence to support or validate them
+We changed title as "Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
+There is more evidence to validate them (please see Answer 2-3).
 
@@
 \subsection*{2-3}
-
+% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity
 % strategy should changing; run GCP Rstudio? hard work to do
-In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$.
-Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable.
-The p-values are affected by the sample size, which should be described in the main text.
-As I mentioned above, the authors should look for more data to verify these biomarkers.
+In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1
+Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
+The p-values are affected by the sample size, which should be described in the main text. % writing
+As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO
 
@@
 
-We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
-***調整 workflow 更加嚴格以增加 validation rate
-Validation rate: 
-FDR for Cutoff mining: 先偷看答案 2837
-重新挑選 candidate (from Cox) 多選一些、偷偷看答案(GSE2837)
+% the validation rate
+% more GSE datasets
+% using  receiver operating characteristic (ROC) analysis and more GEO datasets
+We appreciate the reviewer for the critical comments and thanks for the agreement of our work in cancer research.
+
+%***調整 workflow 更加嚴格以增加 validation rate
+Validation rate:\\
+%重新挑選 candidate (from Cox) 多選一些、偷偷看答案(GSE2837 and GSE65858)
 
@@
 Validation by:
-TCIA CPTAC (not HPA 抗體很少）
+%TCIA CPTAC (not HPA 抗體很少）
 
 This collection contains subjects from the National Cancer Institute’s Clinical Proteomic Tumor Analysis Consortium Head-and-Neck cancer (CPTAC-HNSCC) cohort.
-
-https://wiki.cancerimagingarchive.net/display/Public/CPTAC-HNSCC
+%https://wiki.cancerimagingarchive.net/display/Public/CPTAC-HNSCC
 As digital tissue microarray?
 
-===
+%%%
 For validation by GEO datasets:
-*The p-values are affected by the sample size, which has be described in the main text.
-
-GEOquery: SOFT file (or MINiML) %https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
+
+% National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009)
+
+GEOquery\cite{Sean2007}: SOFT file (or MINiML)
+the NCBI GEO repositories
+%https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
 *the authors should look for more data to verify these biomarkers.
@@
 
-or more GEO datasets (GEO2837, GSE40774, GSE65858, GSE148944, and GSE41613/xGSE42743)i
+or more GEO datasets (*GEO2837, GSE40774, ***GSE65858, *GSE117973, GSE148944, and GSE41613/xGSE42743)
+* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837
+
+*** https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858 GSE65858
+https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
+OS event and RFS event and survival time
+n=270\cite{Wichmann2015}
+Each array on the HumanHT-12 v4 Expression BeadChip targets more than 31,000 annotated genes with more than 47,000 probes derived from the \acrfull{ncbi} Reference Sequence (RefSeq) Release 38 (November 7, 2009) and other sources.
+% https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GPL10558
+
 **  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
-*** \cite{Zhao2018} used GSE41613 (with survival data of 97 HNSCC cohort) for DEGs.
-GEO2R: GSE41613 and GSE42743 has only 131 genes of the Affymetrix array data % https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE41613
+PFS and DSS event and months
+
+*x* \cite{Zhao2018} used GSE41613 (with survival data of 97 HNSCC cohort) for DEGs.
+GEO2R: GSE41613 and GSE42743 可是*** has only 131 genes of the Affymetrix array data % https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE41613
 from 97 HPV-negative OSCC patients %on the 131 gene 
@@
 
-as following: % search by StarGEO
+x 7. Integration of molecular gene signatures with clinicopathological variables improves staging and outcome prediction of oral cancer.
+(Submitter supplied) The aim of this study is to identify and validate clinically implementable gene signatures for outcome prediction of patients with oral squamous cell carcinoma.
+Organism:	Homo sapiens
+Type:		Expression profiling by array
+Platform: GPL6480 99 Samples
+FTP download: GEO (TXT) ftp://ftp.ncbi.nlm.nih.gov/geo/series/GSE84nnn/GSE84846/
+Series		Accession: GSE84846	ID: 200084846
+only alive or death (no survival time) => Similarly preprocessed VUmc (GSE84846) and UMCU (GSE30788) microarray datasets (https://www.oncotarget.com/article/19576/text/)
+\cite{Mes2017}
+
+%as following: % search by StarGEO ===========
 StarGEO http://stargeo.org/ searching: HNSCC + survival (n>100]
-GSE 2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837
-
-and more
-https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE40774
+* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837
+
+x https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE40774
 n=134; Agilent-026652 Whole Human Genome Microarray 4x44K v2 (Probe Name version)
@@
 https://clincancerres.aacrjournals.org/content/21/4/870.figures-only#fig-data-additional-files
+n=134 (no survival)
 # Version info: R 3.2.3, Biobase 2.30.0, GEOquery 2.40.0, limma getGEO("GSE40774", GSEMatrix =TRUE, cex=1.5)library("maptools")
 
-https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858GSE65858
-https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
-
-https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE148944
+x https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE148944
    784 probes (gene）
@@
 Data were externally validated in the TCGA head and neck (HNSCC), melanoma and lung squamous cell carcinoma (LSCC) cohorts.
-GPL28285
-NanoString nCounter PanCancer Immune Profiling Panel
+GPL28285 NanoString nCounter PanCancer Immune Profiling Panel
 
@@
 In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
-
-\end{MyColorPar}
+%---
+
+We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+\\[0.3cm]
+
+\begin{MyColorPar}{red}
+validation rate
+...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size
+
+\end{MyColorPar} % red
+
+\end{MyColorPar} % blue
 
@@
 \subsection*{2-4} % (ok)
-
+%(OK)
 How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
@@
 Answer
-
+%(OK)
 We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
@@
 \subsection*{2-6}
+%(OK)
 \subsubsection*{[Minor comments]}
@@
 Answer
-
+%(OK x3)
 % (ok) minor comments1
@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his collegues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{p} value $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{p} value $< 0.01$) were selected as primitive biomarkers.
+Xu and his collegues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{P} value $< 0.01$) were selected as primitive biomarkers.
 %By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
@@
 %HNSCC samples were randomly divided into a training set and a validation set.
-Univariate Cox regression was used to select prognosis-associated genes (\textit{p} value $< 0.05$).
+Univariate Cox regression was used to select prognosis-associated genes (\textit{P} value $< 0.05$).
 Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
@@
 %for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
-%NCBI Reference Sequences (RefSeq)
+%NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
 According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
@@
 %by GEO GSE2837 HNSCC dataset (PrognoScan)
-We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
+We analysed GSE2837 dataset (\acrfull{ncbi} GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
 %??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/

### 2021-06-07 main.tex
Answer 2-1 done (FDR)

@@
 
+\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
 \newacronym{degs}{DEGs}{differentially expressed genes}
@@
 % Full title of the paper (Capitalized)
-\Title{Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+\Title{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
 %\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
@@
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+\TitleCitation{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
 %\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
@@
 then performing the survival analyses (within \textcolor{yellow}{yellow} square).
-The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of gene expression for subsequent Cox modeling.
+The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} value (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling.
 The candidate selection performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, based on the results from the survival analyses.
@@
 \centering
-\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }
+\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 \arrayrulecolor{black}\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
+\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier \acrshort{fdr}-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
 \hline
@@
 \centering
-\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }
+\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by corrected \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 \hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\ * Cox's model: \textit{P} value \textless{} 0.001\\lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier \acrshort{fdr}-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\ * Cox's model: \textit{P} value \textless{} 0.001\\lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
 \hline
@@
 %statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
-There were also multiple correlated tests of null hypotheses in the Kaplan-Meier family during our global scanning of protein-coding genes.
-The stringent Bonferroni correction could result in an adjusted \textit{P} value to ensure the control for type I error.
+There were also multiple correlated tests of null hypotheses 
+%in the Kaplan-Meier family 
+during our global scanning of 205,00 protein-coding genes. The stringent Bonferroni correction could result in an adjusted \textit{P} value to ensure the control for type I error. 
 %There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes.
@@
 \subsection{Biomarker Selection and Validation}
-
+% Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction 才對
 Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
@@
 Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
-we analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
+we analysed GSE2837 dataset (\acrfull{ncbi} GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
 %??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/

### 2021-06-08 Cover_letter_JPM.tex
go survival analysis of GSE65858

@@
 Once it is known that a gene is a strong biomarker (e.g., from a genome-wide test using fixed cutoffs), one can fine-tune the cutoffs utilizing this strategy.
+% percentage of genes using 50% cutoff in total 20500 genes
 
@@
 But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
-This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
+This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % => NOT weak 其實 very significant
 Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
@@
 % and give us this nomenclature as "sliding window"
+%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
 We correct our statement of this workflow (please see Answer 2-2).
@@
 \subsection*{2-3}
-% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity
-% strategy should changing; run GCP Rstudio? hard work to do
-In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1
+% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity (less biomarkers but more P value < 1e-5?)
+
+% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO validation
+In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
 Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
@@
 % the validation rate
-% more GSE datasets
+% more GSE datasets; pick-up more candidate (run GCP) in hands 而且要偷看答案
 % using  receiver operating characteristic (ROC) analysis and more GEO datasets
@@
 Validation rate:\\
-%重新挑選 candidate (from Cox) 多選一些、偷偷看答案(GSE2837 and GSE65858)
+%重新挑選 candidate (FDR100) 多選一些、偷偷看答案(GSE2837 and GSE65858)
 
@@
 Validation by:
+% SurvExpress http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp
+x Saintigny Mao Survival Oral cancer GSE26549 (n=86) with features of OSCC outcome (no time), Gender, Race, Alcohol, and Smoking.
+Petel Head and Neck Squamous Cell Carcinoma E-MTAB-1328 (n=89) RFS(metastasis) with time
+% https://www.ebi.ac.uk/arrayexpress/experiments/E-MTAB-1328/
+Chung Parker Head and Neck GSE10300 (n=44), RFS with time
+x Prognoscan (GSE2837) (n=30) 不行，太少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff
 %TCIA CPTAC (not HPA 抗體很少）

### 2021-06-08 main.tex
go survival analysis of GSE65858

@@
 then performing the survival analyses (within \textcolor{yellow}{yellow} square).
-The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} value (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling.
-The candidate selection performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, based on the results from the survival analyses.
+The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} values (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling.
+The candidate selection performs dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses.
 The selected genes will be validated by a independent HNSCC cohort (GSE2837).
@@
 \label{fig:figure1}
+% Description:1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
+
 \end{figure}
@@
 \cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\textit{P} value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\\textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
 \hline
@@
 \arrayrulecolor{black}\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier \acrshort{fdr}-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
+\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
 \hline
@@
 
-%\subsubsection{Table3/legend} or Table 2?
-%Table3. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
+%\subsubsection{Table3/legend} or Table 2
+%Table2. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
 \begin{table}[hp]
@@
 \cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
 \cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
@@
 \hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier \acrshort{fdr}-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\ * Cox's model: \textit{P} value \textless{} 0.001\\lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\
+%\hline
+%\multicolumn{9}{|l!{\color{black}\vrule}}{
+* Cox's model: \textit{P} $< 0.001$ \\
+%}                                                                                                                                                                                                                                                                                                                                                                                                  \\
+%\hline
+lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
 \hline
@@
 %\subsubsection{Table3/legend} Table 3
-%Table 2. Univariate/Multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in HNSCC.
+%Table 3. Univariate/Multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in HNSCC.
 %(P-value Significant codes is denoted as  0.01 mark as *; 0.001 mark as **; if $<$0.001  mark as ***)

### 2021-06-11 Cover_letter_JPM.tex
Updates from Overleaf

@@
 But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
-This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % => NOT weak 其實 very significant
+This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖
 Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
-% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity
+% (ok) PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity
 
@@
 
-% 1) ***We modified the workflow as ...(本來就有計算 FDR and excluding >= 0.05)
+% 1) 本來就有計算 FDR and excluding >= 0.05 (ok)
 % 2) and FDR (done)
@@
 There is more evidence to validate them (please see Answer 2-3).
+
+We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (p=0.05).
+*** According to our results, all of preliminary biomarkers have FDR-corrected \textit{P} values from 1e-4 to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see supplementary Figure SXXX).
+There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
+Thus we also performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.
 
@@
 
-% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO validation
+% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) validation
 In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
@@
 %%%
+*the authors should look for more data to verify these biomarkers.
 For validation by GEO datasets:
 
-% National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009)
-
-GEOquery\cite{Sean2007}: SOFT file (or MINiML)
-the NCBI GEO repositories
+% 
+National Center for Biotechnology Information Reference Sequence (NCBI) 
+%RefSeq Release 38 (November 7, 2009) 
+Gene Expression Omnibus (GEO)
+[Dataset]
+The NCBI GEO repositories is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
+R package of GEOquery\cite{Sean2007}: SOFT file (or MINiML) was used to
+download RNA-Seq dataset of HNSCC, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE65858). 
+GSE65858\cite{Wichmann2015} has OS event and RFS event and survival time.
+%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
+The expression data was generated using the HumanHT-12 v4 Expression BeadChip, which targets on more than 31,000 annotated genes (47,000 probes) derived from the \acrfull{ncbi} Reference Sequence (RefSeq) Release 38 (November 7, 2009).
+% an Affymetrix Human Genome U133A microarray (HG-U133A). 
+It was used as a validation dataset.
+
 %https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
-*the authors should look for more data to verify these biomarkers.
+
 by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
@@
 
-or more GEO datasets (*GEO2837, GSE40774, ***GSE65858, *GSE117973, GSE148944, and GSE41613/xGSE42743)
+or more GEO datasets (*GEO2837, GSE40774, ***GSE65858, **GSE117973, GSE148944, and GSE41613/xGSE42743)
 * GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837
@@
 https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
-OS event and RFS event and survival time
-n=270\cite{Wichmann2015}
-Each array on the HumanHT-12 v4 Expression BeadChip targets more than 31,000 annotated genes with more than 47,000 probes derived from the \acrfull{ncbi} Reference Sequence (RefSeq) Release 38 (November 7, 2009) and other sources.
 % https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GPL10558
@@
 
+***
+Third, dissection of ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) due to heterogeneity of 20500 RNA-Seq expression data files.
+
 \end{MyColorPar} % end of red

### 2021-06-12 Cover_letter_JPM.tex
Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf

@@
 
-%{
+*** Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]
+
+% [2021/06/11]決議;
+***  PvalueTex consensus with GSE2837 to yield 9 candidates
+% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
+x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
+%找出  9 candidates
+listed as
 six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
@@
 
-Validation by:
+We further
+validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data): 
+% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002      Gene.Symbol KM.Pvalue FDR.KMpvalue uni_HR   FDR.Pvalue
+1524     CAMK2N1   0.00687   0.03782500  1.814 1.628308e-05
+3967       FCGBP   0.01020   0.03886709  0.573 4.827833e-05
+5262        IL19   0.03390   0.04738901  0.630 6.543871e-06
+5264        IL19   0.00269   0.03068073  0.630 6.543871e-06
+
+CAMK2N1, IL19, and FCGBP
+%candidate_fdr100
+(please see Figure \ref{fig:hazards534}).
+
+%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
+% by Validation_GSE65858_survival.R
+% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
+
+\begin{figure}
+    \centering
+    \includegraphics[width=13cm]{Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf}
+    \bcaption{Validation cohort (GSE65858)}{
+    This HNSCC cohort has been applied for validation of our candidate genes: "CAMK2N1", "IL19" (two probes), and "FCGBP".
+    There are 270 HNSCC participants involved in this cohort.
+    The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30330.
+    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
+    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0;
+    \textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
+    The 22 gene symbol listed on the side: hazard ratio $> 1.8$ or $< 0.6$.\\
+    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);
+    Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
+    }
+    \label{fig:hazards534}
+\end{figure}
+
 % SurvExpress http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp
-x Saintigny Mao Survival Oral cancer GSE26549 (n=86) with features of OSCC outcome (no time), Gender, Race, Alcohol, and Smoking.
-Petel Head and Neck Squamous Cell Carcinoma E-MTAB-1328 (n=89) RFS(metastasis) with time
+%x Saintigny Mao Survival Oral cancer GSE26549 (n=86) with features of OSCC outcome (no time), Gender, Race, Alcohol, and Smoking.
+%Petel Head and Neck Squamous Cell Carcinoma E-MTAB-1328 (n=89) RFS(metastasis) with time
 % https://www.ebi.ac.uk/arrayexpress/experiments/E-MTAB-1328/
-Chung Parker Head and Neck GSE10300 (n=44), RFS with time
-x Prognoscan (GSE2837) (n=30) 不行，太少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff
+%Chung Parker Head and Neck GSE10300 (n=44), RFS with time
+
 %TCIA CPTAC (not HPA 抗體很少）
-
-This collection contains subjects from the National Cancer Institute’s Clinical Proteomic Tumor Analysis Consortium Head-and-Neck cancer (CPTAC-HNSCC) cohort.
+%This collection contains subjects from the National Cancer Institute’s Clinical Proteomic Tumor Analysis Consortium Head-and-Neck cancer (CPTAC-HNSCC) cohort.
 %https://wiki.cancerimagingarchive.net/display/Public/CPTAC-HNSCC
-As digital tissue microarray?
+%As digital tissue microarray?
 
@@
 
-% 
+[materials and methods]
 National Center for Biotechnology Information Reference Sequence (NCBI) 
@@
 % an Affymetrix Human Genome U133A microarray (HG-U133A). 
-It was used as a validation dataset.
-
-%https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
-
-by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
-or CPTAC (digital TMA, not HPA)i
-
-or more GEO datasets (*GEO2837, GSE40774, ***GSE65858, **GSE117973, GSE148944, and GSE41613/xGSE42743)
-* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837
-
-*** https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858 GSE65858
-https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
-% https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GPL10558
-
+It was used as a validation dataset. \\
+
+GSE117973
 **  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
-PFS and DSS event and months
-
-*x* \cite{Zhao2018} used GSE41613 (with survival data of 97 HNSCC cohort) for DEGs.
-GEO2R: GSE41613 and GSE42743 可是*** has only 131 genes of the Affymetrix array data % https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE41613
-from 97 HPV-negative OSCC patients %on the 131 gene 
-to identify a model for prediction of OSCC-specific survival\cite{Lohavanichbutr2013}.
-
-x 7. Integration of molecular gene signatures with clinicopathological variables improves staging and outcome prediction of oral cancer.
-(Submitter supplied) The aim of this study is to identify and validate clinically implementable gene signatures for outcome prediction of patients with oral squamous cell carcinoma.
-Organism:	Homo sapiens
-Type:		Expression profiling by array
-Platform: GPL6480 99 Samples
-FTP download: GEO (TXT) ftp://ftp.ncbi.nlm.nih.gov/geo/series/GSE84nnn/GSE84846/
-Series		Accession: GSE84846	ID: 200084846
-only alive or death (no survival time) => Similarly preprocessed VUmc (GSE84846) and UMCU (GSE30788) microarray datasets (https://www.oncotarget.com/article/19576/text/)
-\cite{Mes2017}
-
-%as following: % search by StarGEO ===========
-StarGEO http://stargeo.org/ searching: HNSCC + survival (n>100]
-* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837
-
-x https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE40774
-n=134; Agilent-026652 Whole Human Genome Microarray 4x44K v2 (Probe Name version)
-supplementary data:
-https://clincancerres.aacrjournals.org/content/21/4/870.figures-only#fig-data-additional-files
-n=134 (no survival)
-# Version info: R 3.2.3, Biobase 2.30.0, GEOquery 2.40.0, limma getGEO("GSE40774", GSEMatrix =TRUE, cex=1.5)library("maptools")
-
-x https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE148944
-   784 probes (gene）
-n=40; 110 FFPE samples were collected from a retrospective cohort of 67 OTSCC patients and 10 non-cancerous tongue samples.
-Targets including CD4, CD8, FOXP3, PD-L1 and PD-1 were analyzed by immunohistochemistry.
-The Nanostring PanCancer Immune Profiling Panel was used for gene expression profiling.
-Data were externally validated in the TCGA head and neck (HNSCC), melanoma and lung squamous cell carcinoma (LSCC) cohorts.
-GPL28285 NanoString nCounter PanCancer Immune Profiling Panel
-
-https://onlinelibrary.wiley.com/doi/full/10.1002/cam4.3106
-.................
+PFS and DSS event and months.
 
@@
 \subsection*{2-5}
-% gene signature
+% gene signature or cluster of genes
 Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
+% to avoid a cutoff: a good idea
 
@@
 In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.
+
+** or using %Rplot_GSE65858_CoxHR1.5_top19.pdf
+KM estimate and Cox modeling to yield a geographically closed gene cluster:
+CAMK2N1, TIMM10, TNFAIP6, SPP1, ADAMTSL2.
 
@@
 Third, dissection of ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) due to heterogeneity of 20500 RNA-Seq expression data files.
+# deal with return(1), return(2) and return(3) errors, try to solve it
+32.2\% error01, ZSWIM2 skip from contingencyTCGA(), it is one group issue in Melt() function.
+21.05\% errors in  one group in survdiff on KM cutofFinder_func.R.
+0.78\%(159 genes) for unknown reason
+%# _marginS_
+%n_percent_Bonferroni <- ZSWIM2_2$Freq[1]/sum(ZSWIM2_2$Freq) # 0.4593171 -> 0.4581951
+%error01_sample <- which(ZSWIM2$X3==1) #  32.2\% error01: "ZSWIM2 skip from contingencyTCGA()"): one group issue in Melt()
+%# => *** re-run
+%error02_sample <- which(ZSWIM2$X3==2) # 14.2\% error02: There has only one group in survdiff.
+%error03_sample <- which(ZSWIM2$X3==3) # 6.85\% error03: There has only one group in survdiff on KM cutofFinder_func.R.
+%#=> Test for difference (log-rank test is multiple Chi-square alone survival time) with P-value; or Test for different KM curve between two groups (seperated by PMM1_median 0 vs 1)
+% error05_sample <- which(ZSWIM2$X3==5) # 0.78\%(159 genes) error05: for why?
 

### 2021-06-13 Supplementary_figures.tex
finallized
Updates from Overleaf
new Table 1 (merged table 1 and table 2)

@@
 \renewcommand{\figurename}{Supplementary Figure } %S
+
+% \usepackage{multirow}
+\usepackage{graphicx}
+\usepackage[table,xcdraw]{xcolor}
+
+\usepackage{siunitx} % for  1e-10 scientific notation
+\usepackage{array}
+\usepackage{ragged2e}
+\usepackage{rotating}
+\usepackage{tabularx}
+\usepackage{makecell}
+% \usepackage{array}
+\usepackage{multirow}
+\usepackage{colortbl}
+\usepackage{hhline}
 
@@
 %\Title{
-Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
+x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
 %}
@@
 
+\section{STables}
 \underline{Supplementary figure legends}\\[1cm]
-% S1
+%ST1
+Supplementary Table \ref{table:table1}\\
+GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as red; the better prognostic genes are marked as green.
+
+%ST2
+Supplementary Table \ref{table:table3}\\
+
+% tables below %%%%
+% table1
+\begin{table}
+%\begin{sidewaystable}[hp]
+\centering
+\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{
+%\begin{tabular}{|l|l|l|l|l|l|l|l|c|}
+\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|c|} % *** capital X or p{2cm}
+% p{2cm}
+\hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\\textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
+\hline
+DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                &                                           \\
+\hline
+CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & \checkmark                                          \\
+\hline
+STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                &                                           \\
+\hline
+PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & \checkmark                                          \\
+\hline
+SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & \checkmark                                           \\
+\hline
+USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & \checkmark                                         \\
+\hline
+NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & \checkmark                                           \\
+\hline
+FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & \checkmark                                          \\
+\hline
+STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                &                                           \\
+\hline
+DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                &                                           \\
+\hline
+\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
+\arrayrulecolor{black}\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
+\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: \textit{P} $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
+\hline
+\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\
+\hline
+\end{tabularx}
+}
+\arrayrulecolor{black}
+\label{table:table1}
+
+%\end{sidewaystable}
+\end{table}
+
+%%%
+%Table2. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
+\begin{table}[hp]
+\centering
+\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by corrected \textit{P} value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
+\hline
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\
+\hline
+IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & \checkmark                                            \\
+\hline
+MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\
+\hline
+FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &  \checkmark                                           \\
+\hline
+LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\
+\hline
+EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\
+\hline
+PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\
+\hline
+KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &   \checkmark                                           \\
+\hline
+NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &      \checkmark                                        \\
+\hline
+                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\
+\hline
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\
+%\hline
+%\multicolumn{9}{|l!{\color{black}\vrule}}{
+* Cox's model: \textit{P} $< 0.001$ \\
+%}                                                                                                                                                                                                                                                                                                                                                                                                  \\
+%\hline
+lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
+\hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table3}
+\end{table}
+
+%%
+
+\section{SFigures}
+\underline{Supplementary figure legends}\\[1cm]
+%S1
+Supplementary Figure \ref{fig:fig_GSE2837}\\
+GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as red; the better prognostic genes are marked as green.
+
+% x S2
 Supplementary Figure \ref{fig:fig_SurvExpress}\\
@@
 
-%S2
+%x S3
 Supplementary Figure \ref{fig:fig_HPA_USP10}\\
@@
 
-%S3
-Supplementary Figure \ref{fig:fig_GSE2837}\\
-GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
-The poor prognostic genes are marked as red; the better prognostic genes are marked as green.
+%%%%%
+% S1
+% from Answer2-2 GSE2837; 
+\begin{figure}
+\raggedleft
+\includegraphics[width=12cm]{Answer_2-2.pdf}
+\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
+The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
+\label{fig:fig_GSE2837}
+\end{figure}
 
-% SFigure 1, SurvExpress
-
+% SFigure 2, SurvExpress
 % red or green is NOT by expression level
@@
 \end{figure}
-%\clearpage
+\clearpage
 
 %%
-
+% S3
 \begin{figure}
@@
 
-% from Answer2-2 GSE2837
-
-\begin{figure}
-\raggedleft
-\includegraphics[width=12cm]{Answer_2-2.pdf}
-\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
-The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
-\label{fig:fig_GSE2837}
-\end{figure}
 %\clearpage

### 2021-06-13 main.tex
new Table 1 (merged table 1 and table 2)

@@
 %[main\_marginSFP\_HNSCC.R] line 1361
-osccT_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
+osccT\_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
 OS\_live_days /30 % derived from last followup [30]/ last known alive [31])
@@
 The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} values (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling.
-The candidate selection performs dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses.
-The selected genes will be validated by a independent HNSCC cohort (GSE2837).
+The candidate selection performs 1) dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses;
+2) survival analyses of the other HNSCC dataset (GSE6585) using Kaplan-Meier estimate (KM, with FDR correction) and Cox modeling (CoxHR).\\
+The selected genes have been validated by third HNSCC cohort (GSE2837).
 (HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
@@
 % before validation
-Among these candidates, ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{table:table1}).
-The other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{table:table3}, with their gene name).
+Among these candidates, ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{tab:newTable1}).
+The other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{tab:newTable1}, with their gene name).
 We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
@@
 
-\begin{table}
-%\begin{sidewaystable}[hp]
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+% \usepackage{graphicx}
+% \usepackage[table,xcdraw]{xcolor}
+
+\begin{table}[ht]
 \centering
-\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }
-\arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{
-%\begin{tabular}{|l|l|l|l|l|l|l|l|c|}
-\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|c|} % *** capital X or p{2cm}
-% p{2cm}
+\caption{The top 3 genes with prognostic impact in HNSCC (ranked by Bonferroni-adjusted \textit{P} values}
+\label{tab:newTable1}
+\resizebox{\linewidth}{!}{% \textwidth
+\begin{tabular}{|l|l|l|c|c|c|c|c|c|}
 \hline
-\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\
-\cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\\textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
+\multicolumn{1}{|c|}{} &
+  \multicolumn{2}{c|}{} &
+  \multicolumn{2}{c|}{Kaplan-Meier survival} &
+  \multicolumn{2}{c|}{Univariate} &
+  \multicolumn{2}{c|}{Multivariate} \\ \cline{4-9} 
+\multicolumn{1}{|c|}{\multirow{-2}{*}{Gene ID}} &
+  \multicolumn{2}{c|}{\multirow{-2}{*}{Gene Description}} &
+  \begin{tabular}[c]{@{}c@{}}FDR\\ \textit{P} value\end{tabular} &
+  \begin{tabular}[c]{@{}c@{}}Bonferroni\\ \textit{P} value\end{tabular} &
+  HR* &
+  95\% CI &
+  HR* &
+  95\% CI \\ \hline
+CAMK2N1 &
+  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}calcium/calmodulin-\\ dependent protein\\ kinase II inhibitor 1\end{tabular}} &
+  \num{2.9e-7} &
+  0.002 &
+  2.101 &
+  1.572-2.809 &
+  2.007 &
+  1.490-2.704 \\ \hline
+\rowcolor[HTML]{FFFFFF} 
+{\color[HTML]{333333} IL19} &
+  \multicolumn{2}{l|}{\cellcolor[HTML]{FFFFFF}{\color[HTML]{333333} interleukin 19}} &
+  {\color[HTML]{333333} \num{3.7e-7}} &
+  {\color[HTML]{333333} 0.002} &
+  {\color[HTML]{333333} 0.472} &
+  {\color[HTML]{333333} 0.351-0.635} &
+  {\color[HTML]{333333} 0.459} &
+  {\color[HTML]{333333} 0.340-0.619} \\ \hline
+\rowcolor[HTML]{FFFFFF} 
+{\color[HTML]{333333} FCGBP} &
+  \multicolumn{2}{l|}{\cellcolor[HTML]{FFFFFF}{\color[HTML]{333333} \begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}}} &
+  {\color[HTML]{333333} \num{1.2e-6}} &
+  {\color[HTML]{333333} 0.008} &
+  {\color[HTML]{333333} 0.484} &
+  {\color[HTML]{333333} 0.359-0.653} &
+  {\color[HTML]{333333} 0.496} &
+  {\color[HTML]{333333} 0.366-0.674} \\ \hline
+\multicolumn{9}{|l|}{} \\
+\multicolumn{9}{|l|}{\multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Selection criteria:
+1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;
+2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5\end{tabular}}} \\ 
+%\hline
 \hline
-DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                &                                           \\
-\hline
-CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & \checkmark                                          \\
-\hline
-STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                &                                           \\
-\hline
-PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & \checkmark                                          \\
-\hline
-SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & \checkmark                                           \\
-\hline
-USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & \checkmark                                         \\
-\hline
-NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & \checkmark                                           \\
-\hline
-FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & \checkmark                                          \\
-\hline
-STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                &                                           \\
-\hline
-DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                &                                           \\
-\hline
-\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
-\arrayrulecolor{black}\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
-\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: \textit{P} $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
-\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\
-\hline
-\end{tabularx}
+\end{tabular}%
 }
-\arrayrulecolor{black}
-\label{table:table1}
-
-%\end{sidewaystable}
 \end{table}
@@
 %\subsubsection{Table3/legend} or Table 2
-%Table2. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
-\begin{table}[hp]
-\centering
-\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by corrected \textit{P} value) }
-\arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
-\hline
-\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
-\cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
-\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\
-\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\
-\hline
-IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & \checkmark                                            \\
-\hline
-MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\
-\hline
-FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &  \checkmark                                           \\
-\hline
-LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\
-\hline
-EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\
-\hline
-PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\
-\hline
-KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &   \checkmark                                           \\
-\hline
-NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &      \checkmark                                        \\
-\hline
-                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\
-\hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\
-%\hline
-%\multicolumn{9}{|l!{\color{black}\vrule}}{
-* Cox's model: \textit{P} $< 0.001$ \\
-%}                                                                                                                                                                                                                                                                                                                                                                                                  \\
-%\hline
-lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
-\hline
-\end{tabular}
-}
-\arrayrulecolor{black}
-\label{table:table3}
-\end{table}
 
@@
 
-Table \ref{table:table1} shows ten overexpressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value.
+Table %\ref{table:table1}
+\ref{tab:newTable1} shows ten overexpressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value.
 Six out of ten genes has been validated by using GSE2837.
@@
 
-In Table \ref{table:table3}, the other ten overexpressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
+In Table \ref{tab:newTable1}, %{table:table3}, 
+the other ten overexpressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
 Four out of ten has been validated by using GSE2837.

### 2021-06-14 Cover_letter_JPM.tex
new Table 1 (merged table 1 and table 2)
Updates from Overleaf

@@
 % https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f
-
+\usepackage{tikz-imagelabels} % for  tikz
+\usepackage{siunitx} % for  1e-10 scientific notation
 \usepackage[bf]{caption}
@@
 The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129).
-Also, it was shown here in the following paragraph.
+Also, it is shown here in the following paragraph.
 
@@
 But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
-This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖
+This strategy only identifies more weak “biomarkers,” and it also captures more false positives. % defense (ok) => NOT weak 其實 very significant; 欠一張圖 => new Figure 4 (ok)
 Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
@@
 % and give us this nomenclature as "sliding window"
-%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
-We correct our statement of this workflow (please see Answer 2-2).
-There is more evidence to validate them (please see Answer 2-3).
-
-We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (p=0.05).
-*** According to our results, all of preliminary biomarkers have FDR-corrected \textit{P} values from 1e-4 to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see supplementary Figure SXXX).
-There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
-Thus we also performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.
+%% *** 準備一張 3/20 candidates: accumulated \textit{P}-value plots 來說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05, even < 0.001
+We have corrected our statement of this workflow (please see Answer 2-2).
+We provide more evidence to validate them (please see Answer 2-3).
+
+We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
+According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").
+%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
+Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.
+
+% and a new Figure 4
+\begin{figure}[hp]
+
+% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
+\setlength{\unitlength}{1cm}
+\begin{picture}(15, 20) %(1,0.55038404)%
+\centering
+  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_IL19_FCGBP.pdf}}%
+  \put(2.5, 14.3){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{1.63e-05}}%CAMK2N1
+    \put(2.5, 9.45){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{6.54e-06}}%IL19
+    \put(2.5, 4.55){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{4.83e-05}}%FCGBP
+
+%\begin{annotationimage}{width=15cm}{Figure_4_CAMK2N1_IL19_FCGBP.pdf}
+%\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
+%\draw[annotation left = {Aries at 0.3}]
+
+%\end{annotationimage}
+\end{picture}%
+
+\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
+{The Kaplan-Meier curves of (a) CAMK2N1, (c) IL19, and (e) FCGBP under optimal \textit{P} value. 
+%((b) the cutoffs derived from it's cumulative \textit{P} value plot).
+%(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value;
+%((d) the cutoffs derived from it's cumulative \textit{P} value plot).
+%(e) Kaplan-Meier plot of FCGBP under optimal \textit{P} value.\\
+The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
+shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
+* \textit{P}: Adjusted \textit{P} value by \acrfull{fdr}
+}
+\label{fig:figure4}
+\end{figure}
 
@@
 %Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
-The caption of Figure 1, Table 1, and Table 2 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 %***=> Bonferroni correction should be used in final decision.
+
+%\begin{MyColorPar}{red}
+
+%\end{MyColorPar}
 
@@
 
+2021/06/13
+CAMK2N1, IL19, and FCGBP is validated?
+%candidate_fdr100
+
+(please see Figure \ref{fig:hazards3}).
+
+%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
+% by Validation_GSE65858_survival.R
+% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
+
+\begin{figure}
+    \centering
+    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
+    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
+%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
+%Y axis: multivariate hazard ratio from Cox proportional regression model.
+%Dotted line: significant Bonferroni corrected \textit{P} value. 
+%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$).
+\textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
+    This cohort has been applied for exploration of the candidate biomarkers.
+    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
+    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
+    Remarks:\\
+    \textcolor{red}{Red spots}: $HR > 1.0$;
+    \textcolor{green}{Green spots}: $HR < 1.0$;\\
+    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
+    Y-axis: HR of Cox proportional hazard regression model\\
+    }
+    \label{fig:hazards3}
+\end{figure}
+
 % SurvExpress http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp
@@
 We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised.
-Also, it was shown here in the following paragraph.\\[0.3cm]
+Also, it is shown here in the following paragraph.\\[0.3cm]
 
@@
 We apologize for exaggerating the difficulties of our workflow.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following two paragraphs.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.
 
@@
 The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised.
-Also, it was shown here in the following paragraph.
+Also, it is shown here in the following paragraph.
 \\[0.3cm]

### 2021-06-14 main.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
+\usepackage{tikz-imagelabels} % for  tikz
 \usepackage[]{caption} % bf
@@
 The other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{tab:newTable1}, with their gene name).
-We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}).
-The plot reveals that the most significant (Bonferroni-adjusted \textit{P} $< 0.05$) candidate genes are located above the dotted line.
-At the same time, Cox's HR separated them on the two-side with prognostic impact.
+We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:hazards3}).
+%{fig:figure3}).
+The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
 % => after validation: The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
@@
 \includegraphics[width=14cm]{Figure2.pdf}
-\bcaption{\acrshort{hnscc} Cox's hazard ratio and \textit{P} value plot.}
+\bcaption{TCGA \acrshort{hnscc} Cox's hazard ratio and \textit{P} value plot.}
 {(a) Univariate HR versus uncorrected \textit{P} value; (b) Multivariate HR versus uncorrected \textit{P} value; (c) Univariate HR versus Bonferroni corrected \textit{P} value; and (d) Multivariate HR versus Bonferroni corrected \textit{P} value.}
@@
 %%% tables
-% Table1
+% Table1 = merged table 1and2
 % wide table \usepackage{tabularx}
@@
 
-\begin{table}[ht]
+\begin{table}[hp]
 \centering
-\caption{The top 3 genes with prognostic impact in HNSCC (ranked by Bonferroni-adjusted \textit{P} values}
+\caption{The top 3 genes with prognostic impact in HNSCC}% (ranked by Bonferroni-adjusted \textit{P} values}
 \label{tab:newTable1}
@@
   \multicolumn{2}{c|}{Kaplan-Meier survival} &
-  \multicolumn{2}{c|}{Univariate} &
-  \multicolumn{2}{c|}{Multivariate} \\ \cline{4-9} 
+  \multicolumn{2}{c|}{Cox Univariate} &
+  \multicolumn{2}{c|}{Cox Multivariate} \\ \cline{4-9} 
 \multicolumn{1}{|c|}{\multirow{-2}{*}{Gene ID}} &
@@
   1.490-2.704 \\ \hline
-\rowcolor[HTML]{FFFFFF} 
-{\color[HTML]{333333} IL19} &
-  \multicolumn{2}{l|}{\cellcolor[HTML]{FFFFFF}{\color[HTML]{333333} interleukin 19}} &
-  {\color[HTML]{333333} \num{3.7e-7}} &
-  {\color[HTML]{333333} 0.002} &
-  {\color[HTML]{333333} 0.472} &
-  {\color[HTML]{333333} 0.351-0.635} &
-  {\color[HTML]{333333} 0.459} &
-  {\color[HTML]{333333} 0.340-0.619} \\ \hline
-\rowcolor[HTML]{FFFFFF} 
-{\color[HTML]{333333} FCGBP} &
-  \multicolumn{2}{l|}{\cellcolor[HTML]{FFFFFF}{\color[HTML]{333333} \begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}}} &
-  {\color[HTML]{333333} \num{1.2e-6}} &
-  {\color[HTML]{333333} 0.008} &
-  {\color[HTML]{333333} 0.484} &
-  {\color[HTML]{333333} 0.359-0.653} &
-  {\color[HTML]{333333} 0.496} &
-  {\color[HTML]{333333} 0.366-0.674} \\ \hline
+IL19 &
+  \multicolumn{2}{l|} {interleukin 19} &
+   \num{3.7e-7} &
+   0.002 &
+   0.472 &
+   0.351-0.635 &
+   0.459 &
+   0.340-0.619 \\ \hline
+FCGBP &
+  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}} &
+   \num{1.2e-6} &
+   0.008 &
+   0.484 &
+   0.359-0.653 &
+   0.496 &
+   0.366-0.674 \\ \hline
 \multicolumn{9}{|l|}{} \\
-\multicolumn{9}{|l|}{\multirow{-2}{*}{\begin{tabular}[c]{@{}l@{}}Selection criteria:
-1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;
-2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5\end{tabular}}} \\ 
-%\hline
+\multicolumn{9}{|l|}%{\multirow{-0}{*}
+{\begin{tabular}[c]{@{}l@{}}
+Selection criteria (fit all):\\
+1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;\\
+2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in TCGA cohort;\\
+3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in GSE65858 cohort
+\end{tabular}
+%}\\ % within \multirow
+} \\ % within \multicolumn
 \hline
+\multicolumn{9}{|l|}{* Cox’s model: \textit{P} \textless 0.001} \\ \hline
+
 \end{tabular}%
@@
 %\subsubsection{Figure 3:h}
-\begin{figure}[hp]
+\begin{figure}
     \centering
-\includegraphics[width=14cm]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
-\bcaption{Volcano plot of genes under survival analyses.}
-{X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
-Y axis: multivariate hazard ratio from Cox proportional regression model.
-Dotted line: significant Bonferroni corrected \textit{P} value. 
-\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$).
-\textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).}
-\label{fig:figure3}
+    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
+    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
+%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
+%Y axis: multivariate hazard ratio from Cox proportional regression model.
+%Dotted line: significant Bonferroni corrected \textit{P} value. 
+%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$).
+\textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
+    This cohort has been applied for exploration of the candidate biomarkers.
+    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
+    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
+    Remarks:\\
+    \textcolor{red}{Red spots}: $HR > 1.0$;
+    \textcolor{green}{Green spots}: $HR < 1.0$;\\
+    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
+    Y-axis: HR of Cox proportional hazard regression model\\
+    }
+%\label{fig:figure3}
+\label{fig:hazards3} %TCGA volcano
 \end{figure}
@@
 %\subsubsection{Figure 4:h}
+% *** Adjusted P value = 0.002 ; drawing by tikz
+% https://tex.stackexchange.com/questions/9559/drawing-on-an-image-with-tikz
+
+%font code: Computer Modern Sans Serif		cmss
+
 \begin{figure}[hp]
+
+% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
+\setlength{\unitlength}{1cm}
+\begin{picture}(15, 20) %(1,0.55038404)%
 \centering
-\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
+  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_IL19_FCGBP.pdf}}%
+  \put(2.5, 14.3){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{1.63e-05}}%CAMK2N1
+    \put(2.5, 9.45){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{6.54e-06}}%IL19
+    \put(2.5, 4.55){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{4.83e-05}}%FCGBP
+
+%\begin{annotationimage}{width=15cm}{Figure_4_CAMK2N1_IL19_FCGBP.pdf}
+%\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
+%\draw[annotation left = {Aries at 0.3}]
+
+%\end{annotationimage}
+\end{picture}%
+
 \bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
-{(a) Kaplan-Meier plot of CAMK2N1 under optimal \textit{P} value, and (b) the cutoff is derived from cumulative \textit{P} value plot of CAMK2N1.
-(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value, and (d) the cutoff is derived from cumulative \textit{P} value plot of IL19.}
+{The Kaplan-Meier curves of (a) CAMK2N1, (c) IL19, and (e) FCGBP under optimal \textit{P} value. 
+%((b) the cutoffs derived from it's cumulative \textit{P} value plot).
+%(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value;
+%((d) the cutoffs derived from it's cumulative \textit{P} value plot).
+%(e) Kaplan-Meier plot of FCGBP under optimal \textit{P} value.\\
+The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
+shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
+* \textit{P}: Adjusted \textit{P} value by \acrfull{fdr}
+}
 \label{fig:figure4}

### 2021-06-14 Cover_letter_JPM.tex
part of Answer 2-3

@@
 
-\subsection*{2-1}%(ok)
+\subsection*{2-1}%(ok) [2021/06/14]
 % sliding window cutoff selection with FDR corrected
@@
 
-% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) validation
+% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) during candidate selection
 In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
@@
 The p-values are affected by the sample size, which should be described in the main text. % writing
-As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO
+As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) or even GSE117973?
 
@@
 % more GSE datasets; pick-up more candidate (run GCP) in hands 而且要偷看答案
-% using  receiver operating characteristic (ROC) analysis and more GEO datasets
-We appreciate the reviewer for the critical comments and thanks for the agreement of our work in cancer research.
+% x using  receiver operating characteristic (ROC) analysis and more GEO datasets
+We appreciate the reviewer for the critical comments and thanks for the guidance of our work in cancer research.
 
 %***調整 workflow 更加嚴格以增加 validation rate
-Validation rate:\\
+%Validation rate:\\
 %重新挑選 candidate (FDR100) 多選一些、偷偷看答案(GSE2837 and GSE65858)
 
-*** Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]
+%*** Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]
 
 % [2021/06/11]決議;
-***  PvalueTex consensus with GSE2837 to yield 9 candidates
-% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
-x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
-%找出  9 candidates
-listed as
-six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
-four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
-%}
+We introduce an independent HNSCC cohort (GSE65858) for helping in candidate selection.
 
@@
 validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data): 
+ to yield 3 candidates
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002      Gene.Symbol KM.Pvalue FDR.KMpvalue uni_HR   FDR.Pvalue
@@
 2021/06/13
-CAMK2N1, IL19, and FCGBP is validated?
+CAMK2N1, IL19, and FCGBP is validated by
 %candidate_fdr100
-
+PvalueTex consensus with GSE2837 to yield 3 candidates
+% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
+%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
+%找出  3 candidates
+listed as
+six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
+four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
+%}
 (please see Figure \ref{fig:hazards3}).
@@
 
+%GSE117973
+%***  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
+%PFS and DSS event and months.
+
+% *** how to do? ROC
+% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
+%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
+%---
+
+We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
+The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
+\\[0.3cm]
+
+\begin{MyColorPar}{red}
+validation rate
+***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size
+
 %%%
-*the authors should look for more data to verify these biomarkers.
-For validation by GEO datasets:
+% (OK)*the authors should look for more data to verify these biomarkers.
+%For validation by GEO datasets:
 
@@
 It was used as a validation dataset. \\
-
-GSE117973
-**  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
-PFS and DSS event and months.
-
-% *** how to do? ROC
-% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
-In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
-%---
-
-We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
-\\[0.3cm]
-
-\begin{MyColorPar}{red}
-validation rate
-...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size
 

### 2021-06-15 main.tex
table 2 3 4 done

@@
   \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}calcium/calmodulin-\\ dependent protein\\ kinase II inhibitor 1\end{tabular}} &
-  \num{2.9e-7} &
+  \num{1.63e-5} & %2.9e-7} &
   0.002 &
@@
   \multicolumn{2}{l|} {interleukin 19} &
-   \num{3.7e-7} &
+   \num{6.54e-6} & %3.7e-7} &
    0.002 &
@@
   \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}} &
-   \num{1.2e-6} &
+   \num{4.83e-5} & %1.2e-6} &
    0.008 &
@@
     Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
-    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
+    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.5$.\\
     Remarks:\\
@@
 \arrayrulecolor[rgb]{0.255,0.255,0.255}\hline
-\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}=65y                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
 \cline{2-8}
-                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.391                                                                          & 1.025-1.888                                                                   & \textcolor{red}{0.034}                                                         \\
+                                        & $>65y$                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.391                                                                          & 1.025-1.888                                                                   & \textcolor{red}{0.034}                                                         \\
 \hline
@@
 \hline
-\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
+\multirow{2}{*}{Gene Expression}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\
 \cline{2-8}
@@
 \hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
-\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}=65y                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
 \arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
-                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.481                                & 1.087-2.018                                      & \textcolor{red}{0.013}                     \\
+                                        & $>65y$                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.481                                & 1.087-2.018                                      & \textcolor{red}{0.013}                     \\
 \hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
@@
 \hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
-\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\multirow{2}{*}{Gene Expression}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
 \arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
@@
 \label{table:table4}
+\end{table}
+
+%\subsubsection{Table4/legend} new Table 4 for FCGBP
+% \ref{table:table_FCGBP}
+\begin{table}[!hp]
+\centering
+\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of FCGBP gene expression in HNSCC}
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l!{\color{black}\vrule}l!{\color{black}\vrule}l!{\color{black}\vrule}} 
+\arrayrulecolor{black}\cline{1-2}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{3-8}
+\multicolumn{2}{|l!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                    \\
+\cline{3-8}
+\multicolumn{2}{|l!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{l!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{l!{\color{black}\vrule}}{\textit{P}~value}                    & HR                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%} & \textit{P}~value                           \\
+\arrayrulecolor{black}\hline
+\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\cline{2-8}
+                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.196                                & 0.858-1.669                                      & 0.291                                      \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & $>65y$                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.372                                & 1.008-1.867                                      & \textcolor{red}{0.044}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Clinical T Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}T1+T2                                            & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 2.207                                & 1.169-4.165                                      & \textcolor{red}{0.015}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Clinical N Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}N0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.328                                & 0.927-1.902                                      & 0.122                                      \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Clinical M Status}      & {\cellcolor[rgb]{0.62,0.812,0.878}}M0                                               & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.644                                                                  & \textcolor{red}{0.049}                                                        & 7.571                                & 1.645-34.846                                      & \textcolor{red}{0.009}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Clinical Stage}         & {\cellcolor[rgb]{0.62,0.812,0.878}}Stage I+II                                       & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.454                                & 0.211-0.976                                      & \textcolor{red}{0.043}                                      \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Surgical Margin status} & {\cellcolor[rgb]{0.62,0.812,0.878}}Negative                                         & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & Positive                                                                            & 1.591                                                                          & 1.155–2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.598                                 & 1.156-2.21                                      & \textcolor{red}{0.005}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Tobacco Exposure}       & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.502                                 & 1.087-1.087                                      & \textcolor{red}{0.014}                     \\
+\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
+\multirow{2}{*}{Gene Expression}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
+                                        & High                                                                                & 0.484                                                                          & 0.359-0.653                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & \multicolumn{1}{l|}{0.496}           & 0.366-0.674                                      & \multicolumn{1}{c|}{\textcolor{red}{***}}  \\
+\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{1-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{8-8}
+\multicolumn{8}{|l|}{}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                \\
+\hline
+\multicolumn{8}{|l|}{(\textit{P}~value significant codes is denoted: red \textless{} 0.05; *** \textless{} 0.001)}                                                                                                                                                                                                                                                                                                                                                                                                    \\
+\hline
+\end{tabular}
+}% end of \resizebox
+\arrayrulecolor{black}
+\label{table:table_FCGBP}
 \end{table}

### 2021-06-15 Cover_letter_JPM.tex
table 2 3 4 done
Updates from Overleaf

@@
 We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
+(  )  Answer 2-1
+%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
+%=> defense: 
+%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
+%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
+% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
+%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
+%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
+%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
 According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").
+Moreover, 
+Rplot_pvaluePlot_NDFIP1.pdf
+%  to find cases_OS outside of range 180-220 (== cutoff not at median)
+%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
+% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
+# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
+# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
+# NDFIP1 (within our 20 candidatte biomarkers), median cut will let NDFIP1 to be kik-out prematurely
+# show it's pvalue plot
+supplementary Figure \ref{fig:pvaluePlot_NDFIP1} as Rplot_pvaluePlot_NDFIP1.pdf
+
+% supplementary figure
+\begin{figure}
+    \centering
+    \includegraphics{Rplot_pvaluePlot_NDFIP1.pdf}
+    \caption{Caption}
+    \label{fig:pvaluePlot_NDFIP1}
+\end{figure}
+
 %There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
@@
 
-% *** how to do? ROC
-% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
-%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
-%---
-
 We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
@@
 risk score = $expression_{gene1} \times \beta_{gene1} + expression_{gene2} \times \beta_{gene2} + ... + expression_{geneX} \times \beta_{geneX}$\\
+
+*** how to do? ROC
+% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
+%In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
+%---
 

### 2021-06-17 Cover_letter_JPM.tex
Updates from Overleaf

@@
 We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
-(  )  Answer 2-1
 %http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
@@
 According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").
-Moreover, 
-Rplot_pvaluePlot_NDFIP1.pdf
+
+Moreover, in the special case, one of our 20 preliminary candidates, gene "NDFIP1", 
+%Rplot_pvaluePlot_NDFIP1.pdf
 %  to find cases_OS outside of range 180-220 (== cutoff not at median)
@@
 % # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
-# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
-# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
-# NDFIP1 (within our 20 candidatte biomarkers), median cut will let NDFIP1 to be kik-out prematurely
-# show it's pvalue plot
-supplementary Figure \ref{fig:pvaluePlot_NDFIP1} as Rplot_pvaluePlot_NDFIP1.pdf
+%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
+%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
+%# NDFIP1 (within our 20 preliminary candidates), 
+will be kick-out prematurely in "median cutoff" of survival analysis.
+In the \textit{P} value plot (Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
+supplementary figure ??), we could see a sliding-window selection with cutoff finding might collect more candidate (\textit{P} $<0.05$) for further Cox's modeling.
+Indeed, it needs to be validated by the other independent cohort.
+%as Rplot_pvaluePlot_NDFIP1.pdf
 
@@
     \centering
-    \includegraphics{Rplot_pvaluePlot_NDFIP1.pdf}
-    \caption{Caption}
+    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
+    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} value is $<0.05$; 2) the middle part (zoom-in and revealed in inset box) has a "W" curve; 3) sliding-window cutoff selection could find it's optimized \textit{P} values while a median cut might yield \textit{P} value $<0.05$ or $>0.05$ by chance.}
     \label{fig:pvaluePlot_NDFIP1}
@@
 \subsection*{2-3}
+% [2021/06/17]
 % PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity (less biomarkers but more P value < 1e-5?)
@@
 %重新挑選 candidate (FDR100) 多選一些、偷偷看答案(GSE2837 and GSE65858)
-
-%*** Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]
+% => answer is: consensus top3 genes
+
+% (ok) Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]
 
 % [2021/06/11]決議;
-We introduce an independent HNSCC cohort (GSE65858) for helping in candidate selection.
-
-We further
-validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data): 
- to yield 3 candidates
-% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002      Gene.Symbol KM.Pvalue FDR.KMpvalue uni_HR   FDR.Pvalue
-1524     CAMK2N1   0.00687   0.03782500  1.814 1.628308e-05
-3967       FCGBP   0.01020   0.03886709  0.573 4.827833e-05
-5262        IL19   0.03390   0.04738901  0.630 6.543871e-06
-5264        IL19   0.00269   0.03068073  0.630 6.543871e-06
-
-CAMK2N1, IL19, and FCGBP
-%candidate_fdr100
-(please see Figure \ref{fig:hazards534}).
-
+We have introduced an independent HNSCC cohort (GSE65858, with RNA-Seq expression data) for helping in candidate selection.
+%We further
+%validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data)
+
+% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
+%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
+%找出  3 candidates
+Even the top 20 genes listed
+%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
+%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
+%}
+in Figure \ref{fig:hazards3}, have significant FDR-adjusted \textit{P} values in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model. 
 %Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
@@
 % Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
-
-\begin{figure}
-    \centering
-    \includegraphics[width=13cm]{Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf}
-    \bcaption{Validation cohort (GSE65858)}{
-    This HNSCC cohort has been applied for validation of our candidate genes: "CAMK2N1", "IL19" (two probes), and "FCGBP".
-    There are 270 HNSCC participants involved in this cohort.
-    The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30330.
-    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
-    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0;
-    \textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
-    The 22 gene symbol listed on the side: hazard ratio $> 1.8$ or $< 0.6$.\\
-    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);
-    Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
-    }
-    \label{fig:hazards534}
-\end{figure}
-
-2021/06/13
-CAMK2N1, IL19, and FCGBP is validated by
-%candidate_fdr100
-PvalueTex consensus with GSE2837 to yield 3 candidates
-% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
-%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
-%找出  3 candidates
-listed as
-six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
-four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
-%}
-(please see Figure \ref{fig:hazards3}).
-
-%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
-% by Validation_GSE65858_survival.R
-% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
-
 \begin{figure}
@@
 
+% [2021/06/13-17]
+%CAMK2N1, IL19, and FCGBP is validated by
+%candidate_fdr100
+%PvalueTex consensus with GSE2837 to yield 3 candidates
+In GSE65858 cohorts, CAMK2N1, IL19, and FCGBP, have FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
+% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
+%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
+%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
+%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
+%IL19    0.03390   0.04738901    0.630   6.543871e-06
+%IL19    0.00269  0.03068073 0.630  6.543871e-06
+%candidate_fdr100
+and also see Figure \ref{fig:hazards534}), however, the "rank" of other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11.
+In the consensus of TCGA and GSE65858 cohorts, we suggest that CAMK2N1, IL19, and FCGBP are still significant candidates.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{graphicx}
+\begin{table}[ht]
+\centering
+\caption{GSE65858 and TCGA Consensus genes in Kaplan-Meier survival and Cox's model}
+\label{tab:table_top3_GSE65858}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{llll}
+Gene Symbol & KM \textit{P} value & FDR-adjusted \textit{P} value & Cox’s univariate HR \\
+\hline
+CAMK2N1 & \num{6.87e-3} & 0.038 & 1.814 \\
+FCGBP   & 0.01 & 0.039 & 0.573 \\
+IL19    & 0.03 & 0.047 & 0.63  \\
+IL19    & \num{2.69e-3} & 0.031 & 0.63\\
+\hline
+(values shown in dataset: GSE65858)\\
+(IL19 has two probes in RNA-Seq experiment)\\
+\hline
+\end{tabular}%
+}
+\end{table}
+
+%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
+% by Validation_GSE65858_survival.R
+% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
+
+\begin{figure}
+    \centering
+    \includegraphics[width=13cm]{Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf}
+    \bcaption{Volcano plot of genes under survival analyses of GSE65858 cohort}{
+    This HNSCC cohort has been applied for filtering of our candidate genes: "CAMK2N1", "IL19" (two probes), and "FCGBP".
+    There are 270 HNSCC participants involved in this cohort.
+    The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30330.
+    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
+    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0;
+    \textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
+    The 22 gene symbol listed on the side: hazard ratio $> 1.8$ or $< 0.6$.\\
+    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);
+    Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
+    }
+    \label{fig:hazards534}
+\end{figure}
+
 % SurvExpress http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp
@@
 \begin{MyColorPar}{red}
-validation rate
+
 ***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size
@@
 % an Affymetrix Human Genome U133A microarray (HG-U133A). 
-It was used as a validation dataset. \\
+It has been used as a dataset for candidate selection. \\
 
@@
 
+more in discussion
+2-3 supplementary figure Rplot_pvaluePlot_NDFIP1.pdf
+iscussion about sliding-window pvalueTex to find the more potential candidate (weak or not weak could be double-checked by GSE65858)
+
 \end{MyColorPar} % end of red

### 2021-06-18 Cover_letter_JPM.tex
Answer 2-1 done

@@
 % 2) and FDR (done)
-We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
+We appreciate the reviewer to kindly advise us about statistical consideration of sliding window cutoff selection in detail.
 % and give us this nomenclature as "sliding window"
@@
 We have corrected our statement of this workflow (please see Answer 2-2).
-We provide more evidence to validate them (please see Answer 2-3).
+We also provide more evidence to validate them by an independent HNSCC cohort (GSE65858) (please see Answer 2-3).
 
@@
 %[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
-According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 whatever grouped by cutoffs at 50\% quantile cutoff or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4} in this cover letter; it is also shown in manuscript as updated "Figure 4").
-
-Moreover, in the special case, one of our 20 preliminary candidates, gene "NDFIP1", 
+According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs at 50\% or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4").
+Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a p-value of \num{1e-6} at 70\% quantile cutoff.
+After the FDR correction, NDFIP1 still has \textit{P} value of \num[3]{0.0001074233}.
 %Rplot_pvaluePlot_NDFIP1.pdf
@@
 %# NDFIP1 (within our 20 preliminary candidates), 
-will be kick-out prematurely in "median cutoff" of survival analysis.
 In the \textit{P} value plot (Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
 supplementary figure ??), we could see a sliding-window selection with cutoff finding might collect more candidate (\textit{P} $<0.05$) for further Cox's modeling.
+%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
 Indeed, it needs to be validated by the other independent cohort.
-%as Rplot_pvaluePlot_NDFIP1.pdf
-
-% supplementary figure
-\begin{figure}
-    \centering
-    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
-    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} value is $<0.05$; 2) the middle part (zoom-in and revealed in inset box) has a "W" curve; 3) sliding-window cutoff selection could find it's optimized \textit{P} values while a median cut might yield \textit{P} value $<0.05$ or $>0.05$ by chance.}
-    \label{fig:pvaluePlot_NDFIP1}
-\end{figure}
-
-%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
-Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.
 
@@
 \end{figure}
+
+%as Rplot_pvaluePlot_NDFIP1.pdf
+%Moreover, in the special case, one of our 20 preliminary candidates, gene "NDFIP1",
+
+% supplementary figure
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
+    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} value is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
+    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
+    \label{fig:pvaluePlot_NDFIP1}
+\end{figure}
+
+%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
+Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.
 

### 2021-06-18 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
-Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine.
+Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine.
 We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.
@@
 
-We understand that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
+We also think that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
 %http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
@@
 %[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
-According to our results, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs at 50\% or at 70\% quantile cutoff (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4").
-Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a p-value of \num{1e-6} at 70\% quantile cutoff.
-After the FDR correction, NDFIP1 still has \textit{P} value of \num[3]{0.0001074233}.
+However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
+Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in
+supplementary figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233}.
 %Rplot_pvaluePlot_NDFIP1.pdf
@@
 %# NDFIP1 (within our 20 preliminary candidates), 
-In the \textit{P} value plot (Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
-supplementary figure ??), we could see a sliding-window selection with cutoff finding might collect more candidate (\textit{P} $<0.05$) for further Cox's modeling.
+In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
 %Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
@@
 % and a new Figure 4
-\begin{figure}[hp]
+\begin{figure}[ht]
 
@@
     \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
-    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} value is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
+    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
     (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
@@
 %There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
-Thus we performed the FDR correction applied on cutoff finding procedure as well as Bonferroni adjustment in candidate filtering.
-
+We performed the FDR correction applied on the Kaplan-Meier \textit{P} values of cutoff finding procedure, then Bonferroni adjustment of those \textit{P} values for candidate selection.
 %\begin{MyColorPar}{red}
 %\end{MyColorPar}
-
 % and FDR (done; ok)
-We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
+We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
 %Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
-***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
+%***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
@@
 It is ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
+Then Bonferroni adjustment of those \textit{P} values has been used for candidate selection.
 \end{MyColorPar}
@@
 %
-
+\clearpage
 \subsection*{2-2}
@@
 We appreciate the reviewer for the critical comment.
-We changed title as "Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
+We changed title as "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
 There is more evidence to validate them (please see Answer 2-3).

### 2021-06-18 Supplementary_figures.tex
Updates from Overleaf

@@
 % Full title of the paper (Capitalized)
-%\Title{
-x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
+\Title{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}\\[2cm]
+%x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
 %}
@@
 % table1
-\begin{table}
+\begin{table}[ht]
 %\begin{sidewaystable}[hp]
@@
 %Table2. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
-\begin{table}[hp]
+\begin{table}[ht]
 \centering
@@
 
-%%
+\clearpage
+
+%%%%%%%%%%%%
 
@@
 %S1
+Supplementary figure \ref{fig:pvaluePlot_NDFIP1}\\
+The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see supplementary Figure S1).
+After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233}.
+However, NDFIP1 could not pass the validation by using GSE65858 cohort.
+
+%S2
 Supplementary Figure \ref{fig:fig_GSE2837}\\
@@
 % x S2
-Supplementary Figure \ref{fig:fig_SurvExpress}\\
-The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
-Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
-Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.
+%Supplementary Figure \ref{fig:fig_SurvExpress}\\
+%The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
+%Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low. Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.
 
-%x S3
-Supplementary Figure \ref{fig:fig_HPA_USP10}\\
-The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
+% x S3
+%Supplementary Figure \ref{fig:fig_HPA_USP10}\\
+%The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
 Over-expression of USP10 has poor prognosis on HNSCC.
@@
 % S1
+% supplementary figure
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
+    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
+    (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
+    \label{fig:pvaluePlot_NDFIP1}
+\end{figure}
+
+% S2
 % from Answer2-2 GSE2837; 
@@
 \end{figure}
-
-% SFigure 2, SurvExpress
-% red or green is NOT by expression level
-\begin{figure}
-\raggedleft
-\includegraphics[width=10cm]{Answer_3-1.pdf}
-\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization.
-%cumulative P-value plots).
-Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
-Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
-\label{fig:fig_SurvExpress}
-\end{figure}
-\clearpage
-
-%%
-% S3
-\begin{figure}
-\raggedleft
-\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
-\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
-Overexpression of USP10 has poor prognosis on HNSCC.}
-\label{fig:fig_HPA_USP10}
-\end{figure}
-%\clearpage
 
@@
 %(optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
+
+%%
+
+% x SFigure 2, SurvExpress
+% red or green is NOT by expression level
+\begin{figure}
+\raggedleft
+\includegraphics[width=10cm]{Answer_3-1.pdf}
+\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization.
+%cumulative P-value plots).
+Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
+Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
+\label{fig:fig_SurvExpress}
+\end{figure}
+\clearpage
+
+%%
+%x S3
+\begin{figure}
+\raggedleft
+\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
+\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
+Overexpression of USP10 has poor prognosis on HNSCC.}
+\label{fig:fig_HPA_USP10}
+\end{figure}
+%\clearpage

### 2021-06-18 main.tex
Updates from Overleaf

@@
 % Full title of the paper (Capitalized)
-\Title{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+\Title{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
 %\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
@@
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+\TitleCitation{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
 %\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

### 2021-06-19 Cover_letter_JPM.tex
Updates from Overleaf

@@
 The p-values are affected by the sample size, which should be described in the main text. % writing
-As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) or even GSE117973?
+As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) 
+%or even GSE117973? GPL10558	Illumina HumanHT-12 V4.0 expression beadchip; https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE117973
+% Progression-free survival (PFS) is "the length of time during and after the treatment of a disease, such as cancer, that a patient lives with the disease but it does not get worse".[1] In oncology, PFS usually refers to situations in which a tumor is present, as demonstrated by laboratory testing, radiologic testing, or clinically.
+Similarly, "disease-free survival" is when patients have received treatment and are left with no detectable disease.
+% disease-specific survival rate: The percentage of people in a study group who have not died from a specific disease in a defined period of time.
+The time period usually begins at the time of diagnosis of the disease and ends at the time of death from the disease.
+%Patients who died from causes other than the disease being studied are not counted in this measurement.
 
@@
 We appreciate the reviewer for the critical comments and thanks for the guidance of our work in cancer research.
-
-%***調整 workflow 更加嚴格以增加 validation rate
+% workflow 更加嚴格以增加 validation rate
 %Validation rate:\\
-%重新挑選 candidate (FDR100) 多選一些、偷偷看答案(GSE2837 and GSE65858)
+%x重新挑選 candidate (FDR100) (GSE2837 and GSE65858)
 % => answer is: consensus top3 genes
-
 % (ok) Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]
-
 % [2021/06/11]決議;
@@
 %找出  3 candidates
-Even the top 20 genes listed
+During our exploration phase with TCGA cohort, the 20 genes, listed
 %six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
@@
 %}
-in Figure \ref{fig:hazards3}, have significant FDR-adjusted \textit{P} values in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model. 
+in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
+%
+% [2021/06/13-17]
+%CAMK2N1, IL19, and FCGBP is validated by
+%candidate_fdr100
+%PvalueTex consensus with GSE2837 to yield 3 candidates
+In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
+% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
+%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
+%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
+%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
+%IL19    0.03390   0.04738901    0.630   6.543871e-06
+%IL19    0.00269  0.03068073 0.630  6.543871e-06
+%candidate_fdr100
+and also see Figure \ref{fig:hazards534}).
+However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11.
+There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
+%In the consensus of TCGA and GSE65858 cohorts,
+
 %Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
@@
 
-% [2021/06/13-17]
-%CAMK2N1, IL19, and FCGBP is validated by
-%candidate_fdr100
-%PvalueTex consensus with GSE2837 to yield 3 candidates
-In GSE65858 cohorts, CAMK2N1, IL19, and FCGBP, have FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
-% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
-% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
-%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
-%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
-%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
-%IL19    0.03390   0.04738901    0.630   6.543871e-06
-%IL19    0.00269  0.03068073 0.630  6.543871e-06
-%candidate_fdr100
-and also see Figure \ref{fig:hazards534}), however, the "rank" of other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11.
-In the consensus of TCGA and GSE65858 cohorts, we suggest that CAMK2N1, IL19, and FCGBP are still significant candidates.
-
 % Please add the following required packages to your document preamble:
 % \usepackage{graphicx}
+% Please add the following required packages to your document preamble:
 \begin{table}[ht]
 \centering
-\caption{GSE65858 and TCGA Consensus genes in Kaplan-Meier survival and Cox's model}
+\caption{The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model}
 \label{tab:table_top3_GSE65858}
 \resizebox{\linewidth}{!}{%
-\begin{tabular}{llll}
-Gene Symbol & KM \textit{P} value & FDR-adjusted \textit{P} value & Cox’s univariate HR \\
+\begin{tabular}{llllclc}
 \hline
-CAMK2N1 & \num{6.87e-3} & 0.038 & 1.814 \\
-FCGBP   & 0.01 & 0.039 & 0.573 \\
-IL19    & 0.03 & 0.047 & 0.63  \\
-IL19    & \num{2.69e-3} & 0.031 & 0.63\\
+%\multirow{2}{*}{}
+Gene Symbol &
+  \multicolumn{2}{c}{KM \textit{P} value} &
+  \multicolumn{2}{c}{FDR-adjusted \textit{P} value} &
+  \multicolumn{2}{c}{Cox’s univariate HR} \\
+%  \hline
+ &
+  \multicolumn{1}{c}{TCGA} &
+  \multicolumn{1}{c}{GSE65858} &
+  \multicolumn{1}{c}{TCGA} &
+  \multicolumn{1}{c}{GSE65858} &
+  \multicolumn{1}{c}{TCGA} &
+  \multicolumn{1}{c}{GSE65858} \\
   \hline
-(values shown in dataset: GSE65858)\\
-(IL19 has two probes in RNA-Seq experiment)\\
+  \hline
+CAMK2N1 & \num{2.97e-7} & \num{6.87e-3} & \num{1.63e-5} & 0.038 & 2.101 & 1.814 \\
+IL19    & n/a           & 0.03          & n/a           & 0.047 & n/a   & 0.630  \\
+IL19    & \num{3.73e-7} & \num{2.69e-3} & \num{6.54e-6} & 0.031 & 0.472 & 0.630  \\
+FCGBP   & \num{1.21e-6} & 0.01          & \num{4.83e-5} & 0.039 & 0.484 & 0.573\\
+\hline
+  \multicolumn{7}{l}{(IL19 has two probes in RNA-Seq experiment of GSE65858)}\\
+  \multicolumn{7}{l}{(FDR: \acrlong{fdr})}\\
 \hline
 \end{tabular}%
-}
+} % end of \resizebox
 \end{table}
@@
     \bcaption{Volcano plot of genes under survival analyses of GSE65858 cohort}{
+    % GSE117973 using the same platform GPL10558
     This HNSCC cohort has been applied for filtering of our candidate genes: "CAMK2N1", "IL19" (two probes), and "FCGBP".

### 2021-06-20 Cover_letter_JPM.tex
Answer 2-3 done
lasso

@@
 \subsection*{2-3}
+% (OK)
 % [2021/06/17]
@@
 and also see Figure \ref{fig:hazards534}).
-However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11.
+However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
 There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
@@
 %(OK)
+
 We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
@@
 We appreciate the reviewer for the critical comments.
+feature selection => includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
+# For example, a group of co-regulated genes that are preferable to be taken into consideration in select features.
+ Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer.
+These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
+
+%Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
+***We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
+HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors.
+The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.
+
+%X Bayesian Robit regression method with Hyper-LASSO priors (shortened by BayesHL) for feature selection in high dimensional genomic data with grouping structure.
+%We apply BayesHL in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
+*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
+% BayesHL is immune to the problem of correlation bias.
+Other convex and non-convex methods may not be able to identify significant features when there is a high number of correlated features, due to the problem of correlation bias
+
+%coxlogit: https://www.info.ucl.ac.be/~pdupont/pdupont/pdf/MCDM_14.pdf
+The Cox proportional hazard regression and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
+Here we make use of both tasks by the Coxlogit mixed model.
+As such this approach outperforms a Cox proportional hazard model or a logistic regression, each of those models being efficient essentially on their own task\cite{Branders2014}.
+*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
+It could be overcame by assigning a consistent weight to each gene, which has been implemented in the adaptive LASSO (APLR)\cite{Algamal2015}\cite{Wu2018}.% was originally proposed to. 
+accuracy from 95\% to 97\% :-)
+
 ***  a gene signature with deep learning CNN,
@@
 or
-Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
-To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.
+% PCA of gene signature => L1/L2 penalized Cox model; L1-penalized (Lasso) Cox proportional hazard regression model (R package glmnet)
+%x Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
+%To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.
 

### 2021-06-22 Cover_letter_JPM.tex
Bayes for Answer 2.5

@@
 \newcommand{\bcaption}[2]{\caption{\textbf{#1} #2}}
+
+\usepackage{subcaption} % for figure  side by side
 
@@
 
-%Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
-***We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
+***The RLassoCox\cite{Liu2021} (bioconductor package, available at https://github.com/weiliu123/RLassoCox) trains the RLasso-Cox model based on gene expression profiles, survival information and gene interaction networks.
+It is based on the hypothesis that topologically important genes in the gene interaction network tend to have stable expression changes.
+The RLasso-Cox model uses random walk to evaluate the topological weight of genes, and then highlights topologically important genes to identify survival biomarkers for HNSCC.
+dGMMirGraph The KEGG network\cite{Simon2011}\cite{Liu2021}.
+
+%x Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
+RLassoCox\\
+We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
 HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors.
 The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.
+
+% **** [2021/06/22] by Bayes_survival.R
+The results shows
+%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
+% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
+cv.mod.candidate 62 genes are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\
+
+\begin{figure}[!tbp]
+%     % two PDF side by side \usepackage{subcaption}
+  \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf}
+        \caption{TCGA HNSCC cohort}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.5\textwidth}
+       \includegraphics[width=\textwidth]{Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf} 
+       \caption{GSE65858 HNSCC cohort}
+  \end{subfigure}
+  \caption{side by side}
+  \label{fig:Bayes62}
+\end{figure}
 
@@
 
-***  a gene signature with deep learning CNN,
-or http://gepia2.cancer-pku.cn/#index
+%***  a gene signature with deep learning CNN,
+%or http://gepia2.cancer-pku.cn/#index
 %https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
 %https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
-or
+%or
 % PCA of gene signature => L1/L2 penalized Cox model; L1-penalized (Lasso) Cox proportional hazard regression model (R package glmnet)
@@
 
-or \cite{Zhao2018}
-Prognostic gene signature:\\ % https://www.hindawi.com/journals/jir/2020/5494858/
+%or \cite{Zhao2018} Prognostic gene signature:\\ % https://www.hindawi.com/journals/jir/2020/5494858/
 
@@
 
-*** how to do? ROC
+%*** how to do? ROC
 % https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
@@
 
-***Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these primitive biomarkers.
+%***Ultimately, the gene expression profile from the GEO and OSCC cell lines and tissues were used to verify these primitive biomarkers.
 In addition, a combination of two or more biomarkers was performed to predict OSCC overall survival according to the gene expression in TCGA\cite{Huang2019}.
 
-** or using %Rplot_GSE65858_CoxHR1.5_top19.pdf
-KM estimate and Cox modeling to yield a geographically closed gene cluster:
-CAMK2N1, TIMM10, TNFAIP6, SPP1, ADAMTSL2.
+%** or using %Rplot_GSE65858_CoxHR1.5_top19.pdf
+%KM estimate and Cox modeling to yield a geographically closed gene cluster:
+%CAMK2N1, TIMM10, TNFAIP6, SPP1, ADAMTSL2.
 

### 2021-06-23 Cover_letter_JPM.tex
4 gene signature

@@
 %or http://gepia2.cancer-pku.cn/#index
+
+%cv.mod$glmnetRes$lambda.1se
+the most regularized model with cross-validation error within 1 standard deviation of the minimum.
+
+Finally, we use gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
+
+However, # 4 gene signature: #### 
+# "EZR" has \textit{P} value $>0.05$
+
+\begin{figure}
+%    \centering
+  \begin{subfigure}[b]{0.4\textwidth}
+    \includegraphics[width=8cm]{rplot_KMplot_HK1.pdf}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.4\textwidth}
+    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
+  \end{subfigure}
+    \caption{OS in TCGA for a gene signature including HK1, EZR, RRAGA, and DUSP16. Those genes have not significant survival impact if calculated individually.}
+    \label{fig:signature4}
+\end{figure}
+
 %https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
@@
 
-The risk score for each HNSCC sample was calculated based on the IRGP prognostic signature using the following formula:\\[0.5cm]
-risk score = $expression_{gene1} \times \beta_{gene1} + expression_{gene2} \times \beta_{gene2} + ... + expression_{geneX} \times \beta_{geneX}$\\
+%The risk score for each HNSCC sample was calculated based on the IRGP prognostic signature using the following formula:\\[0.5cm]
+%risk score = $expression_{gene1} \times \beta_{gene1} + expression_{gene2} \times \beta_{gene2} + ... + expression_{geneX} \times \beta_{geneX}$\\
 
@@
 
-, in which $X$ was the number of IRGPs and $\beta$ was coefficient value for each IRGPs.
+%, in which $X$ was the number of IRGPs and $\beta$ was coefficient value for each IRGPs.
 Taking the median value of risk score as the threshold, we divided all the HCC samples into high-risk or low-risk groups.
@@
 %
+\clearpage
 

### 2021-06-23 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
+Conclusion, we might build a Lasso regression model with L1 regularization to maximize the use of continuous gene expression values (without a cutoff).
+The gene signature integrating multiple genes is also a good approach for biomarker discovery.
+
 \begin{figure}
@@
     \includegraphics[width=8cm]{rplot_KMplot_HK1.pdf}
+    \caption{Kaplan-Meier plot}
   \end{subfigure}
@@
     \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
+    \caption{Volcano plot}
   \end{subfigure}
-    \caption{OS in TCGA for a gene signature including HK1, EZR, RRAGA, and DUSP16. Those genes have not significant survival impact if calculated individually.}
+
+  \caption{(a) OS in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16; (b) Those genes have not significant survival impact if calculated individually (EZR is not shown on volcano plot due to it's \textit{P} value $>0.05$)}
     \label{fig:signature4}

### 2021-06-24 Cover_letter_JPM.tex
Answer 2-5

@@
 Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
-The p-values are affected by the sample size, which should be described in the main text. % writing
+The p-values are affected by the sample size, which should be described in the main text. % writing; also affecting the over-fitting during a model training
 As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) 
@@
 
-***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size
+***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size, if combine several GSE65858 and with TCGA HNSCC 
+An increase of the sample size will decrease overfitting.
 
@@
 We appreciate the reviewer for the critical comments.
-feature selection => includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
-# For example, a group of co-regulated genes that are preferable to be taken into consideration in select features.
-Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer.
+ %=> includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
+A group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
+In the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression.
+%The dependent variables are the survival data.
+%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer.
 These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
-
-***The RLassoCox\cite{Liu2021} (bioconductor package, available at https://github.com/weiliu123/RLassoCox) trains the RLasso-Cox model based on gene expression profiles, survival information and gene interaction networks.
-It is based on the hypothesis that topologically important genes in the gene interaction network tend to have stable expression changes.
+Least Absolute Shrinkage and Selection Operation (LASSO):
+The feature selection (subsets of gene) could be done by the $L_{1}$-regularized path algorithm in LASSO regression.
+That is suggested by Branders and his colleagues\cite{Branders2014} applying on those high-dimensional data i.e., twenty thousands of features (genes) and only hundreds of sample size.
+LASSO is suitable at picking up a small signal (gene signature) through lots of noise (all protein-coding genes).
+% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html
+
+% feature selection by lasso (L1 regularization)
+% LASSO, shrinkage coefficients to zero, for selection the features
+Cross-validation is perhaps the simplest and most widely used method for select one of models at specific \lambda. % k-fold Cross-validation
+As the coefficients of logistic regression are reduced to zero by LASSO, the useless features associated with those coefficients will be omitted.
+The important features that contribute much to the model will be selected.
+Cross-validation error is calculated to find the optimal value of the regularization rate (i.e., lambda, \lambda). \lambda could control the size of a small amount of bias.
+% over-fitting causes problem
+During fitting of logistic model, it is necessary to add that small amount of bias for getting a significant drop in the variance to prevent it's over-fitting.  
+%(over-fitting is called high-variance)
+In case with over-fitting, this trained model will only perfect match every individual cases, while has higher variability to predict what it never see.
+Over-fitting could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
+
+%RLassoCox\\
+We utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://\\github.com/weiliu123/RLassoCox) for training the Cox proportional hazard regression and multinomial logistic regression models in gene expression analysis to identify a group of genes that contribute to the survival outcome of HNSCC patient.
+%and gene interaction networks (The KEGG network\cite{Simon2011}).
+% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
+% based on gene expression profiles,
+The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
+The RLassoCox make use of both tasks for gene-expression based survival analysis.
+
+% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d
+
+%in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
+%It is based on the hypothesis that topologically important genes in the gene interaction network tend to have stable expression changes.
 The RLasso-Cox model uses random walk to evaluate the topological weight of genes, and then highlights topologically important genes to identify survival biomarkers for HNSCC.
-dGMMirGraph The KEGG network\cite{Simon2011}\cite{Liu2021}.
-
-%x Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
-RLassoCox\\
-We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
-HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors.
+%dGMMirGraph The KEGG network\cite{Simon2011}\cite{Liu2021}.
+
+%HTLR\\
+%x Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data ***\cite{Jiang2020} -> citing *** \cite{Li2018d} HTLR
+%We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
+%HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors.
 The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.
+
+%coxlogit\\ 只是 Cox + LR 依照不同比例相加
+%https://www.info.ucl.ac.be/~pdupont/pdupont/pdf/MCDM_14.pdf
+%The Cox proportional hazard regression and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
+%Here we make use of both tasks by the Coxlogit mixed model.
+%As such this approach outperforms a Cox proportional hazard model or a logistic regression, each of those models being efficient essentially on their own task\cite{Branders2014}.
+
+% BayesHL (implementation is not found so far)
+%X Bayesian Robit regression method with Hyper-LASSO priors (shortened by BayesHL) for feature selection in high dimensional genomic data with grouping structure.
+%We apply BayesHL in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
+%*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
+%=> Ridge regression 才是
+%L2 regularization or Ridge regression. As the parameters "tend to zero" 不是 feature selection (all preserved)
+%It could be overcame by assigning a consistent weight to each gene, which has been implemented in the adaptive LASSO (APLR)\cite{Algamal2015}\cite{Wu2018}.% was originally proposed to. 
+% only boost accuracy from 95\% to 97\% :-)
+% BayesHL is immune to the problem of correlation bias.
+Other convex and non-convex methods may not be able to identify significant features when there is a high number of correlated features, due to the problem of correlation bias
+
+%***  a gene signature with deep learning CNN, convolutional neural network
+%or http://gepia2.cancer-pku.cn/#index
+
+%# Logistics Regression
+%# family = binomial 
+%# it assumes a linear relationship between link function (***maximum likelihood; likelihood = odds) and independent variables in logit model
+%# p(X)(1−p(X)) the odds ratio
+%# logit = log(P(x)/(1-P(x))) = β0+β1X
+%# l(β0,β1)=p(X)(1−p(X))
 
@@
 The results shows
+%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
+#Calculating Cox p-value...Done [2021/06/22] 19:42
+#Performing directed random walk...Done
+#Performing cv.glmnet...Done
+#code inside: fit.lasso <- glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
 %Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
 % Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
-cv.mod.candidate 62 genes are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\
+the selected features (62 genes) are selected by their (non-zero) coefficients. 
+%cv.mod.candidate 62 genes 
+However, they are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\
 
@@
 
-%X Bayesian Robit regression method with Hyper-LASSO priors (shortened by BayesHL) for feature selection in high dimensional genomic data with grouping structure.
-%We apply BayesHL in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
-*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
-% BayesHL is immune to the problem of correlation bias.
-Other convex and non-convex methods may not be able to identify significant features when there is a high number of correlated features, due to the problem of correlation bias
-
-%coxlogit: https://www.info.ucl.ac.be/~pdupont/pdupont/pdf/MCDM_14.pdf
-The Cox proportional hazard regression and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
-Here we make use of both tasks by the Coxlogit mixed model.
-As such this approach outperforms a Cox proportional hazard model or a logistic regression, each of those models being efficient essentially on their own task\cite{Branders2014}.
-*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
-It could be overcame by assigning a consistent weight to each gene, which has been implemented in the adaptive LASSO (APLR)\cite{Algamal2015}\cite{Wu2018}.% was originally proposed to. 
-accuracy from 95\% to 97\% :-)
-
-%***  a gene signature with deep learning CNN,
-%or http://gepia2.cancer-pku.cn/#index
-
+% accuracy for the classification in case-control study (or ROC, AUC)
+% **** C-index, concordance index for survival data (with censoring)
+the Harrell concordance index (C-index) (1996) is the standard performance metric for model assessment in survival analysis with censored data.
+%The predictive performances are computed in terms of C-index for the survival prediction.
+
+% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
+the left vertical line in the plot shows us where the cross-validation error curve hits its minimum. 
+The right vertical line shows us the most regularized model with the cross-validation error within 1 standard deviation of the minimum.
+% in lambda 1se
 %cv.mod$glmnetRes$lambda.1se
 the most regularized model with cross-validation error within 1 standard deviation of the minimum.
-
-Finally, we use gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
+It selects 14 genes,
+according to the \textit{P} value, 4 gene signature: HK1, EZR, RRAGA, and DUSP16.
+
+% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
+Finally, we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
 

### 2021-06-25 Cover_letter_JPM.tex
Updates from Overleaf

@@
  %=> includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
-A group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
-In the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression.
+Since we have tried to integrate multiple genes in survival analysis, a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
+Searching about the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression.
 %The dependent variables are the survival data.
@@
 These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
-Least Absolute Shrinkage and Selection Operation (LASSO):
-The feature selection (subsets of gene) could be done by the $L_{1}$-regularized path algorithm in LASSO regression.
-That is suggested by Branders and his colleagues\cite{Branders2014} applying on those high-dimensional data i.e., twenty thousands of features (genes) and only hundreds of sample size.
-LASSO is suitable at picking up a small signal (gene signature) through lots of noise (all protein-coding genes).
+%Least Absolute Shrinkage and Selection Operation (LASSO):
+Branders and his colleagues\cite{Branders2014} have suggested that regularization of regression model should be applied on analysis of the high-dimensional data, i.e.
+twenty thousands of features (genes) and only hundreds of sample size.
+The $L_{1}$-regularized path algorithm by Least Absolute Shrinkage and Selection Operation (LASSO) regression could perform feature selection (a subset of gene).
+LASSO is suitable at picking up a small signal (gene signature) through lots of noise (twenty thousands of protein-coding genes).
 % R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html
-
+Our approach is to build a logistic regression model for the prediction of patient's survival.
+% over-fitting causes problem
+% During fitting of logistic model, 
+Beside feature selection,
+it is also necessary to add that small amount of bias (lambda, $\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
+$\lambda$ could control the amount of bias dealing with over-fitting.
+%(over-fitting is called high-variance)
+In such a case, over-fitted model will only perfectly match every individual cases, and has higher variability to predict what it never see.
+Over-fitting will limit usefulness of the model in it's generalization, and could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
 % feature selection by lasso (L1 regularization)
 % LASSO, shrinkage coefficients to zero, for selection the features
-Cross-validation is perhaps the simplest and most widely used method for select one of models at specific \lambda. % k-fold Cross-validation
-As the coefficients of logistic regression are reduced to zero by LASSO, the useless features associated with those coefficients will be omitted.
-The important features that contribute much to the model will be selected.
-Cross-validation error is calculated to find the optimal value of the regularization rate (i.e., lambda, \lambda). \lambda could control the size of a small amount of bias.
-% over-fitting causes problem
-During fitting of logistic model, it is necessary to add that small amount of bias for getting a significant drop in the variance to prevent it's over-fitting.  
-%(over-fitting is called high-variance)
-In case with over-fitting, this trained model will only perfect match every individual cases, while has higher variability to predict what it never see.
-Over-fitting could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
-
+% perhaps the simplest and 
+Cross-validation error is calculated to find the optimal value of $\lambda$.
+%Cross-validation is most widely used method for select one of models at specific regularization rate (i.e. lambda, \lambda) during the model fitting.
+% k-fold Cross-validation
+As the coefficients of logistic regression are reduced to zero by LASSO, %the useless features (genes) associated with those coefficients will be omitted.
+the important features that contribute much to the model will be selected under that optimal value of $\lambda$.
+
+% multinomial
 %RLassoCox\\
-We utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://\\github.com/weiliu123/RLassoCox) for training the Cox proportional hazard regression and multinomial logistic regression models in gene expression analysis to identify a group of genes that contribute to the survival outcome of HNSCC patient.
+We have utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) for training the Cox proportional hazard regression and logistic regression models in gene expression analysis to identify a group of genes that contribute to survival outcome of HNSCC patient.
 %and gene interaction networks (The KEGG network\cite{Simon2011}).
@@
 % based on gene expression profiles,
-The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
-The RLassoCox make use of both tasks for gene-expression based survival analysis.
-
+%The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
+The RLassoCox make use of both Cox and LASSO logistic regression for gene-expression based survival analysis.
+The model training has been performed under 10-fold cross-validation.
 % medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d
@@
 The results shows
+% k-fold Cross-validation
 %[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
@@
 #Performing cv.glmnet...Done
-#code inside: fit.lasso <- glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
+#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
 %Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
@@
 the selected features (62 genes) are selected by their (non-zero) coefficients. 
-%cv.mod.candidate 62 genes 
-However, they are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\
+%cv.mod.candidate has 62 genes 
+However, they are performed poor either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\
 
@@
 \bibliographystyle{unsrt} %model1-num-names}
-\bibliography{TCGA_margin_cutoff.bib}
+\bibliography{TCGA_margin_cutoff.bib, Deep_Learning.bib}
 

### 2021-06-25 Cover_letter_JPM.tex
Answer 2-5 done (2021/06/25)

@@
 \usepackage{xcolor}
-
+%\usepackage[table,xcdraw]{xcolor}
 \newenvironment{MyColorPar}[1]{%
@@
 We appreciate the reviewer for the critical comments.
- %=> includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
 Since we have tried to integrate multiple genes in survival analysis, a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
@@
 We have utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) for training the Cox proportional hazard regression and logistic regression models in gene expression analysis to identify a group of genes that contribute to survival outcome of HNSCC patient.
-%and gene interaction networks (The KEGG network\cite{Simon2011}).
+% RLassoCox includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
+% gene interaction networks (The KEGG network\cite{Simon2011}).
 % data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
@@
 % **** [2021/06/22] by Bayes_survival.R
-The results shows
 % k-fold Cross-validation
 %[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
-#Calculating Cox p-value...Done [2021/06/22] 19:42
-#Performing directed random walk...Done
-#Performing cv.glmnet...Done
-#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
+%#Calculating Cox p-value...Done [2021/06/22] 19:42
+%#Performing directed random walk...Done
+%#Performing cv.glmnet...Done
+%#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
 %Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
 % Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
-the selected features (62 genes) are selected by their (non-zero) coefficients. 
 %cv.mod.candidate has 62 genes 
-However, they are performed poor either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\
+The results shows the selected features (62 genes) distributing on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}).
 
@@
   \end{subfigure}
-  \caption{side by side}
+  \caption{The 62 genes (listed on the right) have been discovered by LASSO regression in (a) TCGA HNSCC and (b) GSE65858 HNSCC cohort. \textcolor{red}{Red}-square marked genes are our 3 candidates.}
   \label{fig:Bayes62}
@@
 
-% accuracy for the classification in case-control study (or ROC, AUC)
+% C-index = 0.68 in this model fitting
+%accuracy for the classification in case-control study (or ROC, AUC)
 % **** C-index, concordance index for survival data (with censoring)
-the Harrell concordance index (C-index) (1996) is the standard performance metric for model assessment in survival analysis with censored data.
+%the Harrell concordance index (C-index) (1996) is the standard performance metric for model assessment in survival analysis with censored data.
 %The predictive performances are computed in terms of C-index for the survival prediction.
@@
 % Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
-the left vertical line in the plot shows us where the cross-validation error curve hits its minimum. 
-The right vertical line shows us the most regularized model with the cross-validation error within 1 standard deviation of the minimum.
+%the left vertical line in the plot shows us where the cross-validation error curve hits its minimum.
+%The final gene signature has been selected, including 4 genes, named HK1, EZR, RRAGA, and DUSP16 .; fentastic4
+% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
+LASSO calculate the (non-zero) coefficients of features, while the 62 genes hit the minimum of cross-validation error.
 % in lambda 1se
 %cv.mod$glmnetRes$lambda.1se
-the most regularized model with cross-validation error within 1 standard deviation of the minimum.
-It selects 14 genes,
-according to the \textit{P} value, 4 gene signature: HK1, EZR, RRAGA, and DUSP16.
-
-% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
-Finally, we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
-
-However, # 4 gene signature: #### 
-# "EZR" has \textit{P} value $>0.05$
-
-Conclusion, we might build a Lasso regression model with L1 regularization to maximize the use of continuous gene expression values (without a cutoff).
-The gene signature integrating multiple genes is also a good approach for biomarker discovery.
-
-\begin{figure}
+We have further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
+According to their \textit{P} values (please see Table \ref{tab:signature4}), 
+we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
+DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1 in volcano plot of TCGA HNSCC.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{graphicx}
+% \usepackage[table,xcdraw]{xcolor}
+% {\color[HTML]{FE0000} 0.002}  
+% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+% Please add the following required packages to your document preamble:
+
+\begin{table}[ht]
+\centering
+\caption{The most LASSO regularized logistic model under cross-validation. Genes with positive coefficient will increase the patient's risk, while negative reduce it.\\
+    (\textcolor{red}{red}-marked logistic \textit{P} value $< 0.05$)}
+\label{tab:signature4}
+\begin{tabular}{lrr}
+\textbf{Gene Symbol} & \textbf{Coefficients} &  \textbf{\textit{P} value} \\ \hline
+\textbf{POLR2C}      & 0.870                 & 0.150                              \\
+\textbf{EFNB2}       & 0.189                 & 0.521                              \\
+\textbf{PLAU}        & -0.189                & 0.408                              \\
+\textbf{HK1}         & 1.413                 & \textcolor{red}{0.002}       \\
+\textbf{WNT7A}       & 0.211                 & 0.111                              \\
+\textbf{HPRT1}       & 0.620                 & 0.113                              \\
+\textbf{APP}         & 0.219                 & 0.538                              \\
+\textbf{SC5DL}       & 0.262                 & 0.367                              \\
+\textbf{EZR}         & 0.973                 & \textcolor{red}{0.017}       \\
+\textbf{RRAGA}       & 0.925                 & \textcolor{red}{0.022}       \\
+\textbf{S1PR4}       & -0.368                & 0.052                              \\
+\textbf{DUSP16}      & -0.745                & \textcolor{red}{0.035}       \\
+\textbf{SH3BP2}      & -0.606                & 0.107                             
+\end{tabular}
+\end{table}
+
+%%%
+
+\begin{figure}[ht]
 %    \centering
-  \begin{subfigure}[b]{0.4\textwidth}
-    \includegraphics[width=8cm]{rplot_KMplot_HK1.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \includegraphics[width=6cm]{rplot_KMplot_HK1.pdf}
     \caption{Kaplan-Meier plot}
@@
   \hfill
-  \begin{subfigure}[b]{0.4\textwidth}
+  \begin{subfigure}[b]{0.5\textwidth}
     \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
@@
   \end{subfigure}
-
-  \caption{(a) OS in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16; (b) Those genes have not significant survival impact if calculated individually (EZR is not shown on volcano plot due to it's \textit{P} value $>0.05$)}
+%However, # 4 gene signature: #### 
+%# "EZR" has \textit{P} value $>0.05$
+  \caption{(a) OS in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) Those genes (listed on the rigth side) have not significant hazard ratio (HR) if calculated individually (EZR is not shown on volcano plot due to it's Kaplan-Meier \textit{P} value $>0.05$)}
     \label{fig:signature4}
 \end{figure}
+
+In conclusion, we might build a Lasso regression model with LASSO regularization to maximize the use of continuous gene expression values (without the need of a cutoff).
+The gene signature integrating multiple genes is also a good approach for biomarker discovery.
+However, the resulting candidates could be influenced by proper "gene interaction network" applied for model building.
+% gene signature
+RLassoCox package works on the basis of gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
+RLassoCox utilizes Kyoto Encyclopedia of Genes and Genomes (KEGG) network\cite{Simon2011} as the reference of gene interaction networks, constructed by the R package "iSubpathwayMiner".
+% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
 

### 2021-06-25 Cover_letter_JPM.tex
Updates from Overleaf

@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
@@
     Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
-    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
+    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.
+    The 22 genes, listed on the side, have hazard ratio between 0.6 and 1.5.\\
     Remarks:\\
@@
     % GSE117973 using the same platform GPL10558
-    This HNSCC cohort has been applied for filtering of our candidate genes: "CAMK2N1", "IL19" (two probes), and "FCGBP".
-    There are 270 HNSCC participants involved in this cohort.
-    The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30330.
+    This HNSCC cohort has been applied for filtering of our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
     Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
-    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0;
-    \textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
-    The 22 gene symbol listed on the side: hazard ratio $> 1.8$ or $< 0.6$.\\
-    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);
-    Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
+    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0);
+    (\textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
+    The 22 genes, listed on the side, have hazard ratio $> 1.8$ or $< 0.6$.\\
+    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value with log10 transformed);
+    (Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
     }
@@
 
-We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
+We modified the paragraphs in the "Material and Methods" section and "Results" section for the analysis of GSE65858.
+We also described "the \textit{P} values are affected by the sample size" in the Discussion section.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
@@
 \begin{MyColorPar}{red}
-
-***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size, if combine several GSE65858 and with TCGA HNSCC 
-An increase of the sample size will decrease overfitting.
 
@@
 [materials and methods]
-National Center for Biotechnology Information Reference Sequence (NCBI) 
+
 %RefSeq Release 38 (November 7, 2009)
-Gene Expression Omnibus (GEO)
-[Dataset]
-The NCBI GEO repositories is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
-R package of GEOquery\cite{Sean2007}: SOFT file (or MINiML) was used to
-download RNA-Seq dataset of HNSCC, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE65858). 
-GSE65858\cite{Wichmann2015} has OS event and RFS event and survival time.
+
+%[Dataset]
+The Gene Expression Omnibus (GEO) database, founded by National Center for Biotechnology Information Reference Sequence (NCBI), is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
+R package of GEOquery\cite{Sean2007} was used to
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE65858). 
+GSE65858\cite{Wichmann2015} has OS event, RFS event and survival time.
+There are 270 HNSCC participants involved in this cohort.
+%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
 %n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
-The expression data was generated using the HumanHT-12 v4 Expression BeadChip, which targets on more than 31,000 annotated genes (47,000 probes) derived from the \acrfull{ncbi} Reference Sequence (RefSeq) Release 38 (November 7, 2009).
-% an Affymetrix Human Genome U133A microarray (HG-U133A). 
-It has been used as a dataset for candidate selection. \\
+The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrfull{ncbi} Reference Sequence, release 38 on November 7, 2009).
+% (RefSeq)
+GSE65858 has been used as a dataset for selection of our candidates. \\
+
+[Results]
+TCGA HNSCC cohort has been applied for exploration of the candidate biomarkers.
+Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
+The 10 genes, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
+The other ten genes were over-expressed in the better survival patients (with hazard ratio <=0.5), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
+
+CAMK2N1, IL19, FCGBP and the other 17 genes have hazard ratio (HR) $> 1.8$ or $< 0.6$.
+
+%During our exploration phase with TCGA cohort, the 20 genes, listed
+%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
+%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
+%}
+in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
+%
+% [2021/06/13-17] GSE65858
+%CAMK2N1, IL19, and FCGBP is validated by
+%candidate_fdr100
+%PvalueTex consensus with GSE2837 to yield 3 candidates
+In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
+% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
+%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
+%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
+%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
+%IL19    0.03390   0.04738901    0.630   6.543871e-06
+%IL19    0.00269  0.03068073 0.630  6.543871e-06
+%candidate_fdr100
+and also see Figure \ref{fig:hazards534}).
+However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
+This HNSCC cohort has been applied for filtering of our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
+    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
+    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0);
+    (\textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
+    The 22 genes, listed on the side, have hazard ratio $> 1.8$ or $< 0.6$.\\
+However, these 22 genes have hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC.
+There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
+The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
+
+[Discussion]
+***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size, if combine several GSE65858 and with TCGA HNSCC 
+An increase of the sample size will decrease overfitting.
 
@@
 
-***
-Third, dissection of ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) due to heterogeneity of 20500 RNA-Seq expression data files.
-# deal with return(1), return(2) and return(3) errors, try to solve it
-32.2\% error01, ZSWIM2 skip from contingencyTCGA(), it is one group issue in Melt() function.
-21.05\% errors in  one group in survdiff on KM cutofFinder_func.R.
-0.78\%(159 genes) for unknown reason
+% dissection
+%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
+Third, we have analyzed the error log of the cutoff finding and Cox modeling, 
+the results shows that several situations could halt the program running.
+It includes:
+\begin{outline}
+\1 32.2\% event has one group issue in confusion matrix of Chi-square test in Cox regression
+\1 21.05\% errors occur by one group issue in log-rank test (survdiff function in R package "survival") in Kaplan-Meier estimate
+\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow)
+\end{outline}
+, which could not be detected prior to the program running.
+It might be due to heterogeneity of 20500 RNA-Seq expression data.
+%# deal with return(1), return(2) and return(3) errors, try to solve it
+%32.2\% error01, ZSWIM2 skip from contingencyTCGA(), it is one group issue in Melt() function.
+%21.05\% errors in  one group in survdiff on KM cutofFinder_func.R.
+%0.78\%(159 genes) for unknown reason
 %# _marginS_
@@
 
-more in discussion
-2-3 supplementary figure Rplot_pvaluePlot_NDFIP1.pdf
-iscussion about sliding-window pvalueTex to find the more potential candidate (weak or not weak could be double-checked by GSE65858)
+more in discussion section:
+from Answer 2-3 supplementary figure Rplot_pvaluePlot_NDFIP1.pdf
+discussion about sliding-window pvalueTex to find the more potential candidate (weak or not weak could be double-checked by GSE65858)
 

### 2021-06-26 Cover_letter_JPM.tex
Updates from Overleaf

@@
 \subsection*{2-3}
-% (OK)
+% ( ) not yet for discussion 1) sample size/effect size; 2) ***NDFIP1
 % [2021/06/17]
@@
 Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
-The p-values are affected by the sample size, which should be described in the main text. % writing; also affecting the over-fitting during a model training
+The p-values are affected by the sample size, which should be described in the main text. % writing (ok) [2021/06/26]; also affecting the over-fitting during a model training
 As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) 
@@
 We have introduced an independent HNSCC cohort (GSE65858, with RNA-Seq expression data) for helping in candidate selection.
+We have also performed Kaplan-Meier and Cox survival analyses, under the cutoff of each gene expression at their median value.
 %We further
@@
 %[Dataset]
-The Gene Expression Omnibus (GEO) database, founded by National Center for Biotechnology Information Reference Sequence (NCBI), is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
+The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
 R package of GEOquery\cite{Sean2007} was used to
-download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE65858). 
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
 GSE65858\cite{Wichmann2015} has OS event, RFS event and survival time.
@@
 %n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
-The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrfull{ncbi} Reference Sequence, release 38 on November 7, 2009).
+The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on November 7, 2009).
 % (RefSeq)
-GSE65858 has been used as a dataset for selection of our candidates. \\
+GSE65858 is a dataset for candidate selection in our workflow.
+We have also performed Kaplan-Meier and Cox survival analyses, under the cutoff of each gene expression at their median value.\\
 
 [Results]
-TCGA HNSCC cohort has been applied for exploration of the candidate biomarkers.
+TCGA HNSCC cohort has been applied for exploration of the biomarker candidate
 Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
-The 10 genes, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
-The other ten genes were over-expressed in the better survival patients (with hazard ratio <=0.5), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
-
-CAMK2N1, IL19, FCGBP and the other 17 genes have hazard ratio (HR) $> 1.8$ or $< 0.6$.
-
+%The 10 genes, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
+%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
+Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
 %During our exploration phase with TCGA cohort, the 20 genes, listed
@@
 %}
-in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
-%
+%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
+
 % [2021/06/13-17] GSE65858
@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
@@
 and also see Figure \ref{fig:hazards534}).
-However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
-This HNSCC cohort has been applied for filtering of our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
-    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
-    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0);
-    (\textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
-    The 22 genes, listed on the side, have hazard ratio $> 1.8$ or $< 0.6$.\\
-However, these 22 genes have hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC.
-There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
-The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
+However, the significance of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
+This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
+Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
+Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the HNSCC biomarker.
+%The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
 
 [Discussion]
-***...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size, if combine several GSE65858 and with TCGA HNSCC 
-An increase of the sample size will decrease overfitting.
+[more in the discussion section]
+1) 
+Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
+The effect size is the magnitude of the difference (or relationship) among comparing groups.
+%A \textit{P} value is a tool to help interpret findings from biomedical research.
+%In reporting and interpreting studies, both 
+%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
+While statistical significance can inform the researcher whether an effect exists, 
+the \textit{P} value will not directly tell the effect size.
+%The effect size is the main finding of a quantitative study.
+%Statistical significance depends upon both sample size and effect size. 
+The effect size is independent of the sample size\cite{Sullivan2012}.
+
+%When we increase the sample size, the standard error decrease
+%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
+The larger the sample the more likely a difference to be accepted (i.e. \textit{P} value $< 0.05$), due to the decrease of the standard error\cite{Sullivan2012}.
+However, the small effect size (non-zero) is often meaningless (substantive insignificance).
+%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
+%, that is, when the effect size is exactly zero; 
+%yet very small differences, even if significant, are often meaningless. 
+%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
+%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
+Conversely, an effect size can be large, but fail to get statistical significance if the sample size is small. In this scenario, the \textit{P} value tells the effect does not exist.
+
+The \textit{P} value could be also impacted by error.
+\begin{outline}
+\1 A random error, defined as variability in data, is not considered a bias but rather occurs random across the entire study population and can distort the measurement process (e.x.
+RNA-Seq experiments).
+The larger sample size could reduce the random error. 
+\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
+It could deleteriously impact the statistical significance.
+The larger sample size could not affect the systematic error.
+\end{outline}
+Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has small \textit{P} value\cite{Thiese2016}.
+
+As skewed cutoff that split 425 vs 75 between the two groups, it will also get statistical significance by increasing effect size intentionally.
+% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
+%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
+%effect size, sample size, cutoff 影響 p value!
+
+% [preserved] ***
+%An increase in the sample size will decrease over-fitting of model[Frank Harrell].
+% https://hbiostat.org/rms/
+
+% definition of P value
+%Statistical significance is the probability that the observed difference between two groups is due to chance.
+If the P value is larger than the alpha level chosen (e.x.
+0.05), any observed difference is assumed to be explained by sampling variability.
+%The most commonly used α level is 0.05, as proposed by Fischer, is the amount of type I error you are willing to accept.
+%Fisher suggested 5\% (α=0.05) level could be used for concluding that fairly strong evidence exists against H0, that is 1 out of 20 times you will be wrong and by random chance there is no difference between your groups, but the data you have suggests that there is (2).
+
+%power: Power analysis is the name given to the process for determining the sample size for a research study.
+The technical definition of power is that it is the probability of detecting a "true" effect when it exists.
+Many students think that there is a simple formula for determining sample size for every research situation.
+%As the sample size gets larger, the z value increases therefore we will more likely to reject the null hypothesis; less likely to fail to reject the null hypothesis, thus the power of the test increases.
+
+%the confidence interval of the P value (second generation P value?)
+
+%%%%
+
+2)
+cutoff at optimal by sliding-window or just median:
+when \textit{P} value $<0.05$, the gene number: 9416 , 534 %差別很大，張大網
+run code: if median cut for TCGA KM Cox (by pvalueTex or *** RLassoCox Bayes code) 9416 -> ???
+discussion about sliding-window pvalueTex to find the more potential candidate, while small effect size could be double-checked by GSE65858.
+(  )2-3 put in supplementary figure Rplot_pvaluePlot_NDFIP1.pdf
+%列入 workflow in materials and methods;
+
+***NDFIP1
+a special case of NDFIP1 gene; % 給他們一個機會
+(ok) Answer 2-1 %加入 discussion
+( )  Answer 2-3 supplementary  %圖就好 figure Rplot_pvaluePlot_NDFIP1.pdf
+
+For example, a gene NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile cutoff, could achieve a \textit{P} value of \num{1e-6} at 70\% quantile cutoff.
+NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233}.
+However, it fails as the candidate by inadequate effect size (HR = ??).
+% (ok) Answer 2-1 加入 discussion
+According to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
+Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in
+supplementary figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233}.
+%Rplot_pvaluePlot_NDFIP1.pdf
+%  to find cases_OS outside of range 180-220 (== cutoff not at median)
+%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
+% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
+%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
+%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
+%# NDFIP1 (within our 20 preliminary candidates), 
+In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
+%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
+Indeed, it needs to be validated by the other independent cohort (e.x. GSE65858).
 
@@
 
-more in discussion section:
-from Answer 2-3 supplementary figure Rplot_pvaluePlot_NDFIP1.pdf
-discussion about sliding-window pvalueTex to find the more potential candidate (weak or not weak could be double-checked by GSE65858)
-
 \end{MyColorPar} % end of red
@@
 
-Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and NCBI Gene Expression Omnibus (GEO) datasets (e.x.
+Although other databases carrying HNSCC genomics and clinical data we found, such as MSKCC (151 cases), Broad (74 cases), Johns Hopkins (32 cases), MD Anderson (40 cases), and \acrshort{ncbi} Gene Expression Omnibus (GEO) datasets (e.x.
 GSE2837, 40 cases; GSE6631, 22 cases; GSE31056, 23 cases)\cite{Cerami2012b}\cite{Gao2013a}.

### 2021-06-27 Cover_letter_JPM.tex
Updates from Overleaf

@@
 [more in the discussion section]
-1) 
+1) % (ok)
 Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
@@
 
-As skewed cutoff that split 425 vs 75 between the two groups, it will also get statistical significance by increasing effect size intentionally.
+If a skewed cutoff that split, for example, 425 vs 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
 % https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
@@
 
-2)
+2) in TCGA HNSCC cohort, 
 cutoff at optimal by sliding-window or just median:
-when \textit{P} value $<0.05$, the gene number: 9416 , 534 %差別很大，張大網
-run code: if median cut for TCGA KM Cox (by pvalueTex or *** RLassoCox Bayes code) 9416 -> ???
+when unadjusted \textit{P} value $<0.05$, the gene number: 9416 to 3118, 534 to 209.
+Result by median cutoff: total 20080 genes 
+%3118 are raw KM P value < 0.05; 
+%209 genes are FDR KM P value <0.05
+*** IL19 is excluded by this way :-) (special S-curve P value plot)
+%差別很大，張大網
+%([2021/06/27] run code: if median cut for TCGA KM Cox by *** pvalueTex code)
 discussion about sliding-window pvalueTex to find the more potential candidate, while small effect size could be double-checked by GSE65858.
-(  )2-3 put in supplementary figure Rplot_pvaluePlot_NDFIP1.pdf
+(  )2-3 put in supplementary figure %Rplot_pvaluePlot_NDFIP1.pdf
 %列入 workflow in materials and methods;
 
+% ****** IL19 必須要靠 pvalueTex 才能發現
+\textit{P} value plot with a acute S-curve bending on the median zone, it lets the FDR-KM \textit{P} value has large difference between median cutoff (\num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.1154315}) and optimal cutoff (\num{6.54e-6}).
+A sliding-window selection of cutoffs could boost their statistic significance to pass the correction by even FDR or Bonferroni methods.
+%> gene_labeled_golden[!gene_labeled_golden %in% fdr100_KMsurvival$Gene.Symbol[fdr100_KMsurvival$FDR.Pvalue<0.05]]
+[1] "IL19"
 ***NDFIP1
-a special case of NDFIP1 gene; % 給他們一個機會
+the special cases of gene, such as NDFIP1, DKC1, PNMA5, and NPB % ; % 給他們一個機會
 (ok) Answer 2-1 %加入 discussion
@@
 scientific-notation=true]{0.0001074233}.
-However, it fails as the candidate by inadequate effect size (HR = ??).
+However, it fails as the candidate by less effect size (HR = 1.33 in GSE65858 cohort, comparing with HR = 2.027 in TCGA cohort).
 % (ok) Answer 2-1 加入 discussion
@@
 Third, we have analyzed the error log of the cutoff finding and Cox modeling, 
-the results shows that several situations could halt the program running.
+the results shows that several technique problems could halt the program running.
 It includes:
 \begin{outline}
-\1 32.2\% event has one group issue in confusion matrix of Chi-square test in Cox regression
-\1 21.05\% errors occur by one group issue in log-rank test (survdiff function in R package "survival") in Kaplan-Meier estimate
+
+\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression
+\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate.
+%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
+%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
+% error at 16115 gene ""; why? 518 values all are -0.04203 at T
+%  There is only 1 group 
+%This is because of skewed distribution of the expression value. 
+% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
+% all cases belong to >= median => 改為 > median 即可
+% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
+% median = NaN :-); 
+% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
+% and NaN imputation as median
 \1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow)
@@
 , which could not be detected prior to the program running.
-It might be due to heterogeneity of 20500 RNA-Seq expression data.
+It might be due to skewed distribution of the expression value in 20500 RNA-Seq  data. % heterogeneity
 %# deal with return(1), return(2) and return(3) errors, try to solve it

### 2021-06-27 Cover_letter_JPM.tex
Updates from Overleaf

@@
     This cohort has been applied for exploration of the candidate biomarkers.
-    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
+    Total 9416 genes has %\acrshort{fdr}-
+    unadjusted \textit{P} value less than 0.05.
     \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.
@@
 TCGA HNSCC cohort has been applied for exploration of the biomarker candidate
-Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
+Total 9416 genes has %\acrshort{fdr}-
+unadjusted \textit{P} value less than 0.05.
+The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
 %The 10 genes, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
@@
 cutoff at optimal by sliding-window or just median:
-when unadjusted \textit{P} value $<0.05$, the gene number: 9416 to 3118, 534 to 209.
-Result by median cutoff: total 20080 genes 
-%3118 are raw KM P value < 0.05; 
-%209 genes are FDR KM P value <0.05
+when unadjusted \textit{P} value $<0.05$, the gene number: 6284 vs. 3118, 967 vs. 209.
+% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
+Result by optimal cutoff: total 9416 plots,
+6284 are raw KM P value < 0.05
+534?? genes are FDR KM P value <0.05
+967 genes which HR is greater than 1.5 or less than 0.5.
+Result by median cutoff: total 20080 genes, 
+3118 are raw KM P value < 0.05; 
+209 genes are FDR KM P value <0.05
 *** IL19 is excluded by this way :-) (special S-curve P value plot)

### 2021-06-27 Cover_letter_JPM.tex
Answers done (draft0

@@
 
-[materials and methods]
-
+[materials and methods]\\
 %RefSeq Release 38 (November 7, 2009) 
-
 %[Dataset]
@@
 
-[Results]
+[Results]\\
 TCGA HNSCC cohort has been applied for exploration of the biomarker candidate
@@
 
-[Discussion]
-[more in the discussion section]
-1) % (ok)
+[Discussion]\\
+%[more in the discussion section]
+1) \\% (ok)
 Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
@@
 %%%%
-
-2) in TCGA HNSCC cohort, 
-cutoff at optimal by sliding-window or just median:
-when unadjusted \textit{P} value $<0.05$, the gene number: 6284 vs. 3118, 967 vs. 209.
+%(ok)2-3 put in supplementary figure S1 %Rplot_pvaluePlot_NDFIP1.pdf
+%from Answer 2-3 supplementary Figure S1  %圖就好 figure Rplot_pvaluePlot_NDFIP1.pdf
+
+2) \\
+( ) % pvalueTex is essential
+There is benefit of using sliding-window cutoff method in survival analysis of TCGA HNSCC cohort.
+We have compared the results of cutoff at optimal by sliding-window or just at median of gene expression.
+It shows
+the gene number with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively.
+After FDR-correction, it shows 967 vs. 209, respectively.
 % HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
-Result by optimal cutoff: total 9416 plots,
-6284 are raw KM P value < 0.05
-534?? genes are FDR KM P value <0.05
-967 genes which HR is greater than 1.5 or less than 0.5.
-Result by median cutoff: total 20080 genes, 
-3118 are raw KM P value < 0.05; 
-209 genes are FDR KM P value <0.05
-*** IL19 is excluded by this way :-) (special S-curve P value plot)
+%Result by optimal cutoff: total 9416 plots,
+%6284 are raw KM P value < 0.05
+%534?? genes are FDR KM P value <0.05
+%967 genes which HR is greater than 1.5 or less than 0.5.
+%Result by median cutoff: total 20080 genes, 
+%3118 are raw KM P value < 0.05; 
+%209 genes are FDR KM P value <0.05
+The sliding-window cutoff method could catch more potential candidates (\textit{P} values far less than $0.001$) for Cox's modeling at next stage in our workflow.
+These preliminary candidates must be validated by Bonferroni correction and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
+
+%small effect size could be double-checked by GSE65858.
 %差別很大，張大網
 %([2021/06/27] run code: if median cut for TCGA KM Cox by *** pvalueTex code)
-discussion about sliding-window pvalueTex to find the more potential candidate, while small effect size could be double-checked by GSE65858.
-(  )2-3 put in supplementary figure %Rplot_pvaluePlot_NDFIP1.pdf
 %列入 workflow in materials and methods;
 
-% ****** IL19 必須要靠 pvalueTex 才能發現
-\textit{P} value plot with a acute S-curve bending on the median zone, it lets the FDR-KM \textit{P} value has large difference between median cutoff (\num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.1154315}) and optimal cutoff (\num{6.54e-6}).
-A sliding-window selection of cutoffs could boost their statistic significance to pass the correction by even FDR or Bonferroni methods.
-%> gene_labeled_golden[!gene_labeled_golden %in% fdr100_KMsurvival$Gene.Symbol[fdr100_KMsurvival$FDR.Pvalue<0.05]]
-[1] "IL19"
-***NDFIP1
-the special cases of gene, such as NDFIP1, DKC1, PNMA5, and NPB % ; % 給他們一個機會
-(ok) Answer 2-1 %加入 discussion
-( )  Answer 2-3 supplementary  %圖就好 figure Rplot_pvaluePlot_NDFIP1.pdf
-
-For example, a gene NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile cutoff, could achieve a \textit{P} value of \num{1e-6} at 70\% quantile cutoff.
+We will explain above mentioned by two examples.
+%***NDFIP1  % 給他們一個機會
+Reviewing the special cases of gene, such as NDFIP1, DKC1, PNMA5, and NPB,
+we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
 NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233}.
-However, it fails as the candidate by less effect size (HR = 1.33 in GSE65858 cohort, comparing with HR = 2.027 in TCGA cohort).
+scientific-notation=true]{0.0001074233} (please see supplementary figure S1). % it is \ref{fig:pvaluePlot_NDFIP1
+%Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
+%After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures, scientific-notation=true]{0.0001074233}.
+% the effect size
+Although it has failed to compete as a candidate by less effect size (HR = 1.33) in GSE65858 cohort, compared with one (HR = 2.027) in TCGA cohort%.
+, and the other (HR = 1.42) in GSE2837 cohort.
 % (ok) Answer 2-1 加入 discussion
-According to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
-Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in
-supplementary figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233}.
+%According to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
+
 %Rplot_pvaluePlot_NDFIP1.pdf
@@
 %# NDFIP1 (within our 20 preliminary candidates), 
-In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
+%In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
 %Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
-Indeed, it needs to be validated by the other independent cohort (e.x. GSE65858).
+%Indeed, it needs to be validated by the other independent cohort (e.x. GSE65858).
+
+% ****** IL19 必須要靠 pvalueTex 才能發現
+%*** IL19 is excluded by this way :-) (special S-curve P value plot)
+The other example is one of our candidate: IL19.
+It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-KM \textit{P} value has large difference between median cutoff (\num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.1154315}) and optimal cutoff (\num{6.54e-6}).
+The sliding-window selection of cutoffs could boost their statistic significance to pass the correction by both FDR and Bonferroni methods.
+%> gene_labeled_golden[!gene_labeled_golden %in% fdr100_KMsurvival$Gene.Symbol[fdr100_KMsurvival$FDR.Pvalue<0.05]]
+%[1] "IL19"
+Fortunately, IL19 has passed to become a candidate by better effect size (HR = 0.472 in TCGA cohort), and also by the validation with the other independent cohort (HR = 0.630 in GSE65858 cohort%).
+, and HR = 0.84 in GSE2837).
+
+% ***using GSE2837 or not??? ***
+%(x)
+%After the discovery by our workflow, we validated the those 20 genes in the other independent \acrshort{hnscc} cohort (GSE2837).
+%The survival significance (Kaplan-Meier \textit{P} value) is in the following probes among 10 genes:\\
+%=> Quantile normalization
+%1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758, HR= 1.42), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
+%=> no normalization
+%2) better prognosis: IL19 (0.049731, HR= 0.84), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
 

### 2021-06-27 Cover_letter_JPM.tex
Updates from Overleaf

@@
 However, the significance of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
-This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
+%This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
 Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
-Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the HNSCC biomarker.
+Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
 %The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
@@
 %, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
-The larger the sample the more likely a difference to be accepted (i.e. \textit{P} value $< 0.05$), due to the decrease of the standard error\cite{Sullivan2012}.
+The larger the sample the more likely a difference to be noticed (i.e. \textit{P} value $< 0.05$), due to the decrease of the standard error\cite{Sullivan2012}.
 However, the small effect size (non-zero) is often meaningless (substantive insignificance).
@@
 %If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
-Conversely, an effect size can be large, but fail to get statistical significance if the sample size is small. In this scenario, the \textit{P} value tells the effect does not exist.
-
-The \textit{P} value could be also impacted by error.
+Conversely, an effect size can be large, but fail to get statistical significance if the sample size is small. 
+%In this scenario, the \textit{P} value tells the effect does not exist.
+
+The \textit{P} value could be also impacted by error, which includes:
 \begin{outline}
@@
 \end{outline}
+% effect size is large (whatever is true or artificial), the p value is small
 Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has small \textit{P} value\cite{Thiese2016}.
-
 If a skewed cutoff that split, for example, 425 vs 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
@@
 
-2) \\
-( ) % pvalueTex is essential
-There is benefit of using sliding-window cutoff method in survival analysis of TCGA HNSCC cohort.
-We have compared the results of cutoff at optimal by sliding-window or just at median of gene expression.
-It shows
-the gene number with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively.
-After FDR-correction, it shows 967 vs. 209, respectively.
+%2) \\
+%(ok) % pvalueTex is essential
+There is a benefit for using sliding-window cutoff method (avoiding a skewed cutoff) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
+We have compared the results of cutoff at optimal \textit{P} value by sliding-window or just at median of gene expression.
+It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR-correction, it has reduced as 967 vs. 209, respectively.
 % HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
@@
 %209 genes are FDR KM P value <0.05
-The sliding-window cutoff method could catch more potential candidates (\textit{P} values far less than $0.001$) for Cox's modeling at next stage in our workflow.
-These preliminary candidates must be validated by Bonferroni correction and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
+The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
+That is because of proper selected cutoff improving the statistical significance.
+Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
 
@@
 Reviewing the special cases of gene, such as NDFIP1, DKC1, PNMA5, and NPB,
-we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
+we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
 NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233} (please see supplementary figure S1). % it is \ref{fig:pvaluePlot_NDFIP1
+scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
 %Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
@@
 % the effect size
-Although it has failed to compete as a candidate by less effect size (HR = 1.33) in GSE65858 cohort, compared with one (HR = 2.027) in TCGA cohort%.
+Then it has been excluded as a candidate by less effect size (HR = 1.33) in GSE65858 cohort, compared with one (HR = 2.027) in TCGA cohort%.
 , and the other (HR = 1.42) in GSE2837 cohort.
@@
 The other example is one of our candidate: IL19.
-It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-KM \textit{P} value has large difference between median cutoff (\num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.1154315}) and optimal cutoff (\num{6.54e-6}).
-The sliding-window selection of cutoffs could boost their statistic significance to pass the correction by both FDR and Bonferroni methods.
+It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-adjusted \textit{P} value has large difference between 50\% quantile cutoff (FDR 0.115)
+%(\num[round-precision=3, round-mode=figures, scientific-notation=true]{0.1154315}) 
+and optimal 48\% quantile cutoff (FDR \num{6.54e-6}).
+This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
 %> gene_labeled_golden[!gene_labeled_golden %in% fdr100_KMsurvival$Gene.Symbol[fdr100_KMsurvival$FDR.Pvalue<0.05]]
 %[1] "IL19"
-Fortunately, IL19 has passed to become a candidate by better effect size (HR = 0.472 in TCGA cohort), and also by the validation with the other independent cohort (HR = 0.630 in GSE65858 cohort%).
-, and HR = 0.84 in GSE2837).
+Fortunately, IL19 has competed to become a candidate by its better effect size (HR = 0.472 in TCGA cohort), and also by the validation with the other independent cohort (HR = 0.630 in GSE65858 cohort).
+%, and HR = 0.84 in GSE2837).
 

### 2021-06-28 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
-May 16, 2021
+June 30, 2021
 
@@
 
-Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine.
+Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine.
 We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.
@@
 
-%{%
+%{% A SUMMARY
 Reviewer 1: % {2-4}
-"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
-We re-wrote the Introduction in detail according to the suggestion by reviewer \#2. %(comment No 2-4).
+%"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
+We re-wrote the Introduction in detail according to the suggestion by reviewer \#2.
+added new supplementary Figure S1, S2, and S3
+Reviewer 2: % {3-1}
+%"Are the conclusions supported by the results?
+We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
+%, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
+%to provide more evidence from the significant literature review.
 %}
 
-Reviewer 2: % {3-1}
-"Are the conclusions supported by the results?
-Only computer computing in this research to support 20 candidate biomarkers, ... are all heavily associated with the prognosis of OS.
-There is little information provided. The authors should provide more evidence to support this article."\\
-We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
-According to the suggestion by reviewer \#3,
-we re-wrote the Discussion with additional information, and
-%}
-%{% Answer_3-1_USP10.pdf, Answer_2-1.pdf
-%According to the reviewers' comments, we 
-added new supplementary Figure S1, S2, and S3 %, S2, S3, and Table S2.
-We also replaced Figure 3D and 4A with high magnitude images from the same slides.
-We transferred the original Figure 2 into supplementary Figure S1
-to provide more evidence from the significant literature review.
-%}
-
-According to the editor's comments, we have the manuscript checked for English grammar. %
-We wish our revised manuscript could be satisfied and accepted for publication in JPM. Thanks very much for the kind helps and the reviewers' critical comments.
+%According to the editor's comments, we have the manuscript checked for English grammar. %
+We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine. 
+Thanks very much for the kind helps and the reviewers' critical comments.
 %\\[0.4cm]
@@
 \begin{MyColorPar}{blue}
-Answer
+Answer\\
 %(OK)
@@
 We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
-2) Since that revision, we added holistic cancer care in the discussion section (please see Answer 1-2).% \ref{page:1-2}).
+2) Since that revision, we added holistic cancer care in the discussions section (please see Answer 1-2).% \ref{page:1-2}).
 
@@
 \begin{MyColorPar}{red}
-"%discussion: the third limitation
+" %discussion: the third limitation
 There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
@@
 Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
-Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases.
+Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases.
 They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
@@
 % and FDR (done; ok)
-We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
+We modified the last paragraph of "Cutoff Finder Core Engine" in the Materials and Methods section.
 %Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
@@
 % (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
-The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} has been be applied and shows which genes should be retained for further univariate and multivariate analysis.
+"
+The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} shows which genes should be retained for subsequent univariate and multivariate analysis.
 % of Cox modeling
-It is ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
-Then Bonferroni adjustment of those \textit{P} values has been used for candidate selection.
-\end{MyColorPar}
+It ensures the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
+Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
+"
+\end{MyColorPar} % red
 
@@
 We appreciate the reviewer for the critical comment.
-We changed title as "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
+We changed title, "Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
 There is more evidence to validate them (please see Answer 2-3).
@@
 \begin{MyColorPar}{blue}
-Answer
+Answer\\
 
@@
 We modified the paragraphs in the "Material and Methods" section and "Results" section for the analysis of GSE65858.
-We also described "the \textit{P} values are affected by the sample size" in the Discussion section.
+We also described "the \textit{P} values are affected by the sample size" in the Discussions section.
 The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
@@
 
-[materials and methods]\\
+(In the section of Materials and Methods)\\
 %RefSeq Release 38 (November 7, 2009) 
 %[Dataset]
+"
 The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
@@
 download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
-GSE65858\cite{Wichmann2015} has OS event, RFS event and survival time.
+GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
 There are 270 HNSCC participants involved in this cohort.
@@
 %n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
-The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on November 7, 2009).
+The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009).
 % (RefSeq)
 GSE65858 is a dataset for candidate selection in our workflow.
-We have also performed Kaplan-Meier and Cox survival analyses, under the cutoff of each gene expression at their median value.\\
-
-[Results]\\
+We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
+"
+
+(In the section of Results)\\
+"
 TCGA HNSCC cohort has been applied for exploration of the biomarker candidate
@@
 The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
-%The 10 genes, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
+%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
 %The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
@@
 and also see Figure \ref{fig:hazards534}).
-However, the significance of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
+However, the significance of the other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
 %This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
@@
 Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
+"
 %The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
 
-[Discussion]\\
+(In the Discussions section)\\
 %[more in the discussion section]
-1) \\% (ok)
+"  % (ok)
 Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
@@
 %, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
-The larger the sample the more likely a difference to be noticed (i.e. \textit{P} value $< 0.05$), due to the decrease of the standard error\cite{Sullivan2012}.
-However, the small effect size (non-zero) is often meaningless (substantive insignificance).
+In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
+However, the small effect size (non-zero) is often meaningless or substantive insignificance.
 %With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
@@
 %If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
-Conversely, an effect size can be large, but fail to get statistical significance if the sample size is small. 
+Conversely, the effect size can be significant but fail to get statistical significance if the sample size is small. 
 %In this scenario, the \textit{P} value tells the effect does not exist.
 
-The \textit{P} value could be also impacted by error, which includes:
+The following error could also impact the \textit{P} value:
 \begin{outline}
-\1 A random error, defined as variability in data, is not considered a bias but rather occurs random across the entire study population and can distort the measurement process (e.x.
+\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.x.
 RNA-Seq experiments).
@@
 % effect size is large (whatever is true or artificial), the p value is small
-Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has small \textit{P} value\cite{Thiese2016}.
-If a skewed cutoff that split, for example, 425 vs 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
+Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
+If a skewed cutoff that split, for example, 425 vs. 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
 % https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
@@
 %(ok) % pvalueTex is essential
-There is a benefit for using sliding-window cutoff method (avoiding a skewed cutoff) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
-We have compared the results of cutoff at optimal \textit{P} value by sliding-window or just at median of gene expression.
-It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR-correction, it has reduced as 967 vs. 209, respectively.
+There is a benefit for using sliding-window cutoff method (between $30\%-70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
+We have compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
+It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR correction, it has reduced as 967 vs. 209, respectively.
 % HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
@@
 The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
-That is because of proper selected cutoff improving the statistical significance.
+That is because of the properly selected cutoff improving the statistical significance.
 Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
@@
 
-We will explain above mentioned by two examples.
+We will explain the above mentioned by an example.
 %***NDFIP1  % 給他們一個機會
-Reviewing the special cases of gene, such as NDFIP1, DKC1, PNMA5, and NPB,
+Reviewing the special case of genes, such as NDFIP1, DKC1, PNMA5, and NPB,
 we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
@@
 % the effect size
-Then it has been excluded as a candidate by less effect size (HR = 1.33) in GSE65858 cohort, compared with one (HR = 2.027) in TCGA cohort%.
-, and the other (HR = 1.42) in GSE2837 cohort.
+Then it has been excluded as a candidate by small effect size (HR = 1.33 in GSE65858 cohort and HR = 1.42 in GSE2837 cohort) less than 1.8.
+"
+
+%compared with one (HR = 2.027) in TCGA cohort%.
 % (ok) Answer 2-1 加入 discussion
@@
 
-% ****** IL19 必須要靠 pvalueTex 才能發現
+% x****** IL19 必須要靠 pvalueTex 才能發現
+%The other example is one of our candidate: IL19.
+It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-adjusted \textit{P} value has large difference between 50\% quantile cutoff (FDR 0.115) and optimal 48\% quantile cutoff (FDR \num{6.54e-6}).
+This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
+Fortunately, IL19 has competed to become a candidate by its better effect size (HR = 0.472 in TCGA cohort), and also by the validation with the other independent cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031 in GSE65858 cohort).
+
 %*** IL19 is excluded by this way :-) (special S-curve P value plot)
-The other example is one of our candidate: IL19.
-It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-adjusted \textit{P} value has large difference between 50\% quantile cutoff (FDR 0.115)
-%(\num[round-precision=3, round-mode=figures, scientific-notation=true]{0.1154315}) 
-and optimal 48\% quantile cutoff (FDR \num{6.54e-6}).
-This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
 %> gene_labeled_golden[!gene_labeled_golden %in% fdr100_KMsurvival$Gene.Symbol[fdr100_KMsurvival$FDR.Pvalue<0.05]]
 %[1] "IL19"
-Fortunately, IL19 has competed to become a candidate by its better effect size (HR = 0.472 in TCGA cohort), and also by the validation with the other independent cohort (HR = 0.630 in GSE65858 cohort).
 %, and HR = 0.84 in GSE2837).
+%(\num[round-precision=3, round-mode=figures, scientific-notation=true]{0.1154315})
 
@@
 "
-The Cox proportional-hazards model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
-It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
+The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
+It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
 % Classification trees and artificial neural networks in survival analysis
 The Cox model is also accounting for confounding factors\cite{Magen2019}.
-It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:
+It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x., death) at time t. It can be estimated as follow:
 
@@
 \1 t represents the survival time
-\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g.
-clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.x., clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
 \1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
 \1 the term $h_0$ is called the baseline hazard.
-It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
+It corresponds to the hazard value if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
 The "t" in $h(t)$ indicates the hazard may vary over time
@@
 
-Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
-
-Univariate Cox proportional regression model, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival (OS) individually.
+Thus, the biomarker discovery strategy is survival modeling through a collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
+
+Univariate Cox proportional regression model, using the "coxph" function in R package "survival", has been applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival individually.
 
@@
 In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
-All covariates has been pool in the hazard function h(t) to estimate their impact on the overall survival.
+All covariates have been pooled in the hazard function h(t) to estimate their impact on the overall survival.
 "
-\end{MyColorPar}
+\end{MyColorPar} % red
 
@@
 %%% how other researchers used TCGA to find expression biomarkers
-Usually, researchers developed in-house workflow of gene expression analysis to find HNSCC biomarkers.
+Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.
 %Workflow of GDCRNATool
@@
 % **** DEGs is a different concept with cutoff finding survival analysis of individual gene expression
-They have a number of genes that are differentially expressed between tumor and normal samples.
-It would be useful to show that alteration in gene expression correlates with phenotypes of HNSCC.
+They have several genes that are differentially expressed between tumor and normal samples.
+It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC.
 % https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
@@
 %e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
-They employed the Database for Annotation, Visualization and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO) including biological processes, the cellular component and molecular function.
+They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
 The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.
 %Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
-The protein-protein interaction (PPI) network was conducted by STRING (availalbe at https://string-db.org).
+The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
 The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
-Li\cite{Li2018a} and his colleagues made a R package (GDCRNATool) for the implementation of those workflow on gene expression analyses of the TCGA.
+Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows on gene expression analyses of the TCGA.
 %The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his collegues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{P} value $< 0.01$) were selected as primitive biomarkers.
+Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$).
+The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
 %By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
@@
 %%%%%%%%%
-\end{MyColorPar}
+\end{MyColorPar} % red
 
@@
 %%%
-There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.
+"
+There are three essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
 
@@
 %two things were found during our investigating and data cleaning:
-the preprocessing of TCGA RNA-Seq is as follows:
+the pre-processing of TCGA RNA-Seq is as follows:
 
@@
 SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!\\/hgnc\_id/HGNC:20863).
-Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B, and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
+Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
 % updated on 18-May-2021
@@
 
-% risk of 
-Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy might identify more but weak "biomarkers". 
+% risk of *** Answer 2-3 併入此
+Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
+We have checked this issue in detail (in the Discussions section).
 Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
-And further validation of those candidate is required in the other independent dataset.% in larger patient populations.
+Furthermore, validation of those candidates is required in the other independent dataset.
+% in larger patient populations.% in larger patient
 %warrant.
@@
 Third, we have analyzed the error log of the cutoff finding and Cox modeling, 
-the results shows that several technique problems could halt the program running.
-It includes:
+the results show that several technical problems could halt the program running.
+Those include:
 \begin{outline}
@@
 , which could not be detected prior to the program running.
-It might be due to skewed distribution of the expression value in 20500 RNA-Seq  data. % heterogeneity
+It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity
+"
+
 %# deal with return(1), return(2) and return(3) errors, try to solve it
@@
 
-%\subsection*{Discussion}
+%\subsection*{Discussions}
 
@@
 
-According to the reviewer's comment, the Discussion was modified accordingly.
+According to the reviewer's comment, the Discussions was modified accordingly.
 The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised.

### 2021-06-28 main.tex
Updates from Overleaf

@@
 % Full title of the paper (Capitalized)
-\Title{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+\Title{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}
 %\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
@@
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
+\TitleCitation{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}
 %\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
@@
 \abstract{
-Survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
-It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression.
-We have used a workflow to perform biomarker discovery.
-It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
-Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders, and Bonferroni corrected \textit{P} value.
-After validation with an independent \acrshort{hnscc} cohort (GSE2837), the result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
-Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
-We suggest these ten genes could be the candidates in biomarker discovery of HNSCC.
+The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
+It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis.
+There is some optimization software for cutoff determination.
+However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses.
+There are few clinicopathological features available on their pre-processed data sets.
+
+We developed a workflow that includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
+The independent HNSCC dataset has been used to validate this discovery.
+
+Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes.
+After adjustment with confounders, we found that the clinical tumor stage and the surgical margin involvement are independent risk factors in patient survival.
+According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, IL19, and FCGBP, are significantly associated with the patients' overall survival.
+We suggest the transcriptomic analysis could help for biomarker discovery.
 }
@@
 the Cancer Genome Atlas (TCGA);
-RNA-sequencing;
+Transcriptomic Analysis;
+%RNA-sequencing;
 Survival Analysis;
 Optimal Cutoff;
+Effect Size;
+%Tobacco\sep
+%Cox Proportional Hazards\sep
+%Tumor Aggressiveness\sep
+%Rstudio\sep
+CAMK2N1;
+IL19;
+FCGBP;
 %Biomarker\sep % Discovery\sep

### 2021-06-28 Cover_letter_JPM.tex
Updates from Overleaf

@@
 (In the section of Materials and Methods)\\
-%RefSeq Release 38 (November 7, 2009) 
+%RefSeq Release 38 (November 7, 2009)  GSE65858
 %[Dataset]
@@
 "
-TCGA HNSCC cohort has been applied for exploration of the biomarker candidate
-Total 9416 genes has %\acrshort{fdr}-
-unadjusted \textit{P} value less than 0.05.
-The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
+TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
+The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
+The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
 %The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
@@
 Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
+%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
+The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
 %During our exploration phase with TCGA cohort, the 20 genes, listed
@@
 Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
+Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset other than the TCGA cohort.
+Please see Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
 "
 %The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
+%by GEO GSE2837 HNSCC dataset (PrognoScan)
+%After the discovery by our workflow, we validated the those 20 genes in the other independent \acrshort{hnscc} cohort (GSE2837).
+%The survival significance (Kaplan-Meier \textit{P} value) is in the following probes among 10 genes:\\
+%1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
+%2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
+%17 out of 20 candidates
 
@@
 \begin{MyColorPar}{red}
+% inserted at \subsubsection{From TCGA to expression biomarkers}
 
@@
 It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC.
+
+%%% https://www.biostars.org/p/153013/
+%% download data with offline analysis
+%Usually, investigators could download the TCGA data in order to analyze and find expression biomarkers.
 % https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J

### 2021-06-28 main.tex
Updates from Overleaf

@@
 %\cite{SeanDavis;MartinMorgan2020}
-\end{MyColorPar}
+\end{MyColorPar} % the rest moved into materials and methods
 
@@
 \begin{MyColorPar}{red}
-\subsubsection{From TCGA to expression biomarkers}
-%%% https://www.biostars.org/p/153013/
-%% download data with offline analysis
-Usually, investigators could download the TCGA data in order to analyze and find expression biomarkers.
-A number of genes of interested could be differentially expressed between tumor samples obtained from those patients with better/worse survival of HNSCC.
-A brief overview of steps:
-\begin{outline}
-\1 obtain the data (RNA-Seq and clinicopathological data): go to FireBrowse (firebrowse.org) or FireHose (http://gdac.broadinstitute.org/), select "Clinical" and "mRNASeq" data of \acrfull{hnscc}
-\1 prepare the data for the analysis
-\1 run the analysis under the R package "survival", and interpret the results
-\end{outline}
-
+\subsubsection{From TCGA to expression biomarkers} % from Answer 2-6 minor2
+Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.
+They have several genes that are differentially expressed between tumor and normal samples.
+It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC
+
+% Rstudio\cite{Loraine2015a}
+Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
+Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.x. GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
+% IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
+%e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
+They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
+The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.
+%Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
+The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
+The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
+Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows on gene expression analyses of the TCGA.
+%The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
+Moreover, genes with degree $>= 25$ were selected as hub genes.
+Subsequently, module analysis (16) of the PPI network was performed using the Molecular Complex Detection (MCODE) tool of Cytoscape software, and GO and KEGG analysis of the modules was carried out using the DAVID database.
+%a validation set and
+%Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
+Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$).
+The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
+%By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
+The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
+The candidate genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
+%, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
+), GEPIA2021\cite{Li2021} (available at http://\\gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
+% GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
+% GEPIA1/2 contact us: tangzefang@pku.edu.cn
+Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\
+\end{MyColorPar}
+
+%A brief overview of steps:
+%\begin{outline}
+%\1 obtain the data (RNA-Seq and clinicopathological data): go to FireBrowse (firebrowse.org) or FireHose (http://gdac.broadinstitute.org/), select "Clinical" and "mRNASeq" data of \acrfull{hnscc}
+%\1 prepare the data for the analysis
+%\1 run the analysis under the R package "survival", and interpret the results
+%\end{outline}
 %%%%%% web-based tools
 %Usually,
+
 The other investigators should get the rationale or revelation of the genes of interest on a specific cancer type.
@@
 such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
-packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.
-
-\end{MyColorPar}
+packages/cutoffR). 
+However, non of them could perform jointly predictive of survival times and cutoff selection within subgroups of gene expression.
+%  %combine the scanning of the protein-coding genes and cutoff optimization programmatically.
 
@@
 In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
-\begin{MyColorPar}{red} %%%
-There are two key-points of biomarker discovery from survival analysis of TCGA HNSCC dataset.
-First, although \acrshort{tcga} genomics data has been harmonized, two things were found during our investigating and data cleaning:
+
+\begin{MyColorPar}{red} %%% ***
+There are three essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
+
+First, although \acrshort{tcga} genomics data has been harmonized, 
+%two things were found during our investigating and data cleaning:
+the pre-processing of TCGA RNA-Seq is as follows:
 
 \begin{outline}
-\1 null expressed genes over 50\% of the cohort have been excluded in the workflow
-\1 after extended organizing, the number of protein-coding genes in the  RNA-Seq dataset should be corrected  (from 20499 to 20500);
-%
-that is because of ...
-%[main\_marginSFP\_HNSCC.R] line 1361
-osccT\_2021 <- osccT[c(30,31)] %[30] "days_to_last_followup", [31] "days_to_last_known_alive" 
-OS\_live_days /30 % derived from last followup [30]/ last known alive [31])
-event (alive) to censored (status 0) % to handle missing data of censored by OS_months imputation
-R help from Jorge I Velez
-[line 1654]
-for gene correction (20499 to 20500) from SLC35E2A to 2 genes:
-% SLC35E2A: 9906
-% SLC35E2B: 728661
+\1 HNSCC samples without complete clinical information have been removed;\\
+% or 50\%
+\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded;\\
+
+\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.\\
+After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that gene ID (9906), gene ID (728661), and their expression values were saved together under the entity of gene symbol "SLC35E2".
+The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
+% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
+% [line 1549]
+%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
+%[line 1654]
+%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
+%NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
+According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
+% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
+% keyword: (SLC35E2) AND "Homo sapiens" 
+SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!\\/hgnc\_id/HGNC:20863).
+Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
+% updated on 18-May-2021
 \end{outline}
+
 %Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
 
-%Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
-\end{MyColorPar} %%%
-
-\begin{MyColorPar}{red} %%% %%%
-% risk of 
-Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy might identify more but weak "biomarkers". 
+% risk of *** Answer 2-3 併入此
+Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
+We have checked this issue in detail (in the Discussions section).
 Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
-%Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. 
-%Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05).
-For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff.
-But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff.
-\end{MyColorPar} %%%
-
-Our approach describes a comprehensive workflow implemented in the R script, which runs on the Rstudio server.
-Its function includes data retrieval, data preprocessing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
+Furthermore, validation of those candidates is required in the other independent dataset.
+% in larger patient populations.% in larger patient
+%warrant.
+
+% dissection
+%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
+Third, we have analyzed the error log of the cutoff finding and Cox modeling, 
+the results show that several technical problems could halt the program running.
+Those include:
+\begin{outline}
+
+\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression
+\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate.
+%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
+%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
+% error at 16115 gene ""; why? 518 values all are -0.04203 at T
+%  There is only 1 group 
+%This is because of skewed distribution of the expression value. 
+% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
+% all cases belong to >= median => 改為 > median 即可
+% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
+% median = NaN :-); 
+% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
+% and NaN imputation as median
+\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow)
+\end{outline}
+, which could not be detected prior to the program running.
+It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity
+
+\end{MyColorPar} %%% red
+
+Our approach describes a workflow implemented in the R script, which runs on the Rstudio server.
+Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
+The independent HNSCC dataset has been used to validate this discovery.
 The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.
@@
 
+\begin{MyColorPar}{red}
+TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
 The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
-The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.5 or less than 0.5) (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b) multivariate plots).
-At the final step, a stringent criteria (Bonferroni \textit{P} value correction) was used to yield twenty candidates (see Figure \ref{fig:figure2}(c), (d)). 
-% before validation
-Among these candidates, ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of  \acrshort{os} (see Table \ref{tab:newTable1}).
-The other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival (see Table \ref{tab:newTable1}, with their gene name).
-We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:hazards3}).
-%{fig:figure3}).
+The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
+%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
+%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
+Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
+%These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
 The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
-% => after validation: The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
-Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
-
-%注意 強調GSE2837: 
-%The prognostic significance of the candidate genes has been validated by an independent patient cohort.
-% validation by GSE2837 cohort (with web-tools)
-%\subsubsection*{GSE2837} % non-TCGA
-% from Anwser2-2
-%by GEO GSE2837 HNSCC dataset (PrognoScan)
-After the discovery by our workflow, we validated the those 20 genes in the other independent \acrshort{hnscc} cohort (GSE2837).
-The survival significance (Kaplan-Meier \textit{P} value) is in the following probes among 10 genes:\\
-1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
-2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
-%17 out of 20 candidates
-%?DKK1 (0.253635), 
-%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
-%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
-%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
-%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
-Thus, these 10 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort.
-Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.
+%During our exploration phase with TCGA cohort, the 20 genes, listed
+%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
+%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
+%}
+%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
+
+% [2021/06/13-17] GSE65858
+%CAMK2N1, IL19, and FCGBP is validated by
+%candidate_fdr100
+%PvalueTex consensus with GSE2837 to yield 3 candidates
+In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
+% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
+%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
+%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
+%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
+%IL19    0.03390   0.04738901    0.630   6.543871e-06
+%IL19    0.00269  0.03068073 0.630  6.543871e-06
+%candidate_fdr100
+and also see Figure \ref{fig:hazards534}).
+However, the significance of the other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
+%This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
+Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
+Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
+Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset other than the TCGA cohort.
+Please see Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
+\end{MyColorPar} % end red
 
@@
 \label{fig:figure2}
+\end{figure}
+
+%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
+% by Validation_GSE65858_survival.R
+% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
+\begin{figure}
+    \centering
+    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
+    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
+%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
+%Y axis: multivariate hazard ratio from Cox proportional regression model.
+%Dotted line: significant Bonferroni corrected \textit{P} value. 
+%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$).
+\textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
+    This cohort has been applied for exploration of the candidate biomarkers.
+    Total 9416 genes has %\acrshort{fdr}-
+    unadjusted \textit{P} value less than 0.05.
+    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.
+    The 22 genes, listed on the side, have hazard ratio between 0.6 and 1.5.\\
+    Remarks:\\
+    \textcolor{red}{Red spots}: $HR > 1.0$;
+    \textcolor{green}{Green spots}: $HR < 1.0$;\\
+    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
+    Y-axis: HR of Cox proportional hazard regression model\\
+    }
+    \label{fig:hazards3}
+\end{figure}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{graphicx}
+% Please add the following required packages to your document preamble:
+\begin{table}[ht]
+\centering
+\caption{The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model}
+\label{tab:table_top3_GSE65858}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{llllclc}
+\hline
+%\multirow{2}{*}{}
+Gene Symbol &
+  \multicolumn{2}{c}{KM \textit{P} value} &
+  \multicolumn{2}{c}{FDR-adjusted \textit{P} value} &
+  \multicolumn{2}{c}{Cox’s univariate HR} \\
+%  \hline
+ &
+  \multicolumn{1}{c}{TCGA} &
+  \multicolumn{1}{c}{GSE65858} &
+  \multicolumn{1}{c}{TCGA} &
+  \multicolumn{1}{c}{GSE65858} &
+  \multicolumn{1}{c}{TCGA} &
+  \multicolumn{1}{c}{GSE65858} \\
+  \hline
+  \hline
+CAMK2N1 & \num{2.97e-7} & \num{6.87e-3} & \num{1.63e-5} & 0.038 & 2.101 & 1.814 \\
+IL19    & n/a           & 0.03          & n/a           & 0.047 & n/a   & 0.630  \\
+IL19    & \num{3.73e-7} & \num{2.69e-3} & \num{6.54e-6} & 0.031 & 0.472 & 0.630  \\
+FCGBP   & \num{1.21e-6} & 0.01          & \num{4.83e-5} & 0.039 & 0.484 & 0.573\\
+\hline
+  \multicolumn{7}{l}{(IL19 has two probes in RNA-Seq experiment of GSE65858)}\\
+  \multicolumn{7}{l}{(FDR: \acrlong{fdr})}\\
+\hline
+\end{tabular}%
+} % end of \resizebox
+\end{table}
+
+%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
+% by Validation_GSE65858_survival.R
+% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
+
+\begin{figure}
+    \centering
+    \includegraphics[width=13cm]{Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf}
+    \bcaption{Volcano plot of genes under survival analyses of GSE65858 cohort}{
+    % GSE117973 using the same platform GPL10558
+    This HNSCC cohort has been applied for filtering of our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
+    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
+    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0);
+    (\textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
+    The 22 genes, listed on the side, have hazard ratio $> 1.8$ or $< 0.6$.\\
+    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value with log10 transformed);
+    (Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
+    }
+    \label{fig:hazards534}
 \end{figure}
@@
 
-After validated by GSE2837, our top 1 candidate is \acrfull{CAMK2N1}.
+Our top 1 candidate is \acrfull{CAMK2N1}.
 The Kaplan-Meier curve reveals 152 patients bearing the higher expression of \acrshort{CAMK2N1} were suffered from only 35\% of 5-year \acrshort{os} rate.
@@
 
-\begin{figure}[hp]
+% and a new Figure 4
+\begin{figure}[ht]
 
@@
 
-In Table \ref{tab:newTable1}, %{table:table3}, 
-the other ten overexpressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
-Four out of ten has been validated by using GSE2837.
+%In Table \ref{tab:newTable1}, %{table:table3}, 
+%the other ten overexpressed genes have been found in better prognosis of \acrshort{hnscc} patients. Cox's univariate and multivariate HR is under 0.5.
+%Four out of ten has been validated by using GSE2837.
 In Table \ref{table:table4},
@@
 
-In summary, those ten candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
-Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. 
+In summary, those three biomarker candidates , clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+Thus, the prognosis model with coefficients is established from \acrshort{tcga} and GSE65858 \acrshort{hnscc} cohorts. 
 %The important input $X_1...X_n$ should be patients' features: age, specific ten gene expressions, clinical T stage, and surgical margin.
@@
 
-%%%%
+%%%% LASSO regression
 \subsection{Feature Selection for Survival Modeling} % Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
@@
 
+%%% Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff.
+\subsection{\textit{P} value is affected by sample size and cutoff}
+Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
+The effect size is the magnitude of the difference (or relationship) among comparing groups.
+%A \textit{P} value is a tool to help interpret findings from biomedical research.
+%In reporting and interpreting studies, both 
+%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
+While statistical significance can inform the researcher whether an effect exists, 
+the \textit{P} value will not directly tell the effect size.
+%The effect size is the main finding of a quantitative study.
+%Statistical significance depends upon both sample size and effect size. 
+The effect size is independent of the sample size\cite{Sullivan2012}.
+
+%When we increase the sample size, the standard error decrease
+%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
+In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
+However, the small effect size (non-zero) is often meaningless or substantive insignificance.
+%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
+%, that is, when the effect size is exactly zero; 
+%yet very small differences, even if significant, are often meaningless. 
+%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
+%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
+Conversely, the effect size can be significant but fail to get statistical significance if the sample size is small. 
+%In this scenario, the \textit{P} value tells the effect does not exist.
+
+The following error could also impact the \textit{P} value:
+\begin{outline}
+\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.x.
+RNA-Seq experiments).
+The larger sample size could reduce the random error. 
+\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
+It could deleteriously impact the statistical significance.
+The larger sample size could not affect the systematic error.
+\end{outline}
+% effect size is large (whatever is true or artificial), the p value is small
+Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
+If a skewed cutoff that split, for example, 425 vs. 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
+% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
+%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
+%effect size, sample size, cutoff 影響 p value!
+
+% [preserved] ***
+%An increase in the sample size will decrease over-fitting of model[Frank Harrell].
+% https://hbiostat.org/rms/
+
+% definition of P value
+%Statistical significance is the probability that the observed difference between two groups is due to chance.
+If the P value is larger than the alpha level chosen (e.x.
+0.05), any observed difference is assumed to be explained by sampling variability.
+%The most commonly used α level is 0.05, as proposed by Fischer, is the amount of type I error you are willing to accept.
+%Fisher suggested 5\% (α=0.05) level could be used for concluding that fairly strong evidence exists against H0, that is 1 out of 20 times you will be wrong and by random chance there is no difference between your groups, but the data you have suggests that there is (2).
+
+%power: Power analysis is the name given to the process for determining the sample size for a research study.
+The technical definition of power is that it is the probability of detecting a "true" effect when it exists.
+Many students think that there is a simple formula for determining sample size for every research situation.
+%As the sample size gets larger, the z value increases therefore we will more likely to reject the null hypothesis; less likely to fail to reject the null hypothesis, thus the power of the test increases.
+
+%the confidence interval of the P value (second generation P value?)
+
+%%%%
+%(ok)2-3 put in supplementary figure S1 %Rplot_pvaluePlot_NDFIP1.pdf
+%from Answer 2-3 supplementary Figure S1  %圖就好 figure Rplot_pvaluePlot_NDFIP1.pdf
+
+%2) \\
+%(ok) % pvalueTex is essential
+There is a benefit for using sliding-window cutoff method (between $30\%-70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
+We have compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
+It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR correction, it has reduced as 967 vs. 209, respectively.
+% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
+%Result by optimal cutoff: total 9416 plots,
+%6284 are raw KM P value < 0.05
+%534?? genes are FDR KM P value <0.05
+%967 genes which HR is greater than 1.5 or less than 0.5.
+%Result by median cutoff: total 20080 genes, 
+%3118 are raw KM P value < 0.05; 
+%209 genes are FDR KM P value <0.05
+The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
+That is because of the properly selected cutoff improving the statistical significance.
+Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
+
+%small effect size could be double-checked by GSE65858.
+%差別很大，張大網
+%([2021/06/27] run code: if median cut for TCGA KM Cox by *** pvalueTex code)
+%列入 workflow in materials and methods;
+
+We will explain the above mentioned by an example.
+%***NDFIP1  % 給他們一個機會
+Reviewing the special case of genes, such as NDFIP1, DKC1, PNMA5, and NPB,
+we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
+NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
+%Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
+%After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures, scientific-notation=true]{0.0001074233}.
+% the effect size
+Then it has been excluded as a candidate by small effect size (HR = 1.33 in GSE65858 cohort and HR = 1.42 in GSE2837 cohort) less than 1.8.
 %%%
@@
 \subsubsection{Holistic Cancer Care}
-% carcinogenesis by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system.
-(gene expression is not an independent $X_mrna$, which is correlated with other $X_body, X_stress, X_inflammation, X_ros$)
-% cancer care with person-central approach, PCA; Cullen, Carl Rogers
-
-%TCGA treated by surgery and more; TNM available yes
-
-%discussion: the third limitation
-There are eighty-one ($X_1 ... X_{81}$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
-% since it has comprehensive clinical features, 
-such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
-However, the TCGA did not collect other features from holistic cancer care.
+
+\begin{MyColorPar}{red}
+There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
+such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
+However, the TCGA did not collect other features related to holistic care.
 % Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
-Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status (see Figure \ref{fig:figure5}).
-
-%
-World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
-Core principles can be taken to achieve people-centred and integrated health service delivery. 
-The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
-Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
-%that considers  factors rather than just the symptoms of disease or ill-health.
-The second principle is empowering – supporting people to manage and take responsibility for their health,
-%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
-for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
-People-centred care requires that people have the education and support they need to make decisions and participate in their care.
-%Glossary:
-%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways.
-People-centred care also requires that people have the education and support they need to make decisions and participate in their own care.
-It is organized around the health needs and expectations of people rather than diseases (7,8)
-%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
-%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure \ref{fig:figure5}).
+Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
+These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
+Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
+Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases.
+They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
+Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
+The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure \ref{fig:figure5}).
+\end{MyColorPar} % red
 
@@
 
-%we educate them
-%1.
-Mong, L.-C., Liao, F., Chiou, J.
-& Chiang, P.
-Tips for Integrating Spiritual Care Delivery in Dental Education.
-in Asia Pacific Medical Education Conference.
-Short Communication 5 (National University of Singapore, 2021).\cite{Ling-ChengMong2021}
-Spiritual care is the key to holistic healthcare in dental practice\cite{Ling-ChengMong2021} and cancer patient care\cite{Hulett2016}. 
-It is mindful of patient's mental health, emotional changes, socioeconomic during healthcare.
-%Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration.
-We are learning to listen proactively.
-It is aware of the patient's spiritual needs.
-%Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}
-% mindfulness-based cognitive therapies [MBCT]
-%%%% MBSR "念" 今天的心 專心才有幸福感(味覺嗅覺靈敏專心吃
-Jon Kabat-Zinn has introduced the mindfulness-Based Stress Reduction (MBSR) program in 1979\cite{Niazi2011}.
-MBSR composes the contemplative, spiritually based Buddhist philosophy, which promotes a nonjudgmental, accepting, and patient worldview and teaches relaxation through focused awareness on breathing during meditation.
-It employs (static) mindfulness meditation to alleviate suffering associated with physical (pain), psychosomatic and psychiatric disorders.
-%是1979年麻薩諸塞大學的榮譽教授Jon Kabat-Zinn => 佛教禪修的mindfulness 正念止觀（中譯建譯：自我覺察）帶入西方身心醫學及心理學領域。
-The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage (dynamic) mindfulness and self-awareness. 
-%Search Inside Yourself was born at Google in 2007 when one of Google’s earliest engineers, Chade-Meng Tan, gathered a team of leading experts in mindfulness, neuroscience, leadership and emotional intelligence to develop an internal course for fellow Google employees lovingly called Search Inside Yourself (SIY).
 % 目的與功效  出入息 呼吸念頭 回到覺知，不再被潛意識自動導航干擾情緒
@@
 %冤親債主 決定不再影響環境 基因 expression，減少意外與疾病、癌症
-A systematic review of spiritually based interventions and psychoneuroimmunological (PNI) outcomes in breast cancer survivorship was reported by Hulett et al.\cite{Hulett2016}. 
-%Objective This is a review of spiritually based interventions (eg, mindfulness-based stress reduction, MBSR) that utilized psychoneuroimmunological (PNI) outcome measures in breast cancer survivors.
-Specifically, this review sought to examine the evidence regarding relationships between spiritually based interventions, psychosocial-spiritual outcomes, and biomarker outcomes in breast cancer survivors.
-%Methods A systematic search of 9 online databases was conducted for articles of original research, peer-reviewed, randomized and nonrandomized control trials from 2005-2015.
-Data were extracted in order to answer selected questions regarding relationships between psychosocial-spiritual and physiological measures utilized in spiritually based interventions.
-Implications for future spiritually based interventions in breast cancer survivorship are discussed.
-Results Twenty-two articles were reviewed.
-%mindfulness-based cancer recovery (MBCR) 
-Psychosocial stress is associated with cancer incidence and poor survival\cite{Chida2008}.
-These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
-Thus, cortisol is one of the most common (objective) outcomes studied in PNI factors.
-% others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV
-The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
-%  body-mind-spirit (BMS) group therapy in the Meaning in Life questionnaire (MLQ) including two sub-scales: MLQ-Presence and MLQ-Search.
-% The MLQ [15] for measuring psychological well-being consists of two subscales: the 5-item MLQ-Presence subscale, measuring the subjective sense that one’s life is meaningful, and the 5-item MLQ-Search subscale, measuring the drive and orientation toward finding meaning in one’s life.
-%Compared with control groups, intervention groups demonstrated positive mental health outcomes and improved or stable neuroendocrine-immune profiles, although limitations exist.
-%Design methods have improved with regard to increased use of comparison groups compared with previous reviews.
-There are few spiritually based interventions that specifically measure religious or spiritual constructs.
-Similarly, there are few existing studies that utilize standardized religious or spiritual measures with PNI outcome measures.
-Findings suggest that mindfulness meditation could stabilize neuroendocrine-immune activity (measured by PNI biomarkers) in breast cancer patients comparing to control groups\cite{Hulett2016}.
-%This review revealed a positive pattern between spiritually-based interventions and several PNI biomarker outcomes, suggesting that spiritually-based interventions offer positive mental and physiological health benefits.
-%For breast cancer survivors, these studies suggested that engaging in spiritually-based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.
-%From a PNI perspective, future spiritually based interventions should include standardized measures of religiousness and spirituality in order to understand relationships between and among religiousness, spirituality, and neuroendocrine-immune outcomes.
-Future research should now focus on determining the minimum dose and duration needed to improve or stabilize neuroendocrine-immune function, as well as
-%diverse setting needs, including tele-medicine practice for survivors who are too ill to travel to group sessions or lack economic resources.
-% 自動導航（潛意識）易受情緒影響，造成焦慮、發炎、免疫 Cancer
-%Mindfulness based stress reduction provides psychological benefit and restores immune function of women newly diagnosed with breast cancer: A randomized trial with active control.
-%BACKGROUND: Women newly diagnosed with breast cancer experience psychological distress, accompanied by reduced Natural Killer Cell Activity (NKCA) and altered levels of cytokines, which may compromise cancer control.
-Few studies have evaluated psycho-immune outcomes of mindfulness-based stress reduction (MBSR) for women newly diagnosed with breast cancer in comparison to an active control condition.
-OBJECTIVE: The purpose of this study was to determine whether MBSR benefits psychological, behavioral, and immunological function in women recently diagnosed with breast cancer.
-DESIGN: After confirmation of breast cancer staging, women diagnosed with early-stage breast cancer (n = 192) were randomized to an 8-week MBSR program or an 8-week active control condition (ACC).
-The ACC consisted of a series of cancer recovery and health education classes.
-Both MBSR and the ACC were administered in group format.
-METHODS: Women completed psychometric instruments and provided blood for NKCA and cytokine levels at pre-, mid-, and completion of program, as well as at 1- and 6-months post-program.
-One hundred and twenty four women completed all five-assessments (MBSR, n = 63; ACC, n = 61).
-Hierarchical linear modeling was used to analyze trajectories of outcomes over time and between groups.
-%RESULTS: Compared to the ACC group, women randomized to MBSR exhibited decreasing trajectories of perceived stress, fatigue, sleep disturbance, and depressive symptoms. 
-%Further, compared to women randomized to ACC, MBSR women exhibited trajectories demonstrating significantly more rapid restoration of NKCA, accompanied by 
-%lower circulating TNF-alpha levels, lower IL-6 production =>  pro-inflammatory cytokines
-%and greater IFN-gamma production => IFN gamma supports an immune-mediated response against cancer and this may be important during the transition following cancer treatment
-A randomized clinical trial with active control proved that early provision of MBSR for women newly diagnosed with breast cancer provides psychological benefits (reduction of stress, fatigue, sleep disturbance, and depressive symptoms), and also optimizes immune functions (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) supportive of cancer survival\cite{WitekJanusek2019}.
-
-%%%% PCA and ECA: the way to delivery of MBSR
-The therapeutic relationship (TR) is essential towards spiritual care.
-According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
-In 1979, Carl Rogers wrote\cite{Rogers1979}: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
-Then simply my presence is releasing and helpful."
-Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
-Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
-%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
-1. Two persons are in psychological contact. \\
-2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
-3. The second person, whom we shall term the therapist, is congruent
-or integrated with the relationship. \\
-4. The therapist experiences "unconditional positive regard" for the client. \\
-5. The therapist experiences an empathic understanding of the client's
-internal frame of reference and endeavors to communicate this experience to the client. \\
-6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
-%empowering
-%(一)雙方有心理的接觸。
-%(二)當事人正感到焦慮或不一致(incongruence)。 
-%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
-%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
-%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
-%(六) 第五點只要有個適當的開始，療癒就會開始
-%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
-As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
+
 %七情: 喜、怒、思、悲、恐、驚、憂
-depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
+%depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
 % 只是陪伴
-%The research implication is to investigate the necessity and sufficiency of the six conditions.
-%Rogers, C.
-R.
-A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework.
-in Psychology: A Study of a Science.
-Study 1, Volume 3: Formulations of the Person and the Social Context (ed.
-Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
-%PCA理論 by *** Tex Chi
-%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
-%以心印心 engaging
-%身心相連 body-mind connection
-%捨末求本 find the source: emotion
-Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
-Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases.
-They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
-Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
-The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure \ref{fig:figure5}).
+
 %身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
@@
 
-%Personhood: Carl Rogers
-% ***尋找生命的意義 meaning of life
-%真誠、能深刻地善解人意
-%非認知性核心能力
-%正念止觀(在當下) mindfulness meditation
-%人人有自癒能力 resilience
-%真誠 (Genuineness/Validity/Bona Fides) 善意?
-%內在聲音與外在態度一致/明心見性/超越的意識狀態 (Congruence/Consistency)
-%共情理解(設身處地/同理心/除我執 自他不二) (Empathic Understanding of Reference/Track)
-%無條件關懷(不批判/頓悟) (unconditional positive regard) 只是陪伴
-%***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）by 諮商員的靈性功力
-%治療關係: 
-%Tex Chi's Therapeutic relationship: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
-%I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing.
-Then simply my presence is releasing and helpful\cite{Rogers1979}.
-%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
-%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
-%***「診後說三句，更勝良帖十方」
-
-%% why holistic? 太極 氣功 情緒 myofascia and sympathetic system
-%中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
-%養生和治療的原則:
-%一、某些病症可以透過食療而改善的會建議自行調養
-%二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
-%三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
-%四、沒有一勞永逸的食療，不宜執著特定的食療神話
-%五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
-%六、認識自己身體的狀態比吸收營養資訊更重要
-%七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
 %情志養生 喜、怒、思、悲、恐 or 七情
@@
 
-%% why holistic? % Environment 環境 => 分享權力、 自決 empowering
-The WHO's second principle is empowering – supporting people to manage and take responsibility for their health.
-Bruce Lipton introduced mind-brain-body system in 1992\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}.
-%Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
-In a state of fear, the brain releases chemicals of stress hormones and inflammatory cytokines.
-Conversely, dopamine, oxytocin, vasopressin, and growth hormone will be released by the central nervous system in response to the perception of love.
-% Arginine vasopressin (AVP) and oxytocin (OXT) are two centrally released neuropeptides that are involved in shaping essential social behaviors, like aggression, social recognition, and social motivation.
-%Bruce Lipton: the biology of belief %信念的力量 \cite{Lipton2015}
-%placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
-%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
-%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
-%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
-%As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life.
-I have experienced unjustified conflicts in my social relations, feeling stale in mind and body
-%Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds.
-These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment.
-%Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings.
-%Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors.
-As Dr.
-Bruce Lipton explains in his book, 'The Biology of Belief'\cite{Lipton2015}: DNA does not control our biology; instead DNA is controlled by signals from outside the cell.
-Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows.
-% 萬法唯心造
-Holistic healthcare should be considered for treating patients as a complete synchronized system of soul, mind, and body; treatment should include more than medication or surgery, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}\cite{Lipton2015}
-
-%騙過你的病-安慰劑效應 
-%The Placebo Effect (film by Emmanuelle Sapin, Pascal Goblot)\cite{Sapin2014}
-%1. Sapin, E. & Goblot, P. L’effet placebo (English: The Placebo Effect) [enregistrement vidéo] : le formidable pouvoir de l’auto-guérison. 53 PP-Quebec (Cinéfête, 2014).\cite{Sapin2014}
-% https://biblio.bdeb.qc.ca/in/sim/faces/details.xhtml;jsessionid=E3DD39109012D0BEA598E6E5B66A4FD2?id=p::usmarcdef_0000058243&posInPage=8
-%1. Finniss, D. G. Placebo Effects: Historical and Modern Evaluation. in International review of neurobiology vol. 139 1–27 (2018).\cite{Finniss2018}
-%蓋倫劑量 placebo effect 身心靈醫學的核心
-In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo.
-If I had thought of any internal medicine, it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}
-Cullen studied the objective science of analytical chemistry. He also studied that the patient's therapeutic response could be influenced by his
-subjective, psychosomatic, or "sympathetic constitution"\cite{Kerr2008}.
-%Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with the psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
-Cullen's theory of sympathy (or empathy) is a mind-body therapeutics, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.
-%This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine.
-%啟蒙運動
-%Cullen found the power of mind-body interaction that a physician's therapeutic intentions could be triggered by sympathy\cite{Sapin2014}.
-%How does placebo effect work in patient's internal environment?  %改造患者的心，就能改造他的身體環境，有利消除癌症
-%安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
-%前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
-%But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}.
-Pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced in neuroimaging studies\cite{Bennett2018}. 
-The anterior cingulate cortex and the dorsolateral prefrontal cortex of the brain have been found to be activated by placebo administration\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}.
-The prefrontal cortex runs conscious mind generating empathy and love, and will be influenced during mindfulness meditation\cite{Krummenacher2010}\cite{Bennett2018}.
-%prefrontal lobe 理智腦 意識 正念 杏仁核 prefrontal cortex runs conscious mind「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
-%sympathy 富有同情心、慈悲心，靈性高度成熟的醫師，不是只用藥物或手術來治療病患，「他自己本身」就具有療癒效果。
-The physician could listen and interpret the patient's sympathetic disorder and select either placebos to please (influence the patients' emotional states) or medicine to cure the patient's disorder.
-%placebo effect 安慰劑的研究，拓展了我們對醫病關係的理解，回歸到以病患為中心。
-%醫療處理的不只是藥物和手術，人更是必須處理的對象，把病患看作一個整體，要掌握身與心的個人特質。
-%#正念 減壓，療癒疼痛\cite{Krummenacher2010}\cite{Bennett2018}、免疫系統、內分泌系統或自律神經系統相關的疾病，以及憂鬱症、焦慮症 
-%The idea of placebo as a diluted but active substance persisted into the 19th century but the term also came to mean a physiologically inert substance - bread or lactose, for example.
-Inert substances began to be used in comparative clinical trials during the first half of the 19th century but this latter meaning of the term was given particular impetus at the end of the 19th century and the beginning of the 20th century, when inert substances were used as controls in pharmacological experiments.
-This shift in meaning may have reflected the rise of a new emphasis (or even metaphysics) in medicine, in which the molecular make up of an active drug assumed central importance, and any other positive benefits were seen as non-specific, placebo effects.\cite{Kerr2008} % 漸漸被特意忽略
-%物理作用、信號，雷射針灸
-%non-verbal contact
-%前額葉內側 (medial prefrontal cortex)
-%額葉底部(orbitofrontal cortex)
-%%%%%%%%
-% mindfulness meditation
-% 人的腦波一般分為β（12-30Hz）、α(8-12Hz）、θ(4-8Hz)、δ（1-4Hz)，四種波。當我們處於清醒、警覺狀態時，腦波是處於高頻率的β波。隨著身心狀態逐漸放鬆，卸下防衛時，腦波頻率也會逐漸下降至α、θ波，此時身心狀態是處於最寧靜、創造能力最好、對事情洞察能力最佳的狀態。如果能夠安祥進入睡眠階段，則腦波會降至δ波。靜坐時不僅可以使腦波由快速的β波降至α、θ波
-%In human EEG studies, cortical theta wave (4–7 Hz) tends to appear during meditative, drowsy, hypnotic or sleeping states in older children and adults.
-Theta is a frequency lower than consciousness.
-Theta is actually a brain function also associated with imagination.
-
-%cancer therapy by 患者自癒 Mindfulness Meditation help 復原力（resilience）
-%Self-Compassion  慈悲
-% 除我執 global self-esteem:
-%自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
-
-%%%% healing and cure by Changing the Environment 環境
-%genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
-The genetics of the cell gives all kinds of potentials. % 自性空
-Environmental signals from the cell membrane can go into the nucleus via signal transduction.
-The signal selectively changes the reading of our gene, e.g., epigenetics regulation, controlling cell behaviors.% including genetics.
-The central dogma of molecular biology should be modified as environmental signals to regulatory protein to DNA to RNA and then to protein.
-Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017} (e.x.
-stressful environment, see Figure \ref{fig:figure5}).
-% so do the cancer
-%Individual treatment and avoiding assumptions.
-Although it is useful for therapists to have a knowledge of the trauma literature on the general reactions of people who experience trauma, the therapist should not assume that this knowledge necessarily applies to each and every client\cite{Joseph2004}.
-%The membrane proteins and the chromosomal proteins that control the DNA, called regulatory proteins. But even those proteins are controlled by environmental signals. %It is not DNA to RNA to protein.
-%療癒 
-Study showed that after several hours of meditation, the expression of some inflammatory genes changed\cite{Gustafson2017}.
-%You can change your genetic activity by how you change your response to the environment. 
-%to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.
-Becoming aware of our behavior's subconscious source allows us to change our lives by rewriting the programs (in the subconscious mind) of limitation or the things that interfere with us.
-Warburg effect\cite{Warburg1956}\cite{Chang2017b} is an example of carcinogenesis and metabolic reprogramming of cells by some environmental factors.
-%honeymoon by Lipton 愛自己就是渡蜜月；其實是 正念 mindfulness (因為自他不二）
-%You are creating a world of joy and love, and that’s called the honeymoon. When we fall in love, we stop focusing our conscious mind in thought and start keeping it present. 
-%It is called being mindful. 
-%You’ve been looking for yourself your whole life.
-%愛、性、正念止觀
-%Science has recognized that immediately after falling in love, we enter a period of mindfulness where we keep our conscious mind present.
-%You start running programs that are based on your conscious wishes and desires. All of a sudden, without the programs—without the subconscious programs—we begin to experience a heavenly life.
-%%%%%% carcinogenesis
-%95\% of cognitive behavior runs on subconscious program:
-%70\% %對於健康有不良影響 => 卻是惡劣競爭下的生存技能
-%Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage.
-These programs were acquired from other people, not from ourselves, with a survival advantage.
-%Being subconscious, those programs acquired from other people before age 7, are occurring without conscious recognition and awareness. 
-The survival advantage programs, such as limitation, disempowerment, and self-sabotage, will affect epigenetic regulation.
-Genes are not self-actualizing. %The control of genes is not due to any inherent activity in the DNA itself. 
-The regulation of genetic activity is due to the interaction of the cell with environmental signals.
-%Less than 1\% of disease is associated with genetics. 
-Over 90\% of disease is a total reflection of the environment.% and especially our programming.
-%the disempowering, self-sabotaging behaviors that we acquired in the first 7 years.
-%the cell membrane through receptors picking up the signals and translating them into biology, which then sends signals into the nucleus, which then controls the genetic activity.
-The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression. 
-%Carcinogenesis will occur if the reprogramming is persistent for a longer time.
-Moreover, long-term stress could be correlated with cancer metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021},
-and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}.(see Figure \ref{fig:figure5}) %HNSCC
-Adverse psychosocial experiences in early life, such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased risk of diabetes, heart disease, cancers, and psychiatric illnesses.
-The possible molecular mechanisms could be also related with the mind-brain-body axis\cite{Berens2017}.
-%Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}
-%%%%%
-
-%% TCGA new holistic features %%%%%
-Our current \acrshort{hnscc} study summarizes that six candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors.
-The prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort.
-The important input $X_1...X_n$ should be patients' features: age, specific six gene expressions, clinical T stage, and surgical margin so far.
-When we consider the survival prediction model in holistic manner,
-ground truth Y (e.x. patient's survival):\\[0.5cm]
-%Y$:\\[0.3cm]
-$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\[0.5cm]
-Gene expression is not an independent $X_{mrna}$. It could be correlated with other (for example)\\ $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{empathy}$ factors.\\
-There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
-%We wish the TCGA does collect more holistic features from their participants in the future.
-%依舊是以管窺天
-% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
-%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
-We suggest TCGA should cover more holistic features:
-cortisol is one of the most common objective outcomes studied in psychoneuroimmunological (PNI) factor, interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, and heart rate variability (HRV).
-The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
-%冤親債主的意念 unknown X factors 回到我們的文章
-Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.
-
-% holistic EHR
-Moreover, we encourage physicians to write their electric healthcare record (EHR) in a "holistic way".
-% Deep Patient:  
-Deep learning can convert EHR to the Fast Healthcare Interoperability Resources (FHIR) format\cite{Rajkomar2018}\cite{HealthLevelSeven2019} for handling free-text notes by physicians.
-Deep learning can also derive patient representations that offer improved clinical predictions\cite{Miotto2016}.
-%=> Level 4 Record-keeping and Data Exchange for the healthcare process (clinical data) %Under HL7, RESTful
-%Allergy, Problem,
-%Procedure,
-%CarePlan/Goal,
-%ServiceRequest,
-%Family History,
-%Risk Assessment (APGAR, Glasgow coma scale)
-%condition: physical, mental
-%{observations: 
-%vital signs, 
-%body temperature, body weight and body height, 
-%x-ray, 
-%laboratory data, 
-%pulse oximetry, 
-%ECG, EEG, EMG, 
-%clinical findings (symptom and sign), 
-%tobacco exposure, family support, cognitive status and pregnancy status.
-%death assertion
-%HIV, HBV, HCV status
-%}
-%https://mos2718.github.io/FHIRspec/Index.html
-%https://www.hl7.org/fhir/patient.html
-%https://mos2718.github.io/FHIRspec/Spec/Patient/EHR_Patient.docx
-Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
-
-In Taipei Medical University Hospital, holistic-enabled EHR has been designed as the holistic dental chart for our outpatient with psycho-social-spiritual evaluation\cite{Ling-ChengMong2021}:\\
-1. Emotional: stable/depression/ anxiety/ agitated/ perplexed\\
-2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment\\
-3. Social: (disturbing living/ disturbing working/ disturbing other life aspect)\\
-4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind\\
-5. Self-expectation: lack of confidence/ low self-esteem/ social-withdrawal\\
-6. Impact to life: financial problem/ family problem\\
-7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[0.1cm]
-
-In personal history section of admission note for inpatient:\\
-<Habits>\\
--Tobacco: \underline{ }\underline{ } pack/day for \underline{ }\underline{ } years\\
--Alcohol drinking: Occasionally\\
--Betel nuts: \underline{ }\underline{ } nuts/day for \underline{ }\underline{ } years\\
-<Social/Economic Evaluation>\\
--Living condition: Living with family\\
--Family support: Well\\
--Main caregiver: Spouse\\
--Financial support: Sufficient\\
-<Psychological Evaluation>\\
-Stable but worry about this oral lesion\\
-Suspected to be abuse or neglected victim: negative\\
-<Spiritual Assessment>\\
-Religion: Nil\\
-Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{MyColorPar}{red}
-The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
-\end{MyColorPar}
+% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
+The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} shows which genes should be retained for subsequent univariate and multivariate analysis.
+% of Cox modeling
+It ensures the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
+Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
+\end{MyColorPar} % red
 
@@
 
-% reviewer comment 
+% reviewer comment; Answer 2-4 (Cox regression)
 \begin{MyColorPar}{red}
-%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
-The Cox proportional-hazards model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
-It allows to analyze survival with respect to one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
+%The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
+It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
 % Classification trees and artificial neural networks in survival analysis
 The Cox model is also accounting for confounding factors\cite{Magen2019}.
-It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x. death) at time t. It can be estimated as follow:
+It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x., death) at time t. It can be estimated as follow:
 
@@
 
-Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
-
-Univariate Cox proportional regression model, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival (OS) individually.
+Thus, the biomarker discovery strategy is survival modeling through a collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
+
+Univariate Cox proportional regression model, using the "coxph" function in R package "survival", has been applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival individually.
+
+% dimension reduction? feature selection for further multivariate Cox modeling =>
+%Least absolute shrinkage and selection operator (LASSO) is a biased estimation tool for data with complex collinearity.
+It can select variables and estimate parameter simultaneously and better solve the multicollinearity problem in regression analysis [19].
+Thus, we used the LASSO Cox regression analysis to decrease the number of IRGPs by R package glmnet.
 
 In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
-All covariates has been pool in the hazard function h(t) to estimate their impact on the overall survival.
-\end{MyColorPar}
+All covariates have been pooled in the hazard function h(t) to estimate their impact on the overall survival.
+\end{MyColorPar} % red
 %%
@@
 
+\begin{MyColorPar}{red}
+GSE65858 is a dataset for candidate selection in our workflow.
+The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
+R package of GEOquery\cite{Sean2007} was used to
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
+GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
+There are 270 HNSCC participants involved in this cohort.
+%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
+%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
+The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009).
+% (RefSeq)
+GSE65858 is a dataset for candidate selection in our workflow.
+We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
+\end{MyColorPar} % red
+
 Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
-we analysed GSE2837 dataset (\acrfull{ncbi} GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
+GSE2837 HNSCC dataset (microarray gene expression by Affymetrix X3P chips U133\_X3P) has 28 participants and RFS information. 
+Using PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a} for the validation of candidates.
 %??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
 %https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005)
-microarray gene expression (by Affymetrix X3P chips U133\_X3P).
+%The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005).
 %and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.

### 2021-06-29 main0.tex
fixed compiler problems

--- 2021-06-28 main.tex
@@
 
-Head and neck squamous cell carcinoma (\acrshort{hnscc}), including oral, oropharyngeal, and hypopharyngeal origin, is the fourth leading cancer causes of death for males in Taiwan\cite{MOHW_death2017}.
-The age-standardized incidence rate of \acrshort{hnscc} in males is 42.43 per 100,000 persons\cite{MOHW_incidence2018}.
+Head and neck squamous cell carcinoma (\acrshort{hnscc}), including oral, oropharyngeal, and hypopharyngeal origin, is the fourth leading cancer causes of death for males in Taiwan\cite{MOHWdeath2017}.
+The age-standardized incidence rate of \acrshort{hnscc} in males is 42.43 per 100,000 persons\cite{MOHWincidence2018}.
 % chemotherapy => systemic therapy
@@
 %\cite{SeanDavis;MartinMorgan2020}
-\end{MyColorPar} % the rest moved into materials and methods
+\end{MyColorPar} % red; the rest moved into materials and methods
 
@@
 \begin{MyColorPar}{red}
-\subsubsection{From TCGA to expression biomarkers} % from Answer 2-6 minor2
+%\subsubsection{From TCGA to expression biomarkers} % from Answer 2-6 minor2
 Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.
@@
 Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\
-\end{MyColorPar}
+\end{MyColorPar} % red
 
@@
 %\subsubsection{Figure 1:h}
-\begin{figure}[hp]
+\begin{figure}[hbt!]
 \centering
@@
 \bcaption{A workflow of \acrshort{hnscc} biomarker discovery}
-{The workflow includes data retrieval from TCGA GDC data portal, data process with merging and cleaning,% should be modified aggressively according to different sources of database)
-then performing the survival analyses (within \textcolor{yellow}{yellow} square).
+{The workflow includes data retrieval from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses (within \textcolor{yellow}{yellow} square).
 The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} values (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling.
-The candidate selection performs 1) dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses;
-2) survival analyses of the other HNSCC dataset (GSE6585) using Kaplan-Meier estimate (KM, with FDR correction) and Cox modeling (CoxHR).\\
+The candidate selection performs (1) dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses;
+(2) survival analyses of the other HNSCC dataset (GSE6585) using Kaplan-Meier estimate (KM, with FDR correction) and Cox modeling (CoxHR).\\
 The selected genes have been validated by third HNSCC cohort (GSE2837).
@@
 %\subsubsection{Figure 2:h}
-\begin{figure}[hp]
+\begin{figure}[hbt!]
 \centering
@@
 \end{figure}
+\clearpage
 
@@
 % Please add the following required packages to your document preamble:
-\begin{table}[ht]
+\begin{table}[hbt!]
 \centering
@@
 
-\begin{table}[hp]
+\begin{table}[hbt!]
 \centering
@@
 Selection criteria (fit all):\\
-1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;\\
-2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in TCGA cohort;\\
-3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in GSE65858 cohort
+(1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;\\
+(2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in TCGA cohort;\\
+(3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in GSE65858 cohort
 \end{tabular}
@@
 % and a new Figure 4
-\begin{figure}[ht]
+\begin{figure}[hbt!]
 
@@
 %(P-value Significant codes is denoted as  0.01 mark as *; 0.001 mark as **; if $<$0.001  mark as ***)
-\begin{table}[hp]
+\begin{table}[hbt!]
 \centering
@@
 Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 6 genes:\\ % SurvExpress 有類似的結果:
-1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
+(1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
 %, STIP1 (0.001), DKC1 (0.01);\\
 %DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-2) better prognosis: FCGBP (0.001).\\
+(2) better prognosis: FCGBP (0.001).\\
 %ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
@@
 %*** make Figure 5 holistic: Figure_5_holisticCare.pdf
-\begin{figure}[hp]
+\begin{figure}[hbt!]
 \centering
@@
 \end{figure}
+\clearpage
 %meridian and emotion has mutual reaction
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{paracol}
+\end{paracol}% {2} column
 \reftitle{References}

### 2021-07-01 Cover_letter_JPM.tex
fixed compiler problems
Updates from Overleaf

@@
 % https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f
+
+\newenvironment{MyIndent}
+{\par\leftskip1cm\relax\rightskip1cm\relax}
+{\par\leftskip0cm\relax\rightskip0cm\relax}
+
 \usepackage{tikz-imagelabels} % for  tikz
@@
 %%% for abbreviations, or acronyms
-\usepackage[automake, acronym, nopostdot]{glossaries} 
+\usepackage[acronym, nopostdot]{glossaries} 
 %\usepackage{glossary-inline}
@@
 
+\begin{MyIndent}
 \begin{MyColorPar}{red}
 " %discussion: the third limitation
-There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
+There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
 such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
@@
 "
-
+\end{MyColorPar} %red
+\end{MyIndent}
 %身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
@@
 
-\end{MyColorPar} %red
 \end{MyColorPar} % blue
@@
 
+\begin{MyIndent}
 \begin{MyColorPar}{red}
@@
 \end{MyColorPar} % red
+\end{MyIndent}
 
@@
 
-(In the section of Materials and Methods)\\
+\textcolor{blue}{In the section of Materials and Methods}\\
 %RefSeq Release 38 (November 7, 2009)  GSE65858
@@
 The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
-R package of GEOquery\cite{Sean2007} was used to
-download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
+R package of \\GEOquery\cite{Sean2007} was used to
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/\\geo2r/?\\acc=GSE65858). 
 GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
@@
 
-(In the section of Results)\\
+\textcolor{blue}{In the section of Results}\\
 "
@@
 Please see Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
-"
+"\\[0.3cm]
 %The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model
@@
 
-(In the Discussions section)\\
+\textcolor{blue}{In the Discussions section}\\
 %[more in the discussion section]
@@
 % GEPIA1/2 contact us: tangzefang@pku.edu.cn
-Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\
-
+Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.
+"
 %DEGs to hub: The 230 differentially expressed genes and 12 hub genes were subjected to functional and pathway enrichment analyses. Then hub genes for survival analyses.
@@
 %
-"
 
@@
 \end{MyColorPar} % end of red
+\end{MyIndent}
 
@@
 
-\section{end_document}
+%\section{end_document}
 \end{document}

### 2021-07-01 main.tex
Updates from Overleaf

@@
 %=================================================================
+\documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi} 
 % pm-1174473
 % Journal of Personalized Medicine, JPM
-\documentclass[jpm,article,submit,moreauthors,pdftex]{Definitions/mdpi}
-\maxdeadcycles=1000 % Output loop---200 consecutive dead cycles.
 
@@
 
+%=================================================================
+% MDPI internal commands
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{1}
+\issuenum{1}
+\articlenumber{0}
+\pubyear{2021}
+\copyrightyear{2021}
+%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
+\datereceived{} 
+\dateaccepted{} 
+\datepublished{} 
+%\hreflink{https://doi.org/} % If needed use \linebreak
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
+
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Tex
+\maxdeadcycles=1000 % Output loop---200 consecutive dead cycles.
+
+\usepackage{amsmath,amsfonts}
 \usepackage{tikz-imagelabels} % for  tikz
@@
 
-%\begin{MyColorPar}{red}
-%\end{MyColorPar}
-
-%\usepackage[upplemac]{inputenc} %applemac support if unicode package fails
-%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
-%...
-%\usepackage{graphicx}
-%\DeclareGraphicsExtensions{.pdf,.png} % for high-resolution PDF image
-%\usepackage{hyperref}
+\usepackage{hyperref}
 \usepackage{xr}
@@
 \myexternaldocument{Supplementary_figures} %.tex .aux
-
-%\usepackage{url}
 
@@
 %\newcommand{\abbrlabel}[1]{\makebox[3cm][l]{\textbf{#1}\ \dotfill}}
-\newenvironment{abbreviation}%{\begin{list}{}{\renewcommand{\makelabel}{\abbrlabel}}}{\end{list}}
-% \newenvironment{<name>}[<number>][<default>]
-
+\newenvironment{abbreviation}
+
+%%%%%%%%%%%%% Define abbreviation
 \makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
@@
 %=================================================================
-\firstpage{1} 
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother
-\pubvolume{1}
-\issuenum{1}
-\articlenumber{0}
-\pubyear{2021}
-\copyrightyear{2021}
-%\externaleditor{Academic Editor: Firstname Lastname}
-\datereceived{} 
-\dateaccepted{} 
-\datepublished{}
-
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
-
-%=================================================================
 %% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
@@
 \Title{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}
-%\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
 
@@
 \TitleCitation{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}
-%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
 
@@
 
+%%%%%%%%%%
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{
-The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
+\abstract{The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
 It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis.
@@
 There are few clinicopathological features available on their pre-processed data sets.
-
 We developed a workflow that includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
 The independent HNSCC dataset has been used to validate this discovery.
-
 Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes.
@@
 According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, IL19, and FCGBP, are significantly associated with the patients' overall survival.
-We suggest the transcriptomic analysis could help for biomarker discovery.
-}
-
-%Survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
-It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression.
-Usually, an optimization algorithm for cutoff determination has been set at the median or quantiles of RNA sequencing value.
-%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
-% validated by the other HNSCC cohort:
-%1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
-%2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
-
-% row 20: The result showed ten overexpressed genes (symbol as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) are significantly associated with a poor prognosis of overall survival.
-Furthermore, the other ten overexpressed genes (symbol as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
+We suggest the transcriptomic analysis could help for biomarker discovery.}
 
 % Keywords
-\keyword{
-Head and Neck Squamous Cell Carcinoma (HNSCC);
-%Genome Database\sep
-the Cancer Genome Atlas (TCGA);
-Transcriptomic Analysis;
-%RNA-sequencing;
-Survival Analysis;
-Optimal Cutoff;
-Effect Size;
-%Tobacco\sep
-%Cox Proportional Hazards\sep
-%Tumor Aggressiveness\sep
-%Rstudio\sep
-CAMK2N1;
-IL19;
-FCGBP;
-%Biomarker\sep % Discovery\sep
-%Tumor Type-agnostic Therapy\sep
-%Immuno-Oncology\sep
-%Targeted Therapy\sep
-%Systemic Therapy\sep
-%Surgical Margin
-%Holistic Cancer Care;
-%Therapeutic Relationship;
-Mindfulness Meditation
-}
+\keyword{Head and Neck Squamous Cell Carcinoma (HNSCC);
+the Cancer Genome Atlas (TCGA); Transcriptomic Analysis; Survival Analysis; Optimal Cutoff; Effect Size; CAMK2N1; IL19; FCGBP; Mindfulness Meditation}
 
 % I have a graphic abstract: graphic_abstract_pvalueTex.pdf
-% National Cancer Institute.
-Changing the dressing on a patient’s neck.
-https://unsplash.com/photos/IrqLPsxemQ4?utm_source=unsplash&utm_medium=referral&utm_content=creditShareLink (1950).\cite{nci1950}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\globalcounter* % for paracol
+%\globalcounter* % for paracol
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Diversity
+%\LSID{\url{http://}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Applied Sciences:
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data:
+%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
+If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
+In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
+
+%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Toxins
+%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Encyclopedia
+%\encyclopediadef{Instead of the abstract}
+%\entrylink{The Link to this entry published on the encyclopedia platform.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-%\linenumbers
-%\begin{paracol}{2}
-
+%\begin{paracol}{2} % there is no this item here
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
-%%
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=14cm]{graphic_abstract_pvalueTex.pdf}
-%    \caption{(inset image courtesy of National Cancer Institute\cite{nci1950})}
-%    \label{fig:my_label}
-%\end{figure}
 
@@
 According to the phase 3 KEYNOTE-048 study, \acrshort{pdl1} is a validated biomarker used in clinical guidance for candidate selection of pembrolizumab\cite{Burtness2019}\cite{Gavrielatou2020}.
-However, because of the complexity of immune-tumor interaction, \acrshort{ici} has 20\% response rate to \acrfull{pdl1} expressed patients (over 50\% in \acrlong{ihc}, \acrshort{ihc} staining of \acrshort{hnscc})\cite{Swanson2015}\cite{Gavrielatou2020}.
+However, due to the complexity of immune-tumor interaction, \acrshort{ici} has 20\% response rate to \acrfull{pdl1} expressed patients (over 50\% in \acrlong{ihc}, \acrshort{ihc} staining of \acrshort{hnscc})\cite{Swanson2015}\cite{Gavrielatou2020}.
 
@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$).
+Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value \begin{equation}< 0.05 \end{equation}).
 The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
@@
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage % end of Introduction
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
-The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
+The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
 The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
@@
 %Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
+
+%%%%%%%%%%%%%
+\end{paracol}
+\nointerlineskip
+%%%%%%%%%%%%% give wide full-paged tables
 
@@
 % end of result
-
-%Bulleted lists look like this:
-%\begin{itemize}
-%\item	First bullet;
-%\item	Second bullet;
-%\item	Third bullet.
-%\end{itemize}
-
-%Numbered lists can be added as follows:
-%\begin{enumerate}
-%\item	First item; 
-%\item	Second item;
-%\item	Third item.
-%\end{enumerate}
-
-%\subsection{Figures, Tables and Schemes}
-
-%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
-
-%\begin{figure}[H]
-%\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-%\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
-%\end{figure}
-
-% The MDPI table float is called specialtable
-%\begin{specialtable}[H] 
-%\caption{This is a table caption. Tables %should be placed in the main text near to %the first time they are~cited.\label{tab1}}
-%%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-%\begin{tabular}{ccc}
-%\toprule
-%\textbf{Title 1}	& \textbf{Title 2}	& %\textbf{Title 3}\\
-%\midrule
-%Entry 1		& Data			& Data\\
-%Entry 2		& Data			& Data\\
-%\bottomrule
-%\end{tabular}
-%\end{specialtable}
-
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
-
-%\subsection{Formatting of Mathematical Components}
-
-%This is the example 1 of equation:
-
-%\begin{equation}
-%a = 1,
-%\end{equation}
-
-%the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
@@
 
-\end{paracol}
-\nointerlineskip
+%This is the example 2 of equation:
 
@@
 % Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
+%\begin{figure}[H]	
+%\widefigure
+%\includegraphics[width=15 cm]{Definitions/logo-mdpi}
+%\caption{This is a wide figure.\label{fig2}}
+%\end{figure}
 
@@
 \linenumbers
-\switchcolumn[1]
-
-%Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-%\begin{Theorem}
-%Example text of a theorem.
-%\end{Theorem}
-
-%% Example of a proof:
-%\begin{proof}[Proof of Theorem 1]
-%Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-%\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\switchcolumn
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%
 \section{Discussion}
@@
 \begin{MyColorPar}{red}
-There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
+There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
 such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\begin{quote}
+%This is an example of a quote.
+%\end{quote}
+
 \section{Materials and Methods} % 4
@@
 
-%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions} % 5
@@
 %the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
 %% optional: The data presented in this study are available in supplementary material.
 \supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, 
-Figure S1: GSE2837 analysis by PrognoScan, 
-Figure S2: The query results from SurvExpress, 
-Figure S3: The query results from HPA.}
-%Table S1: title, Video S1: title.}
-%S1
-%S2
-%S3
+	Figure S1: \textit{P} value plot of the gene NDFIP1,
+	Figure S2: GSE2837 analysis by PrognoScan,  
+	Table S1: The GSE2837 query results from PrognoScan,
+	Table S2: 10 good guys, % ? don't keep it
+	Video S1: title. A supporting video article is available at doi: link}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{
-%For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``
-%Conceptualization, Michael Hsiao; Funding acquisition, Yu-Chuan (Jack) Li; Methodology, Li-Hsing Chi; Resources, Alexander TH Wu; Software, Li-Hsing Chi; Supervision, Yu-Chuan (Jack) Li; Validation, Michael Hsiao; Writing - original draft, Li-Hsing Chi; Writing - review and editing, Alexander TH Wu.
-Conceptualization, Yu-Chuan (Jack) Li; Data curation, Alexander TH Wu; Formal analysis, Li-Hsing Chi; Investigation, Michael Hsiao; Methodology, Michael Hsiao; Resources, Alexander TH Wu; Software, Li-Hsing Chi and Yu-Chuan (Jack) Li; Supervision, Michael Hsiao and Yu-Chuan (Jack) Li; Writing – original draft, Li-Hsing Chi; Writing – review and editing, Alexander TH Wu.
+\authorcontributions{Conceptualization, Yu-Chuan (Jack) Li; Data curation, Alexander TH Wu; Formal analysis, Li-Hsing Chi; Investigation, Michael Hsiao; Methodology, Michael Hsiao; Resources, Alexander TH Wu; Software, Li-Hsing Chi and Yu-Chuan (Jack) Li; Supervision, Michael Hsiao and Yu-Chuan (Jack) Li; Writing – original draft, Li-Hsing Chi; Writing – review and editing, Alexander TH Wu.
 All authors have read and agreed to the published version of the manuscript.}
-%'' please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.
+
+%\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
+Please note that the Editorial Office might ask you for further information.
+Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals.
+You might also choose to exclude this statement if the study did not involve humans or animals.}
+
+%\informedconsent{Any research article describing a study involving humans should contain this statement.
+Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
+You might also choose to exclude this statement if the study did not involve humans.
+
+%Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
+Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
 
@@
 \acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
-The tables were generated by latex code with the help from https://www.tablesgenerator.com/latex_tables# and https://github.com/JDMCreator/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
-We like to thank Dr. Wen-Chang Wang,
-%https://orcid.org/0000-0003-3124-2136
+The tables were generated by latex code with the help from https://www.tablesgenerator.com/latex\_tables# and
+https://github.com/JDMCreator\\/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
+We like to thank Dr. Wen-Chang Wang, %https://orcid.org/0000-0003-3124-2136
 College of Medical Science and Technology, Taipei Medical University, for bioinformatics consultation and helps. 
@@
 % *** URL Accessed 20 May 2013.
-The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/\newline
-mtbwi/index.do. Accessed 20 May 2020.}
+The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/mtbwi/index.do.  Accessed 20 May 2020.}
 
@@
 \renewcommand*{\glsinlinenameformat}[2]{\glstarget{#1} {\textsc{#2}},}
-\printglossary[type=\acronymtype, title= , nonumberlist, style=inline]
+\printglossary[type=\acronymtype, title= , nonumberlist, style=inline]}
 % Abbreviations
 
-%\begin{tabular}{@{}ll}
-%MDPI & Multidisciplinary Digital Publishing Institute\\
-%DOAJ & Directory of open access journals\\
-%TLA & Three letter acronym\\
-%LD & Linear dichroism
-%\end{tabular}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-%\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
-If the appendix sections contain a heading then change the argument to "yes".
-%\appendix
-%\section{}
-%\subsection{}
-%The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-%\section{}
-%All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{paracol}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{paracol} % {2} column
 \reftitle{References}
@@
 %=====================================
+%\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
+
 \externalbibliography{yes}
 %\bibliography{your_external_BibTeX_file}
-%\bibliographystyle{model1-num-names}
+\bibliographystyle{chicago} %model1-num-names
 \bibliography{TCGA_margin_cutoff.bib, Holistic.bib, Deep_Learning.bib}
 
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-%\begin{thebibliography}{999}
-% Reference 1
-%\bibitem[Author1(year)]{ref-journal}
-%Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-%\bibitem[Author2(year)]{ref-book1}
-%Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 8
-%\bibitem[Author8(year)]{ref-url}
-%Title of Site. Available online: URL (accessed on Day Month Year).
-%\end{thebibliography}
+% If authors have biography, please use the format below
+%\section*{Short Biography of Authors}
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
+%{\textbf{Firstname Lastname} Biography of first author}
+%
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
+%{\textbf{Firstname Lastname} Biography of second author}
 
@@
 \end{document}
-
-% moved from line 363
-
-%latex https://www.latex-tutorial.com/symbols/greek-alphabet/
-%\subsection*{Linear regression in biomarker discovery}
-Linear regression is useful as a concept in biomarker discovery.
-A linear regression equation that relates a Y-variable to n X-variables is written as\\[1cm]
-%\par
-%Highlights
-% https://quicklatex.com
-\begin{flushleft}
-% equation
-%\begin{math}
-
-ground truth Y (e.x. patient's survival):\\[0.5cm]
-%Y$:\\[0.3cm]
-$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
-\linebreak
-\linebreak
-Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
-\\[0.5cm]
-Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
-A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
-Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
-$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
-\linebreak
-%(predicted Y, output) intercept, slope, independent (input) \Times
-%\end{math}
-\end{flushleft}
-Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.\\[1cm]

### 2021-07-01 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
-We modified the paragraphs in the "Material and Methods" section and "Results" section for the analysis of GSE65858.
-We also described "the \textit{P} values are affected by the sample size" in the Discussions section.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
+We modified the paragraphs in the "Materials and Methods" section, and "Results" section for the analysis of GSE65858.
+We also described "the \textit{P} values are affected by the sample size" in the "Discussions" section.
+The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129),
+% results ok
+the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 184) to page 6 (line 208), and
+the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129)
+are the part of the manuscript that has been revised. 
+Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 "
-TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
-The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
-The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
-%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
-%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
-Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
+TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
+A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
+%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, 
+The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
+In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure 2(c), (d)).
+%em dash ---
+These CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN---previous name as KIAA1683, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
 %These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
-The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
+The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separates them on the two-side with significant prognostic impact.
 %During our exploration phase with TCGA cohort, the 20 genes, listed
@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox's HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002
@@
 %This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
-Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
+Conversely, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
 Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
-Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset other than the TCGA cohort.
-Please see Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
+Finally, these 3 candidates were also confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
 "\\[0.3cm]
@@
 We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction section.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised.
+The paragraphs marked in \textcolor{red}{Red} from page 3 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised.
 Also, it is shown here in the following paragraph.\\[0.3cm]
@@
 %%% how other researchers used TCGA to find expression biomarkers
-Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.
+Usually, researchers developed an in-house workflow of gene expression analysis of TCGA data to find HNSCC biomarkers.
 %Workflow of GDCRNATool
@@
 It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC.
-
 %%% https://www.biostars.org/p/153013/
@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$).
+Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves with a log-rank test, and univariate Cox regression to screen prognostic factors.
 The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
@@
 
-First, although \acrshort{tcga} genomics data has been harmonized, 
-%two things were found during our investigating and data cleaning:
-the pre-processing of TCGA RNA-Seq is as follows:
-
+First, although \acrshort{tcga} genomics data were harmonized, 
+% three things were found during our investigating and data cleaning:
+the pre-processing of TCGA RNA-Seq in our workflow has been done as follows: 
 \begin{outline}
-\1 HNSCC samples without complete clinical information have been removed;\\
-% or 50\%
-\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded;\\
-
-\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.\\
-After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that gene ID (9906), gene ID (728661), and their expression values were saved together under the entity of gene symbol "SLC35E2".
+\1 HNSCC samples without complete clinical information have been removed;
+\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded; % or 50\%
+\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.
+\end{outline}
+After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that expression value of two genes (gene ID: 9906 and gene ID: 728661) was saved together under the entity of gene symbol "SLC35E2".
 The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
@@
 %NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
-According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
+According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?\\queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
 % https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
 % keyword: (SLC35E2) AND "Homo sapiens" 
-SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!\\/hgnc\_id/HGNC:20863).
-Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
-% updated on 18-May-2021
-\end{outline}
+SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\\\#!/hgnc\_id/HGNC:20863).
+Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in this TCGA HNSCC dataset from 20499 to 20500.
+% updated on 18-May-2021 then 01 July 2021
 
@@
 %ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
-Third, we have analyzed the error log of the cutoff finding and Cox modeling, 
-the results show that several technical problems could halt the program running.
-Those include:
+Third, we analyzed the error log during the cutoff finding and Cox modeling, 
+the result shows that program running could be halted by several technical problems.
+These include:
 \begin{outline}
 
-\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression
-\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate.
+\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression;
+\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;
 %1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
@@
 % and NaN imputation as median
-\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow)
+\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow).
 \end{outline}
-, which could not be detected prior to the program running.
+These technical problems could not be detected prior to program running.
 It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity

### 2021-07-01 main.tex
Updates from Overleaf

@@
 We developed a workflow that includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
-The independent HNSCC dataset has been used to validate this discovery.
 Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes.
@@
 According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, IL19, and FCGBP, are significantly associated with the patients' overall survival.
+The other independent HNSCC data were also used to validate this discovery.
 We suggest the transcriptomic analysis could help for biomarker discovery.}
@@
 \keyword{Head and Neck Squamous Cell Carcinoma (HNSCC);
-the Cancer Genome Atlas (TCGA); Transcriptomic Analysis; Survival Analysis; Optimal Cutoff; Effect Size; CAMK2N1; IL19; FCGBP; Mindfulness Meditation}
+the Cancer Genome Atlas (TCGA); Transcriptomic Analysis; Survival Analysis; Optimal Cutoff; Effect Size; \acrfull{CAMK2N1}; \acrfull{IL19}; \acrfull{FCGBP}; Mindfulness Meditation}
 
@@
 %% TP53 gene => p53 protein; mutation of TP53
-Accumulative knowledge showed that some biomarkers have prognostic significance in \acrshort{hnscc}.
+Accumulative knowledge shows that some biomarkers have prognostic significance in \acrshort{hnscc}.
 For example, node-negative \acrshort{hnscc} patients with p53 overexpression were found to hold lower survival\cite{DeVicente2004}.
@@
 From 2000 to 2006, the first anti-\acrshort{egfr} antibody-drug (cetuximab) has been developed and combined with radiotherapy, known as bio-\acrshort{rt}, to increase survival of unresectable locoregionally advanced disease\cite{Bonner2006a}.
-The systemic therapy of cetuximab plus platinum-fluorouracil chemotherapy (EXTREME regimen) has improved overall survival when given as first-line treatment in patients with recurrent or metastatic \acrshort{hnscc}\cite{Vermorken2008}\cite{Rivera2009}.
+The systemic therapy of cetuximab plus platinum-fluorouracil chemotherapy (EXTREME regimen) improves overall survival when given as first-line treatment in patients with recurrent or metastatic \acrshort{hnscc}\cite{Vermorken2008}\cite{Rivera2009}.
 It has been approved by the \acrshort{us} \acrfull{fda} since 2008.
@@
 Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients.
-So far, cetuximab is still the only drug of choice with proven efficacy, which has targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
+Before the year 2019, cetuximab is still the only drug of choice with proven efficacy, which has targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
 
@@
 
-According to our proteomic study between 2010 to 2017, \acrfull{tmsb4x} was reported to be related to tumor growth and metastasis of \acrshort{hnscc}\cite{Chi2017}.
+According to our previous proteomic study from 2010 to 2017, \acrfull{tmsb4x} was reported to be related to tumor growth and metastasis of \acrshort{hnscc}\cite{Chi2017}.
 It was also reported by the subsequent investigations that \acrshort{tmsb4x} has engaged in tumor aggressiveness through \acrfull{emt} on pancreatic\cite{Zhang2008}, gastric\cite{Ryu2012}, colorectal\cite{Gemoll2015}, lung\cite{Huang2016}, ovarian\cite{Chu2019}, and melanoma\cite{Makowiecka2019} cancers.
@@
 
-\begin{MyColorPar}{red}
-The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
+%\begin{MyColorPar}{red}
+The Cancer Genome Atlas (\acrshort{tcga}) profiled \acrshort{hnscc} (528 participants) clinical and genomic data, which were standardized and are available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
 %\cite{SeanDavis;MartinMorgan2020}
-\end{MyColorPar} % red; the rest moved into materials and methods
-
+%\end{MyColorPar} % red; the rest moved into materials and methods
 % to summarize the advantages of its use.
-The highlights of the advantages of applying the TCGA data for cancer biomarker identification include:
+The highlight of the advantages of applying the TCGA data for cancer biomarker identification includes:
 \begin{outline}
@@
 There are many physical and social features of patients available for survival modeling. % ($X_1 ... X_n$)
-The whole-genome sequencing data has been harmonized across all GDACs.
+The whole-genome sequencing data were harmonized across all \acrfull{gdac}s.
 Many databases adopt the essential demographic data from TCGA since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
@@
 It might be getting help quickly from the research community for trouble-shooting.
-\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing\cite{Tomczak2015}.\\[0.5cm]
+\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data were already published and keep growing\cite{Tomczak2015}.\\[0.1cm]
 \end{outline}
@@
 %\subsubsection{From TCGA to expression biomarkers} % from Answer 2-6 minor2
-Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.
+Usually, researchers developed an in-house workflow of gene expression analysis of TCGA data to find HNSCC biomarkers.
 They have several genes that are differentially expressed between tumor and normal samples.
 It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC
-
 % Rstudio\cite{Loraine2015a}
 Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
-Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.x. GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
+Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.g., GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
 % IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
-%e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
+%e.g., GSE30784: 167 HNSCC samples and 45 normal controls). 
 They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value \begin{equation}< 0.05 \end{equation}).
+Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves with a log-rank test, and univariate Cox regression to screen prognostic factors.
 The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
@@
 %, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
-), GEPIA2021\cite{Li2021} (available at http://\\gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
+), GEPIA2021\cite{Li2021} (available at http://gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
 % GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
@@
 They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
-SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.x.
-\acrshort{tcga}).
+SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.g., \acrshort{tcga}).
 After downloading the survival results, they could curate plots and tables carefully.
 It is not possible to scan the whole human protein-coding genome in this way.
-The web-based tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
+The web-based tools might set a cutoff at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses.
 There are several visualization software or R packages which deal with cutoff determination\cite{Abel1984}, %CRITLEVEL
@@
 %NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
-According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
+According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?\\queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
 % https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
 % keyword: (SLC35E2) AND "Homo sapiens" 
-SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!\\/hgnc\_id/HGNC:20863).
-Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
+SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!/hgnc\_id/HGNC:20863).
+Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in this TCGA HNSCC dataset from 20499 to 20500.
 % updated on 18-May-2021
-\end{outline}
+%\end{outline}
 
@@
 Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
-The independent HNSCC dataset has been used to validate this discovery.
+The independent HNSCC datasets were used to validate this strategy.
 The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.
@@
 The candidate selection performs (1) dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses;
-(2) survival analyses of the other HNSCC dataset (GSE6585) using Kaplan-Meier estimate (KM, with FDR correction) and Cox modeling (CoxHR).\\
-The selected genes have been validated by third HNSCC cohort (GSE2837).
+(2) survival analyses of the other HNSCC dataset (GSE65858) using Kaplan-Meier estimate (KM, with FDR correction) and Cox modeling (CoxHR).\\
+The selected genes were validated by third HNSCC cohort (GSE2837).\\
 (HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
@@
 \begin{MyColorPar}{red}
-TCGA HNSCC cohort has been applied for exploration of the biomarker candidate.
-The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
-The 967 genes were kept by criteria of unadjusted \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
+TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
+A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
+%By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
+The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure \ref{fig:figure2}(a), (b), initial trial).
+In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
+
+%\subsubsection{Figure 2:h}
+\begin{figure}[hbt!]
+\centering
+\includegraphics[width=14cm]{Figure2.pdf}
+\bcaption{The initial progress of candidate selection from TCGA \acrshort{hnscc} cohort.}{The \textit{P} values of Kaplan-Meier survival is one of the selection criteria.
+The effect size is estimated by Cox's hazard ratio.
+Initial trial step: (a) univariate HR versus \textit{P} value; (b) multivariate HR versus \textit{P} value.
+After stringent criteria by Bonferroni-adjusted \textit{P} value, and the Cox's HR, few top-ranked genes are shown in
+(c) univariate HR versus Bonferroni-adjusted \textit{P} value; and (d) multivariate HR versus Bonferroni-adjusted \textit{P} value.\\
+(TCGA: \acrlong{tcga}; HR: hazard ratio)}
+\label{fig:figure2}
+\end{figure}
+
 %The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
 %The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
-Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
+%em dash ---
+These CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN---previous name as KIAA1683, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
 %These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
-The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separated them on the two-side with prognostic impact.
+The plot reveals that the top 20 genes (Bonferroni-adjusted \textit{P} $< 0.05$) are located on the peaks. At the same time, Cox's HR separates them on the two-side with significant prognostic impact.
 %During our exploration phase with TCGA cohort, the 20 genes, listed
@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 out of those 20 genes discovered in the TCGA cohort), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox's HR ($> 1.8$ or $< 0.65$) (please see Table \ref{tab:table_top3_GSE65858}).
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002
@@
 %candidate_fdr100
-and also see Figure \ref{fig:hazards534}).
 However, the significance of the other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
 %This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
-Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
+Conversly, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
 Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
-Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset other than the TCGA cohort.
-Please see Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
+Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
 \end{MyColorPar} % end red
 
-%\subsubsection{Figure 2:h}
-\begin{figure}[hbt!]
-\centering
-\includegraphics[width=14cm]{Figure2.pdf}
-\bcaption{TCGA \acrshort{hnscc} Cox's hazard ratio and \textit{P} value plot.}
-{(a) Univariate HR versus uncorrected \textit{P} value; (b) Multivariate HR versus uncorrected \textit{P} value; (c) Univariate HR versus Bonferroni corrected \textit{P} value; and (d) Multivariate HR versus Bonferroni corrected \textit{P} value.}
-\label{fig:figure2}
-\end{figure}
-\clearpage
-
+%\clearpage
+
+%\subsubsection{Figure 3:h} % new figure 3
 %Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
@@
 \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
-    This cohort has been applied for exploration of the candidate biomarkers.
-    Total 9416 genes has %\acrshort{fdr}-
+    This cohort was applied for exploration of the candidate biomarkers.
+    A total of 9416 genes have %\acrshort{fdr}-
     unadjusted \textit{P} value less than 0.05.
@@
     The 22 genes, listed on the side, have hazard ratio between 0.6 and 1.5.\\
-    Remarks:\\
-    \textcolor{red}{Red spots}: $HR > 1.0$;
-    \textcolor{green}{Green spots}: $HR < 1.0$;\\
-    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
-    Y-axis: HR of Cox proportional hazard regression model\\
+    (\textcolor{red}{Red spots}: $HR > 1.0$,
+    \textcolor{green}{Green spots}: $HR < 1.0$);\\
+    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed));\\
+    (Y-axis: HR of Cox proportional hazard regression model.)
     }
@@
 \end{figure}
-\clearpage
-
-% tables 1  3
+%\clearpage
+
+%\begin{figure}
+
+%    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
+%    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{This cohort has been applied for exploration of the candidate biomarkers.
+%    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
+%    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.5$.\\
+%    Remarks:\\
+%    \textcolor{red}{Red spots}: $HR > 1.0$;
+%    \textcolor{green}{Green spots}: $HR < 1.0$;\\
+%    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
+%    Y-axis: HR of Cox proportional hazard regression model\\}
+%\label{fig:figure3}
+%\label{fig:hazards3} %TCGA volcano
+%\end{figure}
+% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
+% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.
+
+%\clearpage
+
+%CAMK2N1
+Our top 1 candidate is \acrfull{CAMK2N1}.
+The Kaplan-Meier curve reveals that 152 patients bearing the higher expression of \acrshort{CAMK2N1} were suffered from only 35\% of 5-year \acrshort{os} rate.
+In comparison, the other 262 patients with lower expression had a better prognosis (Bonferroni-adjusted \textit{P} $= 0.002$) (see Figure \ref{fig:figure4}(a)).
+Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot shows that the uncorrected 147 \textit{P} values ($< 0.05$) have been estimated by a serial cut from 144 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, cutoff engine).
+The smallest \textit{P} value (\num{2.97e-7}), when cut at n = 262 (63.3\% of total cohort 414, with the cutoff value 0.027 in \acrlong{rsem}, \acrshort{rsem}), has been defined as an optimal \textit{P} value.
+The plot in Figure \ref{fig:figure4}(b) shows a "backlash" curve with the half of values below \num{1.0e-3}.
+%IL19
+Conversely, the most associated gene with better survival is \acrfull{IL19}.
+In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 215 patients bearing the higher expression of \acrshort{IL19} had 60\% of 5-year OS survival rate (Bonferroni-adjusted \textit{P} $ = 0.002$).
+The sliding-window cutoff selection generated cumulative \textit{P} value plot in Figure \ref{fig:figure4}(d).
+This plot reveals a special "S" curve with a acute bending on the middle portion (we will discuss this finding in the Discussions section).
+The 161 uncorrected \textit{P} values were estimated by a serial cut from 125 to 286 for grouping the cohort.
+The smallest \textit{P} value (\num{3.73e-7}), when cut at n = 199 (48.1\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.147 \acrshort{rsem} of \acrshort{rnaseq}.
+% FCGBP
+The third candidate is \acrfull{FCGBP}.
+It relates with also better survival in both the TCGA and GSE65858 cohorts.
+In Figure \ref{fig:figure4}(e), a Kaplan-Meier curve reveals 282 patients bearing the higher expression of \acrshort{FCGBP} had 60\% of 5-year OS survival rate (Bonferroni-adjusted \textit{P} $ = 0.008$).
+The sliding-window cutoff selection generated cumulative \textit{P} value plot in Figure \ref{fig:figure4}(f).
+This plot has a "W-shaped" curve with the most majority of values far below \num{1.0e-3}.
+The 166 uncorrected \textit{P} values were estimated by a serial cut from 125 to 290 for grouping the cohort.
+The smallest \textit{P} value (\num{1.21e-6}), when cut at n = 132 (31.9\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.472 \acrshort{rsem} of \acrshort{rnaseq}.
+%The second candidate, which improving patient survival, is ZNF266.
+%\subsubsection{Tables} in main article
+
+%\subsubsection{Figure 4:h}
+% *** Adjusted P value = 0.002 ; drawing by tikz
+% https://tex.stackexchange.com/questions/9559/drawing-on-an-image-with-tikz
+
+%font code: Computer Modern Sans Serif		cmss
+
+% and a new Figure 4
+\begin{figure}[hbt!]
+
+% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
+\setlength{\unitlength}{1cm}
+\begin{picture}(15, 20) %(1,0.55038404)%
+\centering
+  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_IL19_FCGBP.pdf}}%
+  \put(2.5, 14.3){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{1.63e-05}}%CAMK2N1
+    \put(2.5, 9.45){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{6.54e-06}}%IL19
+    \put(2.5, 4.55){\fontfamily{qcr}\selectfont
+  \tiny *\textit{P} = \num{4.83e-05}}%FCGBP
+
+%\begin{annotationimage}{width=15cm}{Figure_4_CAMK2N1_IL19_FCGBP.pdf}
+%\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
+%\draw[annotation left = {Aries at 0.3}]
+
+%\end{annotationimage}
+\end{picture}%
+
+\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
+{The Kaplan-Meier curves of (a) CAMK2N1, (c) IL19, and (e) FCGBP under optimal \textit{P} value. 
+%((b) the cutoffs derived from it's cumulative \textit{P} value plot).
+%(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value;
+%((d) the cutoffs derived from it's cumulative \textit{P} value plot).
+%(e) Kaplan-Meier plot of FCGBP under optimal \textit{P} value.\\
+%The optimal cutoff value for CAMK2N1 is 
+The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
+shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
+(* \textit{P}: \textit{P} value adjusted by \acrlong{fdr}, \acrshort{fdr})
+}
+\label{fig:figure4}
+\end{figure}
+
+% tables 1  3 2
 %%% tables
@@
 
-%\subsubsection{Table3/legend} or Table 2
-
-%\subsubsection{Figure 3:h}
-\begin{figure}
-    \centering
-    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
-    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
-%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
-%Y axis: multivariate hazard ratio from Cox proportional regression model.
-%Dotted line: significant Bonferroni corrected \textit{P} value. 
-%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$).
-\textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
-    This cohort has been applied for exploration of the candidate biomarkers.
-    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
-    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.5$.\\
-    Remarks:\\
-    \textcolor{red}{Red spots}: $HR > 1.0$;
-    \textcolor{green}{Green spots}: $HR < 1.0$;\\
-    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
-    Y-axis: HR of Cox proportional hazard regression model\\
-    }
-%\label{fig:figure3}
-\label{fig:hazards3} %TCGA volcano
-\end{figure}
-% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
-% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.
-
-\clearpage
-
-Our top 1 candidate is \acrfull{CAMK2N1}.
-The Kaplan-Meier curve reveals 152 patients bearing the higher expression of \acrshort{CAMK2N1} were suffered from only 35\% of 5-year \acrshort{os} rate.
-In comparison, the other 262 patients with lower expression (the cutoff at 0.027(RSEM)) had a better prognosis (adjusted \textit{P} = $0.002$) (see Figure \ref{fig:figure4}(a)).
-Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot shows that the uncorrected 147 \textit{P} values ($< 0.05$) have been estimated by a serial cut from 144 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, cutoff engine).
-The smallest \textit{P} value (\num{2.97e-7}), when cut on n=262 (63.3\% of 414), has been defined as an optimal \textit{P} value.
-Conversely, the most associated gene with better survival is \acrfull{IL19}.
-In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 215 patients bearing the higher expression of \acrshort{IL19} had 60\% of 5-year OS survival rate (adjusted \textit{P} = $0.002$).
-The cutoff finding procedure (cutofFinder\_func.R) generated cumulative \textit{P} value plot in Figure \ref{fig:figure4}(d).
-The 161 uncorrected \textit{P} values were estimated by a serial cut from 125 to 286 for grouping the cohort.
-The smallest \textit{P} value (\num{3.73e-7}), when cut on n=199 (48.1\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.147(RSEM) of \acrshort{rnaseq}.
-%The second candidate, which improving patient survival, is ZNF266.
-%\subsubsection{Tables} in main article
-
-%\subsubsection{Figure 4:h}
-% *** Adjusted P value = 0.002 ; drawing by tikz
-% https://tex.stackexchange.com/questions/9559/drawing-on-an-image-with-tikz
-
-%font code: Computer Modern Sans Serif		cmss
-
-% and a new Figure 4
-\begin{figure}[hbt!]
-
-% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
-\setlength{\unitlength}{1cm}
-\begin{picture}(15, 20) %(1,0.55038404)%
-\centering
-  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_IL19_FCGBP.pdf}}%
-  \put(2.5, 14.3){\fontfamily{qcr}\selectfont
-  \tiny *\textit{P} = \num{1.63e-05}}%CAMK2N1
-    \put(2.5, 9.45){\fontfamily{qcr}\selectfont
-  \tiny *\textit{P} = \num{6.54e-06}}%IL19
-    \put(2.5, 4.55){\fontfamily{qcr}\selectfont
-  \tiny *\textit{P} = \num{4.83e-05}}%FCGBP
-
-%\begin{annotationimage}{width=15cm}{Figure_4_CAMK2N1_IL19_FCGBP.pdf}
-%\includegraphics[width=15cm]{Figure_4_CAMK2N1_IL19.pdf}
-%\draw[annotation left = {Aries at 0.3}]
-
-%\end{annotationimage}
-\end{picture}%
-
-\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
-{The Kaplan-Meier curves of (a) CAMK2N1, (c) IL19, and (e) FCGBP under optimal \textit{P} value. 
-%((b) the cutoffs derived from it's cumulative \textit{P} value plot).
-%(c) Kaplan-Meier plot of IL19 under optimal \textit{P} value;
-%((d) the cutoffs derived from it's cumulative \textit{P} value plot).
-%(e) Kaplan-Meier plot of FCGBP under optimal \textit{P} value.\\
-The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
-shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
-* \textit{P}: Adjusted \textit{P} value by \acrfull{fdr}
-}
-\label{fig:figure4}
-\end{figure}
-
-\clearpage
-
-Table %\ref{table:table1}
-\ref{tab:newTable1} shows ten overexpressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value.
-Six out of ten genes has been validated by using GSE2837.
-We found those six candidates have the Cox's univariate and multivariate HR above 1.914.
+%\clearpage
+
+%Table %\ref{table:table1}
+%\ref{tab:newTable1} shows ten overexpressed genes are associated with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value.
+%Six out of ten genes has been validated by using GSE2837.
+%We found those six candidates have the Cox's univariate and multivariate HR above 1.914.
 %There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
@@
 
+%\subsubsection{Table3/legend} or Table 2
+% Table 2
 %\subsubsection{Table3/legend} Table 3
@@
 \hline
-\multicolumn{8}{|l|}{(\textit{P}~value significant codes is denoted: red \textless{} 0.05; *** \textless{} 0.001)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               \\
+\multicolumn{8}{|l|}{(OS: overall survival ; \textit{P}~value significant codes is denoted: red \textless{} 0.05; *** \textless{} 0.001)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               \\
 \hline
@@
 
+\clearpage
+
 %In Table \ref{tab:newTable1}, %{table:table3}, 
@@
 %Four out of ten has been validated by using GSE2837.
-In Table \ref{table:table4},
-after adjustment of confounders, prognosis is influenced by advance clinical T Status (HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] ), positive surgical margin involvement (HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003]) , and higher tobacco exposure (HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022]).
-Overexpressed \acrshort{IL19} gene could has a protective influencce on prognosis (HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001]).
+% skip IL19 paragraph
+%Overexpressed \acrshort{IL19} gene could has a protective influencce on prognosis (HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001]).
+%In Table \ref{table:table4},
+%after adjustment of confounders, prognosis is influenced by advance clinical T Status (HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] ), positive surgical margin involvement (HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003]) , and higher tobacco exposure (HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022]).
 
 In summary, those three biomarker candidates , clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
+We also found those candidates have proper effect size---the Cox's HR either $> 2.0$ or $< 0.5$.
 Thus, the prognosis model with coefficients is established from \acrshort{tcga} and GSE65858 \acrshort{hnscc} cohorts. 
@@
 %%%%%%%%%%%%% give wide full-paged tables
+% end of result
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+This ensures correct linenumbering.
+The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
+
+%This is the example 2 of equation:
+
+%\begin{equation}
+%a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
+%\end{equation}
+
+% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
+%\begin{figure}[H]	
+%\widefigure
+%\includegraphics[width=15 cm]{Definitions/logo-mdpi}
+%\caption{This is a wide figure.\label{fig2}}
+%\end{figure}  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{paracol}{2}
+\linenumbers
+\switchcolumn
+
+%%%%%%%%%%%%%%%
+\section{Discussion}
+
+%%%% LASSO regression
+\subsection{Feature Selection for Survival Modeling} % Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
+% TCGAbiolinks
+%alcohol consumption
+Besides ethnicity, age, gender, \acrshort{tnm} stage, radiation therapy, chemotherapy, and targeted therapy, the comprehensive adversely prognostic features in \acrshort{hnscc} should also include tobacco exposure, \acrshort{egfr} amplification, \acrfull{hpv} status, positive/close surgical margin ($<5 mm$), \acrfull{ene}, \acrfull{lvsi}, \acrfull{pni}, \acrfull{doi} ($>5 mm$), as well as metastatic \acrfull{lnd}\cite{Cheraghlou2018}, and \acrfull{wpoi5}, which is defined as tumor dispersion (1 mm apart between tumor satellites) or positive \acrshort{pni}/\acrshort{lvsi}\cite{Amin2017}.
+The features of \acrshort{doi}, \acrshort{lnd}, and tumor dispersion are not available on the \acrshort{tcga} dataset.
+The Brandwein-Gensler's risk model (lymphocytic host response, \acrshort{wpoi5}, and \acrshort{pni})\cite{Brandwein-Gensler2010}\cite{Sinha2018} has been suggested to be routinely performed on pathological examination.
+In previous reports of \acrshort{hnscc}, the loco-regional failure will be high when the initial frozen section has a positive/close surgical margin, and even the final margin revision revealed negative\cite{Bulbul2019b}.
+According to Table \ref{table:table2} %and Table \ref{table:table4}
+in our study, the positive surgical margin yields a hazard ratio greater than 1.6 to influence on patient's \acrshort{os}.
+It is suggested by authors \cite{Scholl1986}\cite{Sutton2003}\cite{Shaw2004}\cite{Guillemaud2010a}\cite{Patel2010}\cite{Kuriakose2017}\cite{Shapiro2017}\cite{Saidak2018}\cite{Miguelanez-Medran2019}\cite{Saidak2019} that the reason of positive/close surgical margin is possibly due to tumor aggressiveness or dispersion (WPOI-5) instead of iatrogenic reason of surgery.
+The surgical margin status has also been suggested as an independent surrogate for tumor dispersion in the \acrshort{hnscc} study.
+Thus, we selected common clinicopathological features in the current biomarker discovery, including gender, age, clinical T, clinical N, clinical M, surgical margin status, and tobacco exposure, to adjust confounders (details description at Materials and Methods section).
+
+\begin{MyColorPar}{red}
+
+%%% Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff.
+\subsection{\textit{P} value is affected by sample size and cutoff}
+Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
+The effect size is the magnitude of the difference (e.g., \acrlong{hr}) among comparing groups.
+%A \textit{P} value is a tool to help interpret findings from biomedical research.
+%In reporting and interpreting studies, both 
+%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
+While statistical significance can inform the researcher whether an effect exists, 
+the \textit{P} value will not directly tell the effect size.
+%The effect size is the main finding of a quantitative study.
+%Statistical significance depends upon both sample size and effect size. 
+The effect size is independent of the sample size\cite{Sullivan2012}.
+
+%When we increase the sample size, the standard error decrease
+%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
+In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
+However, the small effect size (non-zero) is often meaningless or substantive insignificance.
+%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
+%, that is, when the effect size is exactly zero; 
+%yet very small differences, even if significant, are often meaningless. 
+%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
+%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
+Conversely, the effect size can be large but fail to get statistical significance if the sample size is small. 
+%In this scenario, the \textit{P} value tells the effect does not exist.
+
+The following error could also impact the \textit{P} value:
+\begin{outline}
+\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.g., RNA-Seq experiments).
+The larger sample size could reduce the random error. 
+\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
+It could deleteriously impact the statistical significance.
+The larger sample size could not affect the systematic error.
+\end{outline}
+% effect size is large (whatever is true or artificial), the p value is small
+Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
+If a skewed cutoff that split, for example, 425 vs. 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
+% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
+%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
+%effect size, sample size, cutoff 影響 p value!
+
+% [preserved] ***
+%An increase in the sample size will decrease over-fitting of model[Frank Harrell].
+% https://hbiostat.org/rms/
+
+% definition of P value
+%Statistical significance is the probability that the observed difference between two groups is due to chance.
+If the P value is larger than the alpha level chosen (e.g., 0.05), any observed difference is assumed to be explained by sampling variability.
+%The most commonly used α level is 0.05, as proposed by Fischer, is the amount of type I error you are willing to accept.
+%Fisher suggested 5\% (α=0.05) level could be used for concluding that fairly strong evidence exists against H0, that is 1 out of 20 times you will be wrong and by random chance there is no difference between your groups, but the data you have suggests that there is (2).
+
+%power: Power analysis is the name given to the process for determining the sample size for a research study.
+The technical definition of power is that it is the probability of detecting a "true" effect when it exists.
+Many students think that there is a simple formula for determining sample size for every research situation.
+%As the sample size gets larger, the z value increases therefore we will more likely to reject the null hypothesis; less likely to fail to reject the null hypothesis, thus the power of the test increases.
+
+%the confidence interval of the P value (second generation P value?)
+
+%%%%
+%(ok)2-3 put in supplementary figure S1 %Rplot_pvaluePlot_NDFIP1.pdf
+%from Answer 2-3 supplementary Figure S1  %圖就好 figure Rplot_pvaluePlot_NDFIP1.pdf
+
+%2) \\
+%(ok) % pvalueTex is essential
+There is a benefit for using sliding-window cutoff method (between $30\%-70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
+We have compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
+It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR correction, it has reduced as 967 vs. 209, respectively.
+% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
+%Result by optimal cutoff: total 9416 plots,
+%6284 are raw KM P value < 0.05
+%534?? genes are FDR KM P value <0.05
+%967 genes which HR is greater than 1.5 or less than 0.5.
+%Result by median cutoff: total 20080 genes, 
+%3118 are raw KM P value < 0.05; 
+%209 genes are FDR KM P value <0.05
+The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
+That is because of the properly selected cutoff improving the statistical significance.
+Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
+
+%small effect size could be double-checked by GSE65858.
+%差別很大，張大網
+%([2021/06/27] run code: if median cut for TCGA KM Cox by *** pvalueTex code)
+%列入 workflow in materials and methods;
+
+We will explain the above mentioned by an example.
+%***NDFIP1  % 給他們一個機會
+Reviewing the special case of genes, such as NDFIP1, DKC1, PNMA5, and NPB,
+we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
+NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
+%Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
+%After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures, scientific-notation=true]{0.0001074233}.
+% the effect size
+Then it has been excluded as a candidate by small effect size (HR = 1.33 in GSE65858 cohort and HR = 1.42 in GSE2837 cohort) less than 1.8.
+%%%
+\end{MyColorPar} % red
+
+\subsection{Validation by Web-based Tools}
+% GSE2837 validated candidates: 10
+We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
+%\subsubsection*{SurvExpress} % TCGA
+% 2021/01/23 pdf x 12 from SurvExpress
+SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
+Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 6 genes:\\ % SurvExpress 有類似的結果:
+(1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
+%, STIP1 (0.001), DKC1 (0.01);\\
+%DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+(2) better prognosis: FCGBP (0.001).\\
+%ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635),
+The 6 out of 10 candidate genes are also confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
+% moved to supplementary file: Supplementary_figures.tex
+% \linksupplementary{Supplementary_figures.pdf},
+% % SurvExpress 沒有類似的結果是因為:
+%Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
+Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
+Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
+%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
+
+%\subsubsection{HPA} %still TCGA's RNA-Seq
+The Human Protein Atlas project (HPA) has proteomics analysis based on 26,941 antibodies targeting 17,165 unique proteins.
+The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA.
+Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
+All transcriptomics data has been retrieved from the TCGA, and all proteomics data has been generated in-house using the same antibodies.
+Our 5 candidates (e.g.
+CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+FCGBP is on the list of favorable prognostic genes as well.
+% DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
+% ZNF557, ZNF266, and FCGBP
+Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.\\
+org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset 
+(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
+% moved to Supplementary
+
+% Version: 3.0.2 Date: 2015/06/11 SurvNet
+%Preloaded TCGA  data is also available for analysis.
+%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
+%gene regulatory or protein interaction network
+% cited by 10 articles
+% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
+% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
+%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
+
+%%%
+\subsection{The Candidates Shown in Literature Review}
+
+%%
+%\subsection*{Review articles}
+Since the discovery of workflow, we performed the literature review by Embase/Pubmed.% to find the evidence convincing the suggested biomarkers in cancer research. 
+The 5 out of 10 candidates has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+
+%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
+
+%%%%%% bad guy
+%The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+Pang et al.\cite{Pang2018} has proved that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhances their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Increased DKK1 levels in HNSCC tissues is correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+DKK1 expression is significantly associated with smoking, alcohol abuse, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+The mRNA expression of DKK1 and DKK3 is elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
+
+%STC2:
+%The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway\cite{Ma2020}.
+
+% PGK1
+Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). 
+The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
+PGK1 is responsive in hypoxia status, since it is one of \acrshort{hif}-1 alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.
+
+%SURF4
+The patients with tumors (such as glioma, breast cancer, lymphoma, pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
+) exhibiting high Surfeit gene 4 (SURF4) expression have significantly shorter overall survival than low SURF4 expression.
+SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
+%NIH/3T3 cells (Mus musculus, mouse), 293T cell
+%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
+%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
+%web-based tools survival (not TCGA?)
+
+% USP10
+Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs), may serve as a prognostic biomarker and target for various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
+Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - reveals that USP10 is significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL-2–STAT5 signaling, transforming growth factor beta (TGFB or $TGF\beta$) signaling, and PI3K/Akt/mTOR signaling\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
+https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
+
+%FOXA2
+Prognostic signature integrated of DNA methylation, gene expression, and clinical information could provide a prognostic prediction value for HNSCC patients.
+Forkhead Box A2 (FOXA2) is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
+%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
+%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
+% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
+%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
+Further, SIS analysis was performed to further screen out a stable probe combination.
+Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
+2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
+Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
+2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
+%Association between gene expression and methylation.
+Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
+Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
+
+% STIP1; non-TCGA
+%Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}.
+The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
+%STIP1 could bind to bind Hsp70 and Hsp90.
+
+%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
+%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
+%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
+% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
+
+%%%%%% good guy
+%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
+%Oncogenic human herpesviruses (e.g., EBV and KSHV) 
+%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
+%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
+
+%ZNF266, % or ZNF16, HZF1?
+%MYO1H associated mandibular prognathism\cite{Sun2018}
+
+% FCGBP
+% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
+Fc fragment of IgG binding protein ($Fc\gamma BP$ or FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas\cite{ODonovan2002}\cite{Griffith2006}.
+%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
+%gene ID @gene@8857
+
+%\acrfull{LOC148709} has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
+In our current study, LOC148709 is also suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3} on page \pageref{table:table3}).
+
+%EVPLL in cDNA project
+
+% PNMA5
+%Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}.
+
+%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
+GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
+
+%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
+(PMID31598163)
+%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
+The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
+Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
+%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
+%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
+%\cite{Li2018b}
+%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
+%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+
+%NDFIP1:
+%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
+was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
+%MCF7 cells 
+%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
+%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
+%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
+Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
+We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
+hepatocellular carcinoma\cite{Zhang2019a}
+% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
+%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
+It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
+
+%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+%DKC1 is the tumor suppressor gene in HNSCC
+% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
+
+\subsection{Limitations of the Work}
+
+Although we combine the power of genome-wide scanning and an optimal cutoff finder for survival analysis, the study has some limitations.
+% first limitation:
+We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
+The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excites the cancer research community\cite{Li2013c}\cite{Li2017b}.
+By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray kind of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses from \acrshort{rnaseq} study.
+However, in the \acrshort{tcpa} database (v3.0\cite{Chen2019}), there are only 237 antibodies available, not covering our candidates so far. %  USP-10 in HPA
+%> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))
+%validation at protein level:
+%At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteomepathology/head+and+neck+cancer, accessed 28 September 2020).
+The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
+% > semi_join(pvalueTex_good, HPA_good, by=c("V1"="Gene"))
+%There are 628 genes that consensus of pvalue005KM (6429 genes) and HPA (bad+good in HNSCC)
+%%%%%%%%%% modified discussion
+%\begin{MyColorPar}{red}
+
+\subsubsection{Laboratory Validation}
+It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
+%下一篇文章的內容。目前在計畫中，但還沒有開始進行
+These in vitro and in vivo validation experiments will be undertaken in our laboratory.
+We plan to analyze mRNA (e.g., qRT-PCR) and protein (e.g., Western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
+%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
+The effect of overexpression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.g., proliferation, migration, and invasion) and mouse xenograft model (e.g., tumor growth).
+%這些都需要一年以上的時間
+%their rationale for looking into TMSB4X is not strongly supported by the available data.
+
+% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
+Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
+%Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
+%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
+%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
+%the rest of the analysis seems fine, but 
+%文章的初衷、跨領域：如同deep leaning Keras API，推廣給研究者一個有效的方法 
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
+% to find more useful biomarkers.
+% or even other cancer types
+% to allow successful repetition and extension of analyses based on original data
+A good research reproducibility practice is necessary to allow the reuse of code and results for new projects.
+%previously developed methodology to be effectively applied on new data, or to allow 
+%reuse of code and results for new projects. %In other words, good habits of reproducibility
+It may turn out to be a time-saver in the longer run.
+When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
+%why reproducibility?
+%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows.
+Thus, it guarantees to final users the ability to repeat any analysis independently using UNIX-like architecture.
+%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
+Once our laboratory or the community confirms those candidates as the targets, the compound screening\cite{Yang2004}\cite{Hsu2011}\cite{Pathak2021} could facilitate more individualized therapy for HNSCC patients.
+%and improve prognosis.
+% 1.
+Pathak, N.
+et al.
+Uncovering flexible active site conformations of SARS-COV-2 3Cl proteases through protease pharmacophore clusters and covid-19 drug repurposing.
+ACS Nano 15, 857–872 (2021).
+陽明交大
+
+%***
+
+\subsection{Future Direction in Translational Medicine}
+
+%\subsubsection{Tumor-agnostic Research}
+% second limitation:
+\subsubsection{Cancer Type-agnostic Study}
+Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
+% *** yes here
+In our previous work, altered glucose metabolism (e.k.a.
+the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
+% Cited In for PMID: 28061796
+Lactic acidosis induced \acrshort{glut4} overexpression was also found in lung cancer cells\cite{Prado-Garcia2020}. 
+%The overexpression of \acrshort{glut4} will lead to higher glucose uptake in proliferating cancer cells\cite{Mani2020}.
+%There is a trend toward cancer type-agnostic study. 
+Currently, Pembrolizumab and nivolumab's success has been based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
+It shows a model of tumor type-agnostic therapy\cite{Yan2018}.
+%*** PD-L1/PD-L2 is a biomarker; Keynote-012
+There are several common biomarkers of \acrfull{ici} under evaluation, including \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
+The other \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019} (ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (NCT04080804) studies.
+
+In line with tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases.
+However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
+Before the global genes scanning process, it is necessary to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
+This process should be carefully curated to confirm the data integrity within the correct definition\cite{Rendleman2019}.
+We also plan to upgrade our R script of the cutoff engine to the C++ language and source it in the Rstudio server.
+The high performance of C++ could speed up the critical steps in this workflow involving heavy computation of matrix data\cite{Woodward2020}.
+Moreover, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+
+%****************%
+\subsubsection{Holistic Cancer Care}
+
+\begin{MyColorPar}{red}
+There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
+such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
+However, the TCGA did not collect other features related to holistic care.
+% Input $X_1...X_n$ (e.g., patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure \ref{fig:figure5}).
+Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
+These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
+Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
+Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases.
+They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
+Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
+The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure \ref{fig:figure5}).
+\end{MyColorPar} % red
+
+%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
+\begin{figure}[hbt!]
+\centering
+\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
+\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
+{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment (giant \textcolor{black}{black} arrow) will trigger emotional reception.
+The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.
+The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression.
+In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy (e.g., HNSCC) with helping from known carcinogens.\\
+Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs.
+Physical care will be carried out by medication therapy or surgery.
+After establishing a therapeutic relationship (TR), the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease through their mind-brain-body axis.
+Thus, we suggest electric healthcare records (EHR) include physical, pathological, psychological data, and even more spiritual information.
+The \acrshort{tcga} should collect "holistic features" as well (\textcolor{green}{green} dashed line).}
+\label{fig:figure5}
+\end{figure}
+\clearpage
+%meridian and emotion has mutual reaction
+%meridian effect tissue and organ
+%(autonomic nerve system, myofascial network, prefrontal cortex)
+%placebo-effect influence on drug discovery
+%gene expression in deep learning
+%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
+%慈悲心 利他心
+%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
+%#正念 除了可以減壓，還可以治癒疼痛
+% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
+
+% 目的與功效  出入息 呼吸念頭 回到覺知，不再被潛意識自動導航干擾情緒
+%正念，放下二元評價 正念覺知 XAI saliency mapping and trustworthiness in deep learning
+%覺知 漸入空性 Y=wX + bias
+%解決情緒苦(七情) 四聖諦
+%慈悲心 安心（情緒穩定）
+%了卻見人苦的「慈悲心」易感者同理心 empathy
+%道歉不是一段文字，不是一個儀式（療癒冤親債主來自慈悲心）
+%冤親債主 決定不再影響環境 基因 expression，減少意外與疾病、癌症
+
+%七情: 喜、怒、思、悲、恐、驚、憂
+%depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
+% 只是陪伴
+
+%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
+%「把自己當藥方開出去」
+%Spirituality
+%慈悲心 compassion 
+%同情心 sympathy
+%同理心 empathy
+%non-verbal contact
+
+%情志養生 喜、怒、思、悲、恐 or 七情
+%喜、怒、思、悲、恐為代表，就稱為五志 Joy, anger, thought, sadness, fear
+%喜、怒、思、悲、恐、"驚憂"，稱為七氣，即七情。加之以寒熱，稱為九氣
+%人俯仰於天地之間
+%順從四季氣候變化
+%保養正氣陶冶性情
+%自我療癒身心靈疾病
+%自他不二 心存正念 向內看，解決苦之源
+%1.衷心懺悔
+%2.真心感謝
+%3.誠意祝福
+%4.永存善念 慈悲
+%5.心無恐懼: 情志養生
+%每位醫師都可以成為「創傷知情者」幫助我們身邊的病患，懂他的心靈創傷，讓他有安全感， 才有機會改變疾病的走向
+%"每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）"
+%解說：患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\begin{quote}
+%This is an example of a quote.
+%\end{quote}
+
+\section{Materials and Methods} % 4
+
+\subsection{Patient Cohort}
+
+\begin{MyColorPar}{red}
+%\subsection{A introduction of TCGA}
+%\begin{MyColorPar}{red}
+%%%%%% revision1 added [TCGA] [2021/02/02] %$X_1 ... X_n$ of independent features
+A large-scale cancer database, aggregating many independent features, is necessary to facilitate the biomarker discovery.
+The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} has been developed since 2005 and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government.
+TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
+%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
+TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen.
+Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.
+
+The NCI's Genomic Data Commons (GDC, available at https://portal.gdc.cancer.gov) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
+The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
+The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
+\acrshort{tcga}, GDC and some research communities offer several computational tools to the public for facilitating cancer research.
+%There is three categories of tools to approach the TCGA data from GDC.
+GDC Data Portal is the official web-based TCGA data analysis tools. Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and 
+Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
+One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
+Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.g., GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering).
+A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).
+%Python and UNIX bindings
+%R bindings
+Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.
+
+%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
+% RESTful API
+\end{MyColorPar}
+
+GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
+Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
+Moreover, if restricted data is requested, the user must provide a token along with the API call.
+This token can be downloaded directly from the GDC Portals.
+(paragraph is provided here courtesy of the National Cancer Institute)
+% Articles from Cureus are provided here courtesy of Cureus Inc.
+Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
+
+% clinical
+%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
+
+GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
+\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
+Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
+The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
+FirebrowseR)\cite{Deng2017}. 
+We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, \textcolor{green}{green} square) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
+
+\subsubsection{RNA Sequencing Data}
+
+The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}.
+The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
+\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
+The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
+It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
+We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].Fire.Rda".
+After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
+We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
+We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
+
+\subsubsection{Clinical Data}
+
+We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.Fire.Rda" (accessed November 2019).
+%\linebreak or \newline
+
+One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.[GeneName].\\
+Fire.Rda" tables were transposed and merged by their \_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
+The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
+The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
+% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
+We made data clean by removing duplicated rows and columns.
+
+\subsection{Cutoff Finder Core Engine}
+
+%\label{key:cutoff}
+To evaluate the effect of gene expression on the patient's survival, we introduce a sliding window cutoff selection by stratifying patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
+Our cutofFinder\_func subroutine employs the minimum \textit{P} value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
+First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
+Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} cutoff engine).
+The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier \textit{P} values for each gene.
+Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum \textit{P} value, was selected by the cutofFinder\_func subroutine.
+This iteration method could calculate all possible cutoff of each gene expression in this cohort.
+At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff at specific patient grouping  (e.g., low-expression in 262 persons vs.
+high-expression in 152 persons with gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}, please see Figure \ref{fig:figure4}).
+The cutoff would be returned to the main program to allow downstream Cox survival analysis.
+The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
+In case there was no significant \textit{P} value, a median expression of this gene was set as its cutpoint as usual.
+\begin{MyColorPar}{red}
+% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
+The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} shows which genes should be retained for subsequent univariate and multivariate analysis.
+% of Cox modeling
+It ensures the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
+Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
+\end{MyColorPar} % red
+
+\subsection{Statistical Consideration for Survival Analysis}
+
+Our workflow has loops to call function survival\_marginSFP(GeneName) with given GeneName to process the survival analysis gene by gene.
+We dichotomized the clinicopathological features, which includes gender (male/ female), age at diagnosed (below/beyond 65 year-old), clinical tumor size (T1-2/T3-4), clinical nodal status (negative/positive), clinical distant metastasis (negative/positive), TNM staging (early/late), surgical margin status (negative/positive) and tobacco exposure (low/high).
+The patients were grouped by an \acrshort{rnaseq} value of each gene, cut at low- or high-expression on an optimal \textit{P} value obtained from the cutofFinder\_func subroutine (see the section of "Cutoff Finder Core Engine").
+Pearson's chi-square test was used for these binary variables.
+Kaplan-Meier survival was analyzed using the log-rank test for two groups OS comparison.
+
+% reviewer comment; Answer 2-4 (Cox regression)
+\begin{MyColorPar}{red}
+%The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
+It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
+% Classification trees and artificial neural networks in survival analysis
+The Cox model is also accounting for confounding factors\cite{Magen2019}.
+It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.g.,, death) at time t. It can be estimated as follow:
+
+%Highlights
+% https://quicklatex.com
+\begin{flushleft}
+% equation
+%\begin{math}
+
+$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
+% natural exponential function => y=e^x
+\end{flushleft}
+where,\\
+\begin{outline} % for highlight
+\1 t represents the survival time
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g.,, clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
+\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
+\1 the term $h_0$ is called the baseline hazard.
+It corresponds to the hazard value if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
+The "t" in $h(t)$ indicates the hazard may vary over time
+\end{outline}
+
+Thus, the biomarker discovery strategy is survival modeling through a collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
+
+Univariate Cox proportional regression model, using the "coxph" function in R package "survival", has been applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival individually.
+
+% dimension reduction? feature selection for further multivariate Cox modeling =>
+%Least absolute shrinkage and selection operator (LASSO) is a biased estimation tool for data with complex collinearity.
+It can select variables and estimate parameter simultaneously and better solve the multicollinearity problem in regression analysis [19].
+Thus, we used the LASSO Cox regression analysis to decrease the number of IRGPs by R package glmnet.
+
+In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
+All covariates have been pooled in the hazard function h(t) to estimate their impact on the overall survival.
+\end{MyColorPar} % red
+%%
+
+Results were considered statistically significant when a two-sided \textit{P} $<$ 0.05, or a lower threshold if indicated.
+The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal \textit{P} value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
+%statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
+There were also multiple correlated tests of null hypotheses 
+%in the Kaplan-Meier family 
+during our global scanning of 205,00 protein-coding genes. The stringent Bonferroni correction could result in an adjusted \textit{P} value to ensure the control for type I error. 
+%There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes.
+The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
+
+The resulting data, including Kaplan-Meier curves, cumulative \textit{P} value plots, and Cox regression tables, were exported to ".xlsx" and ".Rda" files (by R package "r2excel") for subsequent biomarker selection.
+
+\subsection{Biomarker Selection and Validation}
+% Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction 才對
+Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
+Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, candidate selection).
+
+\begin{MyColorPar}{red}
+GSE65858 is a dataset for candidate selection in our workflow.
+The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
+R package of GEOquery\cite{Sean2007} was used to
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
+GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
+There are 270 HNSCC participants involved in this cohort.
+%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
+%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
+The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009).
+% (RefSeq)
+GSE65858 is a dataset for candidate selection in our workflow.
+We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
+\end{MyColorPar} % red
+
+Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
+GSE2837 HNSCC dataset (microarray gene expression by Affymetrix X3P chips U133\_X3P) has 28 participants and RFS information. 
+Using PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a} for the validation of candidates.
+%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
+%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
+%The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005).
+%and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions} % 5
+% Conclusions: This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+%The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
+Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
+Our findings suggested 10 candidate biomarkers,CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2, as well as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni \textit{P} values and proper confounders control.
+They also might be potential common biomarkers for subsequent study.
+% welcome for study
+%tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases
+We wish this workflow will be available for the reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} and tumor-agnostic research\cite{Looney2020} to crossing several \acrshort{tcga} diseases to make translational impacts.
+%Tex: PvalueTex
+% the broad usage
+%We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
+%TCGA has not collected holistic features so far.
+
+The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using holistic multi-parametric approaches.
+% cancer cure (care) 的證明
+%# 懺悔
+Since mindfulness meditation will be helpful in cancer healthcare, we continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for their physical body's hard working.
+
+%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
+%七情: 喜、怒、思、悲、恐、驚、憂
+%with more TCGA features (holistic)
+%Dali Lama: Wish and bless the whole world %慈悲心 利他心
+% 多了解身心靈的關係，減少癌症對健康的損害
+
+%the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Patents}
+
+%This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+%% optional: The data presented in this study are available in supplementary material.
+\supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, 
+	Figure S1: \textit{P} value plot of the gene NDFIP1,
+	Figure S2: GSE2837 analysis by PrognoScan,  
+	Table S1: The GSE2837 query results from PrognoScan,
+	Table S2: 10 good guys, % ? don't keep it
+	Video S1: title. A supporting video article is available at doi: link}
+
+% Only for the journal Methods and Protocols:
+% If you wish to submit a video article, please do so with any other supplementary material.
+% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{Conceptualization, Yu-Chuan (Jack) Li; Data curation, Alexander TH Wu; Formal analysis, Li-Hsing Chi; Investigation, Michael Hsiao; Methodology, Michael Hsiao; Resources, Alexander TH Wu; Software, Li-Hsing Chi and Yu-Chuan (Jack) Li; Supervision, Michael Hsiao and Yu-Chuan (Jack) Li; Writing – original draft, Li-Hsing Chi; Writing – review and editing, Alexander TH Wu.
+All authors have read and agreed to the published version of the manuscript.}
+
+%\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
+Please note that the Editorial Office might ask you for further information.
+Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals.
+You might also choose to exclude this statement if the study did not involve humans or animals.}
+
+%\informedconsent{Any research article describing a study involving humans should contain this statement.
+Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
+You might also choose to exclude this statement if the study did not involve humans.
+
+%Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
+Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
+
+\funding{The APC was funded by Taipei Medical University}
+
+\institutionalreview{Not applicable}
+
+\informedconsent{Not applicable}
+
+\dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
+%The supplementary figures are available online.%, tables, and R script codes 
+The R script codes and datasets generated during the current study are available at the GitHub repository, https://github.com/texchi2/pvalueTex.}
+
+\acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
+The tables were generated by latex code with the help from https://www.tablesgenerator.com and
+https://github.com/JDMCreator\\/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
+We like to thank Dr. Wen-Chang Wang, %https://orcid.org/0000-0003-3124-2136
+College of Medical Science and Technology, Taipei Medical University, for bioinformatics consultation and helps. 
+We like to thank Sylvain Hall\'e, Department of Computer Science and Mathematics, Univerit\'e du Qu\'ebec \`a Chicoutimi, Canada, for latex technique help with his TeXtidote.
+%We also thank the statistical consultation and helps by Dr. Hsin-Chou Yang of the Institute of Statistical Science, Academia Sinica, Taipei, Taiwan.
+We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
+% *** URL Accessed 20 May 2013.
+The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/mtbwi/index.do.  Accessed 20 May 2020.}
+
+%\subsection*{Authors' information} % Author details (automatic placed here)
+
+\conflictsofinterest{The authors declare no conflict of interest.}
+
+%% Optional
+%\sampleavailability{Samples of the compounds ... are available from the authors.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Only for journal Encyclopedia
+%\entrylink{The Link to this entry published on the encyclopedia platform.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional
+\abbreviations{The following abbreviations are used in this manuscript:
+\noindent 
+\renewcommand*{\glsinlinenameformat}[2]{\glstarget{#1} {\textsc{#2}},}
+\printglossary[type=\acronymtype, title= , nonumberlist, style=inline]}
+% Abbreviations
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{paracol} % {2} column
+\reftitle{References}
+
+% Please provide either the correct journal abbreviation (e.g.
+according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
+% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
+
+%=====================================
+% References, variant A: external bibliography
+%=====================================
+%\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
+
+\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
+%\bibliographystyle{chicago2} %model1-num-names
+\bibliography{TCGA_margin_cutoff.bib, Holistic.bib, Deep_Learning.bib}
+
+% If authors have biography, please use the format below
+%\section*{Short Biography of Authors}
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
+%{\textbf{Firstname Lastname} Biography of first author}
+%
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
+%{\textbf{Firstname Lastname} Biography of second author}
+
+% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
+For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
+% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
+% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
+328; \citeyear{ref-journal-3b}, p.475).
+This produces: Wong (1999, p.
+328; 2000, p.
+475)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% for journal Sci
+%\reviewreports{\\
+%Reviewer 1 comments and authors’ response\\
+%Reviewer 2 comments and authors’ response\\
+%Reviewer 3 comments and authors’ response
+%}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% figure for IL19 Cox's table
 
@@
 \end{table}
-
-% end of result
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-%This is the example 2 of equation:
-
-%\begin{equation}
-%a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-%\end{equation}
-
-% Example of a figure that spans the whole page width (the commands \widefigure and \begin{paracol}{2}, \linenumbers, and\switchcolumn need to be present). The same concept works for tables, too.
-%\begin{figure}[H]	
-%\widefigure
-%\includegraphics[width=15 cm]{Definitions/logo-mdpi}
-%\caption{This is a wide figure.\label{fig2}}
-%\end{figure}
-
-\begin{paracol}{2}
-\linenumbers
-\switchcolumn
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%
-\section{Discussion}
-
-%%%% LASSO regression
-\subsection{Feature Selection for Survival Modeling} % Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
-% TCGAbiolinks
-%alcohol consumption
-Besides ethnicity, age, gender, \acrshort{tnm} stage, radiation therapy, chemotherapy, and targeted therapy, the comprehensive adversely prognostic features in \acrshort{hnscc} should also include tobacco exposure, \acrshort{egfr} amplification, \acrfull{hpv} status, positive/close surgical margin ($<5 mm$), \acrfull{ene}, \acrfull{lvsi}, \acrfull{pni}, \acrfull{doi} ($>5 mm$), as well as metastatic \acrfull{lnd}\cite{Cheraghlou2018}, and \acrfull{wpoi5}, which is defined as tumor dispersion (1 mm apart between tumor satellites) or positive \acrshort{pni}/\acrshort{lvsi}\cite{Amin2017}.
-The features of \acrshort{doi}, \acrshort{lnd}, and tumor dispersion are not available on the \acrshort{tcga} dataset.
-The Brandwein-Gensler's risk model (lymphocytic host response, \acrshort{wpoi5}, and \acrshort{pni})\cite{Brandwein-Gensler2010}\cite{Sinha2018} has been suggested to be routinely performed on pathological examination.
-In previous reports of \acrshort{hnscc}, the loco-regional failure will be high when the initial frozen section has a positive/close surgical margin, and even the final margin revision revealed negative\cite{Bulbul2019b}.
-According to Table \ref{table:table2} and Table \ref{table:table4} in our study, the positive surgical margin yields a hazard ratio greater than 1.6 to influence on patient's \acrshort{os}.
-It is suggested by authors \cite{Scholl1986}\cite{Sutton2003}\cite{Shaw2004}\cite{Guillemaud2010a}\cite{Patel2010}\cite{Kuriakose2017}\cite{Shapiro2017}\cite{Saidak2018}\cite{Miguelanez-Medran2019}\cite{Saidak2019} that the reason of positive/close surgical margin is possibly due to tumor aggressiveness or dispersion (WPOI-5) instead of iatrogenic reason of surgery.
-The surgical margin status has also been suggested as an independent surrogate for tumor dispersion in the \acrshort{hnscc} study.
-Thus, we selected common clinicopathological features in the current biomarker discovery, including gender, age, clinical T, clinical N, clinical M, surgical margin status, and tobacco exposure, to adjust confounders (details description at Materials and Methods section).
-
-%%% Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff.
-\subsection{\textit{P} value is affected by sample size and cutoff}
-Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
-The effect size is the magnitude of the difference (or relationship) among comparing groups.
-%A \textit{P} value is a tool to help interpret findings from biomedical research.
-%In reporting and interpreting studies, both 
-%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
-While statistical significance can inform the researcher whether an effect exists, 
-the \textit{P} value will not directly tell the effect size.
-%The effect size is the main finding of a quantitative study.
-%Statistical significance depends upon both sample size and effect size. 
-The effect size is independent of the sample size\cite{Sullivan2012}.
-
-%When we increase the sample size, the standard error decrease
-%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
-In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
-However, the small effect size (non-zero) is often meaningless or substantive insignificance.
-%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
-%, that is, when the effect size is exactly zero; 
-%yet very small differences, even if significant, are often meaningless. 
-%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
-%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
-Conversely, the effect size can be significant but fail to get statistical significance if the sample size is small. 
-%In this scenario, the \textit{P} value tells the effect does not exist.
-
-The following error could also impact the \textit{P} value:
-\begin{outline}
-\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.x.
-RNA-Seq experiments).
-The larger sample size could reduce the random error. 
-\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
-It could deleteriously impact the statistical significance.
-The larger sample size could not affect the systematic error.
-\end{outline}
-% effect size is large (whatever is true or artificial), the p value is small
-Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
-If a skewed cutoff that split, for example, 425 vs. 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
-% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
-%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
-%effect size, sample size, cutoff 影響 p value!
-
-% [preserved] ***
-%An increase in the sample size will decrease over-fitting of model[Frank Harrell].
-% https://hbiostat.org/rms/
-
-% definition of P value
-%Statistical significance is the probability that the observed difference between two groups is due to chance.
-If the P value is larger than the alpha level chosen (e.x.
-0.05), any observed difference is assumed to be explained by sampling variability.
-%The most commonly used α level is 0.05, as proposed by Fischer, is the amount of type I error you are willing to accept.
-%Fisher suggested 5\% (α=0.05) level could be used for concluding that fairly strong evidence exists against H0, that is 1 out of 20 times you will be wrong and by random chance there is no difference between your groups, but the data you have suggests that there is (2).
-
-%power: Power analysis is the name given to the process for determining the sample size for a research study.
-The technical definition of power is that it is the probability of detecting a "true" effect when it exists.
-Many students think that there is a simple formula for determining sample size for every research situation.
-%As the sample size gets larger, the z value increases therefore we will more likely to reject the null hypothesis; less likely to fail to reject the null hypothesis, thus the power of the test increases.
-
-%the confidence interval of the P value (second generation P value?)
-
-%%%%
-%(ok)2-3 put in supplementary figure S1 %Rplot_pvaluePlot_NDFIP1.pdf
-%from Answer 2-3 supplementary Figure S1  %圖就好 figure Rplot_pvaluePlot_NDFIP1.pdf
-
-%2) \\
-%(ok) % pvalueTex is essential
-There is a benefit for using sliding-window cutoff method (between $30\%-70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
-We have compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
-It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR correction, it has reduced as 967 vs. 209, respectively.
-% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
-%Result by optimal cutoff: total 9416 plots,
-%6284 are raw KM P value < 0.05
-%534?? genes are FDR KM P value <0.05
-%967 genes which HR is greater than 1.5 or less than 0.5.
-%Result by median cutoff: total 20080 genes, 
-%3118 are raw KM P value < 0.05; 
-%209 genes are FDR KM P value <0.05
-The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
-That is because of the properly selected cutoff improving the statistical significance.
-Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
-
-%small effect size could be double-checked by GSE65858.
-%差別很大，張大網
-%([2021/06/27] run code: if median cut for TCGA KM Cox by *** pvalueTex code)
-%列入 workflow in materials and methods;
-
-We will explain the above mentioned by an example.
-%***NDFIP1  % 給他們一個機會
-Reviewing the special case of genes, such as NDFIP1, DKC1, PNMA5, and NPB,
-we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
-NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
-%Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
-%After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures, scientific-notation=true]{0.0001074233}.
-% the effect size
-Then it has been excluded as a candidate by small effect size (HR = 1.33 in GSE65858 cohort and HR = 1.42 in GSE2837 cohort) less than 1.8.
-%%%
-
-\subsection{Validation by Web-based Tools}
-% GSE2837 validated candidates: 10
-We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
-%\subsubsection*{SurvExpress} % TCGA
-% 2021/01/23 pdf x 12 from SurvExpress
-SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
-Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 6 genes:\\ % SurvExpress 有類似的結果:
-(1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
-%, STIP1 (0.001), DKC1 (0.01);\\
-%DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-(2) better prognosis: FCGBP (0.001).\\
-%ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
-%17 out of 20 candidates
-%?DKK1 (0.253635),
-The 6 out of 10 candidate genes are also confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
-% moved to supplementary file: Supplementary_figures.tex
-% \linksupplementary{Supplementary_figures.pdf},
-% % SurvExpress 沒有類似的結果是因為:
-%Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
-Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
-Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
-%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
-
-%\subsubsection{HPA} %still TCGA's RNA-Seq
-The Human Protein Atlas project (HPA) has proteomics analysis based on 26,941 antibodies targeting 17,165 unique proteins.
-The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA.
-Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
-All transcriptomics data has been retrieved from the TCGA, and all proteomics data has been generated in-house using the same antibodies.
-Our 5 candidates (e.g.
-CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
-FCGBP is on the list of favorable prognostic genes as well.
-% DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
-% ZNF557, ZNF266, and FCGBP
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.\\
-org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset 
-(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
-% moved to Supplementary
-
-% Version: 3.0.2 Date: 2015/06/11 SurvNet
-%Preloaded TCGA  data is also available for analysis.
-%DKK1 has the P-value 1.99328e-07 of multivariable Cox proportional hazards regression model, which was reported by network-based biomarkers research tools (SurvNet, accessed at http://bioinformatics.mdanderson.org/main/SurvNet; saved as supplementary file SurvNet\_HNSCC\_result.tsv)\cite{Li2012a}.
-%gene regulatory or protein interaction network
-% cited by 10 articles
-% he P-values pi from a univariable Cox proportional hazards regression model, which quantifies how significantly the molecular profiling data of the gene correlate with the patient survival data. 
-% SurvNet also calculates the mutivariable Cox P-values for each subnetwork (a group of genes) to validate their clinical utility.
-%The network files are in a '.dot' format that can be visualized by GraphViz (http://www.graphviz.org)
-
-%%%
-\subsection{The Candidates Shown in Literature Review}
-
-%%
-%\subsection*{Review articles}
-Since the discovery of workflow, we performed the literature review by Embase/Pubmed.% to find the evidence convincing the suggested biomarkers in cancer research. 
-The 5 out of 10 candidates has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
-
-%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
-%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
-%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
-
-%%%%%% bad guy
-%The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
-Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
-Pang et al.\cite{Pang2018} has proved that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhances their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
-Increased DKK1 levels in HNSCC tissues is correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
-DKK1 expression is significantly associated with smoking, alcohol abuse, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
-The mRNA expression of DKK1 and DKK3 is elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
-%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
-
-%STC2:
-%The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway\cite{Ma2020}.
-
-% PGK1
-Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). 
-The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
-PGK1 is responsive in hypoxia status, since it is one of \acrshort{hif}-1 alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.
-
-%SURF4
-The patients with tumors (such as glioma, breast cancer, lymphoma, pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
-) exhibiting high Surfeit gene 4 (SURF4) expression have significantly shorter overall survival than low SURF4 expression.
-SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
-%NIH/3T3 cells (Mus musculus, mouse), 293T cell
-%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
-%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
-%web-based tools survival (not TCGA?)
-
-% USP10
-Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs), may serve as a prognostic biomarker and target for various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
-Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - reveals that USP10 is significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL-2–STAT5 signaling, transforming growth factor beta (TGFB or $TGF\beta$) signaling, and PI3K/Akt/mTOR signaling\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
-https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
-
-%FOXA2
-Prognostic signature integrated of DNA methylation, gene expression, and clinical information could provide a prognostic prediction value for HNSCC patients.
-Forkhead Box A2 (FOXA2) is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
-%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
-%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
-% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
-%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
-Further, SIS analysis was performed to further screen out a stable probe combination.
-Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
-2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
-Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
-2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
-%Association between gene expression and methylation.
-Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
-Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
-
-% STIP1; non-TCGA
-%Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}.
-The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
-%STIP1 could bind to bind Hsp70 and Hsp90.
-
-%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
-%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
-%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
-% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
-
-%%%%%% good guy
-%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
-%Oncogenic human herpesviruses (e.x. EBV and KSHV) 
-%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
-%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
-
-%ZNF266, % or ZNF16, HZF1?
-%MYO1H associated mandibular prognathism\cite{Sun2018}
-
-% FCGBP
-% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
-Fc fragment of IgG binding protein ($Fc\gamma BP$ or FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas\cite{ODonovan2002}\cite{Griffith2006}.
-%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
-%gene ID @gene@8857
-
-%\acrfull{LOC148709} has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
-In our current study, LOC148709 is also suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3} on page \pageref{table:table3}).
-
-%EVPLL in cDNA project
-
-% PNMA5
-%Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}.
-
-%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
-GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
-
-%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
-(PMID31598163)
-%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
-The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
-Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
-%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
-%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
-%\cite{Li2018b}
-%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
-%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
-
-%NDFIP1:
-%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
-was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
-%MCF7 cells 
-%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
-%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
-%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
-Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
-We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
-hepatocellular carcinoma\cite{Zhang2019a}
-% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
-%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
-It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
-
-%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
-%DKC1 is the tumor suppressor gene in HNSCC
-% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
-
-\subsection{Limitations of the Work}
-
-Although we combine the power of genome-wide scanning and an optimal cutoff finder for survival analysis, the study has some limitations.
-% first limitation:
-We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
-The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excites the cancer research community\cite{Li2013c}\cite{Li2017b}.
-By the utility of the \acrfull{rppa} or \acrfull{rpma}, a microarray kind of "Western blots" in the \acrshort{tcpa} could help to test our hypotheses from \acrshort{rnaseq} study.
-However, in the \acrshort{tcpa} database (v3.0\cite{Chen2019}), there are only 237 antibodies available, not covering our candidates so far. %  USP-10 in HPA
-%> semi_join(pvalueTex_bad, HPA_bad, by=c("V1"="Gene"))
-%validation at protein level:
-%At the same time, we found our candidates (DKK1, CAMK2N1, STC2, PGK1, SURF4, NDFIP1, STIP1, DKC1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteomepathology/head+and+neck+cancer, accessed 28 September 2020).
-The ZNF557, ZNF266, and FCGBP are on the list of favorable prognostic genes as well.
-% > semi_join(pvalueTex_good, HPA_good, by=c("V1"="Gene"))
-%There are 628 genes that consensus of pvalue005KM (6429 genes) and HPA (bad+good in HNSCC)
-%%%%%%%%%% modified discussion
-%\begin{MyColorPar}{red}
-
-\subsubsection{Laboratory Validation}
-It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
-%下一篇文章的內容。目前在計畫中，但還沒有開始進行
-These in vitro and in vivo validation experiments will be undertaken in our laboratory.
-We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. Western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
-%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
-The effect of overexpression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x.
-proliferation, migration, and invasion) and mouse xenograft model (e.x.
-tumor growth).
-%這些都需要一年以上的時間
-%their rationale for looking into TMSB4X is not strongly supported by the available data.
-
-% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
-Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation.
-%Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
-%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
-%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
-%the rest of the analysis seems fine, but 
-%文章的初衷、跨領域：如同deep leaning Keras API，推廣給研究者一個有效的方法 
-We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
-% to find more useful biomarkers.
-% or even other cancer types
-% to allow successful repetition and extension of analyses based on original data
-A good research reproducibility practice is necessary to allow the reuse of code and results for new projects.
-%previously developed methodology to be effectively applied on new data, or to allow 
-%reuse of code and results for new projects. %In other words, good habits of reproducibility
-It may turn out to be a time-saver in the longer run.
-When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
-%why reproducibility?
-%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows.
-Thus, it guarantees to final users the ability to repeat any analysis independently using UNIX-like architecture.
-%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
-Once our laboratory or the community confirms those candidates as the targets, the compound screening\cite{Yang2004}\cite{Hsu2011}\cite{Pathak2021} could facilitate more individualized therapy for HNSCC patients.
-%and improve prognosis.
-% 1.
-Pathak, N.
-et al.
-Uncovering flexible active site conformations of SARS-COV-2 3Cl proteases through protease pharmacophore clusters and covid-19 drug repurposing.
-ACS Nano 15, 857–872 (2021).
-陽明交大
-
-%***
-
-\subsection{Future Direction in Translational Medicine}
-
-%\subsubsection{Tumor-agnostic Research}
-% second limitation:
-\subsubsection{Cancer Type-agnostic Study}
-Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
-% *** yes here
-In our previous work, altered glucose metabolism (e.k.a.
-the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
-% Cited In for PMID: 28061796
-Lactic acidosis induced \acrshort{glut4} overexpression was also found in lung cancer cells\cite{Prado-Garcia2020}. 
-%The overexpression of \acrshort{glut4} will lead to higher glucose uptake in proliferating cancer cells\cite{Mani2020}.
-%There is a trend toward cancer type-agnostic study. 
-Currently, Pembrolizumab and nivolumab's success has been based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
-It shows a model of tumor type-agnostic therapy\cite{Yan2018}.
-%*** PD-L1/PD-L2 is a biomarker; Keynote-012
-There are several common biomarkers of \acrfull{ici} under evaluation, including \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
-The other \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019} (ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (NCT04080804) studies.
-
-In line with tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases.
-However, the \acrshort{gdc} provided standardized data frames that could not directly fit our workflow's scope.
-Before the global genes scanning process, it is necessary to re-format, transpose and, merge the 528 patients' clinical datasets and correlated 20,500 expressions of bio-specimen.
-This process should be carefully curated to confirm the data integrity within the correct definition\cite{Rendleman2019}.
-We also plan to upgrade our R script of the cutoff engine to the C++ language and source it in the Rstudio server.
-The high performance of C++ could speed up the critical steps in this workflow involving heavy computation of matrix data\cite{Woodward2020}.
-Moreover, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
-
-%****************%
-\subsubsection{Holistic Cancer Care}
-
-\begin{MyColorPar}{red}
-There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
-such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
-However, the TCGA did not collect other features related to holistic care.
-% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
-Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure \ref{fig:figure5}).
-Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
-These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
-Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection.
-Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases.
-They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
-Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
-The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure \ref{fig:figure5}).
-\end{MyColorPar} % red
-
-%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
-\begin{figure}[hbt!]
-\centering
-\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
-\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
-{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment (giant \textcolor{black}{black} arrow) will trigger emotional reception.
-The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion.
-The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression.
-In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy (e.x.
-HNSCC) with helping from known carcinogens.\\
-Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs.
-Physical care will be carried out by medication therapy or surgery.
-After establishing a therapeutic relationship (TR), the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease through their mind-brain-body axis.
-Thus, we suggest electric healthcare records (EHR) include physical, pathological, psychological data, and even more spiritual information.
-The \acrshort{tcga} should collect "holistic features" as well (\textcolor{green}{green} dashed line).}
-\label{fig:figure5}
-\end{figure}
-\clearpage
-%meridian and emotion has mutual reaction
-%meridian effect tissue and organ
-%(autonomic nerve system, myofascial network, prefrontal cortex)
-%placebo-effect influence on drug discovery
-%gene expression in deep learning
-%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
-%慈悲心 利他心
-%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
-%#正念 除了可以減壓，還可以治癒疼痛
-% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
-
-% 目的與功效  出入息 呼吸念頭 回到覺知，不再被潛意識自動導航干擾情緒
-%正念，放下二元評價 正念覺知 XAI saliency mapping and trustworthiness in deep learning
-%覺知 漸入空性 Y=wX + bias
-%解決情緒苦(七情) 四聖諦
-%慈悲心 安心（情緒穩定）
-%了卻見人苦的「慈悲心」易感者同理心 empathy
-%道歉不是一段文字，不是一個儀式（療癒冤親債主來自慈悲心）
-%冤親債主 決定不再影響環境 基因 expression，減少意外與疾病、癌症
-
-%七情: 喜、怒、思、悲、恐、驚、憂
-%depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
-% 只是陪伴
-
-%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
-%「把自己當藥方開出去」
-%Spirituality
-%慈悲心 compassion 
-%同情心 sympathy
-%同理心 empathy
-%non-verbal contact
-
-%情志養生 喜、怒、思、悲、恐 or 七情
-%喜、怒、思、悲、恐為代表，就稱為五志 Joy, anger, thought, sadness, fear
-%喜、怒、思、悲、恐、"驚憂"，稱為七氣，即七情。加之以寒熱，稱為九氣
-%人俯仰於天地之間
-%順從四季氣候變化
-%保養正氣陶冶性情
-%自我療癒身心靈疾病
-%自他不二 心存正念 向內看，解決苦之源
-%1.衷心懺悔
-%2.真心感謝
-%3.誠意祝福
-%4.永存善念 慈悲
-%5.心無恐懼: 情志養生
-%每位醫師都可以成為「創傷知情者」幫助我們身邊的病患，懂他的心靈創傷，讓他有安全感， 才有機會改變疾病的走向
-%"每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）"
-%解說：患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{quote}
-%This is an example of a quote.
-%\end{quote}
-
-\section{Materials and Methods} % 4
-
-\subsection{Patient Cohort}
-
-\begin{MyColorPar}{red}
-%\subsection{A introduction of TCGA}
-%\begin{MyColorPar}{red}
-%%%%%% revision1 added [TCGA] [2021/02/02] %$X_1 ... X_n$ of independent features
-A large-scale cancer database, aggregating many independent features, is necessary to facilitate the biomarker discovery.
-The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} has been developed since 2005 and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government.
-TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
-%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
-TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen.
-Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.
-
-The NCI's Genomic Data Commons (GDC, available at https://portal.gdc.cancer.gov) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs.
-The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}.
-The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
-%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
-\acrshort{tcga}, GDC and some research communities offer several computational tools to the public for facilitating cancer research.
-%There is three categories of tools to approach the TCGA data from GDC.
-GDC Data Portal is the official web-based TCGA data analysis tools. Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and 
-Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
-One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses.
-Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x.
-GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering).
-A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).
-%Python and UNIX bindings
-%R bindings
-Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.
-
-%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
-% RESTful API
-\end{MyColorPar}
-
-GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
-Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
-Moreover, if restricted data is requested, the user must provide a token along with the API call.
-This token can be downloaded directly from the GDC Portals.
-(paragraph is provided here courtesy of the National Cancer Institute)
-% Articles from Cureus are provided here courtesy of Cureus Inc.
-Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
-
-% clinical
-%We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patient.
-
-GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
-\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
-Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
-The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
-FirebrowseR)\cite{Deng2017}. 
-We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, \textcolor{green}{green} square) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
-
-\subsubsection{RNA Sequencing Data}
-
-The number of protein-coding genes was suggested as 20,500\cite{Clamp2007}.
-The \acrshort{gdc} Data Portal provided \acrshort{tcga} data has been harmonized and re-aligned \acrlong{rnaseq} data against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
-\acrshort{rnaseq} expression level read counts produced by Illumina HiSeq have been normalized using the \acrfull{fpkm} method, as described in reference\cite{FPKM2017}.
-The \acrshort{rnaseq} preprocessor of Broad \acrshort{gdac} picked the \acrfull{rsem} value from Illumina HiSeq/GA2 messenger \acrshort{rnaseq} level\_3 (v2) dataset of \acrshort{nci} \acrshort{gdc}.
-It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.
-We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].Fire.Rda".
-After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
-We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
-We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
-
-\subsubsection{Clinical Data}
-
-We utilized FirebrowseR's function call, Samples.Clinical(cohort = "HNSC", format="csv"), to get all 81 clinical features (including pathological data, defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}) of all 528 \acrshort{hnscc} patients, which saved as one data frame file: "HNSCC.clinical.Fire.Rda" (accessed November 2019).
-%\linebreak or \newline
-
-One "HNSCC.clinical.Fire.Rda" tables and 20,500 "HNSCC.mRNA.Exp.[GeneName].\\
-Fire.Rda" tables were transposed and merged by their \_participant\_barcode (unique patient \acrlong{id}, \acrshort{id}) to yield a data frame with 528 rows (participants) against 20,581 columns (81 clinical features as well as 20,500 protein-coding \acrshort{rnaseq} of cancer specimen).
-The clinicopathological features selected for our workflow included gender, age, clinical tumor size, clinical cervical lymph node metastases, clinical distant metastasis assessment, pathological surgical margin, and tobacco exposure with their corresponding survival data.
-The tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M) were classified according to \acrfull{ajcc}\cite{Amin2017} along with \acrfull{uicc}\cite{Brierley2016} \acrshort{tnm} system for clinical staging of \acrshort{hnscc}.
-% In the Eighth Edition, the AJCC has expanded the use of non-anatomic prognostic factors and biomarkers in assigning prognostic stage groups.
-We made data clean by removing duplicated rows and columns.
-
-\subsection{Cutoff Finder Core Engine}
-
-%\label{key:cutoff}
-To evaluate the effect of gene expression on the patient's survival, we introduce a sliding window cutoff selection by stratifying patients with Kaplan-Meier survival analysis according to each gene's low/high expression.
-Our cutofFinder\_func subroutine employs the minimum \textit{P} value approach to recognizing cutoff points in continuous gene expression measurement for patients sub-population.
-First, patients were ordered by \acrshort{rnaseq} value (RSEM) of a given gene.
-Next, patients were stratified at a serial cut (counted by person ranked in 30\% to 70\% percentile of the cohort; please see Figure \ref{fig:figure1} cutoff engine).
-The survival risk differences of the two groups were estimated by log-rank test to yield around 165 Kaplan-Meier \textit{P} values for each gene.
-Then, the optimal cutoff of \acrshort{rnaseq}, giving the minimum \textit{P} value, was selected by the cutofFinder\_func subroutine.
-This iteration method could calculate all possible cutoff of each gene expression in this cohort.
-At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff at specific patient grouping  (e.x.
-low-expression in 262 persons vs.
-high-expression in 152 persons with gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}, please see Figure \ref{fig:figure4}).
-The cutoff would be returned to the main program to allow downstream Cox survival analysis.
-The percentile range we applied as 30\% to 70\% was used to avoid a small grouping effect\cite{Miller1982}\cite{Mizuno2009a}.
-In case there was no significant \textit{P} value, a median expression of this gene was set as its cutpoint as usual.
-\begin{MyColorPar}{red}
-% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
-The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} shows which genes should be retained for subsequent univariate and multivariate analysis.
-% of Cox modeling
-It ensures the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
-Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
-\end{MyColorPar} % red
-
-\subsection{Statistical Consideration for Survival Analysis}
-
-Our workflow has loops to call function survival\_marginSFP(GeneName) with given GeneName to process the survival analysis gene by gene.
-We dichotomized the clinicopathological features, which includes gender (male/ female), age at diagnosed (below/beyond 65 year-old), clinical tumor size (T1-2/T3-4), clinical nodal status (negative/positive), clinical distant metastasis (negative/positive), TNM staging (early/late), surgical margin status (negative/positive) and tobacco exposure (low/high).
-The patients were grouped by an \acrshort{rnaseq} value of each gene, cut at low- or high-expression on an optimal \textit{P} value obtained from the cutofFinder\_func subroutine (see the section of "Cutoff Finder Core Engine").
-Pearson's chi-square test was used for these binary variables.
-Kaplan-Meier survival was analyzed using the log-rank test for two groups OS comparison.
-
-% reviewer comment; Answer 2-4 (Cox regression)
-\begin{MyColorPar}{red}
-%The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
-It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
-% Classification trees and artificial neural networks in survival analysis
-The Cox model is also accounting for confounding factors\cite{Magen2019}.
-It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x., death) at time t. It can be estimated as follow:
-
-%Highlights
-% https://quicklatex.com
-\begin{flushleft}
-% equation
-%\begin{math}
-
-$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
-% natural exponential function => y=e^x
-\end{flushleft}
-where,\\
-\begin{outline} % for highlight
-\1 t represents the survival time
-\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.x., clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
-\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
-\1 the term $h_0$ is called the baseline hazard.
-It corresponds to the hazard value if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
-The "t" in $h(t)$ indicates the hazard may vary over time
-\end{outline}
-
-Thus, the biomarker discovery strategy is survival modeling through a collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
-
-Univariate Cox proportional regression model, using the "coxph" function in R package "survival", has been applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features and gene expression to the overall survival individually.
-
-% dimension reduction? feature selection for further multivariate Cox modeling =>
-%Least absolute shrinkage and selection operator (LASSO) is a biased estimation tool for data with complex collinearity.
-It can select variables and estimate parameter simultaneously and better solve the multicollinearity problem in regression analysis [19].
-Thus, we used the LASSO Cox regression analysis to decrease the number of IRGPs by R package glmnet.
-
-In a multivariate test, those covariates used include the clinicopathological features (gender, age at diagnosed separated by 65 year-old, clinical tumor size [T1-2/T3-4], clinical nodal status [N0/N+], clinical distant metastasis [M0/M1], TNM staging [stage 1-2/stage 3-4], surgical margin status [negative/positive] and tobacco exposure [low/high]), and gene expression level [low/high] defined by the cutoff.
-All covariates have been pooled in the hazard function h(t) to estimate their impact on the overall survival.
-\end{MyColorPar} % red
-%%
-
-Results were considered statistically significant when a two-sided \textit{P} $<$ 0.05, or a lower threshold if indicated.
-The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal \textit{P} value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
-%statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
-There were also multiple correlated tests of null hypotheses 
-%in the Kaplan-Meier family 
-during our global scanning of 205,00 protein-coding genes. The stringent Bonferroni correction could result in an adjusted \textit{P} value to ensure the control for type I error. 
-%There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes.
-The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.
-
-The resulting data, including Kaplan-Meier curves, cumulative \textit{P} value plots, and Cox regression tables, were exported to ".xlsx" and ".Rda" files (by R package "r2excel") for subsequent biomarker selection.
-
-\subsection{Biomarker Selection and Validation}
-% Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction 才對
-Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
-Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, candidate selection).
-
-\begin{MyColorPar}{red}
-GSE65858 is a dataset for candidate selection in our workflow.
-The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
-R package of GEOquery\cite{Sean2007} was used to
-download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
-GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
-There are 270 HNSCC participants involved in this cohort.
-%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
-%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
-The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009).
-% (RefSeq)
-GSE65858 is a dataset for candidate selection in our workflow.
-We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
-\end{MyColorPar} % red
-
-Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
-GSE2837 HNSCC dataset (microarray gene expression by Affymetrix X3P chips U133\_X3P) has 28 participants and RFS information. 
-Using PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a} for the validation of candidates.
-%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
-%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
-%The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005).
-%and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions} % 5
-% Conclusions: This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-%The result showed six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are significantly associated with a poor prognosis of overall survival.
-Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
-Our findings suggested 10 candidate biomarkers,CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2, as well as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni \textit{P} values and proper confounders control.
-They also might be potential common biomarkers for subsequent study.
-% welcome for study
-%tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases
-We wish this workflow will be available for the reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} and tumor-agnostic research\cite{Looney2020} to crossing several \acrshort{tcga} diseases to make translational impacts.
-%Tex: PvalueTex
-% the broad usage
-%We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
-%TCGA has not collected holistic features so far.
-
-The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using holistic multi-parametric approaches.
-% cancer cure (care) 的證明
-%# 懺悔
-Since mindfulness meditation will be helpful in cancer healthcare, we continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for their physical body's hard working.
-
-%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
-%七情: 喜、怒、思、悲、恐、驚、憂
-%with more TCGA features (holistic)
-%Dali Lama: Wish and bless the whole world %慈悲心 利他心
-% 多了解身心靈的關係，減少癌症對健康的損害
-
-%the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Patents}
-
-%This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%% optional: The data presented in this study are available in supplementary material.
-\supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, 
-	Figure S1: \textit{P} value plot of the gene NDFIP1,
-	Figure S2: GSE2837 analysis by PrognoScan,  
-	Table S1: The GSE2837 query results from PrognoScan,
-	Table S2: 10 good guys, % ? don't keep it
-	Video S1: title. A supporting video article is available at doi: link}
-
-% Only for the journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, Yu-Chuan (Jack) Li; Data curation, Alexander TH Wu; Formal analysis, Li-Hsing Chi; Investigation, Michael Hsiao; Methodology, Michael Hsiao; Resources, Alexander TH Wu; Software, Li-Hsing Chi and Yu-Chuan (Jack) Li; Supervision, Michael Hsiao and Yu-Chuan (Jack) Li; Writing – original draft, Li-Hsing Chi; Writing – review and editing, Alexander TH Wu.
-All authors have read and agreed to the published version of the manuscript.}
-
-%\institutionalreview{In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals.
-Please note that the Editorial Office might ask you for further information.
-Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals.
-You might also choose to exclude this statement if the study did not involve humans or animals.}
-
-%\informedconsent{Any research article describing a study involving humans should contain this statement.
-Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
-You might also choose to exclude this statement if the study did not involve humans.
-
-%Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
-Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
-
-\funding{The APC was funded by Taipei Medical University}
-
-\institutionalreview{Not applicable}
-
-\informedconsent{Not applicable}
-
-\dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
-%The supplementary figures are available online.%, tables, and R script codes 
-The R script codes and datasets generated during the current study are available at the GitHub repository, https://github.com/texchi2/pvalueTex.}
-
-\acknowledgments{The results shown here are in whole based upon data generated by the \acrshort{tcga} Research Network: https://www.cancer.gov/tcga.
-The tables were generated by latex code with the help from https://www.tablesgenerator.com/latex\_tables# and
-https://github.com/JDMCreator\\/LaTeXTableEditor (accessed at https://www.latex-tables.com/v1/index.html).
-We like to thank Dr. Wen-Chang Wang, %https://orcid.org/0000-0003-3124-2136
-College of Medical Science and Technology, Taipei Medical University, for bioinformatics consultation and helps. 
-We like to thank Sylvain Hall\'e, Department of Computer Science and Mathematics, Univerit\'e du Qu\'ebec \`a Chicoutimi, Canada, for latex technique help with his TeXtidote.
-%We also thank the statistical consultation and helps by Dr. Hsin-Chou Yang of the Institute of Statistical Science, Academia Sinica, Taipei, Taiwan.
-We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
-% *** URL Accessed 20 May 2013.
-The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/mtbwi/index.do.  Accessed 20 May 2020.}
-
-%\subsection*{Authors' information} % Author details (automatic placed here)
-
-\conflictsofinterest{The authors declare no conflict of interest.}
-
-%% Optional
-%\sampleavailability{Samples of the compounds ... are available from the authors.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\abbreviations{The following abbreviations are used in this manuscript:
-\noindent 
-\renewcommand*{\glsinlinenameformat}[2]{\glstarget{#1} {\textsc{#2}},}
-\printglossary[type=\acronymtype, title= , nonumberlist, style=inline]}
-% Abbreviations
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{paracol} % {2} column
-\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-%\externalbibliography{yes}
-%\bibliography{your_external_BibTeX_file}
-
-\externalbibliography{yes}
-%\bibliography{your_external_BibTeX_file}
-\bibliographystyle{chicago} %model1-num-names
-\bibliography{TCGA_margin_cutoff.bib, Holistic.bib, Deep_Learning.bib}
-
-% If authors have biography, please use the format below
-%\section*{Short Biography of Authors}
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
-%{\textbf{Firstname Lastname} Biography of first author}
-%
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
-%{\textbf{Firstname Lastname} Biography of second author}
-
-% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
-For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{document}

### 2021-07-01 Cover_letter_JPM.tex
Updates from Overleaf

@@
 %\end{MyColorPar}
-The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129).
+% from page (ok)
+The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 377 to line 392).
 Also, it is shown here in the following paragraph.
@@
 %[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
-However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
+However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
 Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in
@@
 % and FDR (done; ok)
-We modified the last paragraph of "Cutoff Finder Core Engine" in the Materials and Methods section.
+We modified Figure 5 (with three candidates) and the last paragraph of "Cutoff Finder Core Engine" in the Materials and Methods section.
 %Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
 %***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
+The paragraphs marked in \textcolor{red}{Red} from page 16 (line 502 to line 505) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 We also described "the \textit{P} values are affected by the sample size" in the "Discussions" section.
-The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129),
+% ok
+The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} on page 18 (line 560 to line 572),
 % results ok
-the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 184) to page 6 (line 208), and
-the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129)
+the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 148) to page 6 (line 172) , and
+% ok
+the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 10 (line 236) to page 11 (line 280)
 are the part of the manuscript that has been revised. 
@@
 "  % (ok)
+Trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
+Thus, we should try our best to handle the effect size from Cox's modeling.
+And validation of those candidates is required by using other independent dataset.
+%%% Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff.
+%\subsection{The Purpose of a Sliding-window Cutoff Method}
 Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
-The effect size is the magnitude of the difference (or relationship) among comparing groups.
+The effect size is the magnitude of the difference (e.g., \acrlong{hr}) among comparing groups.
 %A \textit{P} value is a tool to help interpret findings from biomedical research.
@@
 %the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
-While statistical significance can inform the researcher whether an effect exists, 
-the \textit{P} value will not directly tell the effect size.
-%The effect size is the main finding of a quantitative study.
 %Statistical significance depends upon both sample size and effect size. 
@@
 %If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
-Conversely, the effect size can be significant but fail to get statistical significance if the sample size is small. 
+Conversely, the effect size can be large but fail to get statistical significance if the sample size is small. 
 %In this scenario, the \textit{P} value tells the effect does not exist.
-
 The following error could also impact the \textit{P} value:
 \begin{outline}
-\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.x.
-RNA-Seq experiments).
+\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.g., RNA-Seq experiments).
 The larger sample size could reduce the random error. 
@@
 % effect size is large (whatever is true or artificial), the p value is small
-Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
-If a skewed cutoff that split, for example, 425 vs. 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
+While statistical significance can inform the researcher whether an effect exists, the \textit{P} value will not directly tell the effect size.
+Thus, if there is no error in two study groups, and the sample size is the same (not small), the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
+%The effect size is the main finding of a quantitative study.
+If a skewed cutoff that split, for example, 425 versus 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
 % https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
@@
 %Statistical significance is the probability that the observed difference between two groups is due to chance.
-If the P value is larger than the alpha level chosen (e.x.
-0.05), any observed difference is assumed to be explained by sampling variability.
+If the P value is larger than the alpha level chosen (e.g., 0.05), any observed difference is assumed to be explained by sampling variability.
 %The most commonly used α level is 0.05, as proposed by Fischer, is the amount of type I error you are willing to accept.
@@
 %2) \\
-%(ok) % pvalueTex is essential
-There is a benefit for using sliding-window cutoff method (between $30\%-70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
-We have compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
-It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR correction, it has reduced as 967 vs. 209, respectively.
+%(ok) % pvalueTex is essential; find smaller P value to predict large effect size (HR)
+% The effect size is the main finding of a quantitative study.
+There is a benefit for using sliding-window cutoff method (between $30\% - 70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
+We compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
+It shows that the number of genes with unadjusted \textit{P} value $< 0.05$, which is 6284 versus 3118, respectively. After FDR correction, it becomes 967 versus 209, respectively.
 % HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
@@
 That is because of the properly selected cutoff improving the statistical significance.
-Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
+To find a smaller \textit{P} value might predict large effect size (HR) associated biomarkers.
+Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
 
@@
 
-We will explain the above mentioned by an example.
+We explain aforementioned situation by an example.
 %***NDFIP1  % 給他們一個機會
 Reviewing the special case of genes, such as NDFIP1, DKC1, PNMA5, and NPB,
-we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
-NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
+we noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
+NDFIP1 has the FDR-adjusted \textit{P} value as \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "S"- or "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
 %Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
@@
 % the effect size
-Then it has been excluded as a candidate by small effect size (HR = 1.33 in GSE65858 cohort and HR = 1.42 in GSE2837 cohort) less than 1.8.
+However, it was excluded as a candidate by small effect size (HR = 1.33 in GSE65858 and HR = 1.42 in GSE2837) less than 1.8.
+%%%
 "
@@
 We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
+% ok
+The paragraphs marked in \textcolor{red}{Red} on page 17 (line 518 to line 544) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 We placed more descriptions about researcher's work using TCGA to find expression biomarkers in the Introduction section.
-The paragraphs marked in \textcolor{red}{Red} from page 3 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised.
-Also, it is shown here in the following paragraph.\\[0.3cm]
+% ok
+The paragraphs marked in \textcolor{red}{Red} on page 3 (line 98 to line 123) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.\\[0.3cm]
 
@@
 We apologize for exaggerating the difficulties of our workflow.
-The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.
+% ok
+The paragraphs marked in \textcolor{red}{Red} on page 11 (line 282 to line 310) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.
 
@@
 "
-There are three essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
+There are two essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
 
@@
 % risk of *** Answer 2-3 併入此
-Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
-We have checked this issue in detail (in the Discussions section).
-Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
-Furthermore, validation of those candidates is required in the other independent dataset.
+%Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
+%We have checked this issue in detail (in the Discussions section).
+%Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
+%Furthermore, validation of those candidates is required in the other independent dataset.
 % in larger patient populations.% in larger patient
@@
 %ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
-Third, we analyzed the error log during the cutoff finding and Cox modeling, 
+Second, we analyzed the error log during the cutoff finding and Cox modeling, 
 the result shows that program running could be halted by several technical problems.

### 2021-07-01 Supplementary_figures.tex
fixed compiler problems
Updates from Overleaf

@@
 \usepackage{graphicx}
-\usepackage[table,xcdraw]{xcolor}
 
@@
 \usepackage{xcolor}
-
-\newenvironment{MyColorPar}[1]{%
-    \leavevmode\color{#1}\ignorespaces%
-}{%
-}%
+%\usepackage[table,xcdraw]{xcolor}
+%\newenvironment{MyColorPar}[1]{%
+%    \leavevmode\color{#1}\ignorespaces%
+%}{%
+%}%
 
@@
 % Full title of the paper (Capitalized)
-\Title{Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}\\[2cm]
+\Title{Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma}\\[2cm]
 %x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
@@
 % x S3
-%Supplementary Figure \ref{fig:fig_HPA_USP10}\\
-%The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
+Supplementary Figure \ref{fig:fig_HPA_USP10}\\
+The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
 Over-expression of USP10 has poor prognosis on HNSCC.

### 2021-07-01 main.tex
Updates from Overleaf

@@
 In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
-
-\begin{MyColorPar}{red} %%% ***
-There are three essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
-
-First, although \acrshort{tcga} genomics data were harmonized, 
-% three things were found during our investigating and data cleaning:
-the pre-processing of TCGA RNA-Seq in our workflow has been done as follows: 
-\begin{outline}
-\1 HNSCC samples without complete clinical information have been removed;
-\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded; % or 50\%
-\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.
-\end{outline}
-After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that expression value of two genes (gene ID: 9906 and gene ID: 728661) was saved together under the entity of gene symbol "SLC35E2".
-The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
-% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
-% [line 1549]
-%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
-%[line 1654]
-%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
-%NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
-According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?\\queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
-% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
-% keyword: (SLC35E2) AND "Homo sapiens" 
-SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!/hgnc\_id/HGNC:20863).
-Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in this TCGA HNSCC dataset from 20499 to 20500.
-% updated on 18-May-2021
-%\end{outline}
-
-%Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
-
-% risk of *** Answer 2-3 併入此
-Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
-We have checked this issue in detail (in the Discussions section).
-Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
-Furthermore, validation of those candidates is required in the other independent dataset.
-% in larger patient populations.% in larger patient
-%warrant.
-
-% dissection
-%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
-Third, we analyzed the error log during the cutoff finding and Cox modeling, 
-the result shows that program running could be halted by several technical problems.
-These include:
-\begin{outline}
-
-\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression;
-\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;
-%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
-%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
-% error at 16115 gene ""; why? 518 values all are -0.04203 at T
-%  There is only 1 group 
-%This is because of skewed distribution of the expression value. 
-% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
-% all cases belong to >= median => 改為 > median 即可
-% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
-% median = NaN :-); 
-% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
-% and NaN imputation as median
-\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow).
-\end{outline}
-These technical problems could not be detected prior to program running.
-It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity
-
-\end{MyColorPar} %%% red
-
 Our approach describes a workflow implemented in the R script, which runs on the Rstudio server.
@@
 In summary, those three biomarker candidates , clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
-We also found those candidates have proper effect size---the Cox's HR either $> 2.0$ or $< 0.5$.
+We also found those candidates have proper effect size---the Cox's HR either $> 1.8$ or $< 0.6$.
 Thus, the prognosis model with coefficients is established from \acrshort{tcga} and GSE65858 \acrshort{hnscc} cohorts. 
@@
 %%% Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff.
-\subsection{\textit{P} value is affected by sample size and cutoff}
+\subsection{The Purpose of a Sliding-window Cutoff Selection}
+
+% risk of *** Answer 2-3 併入此
+%Second, t
+Trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
+%We have checked this issue in detail (in the Discussions section).
+%Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
+Thus, we should try our best to handle the effect size from Cox's modeling.
+And validation of those candidates is required by using other independent dataset.
+% in larger patient populations.% in larger patient
+%warrant.
+
 Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
@@
 %In this scenario, the \textit{P} value tells the effect does not exist.
-
 The following error could also impact the \textit{P} value:
@@
 
-We will explain the above mentioned by an example.
+We explain aforementioned situation by an example.
 %***NDFIP1  % 給他們一個機會
 Reviewing the special case of genes, such as NDFIP1, DKC1, PNMA5, and NPB,
-we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
-NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
+we noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
+NDFIP1 has the FDR-adjusted \textit{P} value as \num[round-precision=3, round-mode=figures,
+scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "S"- or "W"-shaped acute-bending on the \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
 %Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
@@
 % the effect size
-Then it has been excluded as a candidate by small effect size (HR = 1.33 in GSE65858 cohort and HR = 1.42 in GSE2837 cohort) less than 1.8.
+However, it was excluded as a candidate by small effect size (HR = 1.33 in GSE65858 and HR = 1.42 in GSE2837) less than 1.8.
 %%%
@@
 
+% unclean data: moved from introduction to discussion 
+\subsection{Technical Consideration}
+\begin{MyColorPar}{red} %%% ***
+There are two essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
+
+First, although \acrshort{tcga} genomics data were harmonized, 
+% three things were found during our investigating and data cleaning:
+the pre-processing of TCGA RNA-Seq in our workflow has been done as follows: 
+\begin{outline}
+\1 HNSCC samples without complete clinical information have been removed;
+\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded; % or 50\%
+\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.
+\end{outline}
+After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that expression value of two genes (gene ID: 9906 and gene ID: 728661) was saved together under the entity of gene symbol "SLC35E2".
+The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
+% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
+% [line 1549]
+%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
+%[line 1654]
+%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
+%NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
+According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?\\queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
+% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
+% keyword: (SLC35E2) AND "Homo sapiens" 
+SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!/hgnc\_id/HGNC:20863).
+Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in this TCGA HNSCC dataset from 20499 to 20500.
+% updated on 18-May-2021
+%\end{outline}
+
+%Second, we find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}.
+
+% dissection
+%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
+Second, we analyzed the error log during the cutoff finding and Cox modeling, 
+the result shows that program running could be halted by several technical problems.
+These include:
+\begin{outline}
+
+\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression;
+\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;
+%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
+%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
+% error at 16115 gene ""; why? 518 values all are -0.04203 at T
+%  There is only 1 group 
+%This is because of skewed distribution of the expression value. 
+% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
+% all cases belong to >= median => 改為 > median 即可
+% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
+% median = NaN :-); 
+% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
+% and NaN imputation as median
+\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow).
+\end{outline}
+These technical problems could not be detected prior to program running.
+It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity
+
+\end{MyColorPar} %%% red
+
 \subsection{Validation by Web-based Tools}
-% GSE2837 validated candidates: 10
-We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
-%\subsubsection*{SurvExpress} % TCGA
-% 2021/01/23 pdf x 12 from SurvExpress
-SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
-Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 6 genes:\\ % SurvExpress 有類似的結果:
-(1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
-%, STIP1 (0.001), DKC1 (0.01);\\
-%DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
-(2) better prognosis: FCGBP (0.001).\\
-%ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
-%17 out of 20 candidates
-%?DKK1 (0.253635),
-The 6 out of 10 candidate genes are also confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
-% moved to supplementary file: Supplementary_figures.tex
-% \linksupplementary{Supplementary_figures.pdf},
-% % SurvExpress 沒有類似的結果是因為:
-%Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
-Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
-Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
-%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
 
@@
 Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
-All transcriptomics data has been retrieved from the TCGA, and all proteomics data has been generated in-house using the same antibodies.
-Our 5 candidates (e.g.
-CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+All transcriptomic data were retrieved from the TCGA, and all proteomics were generated in-house using the same antibodies.
+The genes (e.g.
+CAMK2N1, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
 FCGBP is on the list of favorable prognostic genes as well.
@@
 % ZNF557, ZNF266, and FCGBP
-Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.\\
-org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
+%Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
 % 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
 %found at Human Protein Atlas dataset 
-(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
+%(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
 % moved to Supplementary
@@
 
-%%%
-\subsection{The Candidates Shown in Literature Review}
-
-%%
-%\subsection*{Review articles}
-Since the discovery of workflow, we performed the literature review by Embase/Pubmed.% to find the evidence convincing the suggested biomarkers in cancer research. 
-The 5 out of 10 candidates has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
-
-%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
-%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
-%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
-
-%%%%%% bad guy
-%The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
-Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
-Pang et al.\cite{Pang2018} has proved that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhances their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
-Increased DKK1 levels in HNSCC tissues is correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
-DKK1 expression is significantly associated with smoking, alcohol abuse, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
-The mRNA expression of DKK1 and DKK3 is elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
-Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
-%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
-%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
-%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
-%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
-%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
-
-%STC2:
-%The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway\cite{Ma2020}.
-
-% PGK1
-Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). 
-The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
-PGK1 is responsive in hypoxia status, since it is one of \acrshort{hif}-1 alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.
-
-%SURF4
-The patients with tumors (such as glioma, breast cancer, lymphoma, pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
-) exhibiting high Surfeit gene 4 (SURF4) expression have significantly shorter overall survival than low SURF4 expression.
-SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
-%NIH/3T3 cells (Mus musculus, mouse), 293T cell
-%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
-%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
-%web-based tools survival (not TCGA?)
-
-% USP10
-Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs), may serve as a prognostic biomarker and target for various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
-Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - reveals that USP10 is significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL-2–STAT5 signaling, transforming growth factor beta (TGFB or $TGF\beta$) signaling, and PI3K/Akt/mTOR signaling\cite{Ren2020}.
-% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
-%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
-https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
-
-%FOXA2
-Prognostic signature integrated of DNA methylation, gene expression, and clinical information could provide a prognostic prediction value for HNSCC patients.
-Forkhead Box A2 (FOXA2) is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
-%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
-%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
-% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
-%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
-Further, SIS analysis was performed to further screen out a stable probe combination.
-Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
-2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
-Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
-2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
-%Association between gene expression and methylation.
-Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
-Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
-
-% STIP1; non-TCGA
-%Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}.
-The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
-%STIP1 could bind to bind Hsp70 and Hsp90.
-
-%IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in oral cancer.
-%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
-%IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
-% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
-
-%%%%%% good guy
-%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
-%Oncogenic human herpesviruses (e.g., EBV and KSHV) 
-%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
-%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
-
-%ZNF266, % or ZNF16, HZF1?
-%MYO1H associated mandibular prognathism\cite{Sun2018}
-
-% FCGBP
-% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
-Fc fragment of IgG binding protein ($Fc\gamma BP$ or FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas\cite{ODonovan2002}\cite{Griffith2006}.
-%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
-%gene ID @gene@8857
-
-%\acrfull{LOC148709} has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
-In our current study, LOC148709 is also suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3} on page \pageref{table:table3}).
-
-%EVPLL in cDNA project
-
-% PNMA5
-%Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}.
-
-%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
-GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
-
-%calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
-(PMID31598163)
-%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
-The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
-Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
-%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
-%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
-%\cite{Li2018b}
-%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
-%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
-
-%NDFIP1:
-%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
-was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
-%MCF7 cells 
-%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
-%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
-%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
-Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
-We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
-hepatocellular carcinoma\cite{Zhang2019a}
-% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
-%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
-It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
-
-%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
-%DKC1 is the tumor suppressor gene in HNSCC
-% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
-
-\subsection{Limitations of the Work}
+\subsection{Future Direction in Translational Medicine}
+
+\subsubsection{Proteomics Validation}
 
@@
 We are aware of the importance of direct assessment of protein products comprising the basic functional units in cancer cells' biological processes.
+% TCPA, TCIA (immune genes), TCIA (whole-slide image)
 The announcement of the Cancer Proteome Atlas (\acrshort{tcpa}, http://tcpaportal.org) excites the cancer research community\cite{Li2013c}\cite{Li2017b}.
@@
 %文章的初衷、跨領域：如同deep leaning Keras API，推廣給研究者一個有效的方法 
-We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
+We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} method allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets.
 % to find more useful biomarkers.
@@
 %Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
-Once our laboratory or the community confirms those candidates as the targets, the compound screening\cite{Yang2004}\cite{Hsu2011}\cite{Pathak2021} could facilitate more individualized therapy for HNSCC patients.
+Once our laboratory or the community confirms those candidates as the targets, the compound screening\cite{Yang2004}\cite{Hsu2011}\cite{Pathak2021} could facilitate more personalized therapy for HNSCC patients.
 %and improve prognosis.
@@
 
-\subsection{Future Direction in Translational Medicine}
-
 %\subsubsection{Tumor-agnostic Research}
@@
 % *** yes here
-In our previous work, altered glucose metabolism (e.k.a.
-the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
+In our previous work, altered glucose metabolism---the Warburg effect\cite{Warburg1956} promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
 % Cited In for PMID: 28061796
@@
 
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 %\subsection{A introduction of TCGA}
@@
 % RESTful API
-\end{MyColorPar}
-
-GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
+%\end{MyColorPar}
+
+GDC's \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals.
 Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters.
@@
 This iteration method could calculate all possible cutoff of each gene expression in this cohort.
-At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff at specific patient grouping  (e.g., low-expression in 262 persons vs.
-high-expression in 152 persons with gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}, please see Figure \ref{fig:figure4}).
+At each run of cutofFinder\_func function call for an individual gene, it returned an optimal cutoff at specific patient grouping  (e.g., low-expression in 262 persons versus high-expression in 152 persons with gene \acrlong{CAMK2N1}, \acrshort{CAMK2N1}, please see Figure \ref{fig:figure4}).
 The cutoff would be returned to the main program to allow downstream Cox survival analysis.
@@
 The Cox model is also accounting for confounding factors\cite{Magen2019}.
-It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.g.,, death) at time t. It can be estimated as follow:
+It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.g., death) at time t. It can be estimated as follow:
 
@@
 \begin{outline} % for highlight
-\1 t represents the survival time
-\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g.,, clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
-\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
-\1 the term $h_0$ is called the baseline hazard.
+\1 t represents the survival time;
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g., clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status);
+\1 The coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates;
+\1 The term $h_0$ is called the baseline hazard.
 It corresponds to the hazard value if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
-The "t" in $h(t)$ indicates the hazard may vary over time
+The "t" in $h(t)$ indicates the hazard may vary over time.
 \end{outline}
 
-Thus, the biomarker discovery strategy is survival modeling through a collection of $X_1...X_n$ features from cancer datasets.\\[1cm]
+Thus, the biomarker discovery strategy is survival modeling through a collection of $X_1...X_n$ features from cancer datasets.%\\[1cm]
 
@@
 % Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction 才對
-Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
-Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, candidate selection).
+Those genes with prognostic impact, whose hazard ratio $>= 1.8$ or $<= 0.6$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
+Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the decision (see Figure \ref{fig:figure1}, candidate selection).
 
@@
 %n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
-The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009).
+The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on 7 November, 2009).
 % (RefSeq)
-GSE65858 is a dataset for candidate selection in our workflow.
-We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
+GSE65858 is a dataset for helping of candidate selection in our workflow.
+We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.
 \end{MyColorPar} % red
@@
 GSE2837 HNSCC dataset (microarray gene expression by Affymetrix X3P chips U133\_X3P) has 28 participants and RFS information. 
-Using PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a} for the validation of candidates.
+Using PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a} for the validation of our candidates.
 %??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
@@
 Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
-Our findings suggested 10 candidate biomarkers,CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2, as well as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff points with stringent Bonferroni \textit{P} values and proper confounders control.
-They also might be potential common biomarkers for subsequent study.
+Our findings suggested 3 biomarker candidates---CAMK2N1, IL19, and FCGBP, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff with stringent Bonferroni \textit{P} values and proper effect size (HR).
+%They also might be potential common biomarkers for subsequent study.
 % welcome for study
 %tumor-agnostic research, we plan to explore common biomarkers crossing TCGA diseases
-We wish this workflow will be available for the reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} and tumor-agnostic research\cite{Looney2020} to crossing several \acrshort{tcga} diseases to make translational impacts.
+%We wish this workflow will be available for the reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} and tumor-agnostic research\cite{Looney2020} to crossing several \acrshort{tcga} diseases to make translational impacts.
 %Tex: PvalueTex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% for journal Sci
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%
+\subsection{x The Candidates Shown in Literature Review}
+
+%%
+% %\subsection*{Review articles}
+Since the discovery of workflow, we performed the literature review by Embase/Pubmed.% to find the evidence convincing the suggested biomarkers in cancer research. 
+The 3 candidates has also been suggested by published studies using TCGA cohort, in-house cohort, or experiments in vitro and in vivo.
+
+%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
+%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
+%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
+
+%%%%%% bad guy
+%The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
+Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}.
+Pang et al.\cite{Pang2018} has proved that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhances their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo.
+Increased DKK1 levels in HNSCC tissues is correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
+DKK1 expression is significantly associated with smoking, alcohol abuse, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
+The mRNA expression of DKK1 and DKK3 is elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}.
+Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}.
+%Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients.
+%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
+%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
+%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
+%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)
+
+%STC2:
+%The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway\cite{Ma2020}.
+
+% PGK1
+%Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). 
+%The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
+%PGK1 is responsive in hypoxia status, since it is one of \acrshort{hif}-1 alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.
+
+%SURF4
+%The patients with tumors (such as glioma, breast cancer, lymphoma, pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC) exhibiting high Surfeit gene 4 (SURF4) expression have significantly shorter overall survival than low SURF4 expression.
+%SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
+%NIH/3T3 cells (Mus musculus, mouse), 293T cell
+%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
+%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
+%web-based tools survival (not TCGA?)
+
+% USP10
+%Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs), may serve as a prognostic biomarker and target for various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
+%Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - reveals that USP10 is significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL-2–STAT5 signaling, transforming growth factor beta (TGFB or $TGF\beta$) signaling, and PI3K/Akt/mTOR signaling\cite{Ren2020}.
+% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
+%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631.
+https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer
+
+%FOXA2
+%Prognostic signature integrated of DNA methylation, gene expression, and clinical information could provide a prognostic prediction value for HNSCC patients.
+Forkhead Box A2 (FOXA2) is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
+%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
+%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
+% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
+%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05.
+Further, SIS analysis was performed to further screen out a stable probe combination.
+Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig.
+2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively.
+Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig.
+2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
+%Association between gene expression and methylation.
+Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis).
+Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.
+
+% STIP1; non-TCGA
+%Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}.
+The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
+%STIP1 could bind to bind Hsp70 and Hsp90.
+
+%%%%%% good guy
+IL-19 specifically activated an intracellular signal and induced proliferation of the cells, which indicated that IL-19 may act in an autocrine manner in HNSCC.
+%IL19 in esophageal squamous cell carcinoma\cite{Hsing2013}, the effects of IL-19 on the esophageal SCC in vivo and in vitro. CE81T cells
+IL-19 may be involved in the pathogenesis of systemic inflammatory diseases. %IL-19 is also involved in various inflammatory diseases such as psoriasis, asthma, and rheumatoid arthritis.
+% the Chi-Mei Medical Center Institutional Review Board (IRB9705-003). n=60
+
+%ZNF557 is a tumor suppressor in HPV-positive HNSCC???
+%Oncogenic human herpesviruses (e.g., EBV and KSHV) 
+%Oncogenic human viruses are silenced through the activities of two members of the Kruppel-associated box (KRAB) domain-zinc finger protein (ZFP) (KRAB-ZFP) epigenetic silencing family, revealing a novel STAT3-KRAB-ZFP axis of virus latency.
+%Epstein-Barr virus (EBV) and Kaposi’s sarcoma-associated herpesvirus (KSHV) are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}
+
+%ZNF266, % or ZNF16, HZF1?
+%MYO1H associated mandibular prognathism\cite{Sun2018}
+
+% FCGBP
+% IgG Fc binding protein ($Fc\gamma BP$), (Fc Fragment Of IgG Binding Protein) 
+Fc fragment of IgG binding protein ($Fc\gamma BP$ or FCGBP) is expressed in normal thyroid and, more significantly, it is down-regulated in papillary and follicular thyroid carcinomas\cite{ODonovan2002}\cite{Griffith2006}.
+%in thyroid biopsies might help to make the difficult distinction between a thyroid follicular adenoma and a follicular carcinoma.\cite{ODonovan2002}\cite{Griffith2006}, 
+%gene ID @gene@8857
+
+%\acrfull{LOC148709} has a contribution to the Warburg effect on esophagus cancer\cite{Liu2019}.
+In our current study, LOC148709 is also suggested as a biomarker of \acrshort{hnscc} (see Table \ref{table:table3} on page \pageref{table:table3}).
+
+%EVPLL in cDNA project
+
+% PNMA5
+%Paraneoplastic Ma 5 (PNMA5) promotes apoptosis signaling in HeLa (cervical cancer) and MCF-7 (breast cancer) cells\cite{Lee2016}.
+
+%The endogenous ligand of G protein-coupled receptors (GPR7) is IQCN (previous/former name as KIAA1683), and NPB (Neuropeptide B)\cite{Andreis2005}.
+GPR7 is associated with a poor prognosis of prostate cancer\cite{Cottrell2007}.
+
+calcium/calmodulin-dependent protein kinase II inhibitor (CAMK2N1) is the endogenous inhibitor of CAMK2, which is activated by an increased intracellular Ca2+ concentration.
+SYT12 plays a critical role in oral cancer and may be a novel therapeutic target.
+(PMID31598163)
+%Overall survival times (as determined by Kaplan-Meier analysis) were markedly longer in patients that had elevated CAMK2N1 expression compared with patients with negative or low CAMK2N1 expression.
+The miR-182-5p plays a vital role in controlling OSCC cell apoptosis and proliferation by regulating CAMK2N1 expression, which was found to be reduced in OSCC.
+Down-regulation of miR-182-5p expression attenuated tumor growth, cell survival, and proliferation in vivo through the regulation of the AKT/ERK1/2/NF-κB signaling pathways.
+%CAMK2N1 operated as a tumor suppressor gene in patients with HNSCC.
+%: 26 results of cancer: ; 1 HNSCC cell line (CAL-27) all said "good guy"
+%\cite{Li2018b}
+%EMT genes (TCF3, CAMK2N1, EGFR, and IGFBP4) 
+%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
+
+%NDFIP1:
+%The adaptor protein Nedd4-family interacting protein 1 (NDFIP1), was reported as candidate biomarker for breast cancer\cite{Tian2020}.
+was both better prognosis in the overall survival (OS) and relapse free survival (RFS)
+%MCF7 cells 
+%Howitt et al showed that NDFIP1 knockdown results in the loss of phosphatase and tensin homolog nuclear compartmentalization, promotes cell proliferation, and alters the cell cycle
+%NDFIP1 is a direct target of miR-155; MiR-155 promotes uveal melanoma cell proliferation and invasion by regulating NDFIP1 expression.
+%=> good guy: Zhang et al\cite{Zhang2019a} report that miR-873 promotes Warburg effect in HCC cells by increasing glucose uptake, extracellular acidification rate (ECAR), lactate production, and ATP generation, and decreasing oxygen consumption rate (OCR) in HCC cells.
+Mechanistically, we show that miR-873 activates the key glycolytic proteins AKT/mTOR via targeting NDFIP1 which triggers metabolic shift.
+We further demonstrate that enhanced glycolysis is essential for the role of miR-873 to drive HCC progression.
+hepatocellular carcinoma\cite{Zhang2019a}
+% MiR-873 promotes the proliferation, migration, and invasion of liver cancer cells via NDFIP1 in HEK293T cell.
+%  the adaptor protein Nedd4-family interacting protein 1 (NDFIP1) plays a key role in the ubiquitination and nuclear translocation of PTEN.
+It represses cell proliferation of melanoma and thus acts as a tumor suppressor.(PMID: 29333944)
+
+%DKC1 (dyskeratin) is related with HNSCC\cite{Smith2010}.
+%DKC1 is the tumor suppressor gene in HNSCC
+% Fanconi anemia (FA) and dyskeratosis congenita (DC) are rare inherited syndromes that cause head and neck squamous cell cancer (HNSCC).
+
+% 3-2 web-tools validation
+% GSE2837 validated candidates: 10
+We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
+%\subsubsection*{SurvExpress} % TCGA
+% 2021/01/23 pdf x 12 from SurvExpress
+SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data.
+Using their TCGA HNSCC cohort (June 2016, n = 502), the survival significance (Kaplan Meier \textit{P} value) shows in 2 genes:\\ % SurvExpress 有類似的結果:
+(1) poor prognosis: CAMK2N1 (0.000006), NDFIP1 (0.000008);\\
+%PGK1 (0.01), SURF4 (0.002), USP10 (0.002), 
+%, STIP1 (0.001), DKC1 (0.01);\\
+%DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
+(2) better prognosis: FCGBP (0.001).\\
+%ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
+%17 out of 20 candidates
+%?DKK1 (0.253635),
+The 6 out of 10 candidate genes are also confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
+% moved to supplementary file: Supplementary_figures.tex
+% \linksupplementary{Supplementary_figures.pdf},
+% % SurvExpress 沒有類似的結果是因為:
+%Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
+Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
+Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
+%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項
+
+%%
 % figure for IL19 Cox's table

### 2021-07-03 Cover_letter_JPM.tex
Updates from Overleaf

@@
 \newacronym{CAMK2N1}{CAMK2N1}{calcium/calmodulin dependent protein kinase II inhibitor 1} 
+\newacronym{CALML5}{CALML5}{calmodulin like 5}
+
 \newacronym{STC2}{STC2}{stanniocalcin 2} 
@@
 %[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
-However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
+However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5": top 3 candidate biomarkers, CAMK2N1, CALML5, and FCGBP).
 Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in
@@
 
-% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
+% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05); CALML5 (1.97e-04)
 \setlength{\unitlength}{1cm}
@@
 \centering
-  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_IL19_FCGBP.pdf}}%
+  \put(0,0){\includegraphics[width=14cm]{Figure_4_CAMK2N1_CALML5_FCGBP.pdf}}%
   \put(2.5, 14.3){\fontfamily{qcr}\selectfont
@@
     \put(2.5, 9.45){\fontfamily{qcr}\selectfont
-  \tiny *\textit{P} = \num{6.54e-06}}%IL19
+  \tiny *\textit{P} = \num{1.97e-04}}%IL19 -> CALML5
     \put(2.5, 4.55){\fontfamily{qcr}\selectfont
@@
 \bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
-{The Kaplan-Meier curves of (a) CAMK2N1, (c) IL19, and (e) FCGBP under optimal \textit{P} value. 
+{The Kaplan-Meier curves of (a) CAMK2N1, (c) CALML5, and (e) FCGBP under optimal \textit{P} value. 
 %((b) the cutoffs derived from it's cumulative \textit{P} value plot).
@@
 %(e) Kaplan-Meier plot of FCGBP under optimal \textit{P} value.\\
-The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
+The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) CALML5, and (f) FCGBP, respectively,
 shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+In the study of GSE65858 cohort, CAMK2N1, CALML5, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
@@
 However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
-There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
+There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the biomarker.
 %In the consensus of TCGA and GSE65858 cohorts,
@@
     unadjusted \textit{P} value less than 0.05.
-    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.
+    \textcolor{red}{CAMK2N1}, \textcolor{red}{CALML5}, \textcolor{red}{FCGBP} and the 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.
     The 22 genes, listed on the side, have hazard ratio between 0.6 and 1.5.\\
@@
 CAMK2N1 & \num{2.97e-7} & \num{6.87e-3} & \num{1.63e-5} & 0.038 & 2.101 & 1.814 \\
-IL19    & n/a           & 0.03          & n/a           & 0.047 & n/a   & 0.630  \\
+CALML5    & \num{5.87e-6}  & \num{4.75e-3}          & \num{1.97e-4}          & 0.035 & 0.493   & 0.541  \\
 IL19    & \num{3.73e-7} & \num{2.69e-3} & \num{6.54e-6} & 0.031 & 0.472 & 0.630  \\
@@
 \hline
-  \multicolumn{7}{l}{(IL19 has two probes in RNA-Seq experiment of GSE65858)}\\
-  \multicolumn{7}{l}{(FDR: \acrlong{fdr})}\\
+%  \multicolumn{7}{l}{(IL19 has two probes in RNA-Seq experiment of GSE65858)}\\
+  \multicolumn{7}{l}{(FDR: \acrlong{fdr}; HR: hazard ratio)}\\
 \hline
@@
     % GSE117973 using the same platform GPL10558
-    This HNSCC cohort has been applied for filtering of our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
+    This HNSCC cohort has been applied for filtering of our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{CALML5}, and \textcolor{red}{FCGBP}.
     Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
@@
 %em dash ---
-These CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN---previous name as KIAA1683, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
+These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN---previous name as KIAA1683, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
 %These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox's HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+In the study of GSE65858 cohort with median cutoffs, CAMK2N1, CALML5, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox's HR ($>1.8$ or $<0.6$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002
@@
 %This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
-Conversely, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
-Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
+Conversely, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $<0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
+Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the HNSCC biomarker.
 Finally, these 3 candidates were also confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
@@
 
-We explain aforementioned situation by an example.
+We explain aforementioned situation by examples.
 %***NDFIP1  % 給他們一個機會
@@
 %%%
-"
 
@@
 % x****** IL19 必須要靠 pvalueTex 才能發現
-%The other example is one of our candidate: IL19.
+The other example is IL19.
 It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-adjusted \textit{P} value has large difference between 50\% quantile cutoff (FDR 0.115) and optimal 48\% quantile cutoff (FDR \num{6.54e-6}).
 This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
-Fortunately, IL19 has competed to become a candidate by its better effect size (HR = 0.472 in TCGA cohort), and also by the validation with the other independent cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031 in GSE65858 cohort).
-
+However, IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
+"
 %*** IL19 is excluded by this way :-) (special S-curve P value plot)

### 2021-07-03 main.tex
Updates from Overleaf

@@
 
+%\section{abbreviation}
 %%%%%%%%%%%%% Define abbreviation
@@
 
+%\section{abstract}
 %%%%%%%%%%
@@
 After adjustment with confounders, we found that the clinical tumor stage and the surgical margin involvement are independent risk factors in patient survival.
-According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, IL19, and FCGBP, are significantly associated with the patients' overall survival.
+According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, CALML5, and FCGBP, are significantly associated with the patients' overall survival.
 The other independent HNSCC data were also used to validate this discovery.
@@
 \keyword{Head and Neck Squamous Cell Carcinoma (HNSCC);
-the Cancer Genome Atlas (TCGA); Transcriptomic Analysis; Survival Analysis; Optimal Cutoff; Effect Size; \acrfull{CAMK2N1}; \acrfull{IL19}; \acrfull{FCGBP}; Mindfulness Meditation}
+the Cancer Genome Atlas (TCGA); Transcriptomic Analysis; Survival Analysis; Optimal Cutoff; Effect Size; \acrfull{CAMK2N1}; \acrfull{CALML5}; \acrfull{FCGBP}; Mindfulness Meditation}
 
@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 out of those 20 genes discovered in the TCGA cohort), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox's HR ($> 1.8$ or $< 0.65$) (please see Table \ref{tab:table_top3_GSE65858}).
+In the study of GSE65858 cohort with median cutoffs, CAMK2N1, CALML5, and FCGBP (3 out of those 20 genes discovered in the TCGA cohort), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox's HR ($> 1.8$ or $<0.6$) (please see Table \ref{tab:table_top3_GSE65858}).
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002
@@
 Conversly, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
-Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
+Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the HNSCC biomarker.
 Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
@@
     (\textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
-    The 22 genes, listed on the side, have hazard ratio $> 1.8$ or $< 0.6$.\\
+    The 22 genes, listed on the side, have hazard ratio $> 1.8$ or $<0.6$.\\
     (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value with log10 transformed);
@@
 The plot in Figure \ref{fig:figure4}(b) shows a "backlash" curve with the half of values below \num{1.0e-3}.
-%IL19
-Conversely, the most associated gene with better survival is \acrfull{IL19}.
-In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 215 patients bearing the higher expression of \acrshort{IL19} had 60\% of 5-year OS survival rate (Bonferroni-adjusted \textit{P} $ = 0.002$).
+%IL19 -> CALML5 Bonferroni 0.039
+Conversely, the most associated gene with better survival is \acrfull{CALML5}.
+In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve reveals 200 patients bearing the higher expression of \acrshort{CALML5} had 60\% of 5-year OS survival rate (Bonferroni-adjusted \textit{P} $ = 0.039$).
 The sliding-window cutoff selection generated cumulative \textit{P} value plot in Figure \ref{fig:figure4}(d).
-This plot reveals a special "S" curve with a acute bending on the middle portion (we will discuss this finding in the Discussions section).
-The 161 uncorrected \textit{P} values were estimated by a serial cut from 125 to 286 for grouping the cohort.
-The smallest \textit{P} value (\num{3.73e-7}), when cut at n = 199 (48.1\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.147 \acrshort{rsem} of \acrshort{rnaseq}.
+This plot reveals a "V" curve with the minimum at middle portion.
+The 166 uncorrected \textit{P} values were estimated by a serial cut from 125 to 290 for grouping the cohort.
+The smallest \textit{P} value (\num{5.87e-6}), when cut at n = 214 (51.7\% of total cohort 414), has been defined as an optimal \textit{P} value with a cutoff value -0.359 \acrshort{rsem} of \acrshort{rnaseq}.
 % FCGBP
@@
 
-% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05)
+% TCGA FDR Pvalue of CAMK2N1 (1.628308e-05), IL19 ( 6.543871e-06), FCGBP (4.827833e-05), CALML5 (0.0001970348)
 \setlength{\unitlength}{1cm}
@@
     \put(2.5, 9.45){\fontfamily{qcr}\selectfont
-  \tiny *\textit{P} = \num{6.54e-06}}%IL19
+  \tiny *\textit{P} = \num{1.97e-4}}%IL19 6.54e-06 -> CALML5 0.0001970348
     \put(2.5, 4.55){\fontfamily{qcr}\selectfont
@@
 %The optimal cutoff value for CAMK2N1 is 
-The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) IL19, and (f) FCGBP, respectively,
+The cutoffs, in the cumulative \textit{P} value plots of (b) CAMK2N1, (d) CALML5, and (f) FCGBP, respectively,
 shows that over 50\% of those unadjusted \textit{P} values are below 0.001 derived by sliding-window cutoff finding procedure.\\
@@
   1.490-2.704 \\ \hline
-IL19 &
-  \multicolumn{2}{l|} {interleukin 19} &
-   \num{6.54e-6} & %3.7e-7} &
-   0.002 &
-   0.472 &
-   0.351-0.635 &
-   0.459 &
-   0.340-0.619 \\ \hline
+CALML5 &
+  \multicolumn{2}{l|} {\acrlong{CALML5}} &
+   \num{1.97e-4} & %\num{6.54e-6} & %3.7e-7} &
+   0.039 &
+   0.51 &
+   0.379-0.686 &
+   0.493 &
+   0.364-0.667 \\ \hline
 FCGBP &
@@
 (1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;\\
-(2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in TCGA cohort;\\
-(3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in GSE65858 cohort
+(2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.6 in TCGA cohort;\\
+(3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.6 in GSE65858 cohort
 \end{tabular}
@@
 %%%
+
+The other example is IL19.
+It has a \textit{P} value plot with acute S-curve bending at the median zone, that lets the FDR-adjusted \textit{P} value has large difference between 50\% quantile cutoff (FDR 0.115) and optimal 48\% quantile cutoff (FDR \num{6.54e-6}).
+This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
+However, IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
+
 \end{MyColorPar} % red
@@
 Furthermore, the four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are correlated with better survival.
-Our findings suggested 3 biomarker candidates---CAMK2N1, IL19, and FCGBP, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff with stringent Bonferroni \textit{P} values and proper effect size (HR).
+Our findings suggested 3 biomarker candidates---CAMK2N1, CALML5, and FCGBP, are all heavily associated with the prognosis of \acrshort{os} under optimal cutoff with stringent Bonferroni \textit{P} values and proper effect size (HR).
 %They also might be potential common biomarkers for subsequent study.

### 2021-07-03 Cover_letter_JPM.tex
Updates from Overleaf

@@
 Since previous reviewer's suggestion, we made a major revision on the followings:
-1) suggested candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
-We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
+1) suggested candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE65858).
+%We also reviewed literature that supports the prognostic impact of these candidate genes. 
+The resulting Figure 4, and Table 3 are different between the two manuscripts.
 2) Since that revision, we added holistic cancer care in the discussions section (please see Answer 1-2).% \ref{page:1-2}).
@@
 %PvalueTex consensus with GSE2837 to yield 3 candidates
-In the study of GSE65858 cohort, CAMK2N1, CALML5, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
+In the study of GSE65858 cohort, CAMK2N1, CALML5, and FCGBP, keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.6$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
 % (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
@@
 Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the HNSCC biomarker.
-Finally, these 3 candidates were also confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
+%Finally, these 3 candidates were also confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
 "\\[0.3cm]
@@
 To find a smaller \textit{P} value might predict large effect size (HR) associated biomarkers.
-Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
+Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
 
@@
 % the effect size
-However, it was excluded as a candidate by small effect size (HR = 1.33 in GSE65858 and HR = 1.42 in GSE2837) less than 1.8.
+However, it was excluded as a candidate by small effect size (HR = 1.33 in GSE65858) less than 1.8.
 %%%
@@
 %# "EZR" has \textit{P} value $>0.05$
-  \caption{(a) OS in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) Those genes (listed on the rigth side) have not significant hazard ratio (HR) if calculated individually (EZR is not shown on volcano plot due to it's Kaplan-Meier \textit{P} value $>0.05$)}
+  \caption{(a) Overall survival in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) Those genes (listed on the right side) have not significant hazard ratio (HR) if calculated individually (EZR is not shown on volcano plot due to it's Kaplan-Meier \textit{P} value $>0.05$)}
     \label{fig:signature4}

### 2021-07-03 Supplementary_figures.tex
Updates from Overleaf

--- 2021-06-18 Supplementary_figures.tex
@@
 %ST1
-Supplementary Table \ref{table:table1}\\
-GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
+%Supplementary Table \ref{table:table1}\\
+%GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
 The poor prognostic genes are marked as red; the better prognostic genes are marked as green.
@@
 \hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\
+\multicolumn{9}{|l!{\color{black}\vrule}}{}%Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\
 \hline
@@
 \hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{}= 1.5\\
 %\hline
@@
 %\hline
-lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
+lncRNA: Long non-coding RNA\\%Remark: \checkmark Validated by GSE2837
+~\end{tabular}}                                                                                                                                                                                                                 \\
 \hline
@@
 %S2
-Supplementary Figure \ref{fig:fig_GSE2837}\\
-GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
+%Supplementary Figure \ref{fig:fig_GSE2837}\\
+%GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots).
 The poor prognostic genes are marked as red; the better prognostic genes are marked as green.
@@
 % from Answer2-2 GSE2837; 
-\begin{figure}
-\raggedleft
-\includegraphics[width=12cm]{Answer_2-2.pdf}
-\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
+%\begin{figure}
+%\raggedleft
+%\includegraphics[width=12cm]{Answer_2-2.pdf}
+%\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots).
 The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
-\label{fig:fig_GSE2837}
-\end{figure}
+%\label{fig:fig_GSE2837}
+%\end{figure}
 

### 2021-07-03 main.tex
Updates from Overleaf

@@
 The candidate selection performs (1) dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses;
-(2) survival analyses of the other HNSCC dataset (GSE65858) using Kaplan-Meier estimate (KM, with FDR correction) and Cox modeling (CoxHR).\\
-The selected genes were validated by third HNSCC cohort (GSE2837).\\
+(2) survival analyses of the other HNSCC dataset (GSE65858) using Kaplan-Meier estimate (with FDR correction) and Cox modeling.\\
+The biomarker candidates were a consensus result of TCGA and GSE65858. 
+%The selected genes were validated by third HNSCC cohort (GSE2837).\\
 (HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
@@
 %candidate_fdr100
-%PvalueTex consensus with GSE2837 to yield 3 candidates
+%PvalueTex consensus with (x) GSE2837 to yield 3 candidates
 In the study of GSE65858 cohort with median cutoffs, CAMK2N1, CALML5, and FCGBP (3 out of those 20 genes discovered in the TCGA cohort), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox's HR ($> 1.8$ or $<0.6$) (please see Table \ref{tab:table_top3_GSE65858}).
@@
 Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the HNSCC biomarker.
-Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
+%Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
 \end{MyColorPar} % end red
@@
 CALML5    & \num{5.87e-6}  & \num{4.75e-3}          & \num{1.97e-4}          & 0.035 & 0.493   & 0.541  \\
-IL19    & \num{3.73e-7} & \num{2.69e-3} & \num{6.54e-6} & 0.031 & 0.472 & 0.630  \\
+%IL19    & \num{3.73e-7} & \num{2.69e-3} & \num{6.54e-6} & 0.031 & 0.472 & 0.630  \\
 FCGBP   & \num{1.21e-6} & 0.01          & \num{4.83e-5} & 0.039 & 0.484 & 0.573\\
@@
 To find a smaller \textit{P} value might predict large effect size (HR) associated biomarkers.
-Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.
-
+Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
+% no more GSE2837
 %small effect size could be double-checked by GSE65858.
@@
 % the effect size
-However, it was excluded as a candidate by small effect size (HR = 1.33 in GSE65858 and HR = 1.42 in GSE2837) less than 1.8.
-%%%
+However, it was excluded as a candidate by small effect size (HR = 1.33 in GSE65858) less than 1.8.
+%%%  and HR = 1.42 in GSE2837
 
@@
 The genes (e.g.
-CAMK2N1, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+CAMK2N1, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/\\humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
 FCGBP is on the list of favorable prognostic genes as well.
@@
 
-Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
-GSE2837 HNSCC dataset (microarray gene expression by Affymetrix X3P chips U133\_X3P) has 28 participants and RFS information. 
+%Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c}, GSE2837 HNSCC dataset (microarray gene expression by Affymetrix X3P chips U133\_X3P) has 28 participants and RFS information.
 Using PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a} for the validation of our candidates.
@@
 %% optional
-%% optional: The data presented in this study are available in supplementary material.
+%% optional: The data presented in this study are available in supplementary material. Supplementary_figures.tex
 \supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, 
 	Figure S1: \textit{P} value plot of the gene NDFIP1,
-	Figure S2: GSE2837 analysis by PrognoScan,  
-	Table S1: The GSE2837 query results from PrognoScan,
-	Table S2: 10 good guys, % ? don't keep it
+%	Figure S2: GSE2837 analysis by PrognoScan,  
+%	Table S1: The GSE2837 query results from PrognoScan,
+	Table S1: 10 bad guys, % ? don't keep it
+	Table S2: 10 good guys, % 要加入 CALML5
 	Video S1: title. A supporting video article is available at doi: link}

### 2021-07-04 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
+%\usepackage{xr}  % for cross-reference
+\usepackage{xr-hyper}
+\usepackage{hyperref}
+
+%\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % for \label page and line
+%\newcommand{\lr}[1]{page~\pageref{#1} (line~\lineref{#1})} % for \ref page and line
+\makeatletter
+  \long\def\myempty{}
+  \def\XR@addURL#1{\XR@@dURL#1\myempty{}{}{}{}{}\\}
+  \def\XR@@dURL#1#2#3#4#5#6#7\\{%
+    {#1}{#2}%
+    \ifx\myempty#6\@empty
+      {#3}{#4}{\XR@URL}%
+    \else
+    \fi
+  }
+\makeatother
+
+\makeatletter
+\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{%
+    \externaldocument{#1}%
+    \addFileDependency{#1.tex}%
+    \addFileDependency{#1.aux}%
+}
+% turn it off
+%\myexternaldocument{main} % or main_REDmarked_revision2.tex
+%\externaldocument{main}
+
 \usepackage{tikz-imagelabels} % for  tikz
@@
 \usepackage{xcolor}
+\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
 %\usepackage[table,xcdraw]{xcolor}
@@
 % from page (ok)
-The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 377 to line 392).
+% Please see page 3, line 23. begins on line 1, page 3, to line 2, page 4.
+The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 377 to 392).
+%and on page \pageref{from:answer1-2}, line?
+%\lr{to:answer1-2}. \lineref[1]{to:answer1-2}),
+% \lr{from:answer1-2}
+%(line 377 \ref{line_fr:answer1-2}) to page \pageref{page_to:answer1-2} (line 392 \ref{line_to:answer1-2}). 
+%\pagelabel{from:answer1-2} \linelabel{from:answer1-2L}
 Also, it is shown here in the following paragraph.
+% line \ref{line_fr:answer1-2} ~ \ref{line_to:answer1-2} of page %\pageref{page_fr:answer1-2}, \pageref{page_to:answer1-2}
+% in main.tex
+% %\label{page_fr:answer1-2}, \label{page_to:answer1-2}
+% \linelabel{line_fr:answer1-2} , \linelabel{line_to:answer1-2}
 
@@
 TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
-A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure ~\ref{fig:figure1}) and justified by the ranking of hazard ratios.
+A total of 9416 Kaplan-Meier plots (under sliding-window cutoff selection) with associated Cox's univariate and multivariate tables were generated by Cox modeling (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
 %The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, 
@@
 %em dash ---
-These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN---previous name as KIAA1683, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
+These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, EVPLL, PNMA5, IQCN, NPB, and CALML5) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
 %These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
@@
   \end{subfigure}
-  \caption{The 62 genes (listed on the right) have been discovered by LASSO regression in (a) TCGA HNSCC and (b) GSE65858 HNSCC cohort. \textcolor{red}{Red}-square marked genes are our 3 candidates.}
+  \caption{The 62 genes (listed on the right), discovered by LASSO regression, distribute in (a) TCGA HNSCC and (b) GSE65858 HNSCC cohorts.
+\textcolor{red}{Red}-square marked genes are our 3 candidates: CAMK2N1, CALML5, and FCGBP.}
   \label{fig:Bayes62}
@@
 Answer
+
 %(OK x3)
@@
 Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
-We made a new Figure 1 with clear direction of the workflow.
-A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
-In Figure 2, the ticks and labels on the x-axis were corrected.\\[0.5cm]
+We made a new "Figure 1" with clear direction of the workflow.
+And the "gene expression values (20500 genes)" replaced the "RNAseq" (it is shown here as Figure \ref{fig:figure1} on page \pageref{page21}).
+In "Figure 2", the ticks and labels on the x-axis were corrected (please also see Figure \ref{fig:figure2} on page \pageref{page22} in this file).\\[0.5cm]
+
+%%% new figure 1; fig:figure1
+
+%\subsubsection{Figure 1:h}
+\begin{figure}[hbt!]
+\centering
+%\widefigure
+\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
+%, height=8cm
+%\caption % , step 1 (\textcolor{blue}{blue line}: main procedure) and step 2 (\textcolor{orange}{orange line}: analysis export).
+%Step 3 (purple line: dealing with surgical margin).
+\bcaption{A workflow of \acrshort{hnscc} biomarker discovery}
+{The workflow includes data retrieval from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses (within \textcolor{yellow}{yellow} square).
+The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} values (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling.
+The candidate selection performs (1) dissecting and selection of candidate genes by further Bonferroni adjusted \textit{P} values as well as a hazard ratio of Cox model, based on the results from the survival analyses;
+(2) survival analyses of the other HNSCC dataset (GSE65858) using Kaplan-Meier estimate (with FDR correction) and Cox modeling.\\
+The biomarker candidates were a consensus result of TCGA and GSE65858. 
+%The selected genes were validated by third HNSCC cohort (GSE2837).\\
+(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
+\label{fig:figure1}
+% Description:1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
+
+\label{page21}
+\end{figure}
+
+%%% new figure 2; fig:figure2
+
+%\subsubsection{Figure 2:h}
+\begin{figure}[hbt!]
+\centering
+\includegraphics[width=14cm]{Figure2.pdf}
+\bcaption{The initial progress of candidate selection from TCGA \acrshort{hnscc} cohort.}{The \textit{P} values of Kaplan-Meier survival is one of the selection criteria.
+The effect size is estimated by Cox's hazard ratio.
+Initial trial step: (a) univariate HR versus \textit{P} value; (b) multivariate HR versus \textit{P} value.
+After stringent criteria by Bonferroni-adjusted \textit{P} value, and the Cox's HR, few top-ranked genes are shown in
+(c) univariate HR versus Bonferroni-adjusted \textit{P} value; and (d) multivariate HR versus Bonferroni-adjusted \textit{P} value.\\
+(TCGA: \acrlong{tcga}; HR: hazard ratio)}
+\label{fig:figure2}
+\label{page22}
+\end{figure}
 
@@
 
+%LOC148709
 \begin{outline} % highlight still blue
-In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (former name as KIAA1683), and NPB, are associated with the prognosis of OS in our study.
+In conclusion, 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, EVPLL, PNMA5, IQCN, NPB and CALML5, are associated with the prognosis of OS in our study.
 Comparison with previous publications or database analyses,

### 2021-07-04 Supplementary_figures.tex
Updates from Overleaf

@@
 \documentclass[jpm,supfile,submit,moreauthors,pdftex]{Definitions/mdpi}
-
+%supfile
 % major revision and answer question (3 reviewers)
 %Sunday, January 24⋅22:30 – 22:55
-%Daily, until Jan 29, 2021
+%Daily, until Jan 29, 2021 => JPM 2021/07/05
 
@@
 
-\begin{document}
 %%%%%%%%% title
@@
 %==================
-
+\begin{document}
 %\underline{Supplementary information}
@@
 \section{STables}
-\underline{Supplementary figure legends}\\[1cm]
+%\underline{Supplementary figure legends}\\[1cm]
 %ST1
@@
 %ST2
-Supplementary Table \ref{table:table3}\\
+Supplementary Table \ref{table:table1}: \\
+Overexpression of 10 genes with Cox's hazard ratio $> 1.5$.\\
+
+Supplementary Table \ref{table:table3}: \\
+Overexpression of 10 genes with Cox's hazard ratio $< 0.6$. \\
 
@@
 \hline
-CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & \checkmark                                          \\
+CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                &                                           \\ %\checkmark
 \hline
@@
 \hline
-PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & \checkmark                                          \\
+PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                &                                           \\ %\checkmark
 \hline
-SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & \checkmark                                           \\
+SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                &                                          \\ %\checkmark
 \hline
-USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & \checkmark                                         \\
+USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                &                                          \\ %\checkmark
 \hline
-NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & \checkmark                                           \\
+NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                &                                           \\ %\checkmark
 \hline
-FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & \checkmark                                          \\
+FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                &                                         \\ %\checkmark
 \hline
@@
 \arrayrulecolor{black}\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
+\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR > 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
 \hline
@@
 \hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{}%Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\
-\hline
+%\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                i                                                                                                                                                                                                                                                                                                                                             \\
+%\hline
 \end{tabularx}
-}
+} % resizebox end
 \arrayrulecolor{black}
@@
 \centering
-\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by corrected \textit{P} value) }
+\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
@@
 \cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\
+ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\num{8.6e-8}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\
 \cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\
+ZNF266                                         & zinc finger protein 266                                & \num{2.2e-7}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\
 \hline
-IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & \checkmark                                            \\
+IL19                                           & interleukin 19                                         & \num{3.7e-7}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           &                                             \\ %\checkmark
 \hline
-MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\
+MYO1H                                          & myosin 1H                                              & \num{3.8e-7}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\
 \hline
-FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &  \checkmark                                           \\
+FCGBP                                          & Fc fragment of IgG binding protein                     & \num{1.2e-6}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &                                             \\ %\checkmark
 \hline
-LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\
+%LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\
+%\hline
+EVPLL                                          & envoplakin-like protein                                & \num{2.0e-6}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\
 \hline
-EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\
+PNMA5                                          & paraneoplastic antigen like 5                          & \num{2.6e-6}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\
 \hline
-PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\
+IQCN                           & \num{3.1e-6}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &                                              \\ %\checkmark
 \hline
-KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &   \checkmark                                           \\
+NPB                                            & neuropeptide B                                         & \num{4.0e-6}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &                                              \\ %\checkmark
 \hline
-NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &      \checkmark                                        \\
+CALML5 &
+\acrlong{CALML5} &
+   \num{2.0e-4} & %\num{6.54e-6} & %3.7e-7} &
+   0.039 &
+   0.510 &
+   0.379-0.686 &
+   0.493 &
+   0.364-0.667 &  \\  % \checkmark \multicolumn{2}{l|} {
 \hline
-                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\
-\hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{}= 1.5\\
+\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{} 0.6\\
 %\hline
@@
 %\hline
-lncRNA: Long non-coding RNA\\%Remark: \checkmark Validated by GSE2837
+%lncRNA: Long non-coding RNA\\%Remark: \checkmark Validated by GSE2837
 ~\end{tabular}}                                                                                                                                                                                                                 \\
@@
 \section{SFigures}
-\underline{Supplementary figure legends}\\[1cm]
+%\underline{Supplementary figure legends}\\[1cm]
 %S1
-Supplementary figure \ref{fig:pvaluePlot_NDFIP1}\\
-The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see supplementary Figure S1).
+Supplementary figure \ref{fig:pvaluePlot_NDFIP1}:\\
+The gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.% (please see supplementary Figure S1).
 After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
@@
     \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
-    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
+    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: (1) 70\% of \textit{P} values is $<0.05$; (2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; (3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
     (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
@@
 %%%
-% MDPI internal command: Title for citation in the left column
-\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}
 

### 2021-07-04 main.tex
Updates from Overleaf

@@
 
+\usepackage{xr-hyper}
 \usepackage{hyperref}
-\usepackage{xr}
+%\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % for \label page and line
+\newcommand{\R}[1]{\linelabel{#1}} % for \label page and line
+%\newcommand{\lr}[1]{page~\pageref{#1} (line~\lineref{#1})} % for \ref page and line
 % for xr in your preamble
 % https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf
-\makeatletter
-\newcommand*{\addFileDependency}[1]{% argument=file name and extension
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
-\makeatother
-
-\newcommand*{\myexternaldocument}[1]{%
-    \externaldocument{#1}%
-    \addFileDependency{#1.tex}%
-    \addFileDependency{#1.aux}%
-}
+%\makeatletter
+%\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+%  \typeout{(#1)}
+%  \@addtofilelist{#1}
+%  \IfFileExists{#1}{}{\typeout{No file #1.}}
+%}
+%\makeatother
+
+%\newcommand*{\myexternaldocument}[1]{%
+%    \externaldocument{#1}%
+%    \addFileDependency{#1.tex}%
+%    \addFileDependency{#1.aux}%
+%}
 % my external document I would like to reference the labels of. 
-\myexternaldocument{Supplementary_figures} %.tex .aux
+%\myexternaldocument{Supplementary_figures} %.tex .aux
 
@@
 There are few clinicopathological features available on their pre-processed data sets.
-We developed a workflow that includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
+We applied a in-house workflow, which includes data retrieving and pre-processing, feature selection, sliding-window cutoff selection, Kaplan-Meier survival analysis, and Cox proportional hazard modeling, for biomarker discovery.
 Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes.
@@
 According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, CALML5, and FCGBP, are significantly associated with the patients' overall survival.
-The other independent HNSCC data were also used to validate this discovery.
-We suggest the transcriptomic analysis could help for biomarker discovery.}
+We validated this discovery by using the other independent HNSCC dataset (GSE65858).
+Thus, we suggest the transcriptomic analysis could help for biomarker discovery.}
 
@@
 %e.g., GSE30784: 167 HNSCC samples and 45 normal controls). 
-They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
-The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.
+They used the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
+The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate their potential function.
 %Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
@@
 The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
-The candidate genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
+The candidate genes were validated by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
 %, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
@@
 % GEPIA1/2 contact us: tangzefang@pku.edu.cn
-Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.\\
+Finally, these biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\
 \end{MyColorPar} % red
@@
 %em dash ---
-These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN---previous name as KIAA1683, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
+These CAMK2N1, CALML5, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, IL19, MYO1H, EVPLL, PNMA5, IQCN, and NPB) have significant FDR-adjusted \textit{P} values ($< 0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003) = -3.5$).
 %These genes have also passed a stringent criteria (Bonferroni \textit{P} value correction less than 0.05).
@@
 
+% in coverletter
+% line \ref{line_fr:answer1-2} ~ \ref{line_to:answer1-2} of page %\pageref{page_fr:answer1-2}, \pageref{page_to:answer1-2}
+% in main.tex
+% %\label{page_fr:answer1-2}, \label{page_to:answer1-2}
+% \linelabel{line_fr:answer1-2} , \linelabel{line_to:answer1-2}
 %****************%
 \subsubsection{Holistic Cancer Care} 
+\R{from:answer1-2}
+%\linelabel{line_fr:answer1-2}
 
@@
 \end{MyColorPar} % red
+
+\R{to:answer1-2}
+%\label{page_to:answer1-2} % page number
+%\linelabel{line_to:answer1-2} % line number
+% \label{line_to:answer1-2} % section number
 
@@
 The Cox model is also accounting for confounding factors\cite{Magen2019}.
-It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.g., death) at time t. It can be estimated as follow:
+It is expressed by the hazard function denoted by h(t). 
+The hazard function represents the risk of a specific event (e.g., death) at time t. It can be estimated as follow:
 
@@
 \1 t represents the survival time;
-\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g., clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status);
-\1 The coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates;
-\1 The term $h_0$ is called the baseline hazard.
-It corresponds to the hazard value if all the $X_i$ are equal to zero (the quantity exp(0) equals 1).
-The "t" in $h(t)$ indicates the hazard may vary over time.
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g., clinicopathological features, including age, gender, gene expression, cancer stage, smoking, alcohol, spiritual, emotional, and social status;
+\1 The coefficients ($\beta_1...\beta_n$) measure the impact---the effect size of covariates;
+\1 The term $h_0$ is called the baseline hazard. It corresponds to the hazard value if all the $X_i$ are equal to zero. The "t" in $h(t)$ indicates the hazard may vary over time.
 \end{outline}
@@
 GSE65858 is a dataset for candidate selection in our workflow.
-The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
+The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
 R package of GEOquery\cite{Sean2007} was used to

### 2021-07-04 Cover_letter_JPM.tex
Updates from Overleaf

@@
 \textcolor{blue}{In the Discussions section}\\
+% %\subsection{The Purpose of a Sliding-window Cutoff Selection}
 %[more in the discussion section]
-"  % (ok)
+  % (ok)
+"
+%%% Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff.
+%\subsection{The Purpose of a Sliding-window Cutoff Selection}
+% risk of *** Answer 2-3 併入此
+%Second, t
 Trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy could identify more but sometimes weak "biomarkers".
+%We have checked this issue in detail (in the Discussions section).
+%Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
 Thus, we should try our best to handle the effect size from Cox's modeling.
 And validation of those candidates is required by using other independent dataset.
-%%% Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff.
-%\subsection{The Purpose of a Sliding-window Cutoff Method}
+% in larger patient populations.% in larger patient
+%warrant.
+
 Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
@@
 In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
-However, the small effect size (non-zero) is often meaningless or substantive insignificance.
+However, the small effect size (non-zero) is often meaningless or substantive insignificance (e.g., hazard ratio between 0.8 and 1.2).
 %With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
@@
 We compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
-It shows that the number of genes with unadjusted \textit{P} value $< 0.05$, which is 6284 versus 3118, respectively. After FDR correction, it becomes 967 versus 209, respectively.
+It shows that the number of genes (with unadjusted \textit{P} value $< 0.05$)  is 6284 versus 3118, respectively. After FDR correction, it becomes 967 versus 209, respectively.
 % HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
@@
 To find a smaller \textit{P} value might predict large effect size (HR) associated biomarkers.
-Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
-
+Then, these preliminary candidates will have an opportunity to be carefully selected by using FDR then stringent Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
+% no more GSE2837
 %small effect size could be double-checked by GSE65858.
@@
 NDFIP1 has the FDR-adjusted \textit{P} value as \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "S"- or "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
+scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "S"- or "W"-shaped acute-bending on the \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
 %Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
@@
 However, it was excluded as a candidate by small effect size (HR = 1.33 in GSE65858) less than 1.8.
-%%%
-
-%compared with one (HR = 2.027) in TCGA cohort%.
-% (ok) Answer 2-1 加入 discussion
-%According to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).
-
-%Rplot_pvaluePlot_NDFIP1.pdf
-%  to find cases_OS outside of range 180-220 (== cutoff not at median)
-%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
-% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
-%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
-%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
-%# NDFIP1 (within our 20 preliminary candidates), 
-%In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
-%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
-%Indeed, it needs to be validated by the other independent cohort (e.x. GSE65858).
-
-% x****** IL19 必須要靠 pvalueTex 才能發現
+%%%  and HR = 1.42 in GSE2837
+
 The other example is IL19.
@@
 This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
-However, IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
+Even IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
 "

### 2021-07-04 main.tex
Updates from Overleaf

@@
 
-\usepackage{xr-hyper}
+%\usepackage{xr-hyper}
 \usepackage{hyperref}
 %\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % for \label page and line
-\newcommand{\R}[1]{\linelabel{#1}} % for \label page and line
+%\newcommand{\R}[1]{\linelabel{#1}} % for \label page and line
 %\newcommand{\lr}[1]{page~\pageref{#1} (line~\lineref{#1})} % for \ref page and line
@@
 The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
-The candidate genes were validated by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
+They validated their candidate genes by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
 %, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
-), GEPIA2021\cite{Li2021} (available at http://gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
+), GEPIA2021\cite{Li2021} (available at http://gepia2021.cancer-pku.cn/), and the web-tools: Human protein atlas (HPA)\cite{Uhlen2017} (please also see the Discussions section "Validation by Web-based Tools" in this article).
 % GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
 % GEPIA1/2 contact us: tangzefang@pku.edu.cn
-Finally, these biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\
+Finally, their biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\
 \end{MyColorPar} % red
@@
 There are several visualization software or R packages which deal with cutoff determination\cite{Abel1984}, %CRITLEVEL
-such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
+such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
 packages/cutoffR). 
@@
 In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial.
-Our approach describes a workflow implemented in the R script, which runs on the Rstudio server.
+Our approach describes an in-house workflow implemented in the R script, which runs on the Rstudio server.
 Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
-The independent HNSCC datasets were used to validate this strategy.
+The independent HNSCC dataset (GSE65858) was used to validate this strategy.
 The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.
@@
 To find a smaller \textit{P} value might predict large effect size (HR) associated biomarkers.
-Then, these preliminary candidates will have an opportunity to be carefully selected by using Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
+Then, these preliminary candidates will have an opportunity to be carefully selected by using FDR then stringent Bonferroni correction, their effect size (Cox's HR), and the other independent cohort (GSE65858) to prevent the false discovery.
 % no more GSE2837
@@
 This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
-However, IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
+Even IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
 
@@
 All transcriptomic data were retrieved from the TCGA, and all proteomics were generated in-house using the same antibodies.
-The genes (e.g.
-CAMK2N1, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/\\humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
-FCGBP is on the list of favorable prognostic genes as well.
+The our candidate, CAMK2N1, is also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/\\humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19).
+CALML5 and FCGBP are on the list of favorable prognostic genes as well.
 % DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
@@
 \subsubsection{Holistic Cancer Care} 
-\R{from:answer1-2}
+%\R{from:answer1-2}
 %\linelabel{line_fr:answer1-2}
@@
 
-\R{to:answer1-2}
+%\R{to:answer1-2}
 %\label{page_to:answer1-2} % page number
@@
 \1 t represents the survival time;
-\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g., clinicopathological features, including age, gender, gene expression, cancer stage, smoking, alcohol, spiritual, emotional, and social status;
+\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g., clinicopathological features, including age, gender, gene expression, cancer stage (tumor size, nodal metastasis, distant metastasis), surgical margin, smoking, and alcohol; unfortunately, spiritual, emotional, and social status are not available in TCGA database;
 \1 The coefficients ($\beta_1...\beta_n$) measure the impact---the effect size of covariates;
@@
 GSE65858 is a dataset for helping of candidate selection in our workflow.
-We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.
+We have also performed Kaplan-Meier (with FDR-correction of \textit{P} value) and Cox survival analyses under the cutoff of each gene expression at their median value.
 \end{MyColorPar} % red

### 2021-07-04 main.tex
Updates from Overleaf

@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves with a log-rank test, and univariate Cox regression to screen prognostic factors.
-The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
+Xu and his colleagues\cite{Xu2021a} also identified their biomarkers by analysis of differentially-expressed genes (DEGs).
+The gene expression was used to select the preliminary biomarkers.
+The significant impact on patients' overall survival was evaluated by Kaplan–Meier survival curves with a log-rank test (\textit{P} value $< 0.01$), and univariate Cox regression.
 %By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
 The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
-They validated their candidate genes by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
+They validated the candidate genes by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
 %, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
@@
 The independent HNSCC dataset (GSE65858) was used to validate this strategy.
-The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.
+The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate by gene-expression based survival analysis.
 

### 2021-07-05 Cover_letter_JPM.tex
final main.tex and main_redmared.tex

@@
 "
-The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
-R package of \\GEOquery\cite{Sean2007} was used to
-download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/\\geo2r/?\\acc=GSE65858). 
-GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
+GSE65858\cite{Wichmann2015} is a dataset for helping of candidate selection in our workflow.
+The Gene Expression Omnibus (GEO) database\cite{Chung2006}, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
+R package of GEOquery\cite{Sean2007} was used to
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
+GSE65858 has OS event, RFS event, and survival time.
 There are 270 HNSCC participants involved in this cohort.
@@
 %n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
-The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009).
+The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on 7 November, 2009).
 % (RefSeq)
-GSE65858 is a dataset for candidate selection in our workflow.
-We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
+We have performed Kaplan-Meier (with FDR-correction of \textit{P} value) and Cox survival analyses under the cutoff of each gene expression at their median value.
+The biomarker candidates were a consensus result of TCGA and GSE65858 analyses.\\
 "
@@
 
-First, although \acrshort{tcga} genomics data were harmonized, 
+First, since \acrshort{tcga} genomics data were harmonized, 
 % three things were found during our investigating and data cleaning:
@@
 These technical problems could not be detected prior to program running.
-It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity
+It might be due to skewed distribution of the expression value or even random error derived during the RNA sequencing procedure. % heterogeneity
 "

### 2021-07-05 main_redMarked.tex
final main.tex and main_redmared.tex

--- 2021-07-04 main.tex
@@
 \begin{outline}
-\1  To the best of our knowledge, the TCGA database is the largest collection (in both cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
-There are many physical and social features of patients available for survival modeling. % ($X_1 ... X_n$)
+\1  To the best of our knowledge, the TCGA database is the largest collection (in both cancer types and cohort size, especially in HNSCC) of comprehensive genomics with survival data available in the field of cancer research so far.
+%There are many physical and social features of patients available for survival modeling. % ($X_1 ... X_n$)
 The whole-genome sequencing data were harmonized across all \acrfull{gdac}s.
-Many databases adopt the essential demographic data from TCGA since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
-\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-based tools and API are ready to analyze and visualize TCGA data.
+Many databases adopt the essential demographic data from TCGA since it has comprehensive physical and social features of patients, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
+\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-based tools and \acrfull{api} are ready to analyze and visualize TCGA data.
 It might be getting help quickly from the research community for trouble-shooting.
-\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data were already published and keep growing\cite{Tomczak2015}.\\[0.1cm]
+\1  Many achievements of diagnoses, treatments, and prevention from the TCGA data were already published and keep growing\cite{Tomczak2015}.\\[0.1cm]
 \end{outline}
@@
 Usually, researchers developed an in-house workflow of gene expression analysis of TCGA data to find HNSCC biomarkers.
-They have several genes that are differentially expressed between tumor and normal samples.
-It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC
+%They have several genes that are differentially expressed---\acrfull{degs} between tumor and normal samples.
+It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC.
 % Rstudio\cite{Loraine2015a}
-Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
-Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.g., GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
+Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\\\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
+Gene expression data were downloaded from the TCGA or Gene Expression Omnibus (GEO) databases (e.g., GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
 % IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
 %e.g., GSE30784: 167 HNSCC samples and 45 normal controls). 
-They used the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
-The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate their potential function.
+They used the Database for Annotation, Visualization, and Integrated Discovery---DAVID (available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
+The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions of their biomarker candidates.
 %Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
-The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
-The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
-Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows on gene expression analyses of the TCGA.
+%The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
+The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, STRING (available at https://string-db.org), or Cytoscape software\cite{Huang2019}\cite{Shen2019}.
+Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows for gene expression analyses of the TCGA.
 %The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves with a log-rank test, and univariate Cox regression to screen prognostic factors.
-The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
+Xu and his colleagues\cite{Xu2021a} also identified their biomarkers by  \acrshort{degs} analysis.
+%The differential expression of gene was used to select the preliminary biomarkers.
+The significant impact of genes on patients' overall survival was evaluated by Kaplan–Meier survival curves with a log-rank test (\textit{P} value $< 0.01$), and univariate Cox regression.
 %By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
 The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
-They validated their candidate genes by using the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
+They validated the candidate genes by using the web-based Tools of Gene Expression Profiling Interactive Analysis tool---GEPIA and Human protein atlas (HPA) databases.
+GEPIA was developed, using TCGA datasets, by Zefang Tang and his colleagues (version 1\cite{Tang2017a}, version 2\cite{Tang2019}, and GEPIA2021\cite{Li2021}, available at http://gepia2021.cancer-pku.cn/).
 %, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
-), GEPIA2021\cite{Li2021} (available at http://gepia2021.cancer-pku.cn/), and the web-tools: Human protein atlas (HPA)\cite{Uhlen2017} (please also see the Discussions section "Validation by Web-based Tools" in this article).
+HPA\cite{Uhlen2017} applied \acrfull{ihc} for the TCGA database (please see details in the Discussions section "Validation by Web-based Tools").
 % GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
@@
 
+%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp
+% bioinformatics
 The other investigators should get the rationale or revelation of the genes of interest on a specific cancer type.
-They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
-SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), and analyze the cohort (e.g., \acrshort{tcga}).
+They should upload those genes manually onto web-based tools, such as SurvExpress\cite{Aguirre-Gamboa2013} (available at http://bioinformatica.mty.itesm.mx:8080/\\Biomatec/SurvivaX.jsp), then analyze the cohort of interest (e.g., \acrshort{tcga}).
 After downloading the survival results, they could curate plots and tables carefully.
@@
 There are several visualization software or R packages which deal with cutoff determination\cite{Abel1984}, %CRITLEVEL
-such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/
-packages/cutoffR). 
-However, non of them could perform jointly predictive of survival times and cutoff selection within subgroups of gene expression.
+such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/cutpointr), and cutoffR (available at https://cran.r-project.org/web/packages/cutoffR).
+However, non of them could perform jointly survival analysis with cutoff selection and whole-genome scanning.
 %  %combine the scanning of the protein-coding genes and cutoff optimization programmatically.
@@
 Our approach describes an in-house workflow implemented in the R script, which runs on the Rstudio server.
-Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff mining, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
-The independent HNSCC dataset (GSE65858) was used to validate this strategy.
-The workflow, shown in Figure \ref{fig:figure1}, scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate.
+Its function includes data retrieving and pre-processing, feature selection, sliding-window cutoff selection, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker discovery.
+The independent HNSCC dataset (GSE65858)\cite{Wichmann2015} was used to validate this strategy.
+The workflow, shown in Figure \ref{fig:figure1}, has scanned 20,500 human protein-coding genes of the \acrshort{tcga} \acrshort{hnscc} cohort to yield a model with biomarker estimate by gene-expression based survival analysis.
 
@@
 NDFIP1 has the FDR-adjusted \textit{P} value as \num[round-precision=3, round-mode=figures,
-scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "S"- or "W"-shaped acute-bending on the \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
+scientific-notation=true]{0.0001074233} (please see supplementary Figure S1, a "S"- or "W"-shaped acute-bending on the \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
 %Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
@@
 This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
-Even IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
+Even IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (small effect size as HR = 0.630, and FDR-KM \textit{P} = 0.031).
 
@@
 
-First, although \acrshort{tcga} genomics data were harmonized, 
+First, since \acrshort{tcga} genomic data were harmonized, 
 % three things were found during our investigating and data cleaning:
@@
 These technical problems could not be detected prior to program running.
-It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity
+It might be due to skewed distribution of the expression value or even random error derived during the RNA sequencing procedure. % heterogeneity
 
@@
 The high performance of C++ could speed up the critical steps in this workflow involving heavy computation of matrix data\cite{Woodward2020}.
-Moreover, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tool (named "pvalueTex" ) packaged with our workflow in the future.
+Moreover, it is possible to introduce the Rstudio Shiny app (https://shiny.rstudio.com) as a web-based tools (named "pvalueTex" ) packaged with our workflow in the future.
 
@@
 After establishing a therapeutic relationship (TR), the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease through their mind-brain-body axis.
-Thus, we suggest electric healthcare records (EHR) include physical, pathological, psychological data, and even more spiritual information.
-The \acrshort{tcga} should collect "holistic features" as well (\textcolor{green}{green} dashed line).}
+Thus, we suggest that electric healthcare records (EHR) should include physical, pathological, psychological data, and even more spiritual information.
+The \acrshort{tcga} might collect those "holistic features"  (\textcolor{green}{green} dashed line) for further study of personalized medicine.}
 \label{fig:figure5}
@@
 Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
-The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
-FirebrowseR)\cite{Deng2017}. 
+The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.
 We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, \textcolor{green}{green} square) to receive standardized data frames while avoiding data re-formatting, often causing some errors.
@@
 We utilized FirebrowseR's function call, Samples.mRNASeq(cohort = "HNSC", gene=GeneName, format="csv"), to download each \acrshort{rnaseq} data of all \acrshort{hnscc} patients and to save as 20,499 data frame files, named as "HNSCC.mRNA.Exp.[GeneName].Fire.Rda".
-After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered two distinct expression entities.
+After careful investigation of the genomics dataset, the \acrshort{rnaseq} values of "\acrfull{slca}" and "\acrfull{slcb}" should be considered as two distinct expression entities.
 We concluded that the number of protein-coding genes in the \acrshort{tcga} dataset is 20,500.
-We removed null expressed genes, which over 50\% of the cohort, to avoid the useless result.
+We removed null expressed genes, which over 30\% of the cohort, to avoid the useless result.
 
@@
 \begin{MyColorPar}{red}
-GSE65858 is a dataset for candidate selection in our workflow.
-The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
+GSE65858\cite{Wichmann2015} is a dataset for helping of candidate selection in our workflow.
+The Gene Expression Omnibus (GEO) database\cite{Chung2006}, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
 R package of GEOquery\cite{Sean2007} was used to
-download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
-GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/\\geo2r/?acc=GSE65858). 
+GSE65858 has OS event, RFS event, and survival time.
 There are 270 HNSCC participants involved in this cohort.
@@
 % (RefSeq)
-GSE65858 is a dataset for helping of candidate selection in our workflow.
-We have also performed Kaplan-Meier (with FDR-correction of \textit{P} value) and Cox survival analyses under the cutoff of each gene expression at their median value.
+We have performed Kaplan-Meier (with FDR-correction of \textit{P} value) and Cox survival analyses under the cutoff of each gene expression at their median value.
+The biomarker candidates were a consensus result of TCGA and GSE65858 analyses.
 \end{MyColorPar} % red
@@
 %% optional: The data presented in this study are available in supplementary material. Supplementary_figures.tex
-\supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}, 
-	Figure S1: \textit{P} value plot of the gene NDFIP1,
+\supplementary{The following are available online at \linksupplementary{Supplementary_figures.pdf}\\
+	Figure S1: \textit{P} value plot of the gene NDFIP1\\
 %	Figure S2: GSE2837 analysis by PrognoScan,  
 %	Table S1: The GSE2837 query results from PrognoScan,
-	Table S1: 10 bad guys, % ? don't keep it
-	Table S2: 10 good guys, % 要加入 CALML5
-	Video S1: title. A supporting video article is available at doi: link}
+	Table S1: 10 genes have unfavorable prognosis\\ % ? don't keep it
+	Table S2: 10 genes have favorable prognosis\\} % 要加入 CALML5
+%	Video S1: title. A supporting video article is available at doi: link}
 
@@
 %We also thank the statistical consultation and helps by Dr. Hsin-Chou Yang of the Institute of Statistical Science, Academia Sinica, Taipei, Taiwan.
-We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to \acrshort{tcga} affiliated biobanks.
+We sincerely want to express our thanks to the \acrshort{hnscc} patients who donated their data to University Hospital Leipzig (GSE65858) and \acrshort{tcga} affiliated biobanks.}
 % *** URL Accessed 20 May 2013.
-The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/mtbwi/index.do.  Accessed 20 May 2020.}
+%The Mouse Tumor Biology Database. http://tumor.informatics.jax.org/mtbwi/index.do.  Accessed 20 May 2020.}
 

### 2021-07-05 Cover_letter_JPM.tex
Updates from Overleaf

@@
 % Please see page 3, line 23. begins on line 1, page 3, to line 2, page 4.
-The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 377 to 392).
+The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 381) to page 14 (line 396).
 %and on page \pageref{from:answer1-2}, line?
@@
 % Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
-Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
+Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 6).%\ref{fig:figure5}).
 Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
@@
 Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
-The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
+The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 6).%\ref{fig:figure5}).
 "
@@
 %***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
-The paragraphs marked in \textcolor{red}{Red} from page 16 (line 502 to line 505) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
+The paragraphs marked in \textcolor{red}{Red} from page 17 (line 505 to line 508) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 % ok
-The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} on page 18 (line 560 to line 572),
+The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} on page 18 (line 567 to line 580),
 % results ok
-the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 148) to page 6 (line 172) , and
+the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 154) to page 6 (line 169) , and
 % ok
-the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 10 (line 236) to page 11 (line 280)
+the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 10 (line 233) to page 11 (line 284)
 are the part of the manuscript that has been revised. 
@@
 % ok
-The paragraphs marked in \textcolor{red}{Red} on page 17 (line 518 to line 544) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
+The paragraphs marked in \textcolor{red}{Red} on page 17 (line 521 to line 551) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
 \\[0.3cm]
@@
 "
-The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
-It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
+The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival data.
+It allows analyzing survival for one or more variables and to provides the effect size (coefficients, i.e., hazard ratios) for them\cite{Bradburn2003b}.
 % Classification trees and artificial neural networks in survival analysis
@@
 % ok
-The paragraphs marked in \textcolor{red}{Red} on page 11 (line 282 to line 310) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.
+The paragraphs marked in \textcolor{red}{Red} on page 11 (line 286) to page 12 (line 314) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.
 
@@
 According to the reviewer's comment, the Discussions was modified accordingly.
-The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised.
+The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line ?) are the part of the manuscript that has been revised.
 Also, it is shown here in the following paragraph.

### 2021-07-05 main.tex
Updates from Overleaf

--- 2021-07-04 main.tex
@@
 \begin{outline}
-\1  To the best of our knowledge, the TCGA database is the largest collection (in both cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far.
-There are many physical and social features of patients available for survival modeling. % ($X_1 ... X_n$)
+\1  To the best of our knowledge, the TCGA database is the largest collection (in both cancer types and cohort size, especially in HNSCC) of comprehensive genomics with survival data available in the field of cancer research so far.
+%There are many physical and social features of patients available for survival modeling. % ($X_1 ... X_n$)
 The whole-genome sequencing data were harmonized across all \acrfull{gdac}s.
-Many databases adopt the essential demographic data from TCGA since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
-\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-based tools and API are ready to analyze and visualize TCGA data.
+Many databases adopt the essential demographic data from TCGA since it has comprehensive physical and social features of patients, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
+\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-based tools and \acrfull{api} are ready to analyze and visualize TCGA data.
 It might be getting help quickly from the research community for trouble-shooting.
-\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data were already published and keep growing\cite{Tomczak2015}.\\[0.1cm]
+\1  Many achievements of diagnoses, treatments, and prevention from the TCGA data were already published and keep growing\cite{Tomczak2015}.\\[0.1cm]
 \end{outline}
 
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 %\subsubsection{From TCGA to expression biomarkers} % from Answer 2-6 minor2
 Usually, researchers developed an in-house workflow of gene expression analysis of TCGA data to find HNSCC biomarkers.
-They have several genes that are differentially expressed between tumor and normal samples.
-It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC
+%They have several genes that are differentially expressed---\acrfull{degs} between tumor and normal samples.
+It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC.
 % Rstudio\cite{Loraine2015a}
-Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
-Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.g., GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
+Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\\\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
+Gene expression data were downloaded from the TCGA or Gene Expression Omnibus (GEO) databases (e.g., GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
 % IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
 %e.g., GSE30784: 167 HNSCC samples and 45 normal controls). 
-They used the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
-The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate their potential function.
+They used the Database for Annotation, Visualization, and Integrated Discovery---DAVID (available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
+The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions of their biomarker candidates.
 %Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
-The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
-The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
-Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows on gene expression analyses of the TCGA.
+%The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
+The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, STRING (available at https://string-db.org), or Cytoscape software\cite{Huang2019}\cite{Shen2019}.
+Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows for gene expression analyses of the TCGA.
 %The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
@@
 Finally, their biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\
-\end{MyColorPar} % red
+%\end{MyColorPar} % red
 
@@
 
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 TCGA HNSCC cohort was applied for exploration of the biomarker candidate.
@@
 %Finally, these 3 candidates have also been confirmed by a HNSCC study using the GSE2837 dataset. Please see the Kaplan-Meier plots in Supplementary Figure S2.%\ref{fig:fig_GSE2837}.
-\end{MyColorPar} % end red
+%\end{MyColorPar} % end red
 
@@
 
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 
@@
 This optimal cutoff method could boost it's statistic significance to pass the correction by both FDR and Bonferroni methods.
-Even IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (HR = 0.630 and FDR-KM \textit{P} = 0.031).
-
-\end{MyColorPar} % red
+Even IL19 has competed as a candidate by its effect size (HR = 0.472 in TCGA cohort), but failed by the validation with GSE65858 cohort (small effect size as HR = 0.630, and FDR-KM \textit{P} = 0.031).
+
+%\end{MyColorPar} % red
 
@@
 \subsection{Technical Consideration}
-\begin{MyColorPar}{red} %%% ***
+%\begin{MyColorPar}{red} %%% ***
 There are two essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
 
-First, although \acrshort{tcga} genomics data were harmonized, 
+First, since \acrshort{tcga} genomic data were harmonized, 
 % three things were found during our investigating and data cleaning:
@@
 These technical problems could not be detected prior to program running.
-It might be due to skewed distribution of the expression value or even random error in 20500 RNA-Seq data. % heterogeneity
-
-\end{MyColorPar} %%% red
+It might be due to skewed distribution of the expression value or even random error derived during the RNA sequencing procedure. % heterogeneity
+
+%\end{MyColorPar} %%% red
 
@@
 
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
@@
 The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure \ref{fig:figure5}).
-\end{MyColorPar} % red
+%\end{MyColorPar} % red
 
@@
 In case there was no significant \textit{P} value, a median expression of this gene was set as its cutpoint as usual.
-\begin{MyColorPar}{red}
+%\begin{MyColorPar}{red}
 % (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
@@
 Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
-\end{MyColorPar} % red
+%\end{MyColorPar} % red
 
@@
 % reviewer comment; Answer 2-4 (Cox regression)
-\begin{MyColorPar}{red}
-%The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
-It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
+%\begin{MyColorPar}{red}
+The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival data.
+It allows analyzing survival for one or more variables and to provides the effect size (coefficients, i.e., hazard ratios) for them\cite{Bradburn2003b}.
 % Classification trees and artificial neural networks in survival analysis
@@
 All covariates have been pooled in the hazard function h(t) to estimate their impact on the overall survival.
-\end{MyColorPar} % red
+%\end{MyColorPar} % red
 %%
@@
 
-\begin{MyColorPar}{red}
-GSE65858 is a dataset for candidate selection in our workflow.
-The Gene Expression Omnibus (GEO) database\cite{Chung2006},, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
+%\begin{MyColorPar}{red}
+GSE65858\cite{Wichmann2015} is a dataset for helping of candidate selection in our workflow.
+The Gene Expression Omnibus (GEO) database\cite{Chung2006}, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data,  including microarray and sequence-based experiments.
 R package of GEOquery\cite{Sean2007} was used to
-download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
-GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
+download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/\\geo2r/?acc=GSE65858). 
+GSE65858 has OS event, RFS event, and survival time.
 There are 270 HNSCC participants involved in this cohort.
@@
 % (RefSeq)
-GSE65858 is a dataset for helping of candidate selection in our workflow.
-We have also performed Kaplan-Meier (with FDR-correction of \textit{P} value) and Cox survival analyses under the cutoff of each gene expression at their median value.
-\end{MyColorPar} % red
+We have performed Kaplan-Meier (with FDR-correction of \textit{P} value) and Cox survival analyses under the cutoff of each gene expression at their median value.
+The biomarker candidates were a consensus result of TCGA and GSE65858 analyses.
+%\end{MyColorPar} % red
 

### 2021-07-05 main_redMarked.tex
Updates from Overleaf

@@
 \begin{MyColorPar}{red}
-%The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data.
-It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}.
+The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival data.
+It allows analyzing survival for one or more variables and to provides the effect size (coefficients, i.e., hazard ratios) for them\cite{Bradburn2003b}.
 % Classification trees and artificial neural networks in survival analysis

### 2021-07-05 Cover_letter_JPM.tex
Updates from Overleaf

@@
 \section*{Cover letter for the re-submission (jpm-1174473)} 
-% 2021/04/25
+% 2021/04/25 to 2021/07/05
 % 直接 online 填寫即可
@@
 
-June 30, 2021
+July 05, 2021
 
@@
 %{% A SUMMARY
-Reviewer 1: % {2-4}
-%"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
-We re-wrote the Introduction in detail according to the suggestion by reviewer \#2.
-added new supplementary Figure S1, S2, and S3
-Reviewer 2: % {3-1}
+%=A summary modified/answers in cover letter (finish the first page) {
+We re-wrote the Introduction with the studies of TCGA database according to the suggestion by reviewer\#2.
+%[introduction] ok
+%Answer 2-6 minor2 (how to study TCGA)
+We introduced an independent HNSCC dataset (GSE65858) to provide more cases and evidence for supporting our biomarker candidates. The Results, Materials and Methods have included this information.
+%[results] ok Answer 2-3 (GSE65858 then final 3 candidates)
+We modified the Discussions about sample size, sliding window method, removal of "unclean data" statement according to the suggestion by reviewer\#2.
+%[discussions] ok
+%Answer 2-3 (sample size, effect size, pvalueTex cutoff of NDFIP1,  and P value)
+%purpose of sliding window (ok 提 一下at  2-6 minor3)
+%Answer 2-6 minor3 (In line 154 paragraph, what does "unclean data")
+And the 'holistic cancer care" was also modified according to the suggestion by reviewer\#1.
+%Answer 1-2 (holistic) figure 5
+We added the description of FDR correction and Cox modeling in the Materials and Methods according to the suggestion by reviewer\#2.
+%[materials and methods] ok
+%Answer 2-1 (cutoff finding), replaced a new Figure 5 %(Figure_4_CAMK2N1_IL19_FCGBP.pdf)
+%Answer 2-4 (Cox regression)
+%Answer 2-3 (GSE65858)
+%}
+We modified Figure 1 and 2 according to the suggestion by reviewer\#2.
+And new Figure 3, 4, 5 ,Table 1 and 2 was made for the updated results from GSE65858.
+We also added new supplementary Figure S1.
 %"Are the conclusions supported by the results?
-We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
+%We provide more evidence by additional analysis of TCGA and GEO databases. %Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
 %, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
 %to provide more evidence from the significant literature review.
-%}
+And all our responses to reviewers' comments are in the following pages.
 
@@
 %[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
-However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5": top 3 candidate biomarkers, CAMK2N1, CALML5, and FCGBP).
+However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5" for top 3 candidate biomarkers, CAMK2N1, CALML5, and FCGBP).
 Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in

### 2021-07-05 Cover_letter_JPM.tex
finished

@@
 
-Dear Ms. Sonia Sun:
+Dear Ms. Sonia Sun:\\[0.3cm]
 
@@
 
-We have since revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,
+We have since revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner.
 
@@
 %[results] ok Answer 2-3 (GSE65858 then final 3 candidates)
-We modified the Discussions about sample size, sliding window method, removal of "unclean data" statement according to the suggestion by reviewer\#2.
+We modified the Discussions about sample size, sliding window method, and removal of "unclean data" statement according to the suggestion by reviewer\#2.
 %[discussions] ok
@@
 We modified Figure 1 and 2 according to the suggestion by reviewer\#2.
-And new Figure 3, 4, 5 ,Table 1 and 2 was made for the updated results from GSE65858.
+And new Figure 3, 4, 5, Table 1 and 2 was made for the updated results from GSE65858.
 We also added new supplementary Figure S1.
@@
 We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine. 
-Thanks very much for the kind helps and the reviewers' critical comments.
-%\\[0.4cm]
-Kind regards,
-
-Yu-Chuan (Jack) Li, M.D., Ph.D.
-
+Thank you very much for the kind helps and the reviewers' critical comments.\\[0.3cm]
+
+Kind regards,\\[0.1cm]
+Yu-Chuan (Jack) Li, M.D., Ph.D.\\
 Graduate Institute of Biomedical Informatics, 

### 2021-07-05 Cover_letter_JPM.tex
Updates from Overleaf

@@
 
-\section*{Cover letter for the re-submission (jpm-1174473)} 
+%\section*{Cover letter for the re-submission (jpm-1174473)} 
 % 2021/04/25 to 2021/07/05
@@
 Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
-We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.
+We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We briefed this section (and Figure 6), then will submit rest of it in the other manuscript.
 
@@
 %[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
-However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5" for top 3 candidate biomarkers, CAMK2N1, CALML5, and FCGBP).
+Since we reviewed the results of sliding-window cutoff finding (from 50\% to 70\% quantile), the 20 preliminary candidates have FDR-corrected \textit{P} values from 1e-4 to 0.04 (or 0.001) (*** see a table?).
+The top 3 the 3 biomarker candidates, CAMK2N1, CALML5, and FCGBP, have FDR-corrected \textit{P} values from \num{1.63e-5} to \num{1.97e-4} (please see Figure \ref{fig:figure4}, 
+%which have been grouped by cutoffs between; 
+it is also shown in manuscript as updated "Figure 5").
 Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in
@@
 %Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
-Indeed, it needs to be validated by the other independent cohort.
+Indeed, it needs to determine its effect size (hazard ratio) then to be validated by the other independent cohort.
 

### 2021-07-06 Cover_letter_JPM.tex
Updates from Overleaf

@@
 % https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f
+
+\usepackage{array}
+\usepackage{ragged2e}
+\usepackage{rotating}
+\usepackage{tabularx} % for resizebox?
+\usepackage{makecell}
+% \usepackage{array}
+\usepackage{multirow}
+\usepackage{colortbl}
+\usepackage{hhline}
+\usepackage{siunitx} % for  1e-10 scientific notation
+%\usepackage{caption}
+%\usepackage{subcaption}
+\usepackage{booktabs, multirow} % for borders and merged ranges
+\usepackage{soul}% for underlines
+%\usepackage[table]{xcolor} % for cell colors
+\usepackage{changepage,threeparttable}
 
@@
 \usepackage{xcolor}
+
 \definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
@@
 
-We also think that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
+Since the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P} = 0.05),
 %http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
@@
 %[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
-Since we reviewed the results of sliding-window cutoff finding (from 50\% to 70\% quantile), the 20 preliminary candidates have FDR-corrected \textit{P} values from 1e-4 to 0.04 (or 0.001) (*** see a table?).
-The top 3 the 3 biomarker candidates, CAMK2N1, CALML5, and FCGBP, have FDR-corrected \textit{P} values from \num{1.63e-5} to \num{1.97e-4} (please see Figure \ref{fig:figure4}, 
+we reviewed the results of cutoffs from 50\% to 70\% quantile to find the evidence.
+%> View(hazards[hazards$Gene.Symbol %in% c(gene_labeled_silver, gene_labeled_golden), c("Gene.Symbol","FDR.Pvalue")])
+A total of 20 preliminary candidates have FDR-corrected \textit{P} values from \num{3.78e-6} to \num{3.03e-4} (please see Table \ref{table:table1} and \ref{table:table3}; also shown in supplementary Table S1, S2).
+The top 3 biomarker candidates, CAMK2N1, CALML5, and FCGBP, have FDR-corrected \textit{P} values from \num{1.63e-5} to \num{1.97e-4} (please see Figure \ref{fig:figure4}, 
 %which have been grouped by cutoffs between; 
 it is also shown in manuscript as updated "Figure 5").
-Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in
-supplementary figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
+Moreover, the gene NDFIP1, one of the 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff.
+NDFIP1 also has a \textit{P} value of \num{2.62e-6} when cut at 70\% quantile  (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
+supplementary figure S1). 
+After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
 scientific-notation=true]{0.0001074233}.
@@
 %# NDFIP1 (within our 20 preliminary candidates), 
-In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
+In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
 %Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
 Indeed, it needs to determine its effect size (hazard ratio) then to be validated by the other independent cohort.
+
+%%% supplementary tables
+%Supplementary Table \ref{table:table1}: \\
+%Overexpression of 10 genes with Cox's hazard ratio $> 1.5$.\\
+
+%Supplementary Table \ref{table:table3}: \\
+%Overexpression of 10 genes with Cox's hazard ratio $< 0.6$. \\
+
+% tables below %%%%
+% table1
+\begin{table}[ht]
+%\begin{sidewaystable}[hp]
+%\centering
+\raggedright
+\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{0.6\linewidth}{!}{%
+%\begin{tabular}{|l|l|l|l|l|l|l|l|c|}
+\begin{tabularx}{\textwidth}{|l|p{6.0cm}|l|l|l|l|l|l|} % *** capital X or p{2cm}
+% p{2cm}
+\cline{1-8}
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate} \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\ \textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI   \\\cline{1-8}
+DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{3.8e-6}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924     \\                          % &                                           \\
+\cline{1-8}
+CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{1.5e-5}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704  \\                            % &                                           \\ %\checkmark
+\cline{1-8}
+STC2                                           & stanniocalcin 2                                            & \num{1.5e-5}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                             \\%   &                                           \\
+\cline{1-8}
+PGK1                                           & phosphoglycerate kinase 1                                  & \num{2.4e-5}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                              \\%    &                                           \\ %\checkmark
+\cline{1-8}
+SURF4                                          & surfeit 4                                                  & \num{6.2e-5}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                               \\%   &                                          \\ %\checkmark
+\cline{1-8}
+USP10                                          & ubiquitin specific peptidase 10                            & \num{7.9e-5}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                              \\%    &                                          \\ %\checkmark
+\cline{1-8}
+NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{1.1e-4}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                               \\%   &                                           \\ %\checkmark
+\cline{1-8}
+FOXA2                                          & forkhead box A2                                            & \num{1.6e-4}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                               \\%   &                                         \\ %\checkmark
+\cline{1-8}
+STIP1                                          & stress-induced-phosphoprotein 1                            & \num{1.8e-4}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                               \\%   &                                           \\
+\cline{1-8}
+DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{2.8e-4}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                               \\%   &                                          \\
+\cline{1-8}
+%\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
+%\arrayrulecolor{black}\hline
+
+\multicolumn{8}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate $HR > 1.5$~\\~(* Cox's model: \textit{P} $< 0.001$)\\ \end{tabular}}   \\
+%\cline{1-8}
+%\multicolumn{8}{|l|}{Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate $HR > 1.5$~\\~* Cox's model: \textit{P} $< 0.001$}   \\ 
+\cline{1-8}
+%\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                i                                                                                                                                                                                                                                                                                                                                             \\
+%\hline
+\end{tabularx}%
+} % resizebox end
+\arrayrulecolor{black}
+\label{table:table1}
+
+%\end{sidewaystable}
+\end{table}
+
+%%%
+%Table2. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
+\begin{table}[ht]
+\centering
+\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }
+\arrayrulecolor[rgb]{0.255,0.255,0.255}
+\resizebox{\linewidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|l|l|l|} 
+\cline{1-8}
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                    \\%   & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}    \\%   & \multicolumn{1}{l|}{}                         \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}%\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\num{4.7e-6}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669}                                              \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}%\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF266                                         & zinc finger protein 266                                & \num{5.2e-6}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                                                                       \\
+\hline
+IL19                                           & interleukin 19                                         & \num{6.5e-6}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                          \\%   &                                             \\ %\checkmark
+\hline
+MYO1H                                          & myosin 1H                                              & \num{1.4e-5}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                          \\%   &                                              \\
+\hline
+FCGBP                                          & Fc fragment of IgG binding protein                     & \num{4.8e-5}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                        \\%     &                                             \\ %\checkmark
+\hline
+%LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\
+%\hline
+EVPLL                                          & envoplakin-like protein                                & \num{7.5e-5}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                            \\% &                                              \\
+\hline
+PNMA5                                          & paraneoplastic antigen like 5                          & \num{3.0e-4}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                            \\% &                                              \\
+\hline
+IQCN            & IQ motif containing N               & \num{1.5e-4}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                  \\%                           &                                              \\ %\checkmark
+\hline
+NPB                                            & neuropeptide B                                         & \num{2.6e-4}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                            \\% &                                              \\ %\checkmark
+\hline
+CALML5 &
+\acrlong{CALML5} &
+   \num{2.0e-4} & %\num{6.54e-6} & %3.7e-7} &
+   0.039 &
+   0.510 &
+   0.379-0.686 &
+   0.493 &
+   0.364-0.667  \\%  &  \\  % \checkmark \multicolumn{2}{l|} {
+\hline
+\multicolumn{8}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{} 0.6\\
+%\hline
+%\multicolumn{9}{|l!{\color{black}\vrule}}{
+(* Cox's model: \textit{P} $< 0.001$) \\
+%}                                                                              
+%lncRNA: Long non-coding RNA\\%Remark: \checkmark Validated by GSE2837
+\end{tabular}}                                                                   \\ \hline
+\end{tabular}
+}
+\arrayrulecolor{black}
+\label{table:table3}
+\end{table}
+
+\clearpage
+
+%%%%
 

### 2021-07-06 Supplementary_figures.tex
Updates from Overleaf

@@
 \usepackage{xcolor}
+\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
+
 %\usepackage[table,xcdraw]{xcolor}
@@
 
-\section{STables}
+%\section{STables}
 %\underline{Supplementary figure legends}\\[1cm]
@@
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{\linewidth}{!}{
+\resizebox{\linewidth}{!}{%
 %\begin{tabular}{|l|l|l|l|l|l|l|l|c|}
-\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|c|} % *** capital X or p{2cm}
+\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|} % *** capital X or p{2cm}
 % p{2cm}
-\hline
-\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\
+\cline{1-8}
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate} \\
 \cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\\textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\
-\hline
-DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                &                                           \\
-\hline
-CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                &                                           \\ %\checkmark
-\hline
-STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                &                                           \\
-\hline
-PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                &                                           \\ %\checkmark
-\hline
-SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                &                                          \\ %\checkmark
-\hline
-USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                &                                          \\ %\checkmark
-\hline
-NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                &                                           \\ %\checkmark
-\hline
-FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                &                                         \\ %\checkmark
-\hline
-STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                &                                           \\
-\hline
-DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                &                                           \\
-\hline
-\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
-\arrayrulecolor{black}\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR > 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\
-\hline
-\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: \textit{P} $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\
-\hline
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\ \textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI   \\\cline{1-8}
+DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{3.8e-6}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924     \\                          % &                                           \\
+\cline{1-8}
+CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{1.5e-5}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704  \\                            % &                                           \\ %\checkmark
+\cline{1-8}
+STC2                                           & stanniocalcin 2                                            & \num{1.5e-5}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                             \\%   &                                           \\
+\cline{1-8}
+PGK1                                           & phosphoglycerate kinase 1                                  & \num{2.4e-5}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                              \\%    &                                           \\ %\checkmark
+\cline{1-8}
+SURF4                                          & surfeit 4                                                  & \num{6.2e-5}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                               \\%   &                                          \\ %\checkmark
+\cline{1-8}
+USP10                                          & ubiquitin specific peptidase 10                            & \num{7.9e-5}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                              \\%    &                                          \\ %\checkmark
+\cline{1-8}
+NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{1.1e-4}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                               \\%   &                                           \\ %\checkmark
+\cline{1-8}
+FOXA2                                          & forkhead box A2                                            & \num{1.6e-4}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                               \\%   &                                         \\ %\checkmark
+\cline{1-8}
+STIP1                                          & stress-induced-phosphoprotein 1                            & \num{1.8e-4}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                               \\%   &                                           \\
+\cline{1-8}
+DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{2.8e-4}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                               \\%   &                                          \\
+\cline{1-8}
+%\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\
+%\arrayrulecolor{black}\hline
+
+\multicolumn{8}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate $HR > 1.5$~\\~(* Cox's model: \textit{P} $< 0.001$)\\ \end{tabular}}   \\
+%\cline{1-8}
+%\multicolumn{8}{|l|}{Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate $HR > 1.5$~\\~* Cox's model: \textit{P} $< 0.001$}   \\ 
+\cline{1-8}
 %\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                i                                                                                                                                                                                                                                                                                                                                             \\
 %\hline
-\end{tabularx}
+\end{tabularx}%
 } % resizebox end
@@
 \resizebox{\linewidth}{!}{%
-\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
+\begin{tabular}{|l|l|l|l|l|l|l|l|} 
+\cline{1-8}
+\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                    \\%   & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
+\cline{3-8}
+\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}    \\%   & \multicolumn{1}{l|}{}                         \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}%\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\num{4.7e-6}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669}                                              \\
+\cline{1-2}\arrayrulecolor{black}\cline{3-8}%\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
+ZNF266                                         & zinc finger protein 266                                & \num{5.2e-6}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                                                                       \\
 \hline
-\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\
-\cline{3-8}
-\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\
-\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\num{8.6e-8}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\
-\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
-ZNF266                                         & zinc finger protein 266                                & \num{2.2e-7}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\
+IL19                                           & interleukin 19                                         & \num{6.5e-6}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                          \\%   &                                             \\ %\checkmark
 \hline
-IL19                                           & interleukin 19                                         & \num{3.7e-7}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           &                                             \\ %\checkmark
+MYO1H                                          & myosin 1H                                              & \num{1.4e-5}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                          \\%   &                                              \\
 \hline
-MYO1H                                          & myosin 1H                                              & \num{3.8e-7}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\
-\hline
-FCGBP                                          & Fc fragment of IgG binding protein                     & \num{1.2e-6}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &                                             \\ %\checkmark
+FCGBP                                          & Fc fragment of IgG binding protein                     & \num{4.8e-5}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                        \\%     &                                             \\ %\checkmark
 \hline
@@
 %\hline
-EVPLL                                          & envoplakin-like protein                                & \num{2.0e-6}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\
+EVPLL                                          & envoplakin-like protein                                & \num{7.5e-5}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                            \\% &                                              \\
 \hline
-PNMA5                                          & paraneoplastic antigen like 5                          & \num{2.6e-6}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\
+PNMA5                                          & paraneoplastic antigen like 5                          & \num{3.0e-4}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                            \\% &                                              \\
 \hline
-IQCN                           & \num{3.1e-6}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &                                              \\ %\checkmark
+IQCN            & IQ motif containing N               & \num{1.5e-4}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                  \\%                           &                                              \\ %\checkmark
 \hline
-NPB                                            & neuropeptide B                                         & \num{4.0e-6}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &                                              \\ %\checkmark
+NPB                                            & neuropeptide B                                         & \num{2.6e-4}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                            \\% &                                              \\ %\checkmark
 \hline
@@
    0.493 &
-   0.364-0.667 &  \\  % \checkmark \multicolumn{2}{l|} {
+   0.364-0.667  \\%  &  \\  % \checkmark \multicolumn{2}{l|} {
 \hline
-\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{} 0.6\\
+\multicolumn{8}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textless{} 0.6\\
 %\hline
 %\multicolumn{9}{|l!{\color{black}\vrule}}{
-* Cox's model: \textit{P} $< 0.001$ \\
-%}                                                                                                                                                                                                                                                                                                                                                                                                  \\
-%\hline
+(* Cox's model: \textit{P} $< 0.001$) \\
+%}                                                                              
 %lncRNA: Long non-coding RNA\\%Remark: \checkmark Validated by GSE2837
-~\end{tabular}}                                                                                                                                                                                                                 \\
-\hline
+\end{tabular}}                                                                   \\ \hline
 \end{tabular}
@@
 
-\section{SFigures}
+%\section{SFigures}
 %\underline{Supplementary figure legends}\\[1cm]

### 2021-07-06 Cover_letter_JPM.tex
Updates from Overleaf

@@
 %(OK)
+
 We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.
@@
 %(OK)
+
 After morning meditation in a wonderful day of February 2021,, the first author (Dr.
@@
 %# NDFIP1 (within our 20 preliminary candidates), 
-In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
+In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more candidates (\textit{P} values far less than $0.0003$) for further Cox's modeling.
 %Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
@@
 \arrayrulecolor[rgb]{0.255,0.255,0.255}
-\resizebox{0.6\linewidth}{!}{%
+\resizebox{0.65\linewidth}{!}{%
 %\begin{tabular}{|l|l|l|l|l|l|l|l|c|}
-\begin{tabularx}{\textwidth}{|l|p{6.0cm}|l|l|l|l|l|l|} % *** capital X or p{2cm}
+\begin{tabularx}{\textwidth}{|l|p{6.5cm}|l|l|l|l|l|l|} % *** capital X or p{2cm}
 % p{2cm}
@@
 
-\clearpage
+%\clearpage
 
@@
     \includegraphics[width=10cm]{Rplot_pvaluePlot_NDFIP1.pdf}
-    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: 1) 70\% of \textit{P} values is $<0.05$; 2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; 3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>=0.05$.\\
+    \caption{Under cutoff-finding procedure of Kaplan-Meier analysis, the \textit{P}-value plot of gene "NDFIP1" shows: (1) 70\% of \textit{P} values is $< 0.05$; (2) the median-cut zone (zoom-in and revealed in inset box) has a "W"-like distribution; (3) sliding-window cutoff selection could find it's optimized \textit{P} values (far less than 0.001) while a median cut might yield \textit{P} value $>= 0.05$.\\
     (x-axis: grouping by person number; y-axis: \textit{P} value in log10 transformed)}
@@
 %(OK)
+
 We appreciate the reviewer for the critical comment.
@@
 %}
-in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
+in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($< \num{3.0e-4}$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
 %
@@
 and also see Figure \ref{fig:hazards534}).
-However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
-There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the biomarker.
+However, the other 17 genes (discovered in TCGA) are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
+Thus, there is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, CALML5, and FCGBP are significant candidates for the biomarker.
 %In the consensus of TCGA and GSE65858 cohorts,
@@
 % results ok
-the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 154) to page 6 (line 169) , and
+the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 147) to page 6 (line 169) , and
 % ok
@@
 %The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, 
-The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
-In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure 2(c), (d)).
+The 967 out of 9416 genes were kept by criteria of \acrshort{fdr}-adjusted Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
+In the next step, a stringent Bonferroni P-value correction was used to yield 20 genes (please see Figure 2(c), (d)).
+%, under the stringent criteria 
 %em dash ---
@@
 We appreciate the reviewer for the critical comments.
-Since we have tried to integrate multiple genes in survival analysis, a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
+We tried to integrate multiple genes in survival analysis, using a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
 Searching about the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression.
@@
 %Least Absolute Shrinkage and Selection Operation (LASSO):
-Branders and his colleagues\cite{Branders2014} have suggested that regularization of regression model should be applied on analysis of the high-dimensional data, i.e.
-twenty thousands of features (genes) and only hundreds of sample size.
+Branders and his colleagues\cite{Branders2014} suggested that regularization of regression model should be applied on analysis of the high-dimensional data, e.g., twenty thousands of features (genes) and only hundreds of sample size.
 The $L_{1}$-regularized path algorithm by Least Absolute Shrinkage and Selection Operation (LASSO) regression could perform feature selection (a subset of gene).
@@
 Beside feature selection,
-it is also necessary to add that small amount of bias (lambda, $\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
+it is also necessary to add that small amount of bias---lambda ($\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
 $\lambda$ could control the amount of bias dealing with over-fitting.
 %(over-fitting is called high-variance)
-In such a case, over-fitted model will only perfectly match every individual cases, and has higher variability to predict what it never see.
+In such a case, over-fitted model will only perfectly match every single case, and has higher variability to predict what it never see.
 Over-fitting will limit usefulness of the model in it's generalization, and could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
@@
 %RLassoCox\\
-We have utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) for training the Cox proportional hazard regression and logistic regression models in gene expression analysis to identify a group of genes that contribute to survival outcome of HNSCC patient.
+We utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) to find the gene signature.
+%for training both Cox proportional hazard regression and logistic regression models to identify a group of genes that contribute to survival outcome of HNSCC patient. 
 % RLassoCox includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
@@
 %The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
-The RLassoCox make use of both Cox and LASSO logistic regression for gene-expression based survival analysis.
+The RLassoCox makes use of both Cox and LASSO logistic regression for gene-expression based survival analysis of HNSCC.
 The model training has been performed under 10-fold cross-validation.
@@
 %cv.mod.candidate has 62 genes 
-The results shows the selected features (62 genes) distributing on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}).
+The results shows that the model-selected features (62 genes) distribute within the region of small effect size (HR) on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}), if see them individually.
 
@@
 %cv.mod$glmnetRes$lambda.1se
-We have further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
+We further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
 According to their \textit{P} values (please see Table \ref{tab:signature4}), 
 we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
-DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1 in volcano plot of TCGA HNSCC.
+DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1.0 on the volcano plot of TCGA HNSCC.
 
@@
 \centering
-\caption{The most LASSO regularized logistic model under cross-validation. Genes with positive coefficient will increase the patient's risk, while negative reduce it.\\
+\caption{The most LASSO regularized logistic model (under cross-validation error within 1 standard deviation of the minimum).
+Genes with positive coefficient will increase the patient's risk, while negative reduce it.\\
     (\textcolor{red}{red}-marked logistic \textit{P} value $< 0.05$)}
 \label{tab:signature4}
+
+\resizebox{0.4\linewidth}{!}{%
 \begin{tabular}{lrr}
@@
 \end{tabular}
+
+} % end resizebox
 \end{table}
@@
 
-In conclusion, we might build a Lasso regression model with LASSO regularization to maximize the use of continuous gene expression values (without the need of a cutoff).
+In conclusion, we might build a logistic regression model with LASSO $L_{1}$-regularization to maximize the use of continuous gene expression values (without cutoff).
 The gene signature integrating multiple genes is also a good approach for biomarker discovery.

### 2021-07-06 main.tex
Updates from Overleaf

@@
 \usepackage{rotating}
-\usepackage{tabularx}
+\usepackage{tabularx} % for resizebox?
 \usepackage{makecell}
@@
 %By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
-The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure \ref{fig:figure2}(a), (b), initial trial).
-In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
+The 967 out of 9416 genes were kept by criteria of \acrshort{fdr}-adjusted Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
+In the next step, a stringent Bonferroni P-value correction was used to yield 20 genes (please see Figure \ref{fig:figure2}(c), (d)).
+%, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
 

### 2021-07-06 main_redMarked.tex
Updates from Overleaf

@@
 %By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots).
-The 967 out of 9416 genes were kept by criteria of Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure \ref{fig:figure2}(a), (b), initial trial).
-In the next step, a Bonferroni P-value correction was used to yield 20 genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)).
+The 967 out of 9416 genes were kept by criteria of \acrshort{fdr}-adjusted Kaplan-Meier \textit{P} value ($< 0.05$) and \acrfull{hr} derived from Cox's model (please see Figure 2(a), (b), initial trial).
+In the next step, a stringent Bonferroni P-value correction was used to yield 20 genes (please see Figure \ref{fig:figure2}(c), (d)).
 

### 2021-07-06 Cover_letter_JPM.tex
submission

@@
 \newacronym{degs}{DEGs}{differentially expressed genes}
-
+\newacronym{ihc}{IHC}{immunohistochemistry}
 \newacronym{fdr}{FDR}{false discovery rate}
@@
 
-July 05, 2021
+July 06, 2021
 
@@
 We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine.
+We are updating very much from this major revision.
 Thank you very much for the kind helps and the reviewers' critical comments.\\[0.3cm]
@@
 
-After morning meditation in a wonderful day of February 2021,, the first author (Dr.
+After morning meditation in a wonderful day of February 2021, the first author (Dr.
 Chi) has raised this idea then wrote it in discussion section with comprehensive references.
 Dr.
-Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
-We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We briefed this section (and Figure 6), then will submit rest of it in the other manuscript.
+Chi wants to express that "stress should also be a kind of biomarker, which includes into the HNSCC study in the future".
+We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care.
+We briefed this section (and Figure 6), then will submit rest of it in the other manuscript (study of electronic health record in survival analysis).
 
@@
 %cv.mod.candidate has 62 genes
-The results shows that the model-selected features (62 genes) distribute within the region of small effect size (HR) on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}), if see them individually.
+% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
+LASSO calculate the (non-zero) coefficients of features to hit the minimum of cross-validation error.
+The results shows that the model-selected features (62 genes) distribute within the region of small effect size (HR from 0.6 to 1.7) on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}), if see them individually.
 
@@
 %The final gene signature has been selected, including 4 genes, named HK1, EZR, RRAGA, and DUSP16 .; fentastic4
-% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
-LASSO calculate the (non-zero) coefficients of features, while the 62 genes hit the minimum of cross-validation error.
 % in lambda 1se
@@
 According to their \textit{P} values (please see Table \ref{tab:signature4}), 
-we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
+we found a gene signature, HK1, EZR, RRAGA, and DUSP16, which will has survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
 DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1.0 on the volcano plot of TCGA HNSCC.
@@
 %# "EZR" has \textit{P} value $>0.05$
-  \caption{(a) Overall survival in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) Those genes (listed on the right side) have not significant hazard ratio (HR) if calculated individually (EZR is not shown on volcano plot due to it's Kaplan-Meier \textit{P} value $>0.05$)}
+  \caption{The LASSO-Cox regression model predict a set of gene signature.
+(a) Overall survival in TCGA HNSCC for the gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) HK1, RRAGA, and DUSP16 have small effect size---hazard ratio within 0.6-1.7, if calculated individually.
+And EZR has Kaplan-Meier \textit{P} value $>0.05$.
+(\textcolor{red}{Red}-squared genes are the biomarker candidates found by sliding-window cutoff survival analysis)}
     \label{fig:signature4}
 \end{figure}
+%(listed on the right side)
 
@@
 Usually, researchers developed an in-house workflow of gene expression analysis of TCGA data to find HNSCC biomarkers.
-%Workflow of GDCRNATool
-% reference https://www.biostars.org/p/153013/
-%Tutorial: Survival analysis of TCGA patients
-%integrating gene expression (RNASeq) data.
-%Why would you want to do survival analysis based on gene expression data? Well, let's say you
-% **** DEGs is a different concept with cutoff finding survival analysis of individual gene expression
-They have several genes that are differentially expressed between tumor and normal samples.
+%They have several genes that are differentially expressed---\acrfull{degs} between tumor and normal samples.
 It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC.
-%%% https://www.biostars.org/p/153013/
-%% download data with offline analysis
-%Usually, investigators could download the TCGA data in order to analyze and find expression biomarkers.
-% https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
-% from Mary Goldman and Jing Zhu, UCSC Cancer Browser
-% https://genome-cancer.ucsc.edu/
-%Here are the summarized techniques currently used: from 2000 to 2017\cite{Tonella2017a}
-%Gene expression profiling is applied for HNSCC to help in early diagnosis, prediction of recurrence or metastasis, prediction of prognosis or response to some therapies.
 % Rstudio\cite{Loraine2015a}
-Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
-Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.x. GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
+Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\\\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
+Gene expression data were downloaded from the TCGA or Gene Expression Omnibus (GEO) databases (e.g., GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).
 % IRB: Patient samples were obtained under the protocol S-206/2011, approved by the Ethics Committee of Heidelberg University, with written informed consent from all participants.
-%e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
-They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
-The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.
+%e.g., GSE30784: 167 HNSCC samples and 45 normal controls). 
+They used the Database for Annotation, Visualization, and Integrated Discovery---DAVID (available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function.
+The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions of their biomarker candidates.
 %Subsequently, comprehensive bioinformatics analysis incorporating gene ontology (GO), Kyoto Encyclopedia of Genes and Genomes (KEGG),
-The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
-The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, String, or Cytoscape software programs\cite{Huang2019}\cite{Shen2019}.
-Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows on gene expression analyses of the TCGA.
+%The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).
+The pathway enrichment analysis of \acrshort{degs} was also performed by DAVID, STRING (available at https://string-db.org), or Cytoscape software\cite{Huang2019}\cite{Shen2019}.
+Li\cite{Li2018a} and his colleagues made an R package (GDCRNATool) for the implementation of those workflows for gene expression analyses of the TCGA.
 %The DEmRNAs were enrolled in a protein-protein interaction (PPI) network through the STRING database (https://string-db.org/) with a confidence score $> 0.9$, and the PPI network was visualized in Cytoscape (Version 3.7.1) software.
@@
 %Then, Kaplan–Meier survival curves along with a log-rank test were applied to select candidates\cite{Xu2021a}.
-Xu and his colleagues\cite{Xu2021a} also used Kaplan–Meier survival curves with a log-rank test, and univariate Cox regression to screen prognostic factors.
-The gene expression was used to select the preliminary biomarkers with a significant impact on patients' overall survival (\textit{P} value $< 0.01$).
+Xu and his colleagues\cite{Xu2021a} also identified their biomarkers by  \acrshort{degs} analysis.
+%The differential expression of gene was used to select the preliminary biomarkers.
+The significant impact of genes on patients' overall survival was evaluated by Kaplan–Meier survival curves with a log-rank test (\textit{P} value $< 0.01$), and univariate Cox regression.
 %By integrated bioinformatics analysis, including protein_protein interaction (PPI) network, Gene Ontology (GO) enrichment, and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analyses.
 The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
-The candidate genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}
+They validated the candidate genes by using the web-based tools of Gene Expression Profiling Interactive Analysis tool---GEPIA and Human protein atlas (HPA) databases.
+GEPIA was developed, using TCGA datasets, by Zefang Tang and his colleagues (version 1\cite{Tang2017a}, version 2\cite{Tang2019}, and GEPIA2021\cite{Li2021}, available at http://gepia2021.cancer-pku.cn/).
 %, datasets from projects of the TCGA and the Genotype-Tissue Expression, GTEx
-), GEPIA2021\cite{Li2021} (available at http://\\gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.
+HPA\cite{Uhlen2017} applied \acrfull{ihc} for the TCGA database (please see details in the Discussions section "Validation by Web-based Tools").
 % GTEx https://gtexportal.org/home/; non-disease 54 tissues/organs
 % GEPIA1/2 contact us: tangzefang@pku.edu.cn
-Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.
+Finally, their biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\
 "
@@
 % 不要誇大說明 謙虛道歉
-We apologize for exaggerating the difficulties of our workflow.
+We apologize for exaggerating the difficulties in our work.
 % ok
-The paragraphs marked in \textcolor{red}{Red} on page 11 (line 286) to page 12 (line 314) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.
+The paragraphs marked in \textcolor{red}{Red} on page 11 (line 286) to page 12 (line 314) are the part of the manuscript that has been revised. 
+We want to share the experience for this HNSCC data pre-processes in detail to help further survival analysis in other TCGA cohorts.
+We added a paragraph of "Technical Consideration".
+Also, it is shown here in the following two paragraphs.\\
+We are improving very much from this major revision.
+Thanks for the reviewers' kind help again.
 
@@
 "
+3.3 Technical Consideration\\[0.2cm]
 There are two essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.
@@
 %NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
-According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?\\queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
+According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?queryString=\\SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
 % https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
 % keyword: (SLC35E2) AND "Homo sapiens" 
-SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\\\#!/hgnc\_id/HGNC:20863).
+SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!/\\hgnc\_id/HGNC:20863).
 Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in this TCGA HNSCC dataset from 20499 to 20500.
@@
 Second, we analyzed the error log during the cutoff finding and Cox modeling, 
-the result shows that program running could be halted by several technical problems.
+the result shows that program running could be halted under several technical situation.
 These include:
@@
 
-\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression;
+\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression (coxph), due to zero in M (distant metastasis) patient subgroup;
 \1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;

### 2021-07-06 main.tex
submission

@@
 The PPI network was established using the Search Tool for the Retrieval of Interacting Genes (STRING) and Cytoscape software.
-They validated the candidate genes by using the web-based Tools of Gene Expression Profiling Interactive Analysis tool---GEPIA and Human protein atlas (HPA) databases.
+They validated the candidate genes by using the web-based tools of Gene Expression Profiling Interactive Analysis tool---GEPIA and Human protein atlas (HPA) databases.
 GEPIA was developed, using TCGA datasets, by Zefang Tang and his colleagues (version 1\cite{Tang2017a}, version 2\cite{Tang2019}, and GEPIA2021\cite{Li2021}, available at http://gepia2021.cancer-pku.cn/).

### 2021-07-06 main.tex
submitted on 2021/07/06

@@
 \abstract{The survival analysis of the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover the gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC).
-It is necessary to determine a cutoff point by the patients' dichotomization for the continuous gene expression in survival analysis.
+A cutoff point is usually used in survival analysis for the patients' dichotomization in the continuous gene expression.
 There is some optimization software for cutoff determination.
-However, the software's predetermined cutoffs are usually set at the median or quantiles of RNA sequencing value to perform the survival analyses.
-There are few clinicopathological features available on their pre-processed data sets.
-We applied a in-house workflow, which includes data retrieving and pre-processing, feature selection, sliding-window cutoff selection, Kaplan-Meier survival analysis, and Cox proportional hazard modeling, for biomarker discovery.
-Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes.
-After adjustment with confounders, we found that the clinical tumor stage and the surgical margin involvement are independent risk factors in patient survival.
-According to the resulting tables with Bonferroni adjusted P-value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, CALML5, and FCGBP, are significantly associated with the patients' overall survival.
+However, the software's predetermined cutoffs are usually set at the median or quantiles of gene expression value to perform the analyses.
+There are also few clinicopathological features available on their pre-processed data sets.
+We applied an in-house workflow, including data retrieving and pre-processing, feature selection, sliding-window cutoff selection, Kaplan-Meier survival analysis, and Cox proportional hazard modeling for biomarker discovery.
+In our approach for the TCGA HNSCC cohort, we scanned human protein-coding genes to find optimal cutoff values.
+After adjustment with confounders, the clinical tumor stage and the surgical margin involvement are independent risk factors for patients' prognosis.
+According to the resulting tables with Bonferroni-adjusted \textit{P} value under the optimal cutoff and the hazard ratio, three biomarker candidates, CAMK2N1, CALML5, and FCGBP, are significantly associated with the patients' overall survival.
 We validated this discovery by using the other independent HNSCC dataset (GSE65858).
